### 2022-06-13 main.tex
Initial Overleaf Import

\documentclass[twocolumn,astrosymb]{aastex631}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\code}[1]{\textbf{\texttt{#1}}}
\usepackage{CJKutf8}
\usepackage{bm}
\usepackage{appendix}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{\today}
\revised{\today}
\accepted{\today}

\submitjournal{ApJ}

%% alias for citations
\defcitealias{Greco2018}{G18}

% \def\G18{\citetalias{Greco2018}}

\shorttitle{UDGs in MW analogs}
\shortauthors{Li et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
%% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%% \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{figures/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}
\begin{CJK*}{UTF8}{gbsn}

\title{Ultra Diffuse Galaxies associated with Milky-Way Analogs}

% \correspondingauthor{Jiaxuan Li}
\author[0000-0001-9592-4190]{Jiaxuan Li (李嘉轩)}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

\author[0000-0002-5612-3427]{Jenny E. Greene}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

\author[0000-0003-4970-2874]{Johnny Greco}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}

\author[0000-0003-1385-7591]{Song Huang (黄崧)}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\affiliation{Department of Astronomy and Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China}

\author{Peter Melchior}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

%% I'd like to invite Shany?

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

\end{abstract}

\keywords{Low surface brightness galaxies (940), Dwarf galaxies (416), Galaxy properties (615), Galaxy abundances (574)}

\section{Introduction} \label{sec:intro}

In this work, we use the circularized effective radius $r_{\rm eff}$, defined as the $r_{\rm eff} = r_{\rm eff, sma} \sqrt{b/a}$, where $r_{\rm eff, sma}$ is the effective radius along the semi-major axis of the aligned elliptical isophotes, and $b/a$ is the axis ratio of the isophotes.

We adopt a $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$. We use the AB system \citep{Oke1983} for magnitudes. The stellar mass used in this work is based on a \citet{Chabrier2003} initial mass function.

\section{Data} \label{sec:data}
\subsection{Hyper Suprime-Camera data}
The Hyper Suprime-Camera Subaru Strategic Program Survey (\citealt{Aihara2018}; hereafter HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}. The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source). HSC data are processed using \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Large Synoptic Survey Telescope (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.

In this work, we use the \code{Wide} layer data from Public Data Release 2 (PDR2, also known as \code{S18A}) of HSC \citealt{Aihara2018}. It covers $\sim 300\ \rm{deg}^2$ in all five bands, which is 1.5 times larger than the dataset analyzed in \citetalias{Greco2018}. One of the key improvements made in \code{S18A} is the sky background subtraction. Compared with previous data releases, \code{S18A} adopted a full focal plane sky subtraction algorithm to overcome the over-subtraction of local sky background around bright objects \citep{Aihara2018,Li2021}. The unprecedented depth and careful sky subtraction makes \code{S18A} an ideal dataset to search for low surface brightness galaxies.

%HSC \code{S18A} also provides bitmasks indicating bad pixels, cosmic rays, edges of CCDs and pixels with source detection, helping us generate image masks when extracting surface brightness profiles (Section \ref{sec:hsc_methods}). In this paper, we use the \code{WIDE} layer data from \code{S18A} (\code{PDR2}). It covers $\sim 300$ deg$^2$ in all five bands.

\subsection{NASA-Sloan Atlas}
We use the NASA-Sloan Atlas (NSA \footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies analogous to the Milky Way. NSA is a catalog of parameters of local galaxies derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}. We use the new version of NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$. It also includes elliptical Petrosian aperture photometry for galaxies, which is considered to be more reliable than the photometry used in older versions. In this paper, we use the stellar mass derived from the ellpitical Petrosian photometry using \code{kcorrect v4\_2}. The redshifts of galaxies in NSA come from several spectroscopic surveys, gas surveys, or direct distance measurements.

\section{Methodology}

\subsection{Source Detection}\label{subsec:detection}

How does S18A search different from \citetalias{Greco2018}.

\subsection{Matching with Milky-Way analogs}
The goal of this paper is to study the UDG population hosted by MW-like galaxies. However, the properties of MW itself vary in literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among groups. In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig 2 of \citealt{SAGA-I}). This luminosity range approximately corresponds to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$. They also require the MW analogs to be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20-40 Mpc). In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$ ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA. We choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($\sim 10^{10.7}\ M_\odot$, \citealt{Licquia2015}). MW analogs selected using this definition is very close to those in SAGA but are slightly more massive than the ELVES hosts.

Since UDGs are relatively scarce in MW-like hosts \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics. However, UDGs will be too small and faint to be detected in HSC images beyond certain distances. We choose our redshift range to be $0.01 < z < 0.04$, which makes sure that we can detect a significant number of faint dwarf galaxies around MW-like hosts. We exclude galaxies $z<0.01$ because 1) the number is very small; 2) their large angular size makes them shredded in deblending step, including them will introduce a lot of spurious LSB objects. Our MW analogs sample complements the ELVES sample and SAGA sample in redshift range.

After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left. Then we match them to the LSBG catalog produced in Section \ref{subsec:detection} as follows. For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}. It turns out that 40\% of hosts have virial radii larger than 300 kpc. Then we identify any LSBG that falls into the projected angular virial radius of the host. Then these LSBGs are associated with the host. We repeat this process for all hosts. If one LSBG is associated to multiple hosts, we assign it to the nearest host (normalized by the angular size of virial radius). In the end, we have 901 MW-like hosts and 8,367 LSBGs associated with them.

\subsection{Modeling}

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{completeness.pdf}
	}
	\caption{Caption}
	\label{fig:completeness}
\end{figure*}

\subsection{Measuring structural parameters}
Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands.

\section{Ultra-diffuse galaxies in Milky-Way analogs}

\subsection{MW host selection}

\subsection{UDG sample}
Remember to filter the UDG sample through the FDFC mask, and also remove duplicated objects.
\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{size_distribution.pdf}
    \caption{Caption}
    \label{fig:size_distribution}
\end{figure}

\subsection{Spatial distribution}

\subsection{Quenched fraction}

\section{Discussion and Conclusion}
Scenarios:
1. violent environmental effects: radial orbits, back-splash both explain large size and quenching. But according to Bernavidis et al, the quenched fraction drops with increasing mass.

2. accreting field UDGs, and quench them due to ram pressure stripping. But how long do accreted UDGs last before being destroyed? Need to look at ram pressure stripping literature.

Homework:
1. 1-sigma definition, UPG
2. number of UDG per host, as a function of host mass bins.
3. Move the stellar mass bin definition, try to match with red/blue, spiral/elliptical plot. If cannot match, does this hint the formation scenarios?
4. How significant do we detect blue UDGs? 
5. Split into redshift bins

UDG rejuvenate after ram pressure stripping?

Why red is equivalent to quenched? Need to clarify in the paper

calculate probability of being a backsplash satellite (e.g., splashed to 1.5 Mpc)

Compare spatial distribution with normal dwarf? iF they are indeed high-spin tail of normal dwarfs.

\section*{Acknowledgment}
JL is grateful for discussions with XXX.

\software{\href{http://www.numpy.org}{\code{NumPy}} \citep{Numpy},
          \href{https://www.astropy.org/}{\code{Astropy}} \citep{astropy},  \href{https://www.scipy.org}{\code{SciPy}} \citep{scipy}, \href{https://matplotlib.org}{\code{Matplotlib}} \citep{matplotlib},
          \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017}
          }

\bibliography{citation}{}
\bibliographystyle{aasjournal}

\newpage
\appendix

\section{Mock galaxy tests}

vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$, when deriving the completeness (recovered fraction)

\subsection{Spergel profile}

\subsection{\code{scarlet} measurement error}

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
    \caption{Caption}
    \label{fig:meas_err}
\end{figure}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges
\end{CJK*}
\end{document}

% End of file `sample631.tex'.

### 2022-06-25 main.tex
Updates from Overleaf

@@
 \newcommand{\code}[1]{\textbf{\texttt{#1}}}
+\newcommand{\sersic}{S\'ersic}
 \usepackage{CJKutf8}
@@
 \usepackage{appendix}
+\usepackage{amsmath,amssymb}
 
@@
 \section{Methodology}
+\subsection{Source Detection}\label{subsec:detection}
+\citetalias{Greco2018} performed a search for extended LSBGs in the first $\sim 200$ deg$^2$ of HSC survey.
+We continued the work in \citetalias{Greco2018} and extended the search to HSC \code{S18A} data which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to \code{S16A}.
+We follow the same philosophy of source detection as in \citetalias{Greco2018}, but make several updates to accommodate \code{S18A} data.
+Below we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity.
+We refer interested readers to \citetalias{Greco2018} for more details.
+Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} is also publically available.
 
-\subsection{Source Detection}\label{subsec:detection}
+\begin{enumerate}
+    \item \textbf{Bright source removal}.
+Bright sources and their associated LSB lights can mimic objects of interest and obstruct effective detection of LSBGs.
+In this step, we replace pixels related to bright sources with sky noise.
+The bright sources and their diffuse lights are detected by applying a high thresholding and a low thresholding to the image.
+A diffuse light component is associated with a bright source if more than 15\% of its pixels are above the high threshold.
+In this way, we generate a footprint of bright sources in the image.
 
-How does S18A search different from \citetalias{Greco2018}.
+    Since the sky subtraction in \code{S18A} is significantly better than in previous data releases, LSB features are well conserved after subtracting the sky.
+Therefore, it makes more sense to set the thresholding based on surface brightness, instead of a certain sigma value above sky background (as in \citetalias{Greco2018}).
+We set the high threshold to $\mu_{\rm high} = 22\ \mathrm{mag\ arcsec^{-2}}$ to capture all bright sources above this surface brightness, and the low threshold to $\mu_{\rm low} = 24.5\ \mathrm{mag\ arcsec^{-2}}$ to capture associated diffuse lights.
+
+    %Unlike in \citetalias{Greco2018}, we do not smooth the image prior to thresholding. 
+    After this step, there are still a number of small low surface brightness objects, which are typically marginally resolved galaxies or just pixels with high noise fluctuations.
+We detect and remove them since our main goal is to detect extended LSBGs.
+We run \code{sep}\footnote{\url{https://sep.readthedocs.io/en/v1.1.x/}} \citep{Barbary2016} on the image cleaned as above.
+Based on the segmantation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$.
+This step reduces the number of blended sources.
+These values ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error.
+
+    In the end, we replace pixels within the bright source footprint and small source mask with sky noise.
+The detection is done in $i$-band, and we use the same mask for all $gri$-bands.
+This step effectively cleans out objects and features that hinder the detection of LSBGs.
+
+    \item \textbf{Source Extraction}.
+We use \code{Source Extractor} \citep{Bertin1996} to detect sources on the ``cleaned'' images produced in the previous step.
+This step remains largely the same as in \citetalias{Greco2018}.
+The images are convoled with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast.
+We take a mesh size of $43\arcsec$ (doubles the size used in \citetalias{Greco2018}) to measure the local bacbkground and detect objects that are 0.7$\sigma$ per pixel above the local sky.
+We also require the object contains at least 100 contiguous pixels to further remove small compact objects.
+We perform the detection in $g$-band but require all the sources are also detected in $r$-band to exclude possible artifacts.
+
+    \item \textbf{Initial Sample Selection}.
+In this step, we take the output catalog from the previous step and remove those objects that are not likely to be LSBGs of interest.
+To be specific, we require objects have $g$-band half-light radius (measured by Source Extractor) larger than $r_{\rm min} = 2.0\arcsec$.
+We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$.
+%These cuts are the same as in \citetalias{Greco2018}.
+    \textbf{Morphology? Auto-correlation?}
+
+\end{enumerate}
+After these steps, we have an intial sample containing 86,002 LSBG candidates.
+\textbf{Why we obtain more sources per sqr deg compared with G18?
+Sky?} Among these objects, there are still a lot of false positives, including galaxy outskirts, tidal features, blended compact sources, etc.
+Therefore, we perform an extra ``deblending'' step to remove false positives.
+
+\subsection{Deblending}
+A common type of false positive occurs when point-like sources are blended with diffuse lights from background galaxies or LSB outskirts of  stars and galaxies.
+In order to remove these objects from our sample, we perform non-parametric modeling for  each object using \code{scarlet}\footnote{\url{https://pmelchior.github.io/scarlet/}} \citep{Melchior2018}.
+\code{scarlet} is a deblending and modeling tool designed for multi-band data.
+It utilizes the color and morphology information to seperate blended sources.
+In the following, we briefly summarize how \code{scarlet} works, and we refer intersted readers to \citet{Melchior2018} for more details.
+In \code{scarlet}, each source in the scene $Y_i$ is described by a morphology matrix $S_i$ and a Spectral Energy Distribution (SED) vector $A_i$.
+The goal of modeling is to minimize the object function $f \propto \frac{1}{2}||\sum Y_i - P(\sum A_i S_i)||_2^{2}$ under certain constraints, where $P$ is the convolution with PSF.
+The morphology matrix of each source is limited to be within a bounding box.
+In this section, we assume that all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decreases from their centers to outskirts (monotonoicity constraint).
+Although not all galaxies satisfy the monotonicity constraint, it still provides an easy, sparse, and robust way to deblend overlapping sources.
+We refer to this modeling method as the ``vanilla scarlet''.
+
+In vanilla scarlet, objects can be modeled with different types of sources, including point source, single-extended source, multi-extended source, compact-extended source, and flat-sky source.
+The morphology matrix of point source is simply the normalized PSF.
+For the single-extended source, the morphology matrix follows positivity and monotonicity constraints.
+The multi-extended source is a combination of two or more single-extended sources, which makes it possible to model more complex structure and color gradient of galaxies.
+The compact-extended source is a single-extended source initialized using the morphology matrix of a point-source, which encourages the model to be compact.
+The flat-sky source has uniform color and morphology across the box.
+
+Vanilla scarlet is ideal to identify and remove the false positives in our intial LSBG sample.
+
+We model LSBG candidates using vanilla scarlet as follows.
+
+\begin{enumerate}
+\item \textbf{Peak detection.} We first generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candiate.
+Then we construct a detection image by taking a weighted average of the images in four separate bands.
+We take the total inverse variance as the weight for each band.
+This detection image is considered to be deeper than any single band image.
+
+Next, we detect peaks on the detection image.
+We first run \code{sep} on the detection image using a detection threshold of 4$\sigma$, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels.
+This step idenfities relatively extended sources in the detection image.
+However, there are still faint and compact peaks not detected.
+Therefore, we apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep high spatial frequency components.
+Another round of \code{sep} is then ran on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels.
+This step detects many compact sources that are not detected in the previous step.
+In the end, we combine the two detection catalogs together.
+
+\item \textbf{Model initialization and optimization}.
+The deblending step is designed to deblend sources in the vicinity of the target object.
+The scene will contain both the target object and all the sources in its vicinity.
+Therefore, the sources being modeled is determined by how extended the target is.
+We estimate a bounding box based on the detection image, and include all the peaks inside this box to be modeled.
+
+We use a multi-extended source with two components to model the target object, such that it is capable to capture the details of galaxy structure and color.
+The source is initialized as follows.
+We start by convolving the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}.
+After smoothing, the low surface brightness outskirts of target galaxy will become more prominent, which helps intializing the morphology matrix.
+The smoothed detection image is thresholded using $0.1\sigma$ to remove sky noise, then the morphology matrix $S_i$ of the intial model is determined by constructing a symmetric and monotonic approximation to the region in the detection image around the peak of the target object.
+The intial SED vector $A_i$ is set to be the color of the image averaged with the spatial weight function $S_i$.
+As a byproduct of intialization, we get a bounding box which represents the extent of the target object.
+We also add a flat-sky source to model the local sky around the target.
+This is helpful for situations where an object overlaps with the LSB outskirts of a bright galaxy.
+
+Then we initialize all the sources inside the bounding box of the target.
+The extended objects detected in the first detection step are modeled as single-extended sources.
+For compact objects that are only detected in the second step, we model them as point sources if their FWHM $<$ 5 pixels, otherwise as compact-extended sources.
+The morphology matrices and SED vectors of these sources are also intialized in the same way as above.
+
+As mentinoed above, we only model sources within the bounding box of the target.
+However, scattered lights from nearby bright stars and galaxies could bias the modeling within the bounding box.
+We match our field with the GAIA catalog and mask out stars outside of the bounding box.
+Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.
+
+As a result of such initialization, we only optimize the object function $f$ defined for sources within the bounding box of the target object.
+The optimization process uses the adaptive proximal gradient method \citep{Melchior2019}, which is a robust method for optimization with constraints.
+The model is considered to be converged when the relative changes of parameters are smaller than \code{e\_rel\,=\,2e-4}.
+Typically convergence is achieved after $\sim 50$ steps of opimization and the whole modeling takes about 40s for each LSBG.
+
+\textbf{For bright sources? }
+
+\item \textbf{Measurement.}
+After running vanilla scarlet, we get non-parametric models of objects within the bounding box of the target.
+We take out the model of the target galaxy (as shown in Figure \ref{fig:vanilla_scarlet_demo}) and analyze it using \code{statmorph}\footnote{\url{https://statmorph.readthedocs.io/en/latest/}}\citep{statmorph}.
+The goal of this step is to remove false positives using various morphological and structural diagnostics.
+
+\code{Statmorph} calculates non-parametric morphological and structural parameters, including the half-light radius, concentration-asymmetry-smoothness (CAS) statistics \citep{Conselice2003}, Gini-M20 \citep{Lotz2004}, etc.
+It takes an image, a segmentation map indicating the footprint of the object, a variance map, and PSF.
+For our purpose, the image is just the scarlet model convolved with the observed PSF.
+This image represents the deblended target galaxy.
+Because there is no contaminants in the deblended model, the segmentation map just covers the whole image.
+The variance map and PSF are taken from HSC cutouts.
+We also force the sky level to be zero because sky has already been fit in vanilla scarlet.
+
+One of the most important diagnostics is the size of the object.
+Half-light radius is calculated using ellpitical apertures, where the ellipticity $\varepsilon$ is determined by calculating the second moment of the image.
+We define the circularized half-light radius $r_e$ as the geometrical average of the semi-major and semi-minor axis of the half-light elliptical aperture: $r_e = r_{\rm sma} \sqrt{b/a}$.
+The total magnitudes are simply calculated by summing up the model in each band, and colors are defined by the difference among apparent magnitudes.
+Galactic extinction correction is not applied at this point.
+Two kinds of surface brightnesses are measured.
+The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
+We also define the average surface brightness within effective radius as $\mu_{\rm eff} = m - 2.5 \log_{10}(2 \pi r_e^2)$, where $m$ is the total magnitude.
+
+We also use Gini-M20 and CAS statistics.
+The Gini coefficient \citep{Abraham2003,Lotz2004} and M20 statistics quantify how concentrated/extended is the flux distribution across the image.
+The CAS statistics characterize the concentration ($C = 5\log_{10}(r_{80} / r_{20}$), asymmetry, and smoothness of the light distribution of the object.
+We refer the readers to \citet{statmorph} for more details on their definitions and implementations.
+The morphological and structural parameters are the same in different bands due to the construction of \code{scarlet} model.
+
+We apply the following cuts:
+
+\begin{itemize}
+    \item Color:
+    \[0.0 < g-i < 1.2,\ |(g-r) - 0.7\cdot (g-i)| < 0.25\]
+    \item Size: \[2 \arcsec < r_e < 12 \arcsec\]
+    \item Surface brightness: \[\mu_0(g) > 22.5,\ 23.0 < \mu_{\rm eff}(g) < 27.5,\]
+    \item Morphology: 
+    \begin{gather*}
+        \varepsilon < 0.65,\ 1.8 < C < 3.5,\\
+        \mathrm{Gini} < 0.70,\ M_{20} < -1.1,
+    \end{gather*}
+\end{itemize}
+
+To better guide us on how to use these diagnostics, we visually inspected a subset of LSBG candiates.
+
+The measured parameters here does not neccesarily represent the truth.
+We only use them to rule out false positives in a purely empirical way.
+The half-light radius is often too small because the cookie-cutter effect.
+
+\begin{figure*}
+	\vbox{ 
+		%\vskip -10mm
+		\centering
+		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
+		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
+	}
+	\caption{An example of the deblending step.}
+	\label{fig:vanilla_scarlet_demo}
+\end{figure*}
+
+\end{enumerate}
+
+Common false positives: why we want a deblending step
+Why use scarlet: color info, non-par, monotonic, standard in future HSC, fast. Vanilla scarlet.
+How does it work?
+
+We design metric based on visual inspections for a random subset of LSBG candiates.
+
+We do not do scarlet fitting for the entire initial sample, because time consuming. We first match with MW hosts.
+
+\begin{figure*}
+	\vbox{ 
+		%\vskip -10mm
+		\centering
+		\includegraphics[width=1\linewidth]{completeness.pdf}
+	}
+	\caption{Caption}
+	\label{fig:completeness}
+\end{figure*}
+
+\subsection{Completeness}
+
+Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands.
+
+It is crucial to characterize the detection completeness in order to understand the intrinsic physical properties of the LSBG population.
+We performed a large suite of image simulation to derive the detection completeness.
+We inject $\sim 35,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline.
+This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
+However, we find no noticable difference between this method and the direct injection to coadd images.}.
+The mock galaxies span a wide range in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \epsilon < 0.6$) to match the LSBG distribution in \citetalias{Greco2018}.
+
+The detection completeness as a function of size and surface brightness is shown in the left panel of Figure \ref{fig:completeness}.
+The dependences of completeness on other parameters are very weak and are neglected in this work.
+The detection completeness falls steeply towards the high surface brightenss end and small end.
+This is because we manually excluded objects with high surface brightness in detection.
+\textbf{Explain it a little bit.}
+
+\textbf{Wait... Is the detection efficiency map (jenny sent me) for S18A??? }
+
+\subsection{Modeling and measurement error}
+
+\section{UDGs in Milky-Way analogs}
 
@@
 After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left.
-Then we match them to the LSBG catalog produced in Section \ref{subsec:detection} as follows.
+Then we match them to the LSBG catalog (described in Section \ref{subsec:detection}) as follows.
 For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}.
@@
 If one LSBG is associated to multiple hosts, we assign it to the nearest host (normalized by the angular size of virial radius).
-In the end, we have 901 MW-like hosts and 8,367 LSBGs associated with them.
-
-\subsection{Modeling}
-
-\begin{figure*}
-	\vbox{ 
-		%\vskip -10mm
-		\centering
-		\includegraphics[width=1\linewidth]{completeness.pdf}
-	}
-	\caption{Caption}
-	\label{fig:completeness}
-\end{figure*}
-
-\subsection{Measuring structural parameters}
-Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands.
-
-\section{Ultra-diffuse galaxies in Milky-Way analogs}
-
-\subsection{MW host selection}
+In the end, we have 901 MW-like hosts and 8,367 LSBG candidates associated with them.
+However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shrreded large galaxies, compact sources in galaxy outskirts, etc.
+In the following, we perform a deblending step to effectively remove these spurious objects.
 
@@
 
+TODO:
+1. rerun the matching, compensate the left ~1000 LSBGs.
+2. galactic extinction.
+
 UDG rejuvenate after ram pressure stripping?
@@
           \href{https://www.astropy.org/}{\code{Astropy}} \citep{astropy},  \href{https://www.scipy.org}{\code{SciPy}} \citep{scipy}, \href{https://matplotlib.org}{\code{Matplotlib}} \citep{matplotlib},
-          \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017}
+          \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},
+          \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}
           }

### 2022-06-29 main.tex
Updates from Overleaf

@@
-\documentclass[twocolumn,astrosymb]{aastex631}
+\documentclass[twocolumn,astrosymb,twocolappendix]{aastex631}
 
@@
 \newcommand\latex{La\TeX}
+\newcommand{\sbunit}{mag~arcsec$^{-2}$}
 
@@
 
-\author{Peter Melchior}
+\author[0000-0002-8873-5065]{Peter Melchior}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-\author{Remy Joseph}
+\author[0000-0002-2704-5028]{Remy Joseph}
+\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+\author[0000-0002-1841-2252]{Shany Danieli}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
@@
 \section{Methodology}
-\subsection{Source Detection}\label{subsec:detection}
+Given an overview of the steps here.
+
+\subsection{Source Detection}\label{sec:detection}
 \citetalias{Greco2018} performed a search for extended LSBGs in the first $\sim 200$ deg$^2$ of HSC survey.
@@
 These values ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error.
+We also get feedbacks from the completeness tests.
+Not smoothing the images gives us marginal improvement on completeness.
 
@@
 
-\subsection{Deblending}
+\subsection{Deblending}\label{sec:deblending}
 A common type of false positive occurs when point-like sources are blended with diffuse lights from background galaxies or LSB outskirts of  stars and galaxies.
@@
 
-\begin{enumerate}
-\item \textbf{Peak detection.} We first generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candiate.
+\subsubsection{Peak detection}
+We first generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candiate.
 Then we construct a detection image by taking a weighted average of the images in four separate bands.
@@
 
-\item \textbf{Model initialization and optimization}.
+\subsubsection{Model initialization and optimization}
 The deblending step is designed to deblend sources in the vicinity of the target object.
@@
 
-\textbf{For bright sources? }
+\textbf{For bright sources? Cookie cutter effect}
 
-\item \textbf{Measurement.}
+\begin{figure*}
+	\vbox{ 
+		%\vskip -10mm
+		\centering
+		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
+		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
+	}
+	\caption{An example of the deblending step.}
+	\label{fig:vanilla_scarlet_demo}
+\end{figure*}
+
+\subsubsection{Measurement and false positive removal}\label{sec:non-par-measurement}
 After running vanilla scarlet, we get non-parametric models of objects within the bounding box of the target.
@@
 We refer the readers to \citet{statmorph} for more details on their definitions and implementations.
-The morphological and structural parameters are the same in different bands due to the construction of \code{scarlet} model.
+The morphological and structural parameters are the same in different bands by design of the \code{scarlet} model.
 
-We apply the following cuts:
+To better guide us on how to use these diagnostics, we visually inspected a subset of LSBG candiates in our initial sample (Sec \ref{sec:detection}) and use the labels to construct the metrics.
+We randomly selected 5,000 LSBG candidates that are matched with a host at $0.02 < z < 0.04$ (see Sec \ref{sec:match} for details).
+We run vanilla scarlet and measure morphological parameters for this subsample as described above.
+Then we generate color composite image for each object using HSC $griz$-bands with 0.5 arcmin on a side.
+The visual inspection was done by coauthors JEG, JG, SH, RB.
+Each object has been inspected by at least one person.
+Objects are classified into three types: \code{candy} (LSB galaxies with typicall dwarf galaxy features), \code{galaxy} (high surface brightness galaxies, or galaxies with spiral galaxy features), \code{junk} (false positives, including tidal streams, galaxy outskirts, and other artifacts).
+The difference between \code{candy} and \code{galaxy} can be quite ambiguous.
+In the end, we combine the votes from different persons as follows.
+An object is classified as \code{junk} if the number of votes as \code{junk} prevails the number of votes as \code{candy} and \code{galaxy}.
+For objects that are not \code{junk}, if the number of votes as \code{candy} is larger than that as \code{galaxy}, we assign this object as \code{candy}.
+Everything else is classified as \code{galaxy}.
+In total, there are 1146 \code{candies}, 2146 \code{galaxies}, and 1708 \code{junks}.
 
+We use this visual inspection results to guide us on using the morphological and structural diagnostics.
+The distributions of \code{candy}, \code{galaxy}, and \code{junk} in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}.
+False positives (\code{junk}) are highlighted in red.
+Altough false positives are scattered all over the parameter space, a large fraction of them occupy regions with small size, extreme colors, very faint surface brightness, and large concentration and asymmetry.
+Therefore, we come up the following selection cuts to remove the false positives:
 \begin{itemize}
     \item Color:
-    \[0.0 < g-i < 1.2,\ |(g-r) - 0.7\cdot (g-i)| < 0.25\]
-    \item Size: \[2 \arcsec < r_e < 12 \arcsec\]
-    \item Surface brightness: \[\mu_0(g) > 22.5,\ 23.0 < \mu_{\rm eff}(g) < 27.5,\]
+    \[0.0 < g-i < 1.2,\quad |(g-r) - 0.7\cdot (g-i)| < 0.25\]
+    \item Size: \[1.8 \arcsec < r_e < 12 \arcsec\]
+    \item Surface brightness: \[\mu_0(g) > 22.5,\quad 23.0 < \mu_{\rm eff}(g) < 27.5,\]
     \item Morphology: 
     \begin{gather*}
-        \varepsilon < 0.65,\ 1.8 < C < 3.5,\\
-        \mathrm{Gini} < 0.70,\ M_{20} < -1.1,
+        \varepsilon < 0.65,\quad \mathrm{Gini} < 0.70,\quad M_{20} < -1.1,\\
+        \mathrm{Gini} < -0.136\cdot M_{20} + 0.37,\\
+        1.8 < C < 3.5,\quad A < 0.8.
     \end{gather*}
 \end{itemize}
+These criteria (shown as dashed lines) effectively help us remove objects that are not likely being LSBGs of interest.
+The color cuts here is narrower than the one used in detection to further remove junks and background high redshift galaxies.
+It is worth noticing that we not only remove objects with small sizes, but also remove objects with large size, low surface brightness, and high concentration.
+This is because the scarlet model of some junks can be very concentrated in the center but also extends quite far.
+The slant demarcation line on Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to seperate merging galaxies and normal galaxies.
 
-To better guide us on how to use these diagnostics, we visually inspected a subset of LSBG candiates.
+The distributions of objects after applying the above cuts are shown in the bottom panels of Figure \ref{fig:deblending_cuts}.
+After the cuts, 97\% of the \code{junk} are removed, but the majority (70\%) of \code{candy} still remains.
+The number of \code{galaxy} also drops by 75\%.
+This empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample.
+The numbers used in the selection are purely driven by the visual inspection results.
 
-The measured parameters here does not neccesarily represent the truth.
-We only use them to rule out false positives in a purely empirical way.
-The half-light radius is often too small because the cookie-cutter effect.
+It is worthy noticing that the scarlet modeling and non-parametric measurements is not designed to recover the intrinsic properties of the galaxies.
+They are only used as a diagnotic tool to remove false positives.
+Therefore, the half-light radius measured above does not correspond to the half-light radius of the galaxy itself, but merely a proxy.
+In reality, the vanilla scarlet model usually under-estimates the size and the total flux of LSB objects because the faint outskirts are typically not modeled well due to the non-parametric nature of vanilla scarlet and the monotonicity constraint.
+In Section \ref{sec:modeling}, we propose a method to better measure the size and total magnitude of LSBG using \code{scarlet}.
+We use the parameters measured in Section \ref{sec:modeling} for science.
 
@@
 		\centering
-		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
-		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
+		\includegraphics[width=1.0\linewidth]{deblending_cuts.pdf}
 	}
-	\caption{An example of the deblending step.}
-	\label{fig:vanilla_scarlet_demo}
+	\caption{Deblending cuts.}
+	\label{fig:deblending_cuts}
 \end{figure*}
 
-\end{enumerate}
+Common false positives: why we want a deblending step
 
-Common false positives: why we want a deblending step
-Why use scarlet: color info, non-par, monotonic, standard in future HSC, fast. Vanilla scarlet.
-How does it work?
-
-We design metric based on visual inspections for a random subset of LSBG candiates.
+Why use scarlet: color info, non-par, monotonic, standard in future HSC, fast, high success rate. Vanilla scarlet.
 
 We do not do scarlet fitting for the entire initial sample, because time consuming. We first match with MW hosts.
+
+\subsection{Completeness}
 
@@
 
-\subsection{Completeness}
+%Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands. 
+After the source detection step and the deblending step, we obtain a sample of LSBG candidates where the fraction of false positives is very small.
 
-Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands.
+It is crucial to characterize the completeness of both detection and deblending in order to understand our survey efficiency and the properties of the LSBG population.
+We performed a large suite of image simulation to derive the completeness.
+The overall completeness is a combination of detection and deblending completenesses.
+The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remained after cuts.
 
-It is crucial to characterize the detection completeness in order to understand the intrinsic physical properties of the LSBG population.
-We performed a large suite of image simulation to derive the detection completeness.
-We inject $\sim 35,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline.
+For the detection completeness, we inject $\sim 35,000$ (check number with Johnny) mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline.
 This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
 However, we find no noticable difference between this method and the direct injection to coadd images.}.
-The mock galaxies span a wide range in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \epsilon < 0.6$) to match the LSBG distribution in \citetalias{Greco2018}.
+The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \epsilon < 0.6$), resembling the LSBG distribution in \citetalias{Greco2018}.
+They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$) and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
 
-The detection completeness as a function of size and surface brightness is shown in the left panel of Figure \ref{fig:completeness}.
-The dependences of completeness on other parameters are very weak and are neglected in this work.
-The detection completeness falls steeply towards the high surface brightenss end and small end.
-This is because we manually excluded objects with high surface brightness in detection.
-\textbf{Explain it a little bit.}
+We find the detection completeness mainly depends the size and surface brightness of mock galaxy.
+As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
+It drops below 50\% when the surface brightness gets fainter than 27.5 mag arcsec$^{-2}$.
+We find negligible dependendce of completeness on \sersic{} index, color, and additional structure of galaxy (such as star-forming clumps).
+However, we find the completeness declines above ellipticity $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
+In this work, we neglect the dependences of detection completeness on parameters other than size and surface brightness.
 
-\textbf{Wait... Is the detection efficiency map (jenny sent me) for S18A??? }
+\textbf{Need to update the completeness to the S18A version. Ping Johnny.}
 
-\subsection{Modeling and measurement error}
+For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
+The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
+Following the procedure described in Sec \ref{sec:deblending}, we measure the non-parametric sizes and surface brightnesses on the scarlet models of the mock galaxies.
+The deblending completeness is shown in the middel panel of Figure \ref{fig:completeness}.
+The deblending completeness is high at bright surface brightnesses, but starts to decline with increasing size and surface brightness.
+Mock galaxies fainter than $\overline{\mu}_{\rm eff}(g) > 27.5$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
+The deblending step is very effective on removing false positives, but at a cost of losing very LSB galaxies.
+
+The combined completeness is shown in the right panel of Figure \ref{fig:completeness}.
+The countours shows the 70\%, 50\%, and 20\% completenesses, respectively.
+\textbf{Also compare our completeness with other surveys.}
+
+\textbf{Make sure that completeness is assigned based on the bias-corrected size and SB.}
+
+\subsection{Modeling and measurement error}\label{sec:modeling}
+Although vanilla scarlet does a good job on removing false positives, the measured size, magnitude, and surface brightness on the vanilla scarlet model are quite biased.
+These measurements cannot be used to derive the physical properties of LSBGs.
+
+The non-parametric modeling in \code{scarlet} assumes weak correlation between pixels by imposing the monotonicity constraint.
+This leads to two problems when applying vanilla scarlet to the LSBGs.
+First, since pixels are not strongly correlated in the model, the model cannot capture the galaxy light at very low signal-to-noise ratio.
+Second, the monotonicity constraint stops the model to grow in certain directions if there is another source along this direction, otherwise the monotonicity is broken.
+This issue, dubbed as the ``cookie-cutter effect'', can be seen in Figure \ref{fig:vanilla_scarlet_demo}.
+As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biases the measuremenets.
+
+On the other side, parametric modeling imposes a very strong correlation on pixels.
+For example, using a 1-D light profile such as \sersic{}, pixels within an isophote are assumed to have the same intensity.
+Therefore, the signal-to-noise ratio in the outskirts is boosted by effectively combing the information from many pixels.
+The parametric model also does not suffer from the ``cookie-cutter'' issue.
+
+A traditional way of doing parametric modeling is to first mask out contaminants based on the detection segmentation map, then fit a model to the masked image.
+However, the fitting results are very sensitive to the masking scheme \citep[e.g.,][]{Greco2018}.
+A possible solution to this problem is to model all the objects in the cutout simultaneously using parametric models (e.g., in DECaLS, \citealt{Dey2019}).
+In this work, we combine the advantage of parametric modeling with the power of deblending in \code{scarlet}.
+To be specific, we follow the spirit of deblending as described in Section \ref{sec:deblending}, but replace the non-parametric model for the target with a parametric model.
+In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized.
+
+We use the Spergel light profile to model the LSBGs.
+The Spergel profile is motivated by having a simple analytical expression in Fourier space, making it easy to be convolved with a PSF.\footnote{On the opposite, the \sersic{} profile does not have a simple analytic form in Fourier space.} The surface brightness of a Spergel profile \citep{Spergel2010} has a form of
+\begin{equation}
+    \label{eq:spergel}
+    I_\nu(r) = \frac{c_{\nu}^{2} L_{0}}{2\pi r_{0}^{2}} f_{\nu}\left(\frac{c_{\nu} r}{r_{0}}\right),
+\end{equation}
+where 
+\begin{equation}
+    f_{\nu}(u)=\left(\frac{u}{2}\right)^{\nu} \frac{K_{\nu}(u)}{\Gamma(\nu+1)},
+\end{equation}
+and $K_\nu(u)$ is the Modified Bessel function of the second kind.
+The half-light radius is $r_0$, the total luminosity is $L_0$, and $c_\nu$ satisfyies the equation $(1 + \nu)f_{\nu + 1}(c_\nu) = 1/4$.
+Similar to the \sersic{} index, the parameter $\nu$ (Spergel index) controls the concentration of the light profile.
+As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is interested to the study of LSBGs.
+
+There are several changes in the modeling compared to the deblending step.
+First, we intialize a vanilla scarlet model for the target object as in Section \ref{sec:deblending}.
+Then we measure the half-light radius, total flux, and shape of the scarlet model.
+We use these numbers to initialize the Spergel profile.
+The size of the bounding box is also updated to be the maximum between 250 pixel and $10\, r_e$.
+Objects within this bounding box are included in the modeling, but only the target object is modeled by the Spergel profile.
+For the target, we still requires positivity constraint, as the mononicity is automatically satisfied.
+
+After optimization, we take the $r_0$ in Equation \eqref{eq:spergel} as the circularized half-light radius $r_e$, and take the $L_0$ as the total flux.
+The average surface brightness $\overline{\mu}_{\rm eff}$ is calculated in the same way as in Section \ref{sec:non-par-measurement}.
+
+We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{ap:meas_error}.
+Overall speaking, the measurement agrees with the truth quite well.
+However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$ is under-estiamted.
+We also characterize the bias and the scatter in measurement as a function of size and surface brightness.
+We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.
 
@@
 
-\subsection{Matching with Milky-Way analogs}
+\subsection{Matching with Milky-Way analogs}\label{sec:match}
 The goal of this paper is to study the UDG population hosted by MW-like galaxies.
@@
 After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left.
-Then we match them to the LSBG catalog (described in Section \ref{subsec:detection}) as follows.
+Then we match them to the LSBG catalog (described in Section \ref{sec:detection}) as follows.
 For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}.
@@
 
-\subsection{UDG sample}
+\subsection{UDG sample and UPG sample}
 Remember to filter the UDG sample through the FDFC mask, and also remove duplicated objects.
+
+Also append the catalog.
+
+Plot the UDG and UPG population on the re-abs mag plane (Bovy book)
+
 \begin{figure}
@@
           \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},
-          \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}
+          \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}, \href{https://github.com/dr-guangtou/unagi}{\code{unagi}}.
           }
@@
 
-\section{Mock galaxy tests}
+\section{Spergel profiles}\label{ap:spergel}
+
+In this appendix, we demonstrate that the Spergel profile can approximate \sersic{} profile and profile a lookup table for the correspondence between \sersic{} index $n$ and Spergel index $\nu$.
+
+The surface brightness of a \sersic{} profile follows \citep{Sersic1963,Graham2005}:
+\begin{equation}\label{eq:sersic}
+    I(r)=I_{\mathrm{e}} \exp \left\{-b_{n}\left[\left(\frac{r}{r_{\mathrm{e}}}\right)^{1 / n}-1\right]\right\},
+\end{equation}
+where $r_e$ is the half-light radius, $I_e$ is the surface brightness at $r=r_e$, $n$ is the \sersic{} index.
+The value of $b_n$ satisfies $\Gamma(2 n)=2 \gamma\left(2 n, b_{n}\right)$, where $\gamma(a, x)$ is the incomplete gamma function.
+According to \citet{Graham2005}, the total luminosity of a \sersic{} profile is given by
+\begin{equation}\label{eq:sersic_lum}
+    L_0 = I_{e} r_{e}^{2}\, 2 \pi n\, e^{b_{n}} \left(b_{n}\right)^{-2 n} \Gamma(2 n).
+\end{equation}
+The Spergel profile is described in Section \ref{sec:modeling}.
+
+To study the correspondence between \sersic{} and Spergel profiles, we generate \sersic{} profiles with different \sersic{} indices, and try to fit Spergel profiles to \sersic{} ones.
+The \sersic{} index ranges from $n=0.5$ to $n=4.5$, and both profiles are normalized using $r_e$.
+For each \sersic{} profile, we calculate the total luminosity $L_0$ according to \eqref{eq:sersic_lum} and plug it into the Spergel profile \eqref{eq:spergel} as a fixed value.
+Therefore, only the Spergel index $\nu$ is allowed to vary during the fitting.
+The best-fit Spergel index $\nu$ as a function of \sersic{} index $n$ is shown in the left panel of Figure \ref{fig:spgl_calib}.
+As two examples, we show two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) in the right panel.
+A Spergel profile with $\nu=0.5$ is exactly an exponential profile with $n=1$.
+The de vaucouleurs profile \citep{deVaucouleurs1948} with $n=4$ can be approximated by a Spergel profile with $\nu=-0.74$.
+
+As shown in Figure \ref{fig:spgl_calib}, a \sersic{} profile with small \sersic{} index ($0.5 < n < 1.5$) can be well-approximated by a Spergel profile, although the Spergel profile seems to be more extended than \sersic{} in the outskirts.
+For a \sersic{} profile with high \sersic{} index, the approximation gets worse at both small and large radii.
+Overall, the Spergel profile is a good approximation to \sersic{} from $n\approx 0.5$ to $n\approx 4.5$.
+It is well-known that the light profiles of low-mass galaxies are quite flat and can be described using \sersic{} profiles with $0.5 < n < 1.5$ \citep[e.g.,][]{Lange2015,Greco2018,ELVES-I}.
+It is thus reasonalbe to use Spergel profiles to model the LSBGs (Sec \ref{sec:modeling}) and enjoy its convenience in the Fourier space.
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=0.75\linewidth]{spergel_sersic_calib.pdf}
+	}
+    \caption{The correspondence between the \sersic{} profile \eqref{eq:sersic} and the Spergel profile \eqref{eq:spergel}.
+We fit a Spergel profile to \sersic{} while fixing the total luminosity and half-light radius.
+The left panel shows the best-fit Spergel index $\nu$ as a function of \sersic{} index $n$.
+In the right panel, two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) are shown.
+Spergel profile approximates \sersic{} well for small \sersic{} indices.
+    }
+    \label{fig:spgl_calib}
+\end{figure*}
+
+\section{Measurement Error}\label{ap:meas_error}
+
+We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{ap:meas_error}.
+Overall speaking, the measurement agrees with the truth quite well.
+However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$ is under-estiamted.
+We also characterize the bias and the scatter in measurement as a function of size and surface brightness.
+We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.
 
@@
 
-\subsection{Spergel profile}
+Remember to ref SMUDGES papers here.
 
-\subsection{\code{scarlet} measurement error}
-
-\begin{figure}
+\begin{figure*}
+	\vbox{ 
 		\centering
 		\includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
+	}
     \caption{Caption}
     \label{fig:meas_err}
-\end{figure}
+\end{figure*}
 
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
+\section{Catalog}
+\onecolumngrid
 
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
+\begin{table}
+\caption{UDG (UPG) catalog description} 
+\label{tab:catalog}
+\begin{center}
+\begin{tabular}{l l l}
+\hline\hline
+% \multicolumn{3}{c}{Table: LSBGs (781 rows)}                 \\
+% \hline
+Column Name      & Unit    & Description                    \\
+\hline
+ID                       &         & Unique LSBG ID \\
+ra                       & deg     & Right ascension (J2000) \\
+dec                      & deg     & Declination (J2000) \\
+$r_e$         & arcsec  & Circularized effective radius  \\
+$\sigma(r_e)$ & arcsec  & Uncertainty of $r_e$ \\
+$\overline{\mu}_{\mathrm{eff}}(g)$               & \sbunit & $g$-band average surface brightness within $r_e$ \\
+$\sigma(\overline{\mu}_{\mathrm{eff}}(g))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(g)$           \\
+$\overline{\mu}_{\mathrm{eff}}(r)$               & \sbunit & $r$-band average surface brightness within $r_e$ \\
+$\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
+$\overline{\mu}_{\mathrm{eff}}(i)$               & \sbunit & $i$-band average surface brightness within $r_e$ \\
+$\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
+$m_g$                    & mag     & $g$-band apparent magnitude     \\
+$\sigma(m_g)$            & mag     & Uncertainty of $m_g$            \\
+$m_r$                    & mag     & $r$-band apparent magnitude     \\
+$\sigma(m_r)$            & mag     & Uncertainty of $m_r$            \\
+$m_i$                    & mag     & $i$-band apparent magnitude     \\
+$\sigma(m_i)$            & mag     & Uncertainty of $m_i$            \\
+$g-r$                    & mag     & $g-r$ color                     \\
+$\sigma(g-r)$           & mag     & Uncertainty of $g-r$ color      \\
+$g-i$                    & mag     & $g-i$ color                     \\
+$\sigma(g-i)$           & mag     & Uncertainty of $g-i$ color      \\
+$\nu$                    &         & Spergel index              \\
+$\varepsilon$               &         & Ellipticity                     \\
+$A_g$                    & mag     & $g$-band Galactic extinction \\
+$A_r$                    & mag     & $r$-band Galactic extinction \\
+$A_i$                    & mag     & $i$-band Galactic extinction \\
+\hline\hline
+\end{tabular}
+\end{center}
+\tablecomments{
+These tables are published in their entirety in machine-readable format.
+Magnitudes are on the AB system and have not been corrected for Galactic
+extinction. We provide Galactic extinction corrections, which are derived from
+the \citet{Schlafly:2011aa} recalibration of the \citet{Schlegel:1998aa} dust maps. 
+}
+\end{table}
+
 \end{CJK*}
 \end{document}
-
-% End of file `sample631.tex'.

### 2022-07-12 main.tex
Updates from Overleaf

@@
 %These cuts are the same as in \citetalias{Greco2018}.
-    \textbf{Morphology? Auto-correlation?}
+    \textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}
 
@@
 
-\subsection{Completeness}
-
-\begin{figure*}
-	\vbox{ 
-		%\vskip -10mm
-		\centering
-		\includegraphics[width=1\linewidth]{completeness.pdf}
-	}
-	\caption{Caption}
-	\label{fig:completeness}
-\end{figure*}
-
-%Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands. 
-After the source detection step and the deblending step, we obtain a sample of LSBG candidates where the fraction of false positives is very small.
-
-It is crucial to characterize the completeness of both detection and deblending in order to understand our survey efficiency and the properties of the LSBG population.
-We performed a large suite of image simulation to derive the completeness.
-The overall completeness is a combination of detection and deblending completenesses.
-The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remained after cuts.
-
-For the detection completeness, we inject $\sim 35,000$ (check number with Johnny) mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline.
-This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
-However, we find no noticable difference between this method and the direct injection to coadd images.}.
-The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \epsilon < 0.6$), resembling the LSBG distribution in \citetalias{Greco2018}.
-They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$) and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
-
-We find the detection completeness mainly depends the size and surface brightness of mock galaxy.
-As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
-It drops below 50\% when the surface brightness gets fainter than 27.5 mag arcsec$^{-2}$.
-We find negligible dependendce of completeness on \sersic{} index, color, and additional structure of galaxy (such as star-forming clumps).
-However, we find the completeness declines above ellipticity $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
-In this work, we neglect the dependences of detection completeness on parameters other than size and surface brightness.
-
-\textbf{Need to update the completeness to the S18A version. Ping Johnny.}
-
-For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
-The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
-Following the procedure described in Sec \ref{sec:deblending}, we measure the non-parametric sizes and surface brightnesses on the scarlet models of the mock galaxies.
-The deblending completeness is shown in the middel panel of Figure \ref{fig:completeness}.
-The deblending completeness is high at bright surface brightnesses, but starts to decline with increasing size and surface brightness.
-Mock galaxies fainter than $\overline{\mu}_{\rm eff}(g) > 27.5$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
-The deblending step is very effective on removing false positives, but at a cost of losing very LSB galaxies.
-
-The combined completeness is shown in the right panel of Figure \ref{fig:completeness}.
-The countours shows the 70\%, 50\%, and 20\% completenesses, respectively.
-\textbf{Also compare our completeness with other surveys.}
-
-\textbf{Make sure that completeness is assigned based on the bias-corrected size and SB.}
-
-\subsection{Modeling and measurement error}\label{sec:modeling}
+\subsection{Modeling}\label{sec:modeling}
 Although vanilla scarlet does a good job on removing false positives, the measured size, magnitude, and surface brightness on the vanilla scarlet model are quite biased.
@@
 
-We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{ap:meas_error}.
+We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}.
 Overall speaking, the measurement agrees with the truth quite well.
@@
 We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.
+
+\subsection{Completeness and Measurement Uncertainty}
+
+\subsubsection{Completeness}\label{sec:completeness}
+\begin{figure*}
+	\vbox{ 
+		%\vskip -10mm
+		\centering
+		\includegraphics[width=1\linewidth]{completeness.pdf}
+	}
+	\caption{Caption}
+	\label{fig:completeness}
+\end{figure*}
+
+%Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands. 
+After the source detection step and the deblending step, we obtain a sample of LSBG candidates where the fraction of false positives is very small.
+
+It is crucial to characterize the completeness of both detection and deblending in order to understand our survey efficiency and the properties of the LSBG population.
+We performed a large suite of image simulation to derive the completeness.
+The overall completeness is a combination of detection and deblending completenesses.
+The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remained after cuts.
+
+For the detection completeness, we inject $\sim 35,000$ (check number with Johnny) mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline.
+This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
+However, we find no noticable difference between this method and the direct injection to coadd images.}.
+The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \epsilon < 0.6$), resembling the LSBG distribution in \citetalias{Greco2018}.
+They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$) and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
+
+We find the detection completeness mainly depends the size and surface brightness of mock galaxy.
+As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
+It drops below 50\% when the surface brightness gets fainter than 27.5 mag arcsec$^{-2}$.
+We find negligible dependendce of completeness on \sersic{} index, color, and additional structure of galaxy (such as star-forming clumps).
+However, we find the completeness declines above ellipticity $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
+In this work, we neglect the dependences of detection completeness on parameters other than size and surface brightness.
+
+\textbf{Need to update the completeness to the S18A version. Ping Johnny.}
+
+For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
+The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
+Following the procedure described in Sec \ref{sec:deblending}, we measure the non-parametric sizes and surface brightnesses on the scarlet models of the mock galaxies.
+The deblending completeness is shown in the middel panel of Figure \ref{fig:completeness}.
+The deblending completeness is high at bright surface brightnesses, but starts to decline with increasing size and surface brightness.
+Mock galaxies fainter than $\overline{\mu}_{\rm eff}(g) > 27.5$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
+The deblending step is very effective on removing false positives, but at a cost of losing very LSB galaxies.
+
+The combined completeness is shown in the right panel of Figure \ref{fig:completeness}.
+The countours shows the 70\%, 50\%, and 20\% completenesses, respectively.
+\textbf{Also compare our completeness with other surveys.}
+
+%\textbf{Make sure that completeness is assigned based on the bias-corrected size and SB.} Checked. No problem.
+
+\subsubsection{Measurement uncertainty}\label{sec:meas_unc}
+We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}.
+Overall speaking, the measurement agrees with the truth quite well.
+However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$\sbunit is under-estiamted.
+We also characterize the bias and the scatter in measurement as a function of size and surface brightness.
+We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.
+
+In order to test how well do we recover the photometric and structural parameters in the modeling step (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
+We compare the fitting results with the ground truth in Figure \ref{fig:meas_bias}, where $\Delta(X) = X(\rm truth) - X(\rm measured)$, and x-axis corresponds to the truth values.
+We find that the measured half-light radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and apparent size.
+For surface brightness fainter than 27\ \sbunit, the measured size can be much smaller than the truth.
+As a result, the apparent magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truth.
+
+To correct for this bias in size, surface brightness, apparant magnitude, and color, we assume that the bias only depends on the size and surface brightness.
+Indeed, we do not find any significant dependence of the bias on color, ellpticity, and Spergel index.
+We split the $r_e-\overline{\mu}_{\rm eff}(g)$ plane using a $8\times 8$ grid, and calculate the mean bias within each bin.
+Then we interpolate over the grid using a multiquadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
+Figure \ref{fig:meas_err} shows the interpolated bias terms as a function of the measured size and surface brightness.
+For half-light radius, we take $(r_{e, \rm t} - r_{e, \rm m}) / r_{e,\rm m}$ as the bias term; for surface brightness, we take $\overline{\mu}_{\rm eff, t}(g) - \overline{\mu}_{\rm eff, m}(g)$ as the bias term.
+As shown in Figure \ref{fig:meas_err}, the size and surface brightness bias grows as increasing surface brightness.
+The bias has a peak at $r_e\sim 6\arcsec$ because the $r_e$ shown in the figure is the measured size, not the truth size.
+It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
+We also find that the bias in $g-i$ color is quite small.
+
+For LSBGs in our sample, we apply corrections for the bias using the interpolated bias terms.
+We first correct for the bias in size, $g$-band average surface brightness, $g-r$ and $g-i$ colors.
+Then we calculate the $g$-band apparent magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$.
+The magnitudes and surface brightnesses in other bands are derived using $g$-band magnitude, surface brightness, and colors.
+In this way, we apply a self-consistent correction for the measurement bias to the data.
+
+Besides, it is also important to characterize the measurement uncertainty.
+The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, contamination effects, etc.
+Unlike other parametric modeling code such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimial solution.
+Thus we cannot get a statistical error of the measured properties from \code{scarlet}.
+However, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor.
+Following the same way of calculating the bias, in each bin, we compute the standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid.
+The measurement errors are shown in Figure \ref{fig:meas_err} as contours.
+
+TBD: re-think the way of computing the error, especially for $r_e$.
+
+vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$, when deriving the completeness (recovered fraction)
+
+Remember to ref SMUDGES papers here.
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{meas_bias.pdf}
+	}
+    \caption{Caption}
+    \label{fig:meas_bias}
+\end{figure*}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
+	}
+    \caption{Caption}
+    \label{fig:meas_err}
+\end{figure*}
 
@@
 If one LSBG is associated to multiple hosts, we assign it to the nearest host (normalized by the angular size of virial radius).
-In the end, we have 901 MW-like hosts and 8,367 LSBG candidates associated with them.
+Finally, we have 901 MW-like hosts and 8,367 LSBG candidates associated with them.
 However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shrreded large galaxies, compact sources in galaxy outskirts, etc.
@@
 
-\begin{figure}
+\begin{figure*}
+	\vbox{ 
 		\centering
 		\includegraphics[width=1\linewidth]{size_distribution.pdf}
+	}
     \caption{Caption}
     \label{fig:size_distribution}
-\end{figure}
+\end{figure*}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{radial_distribution.pdf}
+	}
+    \caption{Caption}
+    \label{fig:radial_distribution}
+\end{figure*}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{N_UDG_host_mass.pdf}
+	}
+    \caption{Caption}
+    \label{fig:n_udg}
+\end{figure*}
 
@@
 Homework:
-1. 1-sigma definition, UPG
+1. 1.5-sigma definition, UPG
 2. number of UDG per host, as a function of host mass bins.
@@
 1. rerun the matching, compensate the left ~1000 LSBGs.
-2. galactic extinction.
+2. galactic extinction. Done!!!
 
@@
 \section*{Acknowledgment}
-JL is grateful for discussions with XXX.
+JL is grateful for discussions with XXX. The authors thank Yao-Yuan Mao for his tool for visualizing image cutouts.
 
+The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan and Taiwan, and Princeton University.
+The HSC instrumentation and software were developed by National Astronomical Observatory of Japan (NAOJ), Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU), University of Tokyo, High Energy Accelerator Research Organization (KEK), Academia Sinica Institute for Astronomy and Astrophysics in Taiwan (ASIAA) and Princeton University.
+Funding was contributed by the FIRST program from Japanese Cabinet Office, Ministry of Education, Culture, Sports, Science and Technology (MEXT), Japan Society for the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA and Princeton University.
+\vspace{1em}
 \software{\href{http://www.numpy.org}{\code{NumPy}} \citep{Numpy},
@@
 
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
-	}
-    \caption{Caption}
-    \label{fig:meas_err}
-\end{figure*}
-
 \section{Catalog}
@@
 extinction. We provide Galactic extinction corrections, which are derived from
-the \citet{Schlafly:2011aa} recalibration of the \citet{Schlegel:1998aa} dust maps. 
+the \citet{Schlafly2011} recalibration of the \citet{SFD1998} dust maps. 
 }

### 2022-07-21 main.tex
SB_eff_g >= 24.5 definition
Updates from Overleaf

@@
 \newcommand\latex{La\TeX}
-\newcommand{\sbunit}{mag~arcsec$^{-2}$}
+% \newcommand{\sbunit}{mag~arcsec$^{-2}$}
+\newcommand{\sbunit}{\mathrm{mag\ arcsec}^{-2}}
+\newcommand{\sbeff}{\overline{\mu}_{\mathrm{eff}}(g)}
 
@@
 
-\author[0000-0002-8873-5065]{Peter Melchior}
+\author[0000-0002-1841-2252]{Rachael Beaton}
+\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+\author[0000-0002-2991-9251]{Kirsten Casey}
+\affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
+\author[0000-0002-1841-2252]{Shany Danieli}
+\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+\author[0000-0002-1841-2252]{Andy Goulding}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
@@
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-\author[0000-0002-1841-2252]{Shany Danieli}
+\author[0000-0002-1841-2252]{Erin Kado-Fong}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-
-%% I'd like to invite Shany?
+\author[0000-0002-8873-5065]{Peter Melchior}
+\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
 
@@
 
-\section{Methodology}
+\section{LSBG search in HSC S18A}
 Given an overview of the steps here.
@@
 %These cuts are the same as in \citetalias{Greco2018}.
-    \textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}
+    %\textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}
 
@@
 Overall speaking, the measurement agrees with the truth quite well.
-However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$\sbunit is under-estiamted.
+However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27\ \sbunit$ is under-estiamted.
 We also characterize the bias and the scatter in measurement as a function of size and surface brightness.
@@
 We find that the measured half-light radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and apparent size.
-For surface brightness fainter than 27\ \sbunit, the measured size can be much smaller than the truth.
+For surface brightness fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
 As a result, the apparent magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truth.
@@
 The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, contamination effects, etc.
-Unlike other parametric modeling code such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimial solution.
+Unlike other parametric modeling code such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimal solution.
 Thus we cannot get a statistical error of the measured properties from \code{scarlet}.
@@
 Then we identify any LSBG that falls into the projected angular virial radius of the host.
-Then these LSBGs are associated with the host.
-We repeat this process for all hosts.
-If one LSBG is associated to multiple hosts, we assign it to the nearest host (normalized by the angular size of virial radius).
-Finally, we have 901 MW-like hosts and 8,367 LSBG candidates associated with them.
-However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shrreded large galaxies, compact sources in galaxy outskirts, etc.
-In the following, we perform a deblending step to effectively remove these spurious objects.
+If one LSBG is matched to multiple hosts, we assign it to the nearest host based on the separation normalized by host virial radius.
+Finally, we have 901 MW-like hosts and 10,579 LSBG candidates associated with them.
+However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shredded large galaxies, compact sources in galaxy outskirts, etc.
+As introduced in Section \ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects.
+There are 2,673 objects left after the deblending cuts.
+Next, we model them using the Spergel profile as described in Section \ref{sec:modeling}.
+Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives.
+We also remove duplicated objects.
+In the end, we have 2510 LSBG candidates as our final LSBG sample, from which we construct the ultra-diffuse galaxy (UDG) sample and the ultra-puffy galaxy (UPG) sample as follows.
 
-\subsection{UDG sample and UPG sample}
-Remember to filter the UDG sample through the FDFC mask, and also remove duplicated objects.
+\subsection{UDG and UPG sample}\label{sec:sample}
+The UDG population is usually defined based on the surface brightness and the physical size of the galaxy.
+However, there are many different criteria in literature: \citep{vanDokkum2015} define UDGs to have effective radius $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}, and the size criterion also varies from $>1$ kpc to $>1.5$ kpc.
+\citet{vanNest2022} explore these definitions and find that different choice of UDG could drastically affect which subset of dwarfs are selected, therefore affect our understanding of the UDG population.
+
+The measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020} or other contaminants.
+Therefore in this work, we use the average surface brightness within effective radius $\sbeff$ to define UDG.
+The difference between the average surface brightness and the central surface brightness for \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$.
+Since dwarf galaxies and UDGs typically has \sersic{} index in a range of $0.8 < n < 1.2$ \citep{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value.
+In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, which takes the measurement errors into account.
+This definition maximizes the consistency with the definition in \citet{vanDokkum2015} while not losing UDGs harboring nuclear star clusters.
+
+Among the 2510 LSBG candidates, there are 459 objects satisfying the UDG definition.
+We did a final visual inspection for these objects and excluded 16 objects that are very likely to be false positives.
+We also removed another 8 objects having completeness less than 0.1.
+In the end, we obtain our UDG sample with 435 objects.
+The UDG catalog is available and shown in Table \ref{tab:catalog}.
+
+\vspace{1em}
+
+The concept of UDG was proposed for those dwarf galaxies with large physical size and diffuse light distribution.
+However, the size of a galaxy is strongly correlated with its mass, as known as the mass-size relation \citep[e.g.,][]{Lange2015}.
+The slope of the mass-size relation has been shown to be color-dependent for galaxies above $M_\star > 10^{8.5}\ M_\odot$: blue star-forming galaxies have a shallower slope, whereas red quenched galaxies have a steeper slope.
+However, recent works show that the mass-size relation in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$) is quite universal: the slope and intercept are not sensitive to the color and morphology of dwarf galaxy \citep{ELVES-I}.
+This gives us a chance to define a subset of dwarf galaxies that are outliers on the mass-size plane.
+Taking the measured mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the mass-size relation.
+The UPGs are not necessarily large in physical size or faint in average surface brightness.
+Both UDG and UPG represent subsets of dwarf galaxies that are larger and diffuser than average.
+However, the hard cut on size (1.5 kpc) makes UDG losing ``large'' galaxies at the low-mass end because as mass goes smaller, the average size also gets smaller.
+The surface brightness cut of UDG also biases the UDG sample in color distribution and further bias the quenched fraction, as will be discussed in Section \ref{sec:quench}.
+The definition of UPG based on the observed mass-size relation is more physics-motivated, and UPG better represents a homogeneous subset of dwarf galaxies along the stellar mass axis.
+There is also no color preference in the UPG definition for a given stellar mass.
+It is worth noticing that definition based on mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.
+
+There are 392 objects in our LSBG candidates satisfying that they are $1.5\sigma$ above the ridge line of the mass-size relation.
+After visual inspection and removing objects with completeness less than 0.1, we have 363 galaxies in our UPG sample.
+The distribution of the UDG and UPG sample on the size-surface brightness plane are shown in Figure \ref{fig:udg_upg_re_mu}.
+The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively.
+Two marginal plots show the unnormalized histograms of galaxies in the two color bins.
+The numbers of red and blue galaxies are similar in the UDG sample, but there are more blue galaxies than red ones in the UPG sample.
+Since there is no hard surface brightness cut, the UPG sample includes a lot of blue galaxies with higher surface brightness ($\sbeff < 25$).
+The UPG sample also lose a significant fraction of red galaxies at $25 < \sbeff < 26$, because they are not LSB (hence low-mass) enough to be higher than $1.5\sigma$ from the mass-size relation.
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{udg_upg_sample.pdf}
+	}
+    \caption{The distribution of galaxies in the ultra-diffuse galaxy (UDG) sample (\textit{left}) and the ultra-puffy galaxy (UPG) sample (\textit{right}).
+The UDGs are galaxies with $r_e>1.5$ kpc and $\sbeff > 25.0\sbunit$.
+The UPGs is defined to be $1.5\sigma$ above the mass-size relation in \citet{ELVES-I}.
+We split the samples into two color bins and show them in red ($g-i>0.8$) and blue ($g-i<0.8$).
+The marginal histograms are not normalized to highlight the relative number of red and blue galaxies.
+Compared with the UDG sample, the UPG sample includes blue galaxies with surface brightness higher than the UDG cut ($\sbeff < 25\ \sbunit$) and excludes red galaxies at $25 < \sbeff < 26\ \sbunit$.
+    }
+    \label{fig:udg_upg_re_mu}
+\end{figure*}
+
+\vspace{1em}
+
+% Write about mass calculation, extinction correction, etc.
+We only corrected measured colors for Galactic extinction based on \citet{SFD1998,Schlafly2011}.
+
+\subsection{Background contamination}
+
+\section{Results}
+
+Plot the UDG and UPG population on the re-abs mag plane (Bovy book)
+
+\citet{Trujillo2020}: define size based on surface mass density
 
@@
 
-Plot the UDG and UPG population on the re-abs mag plane (Bovy book)
+SBeff relation with SB0: Yagi, Graham
 
@@
 
-\subsection{Quenched fraction}
+\subsection{Quenched fraction}\label{sec:quench}
+
+\citep{Baxter2021}
+
+\citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.\citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
+	}
+    \caption{Caption}
+    \label{fig:mass_size}
+\end{figure*}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{quenched_frac_dist2host.pdf}
+	}
+    \caption{Caption}
+    \label{fig:qfrac_dist2host}
+\end{figure*}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
+	}
+    \caption{Caption}
+    \label{fig:qfrac_host_color}
+\end{figure*}
 
@@
 $\sigma(r_e)$ & arcsec  & Uncertainty of $r_e$ \\
-$\overline{\mu}_{\mathrm{eff}}(g)$               & \sbunit & $g$-band average surface brightness within $r_e$ \\
-$\sigma(\overline{\mu}_{\mathrm{eff}}(g))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(g)$           \\
-$\overline{\mu}_{\mathrm{eff}}(r)$               & \sbunit & $r$-band average surface brightness within $r_e$ \\
-$\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
-$\overline{\mu}_{\mathrm{eff}}(i)$               & \sbunit & $i$-band average surface brightness within $r_e$ \\
-$\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & \sbunit & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
+$\overline{\mu}_{\mathrm{eff}}(g)$               & $\sbunit$ & $g$-band average surface brightness within $r_e$ \\
+$\sigma(\overline{\mu}_{\mathrm{eff}}(g))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(g)$           \\
+$\overline{\mu}_{\mathrm{eff}}(r)$               & $\sbunit$ & $r$-band average surface brightness within $r_e$ \\
+$\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
+$\overline{\mu}_{\mathrm{eff}}(i)$               & $\sbunit$ & $i$-band average surface brightness within $r_e$ \\
+$\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
 $m_g$                    & mag     & $g$-band apparent magnitude     \\
@@
 $A_i$                    & mag     & $i$-band Galactic extinction \\
+comp & & Completeness \\
+%Host information (ra, dec, Mstar, distance to host, Rvir, g-i) \\
 \hline\hline
@@
 
+Also add external link for fake UDG catalog, etc.
+
 \end{CJK*}

### 2022-07-26 main.tex
before changing quench from 0.28 to 0.23 (consistent with Scott)

@@
 \section{Introduction} \label{sec:intro}
+MW satellites: \citep{Nashimoto2022}
 
@@
 
+%All satellite photometry is in the AB system and cor- rected for MW dust extinction using the E(B − V ) maps of Schlegel et al.
+(1998) recalibrated by Schlafly & Finkbeiner (2011).
+We take the solar g-band magni- tude to be Mg⊙ = 5.03 mag (Willmer 2018).
+
 TBD: re-think the way of computing the error, especially for $r_e$.
@@
 
-Among the 2510 LSBG candidates, there are 459 objects satisfying the UDG definition.
+Among the 2510 LSBG candidates, there are 432 objects satisfying the UDG definition.
 We did a final visual inspection for these objects and excluded 16 objects that are very likely to be false positives.
-We also removed another 8 objects having completeness less than 0.1.
-In the end, we obtain our UDG sample with 435 objects.
-The UDG catalog is available and shown in Table \ref{tab:catalog}.
+We also removed another 4 objects having completeness less than 0.1.
+In the end, we obtain our UDG sample with 412 objects, which are associated with 258 hosts.
+The total sky area occupied by UDG hosts (out to 1 $R_{\rm{vir}}$ is 32.71 deg$^{2}$.
+The UDG catalog is available \textbf{online} and the catalog format is shown in Table \ref{tab:catalog}.
 
@@
 
-There are 392 objects in our LSBG candidates satisfying that they are $1.5\sigma$ above the ridge line of the mass-size relation.
-After visual inspection and removing objects with completeness less than 0.1, we have 363 galaxies in our UPG sample.
+There are 362 objects in our LSBG candidates satisfying that they are $1.5\sigma$ above the ridge line of the mass-size relation.
+After visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
+These UPGs are associated with 239 hosts.
+The total sky area occupied by UPG hosts (out to 1 $R_{\rm{vir}}$ is 32.37 deg$^{2}$.
+
 The distribution of the UDG and UPG sample on the size-surface brightness plane are shown in Figure \ref{fig:udg_upg_re_mu}.
@@
     \caption{The distribution of galaxies in the ultra-diffuse galaxy (UDG) sample (\textit{left}) and the ultra-puffy galaxy (UPG) sample (\textit{right}).
-The UDGs are galaxies with $r_e>1.5$ kpc and $\sbeff > 25.0\sbunit$.
+The UDGs are galaxies with $r_e>1.5$ kpc and $\sbeff > 25.0\ \sbunit$.
 The UPGs is defined to be $1.5\sigma$ above the mass-size relation in \citet{ELVES-I}.
@@
 
-\vspace{1em}
+We derive the stellar masses of galaxies in the UDG and UPG sample from the Spergel model fitting and a color-$M_{\star}/L$ relation from \citet{Into2013}:
+\begin{align*}
+&\log \left(M_{\star} / L_{g}\right)=1.774\,(g-r)-0.783, \\
+&\log \left(M_{\star} / L_{g}\right)=1.297\,(g-i)-0.855.
+\end{align*}
+Because we have both $g-r$ and $g-i$ color available from the model fitting, we use the average of the $M_{\star}/L$ derived from the two colors for calculating stellar mass.
+We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}.
+We corrected for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
+The magnitudes and surface brightnesses are also extinction-corrected.
 
-% Write about mass calculation, extinction correction, etc.
-We only corrected measured colors for Galactic extinction based on \citet{SFD1998,Schlafly2011}.
+\subsection{Background contamination}\label{sec:bkg}
+The major weakness of LSBG searches in photometric data is that distance information is typically unknown.
+Although we have matched LSBGs to MW analogs with known redshifts, the affiliation of LSBGs to the host is still not guaranteed.
+As a result, a certain fraction of galaxies in our UDG and UPG sample might just be foreground or background galaxies that fall within the virial radius of the host by projection.
+Given the volume probed by our search, contamination is more probable to be dominated by background galaxies.
+We estimate the fraction of contamination as follows.
 
-\subsection{Background contamination}
+We selected a patch of sky with 24 deg$^{2}$ in HSC S18A.
+Then we performed the same deblending and modeling steps for 2707 LSBGs detected in this region.
+\footnote{The sky region is randomly selected, and these LSBGs share the same properties with our initial LSBG sample described in Section \ref{sec:match}.} We also removed objects that are already in our UDG sample, and we did visual inspection to further remove spurious objects.
+In the end, there are 480 LSBGs representing a population of possible contaminants in our UDG sample.
+Next, because the UDG is defined based on a physical size, we randomly associate the 483 LSBGs to the hosts of galaxies in our UDG sample.
+Then we calculate a physical radius for each LSBG and classify an LSBG as a ``fake`` UDG if it satisfies the definition.
+We repeat the random matching for 200 times, and we obtain 11,458 fake UDGs.
+In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.94\pm0.03\ \mathrm{deg}^{-2}$.
+In the same way, we get 11,867 fake UPGs in 200 random matches, and the estimated number density of fake UPGs is $S_{\rm UPG} = 2.12\pm0.03\ \mathrm{deg}^{-2}$.
+We use these number density to calculate the fraction of contamination in Section \ref{sec:n_udg}.
+The catalogs of fake UDG and UPGs are also available publicly\footnote{\url{xxxxx}}.
 
 \section{Results}
+
+\subsection{Number of UDG (UPG)}\label{sec:n_udg}
+
+ELVES: g-V correction
 
@@
 \citet{Trujillo2020}: define size based on surface mass density
-
-Also append the catalog.
 
@@
 
+When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish?
+
 \begin{figure*}
@@
 Homework:
-1. 1.5-sigma definition, UPG
-2. number of UDG per host, as a function of host mass bins.
 3. Move the stellar mass bin definition, try to match with red/blue, spiral/elliptical plot. If cannot match, does this hint the formation scenarios?
@@
 TODO:
-1. rerun the matching, compensate the left ~1000 LSBGs.
-2. galactic extinction. Done!!!
+2. galactic extinction.
 
@@
 
-\section{Catalog}
+\section{UDG and UPG Catalogs}
 \onecolumngrid
@@
 $A_i$                    & mag     & $i$-band Galactic extinction \\
+$\log\ M_\star$ & $M_\odot$ & Stellar mass of UDG (UPG) \\
 comp & & Completeness \\
-%Host information (ra, dec, Mstar, distance to host, Rvir, g-i) \\
+weight & & Color-dependent weight (see Section \ref{sec:bkg}) \\
+host\_name & & Name of the host galaxy \\
+host\_ra & & Right ascension (J2000) of the host galaxy \\
+host\_dec & & Declination (J2000) of the host galaxy \\
+host\_log\_m\_star & $M_\odot$ & Host stellar mass\\
+host\_r\_vir & kpc & Virial radius of the host galaxy \\
+host\_g\_i & mag & $g-i$ color of the host galaxy \\
+host\_z &  & Redshift of the hsot galaxy \\
+sep\_to\_host & deg & Angular separation between the host and UDG (UPG)\\
 \hline\hline
@@
 Magnitudes are on the AB system and have not been corrected for Galactic
-extinction. We provide Galactic extinction corrections, which are derived from
+extinction. The information of the host galaxies is from NASA-Sloan Atlas. We provide Galactic extinction corrections, which are derived from
 the \citet{Schlafly2011} recalibration of the \citet{SFD1998} dust maps. 

### 2022-08-12 main.tex
Updates from Overleaf

@@
 \newcommand{\sbeff}{\overline{\mu}_{\mathrm{eff}}(g)}
+\newcommand{\jiaxuan}[1]{\textcolor{orange}{\textbf{Jiaxuan: #1}}}
 
@@
 \section{Introduction} \label{sec:intro}
+
+Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content (van Dokkum et al.
+2018) to their globular cluster populations (Danieli et al.
+2022).
+A central question related to UDGs is what physical mechanisms are responsible for their formation.
+Before we can answer this question, it is important to reliably determine in what environment they live.
+Past UDG studies focused on rich galaxy groups and clusters (e.g., Yagi et al.
+2016, Zatrisky et al.
+2019), which provides distance information.
+Although UDGs are also found in field environments (Prole et al.
+2019, Tanoglidis et al.
+2021, Kadowaki et al.
+2021), most studies of field UDGs lack distances and thus are statistical in nature.
+UDGs in groups and clusters are red and quenched; their blue counterparts are typically found in field environments (for some exceptions see Rom\'{a}n et al.
+2019, Prole et al.
+2019).
+This suggests that environment plays a crucial role in the formation and quenching of UDGs.
+Tidal effects and ram-pressure stripping explains the high quenched fraction in clusters and groups, but it is unclear whether field UDGs quench because of internal processes (feedback) and/or external processes (as splashback satellites, Benavides et al.
+2021).
+It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end.
+A larger UDG sample, especially in low-density environments, is needed to test these hypotheses.
+
+The best knowledge we have about dwarf galaxies at the very faint end was derived from systems in the Local Volume (e.g., Simon 2019, Carlsten et al.
+2021).
+To better compare UDGs with other dwarf systems, we turned to looking for UDGs in the vicinity of Milky Way analogs at $0.01 < z < 0.04$.
+Until now, there are only $\sim 10$ confirmed UDGs associated with MW analogs (Cohen et al.
+2018, Mao et al.
+2021).
+The occurrence rate of UDGs in these low-density environments is unknown, and whether UDGs are quenched in such a regime has not been explored.
+With a sample of UDGs around MW-like hosts, we can compare the structural parameters, quenched fractions, nucleation fractions, and radial distributions with normal satellites in the nearby universe \citep[e.g.,][]{SAGA-II,CarlstenELVES2022}, to shed light on questions about the formation and evolution of the UDGs.
+
+Continuing the work by \citep{Greco2018}, we conducted a systematic search for low surface brightness galaxies (LSBGs) in Hyper Suprime-Cam survey (HSC) imaging data (Li et al., in prep).
+In order to study the formation and evolution of UDGs in low-density environments, we first select host galaxies at $0.01 < z < 0.04$ with Milky-Way masses ($10.2 < \log M_*/M_\odot < 11.2$) in the NASA-Sloan Atlas.
+We matched our HSC LSBGs catalog with the MW-like hosts catalog.
+We assign an LSBG to a host if their angular separation is smaller than the projected virial radius of the host.
+Then we select a UDG sample by requiring the $g$-band average surface brightness within the effective radius\footnote{This surface brightness threshold is equivalent to $\mu_0(g) > 24.0\ \mathrm{mag\ arcsec^{-2}}$ (van Dokkum et al.
+2015) for S\'{e}rsic model with $n=1$.} $\overline{\mu_e} > 24.4\ \mathrm{mag\ arcsec^{-2}}$ and effective radius $R_e > 1.5$ kpc, under the assumption that all matched LSBGs are physically associated with the hosts.
+Following these steps, we have identified $\sim$ 250 UDG candidates to be associated with Milky Way-like hosts in projection.
+They span a wide range of surface brightness, size, color, nucleation, and host properties, making this sample ideal for studying UDG spatial distributions, quenched fractions, mass-size relations, nucleation fractions, and their dependence on host properties.
+
 MW satellites: \citep{Nashimoto2022}
@@
 Therefore in this work, we use the average surface brightness within effective radius $\sbeff$ to define UDG.
-The difference between the average surface brightness and the central surface brightness for \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$.
+The difference between the average surface brightness and the central surface brightness for \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
 Since dwarf galaxies and UDGs typically has \sersic{} index in a range of $0.8 < n < 1.2$ \citep{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value.
@@
 These UPGs are associated with 239 hosts.
-The total sky area occupied by UPG hosts (out to 1 $R_{\rm{vir}}$ is 32.37 deg$^{2}$.
+The total sky area occupied by UPG hosts (out to 1 $R_{\rm{vir}}$) is 32.37 deg$^{2}$.
 
@@
 In the same way, we get 11,867 fake UPGs in 200 random matches, and the estimated number density of fake UPGs is $S_{\rm UPG} = 2.12\pm0.03\ \mathrm{deg}^{-2}$.
-We use these number density to calculate the fraction of contamination in Section \ref{sec:n_udg}.
-The catalogs of fake UDG and UPGs are also available publicly\footnote{\url{xxxxx}}.
-
-\section{Results}
-
-\subsection{Number of UDG (UPG)}\label{sec:n_udg}
-
-ELVES: g-V correction
-
-Plot the UDG and UPG population on the re-abs mag plane (Bovy book)
-
-\citet{Trujillo2020}: define size based on surface mass density
-
-SBeff relation with SB0: Yagi, Graham
-
+The catalogs of fake UDG and UPGs are also available publicly\footnote{\url{https://zenodo.org/}}.
+
+Using the number densities and the probed area of our survey, we calculate the fraction of contamination for both UDG and UPG sample.
+For the UDG sample, there are $f_{\rm contam} \approx 16\%$ contaminants; for the UPG sample, the contamination fraction is $f_{\rm contam} \approx 20\%$.
+We take the contamination fraction into account when calculating the average UDG (UPG) number in Section \ref{sec:results}.
+
+One of the main goals of this paper is to study the star formation status of UDGs and UPGs in MW analogs.
+The star formation rate of galaxies is indicated by broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs.
+However, background contaminants affect the color distribution of the UDG (UPG) sample, thus affect the calculated quenched fraction.
+If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG.
+Indeed, we find that the $g-i$ color distribution of the fake UDG sample is bluer than that of the true UDG sample, which motivates us to assign an importance weights based on $g-i$ color.
+We first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at $(g-i)_{k}$ bins) for both true UDG and fake UDG samples.
+Then we multiply $f_{\rm contam}$ with the histogram of fake UDG sample ($\lambda_k^{\rm fake}$) such that the histogram sums up to the average contamination fraction.
+The weights of UDGs in color bin $(g-i)_k$ is estimated to be $w_k = \max\,(1 - f_{\rm contam} \lambda_k^{\rm fake} / \lambda_k^{\rm true}, 0)$.
+This weight stands for a possibility of being a contaminant.
+The weights of UPGs are assigned following the same procedure.
+We find this color-based contamination subtraction scheme is sufficient for this work since the fraction of contamination is small.
+Our main results shown in Section \ref{sec:results} are robust against contamination subtraction.
+
+\section{Results}\label{sec:results}
+In this section, we present statistical analysis of UDGs and UPGs associated with MW analogs in the nearby Universe. TLDR the full section here?
+
+\subsection{Abundance of UDGs and UPGs}\label{sec:n_udg}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{N_UDG_host_mass.pdf}
+	}
+    \caption{The abundance of UDGs as a function of host halo mass.
+\textit{Left}: We compile the UDG abundance measurements from literature covering a wide range of host mass.
+The UDG abundance of our work $N_{\rm UDG} = 0.76\pm 0.04$ is shown as red square, the power-law relation from \citet{vdBurg2017} is shown in gray, and our fitting result is shown in pink.
+Our UDG abundance is consistent with ELVES but significantly higher than that in SAGA.
+After including more measurements at the lower halo mass end, the power-law is shallower than the relation reported in \citet{vdBurg2017}.
+\textit{Right}: We split the UDG sample into bins based on the host halo mass (triangles) and $g-i$ color (pentagons).
+The UDG abundance is higher for more massive host and redder host.
+}
+    \label{fig:n_udg}
+\end{figure*}
+
+As demonstrated by many previous studies \citep[e.g.,][]{vdBurg2016,vdBurg2017}, the average number of UDGs per host scales with host halo mass.
+While many literature focus on finding UDGs in clusters and large groups, there are less constraints on the UDG abundance at the lower halo mass end.
+In this section, we calculate the UDG abundance of MW analogs, and compare with other surveys.
+
+We define the UDG abundance as the average number of UDGs per host galaxy.
+In our UDG sample, there are 412 UDGs associated with 258 hosts.
+After correcting for background contamination (see Section \ref{sec:bkg}) and completeness (see Section \ref{sec:completeness}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host.
+Here we neglect the fact that the number of satellites contained within the virial sphere is different from the number of satellite within a projected cylinder with virial radius (the so-called deprojection factor, \citealt{vdBurg2017}).
+
+We compare our UDG abundance with other surveys focused on MW analogs.
+In the SAGA survey \citep{SAGA-II}, 6 satellite galaxies (out of 127 spectroscopy-confirmed satellites around 36 MW analogs) satisfy the definition of UDG.
+Therefore the UDG fraction in \citet{SAGA-II} is about $N_{\rm UDG,\, SAGA} \approx 0.17\pm0.07$.
+In the ELVES survey \citep{CarlstenELVES2022}, there are 15 satellites (out of 404 satellites associated with 30 MW analogs) satisfying the UDG definition, leading to a UDG fraction of $N_{\rm UDG,\, ELVES} \approx 0.50\pm0.13$.
+\citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}.
+Since both SAGA and ELVES select satellites based on distance measurements and do not correct for completeness, their UDG abundances are interpreted as lower limits.
+\citet{Roman2017b} do not estimate the background contamination fraction and do not correct for completeness either.
+We plot the UDG abundances of these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017}.
+Among these studies, only \citet{vdBurg2017} applied background subtraction and completeness correction to the raw counts.
+The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray.
+The UDG abundance of this work is highlighted as the red square.
+As shown in Figure \ref{fig:n_udg}, the scatter of $N_{\rm UDG}-M_h$ relation get larger at the lower halo mass end.
+Our UDG abundance is similar to the value in ELVES survey, but is higher than the prediction from \citet{vdBurg2017} but is still considered consistent within scatter.
+The UDG abundances from SAGA is significantly lower than both ELVES and our result.
+This might be explained by different photometric depth of data used.
+SAGA selects dwarf candidates in DECaLS data, which is x mag shallower than the CFTH and HSC data used in ELVES and this work.
+It is probable that SAGA missed a significant fraction of red and lower surface brightness galaxies.
+
+Taking all data points from literature (as shown in Figure \ref{fig:n_udg}), we use orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the pink dashed line in Figure \ref{fig:n_udg}.
+The slope of the power law is shallower than \citet{vdBurg2017} ($\beta=1.11\pm0.07$) but still steeper than \citet{Roman2017b} ($\beta=0.85\pm0.05$).
+Since most individual studies do not have a statistical estimation for background contamination and completeness, the UDG abundances for large groups should be interpreted as lower limits.
+If completeness is applied, it is possible that the slope $\beta$ will be steeper than what we are showing in Figure \ref{fig:n_udg}.
+
+In the right panel, we split the UDG sample into different bins based on their host halo mass (shown as triangles) and color (shown as pentagons).
+The UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger on host color.
+
+% Plot the UDG and UPG population on the re-abs mag plane (Bovy book)
+% \citet{Trujillo2020}: define size based on surface mass density
+% We correct for completeness after statistical contamination subtraction.
+
+\subsection{Size distribution}
 \begin{figure*}
@@
 
+The size distribution of UDGs is an important topic since it has been used to test various UDG formation scenario \citep[e.g.,][]{Amorisco2016,vdBurg2017}.
+In this section, we calculate the size distribution of our UDG and UPG sample.
+We split UDGs into 10 bins in $\log r_e$ with a bin width of 0.06 dex.
+Then we calculate the number of UDGs per bin .
+
+We also take the measurement error in $r_e$ into account.
+
+\subsection{Spatial distribution}
+
 \begin{figure*}
@@
 
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{N_UDG_host_mass.pdf}
-	}
-    \caption{Caption}
-    \label{fig:n_udg}
-\end{figure*}
-
-\subsection{Spatial distribution}
-
 \subsection{Quenched fraction}\label{sec:quench}
@@
 When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish?
+
+This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
 
@@
 
-TODO:
-2. galactic extinction.
-
 UDG rejuvenate after ram pressure stripping?
@@
 Compare spatial distribution with normal dwarf? iF they are indeed high-spin tail of normal dwarfs.
+
+Don't forget to discuss \citep{xSAGA-I}
 
@@
 Funding was contributed by the FIRST program from Japanese Cabinet Office, Ministry of Education, Culture, Sports, Science and Technology (MEXT), Japan Society for the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA and Princeton University.
+
+The authors are pleased to acknowledge that the work reported on in this paper was substantially performed using the Princeton Research Computing resources at Princeton University which is consortium of groups led by the Princeton Institute for Computational Science and Engineering (PICSciE) and Office of Information Technology's Research Computing.
+
 \vspace{1em}

### 2022-08-16 main.tex
Updates from Overleaf

@@
 
-Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content (van Dokkum et al.
-2018) to their globular cluster populations (Danieli et al.
+Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content \citep{vanDokkum2018,vanDokkum2019} to their globular cluster populations (Danieli et al.
 2022).
@@
 Before we can answer this question, it is important to reliably determine in what environment they live.
-Past UDG studies focused on rich galaxy groups and clusters (e.g., Yagi et al.
-2016, Zatrisky et al.
-2019), which provides distance information.
-Although UDGs are also found in field environments (Prole et al.
-2019, Tanoglidis et al.
-2021, Kadowaki et al.
-2021), most studies of field UDGs lack distances and thus are statistical in nature.
-UDGs in groups and clusters are red and quenched; their blue counterparts are typically found in field environments (for some exceptions see Rom\'{a}n et al.
-2019, Prole et al.
-2019).
+Past UDG studies focused on rich galaxy groups and clusters \citep[e.g.,][]{Yagi2016,Zaritsky2019}, which provides distance information.
+Although UDGs are also found in field environments \citep{Prole2019,Tanoglidis2021,Kadowaki2021}, most studies of field UDGs lack distances and thus are statistical in nature.
+UDGs in groups and clusters are red and quenched; their blue counterparts are typically found in field environments (for some exceptions see \citealt{Roman2019,Prole2019}).
 This suggests that environment plays a crucial role in the formation and quenching of UDGs.
-Tidal effects and ram-pressure stripping explains the high quenched fraction in clusters and groups, but it is unclear whether field UDGs quench because of internal processes (feedback) and/or external processes (as splashback satellites, Benavides et al.
-2021).
+Tidal effects and ram-pressure stripping explains the high quenched fraction in clusters and groups, but it is unclear whether field UDGs quench because of internal processes (feedback) and/or external processes (as splashback satellites, \citealt{Benavides2021}).
 It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end.
@@
 
-The best knowledge we have about dwarf galaxies at the very faint end was derived from systems in the Local Volume (e.g., Simon 2019, Carlsten et al.
-2021).
+The best knowledge we have about dwarf galaxies at the very faint end was derived from systems in the Local Volume \citep[e.g.,][]{Simon2019,CarlstenELVES2022}.
 To better compare UDGs with other dwarf systems, we turned to looking for UDGs in the vicinity of Milky Way analogs at $0.01 < z < 0.04$.
-Until now, there are only $\sim 10$ confirmed UDGs associated with MW analogs (Cohen et al.
-2018, Mao et al.
-2021).
+Until now, there are only $\sim 30$ confirmed UDGs associated with MW analogs \citep{Cohen2018,SAGA-II,CarlstenELVES2022}.
 The occurrence rate of UDGs in these low-density environments is unknown, and whether UDGs are quenched in such a regime has not been explored.
@@
 
-Continuing the work by \citep{Greco2018}, we conducted a systematic search for low surface brightness galaxies (LSBGs) in Hyper Suprime-Cam survey (HSC) imaging data (Li et al., in prep).
+% Continuing the work by \citep{Greco2018}, we conducted a systematic search for low surface brightness galaxies (LSBGs) in Hyper Suprime-Cam survey (HSC) imaging data (Li et al., in prep).
 In order to study the formation and evolution of UDGs in low-density environments, we first select host galaxies at $0.01 < z < 0.04$ with Milky-Way masses ($10.2 < \log M_*/M_\odot < 11.2$) in the NASA-Sloan Atlas.
@@
 However, scattered lights from nearby bright stars and galaxies could bias the modeling within the bounding box.
-We match our field with the GAIA catalog and mask out stars outside of the bounding box.
+We match our field with the Gaia catalog and mask out stars outside of the bounding box.
 Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.
@@
 
-\subsection{Size distribution}
+\subsection{Size distribution}\label{sec:size_distr}
 \begin{figure*}
@@
 
-The size distribution of UDGs is an important topic since it has been used to test various UDG formation scenario \citep[e.g.,][]{Amorisco2016,vdBurg2017}.
+The size distribution of UDGs is an important topic since it has been used to test UDG formation scenarios \citep[e.g.,][]{Amorisco2016,vdBurg2017}.
 In this section, we calculate the size distribution of our UDG and UPG sample.
-We split UDGs into 10 bins in $\log r_e$ with a bin width of 0.06 dex.
-Then we calculate the number of UDGs per bin .
-
-We also take the measurement error in $r_e$ into account.
-
-\subsection{Spatial distribution}
+First of all, we take the fake UDGs in random fields and calculate their size distribution as a proxy for background contamination, shown as the gray dots in the left panel of Figure \ref{fig:size_distribution}.
+For each host, we calculate the raw size distribution of the associated UDGs (black dots), and we multiply background size distribution by the virial area of the host and subtract it from the UDG size distribution (teal dots).
+Then we combine the UDG size distributions for all hosts together, and correct for completeness (red squares).
+Since the stellar masses of the hosts in our sample are quite similar, we do not weight each host according to their masses.
+The error shown in Figure \ref{fig:size_distribution} takes both Poisson error and the measurement error of size into account.
+
+We find that the UDG size distribution roughly follows a power law.
+We fit a power law relation to our UDG size distribution and get $n\propto r_e^{-1.60\pm0.21}$.
+This is shallower than the power law presented in \citet{vdBurg2016} ($n\propto r_e^{-3.40\pm0.19}$) and \citet{vdBurg2017} ($n\propto r_e^{-2.71\pm0.33}$, shown as gray dash-dotted lines in Figure \ref{fig:size_distribution}).
+We also split the UDG sample based on their host stellar mass, but consistently find shallow power-laws with index $\sim -1.6$.
+\citet{vdBurg2016} studies large galaxy clusters and find a very steep slope, \citet{vdBurg2017} includes less-massive groups and the slope is less steep.
+Combined with our findings, it might be possible that dense environment produces more small UDGs.
+\jiaxuan{Have anything to do with tidal stripping?
+UDGs in denser environs are more stripped thus smaller?}
+
+We also show the size distribution of UPGs in the right panel of Figure \ref{fig:size_distribution}.
+Unlike UDGs, we make the UPG sample by cutting through the 1.5$\sigma$ line above the mass-size relation.
+Therefore, for a given mass, many small UDGs are not in the UPG sample since their sizes are not extreme on the mass-size plane.
+As a consequence, the size distribution of UPG sample is suppressed at the smaller size end.
+
+\subsection{Radial distribution}\label{sec:radial_distr}
+Since the discovery of UDGs in Coma cluster, the radial distribution of UDGs around the hosts has been a valuable tool to test various UDG formation theories (cite simulation papers).
+In \citet{vanDokkum2015}, UDGs are not found within 300 kpc from the cluster center, hinting that UDGs might not survive in such a dense environment.
+\citet{vdBurg2016} has also found that the number of UDGs is suppressed near the center of clusters, and the radial distribution of UDGs in cluster environments roughly follows a projected Einasto \citep{Einasto1965} profile.
+In the following, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.
+
+We calculate the radial distribution as follows.
+For each host, we count the number of UDGs in each radial bin scaled by $R_{\rm vir}$ and calculate the number density within each radial annulus.
+We subtract the contribution of background contaminants based on the background contamination density (Sec.
+\ref{sec:bkg}) and the angular area occupied by the host.
+Then we average over all hosts and correct for the completeness, as shown in Figure \ref{fig:radial_distribution}.
+Red squares are the number of UDGs (UPGs) per radial bin, and the error includes Poisson error, background subtraction error, and completeness error.
+The radial distributions of both UDGs and UPGs turn over around $R=0.2\,R_{\rm vir}$.
+It is known that the detection can be more incomplete as it gets closer to the host due to the blending between UDG and the host galaxy outskirts and possible sky subtraction issues.
+Although we have corrected the completeness for each object based on their size and surface brightness, it is still possible that our completeness does not include the dependence on the distance to the host.
+As we mentioned above, it is also possible that UDGs and UPGs are depleted because of strong tidal interactions.
+
+We fit the radial distributions of UDG (UPG) with the projected NFW and Einasto profiles at $R > 0.2 R_{\rm vir}$.
+The Einasto profile introduces an extra ``shape'' parameter $\alpha$ and has been argued to be a better description to the dark matter halo profiles \citep[e.g.,][]{Navarro2004,Gao2008,Navarro2010,Dutton2014}.
+Einasto profile also makes concentration estimates less sensitive to the radial range fitted.
+The best-fit NFW and Einasto profiles are shown in Figure \ref{fig:radial_distribution} as blue and red lines, respectively.
+The best-fit Einasto profile from \citet{vdBurg2016} is shown as the dashed gray line.
+
+Compared with \citet{vdBurg2016}, there are more UDGs at smaller radial distances in our sample, thus the UDG radial distribution is more concentrated although we exclude $R < 0.2\ R_{\rm vir}$.
+Unlike \citet{vdBurg2016}, we find that both NFW and Einasto could describe the radial distribution of UDGs (UPGs) quite well.
+The concentration of the best-fit NFW profile is $c_{\rm NFW, UDG} = 10.1^{+6.5}_{-3.9}$ for UDGs and $c_{\rm NFW, UPG} = 10.9^{+8.9}_{-4.9}$ for UPGs.
+The best-fit Einasto profile has $\alpha_{\rm Ein, UDG} = 0.44^{+0.42}_{-0.22},\ c_{\rm Ein, UDG} = 3.30^{+2.07}_{-1.27}$ for UDGs and $\alpha_{\rm Ein, UPG} = 0.40^{+0.56}_{-0.23},\ c_{\rm Ein, UPG} = 3.55^{+3.63}_{-1.80}$ for UPGs.
+The radial distribution profiles of UDGs and UPGs are found to be very similar in shape.
+Our best-fit Einasto profiles have lower $\alpha$ and higher concentration compared with \citet{vdBurg2016} where $\alpha_{\rm Ein} = 0.92^{+0.08}_{-0.18},\ c_{\rm Ein} = 1.83^{+0.13}_{-0.12}$.
+
+According to the concentration-mass relation of dark matter halos, the concentration of MW-like halo is $c_{\rm NFW} \sim 10$ \citep{Bullock2001,Duffy2008,Dutton2014}.
+Therefore, if assuming an NFW profile, the UDGs and UPGs follow the underlying dark matter distribution of the host.
+However, the Einasto shape parameter for a MW-like halo is $\alpha\sim 0.15$ at $z=0$ and its concentration $c\sim 8-10$.
+\citep{Gao2008,Dutton2014}.
+Comparing with this, the best-fit Einasto profiles for UDG (UPG) radial distribution have larger shape parameter $\alpha$ and smaller concentration $c$.
+We notice that the errors of the best-fit parameters are large due to the sample size and also the fact that concentration is most sensitive to data at smaller radial distances which are excluded in the analysis.
+Therefore, the UDG (UPG) radial distribution can be considered consistent with the dark matter distribution of the host.
+Nevertheless, a larger and more complete sample is needed to better constrain the radial distributions.
 
@@
 	}
+    \caption{The radial distributions of UDGs (\textit{left}) and UPGs (\textit{right}).
+We subtract the background contamination (shown in teal) and correct for completeness in each radial distance bin (shown in red).
+We fit the projected NFW and Einasto profiles to the radial distributions and find good fits for both profiles.
+The radial distributions of UDGs and UPGs are similar in shape.
+The best-fit NFW concentrations is consistent with a MW-mass halo, whereas the best-fit Einasto profiles have smaller concentration than MW-mass halos.}
+    \label{fig:radial_distribution}
+\end{figure*}
+
+\subsection{Quenched fraction}\label{sec:quench}
+Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched.
+Among others, tidal stripping and ram-pressure stripping are thought to quench the satellites.
+
+UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields, however there are one or two red UDGs in fields.
+It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up?
+3) how are they quenched?
+what's the correlation between quenching and puffing.
+
+We compare with SAGA quenched fraction (Mao) and ELVES (Carlsten, Greene in prep).
+
+\citep{Baxter2021}
+
+\citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.
+\citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.
+
+When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish? because we don't know about their mass-size.
+
+The mass-size doesn't depend on color (carlsten). The quenched fraction also doesn't depend on size. Reflect on Danieli\&vD mass-size slice paper.
+
+SAGA misses a fraction of red faint galaxies in their intial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
+SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{quenched_frac_dist2host.pdf}
+		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
+	}
     \caption{Caption}
-    \label{fig:radial_distribution}
-\end{figure*}
-
-\subsection{Quenched fraction}\label{sec:quench}
-
-\citep{Baxter2021}
-
-\citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.\citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.
-
-When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish?
-
-This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
+    \label{fig:qfrac_dist2host}
+\end{figure*}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
+	}
+    \caption{Caption}
+    \label{fig:qfrac_host_color}
+\end{figure*}
 
@@
 
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{quenched_frac_dist2host.pdf}
-	}
-    \caption{Caption}
-    \label{fig:qfrac_dist2host}
-\end{figure*}
-
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
-	}
-    \caption{Caption}
-    \label{fig:qfrac_host_color}
-\end{figure*}
-
 \section{Discussion and Conclusion}
+TODO: make data products (catalogs, fake UDGs, website for their images, etc.)
+
+\subsection{A better definition for diffuse galaxies}
+
+discuss pros and cons of UDG and UPG (you have to assume a distance to define UPG).
+
 Scenarios:
@@
 \section*{Acknowledgment}
-JL is grateful for discussions with XXX. The authors thank Yao-Yuan Mao for his tool for visualizing image cutouts.
+JL is grateful for discussions with Meng Gu. The authors thank Yao-Yuan Mao for his tool for visualizing image cutouts.
 
@@
           \href{https://www.astropy.org/}{\code{Astropy}} \citep{astropy}, \href{https://www.scipy.org}{\code{SciPy}} \citep{scipy}, \href{https://matplotlib.org}{\code{Matplotlib}} \citep{matplotlib},
-          \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},
+        %   \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},
+          \href{https://bdiemer.bitbucket.io/colossus/index.html}{\code{Colossus}} \citep{Colossus},
           \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}, \href{https://github.com/dr-guangtou/unagi}{\code{unagi}}.
@@
 \section{Spergel profiles}\label{ap:spergel}
+\begin{figure*}[htbp!]
+	\vbox{ 
+		\centering
+		\includegraphics[width=0.75\linewidth]{spergel_sersic_calib.pdf}
+	}
+    \caption{The correspondence between the \sersic{} profile \eqref{eq:sersic} and the Spergel profile \eqref{eq:spergel}.
+We fit a Spergel profile to \sersic{} while fixing the total luminosity and half-light radius.
+The left panel shows the best-fit Spergel index $\nu$ as a function of \sersic{} index $n$.
+In the right panel, two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) are shown.
+Spergel profile approximates \sersic{} well for small \sersic{} indices.
+    }
+    \label{fig:spgl_calib}
+\end{figure*}
 
@@
 A Spergel profile with $\nu=0.5$ is exactly an exponential profile with $n=1$.
-The de vaucouleurs profile \citep{deVaucouleurs1948} with $n=4$ can be approximated by a Spergel profile with $\nu=-0.74$.
+The de Vaucouleurs profile \citep{deVaucouleurs1948} with $n=4$ can be approximated by a Spergel profile with $\nu=-0.74$.
 
@@
 
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=0.75\linewidth]{spergel_sersic_calib.pdf}
-	}
-    \caption{The correspondence between the \sersic{} profile \eqref{eq:sersic} and the Spergel profile \eqref{eq:spergel}.
-We fit a Spergel profile to \sersic{} while fixing the total luminosity and half-light radius.
-The left panel shows the best-fit Spergel index $\nu$ as a function of \sersic{} index $n$.
-In the right panel, two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) are shown.
-Spergel profile approximates \sersic{} well for small \sersic{} indices.
-    }
-    \label{fig:spgl_calib}
-\end{figure*}
-
-\section{Measurement Error}\label{ap:meas_error}
-
-We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{ap:meas_error}.
+% \section{Measurement Error}\label{ap:meas_error}
+
+% We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{ap:meas_error}.
 Overall speaking, the measurement agrees with the truth quite well.
@@
 
-vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$, when deriving the completeness (recovered fraction)
-
-Remember to ref SMUDGES papers here.
+% vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$, when deriving the completeness (recovered fraction)
+
+% Remember to ref SMUDGES papers here.
 

### 2022-08-16 main.tex
Updates from Overleaf

@@
 \affiliation{Department of Astronomy and Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China}
-
+\author[0000-0002-8873-5065]{Peter Melchior}
+\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+\author[0000-0002-2704-5028]{Remy Joseph}
+\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
 \author[0000-0002-1841-2252]{Rachael Beaton}
@@
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-\author[0000-0002-2704-5028]{Remy Joseph}
-\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
 \author[0000-0002-1841-2252]{Erin Kado-Fong}
-\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-\author[0000-0002-8873-5065]{Peter Melchior}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
@@
 It also includes elliptical Petrosian aperture photometry for galaxies, which is considered to be more reliable than the photometry used in older versions.
-In this paper, we use the stellar mass derived from the ellpitical Petrosian photometry using \code{kcorrect v4\_2}.
+In this paper, we use the stellar mass derived from the elliptical Petrosian photometry using \code{kcorrect v4\_2}.
 The redshifts of galaxies in NSA come from several spectroscopic surveys, gas surveys, or direct distance measurements.
@@
 \section{LSBG search in HSC S18A}
-Given an overview of the steps here.
+Given an overview of the steps here. Also read SMUDGES paper and discuss some aspects here.
 
@@
 We model LSBG candidates using vanilla scarlet as follows.
+
+Our code \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} is also available on GitHub.
 
@@
 \subsection{Radial distribution}\label{sec:radial_distr}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{radial_distribution.pdf}
+	}
+    \caption{The radial distributions of UDGs (\textit{left}) and UPGs (\textit{right}).
+We subtract the background contamination (shown in teal) and correct for completeness in each radial distance bin (shown in red).
+We fit the projected NFW and Einasto profiles to the radial distributions and find good fits for both profiles.
+The radial distributions of UDGs and UPGs are similar in shape.
+The best-fit NFW concentrations is consistent with a MW-mass halo, whereas the best-fit Einasto profiles have smaller concentration than MW-mass halos.}
+    \label{fig:radial_distribution}
+\end{figure*}
+
 Since the discovery of UDGs in Coma cluster, the radial distribution of UDGs around the hosts has been a valuable tool to test various UDG formation theories (cite simulation papers).
@@
 We notice that the errors of the best-fit parameters are large due to the sample size and also the fact that concentration is most sensitive to data at smaller radial distances which are excluded in the analysis.
-Therefore, the UDG (UPG) radial distribution can be considered consistent with the dark matter distribution of the host.
+Therefore, the UDG (UPG) radial distribution is considered to be consistent with the dark matter distribution of the host at a $2\sigma$ level.
 Nevertheless, a larger and more complete sample is needed to better constrain the radial distributions.
 
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{radial_distribution.pdf}
-	}
-    \caption{The radial distributions of UDGs (\textit{left}) and UPGs (\textit{right}).
-We subtract the background contamination (shown in teal) and correct for completeness in each radial distance bin (shown in red).
-We fit the projected NFW and Einasto profiles to the radial distributions and find good fits for both profiles.
-The radial distributions of UDGs and UPGs are similar in shape.
-The best-fit NFW concentrations is consistent with a MW-mass halo, whereas the best-fit Einasto profiles have smaller concentration than MW-mass halos.}
-    \label{fig:radial_distribution}
-\end{figure*}
-
 \subsection{Quenched fraction}\label{sec:quench}
-Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched.
-Among others, tidal stripping and ram-pressure stripping are thought to quench the satellites.
-
-UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields, however there are one or two red UDGs in fields.
-It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up?
-3) how are they quenched?
-what's the correlation between quenching and puffing.
-
-We compare with SAGA quenched fraction (Mao) and ELVES (Carlsten, Greene in prep).
-
-\citep{Baxter2021}
-
-\citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.
-\citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.
-
-When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish? because we don't know about their mass-size.
-
-The mass-size doesn't depend on color (carlsten). The quenched fraction also doesn't depend on size. Reflect on Danieli\&vD mass-size slice paper.
-
-SAGA misses a fraction of red faint galaxies in their intial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
-SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.
 
@@
     \caption{Caption}
-    \label{fig:qfrac_dist2host}
+    \label{fig:qfrac}
 \end{figure*}
 
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
-	}
-    \caption{Caption}
-    \label{fig:qfrac_host_color}
-\end{figure*}
+Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched.
+Among others, tidal stripping and ram-pressure stripping are thought to quench the satellites.
+
+In this section we show the quenched fraction of UDG/UPGs without discussing too much about the physical implication on both UDG population and the general quenching-mass-size relation.
+
+UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields \citep{Prole2019,Leisman2017}, however there are one or two red UDGs in fields.
+It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up?
+3) how are they quenched?
+what's the correlation between quenching and puffing.
+
+Find literature for quenched fraction as a function of distance to host (Einasto 1974, Spekkens2014, Karunakaran2022 for MW and M31).
+
+We compare with SAGA quenched fraction (Mao) and ELVES (Carlsten, Greene in prep).
+
+\citep{Baxter2021}
+
+\citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.
+\citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.
+
+When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish? because we don't know about their mass-size.
+
+The mass-size doesn't depend on color (carlsten). The quenched fraction also doesn't depend on size. Reflect on Danieli\&vD mass-size slice paper.
+
+SAGA misses a fraction of red faint galaxies in their intial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
+SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.
+
+\section{Discussion and Conclusion}
+TODO: make data products (catalogs, fake UDGs, website for their images, etc.)
+\subsection{High quenched fraction of UDGs is an artifact}
 
@@
 
-\section{Discussion and Conclusion}
-TODO: make data products (catalogs, fake UDGs, website for their images, etc.)
-
-\subsection{A better definition for diffuse galaxies}
+\subsection{UDG formation}
+Discuss how does quenching and pufffing interplay.
+
+Galaxy conformity: mass-size independent of color, jenny's quenched fraction independent of morph.
+
+Pre-puffed up or pre-quenched?
+
+Amorisco with my size distribution?
 
@@
 Don't forget to discuss \citep{xSAGA-I}
+
+\subsection{A better definition for diffuse galaxies}
 

### 2022-08-16 main.tex
Updates from Overleaf

@@
 
-One of the main goals of this paper is to study the star formation status of UDGs and UPGs in MW analogs.
+One of the main goals of this paper is to study the star-forming properties of UDGs and UPGs in MW analogs.
 The star formation rate of galaxies is indicated by broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs.
@@
 
+The star-forming properties of UDGs and UPGs is an interesting subject given their diffuse stellar component and possible non-trivial formation history.
+In this section, we study the fraction of quenched UDGs and UPGs as a function of both stellar mass and their host properties.
+We defer the discussion on the implications of these results to Section \ref{sec:discussion}.
+
+We refer to quenching as the cessation of star formation in galaxies.
+In principle, direct estimates for the instantaneous star formation rate (SFR) from UV or H$\alpha$ are needed to define a quenched galaxy  population.
+As an example, the SAGA survey measures the H$\alpha$ equivalent width (EW) from spectra to define quenched satellites.
+However, these specific data sets are either not deep enough to probe our UDGs and UPGs, or they are very expensive to obtain and cover all the footprint of our sample.
+Therefore, we seek other indicators including integrated color and morphology to approximate star-forming properties.
+\citet{CarlstenELVES2022} visually inspected all satellites and classified them into early-type (red and smooth) and late-type (blue, asymmetric, clumpy).
+Using this sample, they find that a mass-dependent color cut $g-i = -0.067 M_V - 0.23$ could also divide the sample into early- and late-type that are nearly identical to the ones based on morphology.
+The derived quenched fractions based on morphology and color are very similar.
+Furthermore, \citet{Font2022} showed in simulations that this color cut effectively separates star forming galaxies from quenched ones.
+Since we do not visually inspect all UDGs and UPGs in our sample, we take the color cut from \citet{CarlstenELVES2022} to define our quenched galaxies: galaxies that are redder than $g-i > -0.067 M_V - 0.23$ are defined as quenched, whereas those bluer galaxies are thought to be star-forming.
+However, one caveat is that this criterion was derived from LV satellites in \citet{CarlstenELVES2022}, and the bulk of them are brighter than our UDGs and UPGs.
+It is not guaranteed that the same color cut would work in our regime.
+\footnote{Changing the intercept of the color cut to -0.28 makes the overall quenched fraction higher, but does not change the trend of quenched fraction as a function of stellar mass.}
+
+We derive V-band apparent magnitude following $V = g - 0.5784\, (g - r) - 0.0038$\footnote{This relation wass derived for SDSS filters.
+We neglect the small difference between SDSS and HSC filter systems.
+\url{http://classic.sdss.org/dr4/algorithms/sdssUBVRITransform.html\#Lupton2005}} and convert it to absolute magnitude $M_V$.
+For UDGs (UPGs) in each stellar mass bin, we calculate the fraction of quenched galaxies, but both denominator and numerator are weighted by the weights $w_k$ assigned in Section \ref{sec:bkg} to mitigate the impact of background contamination on quenched fractions.
+
+In Figure \ref{fig:qfrac}, the green lines show the quenched fractions $f_q$ as a function of stellar mass for the whole UDG (\textit{left}) and UPG (\textit{right}) samples, and the error bars correspond to the $1\sigma$ Bernoulli standard error.
+The quenched fraction of UDGs is high ($\sim 0.7$) over $6.8 < \log\ M_\star/M_\odot < 8.5$ and weakly depends on the stellar mass.
+On the contrary, as increasing stellar mass, the quenched fraction of UPGs decreases from $f_q \approx 0.8$ at $10^{6.8}\ M_\odot$ to $f_q \approx 0.1$ at $10^{8.5}\ M_\odot$.
+
+We notice that the UDG sample reaches to $\log\,M_\star\approx 8.3$ whereas UPG sample reaches to $\log\,M_\star\approx 9.0$.
+This is because $10^9\ M_\odot$ galaxies no longer satisfy the surface brightness cut for UDG.
+We are only able to probe galaxies down to $10^6.8\ M_\odot$ due to our detection limit.
+
+Say we don't find dependence on host stellar mass (no fig here)
+
+They derived the quenched fraction based on morphology, and they also find that
+
+It is shown that the morphology correlates with the 
+1
+the SFR is correlated with other
+
+calculate the fraction of quenched
+
 Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched.
@@
 
-\section{Discussion and Conclusion}
+\section{Discussion and Conclusion}\label{sec:discussion}
 TODO: make data products (catalogs, fake UDGs, website for their images, etc.)

### 2022-08-19 main.tex
Updates from Overleaf

@@
 \newcommand{\sbeff}{\overline{\mu}_{\mathrm{eff}}(g)}
+\newcommand{\sbeffr}{\overline{\mu}_{\mathrm{eff}}(r)}
 \newcommand{\jiaxuan}[1]{\textcolor{orange}{\textbf{Jiaxuan: #1}}}
 
-\newcommand{\code}[1]{\textbf{\texttt{#1}}}
+% \newcommand{\code}[1]{\textbf{\texttt{#1}}}
+\newcommand{\code}[1]{\texttt{#1}}
 \newcommand{\sersic}{S\'ersic}
@@
 
+\jiaxuan{Just copied the intro in the Magellan proposal. Not in shape at all.}
 Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content \citep{vanDokkum2018,vanDokkum2019} to their globular cluster populations (Danieli et al.
@@
 
+The goal of this work is to posit UDGs in the framework of satellite systems of MW analogs.
+We compare the statistical properties of UDGs with LV satellites and simulations.
+Try to figure out whether UDG is a special class of galaxies or they are just a tail of mass-size scatter.
+
 % Continuing the work by \citep{Greco2018}, we conducted a systematic search for low surface brightness galaxies (LSBGs) in Hyper Suprime-Cam survey (HSC) imaging data (Li et al., in prep).
@@
 
-In this work, we use the circularized effective radius $r_{\rm eff}$, defined as the $r_{\rm eff} = r_{\rm eff, sma} \sqrt{b/a}$, where $r_{\rm eff, sma}$ is the effective radius along the semi-major axis of the aligned elliptical isophotes, and $b/a$ is the axis ratio of the isophotes.
-
 We adopt a $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$.
@@
 The Hyper Suprime-Camera Subaru Strategic Program Survey (\citealt{Aihara2018}; hereafter HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}.
-The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source).
-HSC data are processed using \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Large Synoptic Survey Telescope (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.
-
-In this work, we use the \code{Wide} layer data from Public Data Release 2 (PDR2, also known as \code{S18A}) of HSC \citealt{Aihara2018}.
-It covers $\sim 300\ \rm{deg}^2$ in all five bands, which is 1.5 times larger than the dataset analyzed in \citetalias{Greco2018}.
-One of the key improvements made in \code{S18A} is the sky background subtraction.
-Compared with previous data releases, \code{S18A} adopted a full focal plane sky subtraction algorithm to overcome the over-subtraction of local sky background around bright objects \citep{Aihara2018,Li2021}.
-The unprecedented depth and careful sky subtraction makes \code{S18A} an ideal dataset to search for low surface brightness galaxies.
+The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection).
+HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Large Synoptic Survey Telescope (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.
+
+In this work, we use the \code{Wide} layer data from the Public Data Release 2 (PDR2, also known as \code{S18A}, \citealt{Aihara2018}) of the HSC survey.
+It covers $\sim 300\ \rm{deg}^2$ in all five bands, being 1.5 times larger than the data set (\code{S16A}) analyzed in \citet{Greco2018}.
+One of the key improvements made in PDR2 is the sky background subtraction.
+Compared with previous data releases, PDR2 adopted a full focal plane sky subtraction algorithm to overcome the over-subtraction of the local sky background around bright objects \citep{Aihara2018,Li2021}.
+The unprecedented depth and careful sky subtraction make PDR2 an ideal data set to study low surface brightness galaxies.
 
@@
 \subsection{NASA-Sloan Atlas}
-We use the NASA-Sloan Atlas (NSA \footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies analogous to the Milky Way.
-NSA is a catalog of parameters of local galaxies derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}.
-We use the new version of NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$.
-It also includes elliptical Petrosian aperture photometry for galaxies, which is considered to be more reliable than the photometry used in older versions.
-In this paper, we use the stellar mass derived from the elliptical Petrosian photometry using \code{kcorrect v4\_2}.
+We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way, then we match the LSBGs to these MW analogs.
+The NSA catalog provides various physical properties of galaxies in the nearby universe as derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}.
+We use the newer version of the NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$.
+The new version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions.
+In this paper, we use the stellar mass derived from elliptical Petrosian photometry using \code{kcorrect v4\_2}.
 The redshifts of galaxies in NSA come from several spectroscopic surveys, gas surveys, or direct distance measurements.
 
-\section{LSBG search in HSC S18A}
-Given an overview of the steps here. Also read SMUDGES paper and discuss some aspects here.
+\jiaxuan{Any other data we should introduce? No?}
+
+\section{LSBG search in HSC PDR2}
+Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the PDR2 data, which covers $\sim 1.5$ of the sky area in \citetalias{Greco2018}.
+The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section.
+For those who do not want to be bothered by technical details, we outline the major steps below:
+\begin{enumerate}
+    \item Source Detection (Sec.
+\ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources.
+Then we applied an initial size and color cut based on the output catalog.
+    \item Deblending (Sec.
+\ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \code{scarlet}.
+We use \code{scarlet} models to define color-size-morphology-surface brightness cuts.
+This step removes roughly 97\% of false positives.
+    \item Modeling (Sec. \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
+    \item Completeness and measurement errors (Sec. \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
+\end{enumerate}
 
 \subsection{Source Detection}\label{sec:detection}
-\citetalias{Greco2018} performed a search for extended LSBGs in the first $\sim 200$ deg$^2$ of HSC survey.
-We continued the work in \citetalias{Greco2018} and extended the search to HSC \code{S18A} data which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to \code{S16A}.
-We follow the same philosophy of source detection as in \citetalias{Greco2018}, but make several updates to accommodate \code{S18A} data.
-Below we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity.
-We refer interested readers to \citetalias{Greco2018} for more details.
-Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} is also publically available.
+\citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs.
+We continued the work in \citetalias{Greco2018} and extended the search to the HSC PDR2 data which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to previous data releases.
+We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate PDR2 data.
+These updates are guided by both our understanding of PDR2 data and the completeness tests using mock galaxies.
+In the following, we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity.
+We refer the interested readers to \citetalias{Greco2018} for more details.
+Our source detection pipeline \href{https://github.com/johnnygreco/hugs}{\code{hugs}} and \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} are also open-sourced and available online.
 
@@
     \item \textbf{Bright source removal}.
-Bright sources and their associated LSB lights can mimic objects of interest and obstruct effective detection of LSBGs.
-In this step, we replace pixels related to bright sources with sky noise.
-The bright sources and their diffuse lights are detected by applying a high thresholding and a low thresholding to the image.
-A diffuse light component is associated with a bright source if more than 15\% of its pixels are above the high threshold.
-In this way, we generate a footprint of bright sources in the image.
-
-    Since the sky subtraction in \code{S18A} is significantly better than in previous data releases, LSB features are well conserved after subtracting the sky.
-Therefore, it makes more sense to set the thresholding based on surface brightness, instead of a certain sigma value above sky background (as in \citetalias{Greco2018}).
-We set the high threshold to $\mu_{\rm high} = 22\ \mathrm{mag\ arcsec^{-2}}$ to capture all bright sources above this surface brightness, and the low threshold to $\mu_{\rm low} = 24.5\ \mathrm{mag\ arcsec^{-2}}$ to capture associated diffuse lights.
-
-    %Unlike in \citetalias{Greco2018}, we do not smooth the image prior to thresholding. 
-    After this step, there are still a number of small low surface brightness objects, which are typically marginally resolved galaxies or just pixels with high noise fluctuations.
-We detect and remove them since our main goal is to detect extended LSBGs.
-We run \code{sep}\footnote{\url{https://sep.readthedocs.io/en/v1.1.x/}} \citep{Barbary2016} on the image cleaned as above.
-Based on the segmantation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$.
-This step reduces the number of blended sources.
-These values ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error.
-We also get feedbacks from the completeness tests.
-Not smoothing the images gives us marginal improvement on completeness.
-
-    In the end, we replace pixels within the bright source footprint and small source mask with sky noise.
-The detection is done in $i$-band, and we use the same mask for all $gri$-bands.
-This step effectively cleans out objects and features that hinder the detection of LSBGs.
+Bright sources and their associated LSB lights can mimic objects of interest and obstruct the detection of LSBGs.
+In this step, we replace pixels related to bright sources and small compact sources with sky noise.
+The bright sources and their diffuse lights are detected in the $i$-band by applying a high thresholding and a low thresholding to the image, respectively.
+We associate a diffuse light component to a bright source if more than 15\% of its pixels are above the high threshold.
+In this way, we generate a footprint of bright sources and their LSB lights.
+Then for the $gri$-bands, we replace every pixel within this footprint with Gaussian noise, where the noise level is determined by masking out all detected sources in the image.
+
+    In \citetalias{Greco2018}, the thresholds are set based on the noise level of the local sky.
+Thanks to the global sky subtraction in PDR2, LSB features are well conserved after subtracting the sky and the sky noise level varies less.
+Therefore, it makes more sense to set the thresholds based on the characteristic surface brightness instead of a certain sigma value above the sky background.
+In this work, we set the high threshold to $\mu_{\rm high} = 22\ \sbunit$ to capture all bright sources above this surface brightness, and the low threshold to $\mu_{\rm low} = 24.5\ \sbunit$ to capture the associated diffuse lights.
+Unlike in \citetalias{Greco2018}, we find it not necessary to smooth the image prior to the thresholding.
+
+    After this step, there are still a number of small and compact LSB objects, which are typically marginally resolved galaxies, blended sources, or just pixels standing out because of noise fluctuation.
+We add an extra step to detect and remove them since our main goal is to detect extended LSBGs.
+We run \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} on the ``cleaned'' image as described above.
+Based on the segmentation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$, and pixels within this mask are also replaced by sky noise.
+This step significantly improves the purity of LSBG search.
+The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by completeness tests (Sec.
+\ref{sec:completeness}).
+    % This step effectively cleans out objects and features that hinder the detection of LSBGs.
 
     \item \textbf{Source Extraction}.
-We use \code{Source Extractor} \citep{Bertin1996} to detect sources on the ``cleaned'' images produced in the previous step.
+We use \code{Source Extractor} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
 This step remains largely the same as in \citetalias{Greco2018}.
-The images are convoled with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast.
-We take a mesh size of $43\arcsec$ (doubles the size used in \citetalias{Greco2018}) to measure the local bacbkground and detect objects that are 0.7$\sigma$ per pixel above the local sky.
-We also require the object contains at least 100 contiguous pixels to further remove small compact objects.
-We perform the detection in $g$-band but require all the sources are also detected in $r$-band to exclude possible artifacts.
+The images are convolved with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast between LSBGs and sky background \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}.
+We take a mesh size of $43\arcsec$ (doubles the mesh size used in \citetalias{Greco2018} to allow bigger galaxies in our sample) to measure the local background and detect objects that are 0.7$\sigma$ per pixel above the local sky background.
+We also require the object to contain at least 100 contiguous pixels to further remove small compact objects.
+We perform the detection in the $g$-band, but require that all sources are also detected in the $r$-band to exclude spurious detection and artifacts.
 
     \item \textbf{Initial Sample Selection}.
-In this step, we take the output catalog from the previous step and remove those objects that are not likely to be LSBGs of interest.
-To be specific, we require objects have $g$-band half-light radius (measured by Source Extractor) larger than $r_{\rm min} = 2.0\arcsec$.
+In this step, we take the output catalog from \code{Source Extractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors.
+To be specific, we require objects to have $g$-band half-light radius (measured by \code{Source Extractor}) greater than $r_{\rm min} = 2.0\arcsec$.
 We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$.
-%These cuts are the same as in \citetalias{Greco2018}.
+This color box is relatively conservative with respect to the color distribution of the discovered LSBGs \citep[e.g.,][]{Greco2018,Zaritsky2019,Tanoglidis2021}.
+    Compared with \citetalias{Greco2018}, we added a new metric on morphology of sources to further remove false positives.
+For each source, we compute the ratio of the 2-D autocorrelation function (ACT) within an aperture of 5 pixel and an annulus between 5 pixels and 9 pixels from the center.
+The ACT characterizes the shape, concentration, and spatial correlation of the source.
+We remove sources that have high autocorrelation ratios $a_{\rm corr} > 1.85$.
+This step helps to improve the purity of our sample.
+\jiaxuan{Jenny and Johnny: can you check if this is meaningful to you?}
     %\textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}
-
 \end{enumerate}
-After these steps, we have an intial sample containing 86,002 LSBG candidates.
-\textbf{Why we obtain more sources per sqr deg compared with G18?
-Sky?} Among these objects, there are still a lot of false positives, including galaxy outskirts, tidal features, blended compact sources, etc.
-Therefore, we perform an extra ``deblending'' step to remove false positives.
+
+After these steps, we have an initial sample that contains 86,002 LSBG candidates.
+We obtain more sources per square degree than \citetalias{Greco2018} mainly because PDR2 has a better sky subtraction, and our detection is more inclusive for larger galaxies.
+Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, blended compact sources, etc.
+Therefore, we perform an extra ``deblending'' step to further remove false positives.
 
 \subsection{Deblending}\label{sec:deblending}
-A common type of false positive occurs when point-like sources are blended with diffuse lights from background galaxies or LSB outskirts of  stars and galaxies.
-In order to remove these objects from our sample, we perform non-parametric modeling for  each object using \code{scarlet}\footnote{\url{https://pmelchior.github.io/scarlet/}} \citep{Melchior2018}.
-\code{scarlet} is a deblending and modeling tool designed for multi-band data.
-It utilizes the color and morphology information to seperate blended sources.
-In the following, we briefly summarize how \code{scarlet} works, and we refer intersted readers to \citet{Melchior2018} for more details.
-In \code{scarlet}, each source in the scene $Y_i$ is described by a morphology matrix $S_i$ and a Spectral Energy Distribution (SED) vector $A_i$.
-The goal of modeling is to minimize the object function $f \propto \frac{1}{2}||\sum Y_i - P(\sum A_i S_i)||_2^{2}$ under certain constraints, where $P$ is the convolution with PSF.
+A common type of false positive occurs when point-like sources are blended with diffuse lights from background galaxies or the LSB outskirts of stars and galaxies.
+Our initial detection cannot distinguish them from the real LSBGs.
+In order to identify and remove these objects from our sample, we perform an non-parametric modeling for each object using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}.
+\code{Scarlet} is a deblending and modeling tool designed for multi-band imaging data.
+It utilizes the color and morphology information to separate blended objects.
+In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018} and the online documentation for more details.
+
+In \code{scarlet}, each source $k$ in the cutout is described by a morphology matrix $S^k_i$ and a Spectral Energy Distribution (SED) vector $A^k_i$, and the multi-band images is $Y_i$, where $i$ denotes different bands.
+The goal of modeling is to minimize the objective function $f \propto \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF.
 The morphology matrix of each source is limited to be within a bounding box.
-In this section, we assume that all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decreases from their centers to outskirts (monotonoicity constraint).
-Although not all galaxies satisfy the monotonicity constraint, it still provides an easy, sparse, and robust way to deblend overlapping sources.
-We refer to this modeling method as the ``vanilla scarlet''.
+We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources should monotonically decrease from center to outskirt (monotonoicity constraint).
+Apparently, the monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample, this assumption still holds for most cases and provides an easy, sparse, and robust way to deblend overlapping sources.
+We refer to this modeling method as the \textit{vanilla scarlet}.
 
 In vanilla scarlet, objects can be modeled with different types of sources, including point source, single-extended source, multi-extended source, compact-extended source, and flat-sky source.
-The morphology matrix of point source is simply the normalized PSF.
-For the single-extended source, the morphology matrix follows positivity and monotonicity constraints.
-The multi-extended source is a combination of two or more single-extended sources, which makes it possible to model more complex structure and color gradient of galaxies.
-The compact-extended source is a single-extended source initialized using the morphology matrix of a point-source, which encourages the model to be compact.
-The flat-sky source has uniform color and morphology across the box.
-
-Vanilla scarlet is ideal to identify and remove the false positives in our intial LSBG sample.
-
-We model LSBG candidates using vanilla scarlet as follows.
-
-Our code \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} is also available on GitHub.
-
-\subsubsection{Peak detection}
-We first generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candiate.
-Then we construct a detection image by taking a weighted average of the images in four separate bands.
-We take the total inverse variance as the weight for each band.
-This detection image is considered to be deeper than any single band image.
-
-Next, we detect peaks on the detection image.
-We first run \code{sep} on the detection image using a detection threshold of 4$\sigma$, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels.
-This step idenfities relatively extended sources in the detection image.
+The morphology matrix of the point source is simply the normalized PSF.
+The single-extended source has a morphology matrix following positivity and monotonicity constraints.
+The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient.
+The compact-extended source is a single-extended source initialized using the morphology matrix of a point-source, which encourages the model to be compact, but still allows the morphology matrix to be extended.
+The flat-sky source has uniform color and morphology within the bounding box.
+
+Similar to many other modeling code (e.g., \code{galfit}, \code{imfit}), \code{scarlet} asks for the information of detected peaks to initialize sources.
+The models are then optimized subject to the constraints.
+Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude blended objects from our sample.
+We unfold the details in the following sections.
+
+\subsubsection{Peak detection}\label{sec:peak}
+We generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candidate in our initial sample.
+We then construct a detection image by taking an average of the four bands weighted by the inverse variance of each band.
+This detection image is considered to be deeper than the single-band images.
+Next, we run \code{sep} on the detection image using a threshold of 4$\sigma$ above the sky, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels.
+This step identifies relatively extended sources in the detection image.
 However, there are still faint and compact peaks not detected.
-Therefore, we apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep high spatial frequency components.
-Another round of \code{sep} is then ran on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels.
-This step detects many compact sources that are not detected in the previous step.
-In the end, we combine the two detection catalogs together.
+We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep high spatial frequency components.
+Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels.
+This step detects many compact sources that were not included in the previous step.
+In the end, we combine the two detection catalogs.
 
 \subsubsection{Model initialization and optimization}
-The deblending step is designed to deblend sources in the vicinity of the target object.
-The scene will contain both the target object and all the sources in its vicinity.
-Therefore, the sources being modeled is determined by how extended the target is.
-We estimate a bounding box based on the detection image, and include all the peaks inside this box to be modeled.
-
-We use a multi-extended source with two components to model the target object, such that it is capable to capture the details of galaxy structure and color.
-The source is initialized as follows.
-We start by convolving the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}.
-After smoothing, the low surface brightness outskirts of target galaxy will become more prominent, which helps intializing the morphology matrix.
-The smoothed detection image is thresholded using $0.1\sigma$ to remove sky noise, then the morphology matrix $S_i$ of the intial model is determined by constructing a symmetric and monotonic approximation to the region in the detection image around the peak of the target object.
-The intial SED vector $A_i$ is set to be the color of the image averaged with the spatial weight function $S_i$.
-As a byproduct of intialization, we get a bounding box which represents the extent of the target object.
-We also add a flat-sky source to model the local sky around the target.
-This is helpful for situations where an object overlaps with the LSB outskirts of a bright galaxy.
-
-Then we initialize all the sources inside the bounding box of the target.
-The extended objects detected in the first detection step are modeled as single-extended sources.
-For compact objects that are only detected in the second step, we model them as point sources if their FWHM $<$ 5 pixels, otherwise as compact-extended sources.
-The morphology matrices and SED vectors of these sources are also intialized in the same way as above.
-
-As mentinoed above, we only model sources within the bounding box of the target.
-However, scattered lights from nearby bright stars and galaxies could bias the modeling within the bounding box.
-We match our field with the Gaia catalog and mask out stars outside of the bounding box.
-Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.
-
-As a result of such initialization, we only optimize the object function $f$ defined for sources within the bounding box of the target object.
-The optimization process uses the adaptive proximal gradient method \citep{Melchior2019}, which is a robust method for optimization with constraints.
-The model is considered to be converged when the relative changes of parameters are smaller than \code{e\_rel\,=\,2e-4}.
-Typically convergence is achieved after $\sim 50$ steps of opimization and the whole modeling takes about 40s for each LSBG.
-
-\textbf{For bright sources? Cookie cutter effect}
 
@@
 	}
-	\caption{An example of the deblending step.}
+	\caption{A demonstration of the deblending step as described in Section \ref{sec:deblending}.
+Here we show two objects from our initial sample (Sec \ref{sec:detection}): the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts.
+The data shown in the first column is $griz$ color-composite image with the bounding boxes overlay.
+The objects covered by the gray shades are masked.
+The bounding boxes and the initial models (second column) are determined from the smoothed image.
+The optimized models (PSF convolved) are shown in the third column, the fourth column shows the residual image, and the last column isolates the model of the target object and labels the measured color, size, and surface brightness.
+After such a deblending step, false positives such as the one in bottom panels can be easily removed based on their measured properties.
+	}
 	\label{fig:vanilla_scarlet_demo}
@@
 
+After peak detection, there are two more things to be determined before optimization.
+We need to know which peaks should be modeled, and we would like to initialize the model as best as we can.
+We note that \code{scarlet} optimizes the model instead of deriving the full posteriors, thus good initialization becomes really important.
+We tackle these problem as follows.
+
+The deblending step is designed to model the sources in the vicinity of the target object.
+Therefore, how large and extended is the target object determines which peaks are relevant.
+We draw a square bounding box around the target object and include all the peaks inside this box to be modeled.
+The size of the bounding box is determined as we initialize the model for target object.
+
+We use a multi-extended source with two components to model the target object, such that the model is capable to capture the galaxy structure and color gradient.
+The source is initialized as follows.
+We convolve the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise.
+After smoothing, the LSB outskirts of the target galaxy become more prominent, which helps use determine the bounding box and initialize the morphology matrix.
+We take the smoothed image and threshold it with $0.1\sigma$ to remove the sky noise.
+The initial morphology matrix $S_i$ is determined by constructing a symmetric and monotonic approximation to the smoothed image around the target object.
+The initial SED vector $A_i$ is set to be the sum of morphology matrix $S_i$ in each band.
+As a byproduct of initialization, we get a bounding box from $S_i$ which indicates the extent of the target object.
+Consequently, the size of the bounding box depends on the smoothing kernel and the threshold.
+We choose the above values by trial and error such that the box is not too large to include many irrelevant peaks, but not too small to lose the outskirts of the target galaxy.
+
+Then we take all peaks within the bounding box of the target galaxy and initialize them following the same way.
+Recall that we have two rounds of peak detection (Sec \ref{sec:peak}), focusing on extended and compact sources respectively.
+The extended objects detected in the first peak detection step are modeled as single-extended sources.
+For compact objects that are only detected in the second peak detection, we model them as point sources if their FWHM $<$ 5 pixels, otherwise as compact-extended sources.
+We also add a flat-sky source to model the local sky around the target.
+This is helpful for situations where an object overlaps with the LSB outskirts of a bright galaxy (e.g., the bottom panel in Figure \ref{fig:vanilla_scarlet_demo}).
+
+As mentioned above, we only model peaks within the bounding box of the target.
+However, scattered lights from nearby bright stars and galaxies could bias the modeling of sources within the bounding box (e.g., the yellow star in the top left panel of Figure \ref{fig:vanilla_scarlet_demo}).
+We match our field with the Gaia catalog and mask out stars outside of the bounding box.
+Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.
+
+We demonstrate the above procedures in Figure \ref{fig:vanilla_scarlet_demo} with two examples.
+The one shown in the top panels is a blue LSBG, whereas the one shown in bottom is a high-$z$ galaxy blended with the outskirts of nearby galaxy which falls in our initial sample as a false positive.
+The first column shows the $griz$ color-composite image \citep{Lupton2004}, where the white boxes mark the bounding box of each source in the scene.
+As seen, the gray shades over objects outside of the target bounding box indicate they are masked out.
+The second column shows the initial \code{scarlet} models.
+They look fuzzy because they are constructed from the smoothed image, but they capture the color and the faint outskirts of the LSBG quite well.
+
+The optimization process uses the adaptive proximal gradient method \citep{Melchior2019}, which is a robust method for optimization with constraints.
+The model is considered to be converged when the relative changes of parameters are smaller than \code{e\_rel\,=\,2e-4}.
+Typically convergence is achieved after $\sim 50$ steps of optimization and the whole modeling takes about 40s for typical LSBGs.
+It takes longer when the target galaxy has large angular size since more peaks are modeled.
+The optimized model is shown in the middle column of Figure \ref{fig:vanilla_scarlet_demo} after convolving with the PSF, and the fourth column shows the residual image.
+The fifth column shows the optimized model only for the target object.
+
+We notice that the optimized model of the blue LSBG captures its color and morphology quite well.
+For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact.
+The reason why it passes our initial selection is that the galaxy outskirts are shredded by Source Extractor and happen to have a large size and right color.
+But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.
+
+% As a result of such initialization, we only optimize the object function $f$ defined for sources within the bounding box of the target object. 
+% \textbf{For bright sources? Cookie cutter effect? I don't think cookie cutter is important here.}
+
 \subsubsection{Measurement and false positive removal}\label{sec:non-par-measurement}
-After running vanilla scarlet, we get non-parametric models of objects within the bounding box of the target.
-We take out the model of the target galaxy (as shown in Figure \ref{fig:vanilla_scarlet_demo}) and analyze it using \code{statmorph}\footnote{\url{https://statmorph.readthedocs.io/en/latest/}}\citep{statmorph}.
-The goal of this step is to remove false positives using various morphological and structural diagnostics.
-
-\code{Statmorph} calculates non-parametric morphological and structural parameters, including the half-light radius, concentration-asymmetry-smoothness (CAS) statistics \citep{Conselice2003}, Gini-M20 \citep{Lotz2004}, etc.
-It takes an image, a segmentation map indicating the footprint of the object, a variance map, and PSF.
-For our purpose, the image is just the scarlet model convolved with the observed PSF.
-This image represents the deblended target galaxy.
-Because there is no contaminants in the deblended model, the segmentation map just covers the whole image.
+
+\begin{figure*}
+	\vbox{
+		\centering
+		\includegraphics[width=1.0\linewidth]{deblending_cuts.pdf}
+	}
+	\caption{The distribution of LSBG candidates from our initial sample in the parameter space as measured from the \code{scarlet} models.
+We visually inspected 5,000 LSBG candidates and labeled them as \code{candy} (LSBGs with typically dwarf galaxy features), \code{galaxy} (higher surface brightness galaxies or galaxies with spiral galaxy features), and \code{junk} (false positives).
+We propose a selection based on size, color, surface brightness and morphology (dashed boxes) to effectively remove false positives.
+After such cuts (bottom panels), 97\% of false positives and 75\% of non-LSB galaxies are removed according to our visual inspection results.
+	}
+	\label{fig:deblending_cuts}
+\end{figure*}
+
+After running the vanilla scarlet for LSGB candidates, we successfully deblend the target object from nearby sources.
+We take out the model of the target object (as shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}) and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}.
+The purpose of this analysis is to extract the structural and morphological parameters of the target object.
+We further use these diagnostics to remove false positives.
+
+\code{Statmorph} calculates non-parametric morphological and structural parameters, including effective radius, concentration-asymmetry-smoothness statistics \citep[CAS,][]{Conselice2003}, and Gini-M20 \citep{Abraham2003,Lotz2004}.
+The measurement requires an image, a variance map, and a PSF.
+For our purpose, the ``image'' is just the \code{scarlet} model convolved with the observed PSF.
 The variance map and PSF are taken from HSC cutouts.
-We also force the sky level to be zero because sky has already been fit in vanilla scarlet.
-
-One of the most important diagnostics is the size of the object.
-Half-light radius is calculated using ellpitical apertures, where the ellipticity $\varepsilon$ is determined by calculating the second moment of the image.
-We define the circularized half-light radius $r_e$ as the geometrical average of the semi-major and semi-minor axis of the half-light elliptical aperture: $r_e = r_{\rm sma} \sqrt{b/a}$.
-The total magnitudes are simply calculated by summing up the model in each band, and colors are defined by the difference among apparent magnitudes.
-Galactic extinction correction is not applied at this point.
-Two kinds of surface brightnesses are measured.
-The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
+We also force the sky level to be zero because sky has already been fit when running vanilla scarlet.
+
+One of the most important diagnostics is the effective radius of the object.
+In this paper, we refer to effective radius as the circularized effective radius $r_{e}$, defined as the $r_{e} = r_{\rm eff, sma} \sqrt{b/a}$ where $r_{\rm eff, sma}$ is the effective radius measured along the semi-major axis of the aligned elliptical isophotes, and $b/a$ is the axis ratio of the isophotes.
+In \code{statmorph}, the effective radius is calculated using elliptical apertures, where the ellipticity $\varepsilon$ is determined by calculating the second moment of the image.
+The total magnitudes are simply calculated by summing up the model in each band, and colors are defined using total magnitudes.\footnote{Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
 We also define the average surface brightness within effective radius as $\mu_{\rm eff} = m - 2.5 \log_{10}(2 \pi r_e^2)$, where $m$ is the total magnitude.
 
-We also use Gini-M20 and CAS statistics.
-The Gini coefficient \citep{Abraham2003,Lotz2004} and M20 statistics quantify how concentrated/extended is the flux distribution across the image.
-The CAS statistics characterize the concentration ($C = 5\log_{10}(r_{80} / r_{20}$), asymmetry, and smoothness of the light distribution of the object.
+We also use the Gini-M20 and CAS statistics.
+The Gini coefficient and M20 statistics \citep{Abraham2003,Lotz2004} quantify how concentrated/extended is the flux distribution across the image.
+The CAS statistics characterize the concentration $C$, asymmetry $A$, and smoothness $S$ of the light distribution of the object.
 We refer the readers to \citet{statmorph} for more details on their definitions and implementations.
-The morphological and structural parameters are the same in different bands by design of the \code{scarlet} model.
-
-To better guide us on how to use these diagnostics, we visually inspected a subset of LSBG candiates in our initial sample (Sec \ref{sec:detection}) and use the labels to construct the metrics.
-We randomly selected 5,000 LSBG candidates that are matched with a host at $0.02 < z < 0.04$ (see Sec \ref{sec:match} for details).
-We run vanilla scarlet and measure morphological parameters for this subsample as described above.
-Then we generate color composite image for each object using HSC $griz$-bands with 0.5 arcmin on a side.
-The visual inspection was done by coauthors JEG, JG, SH, RB.
+The morphological and structural parameters are the same in different bands by construction of the \code{scarlet} model.
+
+To better guide us on how to use these diagnostics, we visually inspected a subset of LSBG candidates in our initial sample (Sec \ref{sec:detection}) and use the labels to construct the metrics.
+We randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see Sec \ref{sec:match} for details).
+We run vanilla scarlet for all of them and measure morphological parameters as described above.
+Then we do visual inspection by looking at the $griz$ color-composite images with 0.5 arcmin on a side.
+Objects are classified into three types: \code{candy} (LSB galaxies with typically dwarf galaxy features), \code{galaxy} (high surface brightness galaxies, or galaxies with spiral galaxy features), and \code{junk} (false positives, including tidal streams, galaxy outskirts blends, and other artifacts).
+The difference between \code{candy} and \code{galaxy} can be quite ambiguous.
+
+The visual inspection was done by coauthors JEG, JG, SH, RB, KC, AG, and EKF.
 Each object has been inspected by at least one person.
-Objects are classified into three types: \code{candy} (LSB galaxies with typicall dwarf galaxy features), \code{galaxy} (high surface brightness galaxies, or galaxies with spiral galaxy features), \code{junk} (false positives, including tidal streams, galaxy outskirts, and other artifacts).
-The difference between \code{candy} and \code{galaxy} can be quite ambiguous.
-In the end, we combine the votes from different persons as follows.
+In the end, we combine the votes from different persons.
 An object is classified as \code{junk} if the number of votes as \code{junk} prevails the number of votes as \code{candy} and \code{galaxy}.
-For objects that are not \code{junk}, if the number of votes as \code{candy} is larger than that as \code{galaxy}, we assign this object as \code{candy}.
+For objects that are not \code{junk}, if the number of votes as \code{candy} is greater than the votes as \code{galaxy}, we classify this object as \code{candy}.
 Everything else is classified as \code{galaxy}.
@@
 
-We use this visual inspection results to guide us on using the morphological and structural diagnostics.
-The distributions of \code{candy}, \code{galaxy}, and \code{junk} in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}.
+We use this visual inspection results to teach us how to use the morphological and structural diagnostics.
+The distributions of \code{candy} (blue), \code{galaxy} (green), and \code{junk} (red) in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}.
 False positives (\code{junk}) are highlighted in red.
-Altough false positives are scattered all over the parameter space, a large fraction of them occupy regions with small size, extreme colors, very faint surface brightness, and large concentration and asymmetry.
-Therefore, we come up the following selection cuts to remove the false positives:
+Although \code{junks} are scattered all over the parameter space, a large fraction of them have small size, extreme colors, very faint surface brightness, large concentration and large asymmetry.
+Therefore, we come up with the following selection cuts to remove the false positives:
 \begin{itemize}
@@
 \end{itemize}
-These criteria (shown as dashed lines) effectively help us remove objects that are not likely being LSBGs of interest.
-The color cuts here is narrower than the one used in detection to further remove junks and background high redshift galaxies.
-It is worth noticing that we not only remove objects with small sizes, but also remove objects with large size, low surface brightness, and high concentration.
+These criteria (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove objects that are not likely being LSBGs of interest.
+The color cuts here is narrower than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junks and background high redshift galaxies.
+We not only remove objects with small sizes, but also exclude objects with large size, very low surface brightness, and high concentration.
 This is because the scarlet model of some junks can be very concentrated in the center but also extends quite far.
-The slant demarcation line on Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to seperate merging galaxies and normal galaxies.
-
-The distributions of objects after applying the above cuts are shown in the bottom panels of Figure \ref{fig:deblending_cuts}.
-After the cuts, 97\% of the \code{junk} are removed, but the majority (70\%) of \code{candy} still remains.
+The slant demarcation line on the Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to separate merging galaxies from normal galaxies.
+
+The bottom panels in Figure \ref{fig:deblending_cuts} show the objects after applying the above selections.
+With these cuts, 97\% of the false positives are removed, but the majority (70\%) of \code{candy} still remains.
 The number of \code{galaxy} also drops by 75\%.
 This empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample.
-The numbers used in the selection are purely driven by the visual inspection results.
-
-It is worthy noticing that the scarlet modeling and non-parametric measurements is not designed to recover the intrinsic properties of the galaxies.
-They are only used as a diagnotic tool to remove false positives.
-Therefore, the half-light radius measured above does not correspond to the half-light radius of the galaxy itself, but merely a proxy.
-In reality, the vanilla scarlet model usually under-estimates the size and the total flux of LSB objects because the faint outskirts are typically not modeled well due to the non-parametric nature of vanilla scarlet and the monotonicity constraint.
-In Section \ref{sec:modeling}, we propose a method to better measure the size and total magnitude of LSBG using \code{scarlet}.
-We use the parameters measured in Section \ref{sec:modeling} for science.
-
-\begin{figure*}
-	\vbox{ 
-		%\vskip -10mm
-		\centering
-		\includegraphics[width=1.0\linewidth]{deblending_cuts.pdf}
-	}
-	\caption{Deblending cuts.}
-	\label{fig:deblending_cuts}
-\end{figure*}
-
-Common false positives: why we want a deblending step
-
-Why use scarlet: color info, non-par, monotonic, standard in future HSC, fast, high success rate. Vanilla scarlet.
-
-We do not do scarlet fitting for the entire initial sample, because time consuming. We first match with MW hosts.
+But everything comes with a price.
+This cuts sacrifice the completeness of real LSBGs.
+In Section \ref{sec:completeness}, we characterize the completeness of this ``deblending'' cuts by injecting mock \sersic{} galaxies.
+
+We emphasize that the vanilla scarlet modeling and non-parametric measurements are not designed to recover the intrinsic properties of the galaxies.
+They are only used as a diagnostic tool to remove false positives.
+In fact, the vanilla scarlet model usually under-estimates the size and the total flux of LSB objects because the faint outskirts are typically not modeled well due to the non-parametric nature of vanilla scarlet and the monotonicity constraint.
+In the following section, we propose a method to better measure the size and total magnitude of LSBG for science.
 
@@
 
-\subsection{Completeness and Measurement Uncertainty}
+\subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}
 
@@
 
-\textbf{Need to update the completeness to the S18A version. Ping Johnny.}
+% \textbf{Need to update the completeness to the S18A version. Ping Johnny.}
 
@@
 
-Remember to ref SMUDGES papers here.
+\jiaxuan{Remember to ref SMUDGES papers here. Maybe compare our method with SMUDGES, Tanoglidis, etc.}
 
@@
 The UPG sample also lose a significant fraction of red galaxies at $25 < \sbeff < 26$, because they are not LSB (hence low-mass) enough to be higher than $1.5\sigma$ from the mass-size relation.
+
+\jiaxuan{The mass-size relation used to define UPG is actually extrapolated to 1e9. Need to say this clearly.}
 
@@
 	}
-    \caption{Caption}
+    \caption{The quenched fractions of UDGs (left panels) and UPGs (right) as a function of their stellar masses.
+The results for the whole sample are shown in green dots.
+The samples are further divided into bins based on the radial distance to the host (top panels) and host color (bottom panels), and are displayed in blue and red lines.
+We also overlie the results from Local Volume \citep[ELVES,][]{CarlstenELVES2022}, nearby Universe \citep[SAGA,][]{SAGA-II}, and simulations including ARTEMIS \citep{Font2022} and FIRE-2 \citep{Samuel2022}.
+The errors in this plot correspond to $1\sigma$ Bernoulli standard error.
+We find that UDGs have high quenched fraction and remains a constant across a decade in stellar mass.
+The quenched fraction of UPGs drops as increasing stellar mass, remarkably similar to that of normal satellites of MW analogs.
+The quenched fraction is larger for those associated to redder hosts and those that are closer to the host.
+}
     \label{fig:qfrac}
@@
 It is not guaranteed that the same color cut would work in our regime.
-\footnote{Changing the intercept of the color cut to -0.28 makes the overall quenched fraction higher, but does not change the trend of quenched fraction as a function of stellar mass.}
-
-We derive V-band apparent magnitude following $V = g - 0.5784\, (g - r) - 0.0038$\footnote{This relation wass derived for SDSS filters.
+\footnote{\jiaxuan{Add some robustness tests, such as ``Changing the intercept of the color cut to -0.28 makes the overall quenched fraction higher, but does not change the trend of quenched fraction as a function of stellar mass.''}}
+
+We derive $V$-band apparent magnitude following $V = g - 0.5784\, (g - r) - 0.0038$\footnote{This relation wass derived for SDSS filters.
 We neglect the small difference between SDSS and HSC filter systems.
@@
 The quenched fraction of UDGs is high ($\sim 0.7$) over $6.8 < \log\ M_\star/M_\odot < 8.5$ and weakly depends on the stellar mass.
-On the contrary, as increasing stellar mass, the quenched fraction of UPGs decreases from $f_q \approx 0.8$ at $10^{6.8}\ M_\odot$ to $f_q \approx 0.1$ at $10^{8.5}\ M_\odot$.
-
-We notice that the UDG sample reaches to $\log\,M_\star\approx 8.3$ whereas UPG sample reaches to $\log\,M_\star\approx 9.0$.
-This is because $10^9\ M_\odot$ galaxies no longer satisfy the surface brightness cut for UDG.
-We are only able to probe galaxies down to $10^6.8\ M_\odot$ due to our detection limit.
-
-Say we don't find dependence on host stellar mass (no fig here)
-
-They derived the quenched fraction based on morphology, and they also find that
-
-It is shown that the morphology correlates with the 
-1
-the SFR is correlated with other
-
-calculate the fraction of quenched
+On the contrary, as increasing stellar mass, the quenched fraction of UPGs drastically decreases from $f_q \approx 0.8$ at $M_\star = 10^{6.8}\ M_\odot$ to $f_q \approx 0.1$ at $M_\star = 10^{8.5}\ M_\odot$.
+We further divide the sample based on the projected radial distance to the host $R/R_{\rm vir}$ (top panels) and the host $g-i$ color (bottom panels).
+As shown in the top panels in Figure \ref{fig:qfrac}, we find that UDGs (UPGs) that are closer to the host have a higher quenched fraction.
+The average difference on quenched fractions between the two radial bins is $\sim 0.1$ for UDG and $\sim 0.2$ for UPG.
+This trend is expected because the density of CGM is higher when it is closer to the host and thus quenches the UDGs (UPGs) via ram pressure stripping more efficiently.
+The tidal stripping is also stronger as satellites get closer to the host.
+From the bottom panels in Figure \ref{fig:qfrac}, we find that UDGs (UPGs) hosted by redder hosts also have a higher quenched fraction.
+The difference on quenched fraction between the two host color bins is $\sim 0.2$ for UDGs.
+But for UPGs, it seems that the host color impacts less than the distance to the host on the quenched fraction.
+This result might hint the ``galaxy conformity'', which refers to the fact that late-type hosts tend to have more late-type satellites \citep{Weinmann2006}.
+We also split the samples based on host stellar mass, but do not find a significant difference in quenched fractions.
+(echo Jenny's paper)
+
+We compare the quenched fractions of UDGs and UPGs with satellites of MW-mass hosts in the Local Volume (ELVES), in nearby Universe (SAGA), and in numerical simulations.
+The quenched fractions from ELVES is shown in orange dashed lines, while SAGA results are shown as gray squares.
+The quenched fraction from ELVES and SAGA used the same color cut to define quenched galaxies as we do (see \citealt{CarlstenELVES2022}).
+SAGA quenched fractions are lower than ELVES arguably because SAGA survey is not sensitive to galaxies below $\sbeffr = 25\sbunit$ \citep{Font2022}.
+We also overlie the quenched fraction from ARTEMIS \citep[purple lines,][]{Font2022} and FIRE-2 \citep[pink dotted lines][]{Samuel2022} simulations, where the quenched galaxies are defined as those with no instantaneous (for ARTEMIS) or recent ($<200$ Myr for FIRE-2) star formation.\footnote{\citet{Font2022} find a similar quenched fraction when using the same color cut as we do.} We select ARTEMIS and FIRE-2 because they roughly cover the highest and lowest quenched fraction produced in simulations (see Fig.
+13 in \citep{Samuel2022}).
+Compared with these results, we see that UDGs have a higher quenched fraction which does not drop as increasing stellar mass.
+Surprisingly, we find that the quenched fraction of UPGs agrees with both local volume observations and simulations quite well, although these results are dominated by the bulk of MW satellites that are not as large as our UPGs.
+
+Compare to ELVES and simulations, our sample spans a narrower range in stellar mass.
+The detection limit in surface brightness and size set the lower bound in stellar mass around $10^{6.8}\ M_\odot$.
+However for UDG sample, it only reaches to $M_\star\approx 10^{8.3}\ M_\odot$ because galaxies with higher stellar mass no longer satisfy the surface brightness cut for UDG.
+On the contrary, the UPG definition does not have hard surface brightness cut such that $M_\star > 10^{8.5}\ M_\odot$ galaxy can get into the UPG sample as long as having an extraordinarily large size.
+As a consequence, background spiral galaxies could dominate the UPG sample at the high-mass end.
+
+\jiaxuan{TODO: make data products (catalogs, fake UDGs, website for their images, etc.)}
+
+\section{Discussion}\label{sec:discussion}
+
+\subsection{High and constant quenched fraction of UDGs is an artifact}
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
+	}
+    \caption{Caption}
+    \label{fig:mass_size}
+\end{figure*}
 
@@
 
-\section{Discussion and Conclusion}\label{sec:discussion}
-TODO: make data products (catalogs, fake UDGs, website for their images, etc.)
-\subsection{High quenched fraction of UDGs is an artifact}
-
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
-	}
-    \caption{Caption}
-    \label{fig:mass_size}
-\end{figure*}
-
 \subsection{UDG formation}
@@
 
+\section{Summary}
+
 \section*{Acknowledgment}
-JL is grateful for discussions with Meng Gu. The authors thank Yao-Yuan Mao for his tool for visualizing image cutouts.
+JL is grateful for discussions with Meng Gu, XXX, XXXX. The authors thank Yao-Yuan Mao for his tool for visualizing image cutouts.
 
@@
           \href{https://www.astropy.org/}{\code{Astropy}} \citep{astropy}, \href{https://www.scipy.org}{\code{SciPy}} \citep{scipy}, \href{https://matplotlib.org}{\code{Matplotlib}} \citep{matplotlib},
+          \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph},
         %   \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},

### 2022-08-19 main.tex
Updates from Overleaf

@@
 
-\jiaxuan{Just copied the intro in the Magellan proposal. Not in shape at all.}
+\jiaxuan{Just copied the intro from the Magellan proposal. Not in shape at all.}
 Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content \citep{vanDokkum2018,vanDokkum2019} to their globular cluster populations (Danieli et al.
@@
 \ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources.
-Then we applied an initial size and color cut based on the output catalog.
+Then we apply an initial size and color cut based on the output catalog.
     \item Deblending (Sec.
@@
 \citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs.
-We continued the work in \citetalias{Greco2018} and extended the search to the HSC PDR2 data which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to previous data releases.
+We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to previous data releases.
 We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate PDR2 data.
@@
 
-\begin{enumerate}
-    \item \textbf{Bright source removal}.
+\subsubsection{Bright source removal}
 Bright sources and their associated LSB lights can mimic objects of interest and obstruct the detection of LSBGs.
@@
 
-    \item \textbf{Source Extraction}.
+\subsubsection{Source Extraction}
 We use \code{Source Extractor} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
@@
 
-    \item \textbf{Initial Sample Selection}.
+\subsubsection{Initial Sample Selection} 
 In this step, we take the output catalog from \code{Source Extractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors.
@@
 We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$.
-This color box is relatively conservative with respect to the color distribution of the discovered LSBGs \citep[e.g.,][]{Greco2018,Zaritsky2019,Tanoglidis2021}.
-    Compared with \citetalias{Greco2018}, we added a new metric on morphology of sources to further remove false positives.
+This color box is relatively conservative with respect to the color distribution of the discovered LSBGs \citep[e.g.,][]{Greco2018,Zaritsky2019,Tanoglidis2021,SAGA-I}.
+
+Compared with \citetalias{Greco2018}, we add a new metric on morphology of sources to further remove false positives.
 For each source, we compute the ratio of the 2-D autocorrelation function (ACT) within an aperture of 5 pixel and an annulus between 5 pixels and 9 pixels from the center.
@@
 %\textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}
-\end{enumerate}
-
+
+\vspace{2em}
 After these steps, we have an initial sample that contains 86,002 LSBG candidates.
-We obtain more sources per square degree than \citetalias{Greco2018} mainly because PDR2 has a better sky subtraction, and our detection is more inclusive for larger galaxies.
-Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, blended compact sources, etc.
+We obtain four times more sources per square degree than \citetalias{Greco2018} mainly because PDR2 has a better sky subtraction,  our detection is more inclusive for larger objects, and our size cut is less restrictive for small objects.
+Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirri, blended compact sources, etc.
 Therefore, we perform an extra ``deblending'' step to further remove false positives.
@@
 \subsection{Deblending}\label{sec:deblending}
-A common type of false positive occurs when point-like sources are blended with diffuse lights from background galaxies or the LSB outskirts of stars and galaxies.
+A common type of false positive occurs when point-like sources are blended with diffuse light from background galaxies or the LSB outskirts of stars and galaxies.
 Our initial detection cannot distinguish them from the real LSBGs.
-In order to identify and remove these objects from our sample, we perform an non-parametric modeling for each object using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}.
+In order to identify and remove these objects from our sample, we perform non-parametric modeling for each object using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}.
 \code{Scarlet} is a deblending and modeling tool designed for multi-band imaging data.
@@
 In \code{scarlet}, each source $k$ in the cutout is described by a morphology matrix $S^k_i$ and a Spectral Energy Distribution (SED) vector $A^k_i$, and the multi-band images is $Y_i$, where $i$ denotes different bands.
-The goal of modeling is to minimize the objective function $f \propto \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF.
+The goal of the modeling is to minimize the objective function $f \propto \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF.
 The morphology matrix of each source is limited to be within a bounding box.
-We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources should monotonically decrease from center to outskirt (monotonoicity constraint).
-Apparently, the monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample, this assumption still holds for most cases and provides an easy, sparse, and robust way to deblend overlapping sources.
-We refer to this modeling method as the \textit{vanilla scarlet}.
+We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirt (monotonoicity constraint).
+The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample, this assumption still holds for most cases and provides an easy, sparse, and robust way to deblend overlapping sources.
+We refer to this modeling method as \textit{vanilla scarlet}.
 
@@
 The morphology matrix of the point source is simply the normalized PSF.
-The single-extended source has a morphology matrix following positivity and monotonicity constraints.
+The single-extended source has a morphology matrix that follows positivity and monotonicity constraints.
 The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient.
@@
 
-Similar to many other modeling code (e.g., \code{galfit}, \code{imfit}), \code{scarlet} asks for the information of detected peaks to initialize sources.
+Similar to many other modeling codes (e.g., \code{galfit}, \code{imfit}), \code{scarlet} is initialized with positions of detected peaks in the prior steps.
 The models are then optimized subject to the constraints.
 Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude blended objects from our sample.
-We unfold the details in the following sections.
+In the following subsections, we describe our peak detection, model initialization, and measurement procedures.
 
@@
 We convolve the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise.
-After smoothing, the LSB outskirts of the target galaxy become more prominent, which helps use determine the bounding box and initialize the morphology matrix.
+After smoothing, the LSB outskirts of the target galaxy become more prominent, which helps in determining the bounding box and initializing the morphology matrix.
 We take the smoothed image and threshold it with $0.1\sigma$ to remove the sky noise.
 The initial morphology matrix $S_i$ is determined by constructing a symmetric and monotonic approximation to the smoothed image around the target object.
-The initial SED vector $A_i$ is set to be the sum of morphology matrix $S_i$ in each band.
+The initial SED vector $A_i$ is set to be the sum of the morphology matrices $S_i$ in each band.
 As a byproduct of initialization, we get a bounding box from $S_i$ which indicates the extent of the target object.
 Consequently, the size of the bounding box depends on the smoothing kernel and the threshold.
-We choose the above values by trial and error such that the box is not too large to include many irrelevant peaks, but not too small to lose the outskirts of the target galaxy.
-
-Then we take all peaks within the bounding box of the target galaxy and initialize them following the same way.
+We choose the above values by trial and error such that the box is not too large to include many irrelevant peaks, but not too small to lose the flux from the target galaxy.
+
+Then we take all peaks within the bounding box of the target galaxy and initialize them in the same way.
 Recall that we have two rounds of peak detection (Sec \ref{sec:peak}), focusing on extended and compact sources respectively.
@@
 As mentioned above, we only model peaks within the bounding box of the target.
-However, scattered lights from nearby bright stars and galaxies could bias the modeling of sources within the bounding box (e.g., the yellow star in the top left panel of Figure \ref{fig:vanilla_scarlet_demo}).
+However, scattered light from nearby bright stars and galaxies could bias the modeling of sources within the bounding box (e.g., the yellow star in the top left panel of Figure \ref{fig:vanilla_scarlet_demo}).
 We match our field with the Gaia catalog and mask out stars outside of the bounding box.
@@
 We demonstrate the above procedures in Figure \ref{fig:vanilla_scarlet_demo} with two examples.
-The one shown in the top panels is a blue LSBG, whereas the one shown in bottom is a high-$z$ galaxy blended with the outskirts of nearby galaxy which falls in our initial sample as a false positive.
+The one shown in the top panels is a blue LSBG, whereas the one shown on the bottom is a high-$z$ galaxy blended with the outskirts of a nearby galaxy which falls in our initial sample as a false positive.
 The first column shows the $griz$ color-composite image \citep{Lupton2004}, where the white boxes mark the bounding box of each source in the scene.
-As seen, the gray shades over objects outside of the target bounding box indicate they are masked out.
+The gray shades over objects outside of the target bounding box indicate they are masked out.
 The second column shows the initial \code{scarlet} models.
@@
 The model is considered to be converged when the relative changes of parameters are smaller than \code{e\_rel\,=\,2e-4}.
-Typically convergence is achieved after $\sim 50$ steps of optimization and the whole modeling takes about 40s for typical LSBGs.
+Typically, convergence is achieved after $\sim 50$ steps of optimization and the whole modeling takes about 40s for a typical LSBG.
 It takes longer when the target galaxy has large angular size since more peaks are modeled.
@@
 For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact.
-The reason why it passes our initial selection is that the galaxy outskirts are shredded by Source Extractor and happen to have a large size and right color.
+The reason why it passes our initial selection is that the galaxy outskirts are shredded by Source Extractor and happen to have a large size and the right color.
 But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.
@@
 The total magnitudes are simply calculated by summing up the model in each band, and colors are defined using total magnitudes.\footnote{Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
-We also define the average surface brightness within effective radius as $\mu_{\rm eff} = m - 2.5 \log_{10}(2 \pi r_e^2)$, where $m$ is the total magnitude.
+We define the average surface brightness within the effective radius as $\mu_{\rm eff} = m - 2.5 \log_{10}(2 \pi r_e^2)$, where $m$ is the total magnitude.
 
 We also use the Gini-M20 and CAS statistics.
-The Gini coefficient and M20 statistics \citep{Abraham2003,Lotz2004} quantify how concentrated/extended is the flux distribution across the image.
+The Gini coefficient and M20 statistics \citep{Abraham2003,Lotz2004} quantify how concentrated/extended the flux distribution is across the image.
 The CAS statistics characterize the concentration $C$, asymmetry $A$, and smoothness $S$ of the light distribution of the object.
 We refer the readers to \citet{statmorph} for more details on their definitions and implementations.
-The morphological and structural parameters are the same in different bands by construction of the \code{scarlet} model.
-
-To better guide us on how to use these diagnostics, we visually inspected a subset of LSBG candidates in our initial sample (Sec \ref{sec:detection}) and use the labels to construct the metrics.
+The morphological and structural parameters are the same in different bands by construction in the \code{scarlet} model.
+
+To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (Sec \ref{sec:detection}) and use the labels to construct the metrics.
 We randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see Sec \ref{sec:match} for details).
@@
 Each object has been inspected by at least one person.
-In the end, we combine the votes from different persons.
-An object is classified as \code{junk} if the number of votes as \code{junk} prevails the number of votes as \code{candy} and \code{galaxy}.
+In the end, we combine the votes from different people.
+An object is classified as \code{junk} if the number of votes as \code{junk} is larger than the number of votes as \code{candy} and \code{galaxy}.
 For objects that are not \code{junk}, if the number of votes as \code{candy} is greater than the votes as \code{galaxy}, we classify this object as \code{candy}.
 Everything else is classified as \code{galaxy}.
-In total, there are 1146 \code{candies}, 2146 \code{galaxies}, and 1708 \code{junks}.
-
-We use this visual inspection results to teach us how to use the morphological and structural diagnostics.
+In total, there are 1146 \code{candies}, 2146 \code{galaxies}, and 1708 \code{junk}.
+
+We use these visual inspection results to teach us how to use the morphological and structural diagnostics.
 The distributions of \code{candy} (blue), \code{galaxy} (green), and \code{junk} (red) in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}.
 False positives (\code{junk}) are highlighted in red.
-Although \code{junks} are scattered all over the parameter space, a large fraction of them have small size, extreme colors, very faint surface brightness, large concentration and large asymmetry.
+Although \code{junk} is scattered throughout the parameter space, a large fraction of the junk comprises small things with extreme colors that have small size and very faint surface brightness, large concentration and large asymmetry.
 Therefore, we come up with the following selection cuts to remove the false positives:
@@
 \end{itemize}
-These criteria (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove objects that are not likely being LSBGs of interest.
-The color cuts here is narrower than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junks and background high redshift galaxies.
+These criteria (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove objects that are not likely to be LSBGs of interest.
+The color cuts here are narrower than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and background high redshift galaxies.
 We not only remove objects with small sizes, but also exclude objects with large size, very low surface brightness, and high concentration.
-This is because the scarlet model of some junks can be very concentrated in the center but also extends quite far.
+This is because the scarlet models of some junk can be very concentrated in the center but also very extended.
 The slant demarcation line on the Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to separate merging galaxies from normal galaxies.
@@
 But everything comes with a price.
-This cuts sacrifice the completeness of real LSBGs.
+Thess cuts sacrifice the completeness of real LSBGs.
 In Section \ref{sec:completeness}, we characterize the completeness of this ``deblending'' cuts by injecting mock \sersic{} galaxies.
+\jiaxuan{say our completeness is still high.
+}
 
@@
 
+\jiaxuan{Compare with smudges and des, discuss why not ML.}
+
 \subsection{Modeling}\label{sec:modeling}
-Although vanilla scarlet does a good job on removing false positives, the measured size, magnitude, and surface brightness on the vanilla scarlet model are quite biased.
+Although vanilla scarlet does a good job at removing false positives, the measured size, magnitude, and surface brightness on the vanilla scarlet model are quite biased.
 These measurements cannot be used to derive the physical properties of LSBGs.
@@
 Second, the monotonicity constraint stops the model to grow in certain directions if there is another source along this direction, otherwise the monotonicity is broken.
-This issue, dubbed as the ``cookie-cutter effect'', can be seen in Figure \ref{fig:vanilla_scarlet_demo}.
-As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biases the measuremenets.
+This issue, dubbed the ``cookie-cutter effect'', can be seen in Figure \ref{fig:vanilla_scarlet_demo}.
+As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biasing the measurements.
 
@@
 \subsection{A better definition for diffuse galaxies}
+
+\subsection{Systematic search for LSBGs in LSST era}
 

### 2022-08-20 main.tex
slowly progressing, now finish proofreading Sec 3.3

@@
 
+This paper is framed as follows. We detect LSBGs, then match them to MW analogs such that we can assume distances.
+
 % Continuing the work by \citep{Greco2018}, we conducted a systematic search for low surface brightness galaxies (LSBGs) in Hyper Suprime-Cam survey (HSC) imaging data (Li et al., in prep).
@@
 
-In this work, we use the \code{Wide} layer data from the Public Data Release 2 (PDR2, also known as \code{S18A}, \citealt{Aihara2018}) of the HSC survey.
+In this work, we use the \code{Wide} layer coadd data from the Public Data Release 2 (PDR2, also known as \code{S18A}, \citealt{Aihara2018}) of the HSC survey.
 It covers $\sim 300\ \rm{deg}^2$ in all five bands, being 1.5 times larger than the data set (\code{S16A}) analyzed in \citet{Greco2018}.
@@
 \subsubsection{Source Extraction}
-We use \code{Source Extractor} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
+We use \href{https://www.astromatic.net/software/sextractor/}{\code{Source Extractor}} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
 This step remains largely the same as in \citetalias{Greco2018}.
@@
 After these steps, we have an initial sample that contains 86,002 LSBG candidates.
-We obtain four times more sources per square degree than \citetalias{Greco2018} mainly because PDR2 has a better sky subtraction,  our detection is more inclusive for larger objects, and our size cut is less restrictive for small objects.
+We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because PDR2 has a better sky subtraction,  our detection is more inclusive for larger objects, and our size cut is less restrictive for small objects.
 Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirri, blended compact sources, etc.
@@
 \subsection{Deblending}\label{sec:deblending}
+Removing false positives from the initial sample while retaining high completeness is one of the major challenges in LSBG search \citep[e.g.,][]{vanDokkum2015,Koda2015,Yagi2016,Greco2018,SAGA-I,Zaritsky2019,Zaritsky2021,Tanoglidis2021,Zaritsky2022}.
 A common type of false positive occurs when point-like sources are blended with diffuse light from background galaxies or the LSB outskirts of stars and galaxies.
@@
 It utilizes the color and morphology information to separate blended objects.
-In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018} and the online documentation for more details.
+In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation for more details.
 
@@
 
-Similar to many other modeling codes (e.g., \code{galfit}, \code{imfit}), \code{scarlet} is initialized with positions of detected peaks in the prior steps.
+Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with positions of detected peaks in the prior steps.
 The models are then optimized subject to the constraints.
@@
 However, there are still faint and compact peaks not detected.
-We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep high spatial frequency components.
+We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering).
 Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels.
@@
 We visually inspected 5,000 LSBG candidates and labeled them as \code{candy} (LSBGs with typically dwarf galaxy features), \code{galaxy} (higher surface brightness galaxies or galaxies with spiral galaxy features), and \code{junk} (false positives).
-We propose a selection based on size, color, surface brightness and morphology (dashed boxes) to effectively remove false positives.
+We propose a selection based on size, color, surface brightness and morphology (dashed boxes) to effectively remove false positives but still achieves a high completeness.
 After such cuts (bottom panels), 97\% of false positives and 75\% of non-LSB galaxies are removed according to our visual inspection results.
@@
 After running the vanilla scarlet for LSGB candidates, we successfully deblend the target object from nearby sources.
-We take out the model of the target object (as shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}) and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}.
+Unlike other modeling codes, the non-parametric \code{scarlet} model is very flexible on modeling galaxies with complex structures.
+But the non-parametric nature means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model.
+As shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}, we take out the model of the target object and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}.
 The purpose of this analysis is to extract the structural and morphological parameters of the target object.
@@
 The distributions of \code{candy} (blue), \code{galaxy} (green), and \code{junk} (red) in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}.
-False positives (\code{junk}) are highlighted in red.
-Although \code{junk} is scattered throughout the parameter space, a large fraction of the junk comprises small things with extreme colors that have small size and very faint surface brightness, large concentration and large asymmetry.
+Although \code{junk} is scattered throughout the parameter space, a large fraction of the junk comprises small things with very red colors, very faint surface brightness, large concentration and large asymmetry.
 Therefore, we come up with the following selection cuts to remove the false positives:
@@
 This empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample.
-But everything comes with a price.
-Thess cuts sacrifice the completeness of real LSBGs.
-In Section \ref{sec:completeness}, we characterize the completeness of this ``deblending'' cuts by injecting mock \sersic{} galaxies.
-\jiaxuan{say our completeness is still high.
-}
-
+Furthermore, the completeness of real LSBG detection remains high.
+In Section \ref{sec:completeness}, we characterize the completeness of this ``deblending'' step by injecting mock \sersic{} galaxies, and we achieve $\sim80\%$ completeness at $\sbeff = 27.0\ \sbunit$ and $>50\%$ completeness at $\sbeff = 27.5\ \sbunit$ (Fig.
+\ref{fig:completeness}).
 We emphasize that the vanilla scarlet modeling and non-parametric measurements are not designed to recover the intrinsic properties of the galaxies.
-They are only used as a diagnostic tool to remove false positives.
-In fact, the vanilla scarlet model usually under-estimates the size and the total flux of LSB objects because the faint outskirts are typically not modeled well due to the non-parametric nature of vanilla scarlet and the monotonicity constraint.
-In the following section, we propose a method to better measure the size and total magnitude of LSBG for science.
-
-\jiaxuan{Compare with smudges and des, discuss why not ML.}
+They are used only as a diagnostic tool to remove false positives.
+We perform more detailed modeling in Section \ref{sec:modeling} to measure galaxy properties for science.
+
+We notice that many other works have been using machine learning (ML) algorithms to classify LSBG candidates and exclude spurious detection.
+Among others, \citet{Tanoglidis2021} take the output catalog from \code{Source Extractor} and use the Support Vector Machine algorithm to classify objects in their initial sample and reduce the number of objects that are visually inspected.
+\citet{Zaritsky2019,Zaritsky2021,Zaritsky2022} use convolutional neural networks to classify LSBGs into binary classes based on their images.
+These endeavors certainly help reducing the human labor on visually inspecting tens of thousands of objects.
+However, training such a supervised ML algorithm relies on the labeled data which should also sample the parameter space evenly.
+Once labels are assigned (e.g., LSBG v.s.
+non-LSBG), there will be little way to change later.
+On the contrary, our cuts based on the measured properties can be tweaked to be more complete (including more junks) or be more pure (aggressive cuts) depends on the specific science goal.
+The visual inspections only guide us to design those metrics.
+This measurement-based method is more intuitive, reproducible, and transferable.
+We will also explore machine learning methods and compare with our deblending cuts in future works.
+We would also like to utilize the information about the Milky Way dust to exclude spurious detection on Galactic cirrus \citep{Zaritsky2021,Zaritsky2022}.
+
+% Tanoglidis doesn't estimate measurement uncertainty.
+Doesn't systematically estimate completeness, only validates the comp using deeper fornax observations.
+Also, the artifact of HSC is less compared with DES/DECaLS?
+% SMUDGES: Their sample might be cleaner thanks to their wavelet detection emphasizing specific spatial frequency. But they still need a lot of visual inspection.
 
 \subsection{Modeling}\label{sec:modeling}
-Although vanilla scarlet does a good job at removing false positives, the measured size, magnitude, and surface brightness on the vanilla scarlet model are quite biased.
-These measurements cannot be used to derive the physical properties of LSBGs.
-
-The non-parametric modeling in \code{scarlet} assumes weak correlation between pixels by imposing the monotonicity constraint.
-This leads to two problems when applying vanilla scarlet to the LSBGs.
-First, since pixels are not strongly correlated in the model, the model cannot capture the galaxy light at very low signal-to-noise ratio.
-Second, the monotonicity constraint stops the model to grow in certain directions if there is another source along this direction, otherwise the monotonicity is broken.
-This issue, dubbed the ``cookie-cutter effect'', can be seen in Figure \ref{fig:vanilla_scarlet_demo}.
+Although the vanilla scarlet modeling provides useful information to help us remove false positives, it does not necessarily give us unbiased estimations on size, color, total magnitude, etc.
+In fact, the vanilla scarlet model usually under-estimates the size and the total flux of LSB objects.
+This is because the faint outskirts of LSBGs are typically not modeled well due to the non-parametric nature of vanilla scarlet.
+We elaborate this point as follows.
+
+When doing parametric modeling such as \sersic{} fitting, we effectively apply radial averaging within elliptical annulus and boost the SNR by binning pixels.
+In other words, pixels within the same isophotal annulus are assumed to have the same intensity thus are strongly correlated.
+However, the non-parametric nature of vanilla \code{scarlet} only assumes monotonicity, which imposes quite weak correlation among pixels.
+Consequently, it is very hard to for the non-parametric modeling to probe down to very low surface brightness features.
+Furthermore, the monotonicity constraint stops the model to grow in certain directions if there is another source along this direction, otherwise the monotonicity is broken.
+This issue, dubbed the ``cookie-cutter effect'', can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model for target object never exceeds the other objects next to it.
 As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biasing the measurements.
-
-On the other side, parametric modeling imposes a very strong correlation on pixels.
-For example, using a 1-D light profile such as \sersic{}, pixels within an isophote are assumed to have the same intensity.
-Therefore, the signal-to-noise ratio in the outskirts is boosted by effectively combing the information from many pixels.
-The parametric model also does not suffer from the ``cookie-cutter'' issue.
+In the following, we explore a novel method to perform parametric fitting while combing the advantage of \code{scarlet}.
 
 A traditional way of doing parametric modeling is to first mask out contaminants based on the detection segmentation map, then fit a model to the masked image.
-However, the fitting results are very sensitive to the masking scheme \citep[e.g.,][]{Greco2018}.
-A possible solution to this problem is to model all the objects in the cutout simultaneously using parametric models (e.g., in DECaLS, \citealt{Dey2019}).
+However, the fitting results are very sensitive to the masking scheme \citep[e.g.,][]{Greco2018} and sky background.
+A possible solution to this problem is to simultaneously model all the objects in the cutout and the sky using parametric models (e.g., in DECaLS, \citealt{Dey2019}).
 In this work, we combine the advantage of parametric modeling with the power of deblending in \code{scarlet}.
 To be specific, we follow the spirit of deblending as described in Section \ref{sec:deblending}, but replace the non-parametric model for the target with a parametric model.
-In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized.
-
-We use the Spergel light profile to model the LSBGs.
-The Spergel profile is motivated by having a simple analytical expression in Fourier space, making it easy to be convolved with a PSF.\footnote{On the opposite, the \sersic{} profile does not have a simple analytic form in Fourier space.} The surface brightness of a Spergel profile \citep{Spergel2010} has a form of
+In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized because they are modeled simultaneously.
+The parametric model for the target object does not suffer from the ``cookie-cutter'' issue any more.
+
+We use the Spergel surface brightness profile \citep{Spergel2010} to model the LSBGs.
+The Spergel profile is motivated by having a simple analytical expression in the Fourier space, making it easy to be convolved with a PSF\footnote{On the opposite, the \sersic{} profile does not have a simple analytic form in the Fourier space.}.
+The surface brightness of a Spergel profile has a form of
 \begin{equation}
@@
 and $K_\nu(u)$ is the Modified Bessel function of the second kind.
-The half-light radius is $r_0$, the total luminosity is $L_0$, and $c_\nu$ satisfyies the equation $(1 + \nu)f_{\nu + 1}(c_\nu) = 1/4$.
-Similar to the \sersic{} index, the parameter $\nu$ (Spergel index) controls the concentration of the light profile.
+The half-light radius is $r_0$, the total luminosity is $L_0$, and $c_\nu$ satisfies the equation $(1 + \nu)f_{\nu + 1}(c_\nu) = 1/4$.
+Similar to the \sersic{} index, the parameter $\nu$ (dubbed as ``Spergel index'') controls the concentration of the light profile.
 As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is interested to the study of LSBGs.
 
-There are several changes in the modeling compared to the deblending step.
-First, we intialize a vanilla scarlet model for the target object as in Section \ref{sec:deblending}.
-Then we measure the half-light radius, total flux, and shape of the scarlet model.
+We initialize the Spergel model for the target object differently, while other objects are still initialized in the same way as in the deblending step (Section \ref{sec:deblending}).
+First, we initialize a vanilla scarlet model for the target object, and we measure the effective radius $r_e$, total flux, and the shape of the scarlet model.
 We use these numbers to initialize the Spergel profile.
-The size of the bounding box is also updated to be the maximum between 250 pixel and $10\, r_e$.
-Objects within this bounding box are included in the modeling, but only the target object is modeled by the Spergel profile.
-For the target, we still requires positivity constraint, as the mononicity is automatically satisfied.
+The size of the bounding box is also updated to be the maximum between 250 pixels and $10\, r_e$.
+Peaks within this bounding box (other than the target) are modeled using vanilla scarlet.
+For the target, we still requires positivity constraint, and the monotonicity is automatically satisfied by the Spergel profile.
 
@@
 The average surface brightness $\overline{\mu}_{\rm eff}$ is calculated in the same way as in Section \ref{sec:non-par-measurement}.
-
-We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}.
-Overall speaking, the measurement agrees with the truth quite well.
-However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$ is under-estiamted.
-We also characterize the bias and the scatter in measurement as a function of size and surface brightness.
-We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.
+In the following section, we assess the quality of the Spergel modeling by injecting mock \sersic{} galaxies and compare recovered properties with truth.
 
 \subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}
+The completeness of the LSBG search is important not only for understanding our searching efficiency and improving the method in the future but also for deriving the completeness-corrected results for LSBG sciences.
+Similar to many other works \citep[e.g.,][]{Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and try to recover them from the image.
+Using these mock galaxies, we also characterize the measurement bias and uncertainty by comparing the measured properties with the truth.
 
 \subsubsection{Completeness}\label{sec:completeness}
+%Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands. 
+A real LSBG can be missed in the detection step (Sec.
+\ref{sec:detection}) or be excluded in the deblending step (Sec.
+\ref{sec:deblending}).
+Thus, the overall completeness is a combination of detection completeness and deblending completeness.
+We performed a large suite of image simulation to derive the completeness.
+The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remained after the deblending cuts.
+
+For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline.
+This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
+However, we find no noticeable difference on the completeness between this method and the direct injection to coadd images.}.
+The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$) by resembling the LSBG distribution in \citetalias{Greco2018}.
+They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
+Then we run the detection step as described in Sec.
+\ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
+
+We find that the detection completeness mainly depends on the size and surface brightness.
+As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
+It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$.
+We find negligible dependence of completeness on \sersic{} index, color, and ellipticity.
+Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
+We find the completeness declines for $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
+Please see \citet{Greene2022} for more details.}
+
+For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
+The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
+We measure the size and surface brightness on the scarlet models of the mock galaxies, then we apply the deblending cuts.
+The deblending completeness as a function of size and surface brightness is shown in the middle panel of Figure \ref{fig:completeness}.
+The deblending completeness is very high at the bright end, but starts to decline with increasing size and surface brightness.
+Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
+Interestingly, the detection completeness and deblending completeness all drop below 40\% around $\sbeff=27.5\ \sbunit$.
+In this sense, the detection and deblending cooperate well in terms of completeness.
+
+The combined completeness is shown in the right panel of Figure \ref{fig:completeness}.
+The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours.
+We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
+The completeness drops as we go to fainter surface brightness and smaller size.
+
+Compare with vdb17, carlsten22, smudges21/22, tanoglidis21.
+
+Our high completeness demonstrates the power of HSC images on LSBG studies.
+
+\jiaxuan{Also compare our completeness with other surveys.}
+
 \begin{figure*}
@@
 	}
-	\caption{Caption}
+	\caption{The completeness of our LSBG search as a function of effective radius $r_e$ and the average surface brightness $\sbeff$.
+We characterize the completeness by injecting mock \sersic{} galaxies into coadd images.
+The overall completeness (right panel) comprises the detection completeness (left panel, see Sec.
+\ref{sec:detection}) and deblending completeness (middle panel, see Sec.
+\ref{sec:deblending}) where false positives are removed.
+The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours.
+The completeness drops for smaller sizes and faint surface brightness.
+We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
+The completeness drops as we go to fainter surface brightness and smaller size.
+	%The mock galaxies span a large range in size, surface brightness, \sersic{} index, color, and ellipticity. 
+	}
 	\label{fig:completeness}
@@
 
-%Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands. 
-After the source detection step and the deblending step, we obtain a sample of LSBG candidates where the fraction of false positives is very small.
-
-It is crucial to characterize the completeness of both detection and deblending in order to understand our survey efficiency and the properties of the LSBG population.
-We performed a large suite of image simulation to derive the completeness.
-The overall completeness is a combination of detection and deblending completenesses.
-The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remained after cuts.
-
-For the detection completeness, we inject $\sim 35,000$ (check number with Johnny) mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline.
-This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
-However, we find no noticable difference between this method and the direct injection to coadd images.}.
-The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \epsilon < 0.6$), resembling the LSBG distribution in \citetalias{Greco2018}.
-They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$) and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
-
-We find the detection completeness mainly depends the size and surface brightness of mock galaxy.
-As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
-It drops below 50\% when the surface brightness gets fainter than 27.5 mag arcsec$^{-2}$.
-We find negligible dependendce of completeness on \sersic{} index, color, and additional structure of galaxy (such as star-forming clumps).
-However, we find the completeness declines above ellipticity $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
-In this work, we neglect the dependences of detection completeness on parameters other than size and surface brightness.
-
-% \textbf{Need to update the completeness to the S18A version. Ping Johnny.}
-
-For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
-The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
-Following the procedure described in Sec \ref{sec:deblending}, we measure the non-parametric sizes and surface brightnesses on the scarlet models of the mock galaxies.
-The deblending completeness is shown in the middel panel of Figure \ref{fig:completeness}.
-The deblending completeness is high at bright surface brightnesses, but starts to decline with increasing size and surface brightness.
-Mock galaxies fainter than $\overline{\mu}_{\rm eff}(g) > 27.5$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
-The deblending step is very effective on removing false positives, but at a cost of losing very LSB galaxies.
-
-The combined completeness is shown in the right panel of Figure \ref{fig:completeness}.
-The countours shows the 70\%, 50\%, and 20\% completenesses, respectively.
-\textbf{Also compare our completeness with other surveys.}
-
-%\textbf{Make sure that completeness is assigned based on the bias-corrected size and SB.} Checked. No problem.
-
 \subsubsection{Measurement uncertainty}\label{sec:meas_unc}
+% , which is common in the low surface brightness regime (see e.g. \citealt{Haussler2007,Zaritsky2021}). Galfit also have very strong bias.
+
 We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}.
@@
 We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.
+
+\citet{Tanoglidis2022ICML} estimates the measurement error using a Bayesian Neural net.
 
@@
 \subsection{Matching with Milky-Way analogs}\label{sec:match}
+
+Distance information of LSBGs is hard to know \citep{Kadowaki2021,Greene2022,Zaritsky2022} (also another cross-correlation paper recently?)
+
 The goal of this paper is to study the UDG population hosted by MW-like galaxies.
@@
 
-\subsection{Systematic search for LSBGs in LSST era}
+% \subsection{Systematic search for LSBGs in the LSST era}
 
@@
 Overall, the Spergel profile is a good approximation to \sersic{} from $n\approx 0.5$ to $n\approx 4.5$.
-It is well-known that the light profiles of low-mass galaxies are quite flat and can be described using \sersic{} profiles with $0.5 < n < 1.5$ \citep[e.g.,][]{Lange2015,Greco2018,ELVES-I}.
+It is well-known that the light profiles of low-mass galaxies are quite flat and can be described using \sersic{} profiles with $0.5 < n < 1.5$ \citep[e.g.,][]{vanDokkum2015,Lange2015,Greco2018,Zaritsky2021,ELVES-I}.
 It is thus reasonalbe to use Spergel profiles to model the LSBGs (Sec \ref{sec:modeling}) and enjoy its convenience in the Fourier space.

### 2022-08-21 main.tex
噫芜

@@
 The redshifts of galaxies in NSA come from several spectroscopic surveys, gas surveys, or direct distance measurements.
-
-\jiaxuan{Any other data we should introduce? No?}
 
@@
 In other words, pixels within the same isophotal annulus are assumed to have the same intensity thus are strongly correlated.
-However, the non-parametric nature of vanilla \code{scarlet} only assumes monotonicity, which imposes quite weak correlation among pixels.
-Consequently, it is very hard to for the non-parametric modeling to probe down to very low surface brightness features.
-Furthermore, the monotonicity constraint stops the model to grow in certain directions if there is another source along this direction, otherwise the monotonicity is broken.
-This issue, dubbed the ``cookie-cutter effect'', can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model for target object never exceeds the other objects next to it.
+However, the non-parametric nature of vanilla \code{scarlet} only assumes monotonicity, which imposes quite weak correlations among pixels.
+Consequently, it is very hard for the non-parametric modeling to probe down to very low surface brightness features.
+Furthermore, the monotonicity constraint stops the model from growing in certain directions if there is another source along this direction, otherwise monotonicity is broken.
+This issue, dubbed the ``cookie-cutter effect'', can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model of the target object never exceeds the other objects next to it.
 As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biasing the measurements.
-In the following, we explore a novel method to perform parametric fitting while combing the advantage of \code{scarlet}.
+In the following, we explore a novel method to perform parametric fitting while exploiting the advantages of \code{scarlet}.
 
@@
 Similar to the \sersic{} index, the parameter $\nu$ (dubbed as ``Spergel index'') controls the concentration of the light profile.
-As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is interested to the study of LSBGs.
+As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is relevant to the study of LSBGs.
 
@@
 Peaks within this bounding box (other than the target) are modeled using vanilla scarlet.
-For the target, we still requires positivity constraint, and the monotonicity is automatically satisfied by the Spergel profile.
-
-After optimization, we take the $r_0$ in Equation \eqref{eq:spergel} as the circularized half-light radius $r_e$, and take the $L_0$ as the total flux.
+For the target, we still require positivity constraint, and the monotonicity is automatically satisfied by the Spergel profile.
+
+After optimization, we take the $r_0$ in Equation \eqref{eq:spergel} as the circularized half-light radius $r_e$, and take $L_0$ as the total flux.
 The average surface brightness $\overline{\mu}_{\rm eff}$ is calculated in the same way as in Section \ref{sec:non-par-measurement}.
-In the following section, we assess the quality of the Spergel modeling by injecting mock \sersic{} galaxies and compare recovered properties with truth.
+In the following section, we assess the quality of the Spergel modeling by injecting mock \sersic{} galaxies and comparing the recovered properties with truth.
 
@@
 We performed a large suite of image simulation to derive the completeness.
-The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remained after the deblending cuts.
-
-For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline.
+The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.
+
+For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
 This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
-However, we find no noticeable difference on the completeness between this method and the direct injection to coadd images.}.
+However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}.
 The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$) by resembling the LSBG distribution in \citetalias{Greco2018}.
@@
 We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}.
-Overall speaking, the measurement agrees with the truth quite well.
-However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27\ \sbunit$ is under-estiamted.
-We also characterize the bias and the scatter in measurement as a function of size and surface brightness.
-We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.
+Overall, the measurement agrees with the truth quite well.
+However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27\ \sbunit$ are systematically under-estimated.
+We also characterize the bias and the scatter in the measurement as a function of size and surface brightness.
+We apply the bias correction to the LSBG measurement, and incorporate the measurement error into the science figures.
 
@@
 
-In order to test how well do we recover the photometric and structural parameters in the modeling step (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
+In order to test how well we recover the photometric and structural parameters in the modeling step (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
 We compare the fitting results with the ground truth in Figure \ref{fig:meas_bias}, where $\Delta(X) = X(\rm truth) - X(\rm measured)$, and x-axis corresponds to the truth values.
@@
 
-To correct for this bias in size, surface brightness, apparant magnitude, and color, we assume that the bias only depends on the size and surface brightness.
+To correct for this bias in size, surface brightness, apparent magnitude, and color, we assume that the bias only depends on the size and surface brightness.
 Indeed, we do not find any significant dependence of the bias on color, ellpticity, and Spergel index.
-We split the $r_e-\overline{\mu}_{\rm eff}(g)$ plane using a $8\times 8$ grid, and calculate the mean bias within each bin.
+We split the $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias within each bin.
 Then we interpolate over the grid using a multiquadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
@@
 For half-light radius, we take $(r_{e, \rm t} - r_{e, \rm m}) / r_{e,\rm m}$ as the bias term; for surface brightness, we take $\overline{\mu}_{\rm eff, t}(g) - \overline{\mu}_{\rm eff, m}(g)$ as the bias term.
-As shown in Figure \ref{fig:meas_err}, the size and surface brightness bias grows as increasing surface brightness.
-The bias has a peak at $r_e\sim 6\arcsec$ because the $r_e$ shown in the figure is the measured size, not the truth size.
+As shown in Figure \ref{fig:meas_err}, the size and surface brightness bias grows with increasing surface brightness.
+The bias has a peak at $r_e\sim 6\arcsec$ because the $r_e$ shown in the figure is the measured size, not the true size.
 It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
@@
 
-Besides, it is also important to characterize the measurement uncertainty.
+It is also important to characterize the measurement uncertainty.
 The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, contamination effects, etc.
-Unlike other parametric modeling code such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimal solution.
-Thus we cannot get a statistical error of the measured properties from \code{scarlet}.
+Unlike other parametric modeling codes such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimal solution.
+Thus we cannot get a statistical error on the measured properties from \code{scarlet}.
 However, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor.
-Following the same way of calculating the bias, in each bin, we compute the standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid.
+Following the same method as that of calculating the bias, in each bin we compute the standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid.
 The measurement errors are shown in Figure \ref{fig:meas_err} as contours.
@@
 The goal of this paper is to study the UDG population hosted by MW-like galaxies.
-However, the properties of MW itself vary in literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among groups.
+However, the properties of the MW itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among groups.
 In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig 2 of \citealt{SAGA-I}).
@@
 They also require the MW analogs to be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20-40 Mpc).
-In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$ ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA.
+In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$~mag ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA.
 We choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($\sim 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
-MW analogs selected using this definition is very close to those in SAGA but are slightly more massive than the ELVES hosts.
+MW analogs selected using this definition are very close to those in SAGA but are slightly more massive than the ELVES hosts.
 
 Since UDGs are relatively scarce in MW-like hosts \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics.
-However, UDGs will be too small and faint to be detected in HSC images beyond certain distances.
+However, UDGs will be too small and faint to be detected in HSC images beyond a certain distance.
 We choose our redshift range to be $0.01 < z < 0.04$, which makes sure that we can detect a significant number of faint dwarf galaxies around MW-like hosts.
-We exclude galaxies $z<0.01$ because 1) the number is very small; 2) their large angular size makes them shredded in deblending step, including them will introduce a lot of spurious LSB objects.
-Our MW analogs sample complements the ELVES sample and SAGA sample in redshift range.
+We exclude galaxies $z<0.01$ because 1) the number is very small; 2) their large angular size makes they may be shredded in the deblending step, so that including them will introduce a number of spurious LSB objects.
+Our MW analogs sample complements the ELVES sample and SAGA sample in our redshift range.
 
@@
 We also remove duplicated objects.
-In the end, we have 2510 LSBG candidates as our final LSBG sample, from which we construct the ultra-diffuse galaxy (UDG) sample and the ultra-puffy galaxy (UPG) sample as follows.
+In the end, we have 2510 LSBG candidates as our final LSBG sample, from which we construct the ultra-diffuse galaxy (UDG) sample and the ultra-puffy galaxy (UPG) samples as follows.
 
@@
 The measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020} or other contaminants.
-Therefore in this work, we use the average surface brightness within effective radius $\sbeff$ to define UDG.
-The difference between the average surface brightness and the central surface brightness for \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
-Since dwarf galaxies and UDGs typically has \sersic{} index in a range of $0.8 < n < 1.2$ \citep{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value.
+Therefore in this work, we use the average surface brightness within an effective radius $\sbeff$ to define UDG.
+The difference between the average surface brightness and the central surface brightness for a \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
+Since dwarf galaxies and UDGs typically show a range of \sersic{} index $0.8 < n < 1.2$ \citep{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value.
 In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, which takes the measurement errors into account.
@@
 The concept of UDG was proposed for those dwarf galaxies with large physical size and diffuse light distribution.
-However, the size of a galaxy is strongly correlated with its mass, as known as the mass-size relation \citep[e.g.,][]{Lange2015}.
+However, the size of a galaxy is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Lange2015}.
 The slope of the mass-size relation has been shown to be color-dependent for galaxies above $M_\star > 10^{8.5}\ M_\odot$: blue star-forming galaxies have a shallower slope, whereas red quenched galaxies have a steeper slope.
@@
 Taking the measured mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the mass-size relation.
-The UPGs are not necessarily large in physical size or faint in average surface brightness.
-Both UDG and UPG represent subsets of dwarf galaxies that are larger and diffuser than average.
-However, the hard cut on size (1.5 kpc) makes UDG losing ``large'' galaxies at the low-mass end because as mass goes smaller, the average size also gets smaller.
-The surface brightness cut of UDG also biases the UDG sample in color distribution and further bias the quenched fraction, as will be discussed in Section \ref{sec:quench}.
-The definition of UPG based on the observed mass-size relation is more physics-motivated, and UPG better represents a homogeneous subset of dwarf galaxies along the stellar mass axis.
+The UPGs are not necessarily large in physical size or faint in average surface brightness {\bf JEG: but they are size outliers for their mass}.
+Both UDG and UPG represent subsets of dwarf galaxies that are larger and more diffuse than average.
+However, the hard cut on size (1.5 kpc) means that the UDG definition excludes ``large'' galaxies at the low-mass end because as mass goes smaller, the average size also gets smaller.
+The surface brightness cut also biases the UDG sample because of mass-to-light ratio differences between blue and red galaxies, as will be discussed in Section \ref{sec:quench}.
+The definition of UPG based on the observed mass-size relation is more physically-motivated, and UPGs better represent a homogeneous subset of dwarf galaxies along the stellar mass axis.
 There is also no color preference in the UPG definition for a given stellar mass.
-It is worth noticing that definition based on mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.
-
-There are 362 objects in our LSBG candidates satisfying that they are $1.5\sigma$ above the ridge line of the mass-size relation.
+It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.
+
+There are 362 objects in our LSBG candidates that fall $1.5\sigma$ above the ridge line of the mass-size relation.
 After visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
@@
 The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively.
-Two marginal plots show the unnormalized histograms of galaxies in the two color bins.
+The two marginal plots show the unnormalized histograms of galaxies in the two color bins.
 The numbers of red and blue galaxies are similar in the UDG sample, but there are more blue galaxies than red ones in the UPG sample.
-Since there is no hard surface brightness cut, the UPG sample includes a lot of blue galaxies with higher surface brightness ($\sbeff < 25$).
-The UPG sample also lose a significant fraction of red galaxies at $25 < \sbeff < 26$, because they are not LSB (hence low-mass) enough to be higher than $1.5\sigma$ from the mass-size relation.
+Since there is no hard surface brightness cut, the UPG sample includes many blue galaxies with higher surface brightness ($\sbeff < 25$).
+The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26$, because they are not LSB (hence low-mass) enough to be higher than $1.5\sigma$ from the mass-size relation.
 
@@
 We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}.
-We corrected for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
+We correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
 The magnitudes and surface brightnesses are also extinction-corrected.
@@
 The major weakness of LSBG searches in photometric data is that distance information is typically unknown.
-Although we have matched LSBGs to MW analogs with known redshifts, the affiliation of LSBGs to the host is still not guaranteed.
-As a result, a certain fraction of galaxies in our UDG and UPG sample might just be foreground or background galaxies that fall within the virial radius of the host by projection.
-Given the volume probed by our search, contamination is more probable to be dominated by background galaxies.
-We estimate the fraction of contamination as follows.
-
-We selected a patch of sky with 24 deg$^{2}$ in HSC S18A.
-Then we performed the same deblending and modeling steps for 2707 LSBGs detected in this region.
+Although we have matched LSBGs to MW analogs with known redshifts, the affiliation of LSBGs to the host is not guaranteed.
+As a result, a certain fraction of galaxies in our UDG and UPG sample might just be foreground or background galaxies that fall within the virial radius of the host in projection.
+Given the volume probed by our search, contamination is most likely to be dominated by background galaxies.
+We estimate the contamination fraction as follows.
+
+We select a patch of sky of 24 deg$^{2}$ in HSC S18A.
+Then we perform the same deblending and modeling steps for the 2707 LSBGs detected in this region.
 \footnote{The sky region is randomly selected, and these LSBGs share the same properties with our initial LSBG sample described in Section \ref{sec:match}.} We also removed objects that are already in our UDG sample, and we did visual inspection to further remove spurious objects.
@@
 Then we calculate a physical radius for each LSBG and classify an LSBG as a ``fake`` UDG if it satisfies the definition.
-We repeat the random matching for 200 times, and we obtain 11,458 fake UDGs.
+We repeat the random matching 200 times, and we obtain 11,458 fake UDGs.
 In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.94\pm0.03\ \mathrm{deg}^{-2}$.
@@
 
-Using the number densities and the probed area of our survey, we calculate the fraction of contamination for both UDG and UPG sample.
-For the UDG sample, there are $f_{\rm contam} \approx 16\%$ contaminants; for the UPG sample, the contamination fraction is $f_{\rm contam} \approx 20\%$.
+Using the number densities and the probed area of our survey, we calculate the contamination fraction for both the UDG and UPG samples.
+For the UDG sample, we find $f_{\rm contam} \approx 16\%$; for the UPG sample, the contamination fraction is $f_{\rm contam} \approx 20\%$.
 We take the contamination fraction into account when calculating the average UDG (UPG) number in Section \ref{sec:results}.
@@
 If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG.
-Indeed, we find that the $g-i$ color distribution of the fake UDG sample is bluer than that of the true UDG sample, which motivates us to assign an importance weights based on $g-i$ color.
+Indeed, we find that the $g-i$ color distribution of the fake UDG sample is bluer than that of the true UDG sample, which motivates us to assign importance weights based on $g-i$ color.
 We first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at $(g-i)_{k}$ bins) for both true UDG and fake UDG samples.
@@
 The weights of UPGs are assigned following the same procedure.
-We find this color-based contamination subtraction scheme is sufficient for this work since the fraction of contamination is small.
-Our main results shown in Section \ref{sec:results} are robust against contamination subtraction.
+We find this color-based contamination subtraction scheme is sufficient for this work since the contamination fraction is small.
+Our main results aren shown in Section \ref{sec:results} are robust against contamination subtraction.
 
@@
 As demonstrated by many previous studies \citep[e.g.,][]{vdBurg2016,vdBurg2017}, the average number of UDGs per host scales with host halo mass.
-While many literature focus on finding UDGs in clusters and large groups, there are less constraints on the UDG abundance at the lower halo mass end.
+While much literature focuses on finding UDGs in clusters and large groups, there are fewer constraints on the UDG abundance at the lower halo mass end.
 In this section, we calculate the UDG abundance of MW analogs, and compare with other surveys.
@@
 We plot the UDG abundances of these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017}.
-Among these studies, only \citet{vdBurg2017} applied background subtraction and completeness correction to the raw counts.
+Among these studies, only \citet{vdBurg2017} applies a background subtraction and completeness correction to the raw counts.
 The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray.
 The UDG abundance of this work is highlighted as the red square.
-As shown in Figure \ref{fig:n_udg}, the scatter of $N_{\rm UDG}-M_h$ relation get larger at the lower halo mass end.
-Our UDG abundance is similar to the value in ELVES survey, but is higher than the prediction from \citet{vdBurg2017} but is still considered consistent within scatter.
-The UDG abundances from SAGA is significantly lower than both ELVES and our result.
-This might be explained by different photometric depth of data used.
+As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo mass end.
+Our UDG abundance is similar to the value in ELVES survey, but is marginally higher than the prediction from \citet{vdBurg2017} although still consistent within the scatter.
+The UDG abundances from SAGA are significantly lower than both ELVES and our result.
+This might be explained by the different photometric depth of data used.
 SAGA selects dwarf candidates in DECaLS data, which is x mag shallower than the CFTH and HSC data used in ELVES and this work.
@@
 
-In the right panel, we split the UDG sample into different bins based on their host halo mass (shown as triangles) and color (shown as pentagons).
-The UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger on host color.
+In the right panel, we split the UDG sample into different bins based on their host halo mass (shown as triangles) and host color (shown as pentagons).
+The UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger with host color.
 
@@
 First of all, we take the fake UDGs in random fields and calculate their size distribution as a proxy for background contamination, shown as the gray dots in the left panel of Figure \ref{fig:size_distribution}.
-For each host, we calculate the raw size distribution of the associated UDGs (black dots), and we multiply background size distribution by the virial area of the host and subtract it from the UDG size distribution (teal dots).
+For each host, we calculate the raw size distribution of the associated UDGs (black dots), and we multiply the background size distribution by the virial area of the host and subtract it from the UDG size distribution (teal dots).
 Then we combine the UDG size distributions for all hosts together, and correct for completeness (red squares).
 Since the stellar masses of the hosts in our sample are quite similar, we do not weight each host according to their masses.
-The error shown in Figure \ref{fig:size_distribution} takes both Poisson error and the measurement error of size into account.
+The error shown in Figure \ref{fig:size_distribution} takes both Poisson error and the measurement error in size into account.
 
@@
 The Einasto profile introduces an extra ``shape'' parameter $\alpha$ and has been argued to be a better description to the dark matter halo profiles \citep[e.g.,][]{Navarro2004,Gao2008,Navarro2010,Dutton2014}.
-Einasto profile also makes concentration estimates less sensitive to the radial range fitted.
+The Einasto profile also makes concentration estimates less sensitive to the radial range fitted.
 The best-fit NFW and Einasto profiles are shown in Figure \ref{fig:radial_distribution} as blue and red lines, respectively.
@@
 
-We derive $V$-band apparent magnitude following $V = g - 0.5784\, (g - r) - 0.0038$\footnote{This relation wass derived for SDSS filters.
+We derive $V$-band apparent magnitude following $V = g - 0.5784\, (g - r) - 0.0038$\footnote{This relation was derived for SDSS filters.
 We neglect the small difference between SDSS and HSC filter systems.
@@
 But for UPGs, it seems that the host color impacts less than the distance to the host on the quenched fraction.
-This result might hint the ``galaxy conformity'', which refers to the fact that late-type hosts tend to have more late-type satellites \citep{Weinmann2006}.
+This result might hint at ``galaxy conformity'', which refers to the fact that late-type hosts tend to have more late-type satellites \citep{Weinmann2006}.
 We also split the samples based on host stellar mass, but do not find a significant difference in quenched fractions.
@@
 However for UDG sample, it only reaches to $M_\star\approx 10^{8.3}\ M_\odot$ because galaxies with higher stellar mass no longer satisfy the surface brightness cut for UDG.
-On the contrary, the UPG definition does not have hard surface brightness cut such that $M_\star > 10^{8.5}\ M_\odot$ galaxy can get into the UPG sample as long as having an extraordinarily large size.
+On the contrary, the UPG definition does not have a hard surface brightness cut such that $M_\star > 10^{8.5}\ M_\odot$ galaxy can get into the UPG sample as long as having an extraordinarily large size.
 As a consequence, background spiral galaxies could dominate the UPG sample at the high-mass end.
@@
 \subsection{High and constant quenched fraction of UDGs is an artifact}
+
 \begin{figure*}
@@
 	}
-    \caption{Caption}
+    \caption{The distributions of the UDG and UPG sample on the mass-size plane.
+The data points are color-coded by the distance to the quenching color cut.
+Squares are those galaxies satisfying both UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
+    We plot the average mass-size relation (light green) and $1.5\sigma$ above the average relation (dark green) as dashed lines for reference.
+In the left panel, we show the constant surface brightness line as solid lines by assuming two different $g-i$ colors.
+Galaxies falling between these two lines are mostly red and quenched because blue UDGs have too be very large in size to satisfy the surface brightness criterion.
+This hard surface brightness cut makes the UDG quenched fraction high.
+    }
     \label{fig:mass_size}
 \end{figure*}
+
+In Section \ref{sec:quench}, we calculate the quenched fraction as a function of stellar mass for UDGs (left panels in Figure \ref{fig:qfrac}).
+We find that the UDG quenched fraction is reasonably a constant over $>1$ dex in stellar mass, and is higher than the quenched fractions of UPGs and satellite population of MW analogs.
+In this subsection, we argue that UDG's high and constant quenched fraction is merely an artifact due to its contrived definition.
+
+In Figure \ref{fig:mass_size}, we plot our UDG sample on the mass-size plane.
+Because we use a color cut $(g-i)_{Q} = -0.067 M_V - 0.23$ to define quenching, we define $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ as an indicator for how much it has been quenched.
+Higher $\Delta(\mathrm{Quench})$ means that the galaxy is actively star-forming, whereas smaller $\Delta(\rm Quench)$ indicates the galaxy has been quenched more.
+The data points in Figure \ref{fig:mass_size} are color-coded by this $\Delta(\mathrm{Quench})$.
+As shown as green dashed lines, we plot the mass-size relation (and $1.5\sigma$ above the mean mass-size relation) derived from the satellite systems of MW analogs in Local Volume \citep{ELVES-I}.
+The two solid lines correspond to the surface brightness cut at $\sbeff = 25.0\ \sbunit$ by assuming different colors.
+For the redshift range of our sample, the surface brightness is a constant with distance since the cosmological effect is negligible.
+
+UDG with a redder color has a higher mass-to-light ratio, thus for a given mass and surface brightness, its size is smaller than a blue UDG.
+Consequently, only those large blue UDGs can satisfy the UDG definition.
+As shown in the left panel of Figure \ref{fig:mass_size}, galaxies between the red and the blue solid lines are mostly quenched ($\Delta(\mathrm{Quench}) < 0$).
+Due to the color-M/L relation, a fixed surface brightness cut makes red galaxies dominate the UDG population at the smaller size end, and thus giving rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}.
+
+The UPGs are defined as those galaxies at $1.5\sigma$ above the average mass-size relation.
+The right panel of Figure \ref{fig:mass_size} shows their distribution on mass-size plane.
+The squares are those galaxies classified as both UDG and UPG, stars are objects that are classified as UDG only, and triangles are UPGs only.
+We see a lot of blue galaxies with large size classified only as UPG because their surface brightness is too high to satisfy the UDG definition.
+
+We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\mu_0(g) > 24.0\ \sbunit$ (or equivalently $\sbeff > 25.0\ \sbunit$).
+
+We advocate that UPGs better represent the large-size tail of the dwarf galaxy population and have a more objective definition.
 

### 2022-08-21 main.tex
Updates from Overleaf

@@
     \item Modeling (Sec. \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
-    \item Completeness and measurement errors (Sec. \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
+    \item Completeness and measurement uncertainties (Sec. \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
 \end{enumerate}
@@
 The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours.
+The completeness drops as we go to fainter surface brightness and smaller size.
 We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-The completeness drops as we go to fainter surface brightness and smaller size.
-
-Compare with vdb17, carlsten22, smudges21/22, tanoglidis21.
-
-Our high completeness demonstrates the power of HSC images on LSBG studies.
-
-\jiaxuan{Also compare our completeness with other surveys.}
+
+% As noted in Paper II, our ability to estimate uncertainties and completeness is limited by the differences between our smooth Sérsic models and real UDGs, some of which may have complex morphologies.
+Nonetheless, they do provide baseline estimates of these parameters, which may be augmented in the future by comparing our results to other surveys using different observational and analytic strategies.
+
+% Bias corrections are applied to our catalog entries before estimating their completeness probabilities.
+
+We compare our completeness with that of other LSBG searches.
+Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more as increasing size.
+\citet{CarlstenELVES2022} use a similar searching algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$.
+\citet{vdBurg2017} searched LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
+\citet{Zaritsky2021} focus on searching LSBGs in SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) survey and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$.
+Their low completeness might be explained by the fact that they remove a large fraction of the sky covered by the Galactic dust.
+\citet{Tanoglidis2021} conducted LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data but did not provide systematic analysis on completeness using mock galaxies.
+They compare their catalog with the deeper observations in the Fornax cluster and conclude an overall completeness of $\sim 40\%$.
+\citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but much smaller completeness above $\sbeff > 26.5\ \sbunit$.
+In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies.
 

### 2022-08-22 main.tex
Updates from Overleaf

@@
 The unprecedented depth and careful sky subtraction make PDR2 an ideal data set to study low surface brightness galaxies.
+In this work we use the PSF models generated by \code{hscPipe}.
 
@@
 \subsubsection{Completeness}\label{sec:completeness}
-%Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands. 
+
 A real LSBG can be missed in the detection step (Sec.
@@
 \ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
+We split the size and surface brightness range into 15 bins with $\Delta r_e = 0.86\arcsec$, $\Delta \sbeff = 0.33\ \sbunit$, and interpolate over bins using an isotropic Gaussian kernel with $\sigma = 0.5$.
+We notice that the size and surface brightness shown in Figure \ref{fig:completeness} are all the intrinsic values for the mock galaxies, which are different from the measured ones.
+We discuss measurement biases in Section \ref{sec:meas_unc}.
 
@@
 We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-
-% As noted in Paper II, our ability to estimate uncertainties and completeness is limited by the differences between our smooth Sérsic models and real UDGs, some of which may have complex morphologies.
-Nonetheless, they do provide baseline estimates of these parameters, which may be augmented in the future by comparing our results to other surveys using different observational and analytic strategies.
-
-% Bias corrections are applied to our catalog entries before estimating their completeness probabilities.
+Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness.
+In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).
 
@@
 Their low completeness might be explained by the fact that they remove a large fraction of the sky covered by the Galactic dust.
-\citet{Tanoglidis2021} conducted LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data but did not provide systematic analysis on completeness using mock galaxies.
-They compare their catalog with the deeper observations in the Fornax cluster and conclude an overall completeness of $\sim 40\%$.
+\citet{Tanoglidis2021} conducted LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
 \citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but much smaller completeness above $\sbeff > 26.5\ \sbunit$.
@@
 
-\subsubsection{Measurement uncertainty}\label{sec:meas_unc}
-% , which is common in the low surface brightness regime (see e.g. \citealt{Haussler2007,Zaritsky2021}). Galfit also have very strong bias.
-
-We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}.
-Overall, the measurement agrees with the truth quite well.
-However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27\ \sbunit$ are systematically under-estimated.
-We also characterize the bias and the scatter in the measurement as a function of size and surface brightness.
-We apply the bias correction to the LSBG measurement, and incorporate the measurement error into the science figures.
-
-\citet{Tanoglidis2022ICML} estimates the measurement error using a Bayesian Neural net.
-
-In order to test how well we recover the photometric and structural parameters in the modeling step (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
-We compare the fitting results with the ground truth in Figure \ref{fig:meas_bias}, where $\Delta(X) = X(\rm truth) - X(\rm measured)$, and x-axis corresponds to the truth values.
-We find that the measured half-light radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and apparent size.
+\subsubsection{Measurement bias and uncertainty}\label{sec:meas_unc}
+
+Due to the low surface brightness nature of LSBGs, their size, magnitude, surface brightness and shape are hard to characterize and are typically associated with large uncertainties.
+\citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects.
+In the low surface brightness regime, the measured size and total magnitude can be quite biased and have large uncertainties.
+Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs.
+\citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth.
+\citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network.
+In this paper, we simply take the former method because of its simplicity.
+
+In order to test how well we recover the photometric and structural parameters in the our measurement (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
+We compare the fitting results with the ground truth, and we find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
 For surface brightness fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
-As a result, the apparent magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truth.
-
-To correct for this bias in size, surface brightness, apparent magnitude, and color, we assume that the bias only depends on the size and surface brightness.
-Indeed, we do not find any significant dependence of the bias on color, ellpticity, and Spergel index.
+As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truths.
+
+Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shapes.
+However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index.
+Thus we just model the bias and uncertainty as a function of angular size $r_e$ and surface brightness $\sbeff$.
+
 We split the $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias within each bin.
@@
 
+Overall, the measurement agrees with the truth quite well.
+However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27\ \sbunit$ are systematically under-estimated.
+We also characterize the bias and the scatter in the measurement as a function of size and surface brightness.
+We apply the bias correction to the LSBG measurement, and incorporate the measurement error into the science figures.
+
+Unlike \citet{Zaritsky2021}, since we only work on a 2-D plane, we find interpolation working well enough and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
+
+We remind the readers that the values presented in our catalog are already bias-corrected. But we do provide the bias values for reference.
+
+% Bias corrections are applied to our catalog entries before estimating their completeness probabilities.
+
 %All satellite photometry is in the AB system and cor- rected for MW dust extinction using the E(B − V ) maps of Schlegel et al.
@@
 
-\jiaxuan{Remember to ref SMUDGES papers here. Maybe compare our method with SMUDGES, Tanoglidis, etc.}
+say somewhere in the results section that only SMUDGES measured and corrected measurement bias.
 

### 2022-08-22 main.tex
Updates from Overleaf

@@
 A larger UDG sample, especially in low-density environments, is needed to test these hypotheses.
+
+Distance information of LSBGs is hard to know \citep{Kadowaki2021,Greene2022,Zaritsky2022} (also another cross-correlation paper recently?). Thus we turn to match with MW analogs.
+
+explain those acronyms (SAGA, ELVES)
 
@@
 
+\textbf{
+Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives. }
+\jiaxuan{Check if this is considered in the completeness.}
+
 \subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}
@@
 \subsubsection{Completeness}\label{sec:completeness}
+\begin{figure*}
+	\vbox{ 
+		%\vskip -10mm
+		\centering
+		\includegraphics[width=1\linewidth]{completeness.pdf}
+	}
+	\caption{The completeness of our LSBG search as a function of effective radius $r_e$ and the average surface brightness $\sbeff$.
+We characterize the completeness by injecting mock \sersic{} galaxies into coadd images.
+The overall completeness (right panel) comprises the detection completeness (left panel, see Sec.
+\ref{sec:detection}) and deblending completeness (middle panel, see Sec.
+\ref{sec:deblending}) where false positives are removed.
+The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours.
+The completeness drops for smaller sizes and faint surface brightness.
+We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
+The completeness drops as we go to fainter surface brightness and smaller size.
+	%The mock galaxies span a large range in size, surface brightness, \sersic{} index, color, and ellipticity. 
+	}
+	\label{fig:completeness}
+\end{figure*}
 
@@
 
-\begin{figure*}
-	\vbox{ 
-		%\vskip -10mm
-		\centering
-		\includegraphics[width=1\linewidth]{completeness.pdf}
-	}
-	\caption{The completeness of our LSBG search as a function of effective radius $r_e$ and the average surface brightness $\sbeff$.
-We characterize the completeness by injecting mock \sersic{} galaxies into coadd images.
-The overall completeness (right panel) comprises the detection completeness (left panel, see Sec.
-\ref{sec:detection}) and deblending completeness (middle panel, see Sec.
-\ref{sec:deblending}) where false positives are removed.
-The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours.
-The completeness drops for smaller sizes and faint surface brightness.
-We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-The completeness drops as we go to fainter surface brightness and smaller size.
-	%The mock galaxies span a large range in size, surface brightness, \sersic{} index, color, and ellipticity. 
-	}
-	\label{fig:completeness}
-\end{figure*}
-
 \subsubsection{Measurement bias and uncertainty}\label{sec:meas_unc}
@@
 However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index.
-Thus we just model the bias and uncertainty as a function of angular size $r_e$ and surface brightness $\sbeff$.
-
-We split the $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias within each bin.
-Then we interpolate over the grid using a multiquadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
-Figure \ref{fig:meas_err} shows the interpolated bias terms as a function of the measured size and surface brightness.
-For half-light radius, we take $(r_{e, \rm t} - r_{e, \rm m}) / r_{e,\rm m}$ as the bias term; for surface brightness, we take $\overline{\mu}_{\rm eff, t}(g) - \overline{\mu}_{\rm eff, m}(g)$ as the bias term.
-As shown in Figure \ref{fig:meas_err}, the size and surface brightness bias grows with increasing surface brightness.
-The bias has a peak at $r_e\sim 6\arcsec$ because the $r_e$ shown in the figure is the measured size, not the true size.
+Thus we just model the bias and uncertainty as a function of the \textit{measured} angular size $r_e$ and surface brightness $\sbeff$.
+
+Given the size and surface brightness of our simulated galaxies, we set the ranges of the observed size and surface brightness to be $r_e\in[1\arcsec, 15\arcsec],\ \sbeff\in[23, 29]$.
+We then split the observed $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias $\Delta X = X_{\rm truth} - X_{\rm meas}$ within each bin, where $X=\{\sbeff,\ g-i,\ g-r\}$.
+For $r_e$, we calculate the relative bias $\Delta r_e / r_e$ instead because it is less dependent on the angular size.
+Then we interpolate over the grid using a multi-quadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
+Unlike \citet{Zaritsky2021} where they fit models in 4-D space, we find interpolation working well enough in the 2-D space and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
+We emphasize that the bias and uncertainty are modeled to be functions of the measured properties, not intrinsic ones, such that we can correct for bias based on our measurements.
+
+In Figure \ref{fig:meas_err}, the colors show the interpolated bias terms as a function of the measured size and surface brightness.
+The size and surface brightness bias grows with increasing surface brightness.
+The bias term is not a monotonic function of size because the size here is not intrinsic size.
 It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
-We also find that the bias in $g-i$ color is quite small.
+We also find the bias in $g-i$ color quite small.
 
@@
 We first correct for the bias in size, $g$-band average surface brightness, $g-r$ and $g-i$ colors.
-Then we calculate the $g$-band apparent magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$.
+Then we calculate the $g$-band total magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$.
 The magnitudes and surface brightnesses in other bands are derived using $g$-band magnitude, surface brightness, and colors.
-In this way, we apply a self-consistent correction for the measurement bias to the data.
-
-It is also important to characterize the measurement uncertainty.
-The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, contamination effects, etc.
-Unlike other parametric modeling codes such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimal solution.
-Thus we cannot get a statistical error on the measured properties from \code{scarlet}.
-However, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor.
-Following the same method as that of calculating the bias, in each bin we compute the standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid.
-The measurement errors are shown in Figure \ref{fig:meas_err} as contours.
-
-Overall, the measurement agrees with the truth quite well.
-However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27\ \sbunit$ are systematically under-estimated.
-We also characterize the bias and the scatter in the measurement as a function of size and surface brightness.
-We apply the bias correction to the LSBG measurement, and incorporate the measurement error into the science figures.
-
-Unlike \citet{Zaritsky2021}, since we only work on a 2-D plane, we find interpolation working well enough and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
-
-We remind the readers that the values presented in our catalog are already bias-corrected. But we do provide the bias values for reference.
-
-% Bias corrections are applied to our catalog entries before estimating their completeness probabilities.
+In this way, we apply a self-consistent correction for the measurement biases to the data.
+
+The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, neighboring contamination, etc.
+Unlike other parametric modeling codes, \code{scarlet} does not explore the full posterior space but rather finds one optimal solution.
+Thus we have no access to the statistical error on the measured properties from \code{scarlet}.
+Fortunately, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor.
+Following the same method as that of calculating the bias, in each bin we compute the $1\sigma$ standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid.
+The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the biases.
+We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
+
+In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on bias-corrected properties.
+We also incorporate the measurement errors into the science figures.
+The values presented in our catalogs are already bias-corrected, but we do provide the bias values for reference.
 
@@
 We take the solar g-band magni- tude to be Mg⊙ = 5.03 mag (Willmer 2018).
-
-TBD: re-think the way of computing the error, especially for $r_e$.
-
-vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$, when deriving the completeness (recovered fraction)
-
-say somewhere in the results section that only SMUDGES measured and corrected measurement bias.
-
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{meas_bias.pdf}
-	}
-    \caption{Caption}
-    \label{fig:meas_bias}
-\end{figure*}
+% say somewhere in the results section that only SMUDGES measured and corrected measurement bias. vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$
+
+% \begin{figure*}
+% 	\vbox{ 
+% 		\centering
+% 		\includegraphics[width=1\linewidth]{meas_bias.pdf}
+% 	}
+%     \caption{Caption}
+%     \label{fig:meas_bias}
+% \end{figure*}
 
@@
 	}
-    \caption{Caption}
+    \caption{The measurement bias and uncertainty as a function of measured angular size $r_e$ and surface brightness $\sbeff$.
+The colors show the bias term while the dashed contours show the constant uncertainty lines.
+We derive the bias of total magnitudes from the biases of $r_e$, $\sbeff$, and colors consistently.
+We find that the bias and uncertainty of our measurement increase toward the fainter end.
+We apply the bias correction to the real LSBGs before studying their physical properties.}
     \label{fig:meas_err}
@@
 
-Distance information of LSBGs is hard to know \citep{Kadowaki2021,Greene2022,Zaritsky2022} (also another cross-correlation paper recently?)
-
 The goal of this paper is to study the UDG population hosted by MW-like galaxies.
-However, the properties of the MW itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among groups.
+However, the properties of the MW itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among different studies.
 In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig 2 of \citealt{SAGA-I}).
 This luminosity range approximately corresponds to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$.
-They also require the MW analogs to be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20-40 Mpc).
+They also require the MW analogs to be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20--40 Mpc).
 In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$~mag ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA.
-We choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($\sim 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
-MW analogs selected using this definition are very close to those in SAGA but are slightly more massive than the ELVES hosts.
+In this work, we choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($\sim 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
+MW analogs selected using this definition are very close to those in SAGA but are slightly less massive than the ELVES hosts since ELVES has several groups more massive than SAGA.
 
 Since UDGs are relatively scarce in MW-like hosts \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics.
-However, UDGs will be too small and faint to be detected in HSC images beyond a certain distance.
+However, UDGs will be too small and too faint to be detected in HSC images beyond a certain distance.
 We choose our redshift range to be $0.01 < z < 0.04$, which makes sure that we can detect a significant number of faint dwarf galaxies around MW-like hosts.
-We exclude galaxies $z<0.01$ because 1) the number is very small; 2) their large angular size makes they may be shredded in the deblending step, so that including them will introduce a number of spurious LSB objects.
+We exclude galaxies $z<0.01$ because 1) the number of UDGs will be very small due to the small volume; 2) their large angular size makes them more probable to be shredded in the deblending step, so including them will introduce a number of spurious LSB objects.
 Our MW analogs sample complements the ELVES sample and SAGA sample in our redshift range.
@@
 After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left.
-Then we match them to the LSBG catalog (described in Section \ref{sec:detection}) as follows.
-For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}.
-It turns out that 40\% of hosts have virial radii larger than 300 kpc.
+Then we match them to the initial LSBG sample (described in Section \ref{sec:detection}, before the deblending step) as follows.
+For a given MW analog, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}.
+It turns out that 40\% of hosts have virial radii larger than 300 kpc, which is commonly used as the virial radius of MW.
 Then we identify any LSBG that falls into the projected angular virial radius of the host.
@@
 Finally, we have 901 MW-like hosts and 10,579 LSBG candidates associated with them.
-However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shredded large galaxies, compact sources in galaxy outskirts, etc.
+However, there are still a significant fraction of spurious objects in this cross-matched LSBG sample, including galactic cirri, tidal tails/streams, shredded large galaxies, compact sources blended with galaxy outskirts, etc.
 As introduced in Section \ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects.
 There are 2,673 objects left after the deblending cuts.
-Next, we model them using the Spergel profile as described in Section \ref{sec:modeling}.
+Next, we model them using the Spergel profile as described in Section \ref{sec:modeling} and obtain their properties from the fitting results.
 Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives.
 We also remove duplicated objects.
-In the end, we have 2510 LSBG candidates as our final LSBG sample, from which we construct the ultra-diffuse galaxy (UDG) sample and the ultra-puffy galaxy (UPG) samples as follows.
+In the end, we have 2,510 LSBG candidates as our final LSBG sample, from which we construct the ultra-diffuse galaxy (UDG) sample and the ultra-puffy galaxy (UPG) samples as follows.
 
@@
 The measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020} or other contaminants.
-Therefore in this work, we use the average surface brightness within an effective radius $\sbeff$ to define UDG.
+Therefore in this work, we use the average surface brightness within effective radius $\sbeff$ to define UDG.
 The difference between the average surface brightness and the central surface brightness for a \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
@@
 Taking the measured mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the mass-size relation.
-The UPGs are not necessarily large in physical size or faint in average surface brightness {\bf JEG: but they are size outliers for their mass}.
+The UPGs are not necessarily large in physical size or faint in average surface brightness, but they are outliers in size for their masses.
 Both UDG and UPG represent subsets of dwarf galaxies that are larger and more diffuse than average.
@@
 The error shown in Figure \ref{fig:size_distribution} takes both Poisson error and the measurement error in size into account.
+
+\jiaxuan{vdb17 doesn't estimate measurement bias.}
 

### 2022-08-24 main.tex
scratch my head on writing discussion

@@
 Before we can answer this question, it is important to reliably determine in what environment they live.
+
 Past UDG studies focused on rich galaxy groups and clusters \citep[e.g.,][]{Yagi2016,Zaritsky2019}, which provides distance information.
@@
 With a sample of UDGs around MW-like hosts, we can compare the structural parameters, quenched fractions, nucleation fractions, and radial distributions with normal satellites in the nearby universe \citep[e.g.,][]{SAGA-II,CarlstenELVES2022}, to shed light on questions about the formation and evolution of the UDGs.
+
+Also compare with LCDM-based hydro sims. Study the quenching along the direction perpendicular to the mass-size.
+
+While satellite galaxies in the fields are star-forming \citet{Geha2012}.
 
@@
 In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies.
+\jiaxuan{also cite dragonfly}
 
 \subsubsection{Measurement bias and uncertainty}\label{sec:meas_unc}
-
-Due to the low surface brightness nature of LSBGs, their size, magnitude, surface brightness and shape are hard to characterize and are typically associated with large uncertainties.
-\citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects.
-In the low surface brightness regime, the measured size and total magnitude can be quite biased and have large uncertainties.
-Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs.
-\citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth.
-\citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network.
-In this paper, we simply take the former method because of its simplicity.
-
-In order to test how well we recover the photometric and structural parameters in the our measurement (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
-We compare the fitting results with the ground truth, and we find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
-For surface brightness fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
-As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truths.
-
-Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shapes.
-However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index.
-Thus we just model the bias and uncertainty as a function of the \textit{measured} angular size $r_e$ and surface brightness $\sbeff$.
-
-Given the size and surface brightness of our simulated galaxies, we set the ranges of the observed size and surface brightness to be $r_e\in[1\arcsec, 15\arcsec],\ \sbeff\in[23, 29]$.
-We then split the observed $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias $\Delta X = X_{\rm truth} - X_{\rm meas}$ within each bin, where $X=\{\sbeff,\ g-i,\ g-r\}$.
-For $r_e$, we calculate the relative bias $\Delta r_e / r_e$ instead because it is less dependent on the angular size.
-Then we interpolate over the grid using a multi-quadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
-Unlike \citet{Zaritsky2021} where they fit models in 4-D space, we find interpolation working well enough in the 2-D space and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
-We emphasize that the bias and uncertainty are modeled to be functions of the measured properties, not intrinsic ones, such that we can correct for bias based on our measurements.
-
-In Figure \ref{fig:meas_err}, the colors show the interpolated bias terms as a function of the measured size and surface brightness.
-The size and surface brightness bias grows with increasing surface brightness.
-The bias term is not a monotonic function of size because the size here is not intrinsic size.
-It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
-We also find the bias in $g-i$ color quite small.
-
-For LSBGs in our sample, we apply corrections for the bias using the interpolated bias terms.
-We first correct for the bias in size, $g$-band average surface brightness, $g-r$ and $g-i$ colors.
-Then we calculate the $g$-band total magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$.
-The magnitudes and surface brightnesses in other bands are derived using $g$-band magnitude, surface brightness, and colors.
-In this way, we apply a self-consistent correction for the measurement biases to the data.
-
-The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, neighboring contamination, etc.
-Unlike other parametric modeling codes, \code{scarlet} does not explore the full posterior space but rather finds one optimal solution.
-Thus we have no access to the statistical error on the measured properties from \code{scarlet}.
-Fortunately, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor.
-Following the same method as that of calculating the bias, in each bin we compute the $1\sigma$ standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid.
-The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the biases.
-We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
-
-In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on bias-corrected properties.
-We also incorporate the measurement errors into the science figures.
-The values presented in our catalogs are already bias-corrected, but we do provide the bias values for reference.
-
-%All satellite photometry is in the AB system and cor- rected for MW dust extinction using the E(B − V ) maps of Schlegel et al.
-(1998) recalibrated by Schlafly & Finkbeiner (2011).
-We take the solar g-band magni- tude to be Mg⊙ = 5.03 mag (Willmer 2018).
-% say somewhere in the results section that only SMUDGES measured and corrected measurement bias. vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$
 
@@
 \end{figure*}
+
+Due to the low surface brightness nature of LSBGs, their size, magnitude, surface brightness and shape are hard to characterize and are typically associated with large uncertainties.
+\citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects.
+In the low surface brightness regime, the measured size and total magnitude can be quite biased and have large uncertainties.
+Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs.
+\citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth.
+\citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network.
+In this paper, we simply take the former method because of its simplicity.
+
+In order to test how well we recover the photometric and structural parameters in the our measurement (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
+We compare the fitting results with the ground truth, and we find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
+For surface brightness fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
+As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truths.
+
+Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shapes.
+However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index.
+Thus we just model the bias and uncertainty as a function of the \textit{measured} angular size $r_e$ and surface brightness $\sbeff$.
+
+Given the size and surface brightness of our simulated galaxies, we set the ranges of the observed size and surface brightness to be $r_e\in[1\arcsec, 15\arcsec],\ \sbeff\in[23, 29]$.
+We then split the observed $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias $\Delta X = X_{\rm truth} - X_{\rm meas}$ within each bin, where $X=\{\sbeff,\ g-i,\ g-r\}$.
+For $r_e$, we calculate the relative bias $\Delta r_e / r_e$ instead because it is less dependent on the angular size.
+Then we interpolate over the grid using a multi-quadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
+Unlike \citet{Zaritsky2021} where they fit models in 4-D space, we find interpolation working well enough in the 2-D space and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
+We emphasize that the bias and uncertainty are modeled to be functions of the measured properties, not intrinsic ones, such that we can correct for bias based on our measurements.
+
+In Figure \ref{fig:meas_err}, the colors show the interpolated bias terms as a function of the measured size and surface brightness.
+The size and surface brightness bias grows with increasing surface brightness.
+The bias term is not a monotonic function of size because the size here is not intrinsic size.
+It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
+We also find the bias in $g-i$ color quite small.
+
+For LSBGs in our sample, we apply corrections for the bias using the interpolated bias terms.
+We first correct for the bias in size, $g$-band average surface brightness, $g-r$ and $g-i$ colors.
+Then we calculate the $g$-band total magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$.
+The magnitudes and surface brightnesses in other bands are derived using $g$-band magnitude, surface brightness, and colors.
+In this way, we apply a self-consistent correction for the measurement biases to the data.
+
+The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, neighboring contamination, etc.
+Unlike other parametric modeling codes, \code{scarlet} does not explore the full posterior space but rather finds one optimal solution.
+Thus we have no access to the statistical error on the measured properties from \code{scarlet}.
+Fortunately, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor.
+Following the same method as that of calculating the bias, in each bin we compute the $1\sigma$ standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid.
+The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the biases.
+We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
+
+In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on bias-corrected properties.
+We also incorporate the measurement errors into the science figures.
+The values presented in our catalogs are already bias-corrected, but we do provide the bias values for reference.
+
+%All satellite photometry is in the AB system and cor- rected for MW dust extinction using the E(B − V ) maps of Schlegel et al.
+(1998) recalibrated by Schlafly & Finkbeiner (2011).
+We take the solar g-band magni- tude to be Mg⊙ = 5.03 mag (Willmer 2018).
+% say somewhere in the results section that only SMUDGES measured and corrected measurement bias. vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$
 
@@
 In this section, we present statistical analysis of UDGs and UPGs associated with MW analogs in the nearby Universe. TLDR the full section here?
+
+\subsection{UDG and UPG on mass-size plane}
 
@@
 
+\citet{Liao2019} also shows a shallower power law with 0.93. We can add that paper here.
+
+\jiaxuan{UPG abundances, and compare with UDGs}
+
+quenched line: Meng's manga paper. color-mass.
+
 % Plot the UDG and UPG population on the re-abs mag plane (Bovy book)
@@
 \subsection{Size distribution}\label{sec:size_distr}
+\jiaxuan{Plot size distribution in two radial bins, to test whether tidal stripping prevails ram pressure stripping. }
 \begin{figure*}
@@
 We refer to quenching as the cessation of star formation in galaxies.
-In principle, direct estimates for the instantaneous star formation rate (SFR) from UV or H$\alpha$ are needed to define a quenched galaxy  population.
+In principle, direct estimates for the instantaneous star formation rate (SFR) from UV or H$\alpha$ or estimations for the \ion{H}{1} gas are needed to define a quenched galaxy  population.
 As an example, the SAGA survey measures the H$\alpha$ equivalent width (EW) from spectra to define quenched satellites.
+There are also many studies probing \ion{H}{1} masses for MW and M31 satellites \citep[e.g.,][]{Grcevich2009,Spekkens2014,Putman2021}.
 However, these specific data sets are either not deep enough to probe our UDGs and UPGs, or they are very expensive to obtain and cover all the footprint of our sample.
@@
 Furthermore, \citet{Font2022} showed in simulations that this color cut effectively separates star forming galaxies from quenched ones.
+This makes the color cut more promising since their simulations are not fine tuned to match the observed properties of dwarfs.
 Since we do not visually inspect all UDGs and UPGs in our sample, we take the color cut from \citet{CarlstenELVES2022} to define our quenched galaxies: galaxies that are redder than $g-i > -0.067 M_V - 0.23$ are defined as quenched, whereas those bluer galaxies are thought to be star-forming.
-However, one caveat is that this criterion was derived from LV satellites in \citet{CarlstenELVES2022}, and the bulk of them are brighter than our UDGs and UPGs.
+However, one caveat is that this criterion was derived from LV satellites in \citet{CarlstenELVES2022} and the bulk of them have higher surface brightness and less extended than our UDGs and UPGs.
 It is not guaranteed that the same color cut would work in our regime.
@@
 We also overlie the quenched fraction from ARTEMIS \citep[purple lines,][]{Font2022} and FIRE-2 \citep[pink dotted lines][]{Samuel2022} simulations, where the quenched galaxies are defined as those with no instantaneous (for ARTEMIS) or recent ($<200$ Myr for FIRE-2) star formation.\footnote{\citet{Font2022} find a similar quenched fraction when using the same color cut as we do.} We select ARTEMIS and FIRE-2 because they roughly cover the highest and lowest quenched fraction produced in simulations (see Fig.
-13 in \citep{Samuel2022}).
+13 in \citealt{Samuel2022}).
 Compared with these results, we see that UDGs have a higher quenched fraction which does not drop as increasing stellar mass.
@@
 As a consequence, background spiral galaxies could dominate the UPG sample at the high-mass end.
+
+% lower-mass satellites are mostly quiescent, roughly half of intermediate-mass satellites are quiescent, and higher-mass satellites are mostly star-forming
 
@@
 
-We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\mu_0(g) > 24.0\ \sbunit$ (or equivalently $\sbeff > 25.0\ \sbunit$).
+% We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\mu_0(g) > 24.0\ \sbunit$ (or equivalently $\sbeff > 25.0\ \sbunit$).
 
@@
 Among others, tidal stripping and ram-pressure stripping are thought to quench the satellites.
-
-In this section we show the quenched fraction of UDG/UPGs without discussing too much about the physical implication on both UDG population and the general quenching-mass-size relation.
 
@@
 
-\citep{Baxter2021}
-
-\citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.
-\citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.
+% \citep{Baxter2021}: machine learning derived quenched fraction
+
+% \citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.
+
+% \citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.
 
@@
 \subsection{UDG formation}
+Questions:
+1. How are MW satellites quenched? 
+2. How are UDG puffed up?
+
+Answer the two questions, then combine the answers together to form a story
+
+We need an outline of discussion
+
+%%%%%%%%%%%%%%%%%%%
+% 如果upg也是一边quench一边变大，那么为什么upg变得那么大？是不是某种机制能让tidal stripping/heating对于upg非常强？
+
+Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are mostly quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,CarlstenELVES2022}.
+This difference hints that environmental effects play an important role on regulating the star formation activities in dwarf galaxies.
+There have been extensive works using simulations to study the quenching of satellites in MW analogs \citep[e.g.,][]{Simpson2018,Buck2019,Garrison-Kimmel2019,Simons2020,Joshi2021,Akins2021,Karunakaran2021,Font2022,Samuel2022}, and many of the simulations are able to reproduce the observed quenched fraction in the Local Group and in the Local Volume: the satellites in MW analogs are mostly quiescent below $M_\star\approx 10^7\ M_\odot$, and the quenched fraction decreases as increasing stellar mass.
+
+In theory, satellite galaxies in MW analogs are accreted from the field, therefore quenching can happen either prior to the infall or after the infall to MW host.
+For the former case, isolated dwarf galaxies can be quenched by bursty stellar feedback \citep[e.g.,][]{Bahe2015,Kazantzidis2017,ElBadry2018}, reionization \citep[e.g.,][]{Bullock2000,Benson2002,Somerville2002,Tollerud2018,Applebaum2021}, or being backsplash satellites \citep{Simpson2018}.
+If a satellite is still star-forming before infall, then the ram pressure \citep[e.g.,][]{GunnGott1972,McCarthy2008,Simpson2018,Tremmel2020,Samuel2022} experienced by the satellite as it move through the hot circumgalactic medium (CGM) of the host could remove the gas and cause the cessation of star formation.
+Ram pressure stripping can
+efficiently quench galaxies at $M_\star < 10^{8}\ M_\odot$ \citep{Fillingham2016,Simpson2018,Buck2019}, but the quenching depends on the CGM mass and distribution, the orbits of satellites, etc.
+Another quenching mechanism is the so-called preprocessing in a lower-mass group prior to the infall into a MW analog \citep{Wetzel2015b,Jahn2022,Samuel2022}.
+Satellites might be quenched in the previous group via ram pressure striping or tidal interactions.
+Preprocessing can augment the environmental quenching.
+Some studies show that the paired host environments might regulate the quenching of satellites (\citealt{Garrison-Kimmel2019,Putman2021}, but also see \citealt{Samuel2022}).
+Tidal stripping can also deprive the gas from the satellite or stop the gas accretion and starve the galaxy \citep{Simpson2018}.
+%Combining all these factors together, returning backsplash galaxies can also exhibit as other satellites.
+
+\citet{Simpson2018} show in Auriga simulations that the quenched fraction of satellites $M_\star < 10^8\ M_\odot$ have a strong dependence on the distance to the hosts.
+Using the FIRE-2 simulation, \citet{Samuel2022} also show that the quenched fraction increase as the distance to the host decreases, and hosts with higher CGM mass have more quenched satellites.
+In Figure \ref{fig:qfrac}, by comparing UDGs and UPGs at two radial bins, we find the very similar trends that UDGs (UPGs) closer to the host are more quiescent.
+In the ram pressure stripping picture, this is because the density of CGM increases when being closer to the host and the ram pressure is stronger.
+Our observation supports that UDGs and UPGs are mainly quenched by ram pressure stripping.
+
+\citet{Samuel2022} show that 40\% of satellites were in another group prior to the infall to MW, and preprocessed satellites have higher quenched fraction, and 10\% were quenched during preprocessing.
+
+Many mechanisms are also proposed to explain the large size of UDGs in simulation.
+For isolated UDGs, burst stellar feedback can cause the stellar component of dwarf galaxy to expand \citep[e.g.,][]{DiCintio2017,Chan2018,Martin2019,Jiang2019}.
+Analytical models also support a scenario where UDGs originates from a population of dwarf galaxies with higher spin than normal dwarfs \citep{Amorisco2016,Rong2017,Liao2019}.
+For UDGs in groups and clusters, environmental effects are more pronounced and tidal interactions are believed to puff up normal dwarfs to become UDGs.
+\citet{Jiang2019} argue that normal dwarfs can be tidally heated near the orbital pericenter,
+
+\citet{Jiang2019} find that the average color is redder when it's closer to the host, and no size gradient as a function of distance, also attributing that ram-pressure stripping quenches the UDGs in groups, rather than tidal stripping.
+
+\citet{Tremmel2020} study UDG formation in cluster environment and find UDGs with higher mass are puffed up suddenly due to tidal heating at pericenter, UDGs with lower mass are gradually puffed up due to adiabatic expansion as a response to the mass loss (DM + gas + star) from tidal stripipng and ram pressures stripping.
+
+% Jiang: If tidal stripping is more important, the tidal force that strips the cold gas can also remove the stars from the outskirts of the satellite, reducing its r1/2 and M⋆.
+Since the tidal field is stronger in the inner part of a group, an inevitable side effect, if tidal stripping is the dominant quenching mechanism, is that the UDGs closer to the cluster centre would have lower M⋆ and r1/2 than the UDGs on the outskirts or in the field.
+
+% We don't discriminate our hosts to be paired or not.
+
+% Ram pressure within a MW-mass halo should be sufficient to quench most satellites with $M_\star < 10^8\ M_\odot$, as long as the host CGM is suf- ficiently clumpy (Fillingham et al. 2016).
+
+% \citet{Samuel2022} find that HI gas can form a concentrated core after ram-pressure stripping and be there for quite long.
+\citet{Font2022} find LSB galaxies in FIRE-2 have concentrated stellar core.
+Oh, but the core might not be dense enough to form stars.
+
+% The MW simulations we use from the FIRE-2 simulations do not include any form of AGN feedback, but we note that this feedback channel does not seem to be necessary to reproduce the quiescent fraction of observed LG and SAGA survey satellite galaxies.
+
+discuss splashback
+
+quenching and puffing are decoupled.
+
+No splashback
+
 Discuss how does quenching and pufffing interplay.
@@
 
-discuss pros and cons of UDG and UPG (you have to assume a distance to define UPG).
+UDGs are HI enhanced \citep{Wright2021,Kado-Fong2021}
 
@@
 
-Why red is equivalent to quenched? Need to clarify in the paper
-
 calculate probability of being a backsplash satellite (e.g., splashed to 1.5 Mpc)
@@
 
+Host-to-host variation
+
 Don't forget to discuss \citep{xSAGA-I}
@@
 \subsection{A better definition for diffuse galaxies}
+
+From \citet{Wright2021}, We can take this into our paper: At high mass (M⋆ > 108 M⊙), most galaxies have reff > 1.5 kpc.
+UDGs are therefore those galaxies that are unusually LSB.
+At low mass (M⋆ < 107.5 M⊙), most galaxies have μ0,g > 24 mag arcsec−2.
+UDGs are therefore those galaxies that have unusually large effective radii.
+It is only really at intermediate masses that both the central surface brightness and the effective radius criteria are relevant.
+
+discuss pros and cons of UDG and UPG (you have to assume a distance to define UPG).
 

### 2022-08-25 main.tex
Updates from Overleaf

@@
 
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
+	}
+    \caption{The distributions of the UDG and UPG sample on the mass-size plane.
+The data points are color-coded by the distance to the quenching color cut.
+Squares are those galaxies satisfying both UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
+    We plot the average mass-size relation (light green) and $1.5\sigma$ above the average relation (dark green) as dashed lines for reference.
+In the left panel, we show the constant surface brightness line as solid lines by assuming two different $g-i$ colors.
+Galaxies falling between these two lines are mostly red and quenched because blue UDGs have too be very large in size to satisfy the surface brightness criterion.
+This hard surface brightness cut makes the UDG quenched fraction high.
+    }
+    \label{fig:mass_size}
+\end{figure*}
+
 \subsection{Abundance of UDGs and UPGs}\label{sec:n_udg}
-
+\jiaxuan{Discuss NGVS}
 \begin{figure*}
@@
 
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
-	}
-    \caption{The distributions of the UDG and UPG sample on the mass-size plane.
-The data points are color-coded by the distance to the quenching color cut.
-Squares are those galaxies satisfying both UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
-    We plot the average mass-size relation (light green) and $1.5\sigma$ above the average relation (dark green) as dashed lines for reference.
-In the left panel, we show the constant surface brightness line as solid lines by assuming two different $g-i$ colors.
-Galaxies falling between these two lines are mostly red and quenched because blue UDGs have too be very large in size to satisfy the surface brightness criterion.
-This hard surface brightness cut makes the UDG quenched fraction high.
-    }
-    \label{fig:mass_size}
-\end{figure*}
-
 In Section \ref{sec:quench}, we calculate the quenched fraction as a function of stellar mass for UDGs (left panels in Figure \ref{fig:qfrac}).
@@
 
+% How are UDGs puffed up?
 Many mechanisms are also proposed to explain the large size of UDGs in simulation.
 For isolated UDGs, burst stellar feedback can cause the stellar component of dwarf galaxy to expand \citep[e.g.,][]{DiCintio2017,Chan2018,Martin2019,Jiang2019}.
-Analytical models also support a scenario where UDGs originates from a population of dwarf galaxies with higher spin than normal dwarfs \citep{Amorisco2016,Rong2017,Liao2019}.
+Analytical models also support a scenario where UDGs originates from a population of dwarf galaxies with higher spin than normal dwarfs \citep{Dalcanton1997,Amorisco2016,Rong2017,Liao2019}.
+\citet{Wright2021} show that field UDGs can also be formed from major mergers that cause star formation to
+migrate outward.
 For UDGs in groups and clusters, environmental effects are more pronounced and tidal interactions are believed to puff up normal dwarfs to become UDGs.
-\citet{Jiang2019} argue that normal dwarfs can be tidally heated near the orbital pericenter,
-
-\citet{Jiang2019} find that the average color is redder when it's closer to the host, and no size gradient as a function of distance, also attributing that ram-pressure stripping quenches the UDGs in groups, rather than tidal stripping.
-
-\citet{Tremmel2020} study UDG formation in cluster environment and find UDGs with higher mass are puffed up suddenly due to tidal heating at pericenter, UDGs with lower mass are gradually puffed up due to adiabatic expansion as a response to the mass loss (DM + gas + star) from tidal stripipng and ram pressures stripping.
+\citet{Jiang2019} use the NIHAO simulations and find that the UDGs in groups are either accreted as UDGs or accreted as normal dwarfs but get tidally heated near the orbital pericenter.
+\citet{Tremmel2020} study UDG formation in cluster environment and find UDGs with higher mass ($M_\star > 10^{8}\ M_\odot$) are puffed up suddenly due to tidal heating at pericenter, but UDGs with lower mass ($M_\star \sim 10^{7.5}\ M_\odot$) are gradually puffed up due to adiabatic expansion as a response to the mass loss from tidal stripping and ram pressures stripping.
+
+For UDGs in groups, since they probably experienced strong tidal interactions, it is not obviously clear whether they are quenched by tidal stripping or ram pressure stripping.
+However, in the tidal stripping scenario, dark matter needs to be removed before a significant fraction of gas are deprived by tidal force, indicating a longer quenching timescale.
+\citet{Jiang2019} argue that if tidal stripping is dominant in quenching, the satellites closer to the host will have smaller size and stellar mass since stars are also stripped.
+They find no such trend in simulation, but find that the average color is redder when the UDGs closer to the host, supporting that ram pressure stripping is dominant.
+In Section \ref{sec:size_distr}, we split the sample into two radial distance bins, and we do not find significant change in size distribution as UDGs get closer to the host.
+We also do not find any significant dependence of stellar mass distribution on radial distance for both UDGs and UPGs.
+Together with the fact that the quenched fraction decreases as UDGs (UPGs) get closer to their hosts, our findings agree with \citet{Jiang2019} that ram pressure stripping is the major quenching channel for UDGs (UPGs) in MW analogs.
+
+One surprising finding in this work is that although UPGs have extreme size given their stellar mass, they have similar quiescent fraction as normal satellites in MW analogs.
+In ELVES, Greene et al.
+(in prep) also find no trend of quenched fraction on the distance to average mass-size relation.
+This null trend hints that quenching and size growth must happen separately.
+
+1.
+UPGs are accreted into MW hosts from fields as normal dwarfs.
+If they subsequently get quenched and puffed up together due to tidal forces, we will expect a higher quenched fraction for UPGs since they must undergo more violent tidal interactions.
+If UPGs are quenched due to ram pressure stripping and puffed up due to tidal heating (one time event at pericenter), they will also exhibit higher quenched fraction because ram pressure is also stronger at pericenter.
+If they are puffed up due to a longer term adiabatic expansion \citep{Tremmel2020} due to mass loss, then the expansion should also be proportional to the amount of gas loss, which translates to quenched fraction.
+
+2. If UPGs are already puffed up before accretion (bursty SF, merger, high spin halo), but remain star-forming, then they are quenched together as other normal satellites.
+
+Bursty SF can puff the size up, but can also quench the galaxy due to SN feedback.
+
+Merger: early merger can redistribute the SF to the outer regions in UDGs, but doesn't change the total SFR too much. This might be a good thing.
+
+High spin: blue field UDGs have higher spin.
+
+Preprocessing in a lower-mass group can also puff up the UPGs.
+\citet{Samuel2022} show that preprocessing can boost the quenched fraction by 20\% but only at $M_\star \approx 10^8\ M_\odot$.
+For lower mass satellites, preprocessing merely change the quenched fraction.
+If preprocessing only increase the size of normal dwarfs to be UPGs but not quench them, it might be a plausible way to produce the observed trend in Fig.
+\ref{fig:qfrac}.
+
+splashback: they must be quenched in their prior infall.
+
+However, the efficiency of ram pressure stripping also depends on the stellar mass density which provides the restoring force.
+The diffuse stellar component makes UPGs more vulnerable to ram pressure stripping.
+\jiaxuan{But UDGs have higher HI density?}
+
+\citet{Kado-Fong2021} study the intrinsic shape of UDGs in observation and find the shape agree with merger scenario for field UDGs \citep{Wright2021} and tidal heating/adiabatic expansion for group/cluster UDGs \citep{Jiang2019,Tremmel2020}.
 
@@
 \section{Summary}
+\begin{itemize}
+    \item Future works: nucleation, intrinsic shape, LSBG cross-correlation, unsupervised machine learning, color gradient, non-par shapes.
+\end{itemize}
 

### 2022-08-25 main.tex
some discussion on UDG formation

--- 2022-08-22 main.tex
@@
 
+\jiaxuan{We don't discriminate our hosts to be paired or not. 
+Don't forget to discuss \citep{xSAGA-I} }
+
 \subsection{UDG and UPG sample}\label{sec:sample}
@@
 
+\subsection{UDG and UPG on mass-size plane}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
+	}
+    \caption{The distributions of the UDG and UPG sample on the mass-size plane.
+The data points are color-coded by the distance to the quenching color cut.
+Squares are those galaxies satisfying both UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
+    We plot the average mass-size relation (light green) and $1.5\sigma$ above the average relation (dark green) as dashed lines for reference.
+In the left panel, we show the constant surface brightness line as solid lines by assuming two different $g-i$ colors.
+Galaxies falling between these two lines are mostly red and quenched because blue UDGs have too be very large in size to satisfy the surface brightness criterion.
+This hard surface brightness cut makes the UDG quenched fraction high.
+    }
+    \label{fig:mass_size}
+\end{figure*}
+
 \subsection{Abundance of UDGs and UPGs}\label{sec:n_udg}
-
+\jiaxuan{Discuss NGVS}
 \begin{figure*}
@@
 
+We don't discriminate our hosts to be paired or not.
+
 We refer to quenching as the cessation of star formation in galaxies.
-In principle, direct estimates for the instantaneous star formation rate (SFR) from UV or H$\alpha$ are needed to define a quenched galaxy  population.
+In principle, direct estimates for the instantaneous star formation rate (SFR) from UV or H$\alpha$ or estimations for the \ion{H}{1} gas are needed to define a quenched galaxy  population.
 As an example, the SAGA survey measures the H$\alpha$ equivalent width (EW) from spectra to define quenched satellites.
+There are also many studies probing \ion{H}{1} masses for MW and M31 satellites \citep[e.g.,][]{Grcevich2009,Spekkens2014,Putman2021}.
 However, these specific data sets are either not deep enough to probe our UDGs and UPGs, or they are very expensive to obtain and cover all the footprint of our sample.
@@
 For UDGs (UPGs) in each stellar mass bin, we calculate the fraction of quenched galaxies, but both denominator and numerator are weighted by the weights $w_k$ assigned in Section \ref{sec:bkg} to mitigate the impact of background contamination on quenched fractions.
+
+describe the quenched fraction in percentage, e.g., half of them are quenched at 1e8.
 
@@
 
+% lower-mass satellites are mostly quiescent, roughly half of intermediate-mass satellites are quiescent, and higher-mass satellites are mostly star-forming
+
 \jiaxuan{TODO: make data products (catalogs, fake UDGs, website for their images, etc.)}
@@
 \subsection{High and constant quenched fraction of UDGs is an artifact}
-
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
-	}
-    \caption{The distributions of the UDG and UPG sample on the mass-size plane.
-The data points are color-coded by the distance to the quenching color cut.
-Squares are those galaxies satisfying both UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
-    We plot the average mass-size relation (light green) and $1.5\sigma$ above the average relation (dark green) as dashed lines for reference.
-In the left panel, we show the constant surface brightness line as solid lines by assuming two different $g-i$ colors.
-Galaxies falling between these two lines are mostly red and quenched because blue UDGs have too be very large in size to satisfy the surface brightness criterion.
-This hard surface brightness cut makes the UDG quenched fraction high.
-    }
-    \label{fig:mass_size}
-\end{figure*}
-
 In Section \ref{sec:quench}, we calculate the quenched fraction as a function of stellar mass for UDGs (left panels in Figure \ref{fig:qfrac}).
@@
 
-\subsection{UDG formation}
-Discuss how does quenching and pufffing interplay.
-
-Galaxy conformity: mass-size independent of color, jenny's quenched fraction independent of morph.
-
-Pre-puffed up or pre-quenched?
-
-Amorisco with my size distribution?
+\subsection{UDG and UPG formation}
+In this paper, one surprising finding is that although UPGs have extremely large size for their stellar mass, they have similar quiescent fraction as normal satellites in MW analogs.
+In ELVES, \citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology (equivalently color) of satellites.
+They interpret this trend as that the quenching and morphological transformation involves very mild size evolution.
+These evidences might indicate that quenching and size growth must happen separately.
+Then the question is what physics is responsible for the two processes respectively.
+In this section, we first review the quenching of MW satellites and the mechanisms for puffing up normal dwarfs to produce UDGs (UPGs).
+Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs.
+\footnote{\jiaxuan{Greene et al. (in prep) also find no trend of quenched fraction on the size?}}
+
+%%%%%%%%%%%%%%%%%%%
+Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are more quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,CarlstenELVES2022}.
+This difference hints that the MW environments play an important role on regulating the star formation activities in dwarf galaxies.
+There have been extensive works using simulations to study the quenching of satellites in MW analogs \citep[e.g.,][]{Simpson2018,Buck2019,Garrison-Kimmel2019,Simons2020,Joshi2021,Akins2021,Karunakaran2021,Font2022,Samuel2022}, and many of them are able to reproduce the observed quenched fraction in the Local Group and in the Local Volume.
+% the satellites in MW analogs are mostly quiescent below $M_\star\approx 10^7\ M_\odot$, and the quenched fraction drops as increasing stellar mass.
+
+In theory, satellite galaxies in MW analogs are accreted from the field, therefore quenching can happen either before or after the infall to MW host.
+In the former case, isolated dwarf galaxies can be quenched by bursty stellar feedback \citep[e.g.,][]{Bahe2015,Kazantzidis2017,ElBadry2018}, reionization \citep[e.g.,][]{Bullock2000,Benson2002,Somerville2002,Tollerud2018,Applebaum2021}, or being backsplash satellites \citep{Simpson2018,Benavides2021}.
+If a satellite is star-forming before infall, the ram pressure \citep[e.g.,][]{GunnGott1972,McCarthy2008,Simpson2018,Tremmel2020,Samuel2022} experienced by the satellite as it move through the hot circumgalactic medium (CGM) of the host could remove the gas and cause the cessation of star formation.
+It has been shown that ram pressure stripping can
+efficiently quench galaxies at $M_\star < 10^{8}\ M_\odot$ \citep{Fillingham2016,Simpson2018,Buck2019}.
+Tidal stripping can also deprive the gas from the satellite or stop the gas accretion and starve the galaxy \citep{Simpson2018}, but strong tidal interactions are needed because dark matter needs to be deprived before significant gas loss happens.
+Another quenching mechanism is the so-called preprocessing in a lower-mass group prior to the infall into a MW analog \citep{Wetzel2015b,Jahn2022,Samuel2022}.
+Satellites might be quenched in the previous group via ram pressure striping or tidal interactions, and gas distribution can also be altered in preprocessing even without being quenched.
+\citet{Samuel2022} show that 40\% of satellites were preprocessed before the infall to MW.
+Some studies also show that the paired host environments might enhance the quenching of satellites (\citealt{Garrison-Kimmel2019,Putman2021}, but also see \citealt{Samuel2022}).
+
+For UDGs and UPGs in MW analogs, they have extremely large size compared with normal satellites with their masses.
+Many mechanisms are proposed to explain the large size of UDGs (UPGs) in simulations.
+For isolated UDGs, bursty stellar feedback can cause the stellar component of dwarf galaxy to expand \citep[e.g.,][]{DiCintio2017,Chan2018,Martin2019,Jiang2019,Carleton2019}.
+Analytical models also support a scenario where UDGs originates from a population of dwarf galaxies residing in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Rong2017,Liao2019}.
+\citet{Wright2021} show that field UDGs can also be formed from major mergers that cause star formation to
+migrate outward.
+For UDGs in groups and clusters, environmental effects are more pronounced and tidal interactions are believed to puff up normal dwarfs.
+\citet{Jiang2019} find that the UDGs in groups are either accreted as UDGs from field or accreted as normal dwarfs but get tidally heated near the orbital pericenter.
+\citet{Tremmel2020} study UDG formation in cluster environment and find UDGs with higher mass ($M_\star > 10^{8}\ M_\odot$) are puffed up suddenly due to tidal heating at pericenter, but UDGs with lower mass ($M_\star \sim 10^{7.5}\ M_\odot$) are gradually puffed up due to adiabatic expansion as a response to the mass loss from tidal stripping and ram pressures stripping.
+\citet{Kado-Fong2021} study the intrinsic shape of UDGs in observations and find the inferred shapes agree with merger scenario for field UDGs \citep{Wright2021} and tidal heating/adiabatic expansion for group/cluster UDGs \citep{Jiang2019,Tremmel2020}.
+
+For UDGs in groups, since they probably experienced strong tidal interactions, it is not obviously clear whether they are quenched mainly by tidal stripping or ram pressure stripping. 
+% In the tidal stripping scenario, dark matter needs to be removed before a significant fraction of gas are deprived by tidal force, indicating a longer quenching timescale. 
+\citet{Jiang2019} argue that if tidal stripping dominates the quenching, the satellite closer to the host will have smaller stellar mass and effective radius since stars are also stripped.
+They find no such trend in simulation, but find that the average color is redder when the UDGs closer to the host, supporting that ram pressure stripping is more dominant.
+In Section \ref{sec:size_distr}, we split the sample into two radial distance bins, and we do not find significant change in size or stellar mass distribution as UDGs get closer to the host.
+
+In Auriga simulations, \citet{Simpson2018} show that the quenched fraction of satellites $M_\star < 10^8\ M_\odot$ have a strong dependence on the distance to the hosts.
+Using the FIRE-2 simulation, \citet{Samuel2022} also show that the quenched fraction increase as the distance to the host decreases, and hosts with higher CGM mass have more quenched satellites.
+In Figure \ref{fig:qfrac}, by comparing UDGs and UPGs at two radial bins, we find the very similar trends that UDGs (UPGs) closer to the host are more quiescent.
+In the ram pressure stripping picture, this is because the density of CGM increases when being closer to the host and the ram pressure is stronger.
+Together with the null trend on size and stellar mass distribution as UDGs (UPGs) get closer to their hosts, our findings support that ram pressure stripping is the major quenching channel for UDGs (UPGs) in MW analogs.
+
+%Combining all these factors together, returning backsplash galaxies can also exhibit as other satellites.
+
+If UDGs and UPGs are quenched by ram pressure stripping, how are they puffed up?
+UPGs can be puffed during the infall or prior to the infall.
+If UPGs are accreted into MW hosts from the field as normal dwarfs and puffed up due to tidal heating, we will expect a higher quenched fraction since they must undergo more violent tidal interactions, and the ram pressure is also stronger at distances closer to the host.
+If they are puffed up due to a longer term adiabatic expansion due to the mass loss, the expansion should also be proportional to the amount of gas loss, which translates to quenched fraction.
+Therefore, tidal puffing during infall seems to contradict with the normal quenched fraction as seen in Figure \ref{fig:qfrac}.
+
+It is more feasible that UPGs are already puffed up before accretion and remain being star-forming.
+They are quenched by ram pressure stripping in the MW host with other normal satellites.
+In order to achieve similar quenched fraction as normal satellites, field UPGs prior to infall have to be star forming.
+Bursty star formation, early merger, higher halo spin, and preprocessing can all puff up the field dwarfs to become UPGs, and some of them seem not to quench the UPGs.
+\citet{Wright2021} show that early merger does not significant change the total SFR.
+\citet{Samuel2022} show that preprocessing can marginal boost the quenched fraction by 20\% at $M_\star \approx 10^8\ M_\odot$ and merely change the quenched fraction for lower mass satellites.
+Although it is not clear whether the high halo spin is the cause or the consequence of UPG formation, it is probable that higher halo spin does not quench a UPG.
+If any of these mechanisms can only increase the size to make UPGs but not quench them, it provides a plausible way to produce the observed trend in Fig.
+\ref{fig:qfrac} where quenching and size growth are decoupled.
+However, the efficiency of ram pressure stripping also depends on the stellar mass density which provides the restoring force.
+The diffuse stellar component might make UPGs more vulnerable to ram pressure stripping and tidal stripping.
+It is also possible that UPGs in MW analogs are a mixture of field UPGs and normal dwarfs puffed up during infall.
+Using our observations, it is hard to sort out detailed mechanisms for quenching and size growth of UPGs.
+More detailed studies in observation and simulation are needed to solve this puzzle.
+
+% \citet{Wright2021} observed a temporary boost in spin after the early merger.
+\citet{Liao2019} find that blue field UDGs indeed have higher halo spins.
+If field UDGs (UPGs) are born in high spin halos, they might have similar SFR as normal field dwarfs.
+
+% \citet{Samuel2022} show that 40\% of satellites were in another group prior to the infall to MW, and preprocessed satellites have higher quenched fraction, and 10\% were quenched during preprocessing.
+\jiaxuan{Do we need to discuss splashback somewhere?}
+
+% \jiaxuan{But UDGs have higher HI density?}
+
+% splashback: they must be quenched in their prior infall.
+
+% \citet{Samuel2022} find that HI gas can form a concentrated core after ram-pressure stripping and be there for quite long.
+\citet{Font2022} find LSB galaxies in FIRE-2 have concentrated stellar core.
+Oh, but the core might not be dense enough to form stars.
+
+% Galaxy conformity: mass-size independent of color, jenny's quenched fraction independent of morph.
+
+% Scenarios:
+% 1. violent environmental effects: radial orbits, back-splash both explain large size and quenching. But according to Bernavidis et al, the quenched fraction drops with increasing mass.
+
+% 2. accreting field UDGs, and quench them due to ram pressure stripping. But how long do accreted UDGs last before being destroyed? Need to look at ram pressure stripping literature.
+
+% Homework:
+% 1. Move the stellar mass bin definition, try to match with red/blue, spiral/elliptical plot. If cannot match, does this hint the formation scenarios?
+% 2. How significant do we detect blue UDGs? 
+% 3. Split into redshift bins
+
+% UDG rejuvenate after ram pressure stripping?
+
+% calculate probability of being a backsplash satellite (e.g., splashed to 1.5 Mpc)
+% Compare spatial distribution with normal dwarf? iF they are indeed high-spin tail of normal dwarfs. 
+% Host-to-host variation
+
+\subsection{A better definition for diffuse galaxies}
+
+From \citet{Wright2021}, We can take this into our paper: At high mass (M⋆ > 108 M⊙), most galaxies have reff > 1.5 kpc.
+UDGs are therefore those galaxies that are unusually LSB.
+At low mass (M⋆ < 107.5 M⊙), most galaxies have μ0,g > 24 mag arcsec−2.
+UDGs are therefore those galaxies that have unusually large effective radii.
+It is only really at intermediate masses that both the central surface brightness and the effective radius criteria are relevant.
 
@@
 
-Scenarios:
-1. violent environmental effects: radial orbits, back-splash both explain large size and quenching. But according to Bernavidis et al, the quenched fraction drops with increasing mass.
-
-2. accreting field UDGs, and quench them due to ram pressure stripping. But how long do accreted UDGs last before being destroyed? Need to look at ram pressure stripping literature.
-
-Homework:
-3. Move the stellar mass bin definition, try to match with red/blue, spiral/elliptical plot. If cannot match, does this hint the formation scenarios?
-4. How significant do we detect blue UDGs? 
-5. Split into redshift bins
-
-UDG rejuvenate after ram pressure stripping?
-
-Why red is equivalent to quenched? Need to clarify in the paper
-
-calculate probability of being a backsplash satellite (e.g., splashed to 1.5 Mpc)
-
-Compare spatial distribution with normal dwarf? iF they are indeed high-spin tail of normal dwarfs.
-
-Don't forget to discuss \citep{xSAGA-I}
-
-\subsection{A better definition for diffuse galaxies}
-
 % \subsection{Systematic search for LSBGs in the LSST era}
@@
 \section{Summary}
+\begin{itemize}
+    \item we advocate studies for the quenched fraction as a function of size in simulations
+
+    \item Future works: nucleation, intrinsic shape, LSBG cross-correlation, unsupervised machine learning, color gradient, non-par shapes. 
+\end{itemize}
 

### 2022-08-30 main.tex
Updates from Overleaf

@@
 
+UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields \citep{Prole2019,Leisman2017}, however there are one or two red UDGs in fields.
+It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up?
+3) how are they quenched?
+what's the correlation between quenching and puffing.
+
 explain those acronyms (SAGA, ELVES)
@@
 With a sample of UDGs around MW-like hosts, we can compare the structural parameters, quenched fractions, nucleation fractions, and radial distributions with normal satellites in the nearby universe \citep[e.g.,][]{SAGA-II,CarlstenELVES2022}, to shed light on questions about the formation and evolution of the UDGs.
+
+Stellar population of UDGs \citep[e.g.,][]{Gu2018}
 
@@
 \subsection{UDG and UPG sample}\label{sec:sample}
+\jiaxuan{TODO: make data products (catalogs, fake UDGs, website for their images, etc.)}
+
 The UDG population is usually defined based on the surface brightness and the physical size of the galaxy.
@@
 
-We derive the stellar masses of galaxies in the UDG and UPG sample from the Spergel model fitting and a color-$M_{\star}/L$ relation from \citet{Into2013}:
+We derive the stellar masses of galaxies in the UDG and UPG sample from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
 \begin{align*}
@@
 We find this color-based contamination subtraction scheme is sufficient for this work since the contamination fraction is small.
-Our main results aren shown in Section \ref{sec:results} are robust against contamination subtraction.
+Our main results shown in Section \ref{sec:results} are robust against contamination subtraction.
+
+We note that we do not apply any background correction in Fig. \ref{fig:size_distribution} and Fig. \ref{fig:mass_size}.
 
 \section{Results}\label{sec:results}
-In this section, we present statistical analysis of UDGs and UPGs associated with MW analogs in the nearby Universe. TLDR the full section here?
-
-\subsection{UDG and UPG on mass-size plane}
-
+In this section, we present statistical analysis of UDGs and UPGs associated with MW analogs in the nearby Universe.
+
+\subsection{UDG and UPG on the mass-size plane}\label{sec:mass-size}
 \begin{figure*}
@@
 
+In order to build a more comprehensive intuition on our UDG and UPG sample, we show their distributions on the mass-size plane in Figure \ref{fig:mass_size}.
+In the left panel, UDGs that are also classified as UPGs are shown in squares, while UDGs that do not satisfy UPG criteria are marked as stars.
+In the right panel, triangles correspond to UPGs that are not classified as UDGs.
+To orient us on the mass-size plane, we display the average mass-size relation derived from the satellites of MW analogs in the Local Volume \citep{ELVES-I} as the light green dashed lines.
+The darker green line shows $1.5\sigma$ above the average mass-size relation assuming the scatter of the mass-size relation to be $\sigma=0.181$ dex \citep{ELVES-I}.
+Because UDGs are defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$, we see a hard cut on size and surface brightness in the left panel.
+In the right panel, we see that UPGs are all above the $1.5\sigma$ line by construction.
+Comparing the two panels, we find that the UDG sample includes a number of galaxies below $1.5\sigma$ line (highlighted as stars), but also lose a few low-mass galaxies with sizes smaller than 1.5 kpc.
+UDGs below $1.5\sigma$ line have sizes larger than 1.5 kpc, but not large enough given their masses.
+It is also noticeable that UPG sample has a few galaxies with $M_\star > 10^{8.5}\ M_\odot$ which have surface brightness brighter than $25.0\ \sbunit$.
+As a consequence, the size distribution of UPGs at the smaller end is suppressed as shown in Fig.
+\ref{fig:size_distribution}.
+
+As we will introduce in Section \ref{sec:quench}, we use a color cut $(g-i)_{Q}$ to separate galaxies with active star formation from quiescent ones.
+Here we define $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ as an indicator for how much it has been quenched.
+Higher $\Delta(\mathrm{Quench})$ indicates that the galaxy is actively star-forming, whereas smaller $\Delta(\rm Quench)$ means the galaxy has lower star formation rate.
+We color-code the galaxies in Figure \ref{fig:mass_size} with $\Delta(\mathrm{Quench})$.
+UDGs below the $1.5\sigma$ line have near zero or negative $\Delta(\mathrm{Quench})$, implying that the UDG sample includes plenty of quenched galaxies compared with the UPG sample.
+Instead, the UPG sample is comprised of many star-forming galaxies at the high-mass end.
+
+In Fig.
+\ref{fig:mass_size}, we also show constant surface brightness lines in the left panel and constant mass surface density in the right panel.
+We will discuss how the definition of UDG could bias the quenched fraction later in Sec.
+\ref{sec:discussion}.
+
+\jiaxuan{@Jenny: any other things to mention in this section?}
+
 \subsection{Abundance of UDGs and UPGs}\label{sec:n_udg}
-\jiaxuan{Discuss NGVS}
+
 \begin{figure*}
@@
 
-As demonstrated by many previous studies \citep[e.g.,][]{vdBurg2016,vdBurg2017}, the average number of UDGs per host scales with host halo mass.
+As demonstrated by many previous studies \citep[e.g.,][]{vdBurg2016,vdBurg2017,Roman2017a}, the average number of UDGs per host scales with host halo mass.
 While much literature focuses on finding UDGs in clusters and large groups, there are fewer constraints on the UDG abundance at the lower halo mass end.
@@
 
-We define the UDG abundance as the average number of UDGs per host galaxy.
+We define the UDG (UPG) abundance as the average number of UDGs (UPGs) per host galaxy.
 In our UDG sample, there are 412 UDGs associated with 258 hosts.
 After correcting for background contamination (see Section \ref{sec:bkg}) and completeness (see Section \ref{sec:completeness}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host.
+The UPG abundance in our sample is $N_{\rm UPG} = 0.61\pm 0.04$ per host.
 Here we neglect the fact that the number of satellites contained within the virial sphere is different from the number of satellite within a projected cylinder with virial radius (the so-called deprojection factor, \citealt{vdBurg2017}).
@@
 In the SAGA survey \citep{SAGA-II}, 6 satellite galaxies (out of 127 spectroscopy-confirmed satellites around 36 MW analogs) satisfy the definition of UDG.
-Therefore the UDG fraction in \citet{SAGA-II} is about $N_{\rm UDG,\, SAGA} \approx 0.17\pm0.07$.
-In the ELVES survey \citep{CarlstenELVES2022}, there are 15 satellites (out of 404 satellites associated with 30 MW analogs) satisfying the UDG definition, leading to a UDG fraction of $N_{\rm UDG,\, ELVES} \approx 0.50\pm0.13$.
+Therefore the UDG abundance in \citet{SAGA-II} is about $N_{\rm UDG,\, SAGA} \approx 0.17\pm0.07$.
+In the ELVES survey \citep{CarlstenELVES2022}, there are 15 satellites (out of 404 satellites associated with 30 MW analogs) satisfying the UDG definition, leading to a UDG abundance of $N_{\rm UDG,\, ELVES} \approx 0.50\pm0.13$.
 \citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}.
@@
 Among these studies, only \citet{vdBurg2017} applies a background subtraction and completeness correction to the raw counts.
+In the Auriga simulations, \citet{Liao2019} find $N_{\rm UDG,\ Auriga}=1.27\pm 1.06$ for UDGs in MW-mass hosts.
 The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray.
@@
 This might be explained by the different photometric depth of data used.
-SAGA selects dwarf candidates in DECaLS data, which is x mag shallower than the CFTH and HSC data used in ELVES and this work.
+As pointed out by \citet{CarlstenELVES2022,Font2022}, SAGA survey reaches a surface brightness depth of $\sbeffr\approx 25\ \sbunit$, which is $\sim 2.5\ \sbunit$ shallower than the ELVES survey and this work.
 It is probable that SAGA missed a significant fraction of red and lower surface brightness galaxies.
@@
 If completeness is applied, it is possible that the slope $\beta$ will be steeper than what we are showing in Figure \ref{fig:n_udg}.
-
-In the right panel, we split the UDG sample into different bins based on their host halo mass (shown as triangles) and host color (shown as pentagons).
+We also note that many studies do no consider measurement bias and uncertainty, which makes the comparisons more difficult.
+
+In the right panel of Figure \ref{fig:n_udg}, we split the UDG sample into different bins based on their host halo mass (shown as triangles) and host color (shown as pentagons).
 The UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger with host color.
 
-\citet{Liao2019} also shows a shallower power law with 0.93. We can add that paper here.
-
-\jiaxuan{UPG abundances, and compare with UDGs}
-
-quenched line: Meng's manga paper. color-mass.
-
-% Plot the UDG and UPG population on the re-abs mag plane (Bovy book)
-% \citet{Trujillo2020}: define size based on surface mass density
-% We correct for completeness after statistical contamination subtraction.
+Another interesting quantity is the fraction of UDGs (UPGs) out of all satellites in a group or cluster.
+We denote this fraction as UDG (UPG) fraction hereafter, which characterizes the tail of the size distribution of satellites.
+In order to calculate this fraction, we assume that MW analogs have $\sim 5$ satellites with $M_\star > 10^{6.5}\ M_\odot$ \citep{CarlstenELVES2022}.
+This lower limit of stelalr mass is roughly our detection limit (see Fig.
+\ref{fig:mass_size}).
+Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.15$ and $f_{\rm UPG} \approx 0.12$.
+We compare our results with the Virgo cluster.
+Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}), there are 15 UDGs and 24 UPGs out of 404 identified satellites without completeness correction.
+Thus their UDG (UPG) fraction is $f_{\rm UDG,\  Virgo}=0.04$ and $f_{\rm UPG,\ Virgo} = 0.06$.
+However, we note that \citet{Ferrarese2020} only survey the central 4 deg$^2$ of the Virgo cluster, which probably biases the UDG (UPG) fraction.
+A more systematic comparison on UDG (UPG) fraction in different environments is needed in the future.
 
 \subsection{Size distribution}\label{sec:size_distr}
-\jiaxuan{Plot size distribution in two radial bins, to test whether tidal stripping prevails ram pressure stripping. }
+
 \begin{figure*}
@@
 
-\jiaxuan{vdb17 doesn't estimate measurement bias.}
-
 We find that the UDG size distribution roughly follows a power law.
@@
 This is shallower than the power law presented in \citet{vdBurg2016} ($n\propto r_e^{-3.40\pm0.19}$) and \citet{vdBurg2017} ($n\propto r_e^{-2.71\pm0.33}$, shown as gray dash-dotted lines in Figure \ref{fig:size_distribution}).
-We also split the UDG sample based on their host stellar mass, but consistently find shallow power-laws with index $\sim -1.6$.
+We also split the UDG sample based on their host stellar masses and also distance to their hosts, but consistently find shallow power-laws with index $\sim -1.6$.
+In particular, we do not find significant change in the size distribution as UDGs (UPGs) get closer to their hosts.
 \citet{vdBurg2016} studies large galaxy clusters and find a very steep slope, \citet{vdBurg2017} includes less-massive groups and the slope is less steep.
-Combined with our findings, it might be possible that dense environment produces more small UDGs.
-\jiaxuan{Have anything to do with tidal stripping?
-UDGs in denser environs are more stripped thus smaller?}
+Combined with our findings, it might be possible that dense environment produces more smaller UDGs.
+As we will discuss in Sec.
+\ref{sec:discussion}, cluster environments provide stronger tidal fields and thus are more efficient on producing large UDGs due to tidal heating.
 
@@
 In \citet{vanDokkum2015}, UDGs are not found within 300 kpc from the cluster center, hinting that UDGs might not survive in such a dense environment.
-\citet{vdBurg2016} has also found that the number of UDGs is suppressed near the center of clusters, and the radial distribution of UDGs in cluster environments roughly follows a projected Einasto \citep{Einasto1965} profile.
+\citet{vdBurg2016} has also found that the number of UDGs is suppressed near the center of clusters, and the radial distribution of UDGs in cluster environments roughly follows a projected Einasto profile \citep{Einasto1965}.
 In the following, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.
@@
 We defer the discussion on the implications of these results to Section \ref{sec:discussion}.
-
-We don't discriminate our hosts to be paired or not.
 
@@
 % lower-mass satellites are mostly quiescent, roughly half of intermediate-mass satellites are quiescent, and higher-mass satellites are mostly star-forming
-
-\jiaxuan{TODO: make data products (catalogs, fake UDGs, website for their images, etc.)}
+% the satellites in MW analogs are mostly quiescent below $M_\star\approx 10^7\ M_\odot$, and the quenched fraction drops as increasing stellar mass.
 
@@
 In Section \ref{sec:quench}, we calculate the quenched fraction as a function of stellar mass for UDGs (left panels in Figure \ref{fig:qfrac}).
-We find that the UDG quenched fraction is reasonably a constant over $>1$ dex in stellar mass, and is higher than the quenched fractions of UPGs and satellite population of MW analogs.
+We find that the quenched fraction of UDGs is higher than the quenched fractions of UPGs and the satellite population of MW analogs.
+Furthermore, it remains a constant over $>1$ dex in stellar mass.
 In this subsection, we argue that UDG's high and constant quenched fraction is merely an artifact due to its contrived definition.
-
-In Figure \ref{fig:mass_size}, we plot our UDG sample on the mass-size plane.
-Because we use a color cut $(g-i)_{Q} = -0.067 M_V - 0.23$ to define quenching, we define $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ as an indicator for how much it has been quenched.
-Higher $\Delta(\mathrm{Quench})$ means that the galaxy is actively star-forming, whereas smaller $\Delta(\rm Quench)$ indicates the galaxy has been quenched more.
-The data points in Figure \ref{fig:mass_size} are color-coded by this $\Delta(\mathrm{Quench})$.
-As shown as green dashed lines, we plot the mass-size relation (and $1.5\sigma$ above the mean mass-size relation) derived from the satellite systems of MW analogs in Local Volume \citep{ELVES-I}.
-The two solid lines correspond to the surface brightness cut at $\sbeff = 25.0\ \sbunit$ by assuming different colors.
-For the redshift range of our sample, the surface brightness is a constant with distance since the cosmological effect is negligible.
-
-UDG with a redder color has a higher mass-to-light ratio, thus for a given mass and surface brightness, its size is smaller than a blue UDG.
-Consequently, only those large blue UDGs can satisfy the UDG definition.
-As shown in the left panel of Figure \ref{fig:mass_size}, galaxies between the red and the blue solid lines are mostly quenched ($\Delta(\mathrm{Quench}) < 0$).
-Due to the color-M/L relation, a fixed surface brightness cut makes red galaxies dominate the UDG population at the smaller size end, and thus giving rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}.
-
-The UPGs are defined as those galaxies at $1.5\sigma$ above the average mass-size relation.
-The right panel of Figure \ref{fig:mass_size} shows their distribution on mass-size plane.
-The squares are those galaxies classified as both UDG and UPG, stars are objects that are classified as UDG only, and triangles are UPGs only.
-We see a lot of blue galaxies with large size classified only as UPG because their surface brightness is too high to satisfy the UDG definition.
-
-% We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\mu_0(g) > 24.0\ \sbunit$ (or equivalently $\sbeff > 25.0\ \sbunit$).
+We also discuss the advantages and disadvantages of different definitions of low surface brightness galaxies.
+
+In Figure \ref{fig:mass_size}, we show our UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench})$ indicating how much a galaxy has been quenched.
+As we described in Section \ref{sec:mass-size}, the UDG sample includes a number of galaxies below the $1.5\sigma$ mass-size line.
+Additionally, these galaxies are mostly quenched (having zero or negative $\Delta(\mathrm{Quench})$).
+In order to help understand this phenomenon, we plot constant surface brightness lines of $\sbeff=25.0\ \sbunit$ for two different colors $g-i=0.4$ (blue solid line) and $g-i=0.8$ (red solid line).
+For our redshift range, the cosmological dimming effect is negligible and the surface brightness is a constant with distance.
+For a given size, surface brightness (e.g., $\sbeff=25.0\ \sbunit$), redder galaxies have the same absolute magnitude as blue galaxies, but have larger stellar mass because they have larger mass-to-light ratio than blue galaxies.
+The mass-to-light ratio effect manifests itself on Figure \ref{fig:mass_size} by separating the two constant surface brightness lines apart.
+We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$.
+As a result of the color-M/L relation, the UDG sample includes more red galaxies than blue ones by having a surface brightness cut at $\sbeff=25.0\ \sbunit$, and thus give rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}.
+It is the pathological definition of UDG that makes the quenched fraction high.
+
+We note that the color-$M_\star/L$ relation are only invoked when converting the absolute magnitude to stellar mass.
+Thus when studying the quenched fraction as a function of absolute magnitudes, the dependence of
+
+one will 't see a high and constant quenched fraction for UDGs.
 
@@
 Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched.
-Among others, tidal stripping and ram-pressure stripping are thought to quench the satellites.
-
-UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields \citep{Prole2019,Leisman2017}, however there are one or two red UDGs in fields.
-It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up?
-3) how are they quenched?
-what's the correlation between quenching and puffing.
 
@@
 
-We compare with SAGA quenched fraction (Mao) and ELVES (Carlsten, Greene in prep).
-
 % \citep{Baxter2021}: machine learning derived quenched fraction
@@
 
-SAGA misses a fraction of red faint galaxies in their intial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
+SAGA misses a fraction of red faint galaxies in their initial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
 SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.
+
+\jiaxuan{UPG help us define mass-size lognormal, more diverse environment. distances.}
+
+\citet{Trujillo2020}: define size based on surface mass density
+
+From \citet{Wright2021}, We can take this into our paper: At high mass (M⋆ > 108 M⊙), most galaxies have reff > 1.5 kpc.
+UDGs are therefore those galaxies that are unusually LSB.
+At low mass (M⋆ < 107.5 M⊙), most galaxies have μ0,g > 24 mag arcsec−2.
+UDGs are therefore those galaxies that have unusually large effective radii.
+It is only really at intermediate masses that both the central surface brightness and the effective radius criteria are relevant.
+
+discuss pros and cons of UDG and UPG (you have to assume a distance to define UPG).
+
+% \subsection{Systematic search for LSBGs in the LSST era}
 
@@
 In this paper, one surprising finding is that although UPGs have extremely large size for their stellar mass, they have similar quiescent fraction as normal satellites in MW analogs.
-In ELVES, \citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology (equivalently color) of satellites.
-They interpret this trend as that the quenching and morphological transformation involves very mild size evolution.
-These evidences might indicate that quenching and size growth must happen separately.
+In ELVES, Greene et al.
+(in prep) also find no trend of quenched fraction on size.
+\citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology (equivalently color) of satellites, suggesting that the quenching and morphological transformation involves very mild size evolution.
+Perhaps quenching and size growth happen separately.
 Then the question is what physics is responsible for the two processes respectively.
@@
 Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs.
-\footnote{\jiaxuan{Greene et al. (in prep) also find no trend of quenched fraction on the size?}}
 
@@
 Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are more quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,CarlstenELVES2022}.
-This difference hints that the MW environments play an important role on regulating the star formation activities in dwarf galaxies.
+This difference hints that the MW environments play an important role in regulating the star formation activities in dwarf galaxies.
 There have been extensive works using simulations to study the quenching of satellites in MW analogs \citep[e.g.,][]{Simpson2018,Buck2019,Garrison-Kimmel2019,Simons2020,Joshi2021,Akins2021,Karunakaran2021,Font2022,Samuel2022}, and many of them are able to reproduce the observed quenched fraction in the Local Group and in the Local Volume.
-% the satellites in MW analogs are mostly quiescent below $M_\star\approx 10^7\ M_\odot$, and the quenched fraction drops as increasing stellar mass.
 
@@
 In the former case, isolated dwarf galaxies can be quenched by bursty stellar feedback \citep[e.g.,][]{Bahe2015,Kazantzidis2017,ElBadry2018}, reionization \citep[e.g.,][]{Bullock2000,Benson2002,Somerville2002,Tollerud2018,Applebaum2021}, or being backsplash satellites \citep{Simpson2018,Benavides2021}.
-If a satellite is star-forming before infall, the ram pressure \citep[e.g.,][]{GunnGott1972,McCarthy2008,Simpson2018,Tremmel2020,Samuel2022} experienced by the satellite as it move through the hot circumgalactic medium (CGM) of the host could remove the gas and cause the cessation of star formation.
+If a satellite is star-forming before infall, the ram pressure \citep[e.g.,][]{GunnGott1972,McCarthy2008,Simpson2018,Tremmel2020,Samuel2022} experienced by the satellite as it moves through the hot circumgalactic medium (CGM) of the host could remove the gas and cause the cessation of star formation.
 It has been shown that ram pressure stripping can
 efficiently quench galaxies at $M_\star < 10^{8}\ M_\odot$ \citep{Fillingham2016,Simpson2018,Buck2019}.
-Tidal stripping can also deprive the gas from the satellite or stop the gas accretion and starve the galaxy \citep{Simpson2018}, but strong tidal interactions are needed because dark matter needs to be deprived before significant gas loss happens.
+Tidal stripping can also remove the gas from the satellite or stop the gas accretion and starve the galaxy \citep{Simpson2018}, but strong tidal interactions are needed because dark matter needs to be stripped before significant gas loss happens.
 Another quenching mechanism is the so-called preprocessing in a lower-mass group prior to the infall into a MW analog \citep{Wetzel2015b,Jahn2022,Samuel2022}.
@@
 
-For UDGs and UPGs in MW analogs, they have extremely large size compared with normal satellites with their masses.
+For UDGs and UPGs in MW analogs, we are still left with the question of how they became so physically large for their mass.
 Many mechanisms are proposed to explain the large size of UDGs (UPGs) in simulations.
-For isolated UDGs, bursty stellar feedback can cause the stellar component of dwarf galaxy to expand \citep[e.g.,][]{DiCintio2017,Chan2018,Martin2019,Jiang2019,Carleton2019}.
-Analytical models also support a scenario where UDGs originates from a population of dwarf galaxies residing in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Rong2017,Liao2019}.
+For isolated UDGs, bursty stellar feedback can cause the stellar component of the dwarf galaxy to expand \citep[e.g.,][]{DiCintio2017,Chan2018,Martin2019,Jiang2019,Carleton2019}.
+Analytical models also support a scenario where UDGs originate from a population of dwarf galaxies residing in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Rong2017,Liao2019}.
 \citet{Wright2021} show that field UDGs can also be formed from major mergers that cause star formation to
@@
 For UDGs in groups and clusters, environmental effects are more pronounced and tidal interactions are believed to puff up normal dwarfs.
-\citet{Jiang2019} find that the UDGs in groups are either accreted as UDGs from field or accreted as normal dwarfs but get tidally heated near the orbital pericenter.
-\citet{Tremmel2020} study UDG formation in cluster environment and find UDGs with higher mass ($M_\star > 10^{8}\ M_\odot$) are puffed up suddenly due to tidal heating at pericenter, but UDGs with lower mass ($M_\star \sim 10^{7.5}\ M_\odot$) are gradually puffed up due to adiabatic expansion as a response to the mass loss from tidal stripping and ram pressures stripping.
+\citet{Jiang2019} find that the UDGs in groups are either accreted as UDGs from the field or accreted as normal dwarfs but tidally heated near the orbital pericenter.
+\citet{Tremmel2020} study UDG formation in the cluster environment and find UDGs with higher mass ($M_\star > 10^{8}\ M_\odot$) are puffed up suddenly due to tidal heating at pericenter, but UDGs with lower mass ($M_\star \sim 10^{7.5}\ M_\odot$) are gradually puffed up due to adiabatic expansion as a response to the mass loss from tidal stripping and ram pressures stripping.
 \citet{Kado-Fong2021} study the intrinsic shape of UDGs in observations and find the inferred shapes agree with merger scenario for field UDGs \citep{Wright2021} and tidal heating/adiabatic expansion for group/cluster UDGs \citep{Jiang2019,Tremmel2020}.
@@
 
-In Auriga simulations, \citet{Simpson2018} show that the quenched fraction of satellites $M_\star < 10^8\ M_\odot$ have a strong dependence on the distance to the hosts.
+In the Auriga simulations, \citet{Simpson2018} show that the quenched fraction of satellites $M_\star < 10^8\ M_\odot$ have a strong dependence on the distance to the hosts.
 Using the FIRE-2 simulation, \citet{Samuel2022} also show that the quenched fraction increase as the distance to the host decreases, and hosts with higher CGM mass have more quenched satellites.
-In Figure \ref{fig:qfrac}, by comparing UDGs and UPGs at two radial bins, we find the very similar trends that UDGs (UPGs) closer to the host are more quiescent.
+In Figure \ref{fig:qfrac}, by comparing UDGs and UPGs at two radial bins, we find a very similar trend that UDGs (UPGs) closer to the host are more quiescent.
 In the ram pressure stripping picture, this is because the density of CGM increases when being closer to the host and the ram pressure is stronger.
@@
 UPGs can be puffed during the infall or prior to the infall.
-If UPGs are accreted into MW hosts from the field as normal dwarfs and puffed up due to tidal heating, we will expect a higher quenched fraction since they must undergo more violent tidal interactions, and the ram pressure is also stronger at distances closer to the host.
-If they are puffed up due to a longer term adiabatic expansion due to the mass loss, the expansion should also be proportional to the amount of gas loss, which translates to quenched fraction.
+If UPGs are accreted into MW hosts from the field as normal dwarfs and puffed up due to tidal heating, we might expect a higher quenched fraction since they must undergo more violent tidal interactions, and the ram pressure is also stronger at distances closer to the host.
+If they are puffed up through longer-term adiabatic expansion from mass loss, the expansion should also be proportional to the amount of gas loss, which translates to quenched fraction.
 Therefore, tidal puffing during infall seems to contradict with the normal quenched fraction as seen in Figure \ref{fig:qfrac}.
@@
 Bursty star formation, early merger, higher halo spin, and preprocessing can all puff up the field dwarfs to become UPGs, and some of them seem not to quench the UPGs.
-\citet{Wright2021} show that early merger does not significant change the total SFR.
-\citet{Samuel2022} show that preprocessing can marginal boost the quenched fraction by 20\% at $M_\star \approx 10^8\ M_\odot$ and merely change the quenched fraction for lower mass satellites.
+\citet{Wright2021} show that early merger does not significantly change the total SFR.
+\citet{Samuel2022} show that preprocessing can marginally boost the quenched fraction by 20\% at $M_\star \approx 10^8\ M_\odot$ and merely change the quenched fraction for lower mass satellites.
 Although it is not clear whether the high halo spin is the cause or the consequence of UPG formation, it is probable that higher halo spin does not quench a UPG.
@@
 
+\jiaxuan{Discuss the UDG fraction v.s. group mass game. How environment shapes the size distribution.}
+
 % \citet{Wright2021} observed a temporary boost in spin after the early merger.
@@
 % \citet{Samuel2022} show that 40\% of satellites were in another group prior to the infall to MW, and preprocessed satellites have higher quenched fraction, and 10\% were quenched during preprocessing.
-\jiaxuan{Do we need to discuss splashback somewhere?}
-
-% \jiaxuan{But UDGs have higher HI density?}
-
+\jiaxuan{Do we need to discuss splashback anywhere?}
+
+% \jiaxuan{But UDGs have higher HI surface density?} 
 % splashback: they must be quenched in their prior infall.
@@
 % Host-to-host variation
-
-\subsection{A better definition for diffuse galaxies}
-
-From \citet{Wright2021}, We can take this into our paper: At high mass (M⋆ > 108 M⊙), most galaxies have reff > 1.5 kpc.
-UDGs are therefore those galaxies that are unusually LSB.
-At low mass (M⋆ < 107.5 M⊙), most galaxies have μ0,g > 24 mag arcsec−2.
-UDGs are therefore those galaxies that have unusually large effective radii.
-It is only really at intermediate masses that both the central surface brightness and the effective radius criteria are relevant.
-
-discuss pros and cons of UDG and UPG (you have to assume a distance to define UPG).
-
-% \subsection{Systematic search for LSBGs in the LSST era}
 

### 2022-08-31 main.tex
very first intro and abstract

@@
 \begin{abstract}
-
+Ultra-diffuse galaxies (UDGs) are dwarf galaxies with extreme sizes and low surface brightness.
+The formation and quenching mechanisms of these intriguing objects are still under debate.
+In this work, we present systematic search for ultra-diffuse galaxies associated with Milky Way (MW) analogs in the nearby Universe ($0.01 < z < 0.04$) using the Hyper Suprime-Cam Strategic Survey Program data.
+We also define a new subset of low surface brightness galaxies dubbed as ``ultra-puffy galaxies'' (UPGs) which better characterize the size outliers on the mass-size plane.
+We perform statistical studies for UDGs and UPGs and compare the results with previous studies for UDGs in clusters and groups.
+We further contrast UDGs and UPGs with the bulk of MW satellites in nearby Universe and simulations.
+We find that UDGs have a higher quenched fraction than MW satellites and the quenched fraction remains constant over 1 dex in stellar mass.
+We argue that this high quiescent fraction is an artifact of the UDG definition.
+Despite their large sizes, UPGs have similar quenched fractions as the MW satellites.
+These results might hint that the size growth and quenching of UPGs must happen separately.
 \end{abstract}
@@
 
-\jiaxuan{Just copied the intro from the Magellan proposal. Not in shape at all.}
-Since the discovery of ultra-diffuse galaxies (UDGs, defined to have $r_e > 1.5$ kpc and $\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$) in the Coma cluster \citep{vanDokkum2015}, there have been a variety of studies for these extreme systems ranging from their dark matter content \citep{vanDokkum2018,vanDokkum2019} to their globular cluster populations (Danieli et al.
-2022).
-A central question related to UDGs is what physical mechanisms are responsible for their formation.
-Before we can answer this question, it is important to reliably determine in what environment they live.
-
-Past UDG studies focused on rich galaxy groups and clusters \citep[e.g.,][]{Yagi2016,Zaritsky2019}, which provides distance information.
-Although UDGs are also found in field environments \citep{Prole2019,Tanoglidis2021,Kadowaki2021}, most studies of field UDGs lack distances and thus are statistical in nature.
-UDGs in groups and clusters are red and quenched; their blue counterparts are typically found in field environments (for some exceptions see \citealt{Roman2019,Prole2019}).
-This suggests that environment plays a crucial role in the formation and quenching of UDGs.
-Tidal effects and ram-pressure stripping explains the high quenched fraction in clusters and groups, but it is unclear whether field UDGs quench because of internal processes (feedback) and/or external processes (as splashback satellites, \citealt{Benavides2021}).
+Ultra-diffuse galaxies (UDGs), defined as dwarf galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$), have attracted much attention to study their formation and properties.
+Although being identified in the past \citep[e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}, UDGs come to the stage again after \citet{vanDokkum2015} discovered a large population of ultra-diffuse galaxies in the Coma cluster, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and fields \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
+There have been a variety of studies for these extremely-diffuse galaxy systems ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022}, and stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
+
+A central question for the UDG population is what physical mechanisms are responsible for their formation and quenching.
+Different mechanisms are proposed to explain the presence of UDGs in different environments.
+Field UDGs might formed after star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, being backsplash satellites \citep{Benavides2021}, or they were born in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019}.
+For UDGs in groups and clusters, they are believed to be puffed up by tidal heating near the pericenter \citep{Jiang2019} or undergo adiabatic expansion due to mass loss \citep{Tremmel2020}.
+Despite advances in theoretical works, it is still an open question that how UDGs in certain environments are formed and quenched.
 It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end.
-A larger UDG sample, especially in low-density environments, is needed to test these hypotheses.
-
-Distance information of LSBGs is hard to know \citep{Kadowaki2021,Greene2022,Zaritsky2022} (also another cross-correlation paper recently?). Thus we turn to match with MW analogs.
-
-UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields \citep{Prole2019,Leisman2017}, however there are one or two red UDGs in fields.
-It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up?
-3) how are they quenched?
-what's the correlation between quenching and puffing.
-
-explain those acronyms (SAGA, ELVES)
-
-The best knowledge we have about dwarf galaxies at the very faint end was derived from systems in the Local Volume \citep[e.g.,][]{Simon2019,CarlstenELVES2022}.
-To better compare UDGs with other dwarf systems, we turned to looking for UDGs in the vicinity of Milky Way analogs at $0.01 < z < 0.04$.
-Until now, there are only $\sim 30$ confirmed UDGs associated with MW analogs \citep{Cohen2018,SAGA-II,CarlstenELVES2022}.
-The occurrence rate of UDGs in these low-density environments is unknown, and whether UDGs are quenched in such a regime has not been explored.
+To answer these questions, a complete sample of ``normal'' satellites is needed to be compared with UDGs in the same environments.
+
+Our best knowledge in the dwarf galaxy regime is about the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}.
+With the advent of deep sky surveys and dedicated spectroscopy programs, the satellite systems of MW analogs in the Local Volume and nearby Universe become approachable.
+The Satellites Around
+Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at $z\sim0.01$ \citep{SAGA-I,SAGA-II}.
+The Exploration of Local VolumE Satellites (ELVES) survey uses the deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume ($D<12$ Mpc) and estimate the surface brightness fluctuation distances from images to confirm satellites \citep{ELVES-I,ELVES-II,CarlstenELVES2022}.
+Having the MW satellites as a reference frame, we can study UDG formation and quenching by comparing UDG with the bulk of observed and simulated MW satellites.
+However, there are only $\sim 30$ confirmed UDGs associated with MW analogs in literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022}.
+A larger sample of ultra-diffuse galaxies associated with MW hosts is needed to conduct such studies.
+
+% One of the major obstacles for studying dwarf galaxies is that it is hard to get distance information especially for low-mass and low surface brightness galaxies.
+Beside direct distance measurements (e.g., SAGA, ELVES), it is common to assume a distance to a dwarf candidate by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
+A statistical background subtraction is needed to account for the contribution from background and foreground galaxies.
+Cross-correlation between the dwarf sample and a host galaxy sample can also reveal the distance distribution of dwarfs \citep{Greene2022}.
+These methods are also complemented by machine learning techniques \citep{Baxter2021,xSAGA-I}.
+
+In this work, using the Hyper-Suprime Camera imaging data, we construct a UDG sample associated with MW analogs at $0.01 < z < 0.04$.
+The goal of this paper is to posit the low surface brightness galaxies in the framework of the satellite systems of MW analogs.
+We compare the statistical properties of UDGs with LV satellites and simulations to shed light on questions about the formation and evolution of the UDGs.
+We also propose a new definition for diffuse galaxies as ``ultra-puffy galaxies'' (UPGs) which better represent the large-size tail of the dwarf galaxy population.
+
+% The occurrence rate of UDGs in these low-density environments is unknown, and whether UDGs are quenched in such a regime has not been explored.
 With a sample of UDGs around MW-like hosts, we can compare the structural parameters, quenched fractions, nucleation fractions, and radial distributions with normal satellites in the nearby universe \citep[e.g.,][]{SAGA-II,CarlstenELVES2022}, to shed light on questions about the formation and evolution of the UDGs.
 
-Stellar population of UDGs \citep[e.g.,][]{Gu2018}
-
-Also compare with LCDM-based hydro sims. Study the quenching along the direction perpendicular to the mass-size.
-
-While satellite galaxies in the fields are star-forming \citet{Geha2012}.
-
-The goal of this work is to posit UDGs in the framework of satellite systems of MW analogs.
-We compare the statistical properties of UDGs with LV satellites and simulations.
-Try to figure out whether UDG is a special class of galaxies or they are just a tail of mass-size scatter.
-
-This paper is framed as follows. We detect LSBGs, then match them to MW analogs such that we can assume distances.
+% UDGs found in groups and clusters are mostly red and quenched, whereas their blue counterparts are found in field environments (although several quenched UDGs are found in the field, \citealt{Roman2019,Prole2019}).
+This suggests that environmental effects play a critical role in the formation and quenching of UDGs.
+
+The layout of this paper is as follows.
+We describe the data we use in Section \ref{sec:data}.
+In Section \ref{sec:lsbg_search}, we describe how we search the LSBG candidates in HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), and modeling (\S \ref{sec:modeling}).
+We present our UDG and UPG samples in Section \ref{sec:sample_construction}.
+In Section \ref{sec:results}, we show statistical analysis for UDGs and UPGs including their abundances (\S \ref{sec:n_udg}), size distributions (\S \ref{sec:size_distr}), spatial distributions (\S \ref{sec:radial_distr}), and quenched fractions (\S \ref{sec:quench}).
+We discuss possible implications on the formation and quenching of LSB diffuse galaxies in Section \ref{sec:discussion}.
+Section \ref{sec:summary} presents a summary of this work and prospects for future works.
+We adopt a $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$.
+We use the AB system \citep{Oke1983} for magnitudes.
+The stellar mass used in this work is based on a \citet{Chabrier2003} initial mass function.
 
@@
 
-MW satellites: \citep{Nashimoto2022}
-
-We adopt a $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$.
-We use the AB system \citep{Oke1983} for magnitudes.
-The stellar mass used in this work is based on a \citet{Chabrier2003} initial mass function.
-
 \section{Data} \label{sec:data}
@@
 
-\section{LSBG search in HSC PDR2}
+\section{LSBG search in HSC PDR2}\label{sec:lsbg_search}
 Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the PDR2 data, which covers $\sim 1.5$ of the sky area in \citetalias{Greco2018}.
@@
 
-\section{UDGs in Milky-Way analogs}
+\section{UDGs and UPGs in Milky-Way analogs}\label{sec:sample_construction}
 
@@
 It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.
+% \citet{Wright2021} can reproduce observed mass-size.
 
@@
 Compared with the UDG sample, the UPG sample includes blue galaxies with surface brightness higher than the UDG cut ($\sbeff < 25\ \sbunit$) and excludes red galaxies at $25 < \sbeff < 26\ \sbunit$.
+We note that this plot is not corrected for background contamination.
     }
@@
 It is the pathological definition of UDG that makes the quenched fraction high.
-
 We note that the color-$M_\star/L$ relation are only invoked when converting the absolute magnitude to stellar mass.
-Thus when studying the quenched fraction as a function of absolute magnitudes, the dependence of
-
-one will 't see a high and constant quenched fraction for UDGs.
-
-We advocate that UPGs better represent the large-size tail of the dwarf galaxy population and have a more objective definition.
-
-Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched.
-
-Find literature for quenched fraction as a function of distance to host (Einasto 1974, Spekkens2014, Karunakaran2022 for MW and M31).
-
-% \citep{Baxter2021}: machine learning derived quenched fraction
-
-% \citep{Akins2021}: quenched fraction and quenching timescale in DC Justice League simulation.
-
-% \citep{Samuel2022}: quenched fraction of MW sats in FIRE-2.
-
-When discussing the quenched fraction, also mention that we are uncertain about the mass-size above 8.5 and below 9-ish? because we don't know about their mass-size.
-
-The mass-size doesn't depend on color (carlsten). The quenched fraction also doesn't depend on size. Reflect on Danieli\&vD mass-size slice paper.
-
-SAGA misses a fraction of red faint galaxies in their initial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
-SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.
-
-\jiaxuan{UPG help us define mass-size lognormal, more diverse environment. distances.}
-
-\citet{Trujillo2020}: define size based on surface mass density
-
-From \citet{Wright2021}, We can take this into our paper: At high mass (M⋆ > 108 M⊙), most galaxies have reff > 1.5 kpc.
-UDGs are therefore those galaxies that are unusually LSB.
-At low mass (M⋆ < 107.5 M⊙), most galaxies have μ0,g > 24 mag arcsec−2.
-UDGs are therefore those galaxies that have unusually large effective radii.
-It is only really at intermediate masses that both the central surface brightness and the effective radius criteria are relevant.
-
-discuss pros and cons of UDG and UPG (you have to assume a distance to define UPG).
-
-% \subsection{Systematic search for LSBGs in the LSST era}
+Thus when studying the quenched fraction as a function of absolute magnitudes, the artifact on mass-size plane would disappears on the size-luminosity plane \citep[e.g., see][]{Danieli2019}.
+
+In this paper, we propose an alternative definition for large diffuse galaxies: ultra-puffy galaxies (UPGs).
+They are defined to be $1.5\sigma$ above the average mass-size relation.
+The specific value above the average mass-size relation can be changed to probe different parts of the size distribution.
+As we discussed in Section \ref{sec:sample}, a mass-dependent size cut for diffuse galaxies is more objective than a hard size cut because the average size gets larger as increasing stellar mass.
+However, the mass-size relation generally depends on the color, morphology, environment, and also redshift of the galaxies \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
+Fortunately, for dwarf galaxies ($10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$) in the nearby Universe, \citet{ELVES-I} find that the mass-size relation is not sensitive to the color and morphology.
+This finding encourages definitions based on the mass-size relation for diffuse galaxies.
+For the UPG population, we show that it has similar quenched fraction as the bulk satellite population of MW analogs (Fig.
+\ref{fig:qfrac}).
+From Fig.
+\ref{fig:mass_size}, it is clear that the UPG definition naturally represents the large-size tail of the mass-size relation without introducing the color-$M_\star/L$ artifacts on stellar mass.
+We thus advocate studying the UPG population and how the properties vary as a function of the puffiness (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).
+
+However, everything comes with a price.
+In order to construct a UPG sample, one need to know the distance information as well as the color to convert observed magnitudes to stellar mass.
+The color-$M_\star/L$ relation also introduces additional uncertainties.
+\citet{ELVES-I} derive the mass-size relation below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$.
+As a result, it is not clear about the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ and how it depends on color and morphology.
+In this work, we simply extrapolate \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$.
+But the caveat on mass-size relation could make the UPG definition subject to systematical uncertainties.
+In this work we use the effective radius $r_e$, but other definitions of sizes might reduce the scatter of mass-size relation \citep[e.g.,][]{Miller2019,Trujillo2020} and further benefit the definition of UPGs.
+
+% Find literature for quenched fraction as a function of distance to host (Einasto 1974, Spekkens2014, Karunakaran2022 for MW and M31).
+
+% SAGA misses a fraction of red faint galaxies in their initial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
+% SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.
+
+% \jiaxuan{UPG help us define mass-size lognormal, more diverse environment. distances.}
 
@@
 Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs.
+\jiaxuan{Cite the Pan et al. paper}
 
 %%%%%%%%%%%%%%%%%%%
-Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are more quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,CarlstenELVES2022}.
+Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are more quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,Baxter2021,CarlstenELVES2022,Karunakaran2022}.
 This difference hints that the MW environments play an important role in regulating the star formation activities in dwarf galaxies.
@@
 
-\section{Summary}
+\section{Summary}\label{sec:summary}
 \begin{itemize}

### 2022-09-02 main.tex
Updates from Overleaf

@@
 \newcommand{\sbunit}{\mathrm{mag\ arcsec}^{-2}}
+\newcommand{\sbcen}{\mu_{0}(g)}
 \newcommand{\sbeff}{\overline{\mu}_{\mathrm{eff}}(g)}
@@
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{\today}
-\revised{\today}
-\accepted{\today}
-
-\submitjournal{ApJ}
+% \received{\today}
+% \revised{\today}
+% \accepted{\today}
+
+% \submitjournal{ApJ}
 
@@
 \defcitealias{Greco2018}{G18}
-
-% \def\G18{\citetalias{Greco2018}}
 
@@
 
-Ultra-diffuse galaxies (UDGs), defined as dwarf galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\mu(g,0)>24.0\ \mathrm{mag\ arcsec^{-2}}$), have attracted much attention to study their formation and properties.
-Although being identified in the past \citep[e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}, UDGs come to the stage again after \citet{vanDokkum2015} discovered a large population of ultra-diffuse galaxies in the Coma cluster, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and fields \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
+Ultra-diffuse galaxies (UDGs), defined as dwarf galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), have attracted much attention to study their formation and properties.
+Although being identified in the past \citep[e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}, UDGs come to the stage again after \citet{vanDokkum2015} discovered a large population of ultra-diffuse galaxies in the Coma cluster, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and fields \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
 There have been a variety of studies for these extremely-diffuse galaxy systems ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022}, and stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
@@
 
-%All satellite photometry is in the AB system and cor- rected for MW dust extinction using the E(B − V ) maps of Schlegel et al.
-(1998) recalibrated by Schlafly & Finkbeiner (2011).
-We take the solar g-band magni- tude to be Mg⊙ = 5.03 mag (Willmer 2018).
-% say somewhere in the results section that only SMUDGES measured and corrected measurement bias. vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$
+\jiaxuan{say somewhere in the results section that only SMUDGES measured and corrected measurement bias. vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$}
 
 \section{UDGs and UPGs in Milky-Way analogs}\label{sec:sample_construction}
+The goal of this paper is to study the diffuse galaxies hosted by MW-like galaxies.
+However, one of the major obstacles for studying LSBGs is that it is hard to get distance information.
+Beside direct distance measurements (e.g., SAGA, ELVES, \citealt{Kadowaki2021}), it is common to assume a distance to a dwarf candidate by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
+A statistical background subtraction is then needed to account for the contribution from background and foreground galaxies.
+Cross-correlation between the LSBG sample and a host galaxy sample can also reveal the distance distribution of LSBGs \citep{Greene2022}.
+These methods are also complemented by machine learning techniques \citep{Baxter2021,xSAGA-I}.
+In this Section, we cross-match our LSBG catalog with MW-like galaxies in the NSA catalog and construct the UDG and UPG sample.
 
 \subsection{Matching with Milky-Way analogs}\label{sec:match}
-
-The goal of this paper is to study the UDG population hosted by MW-like galaxies.
-However, the properties of the MW itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among different studies.
-In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig 2 of \citealt{SAGA-I}).
+The properties of the Milky Way itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016} and the definitions of MW analogs are different among different studies.
+In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig.
+2 in \citealt{SAGA-I}).
 This luminosity range approximately corresponds to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$.
@@
 In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$~mag ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA.
-In this work, we choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($\sim 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
-MW analogs selected using this definition are very close to those in SAGA but are slightly less massive than the ELVES hosts since ELVES has several groups more massive than SAGA.
-
-Since UDGs are relatively scarce in MW-like hosts \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics.
-However, UDGs will be too small and too faint to be detected in HSC images beyond a certain distance.
+In this work, we choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($M_{\star, \mathrm{MW}}\approx 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
+MW analogs selected using this definition are very close to those in SAGA but are slightly less massive than the ELVES hosts since ELVES has several groups more massive than SAGA hosts.
+
+Since UDGs are relatively scarce in MW analogs \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics.
 We choose our redshift range to be $0.01 < z < 0.04$, which makes sure that we can detect a significant number of faint dwarf galaxies around MW-like hosts.
-We exclude galaxies $z<0.01$ because 1) the number of UDGs will be very small due to the small volume; 2) their large angular size makes them more probable to be shredded in the deblending step, so including them will introduce a number of spurious LSB objects.
-Our MW analogs sample complements the ELVES sample and SAGA sample in our redshift range.
-
-After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left.
+The depth of HSC limits our detection below $z \approx 0.04$ since dwarf galaxies will be too small and too faint to be detected beyond that distance.
+We also exclude galaxies $z<0.01$ because 1) the number of UDGs will be very small due to the small volume; 2) their large angular size makes them more vulnerable to be shredded in the detection, so including them will introduce a number of spurious LSB objects.
+We do not discriminate our hosts to be isolated or paired.
+%Our LSBG sample complements the ELVES sample and SAGA sample in our redshift range.
+
+After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 MW-mass galaxies left.
 Then we match them to the initial LSBG sample (described in Section \ref{sec:detection}, before the deblending step) as follows.
-For a given MW analog, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}.
-It turns out that 40\% of hosts have virial radii larger than 300 kpc, which is commonly used as the virial radius of MW.
-Then we identify any LSBG that falls into the projected angular virial radius of the host.
+For a given MW analog, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar-halo mass relation in \citet{Behroozi2010}.
+It turns out that 40\% of our hosts have virial radii larger than 300 kpc, which is commonly used as the virial radius of MW.
+Then we identify any LSBG that falls into the projected virial radius of the host on the sky.
 If one LSBG is matched to multiple hosts, we assign it to the nearest host based on the separation normalized by host virial radius.
 Finally, we have 901 MW-like hosts and 10,579 LSBG candidates associated with them.
-However, there are still a significant fraction of spurious objects in this cross-matched LSBG sample, including galactic cirri, tidal tails/streams, shredded large galaxies, compact sources blended with galaxy outskirts, etc.
-As introduced in Section \ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects.
+
+However, there are still a significant fraction of spurious objects in this cross-matched LSBG sample, including galactic cirri, tidal streams, shredded large galaxies, compact sources blended with galaxy outskirts, etc.
+As described in Section \ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects.
 There are 2,673 objects left after the deblending cuts.
-Next, we model them using the Spergel profile as described in Section \ref{sec:modeling} and obtain their properties from the fitting results.
+Next, we model them using the Spergel profile as described in Section \ref{sec:modeling} and obtain their photometry and structural parameters from the best-fit models.
 Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives.
 We also remove duplicated objects.
-In the end, we have 2,510 LSBG candidates as our final LSBG sample, from which we construct the ultra-diffuse galaxy (UDG) sample and the ultra-puffy galaxy (UPG) samples as follows.
-
-\jiaxuan{We don't discriminate our hosts to be paired or not. 
-Don't forget to discuss \citep{xSAGA-I} }
+In the end, we have 2,510 LSBG candidates as our final LSBG sample.
+These LSBGs are matched to MW hosts but do not have direct distance measurements.
+We apply the measurement bias correction (\S \ref{sec:meas_unc}) and assign completeness and important weights after bias correction.
+In the end, we correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
+In the next subsection, we construct the UDG and UPG samples from the final LSBG sample.
 
 \subsection{UDG and UPG sample}\label{sec:sample}
-\jiaxuan{TODO: make data products (catalogs, fake UDGs, website for their images, etc.)}
-
-The UDG population is usually defined based on the surface brightness and the physical size of the galaxy.
-However, there are many different criteria in literature: \citep{vanDokkum2015} define UDGs to have effective radius $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}, and the size criterion also varies from $>1$ kpc to $>1.5$ kpc.
-\citet{vanNest2022} explore these definitions and find that different choice of UDG could drastically affect which subset of dwarfs are selected, therefore affect our understanding of the UDG population.
-
-The measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020} or other contaminants.
-Therefore in this work, we use the average surface brightness within effective radius $\sbeff$ to define UDG.
-The difference between the average surface brightness and the central surface brightness for a \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
-Since dwarf galaxies and UDGs typically show a range of \sersic{} index $0.8 < n < 1.2$ \citep{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value.
-In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, which takes the measurement errors into account.
+\jiaxuan{TODO: make data products (catalogs fake UDGs, website for their images, etc.)}
+The UDG sample is usually defined based on the surface brightness and the physical size of the galaxy.
+However, there are many different criteria in literature: \citep{vanDokkum2015} define UDGs to have effective radius $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}.
+The size criterion also varies from $r_e > 1$ kpc to $r_e > 1.5$ kpc.
+\citet{vanNest2022} explore these definitions and find that different choice of UDG can drastically change the selected subset of dwarfs, therefore affect our understanding of the UDG population.
+
+In practice, the measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020,ELVES-II,Somalwar2020} or other contaminants.
+Therefore in this work, we use the average surface brightness within effective radius $\sbeff$ to define UDGs.
+The difference between the average surface brightness and the central surface brightness can be analytically calculated for a \sersic{} profile: $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
+Since dwarf galaxies and UDGs typically have \sersic{} index of $0.8 < n < 1.2$ \citep[e.g.,][]{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value to convert $\mu_0$ to $\mu_{\mathrm{eff}}$.
+In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, where we also take the $1\sigma$ measurement errors into account.
 This definition maximizes the consistency with the definition in \citet{vanDokkum2015} while not losing UDGs harboring nuclear star clusters.
 
-Among the 2510 LSBG candidates, there are 432 objects satisfying the UDG definition.
-We did a final visual inspection for these objects and excluded 16 objects that are very likely to be false positives.
+Among the 2,510 LSBG candidates, there are 432 objects satisfying the UDG definition.
+We did a final visual inspection for these objects and excluded 16 objects that are false positives including blends and Galactic cirri.
 We also removed another 4 objects having completeness less than 0.1.
-In the end, we obtain our UDG sample with 412 objects, which are associated with 258 hosts.
-The total sky area occupied by UDG hosts (out to 1 $R_{\rm{vir}}$ is 32.71 deg$^{2}$.
-The UDG catalog is available \textbf{online} and the catalog format is shown in Table \ref{tab:catalog}.
+In the end, we obtain our UDG sample with 412 objects associated with 258 hosts.
+The total sky area occupied by UDG hosts (out to 1 $R_{\rm{vir}}$) is 32.71 deg$^{2}$.
 
@@
 
-The concept of UDG was proposed for those dwarf galaxies with large physical size and diffuse light distribution.
-However, the size of a galaxy is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Lange2015}.
-The slope of the mass-size relation has been shown to be color-dependent for galaxies above $M_\star > 10^{8.5}\ M_\odot$: blue star-forming galaxies have a shallower slope, whereas red quenched galaxies have a steeper slope.
-However, recent works show that the mass-size relation in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$) is quite universal: the slope and intercept are not sensitive to the color and morphology of dwarf galaxy \citep{ELVES-I}.
-This gives us a chance to define a subset of dwarf galaxies that are outliers on the mass-size plane.
-Taking the measured mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the mass-size relation.
-The UPGs are not necessarily large in physical size or faint in average surface brightness, but they are outliers in size for their masses.
-Both UDG and UPG represent subsets of dwarf galaxies that are larger and more diffuse than average.
-However, the hard cut on size (1.5 kpc) means that the UDG definition excludes ``large'' galaxies at the low-mass end because as mass goes smaller, the average size also gets smaller.
-The surface brightness cut also biases the UDG sample because of mass-to-light ratio differences between blue and red galaxies, as will be discussed in Section \ref{sec:quench}.
-The definition of UPG based on the observed mass-size relation is more physically-motivated, and UPGs better represent a homogeneous subset of dwarf galaxies along the stellar mass axis.
-There is also no color preference in the UPG definition for a given stellar mass.
+The concept of UDG was proposed for those dwarf galaxies with unusually large size and diffuse light distribution.
+However, the size of a galaxy is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
+The slope of the mass-size relation in nearby Universe has been shown to be color- and morphology-dependent for galaxies above $M_\star > 10^{9}\ M_\odot$: blue star-forming galaxies have a shallower slope than the red quenched galaxies.
+However, in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$), \citet{ELVES-I} show that the average mass-size relation is quite universal: the slope and intercept are not sensitive to the color or morphology of dwarf galaxies.
+This gives us a chance to define a subset of dwarf galaxies that are size-outliers in terms of the average mass-size relation.
+Taking the measured average mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the average mass-size relation.
+We note that the mass-size relation in \citet{ELVES-I} is derived for a mass range of $10^{5.5} < M_\star < 10^{8.5}$.
+We have to extrapolate the mass-size relation to $M_\star \sim 10^9\ M_\odot$ to define our UPG sample.
+
+The UPGs are not absolutely large in physical size or absolutely faint in surface brightness, but they are outliers in size for their stellar masses.
+The definition of UPG based on the observed mass-size relation is more physically-motivated, and UPGs better represent a homogeneous subset of large-size dwarf galaxies.
 It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.
-% \citet{Wright2021} can reproduce observed mass-size.
+We discuss the advantages and disadvantages of UDG and UPG in Section \ref{sec:artifact}.
 
@@
 The total sky area occupied by UPG hosts (out to 1 $R_{\rm{vir}}$) is 32.37 deg$^{2}$.
-
-The distribution of the UDG and UPG sample on the size-surface brightness plane are shown in Figure \ref{fig:udg_upg_re_mu}.
+The UDG and UPG catalogs are available in machine-readable format online\footnote{\url{https://github.com/AstroJacobLi/kuaizi/blob/master/data/}}.
+We demonstrate the catalog format in Table \ref{tab:catalog}.
+
+The distribution of UDGs and UPGs on the size-surface brightness plane are shown in Figure \ref{fig:udg_upg_re_mu}.
 The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively.
@@
 The numbers of red and blue galaxies are similar in the UDG sample, but there are more blue galaxies than red ones in the UPG sample.
-Since there is no hard surface brightness cut, the UPG sample includes many blue galaxies with higher surface brightness ($\sbeff < 25$).
-The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26$, because they are not LSB (hence low-mass) enough to be higher than $1.5\sigma$ from the mass-size relation.
-
-\jiaxuan{The mass-size relation used to define UPG is actually extrapolated to 1e9. Need to say this clearly.}
+Since there is no hard surface brightness cut, the UPG sample includes many blue galaxies with higher surface brightness ($\sbeff > 25$).
+The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26$ because their stellar masses are too high for their sizes to make them being size outliers.
+% they are not LSB (hence low-mass) enough to be higher than $1.5\sigma$ from the mass-size relation.
 
@@
 
-We derive the stellar masses of galaxies in the UDG and UPG sample from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
+We derive the stellar masses of UDGs and UPGs from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
 \begin{align*}
@@
 We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}.
-We correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
-The magnitudes and surface brightnesses are also extinction-corrected.
 
 \subsection{Background contamination}\label{sec:bkg}
-The major weakness of LSBG searches in photometric data is that distance information is typically unknown.
-Although we have matched LSBGs to MW analogs with known redshifts, the affiliation of LSBGs to the host is not guaranteed.
+The major weakness of LSBG searches in imaging data is that distance information is typically unknown.
+Although we have matched LSBGs to MW analogs by proximity, the physical affiliation of LSBGs to the host is not guaranteed.
 As a result, a certain fraction of galaxies in our UDG and UPG sample might just be foreground or background galaxies that fall within the virial radius of the host in projection.
@@
 We estimate the contamination fraction as follows.
-
-We select a patch of sky of 24 deg$^{2}$ in HSC S18A.
-Then we perform the same deblending and modeling steps for the 2707 LSBGs detected in this region.
-\footnote{The sky region is randomly selected, and these LSBGs share the same properties with our initial LSBG sample described in Section \ref{sec:match}.} We also removed objects that are already in our UDG sample, and we did visual inspection to further remove spurious objects.
-In the end, there are 480 LSBGs representing a population of possible contaminants in our UDG sample.
-Next, because the UDG is defined based on a physical size, we randomly associate the 483 LSBGs to the hosts of galaxies in our UDG sample.
-Then we calculate a physical radius for each LSBG and classify an LSBG as a ``fake`` UDG if it satisfies the definition.
-We repeat the random matching 200 times, and we obtain 11,458 fake UDGs.
-In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.94\pm0.03\ \mathrm{deg}^{-2}$.
-In the same way, we get 11,867 fake UPGs in 200 random matches, and the estimated number density of fake UPGs is $S_{\rm UPG} = 2.12\pm0.03\ \mathrm{deg}^{-2}$.
-The catalogs of fake UDG and UPGs are also available publicly\footnote{\url{https://zenodo.org/}}.
-
+The methodology is to study the number of those LSBGs that mimic UDGs and UPGs by randomly matching LSBGs to our MW hosts.
+
+We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2.
+Then we perform the same deblending and modeling steps for the 2,707 LSBGs detected in this region.
+We also removed objects that are already in our UDG sample, and we did visual inspection to further remove spurious objects.
+In the end, there are 480 LSBGs representing a population of possible contaminants.
+Next, because both UDG and UPG are defined based on physical size, we randomly associate the 480 LSBGs to the hosts of our UDGs (UPGs).
+Then we calculate a physical size for each LSBG and classify an LSBG as a ``fake`` UDG (or UPG) if it satisfies the definition.
+We repeat such random matching for 200 times.
+In the end, we obtain 11,458 fake UDGs and 11,867 fake UPGs.
+These UDGs and UPGs are ``fake'' only in the sense of being associated with random MW hosts.
+
+In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.94\pm0.03\ \mathrm{deg}^{-2}$, and the number density of fake UPGs is $S_{\rm UPG} = 2.12\pm0.03\ \mathrm{deg}^{-2}$.
+The catalogs of fake UDG and UPGs are also available online\footnote{\url{https://github.com/AstroJacobLi/kuaizi/tree/master/data}}.
 Using the number densities and the probed area of our survey, we calculate the contamination fraction for both the UDG and UPG samples.
-For the UDG sample, we find $f_{\rm contam} \approx 16\%$; for the UPG sample, the contamination fraction is $f_{\rm contam} \approx 20\%$.
-We take the contamination fraction into account when calculating the average UDG (UPG) number in Section \ref{sec:results}.
+For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 16\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 20\%$.
+We take the contamination fraction into account when calculating the abundance, size distribution, radial distribution of UDGs and UPGs in Section \ref{sec:results}.
+We note that we do not apply any background correction in Figure \ref{fig:mass_size} and Figure \ref{fig:size_distribution}.
 
 One of the main goals of this paper is to study the star-forming properties of UDGs and UPGs in MW analogs.
-The star formation rate of galaxies is indicated by broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs.
+The star formation rate of galaxies can be indicated by their broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs (see \S \ref{sec:quench} for more discussion).
 However, background contaminants affect the color distribution of the UDG (UPG) sample, thus affect the calculated quenched fraction.
-If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG.
-Indeed, we find that the $g-i$ color distribution of the fake UDG sample is bluer than that of the true UDG sample, which motivates us to assign importance weights based on $g-i$ color.
-We first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at $(g-i)_{k}$ bins) for both true UDG and fake UDG samples.
-Then we multiply $f_{\rm contam}$ with the histogram of fake UDG sample ($\lambda_k^{\rm fake}$) such that the histogram sums up to the average contamination fraction.
+If the fake UDGs (UPGs) have different properties from the real ones, we can use these information to derive a possibility for an object of being a real UDG (UPG).
+% If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG.
+Indeed, we find that the $g-i$ color distribution of the fake UDG (UPG) sample is bluer than that of the true UDG (UPG) sample, which motivates us to assign importance weights based on the $g-i$ color.
+We first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at the $(g-i)_{k}$ bin) for both true UDG and fake UDG samples.
+Then we multiply $f_{\rm contam}^{\rm UDG}$ with the histogram of fake UDG sample ($\lambda_k^{\rm fake}$) such that the histogram sums up to the average contamination fraction.
 The weights of UDGs in color bin $(g-i)_k$ is estimated to be $w_k = \max\,(1 - f_{\rm contam} \lambda_k^{\rm fake} / \lambda_k^{\rm true}, 0)$.
-This weight stands for a possibility of being a contaminant.
+This weight stands for a possibility of not being a contaminant.
 The weights of UPGs are assigned following the same procedure.
 We find this color-based contamination subtraction scheme is sufficient for this work since the contamination fraction is small.
-Our main results shown in Section \ref{sec:results} are robust against contamination subtraction.
-
-We note that we do not apply any background correction in Fig. \ref{fig:size_distribution} and Fig. \ref{fig:mass_size}.
+Our main results shown in Section \ref{sec:quench} are robust against contamination subtraction.
 
 \section{Results}\label{sec:results}
-In this section, we present statistical analysis of UDGs and UPGs associated with MW analogs in the nearby Universe.
+In this section, we present statistical analysis of UDGs and UPGs associated with MW analogs at $0.01 < z < 0.04$.
 
@@
 This hard surface brightness cut makes the UDG quenched fraction high.
+The constant surface mass density lines in the right panel might provide us new ways to define diffuse dwarf galaxies.
     }
@@
 \end{figure*}
-
-In order to build a more comprehensive intuition on our UDG and UPG sample, we show their distributions on the mass-size plane in Figure \ref{fig:mass_size}.
-In the left panel, UDGs that are also classified as UPGs are shown in squares, while UDGs that do not satisfy UPG criteria are marked as stars.
+Since we propose a new subset of LSBGs as UPG, some intuitions on the UPG population and the difference between UDG and UPG are needed.
+In order to build a more comprehensive understanding on our UDG and UPG sample, we show their distributions on the mass-size plane in Figure \ref{fig:mass_size}.
+In the left panel, UDGs that are also classified as UPGs are shown in squares, while UDGs that do not satisfy UPG definition are marked as stars.
 In the right panel, triangles correspond to UPGs that are not classified as UDGs.
-To orient us on the mass-size plane, we display the average mass-size relation derived from the satellites of MW analogs in the Local Volume \citep{ELVES-I} as the light green dashed lines.
+To orient the readers on the mass-size plane, we also display the average mass-size relation derived from the satellites of MW analogs in the Local Volume \citep{ELVES-I} as the light green dashed line.
 The darker green line shows $1.5\sigma$ above the average mass-size relation assuming the scatter of the mass-size relation to be $\sigma=0.181$ dex \citep{ELVES-I}.
 Because UDGs are defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$, we see a hard cut on size and surface brightness in the left panel.
-In the right panel, we see that UPGs are all above the $1.5\sigma$ line by construction.
+We also see that UPGs are all above the $1.5\sigma$ line by construction.
 Comparing the two panels, we find that the UDG sample includes a number of galaxies below $1.5\sigma$ line (highlighted as stars), but also lose a few low-mass galaxies with sizes smaller than 1.5 kpc.
-UDGs below $1.5\sigma$ line have sizes larger than 1.5 kpc, but not large enough given their masses.
-It is also noticeable that UPG sample has a few galaxies with $M_\star > 10^{8.5}\ M_\odot$ which have surface brightness brighter than $25.0\ \sbunit$.
-As a consequence, the size distribution of UPGs at the smaller end is suppressed as shown in Fig.
-\ref{fig:size_distribution}.
+UDGs below $1.5\sigma$ line have sizes larger than 1.5 kpc, but they are not large enough for their stellar masses.
+It is also noticeable that the UPG sample has a few galaxies with $M_\star > 10^{8.5}\ M_\odot$ which have surface brightness brighter than $25.0\ \sbunit$.
+% As a consequence, the size distribution of UPGs at the smaller end is suppressed as shown in Fig. \ref{fig:size_distribution}.
 
 As we will introduce in Section \ref{sec:quench}, we use a color cut $(g-i)_{Q}$ to separate galaxies with active star formation from quiescent ones.
-Here we define $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ as an indicator for how much it has been quenched.
-Higher $\Delta(\mathrm{Quench})$ indicates that the galaxy is actively star-forming, whereas smaller $\Delta(\rm Quench)$ means the galaxy has lower star formation rate.
+Here we define $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ as an indicator for the star formation rate of the galaxy.
+Higher $\Delta(\mathrm{Quench})$ indicates that the galaxy is actively star-forming, whereas lower $\Delta(\rm Quench)$ means the galaxy has lower star formation rate.
 We color-code the galaxies in Figure \ref{fig:mass_size} with $\Delta(\mathrm{Quench})$.
-UDGs below the $1.5\sigma$ line have near zero or negative $\Delta(\mathrm{Quench})$, implying that the UDG sample includes plenty of quenched galaxies compared with the UPG sample.
+UDGs below the $1.5\sigma$ line have near zero or negative $\Delta(\mathrm{Quench})$, indicating that the UDG sample includes plenty of quenched galaxies compared with the UPG sample.
 Instead, the UPG sample is comprised of many star-forming galaxies at the high-mass end.
 
-In Fig.
-\ref{fig:mass_size}, we also show constant surface brightness lines in the left panel and constant mass surface density in the right panel.
+% In Figure \ref{fig:mass_size}, we also show constant surface brightness lines in the left panel and constant mass surface density in the right panel.
 We will discuss how the definition of UDG could bias the quenched fraction later in Sec.
@@
 While much literature focuses on finding UDGs in clusters and large groups, there are fewer constraints on the UDG abundance at the lower halo mass end.
-In this section, we calculate the UDG abundance of MW analogs, and compare with other surveys.
+In this section, we calculate the UDG and UPG abundances of MW analogs, and compare with other surveys.
 
@@
 In our UDG sample, there are 412 UDGs associated with 258 hosts.
-After correcting for background contamination (see Section \ref{sec:bkg}) and completeness (see Section \ref{sec:completeness}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host.
+After correcting for background contamination (see \S \ref{sec:bkg}) and completeness (see \S \ref{sec:completeness}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host.
 The UPG abundance in our sample is $N_{\rm UPG} = 0.61\pm 0.04$ per host.
@@
 \citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}.
-Since both SAGA and ELVES select satellites based on distance measurements and do not correct for completeness, their UDG abundances are interpreted as lower limits.
-\citet{Roman2017b} do not estimate the background contamination fraction and do not correct for completeness either.
+Because both SAGA and ELVES select satellites based on distance measurements and do not correct for completeness, we interpret their UDG abundances as lower limits.
+We note that \citet{Roman2017b} do not estimate the background contamination fraction and correct for completeness.
 We plot the UDG abundances of these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017}.
 Among these studies, only \citet{vdBurg2017} applies a background subtraction and completeness correction to the raw counts.
-In the Auriga simulations, \citet{Liao2019} find $N_{\rm UDG,\ Auriga}=1.27\pm 1.06$ for UDGs in MW-mass hosts.
+% In the Auriga simulations, \citet{Liao2019} find $N_{\rm UDG,\,Auriga}=1.27\pm 1.06$ for UDGs in MW-mass hosts. 
 The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray.
@@
 As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo mass end.
-Our UDG abundance is similar to the value in ELVES survey, but is marginally higher than the prediction from \citet{vdBurg2017} although still consistent within the scatter.
-The UDG abundances from SAGA are significantly lower than both ELVES and our result.
+Our UDG abundance is similar to the value in ELVES survey, but much higher than the value from SAGA.
 This might be explained by the different photometric depth of data used.
@@
 It is probable that SAGA missed a significant fraction of red and lower surface brightness galaxies.
-
-Taking all data points from literature (as shown in Figure \ref{fig:n_udg}), we use orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the pink dashed line in Figure \ref{fig:n_udg}.
+Our UDG abundance is marginally higher than the prediction from \citet{vdBurg2017} but is still consistent considering the large scatter of the power law.
+
+Taking all data points from literature (as shown in Figure \ref{fig:n_udg}), we use the orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the red dashed line in Figure \ref{fig:n_udg}.
 The slope of the power law is shallower than \citet{vdBurg2017} ($\beta=1.11\pm0.07$) but still steeper than \citet{Roman2017b} ($\beta=0.85\pm0.05$).
+\citet{ManceraPina2018} survey eight clusters and find sublinear power laws.
 Since most individual studies do not have a statistical estimation for background contamination and completeness, the UDG abundances for large groups should be interpreted as lower limits.
@@
 In the right panel of Figure \ref{fig:n_udg}, we split the UDG sample into different bins based on their host halo mass (shown as triangles) and host color (shown as pentagons).
-The UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger with host color.
+We find that the UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger with host color.
+% Since there are not many data sets available for us to derive UPG abundances, we only take the ELVES results \citep{CarlstenELVES2022} and obtain $N_{\rm UPG} = $
 
 Another interesting quantity is the fraction of UDGs (UPGs) out of all satellites in a group or cluster.
-We denote this fraction as UDG (UPG) fraction hereafter, which characterizes the tail of the size distribution of satellites.
+This fraction represent how efficient an environment is at producing diffuse galaxies.
+We denote this quantity as UDG (UPG) fraction hereafter, which characterizes the tail of the size distribution of satellites.
 In order to calculate this fraction, we assume that MW analogs have $\sim 5$ satellites with $M_\star > 10^{6.5}\ M_\odot$ \citep{CarlstenELVES2022}.
-This lower limit of stelalr mass is roughly our detection limit (see Fig.
+This lower limit of stellar mass is roughly our detection limit (see Fig.
 \ref{fig:mass_size}).
 Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.15$ and $f_{\rm UPG} \approx 0.12$.
-We compare our results with the Virgo cluster.
+\jiaxuan{In ELVES, there are 25 UDGs and 27 UPGs out of xxx satellites, so $f_{\rm UDG} \approx xxx$ and $f_{\rm UPG} \approx xxx$.
+The ELVES results are consistent with ours.} We also compare our results with the Virgo cluster.
 Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}), there are 15 UDGs and 24 UPGs out of 404 identified satellites without completeness correction.
@@
 	}
-    \caption{Caption}
+    \caption{The size distribution of UDGs (\textit{left}) and UPGs (\textit{right}).
+The contribution from the background contaminants (gray dots) are subtracted and the completeness has been corrected.
+We fit a power law to the size distribution of UDGs and get a power law shallower than that from \citet{vdBurg2016,vdBurg2017}.
+We find that the power law slope increases as the average halo mass increases.
+It is possible that denser environments provide stronger tidal forces thus produce more smaller UDGs.
+The UPG size distribution is suppressed at the smaller size end because small galaxies are not $1.5\sigma$ above the mass-size relation.
+    }
     \label{fig:size_distribution}
@@
 In this section, we calculate the size distribution of our UDG and UPG sample.
-First of all, we take the fake UDGs in random fields and calculate their size distribution as a proxy for background contamination, shown as the gray dots in the left panel of Figure \ref{fig:size_distribution}.
-For each host, we calculate the raw size distribution of the associated UDGs (black dots), and we multiply the background size distribution by the virial area of the host and subtract it from the UDG size distribution (teal dots).
+First of all, we take the fake UDGs in random fields (\S \ref{sec:bkg}) and calculate their size distribution as a proxy for background contamination, shown as the gray dots in the left panel of Figure \ref{fig:size_distribution}.
+For each host, we calculate the raw size distribution of the associated UDGs (black dots), and we multiply the background size distribution by the virial area of the host and subtract it from the raw size distribution.
 Then we combine the UDG size distributions for all hosts together, and correct for completeness (red squares).
@@
 This is shallower than the power law presented in \citet{vdBurg2016} ($n\propto r_e^{-3.40\pm0.19}$) and \citet{vdBurg2017} ($n\propto r_e^{-2.71\pm0.33}$, shown as gray dash-dotted lines in Figure \ref{fig:size_distribution}).
-We also split the UDG sample based on their host stellar masses and also distance to their hosts, but consistently find shallow power-laws with index $\sim -1.6$.
+We also split the UDG sample based on their host stellar masses and distance to hosts, but consistently find shallow power-laws with index $\sim -1.6$.
 In particular, we do not find significant change in the size distribution as UDGs (UPGs) get closer to their hosts.
-\citet{vdBurg2016} studies large galaxy clusters and find a very steep slope, \citet{vdBurg2017} includes less-massive groups and the slope is less steep.
+Among others, \citet{vdBurg2016} focus on large galaxy clusters and find a very steep slope, \citet{vdBurg2017} includes less-massive groups and the slope is less steep.
 Combined with our findings, it might be possible that dense environment produces more smaller UDGs.
-As we will discuss in Sec.
-\ref{sec:discussion}, cluster environments provide stronger tidal fields and thus are more efficient on producing large UDGs due to tidal heating.
+As we will discuss in Section \ref{sec:discussion}, cluster environments provide stronger tidal fields and thus are more efficient on producing smaller UDGs due to tidal stripping.
 
 We also show the size distribution of UPGs in the right panel of Figure \ref{fig:size_distribution}.
-Unlike UDGs, we make the UPG sample by cutting through the 1.5$\sigma$ line above the mass-size relation.
+As we shown in Figure \ref{fig:mass_size}, the UPG sample does not have those galaxies below the $1.5\sigma$ line but larger than 1.5 kpc.
 Therefore, for a given mass, many small UDGs are not in the UPG sample since their sizes are not extreme on the mass-size plane.
@@
 
-Since the discovery of UDGs in Coma cluster, the radial distribution of UDGs around the hosts has been a valuable tool to test various UDG formation theories (cite simulation papers).
+The radial distribution of UDGs around the hosts has been used to test various UDG formation theories \citep[e.g.,][]{Tremmel2020}.
 In \citet{vanDokkum2015}, UDGs are not found within 300 kpc from the cluster center, hinting that UDGs might not survive in such a dense environment.
-\citet{vdBurg2016} has also found that the number of UDGs is suppressed near the center of clusters, and the radial distribution of UDGs in cluster environments roughly follows a projected Einasto profile \citep{Einasto1965}.
-In the following, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.
+\citet{vdBurg2016,ManceraPina2018} also found that the number of UDGs is depleted near the center of clusters.
+In \citet{vdBurg2016}, the radial distribution of UDGs in cluster environments roughly follows a projected Einasto profile \citep{Einasto1965}.
+In this subsection, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.
 
 We calculate the radial distribution as follows.
-For each host, we count the number of UDGs in each radial bin scaled by $R_{\rm vir}$ and calculate the number density within each radial annulus.
-We subtract the contribution of background contaminants based on the background contamination density (Sec.
-\ref{sec:bkg}) and the angular area occupied by the host.
+For each host, we count the number of UDGs (UPGs) in each radial bin scaled by $R_{\rm vir}$ and calculate the number density of UDGs (UPGs) within each radial annulus.
+We subtract the contribution of background contaminants based on the background contamination density (\S \ref{sec:bkg}) and the angular area occupied by the host.
 Then we average over all hosts and correct for the completeness, as shown in Figure \ref{fig:radial_distribution}.
@@
 The radial distributions of both UDGs and UPGs turn over around $R=0.2\,R_{\rm vir}$.
-It is known that the detection can be more incomplete as it gets closer to the host due to the blending between UDG and the host galaxy outskirts and possible sky subtraction issues.
-Although we have corrected the completeness for each object based on their size and surface brightness, it is still possible that our completeness does not include the dependence on the distance to the host.
-As we mentioned above, it is also possible that UDGs and UPGs are depleted because of strong tidal interactions.
-
-We fit the radial distributions of UDG (UPG) with the projected NFW and Einasto profiles at $R > 0.2 R_{\rm vir}$.
+It is known that the detection can be more incomplete as it gets closer to the host due to the blending between UDG and the host galaxy or due to sky subtraction issues.
+Although we have corrected the completeness for each object based on their size and surface brightness, it is still possible that our completeness does not fully characterize the radial dependence of completeness.
+As we mentioned above, it is also possible that UDGs and UPGs are depleted because of tidal disruption.
+
+We fit the radial distributions of UDGs (UPGs) with the projected NFW and Einasto profiles for $R > 0.2 R_{\rm vir}$.
 The Einasto profile introduces an extra ``shape'' parameter $\alpha$ and has been argued to be a better description to the dark matter halo profiles \citep[e.g.,][]{Navarro2004,Gao2008,Navarro2010,Dutton2014}.
 The Einasto profile also makes concentration estimates less sensitive to the radial range fitted.
-The best-fit NFW and Einasto profiles are shown in Figure \ref{fig:radial_distribution} as blue and red lines, respectively.
+The best-fit NFW (blue) and Einasto (red) profiles are shown in Figure \ref{fig:radial_distribution} as solid lines.
 The best-fit Einasto profile from \citet{vdBurg2016} is shown as the dashed gray line.
@@
 The radial distribution profiles of UDGs and UPGs are found to be very similar in shape.
-Our best-fit Einasto profiles have lower $\alpha$ and higher concentration compared with \citet{vdBurg2016} where $\alpha_{\rm Ein} = 0.92^{+0.08}_{-0.18},\ c_{\rm Ein} = 1.83^{+0.13}_{-0.12}$.
-
-According to the concentration-mass relation of dark matter halos, the concentration of MW-like halo is $c_{\rm NFW} \sim 10$ \citep{Bullock2001,Duffy2008,Dutton2014}.
+Our best-fit Einasto profiles have lower $\alpha$ and higher concentration compared with \citet{vdBurg2016} where they have $\alpha_{\rm Ein, UDG} = 0.92^{+0.08}_{-0.18},\ c_{\rm Ein, UDG} = 1.83^{+0.13}_{-0.12}$.
+
+According to the concentration-mass relation of dark matter halos, the concentration of MW-like halo is $c_{\rm NFW} \sim 10$ \citep[e.g.,][]{Bullock2001,Duffy2008,Dutton2014,Diemer2019}.
 Therefore, if assuming an NFW profile, the UDGs and UPGs follow the underlying dark matter distribution of the host.
-However, the Einasto shape parameter for a MW-like halo is $\alpha\sim 0.15$ at $z=0$ and its concentration $c\sim 8-10$.
+However, the Einasto shape parameter for a MW-like halo is $\alpha\sim 0.15$ at $z=0$ and its concentration is $c\sim 8-10$.
 \citep{Gao2008,Dutton2014}.
-Comparing with this, the best-fit Einasto profiles for UDG (UPG) radial distribution have larger shape parameter $\alpha$ and smaller concentration $c$.
+Comparing with this, the best-fit Einasto profiles for UDGs and UPGs are in tension with MW dark matter profile.
 We notice that the errors of the best-fit parameters are large due to the sample size and also the fact that concentration is most sensitive to data at smaller radial distances which are excluded in the analysis.
-Therefore, the UDG (UPG) radial distribution is considered to be consistent with the dark matter distribution of the host at a $2\sigma$ level.
-Nevertheless, a larger and more complete sample is needed to better constrain the radial distributions.
+Therefore, we consider the UDG (UPG) radial distribution to be consistent with the dark matter distribution of the host at a $2\sigma$ level.
+Nevertheless, a larger, cleaner, and more complete sample is needed to better constrain the radial distributions.
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{quenched_frac_elves.pdf}
+    \caption{A comparison on UPG quenched fractions with ELVES (Greene et al., in prep).}
+    \label{fig:qfrac_upg_elves}
+\end{figure}
 The star-forming properties of UDGs and UPGs is an interesting subject given their diffuse stellar component and possible non-trivial formation history.
@@
 \citet{CarlstenELVES2022} visually inspected all satellites and classified them into early-type (red and smooth) and late-type (blue, asymmetric, clumpy).
-Using this sample, they find that a mass-dependent color cut $g-i = -0.067 M_V - 0.23$ could also divide the sample into early- and late-type that are nearly identical to the ones based on morphology.
+Using this sample, they find that a mass-dependent color cut $(g-i)_{Q} = -0.067\, M_V - 0.23$ could also divide the sample into early- and late-type that are nearly identical to the ones based on morphology.
 The derived quenched fractions based on morphology and color are very similar.
@@
 For UDGs (UPGs) in each stellar mass bin, we calculate the fraction of quenched galaxies, but both denominator and numerator are weighted by the weights $w_k$ assigned in Section \ref{sec:bkg} to mitigate the impact of background contamination on quenched fractions.
-
+We also applied completeness correction.
+% We notice that such statistical background subtraction actually raise the quenched fraction since it reduces the impact of contaminants that are bluer in color.
+
+\jiaxuan{Also describe that we don't see a redshift trend. Null trend in redshfit also attest that our sample is not subjecct to background contamination.}
 describe the quenched fraction in percentage, e.g., half of them are quenched at 1e8.
@@
 
-\subsection{High and constant quenched fraction of UDGs is an artifact}
+\subsection{High and constant quenched fraction of UDGs is an artifact}\label{sec:artifact}
 In Section \ref{sec:quench}, we calculate the quenched fraction as a function of stellar mass for UDGs (left panels in Figure \ref{fig:qfrac}).
@@
 
+also, it is not clear that mass-size is well-described by a normal distribution in the tails.
+
+Both UDG and UPG represent subsets of dwarf galaxies that are larger and more diffuse than average.
+However, the hard cut on size (1.5 kpc) means that the UDG definition excludes ``large'' galaxies at the lower masses because as stellar mass goes smaller, the average size also gets smaller.
+There is also no color preference in the UPG definition for a given stellar mass.
+The surface brightness cut also biases the UDG sample because of the relation between galaxy color and mass-to-light ratio.
+
 % Find literature for quenched fraction as a function of distance to host (Einasto 1974, Spekkens2014, Karunakaran2022 for MW and M31).
@@
 Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs.
-\jiaxuan{Cite the Pan et al. paper}
+\jiaxuan{Cite the \citet{Pan2022} paper}
 
@@
 $\sigma(\overline{\mu}_{\mathrm{eff}}(g))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(g)$           \\
-$\overline{\mu}_{\mathrm{eff}}(r)$               & $\sbunit$ & $r$-band average surface brightness within $r_e$ \\
-$\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
-$\overline{\mu}_{\mathrm{eff}}(i)$               & $\sbunit$ & $i$-band average surface brightness within $r_e$ \\
-$\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
+% $\overline{\mu}_{\mathrm{eff}}(r)$               & $\sbunit$ & $r$-band average surface brightness within $r_e$ \\
+% $\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
+% $\overline{\mu}_{\mathrm{eff}}(i)$               & $\sbunit$ & $i$-band average surface brightness within $r_e$ \\
+% $\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
 $m_g$                    & mag     & $g$-band apparent magnitude     \\
 $\sigma(m_g)$            & mag     & Uncertainty of $m_g$            \\
-$m_r$                    & mag     & $r$-band apparent magnitude     \\
-$\sigma(m_r)$            & mag     & Uncertainty of $m_r$            \\
-$m_i$                    & mag     & $i$-band apparent magnitude     \\
-$\sigma(m_i)$            & mag     & Uncertainty of $m_i$            \\
+% $m_r$                    & mag     & $r$-band apparent magnitude     \\
+% $\sigma(m_r)$            & mag     & Uncertainty of $m_r$            \\
+% $m_i$                    & mag     & $i$-band apparent magnitude     \\
+% $\sigma(m_i)$            & mag     & Uncertainty of $m_i$            \\
 $g-r$                    & mag     & $g-r$ color                     \\
@@
 host\_g\_i & mag & $g-i$ color of the host galaxy \\
-host\_z &  & Redshift of the hsot galaxy \\
+host\_z &  & Redshift of the Host galaxy \\
 sep\_to\_host & deg & Angular separation between the host and UDG (UPG)\\
@@
 These tables are published in their entirety in machine-readable format.
-Magnitudes are on the AB system and have not been corrected for Galactic
+Magnitudes are on the AB system and have been corrected for measurement biases and Galactic
 extinction. The information of the host galaxies is from NASA-Sloan Atlas. We provide Galactic extinction corrections, which are derived from

### 2022-09-08 main.tex
before finishing summary

@@
 
-\shorttitle{UDGs in MW analogs}
+\shorttitle{Mass-size outliers in MW satellites}
 \shortauthors{Li et al.}
@@
 
-\title{Ultra Diffuse Galaxies associated with Milky-Way Analogs}
-
-% \correspondingauthor{Jiaxuan Li}
+% \title{Ultra Diffuse Galaxies associated with Milky-Way Analogs}
+\title{Beyond Ultra-Diffuse Galaxy: Mass-Size Outliers in the Satellites of Milky Way Analogs}
+
+\correspondingauthor{Jiaxuan Li}
 \author[0000-0001-9592-4190]{Jiaxuan Li (李嘉轩)}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+\email{jiaxuanl@princeton.edu}
 
@@
 \affiliation{Department of Astronomy and Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China}
+
 \author[0000-0002-8873-5065]{Peter Melchior}
@@
 \begin{abstract}
+\jiaxuan{Need to rewrite abstract}
 Ultra-diffuse galaxies (UDGs) are dwarf galaxies with extreme sizes and low surface brightness.
@@
 We argue that this high quiescent fraction is an artifact of the UDG definition.
-Despite their large sizes, UPGs have similar quenched fractions as the MW satellites.
-These results might hint that the size growth and quenching of UPGs must happen separately.
+Despite their large sizes, UPGs in MW analogs have similar quenched fractions as the bulk satellites.
+These results hint that the size growth and quenching of UPGs must happen separately.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-
-Ultra-diffuse galaxies (UDGs), defined as dwarf galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), have attracted much attention to study their formation and properties.
-Although being identified in the past \citep[e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}, UDGs come to the stage again after \citet{vanDokkum2015} discovered a large population of ultra-diffuse galaxies in the Coma cluster, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and fields \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
-There have been a variety of studies for these extremely-diffuse galaxy systems ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022}, and stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
-
-A central question for the UDG population is what physical mechanisms are responsible for their formation and quenching.
-Different mechanisms are proposed to explain the presence of UDGs in different environments.
-Field UDGs might formed after star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, being backsplash satellites \citep{Benavides2021}, or they were born in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019}.
-For UDGs in groups and clusters, they are believed to be puffed up by tidal heating near the pericenter \citep{Jiang2019} or undergo adiabatic expansion due to mass loss \citep{Tremmel2020}.
-Despite advances in theoretical works, it is still an open question that how UDGs in certain environments are formed and quenched.
-It is also unclear whether UDGs belong to a special class of galaxy or are just a natural extension of dwarf systems to the lower surface brightness end.
-To answer these questions, a complete sample of ``normal'' satellites is needed to be compared with UDGs in the same environments.
+In a variety of galaxy populations, an interesting subset of galaxies with low surface brightness and large physical size have been identified in the past \citep[dubbed as LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
+Recently, new excitement was generated by the discovery by \citet{vanDokkum2015} of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and fields \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
+There have been a variety of studies of these extremely-diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022}, and stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
+The UDGs are dwarf galaxies with larger size ($r_e > 1.5$ kpc) and lower surface brightness ($\sbcen > 24.0\ \sbunit$) than normal dwarfs, thus are outliers from the average mass-size relation.
+Therefore, a central question about mass-size outliers including UDGs is what physical mechanisms are responsible for the formation and quenching of these large diffuse galaxies.
+
+% In \citet{vanDokkum2015}, the ultra-diffuse galaxies (UDGs) are defined as dwarf galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$).
+
+Different mechanisms are proposed to explain the presence of large diffuse galaxies in different environments.
+Field UDGs might form after star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or they were born in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019}.
+UDGs in groups and clusters are believed to be puffed up by tidal heating near pericenter \citep{Jiang2019} or to undergo adiabatic expansion due to mass loss \citep{Tremmel2020}.
+Despite theoretical advances, it is still an open question how mass-size outliers like UDGs in certain environments are formed and quenched.
+It is also unclear whether mass-size outliers belong to a special class of galaxy or are just a natural extension of dwarf systems to lower surface brightness.
+To answer these questions, we can compare mass-size outliers with the ``normal'' satellites which we have a better understanding.
 
 Our best knowledge in the dwarf galaxy regime is about the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}.
-With the advent of deep sky surveys and dedicated spectroscopy programs, the satellite systems of MW analogs in the Local Volume and nearby Universe become approachable.
-The Satellites Around
-Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at $z\sim0.01$ \citep{SAGA-I,SAGA-II}.
-The Exploration of Local VolumE Satellites (ELVES) survey uses the deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume ($D<12$ Mpc) and estimate the surface brightness fluctuation distances from images to confirm satellites \citep{ELVES-I,ELVES-II,CarlstenELVES2022}.
-Having the MW satellites as a reference frame, we can study UDG formation and quenching by comparing UDG with the bulk of observed and simulated MW satellites.
-However, there are only $\sim 30$ confirmed UDGs associated with MW analogs in literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022}.
-A larger sample of ultra-diffuse galaxies associated with MW hosts is needed to conduct such studies.
-
-% One of the major obstacles for studying dwarf galaxies is that it is hard to get distance information especially for low-mass and low surface brightness galaxies.
-Beside direct distance measurements (e.g., SAGA, ELVES), it is common to assume a distance to a dwarf candidate by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
-A statistical background subtraction is needed to account for the contribution from background and foreground galaxies.
-Cross-correlation between the dwarf sample and a host galaxy sample can also reveal the distance distribution of dwarfs \citep{Greene2022}.
-These methods are also complemented by machine learning techniques \citep{Baxter2021,xSAGA-I}.
-
-In this work, using the Hyper-Suprime Camera imaging data, we construct a UDG sample associated with MW analogs at $0.01 < z < 0.04$.
-The goal of this paper is to posit the low surface brightness galaxies in the framework of the satellite systems of MW analogs.
-We compare the statistical properties of UDGs with LV satellites and simulations to shed light on questions about the formation and evolution of the UDGs.
-We also propose a new definition for diffuse galaxies as ``ultra-puffy galaxies'' (UPGs) which better represent the large-size tail of the dwarf galaxy population.
+With the advent of deep sky surveys and dedicated spectroscopy programs, we are now mapping the satellite systems of MW analogs in the Local Volume and nearby Universe.
+The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at $z\sim0.01$ \citep{SAGA-I,SAGA-II}.
+The Exploration of Local VolumE Satellites (ELVES) survey uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm satellites \citep{ELVES-I,ELVES-II,CarlstenELVES2022}.
+Having the MW satellites as a reference frame, we can study the formation and quenching of large diffuse galaxies by comparing them with the bulk of observed and simulated MW satellites.
+However, there are only $\sim 30$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022}.
+A larger sample of mass-size outliers (including UDGs) associated with MW hosts is needed to conduct such studies.
+
+The goal of this paper is to study large diffuse galaxies in the reference frame of the satellite systems of MW analogs and try to elucidate their formation and quenching.
+Albeit large size and low surface brightness, UDGs are not necessarily mass-size outliers in terms of their offsets to the average mass-size relation (see \S \ref{sec:sample_construction}).
+Motivated by this fact, we propose studying ``ultra-puffy galaxies'' (UPGs) which are $1.5\sigma$ above the average mass-size relation, representing the large-size tail of the dwarf galaxy population.
+Using the Hyper-Suprime Camera imaging data, we construct a sample of low surface brightness galaxies (LSBGs) and match them with MW analogs at $0.01 < z < 0.04$.
+Assuming the host distance, we calculate the physical size and stellar mass for LSBGs and further construct the UDG and UPG samples.
+We compare the statistical properties of mass-size outliers (UDGs and UPGs) with LV satellites and simulations to shed light on questions about their formation and evolution.
 
@@
 The layout of this paper is as follows.
-We describe the data we use in Section \ref{sec:data}.
+Section \ref{sec:data} describes the data used in this work.
 In Section \ref{sec:lsbg_search}, we describe how we search the LSBG candidates in HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), and modeling (\S \ref{sec:modeling}).
-We present our UDG and UPG samples in Section \ref{sec:sample_construction}.
+In Section \ref{sec:sample_construction}, we propose the UPG definition and present our UDG and UPG samples.
 In Section \ref{sec:results}, we show statistical analysis for UDGs and UPGs including their abundances (\S \ref{sec:n_udg}), size distributions (\S \ref{sec:size_distr}), spatial distributions (\S \ref{sec:radial_distr}), and quenched fractions (\S \ref{sec:quench}).
-We discuss possible implications on the formation and quenching of LSB diffuse galaxies in Section \ref{sec:discussion}.
-Section \ref{sec:summary} presents a summary of this work and prospects for future works.
-We adopt a $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$.
+We argue why we need to move beyond UDG and discuss possible implications of our results on the formation and quenching of mass-size outliers in Section \ref{sec:discussion}.
+Section \ref{sec:summary} presents a summary of this work and prospects for the future.
+In this work, we refer to LSBGs as objects selected purely by surface brightness, whereas UDGs and UPGs are selected by both physical size and surface brightness.
+We adopt a flat $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$.
 We use the AB system \citep{Oke1983} for magnitudes.
@@
 \subsection{Hyper Suprime-Camera data}
-The Hyper Suprime-Camera Subaru Strategic Program Survey (\citealt{Aihara2018}; hereafter HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}.
+The Hyper Suprime-Camera Subaru Strategic Program Survey (\citealt{Aihara2018}; hereafter the HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}.
 The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection).
@@
 \section{LSBG search in HSC PDR2}\label{sec:lsbg_search}
-Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the PDR2 data, which covers $\sim 1.5$ of the sky area in \citetalias{Greco2018}.
+Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies (LSBGs) in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}.
 The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section.
-For those who do not want to be bothered by technical details, we outline the major steps below:
+For those who do not want to be bothered by technical details, we outline the major steps below and refer the reader to Section \ref{sec:sample_construction} for UDG and UPG sample construction.
 \begin{enumerate}
-    \item Source Detection (Sec.
-\ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources.
+    \item Source Detection (\S \ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources.
 Then we apply an initial size and color cut based on the output catalog.
-    \item Deblending (Sec.
-\ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \code{scarlet}.
-We use \code{scarlet} models to define color-size-morphology-surface brightness cuts.
+    \item Deblending (\S \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \code{scarlet}.
+We use the \code{scarlet} models to define color-size-morphology-surface brightness cuts.
 This step removes roughly 97\% of false positives.
-    \item Modeling (Sec. \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
-    \item Completeness and measurement uncertainties (Sec. \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
+    \item Modeling (\S \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
+    \item Completeness and measurement uncertainties (\S \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
 \end{enumerate}
+Our source detection pipeline \href{https://github.com/johnnygreco/hugs}{\code{hugs}} and deblending and modeling code \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} are open-sourced and available online.
 
@@
 We refer the interested readers to \citetalias{Greco2018} for more details.
-Our source detection pipeline \href{https://github.com/johnnygreco/hugs}{\code{hugs}} and \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} are also open-sourced and available online.
 
 \subsubsection{Bright source removal}
-Bright sources and their associated LSB lights can mimic objects of interest and obstruct the detection of LSBGs.
+Bright sources and their associated LSB outskirts can mimic objects of interest and obstruct the detection of LSBGs.
 In this step, we replace pixels related to bright sources and small compact sources with sky noise.
-The bright sources and their diffuse lights are detected in the $i$-band by applying a high thresholding and a low thresholding to the image, respectively.
-We associate a diffuse light component to a bright source if more than 15\% of its pixels are above the high threshold.
-In this way, we generate a footprint of bright sources and their LSB lights.
+The bright sources and their diffuse outskirts are detected in the $i$-band by applying a high thresholding and a low thresholding to the image, respectively.
+We associate a diffuse light component with a bright source if more than 15\% of its pixels are above the high threshold.
+In this way, we generate a footprint of bright sources and their associated LSB components.
 Then for the $gri$-bands, we replace every pixel within this footprint with Gaussian noise, where the noise level is determined by masking out all detected sources in the image.
@@
 We add an extra step to detect and remove them since our main goal is to detect extended LSBGs.
-We run \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} on the ``cleaned'' image as described above.
+We run \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} on the ``cleaned'' images as described above.
 Based on the segmentation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$, and pixels within this mask are also replaced by sky noise.
 This step significantly improves the purity of LSBG search.
-The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by completeness tests (Sec.
-\ref{sec:completeness}).
+The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by the completeness tests (\S \ref{sec:completeness}).
     % This step effectively cleans out objects and features that hinder the detection of LSBGs.
@@
 The images are convolved with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast between LSBGs and sky background \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}.
-We take a mesh size of $43\arcsec$ (doubles the mesh size used in \citetalias{Greco2018} to allow bigger galaxies in our sample) to measure the local background and detect objects that are 0.7$\sigma$ per pixel above the local sky background.
-We also require the object to contain at least 100 contiguous pixels to further remove small compact objects.
+We take a mesh size of $43\arcsec$ (double the mesh size used in \citetalias{Greco2018} to allow bigger galaxies in our sample) to measure the local background and detect objects that are 0.7$\sigma$ per pixel above the local sky background.
+We also require the object to contain at least 100 contiguous pixels (equivalent to a square box with $1.7\arcsec$ on each side) to further remove small compact objects.
 We perform the detection in the $g$-band, but require that all sources are also detected in the $r$-band to exclude spurious detection and artifacts.
@@
 In this step, we take the output catalog from \code{Source Extractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors.
-To be specific, we require objects to have $g$-band half-light radius (measured by \code{Source Extractor}) greater than $r_{\rm min} = 2.0\arcsec$.
+To be specific, we require objects to have $g$-band half-light radii (measured by \code{Source Extractor}) greater than $r_{\rm min} = 2.0\arcsec$.
 We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$.
-This color box is relatively conservative with respect to the color distribution of the discovered LSBGs \citep[e.g.,][]{Greco2018,Zaritsky2019,Tanoglidis2021,SAGA-I}.
-
-Compared with \citetalias{Greco2018}, we add a new metric on morphology of sources to further remove false positives.
-For each source, we compute the ratio of the 2-D autocorrelation function (ACT) within an aperture of 5 pixel and an annulus between 5 pixels and 9 pixels from the center.
-The ACT characterizes the shape, concentration, and spatial correlation of the source.
-We remove sources that have high autocorrelation ratios $a_{\rm corr} > 1.85$.
+This color box is relatively conservative with respect to the color distribution of the discovered LSBGs \citep[e.g.,][]{SAGA-I,Greco2018,Zaritsky2019,Tanoglidis2021}.
+
+Compared with \citetalias{Greco2018}, we add a new metric based on the morphology of sources to further remove false positives.
+For each source, we compute the ratio of the 2-D autocorrelation function (ACT) within an aperture of 5 pixels and the ACT within an annulus between 5 pixels and 9 pixels from the center.
+The ACT ratio essentially characterizes the peakiness of the source.
+Peaky sources have higher ACT ratios, thus we remove point-like sources by applying a cut on ACT ratios $a_{\rm corr} < 2.5$.
 This step helps to improve the purity of our sample.
-\jiaxuan{Jenny and Johnny: can you check if this is meaningful to you?}
 %\textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}
@@
 After these steps, we have an initial sample that contains 86,002 LSBG candidates.
-We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because PDR2 has a better sky subtraction,  our detection is more inclusive for larger objects, and our size cut is less restrictive for small objects.
-Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirri, blended compact sources, etc.
+We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because PDR2 has better sky subtraction, our detection here is more inclusive of larger objects, and our size cut is less restrictive for small objects.
+Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirrus, and blended compact sources.
 Therefore, we perform an extra ``deblending'' step to further remove false positives.
@@
 In \code{scarlet}, each source $k$ in the cutout is described by a morphology matrix $S^k_i$ and a Spectral Energy Distribution (SED) vector $A^k_i$, and the multi-band images is $Y_i$, where $i$ denotes different bands.
-The goal of the modeling is to minimize the objective function $f \propto \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF.
-The morphology matrix of each source is limited to be within a bounding box.
-We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirt (monotonoicity constraint).
+The goal of the modeling is to minimize the objective function $f \propto \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF and $*$ is convolution.
+The morphology matrix of each source is limited by a bounding box.
+We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirts (monotonoicity constraint).
 The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample, this assumption still holds for most cases and provides an easy, sparse, and robust way to deblend overlapping sources.
@@
 
-In vanilla scarlet, objects can be modeled with different types of sources, including point source, single-extended source, multi-extended source, compact-extended source, and flat-sky source.
-The morphology matrix of the point source is simply the normalized PSF.
+In vanilla scarlet, objects can be modeled with different types of models as follows.
+The point source has a morphology matrix simply be the normalized PSF.
 The single-extended source has a morphology matrix that follows positivity and monotonicity constraints.
 The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient.
-The compact-extended source is a single-extended source initialized using the morphology matrix of a point-source, which encourages the model to be compact, but still allows the morphology matrix to be extended.
+The compact source is a single-extended source initialized using the morphology matrix of a point-source, which encourages the model to be compact, but still allows the morphology matrix to be extended.
 The flat-sky source has uniform color and morphology within the bounding box.
 
-Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with positions of detected peaks in the prior steps.
+Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with the positions of detected peaks in the prior steps.
 The models are then optimized subject to the constraints.
@@
 \subsubsection{Peak detection}\label{sec:peak}
-We generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candidate in our initial sample.
+We generate cutout images with a size of $1\arcmin$ in the $griz$-bands for each LSBG candidate in our initial sample.
 We then construct a detection image by taking an average of the four bands weighted by the inverse variance of each band.
@@
 However, there are still faint and compact peaks not detected.
-We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering).
+We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep the high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering).
 Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels.
@@
 
-After peak detection, there are two more things to be determined before optimization.
-We need to know which peaks should be modeled, and we would like to initialize the model as best as we can.
+After peak detection, we need to decide which peaks to modeled, and we would like to initialize the model as best as we can.
 We note that \code{scarlet} optimizes the model instead of deriving the full posteriors, thus good initialization becomes really important.
@@
 The deblending step is designed to model the sources in the vicinity of the target object.
-Therefore, how large and extended is the target object determines which peaks are relevant.
-We draw a square bounding box around the target object and include all the peaks inside this box to be modeled.
-The size of the bounding box is determined as we initialize the model for target object.
-
-We use a multi-extended source with two components to model the target object, such that the model is capable to capture the galaxy structure and color gradient.
+Therefore, the size of the target object determines which peaks are relevant.
+We draw a square bounding box around the target object and model all the peaks inside this box.
+The size of the bounding box is determined as we initialize the model for the target object, described as follows.
+
+We use a multi-extended source with two components to model the target object, such that the model is able to capture the galaxy structure and color gradient.
 The source is initialized as follows.
@@
 Consequently, the size of the bounding box depends on the smoothing kernel and the threshold.
-We choose the above values by trial and error such that the box is not too large to include many irrelevant peaks, but not too small to lose the flux from the target galaxy.
+We choose the above values by trial and error such that the box is not so large as to include many irrelevant peaks, but not so small as to lose the flux from the target galaxy.
 
@@
 
-% As a result of such initialization, we only optimize the object function $f$ defined for sources within the bounding box of the target object. 
-% \textbf{For bright sources? Cookie cutter effect? I don't think cookie cutter is important here.}
-
 \subsubsection{Measurement and false positive removal}\label{sec:non-par-measurement}
@@
 We propose a selection based on size, color, surface brightness and morphology (dashed boxes) to effectively remove false positives but still achieves a high completeness.
-After such cuts (bottom panels), 97\% of false positives and 75\% of non-LSB galaxies are removed according to our visual inspection results.
+After such cuts (bottom panels), 97\% of false positives and 76\% of non-LSB galaxies are removed according to our visual inspection results.
 	}
@@
 Unlike other modeling codes, the non-parametric \code{scarlet} model is very flexible on modeling galaxies with complex structures.
-But the non-parametric nature means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model.
-As shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}, we take out the model of the target object and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}.
+But the non-parametric nature of the code means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model.
+As shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}, we isolate the model of the target object and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}.
 The purpose of this analysis is to extract the structural and morphological parameters of the target object.
@@
 In \code{statmorph}, the effective radius is calculated using elliptical apertures, where the ellipticity $\varepsilon$ is determined by calculating the second moment of the image.
-The total magnitudes are simply calculated by summing up the model in each band, and colors are defined using total magnitudes.\footnote{Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
+The total magnitudes are simply calculated by summing up the model in each band, and colors are defined using total magnitudes.\footnote{A Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
 We define the average surface brightness within the effective radius as $\mu_{\rm eff} = m - 2.5 \log_{10}(2 \pi r_e^2)$, where $m$ is the total magnitude.
@@
 The CAS statistics characterize the concentration $C$, asymmetry $A$, and smoothness $S$ of the light distribution of the object.
-We refer the readers to \citet{statmorph} for more details on their definitions and implementations.
+We refer the reader to \citet{statmorph} for more details on their definitions and implementations.
 The morphological and structural parameters are the same in different bands by construction in the \code{scarlet} model.
 
-To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (Sec \ref{sec:detection}) and use the labels to construct the metrics.
-We randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see Sec \ref{sec:match} for details).
+To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the labels to construct the metrics.
+We randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see \S \ref{sec:match} for details).
 We run vanilla scarlet for all of them and measure morphological parameters as described above.
@@
 Everything else is classified as \code{galaxy}.
-In total, there are 1146 \code{candies}, 2146 \code{galaxies}, and 1708 \code{junk}.
+In total, there are 1153 \code{candies}, 2150 \code{galaxies}, and 1697 \code{junk}.
 
@@
 The distributions of \code{candy} (blue), \code{galaxy} (green), and \code{junk} (red) in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}.
-Although \code{junk} is scattered throughout the parameter space, a large fraction of the junk comprises small things with very red colors, very faint surface brightness, large concentration and large asymmetry.
+Although \code{junk} is scattered throughout the parameter space, a large fraction of the junk comprises small things with very red colors, very low surface brightness, large concentration and large asymmetry.
 Therefore, we come up with the following selection cuts to remove the false positives:
@@
 These criteria (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove objects that are not likely to be LSBGs of interest.
-The color cuts here are narrower than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and background high redshift galaxies.
+The color cuts here are restrictive than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and background high redshift galaxies.
 We not only remove objects with small sizes, but also exclude objects with large size, very low surface brightness, and high concentration.
@@
 With these cuts, 97\% of the false positives are removed, but the majority (70\%) of \code{candy} still remains.
-The number of \code{galaxy} also drops by 75\%.
+The number of \code{galaxy} also drops by 76\%.
 This empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample.
@@
 
-We notice that many other works have been using machine learning (ML) algorithms to classify LSBG candidates and exclude spurious detection.
+Many other works have been using machine learning (ML) algorithms to classify LSBG candidates and exclude spurious detection.
 Among others, \citet{Tanoglidis2021} take the output catalog from \code{Source Extractor} and use the Support Vector Machine algorithm to classify objects in their initial sample and reduce the number of objects that are visually inspected.
 \citet{Zaritsky2019,Zaritsky2021,Zaritsky2022} use convolutional neural networks to classify LSBGs into binary classes based on their images.
-These endeavors certainly help reducing the human labor on visually inspecting tens of thousands of objects.
+These endeavors certainly help reduce the human labor on visually inspecting tens of thousands of objects.
 However, training such a supervised ML algorithm relies on the labeled data which should also sample the parameter space evenly.
@@
 non-LSBG), there will be little way to change later.
-On the contrary, our cuts based on the measured properties can be tweaked to be more complete (including more junks) or be more pure (aggressive cuts) depends on the specific science goal.
-The visual inspections only guide us to design those metrics.
+On the contrary, our cuts based on the measured properties can be tweaked to be more complete (including more junk) or be more pure (aggressive cuts) depending on the specific science goal.
+The visual inspection labels only guide us to design those metrics.
 This measurement-based method is more intuitive, reproducible, and transferable.
-We will also explore machine learning methods and compare with our deblending cuts in future works.
-We would also like to utilize the information about the Milky Way dust to exclude spurious detection on Galactic cirrus \citep{Zaritsky2021,Zaritsky2022}.
+We will also explore machine learning methods and compare with our deblending cuts in future work.
+We would also like to utilize information about Milky Way dust to exclude spurious detection on Galactic cirrus \citep{Zaritsky2021,Zaritsky2022}.
 
@@
 Although the vanilla scarlet modeling provides useful information to help us remove false positives, it does not necessarily give us unbiased estimations on size, color, total magnitude, etc.
-In fact, the vanilla scarlet model usually under-estimates the size and the total flux of LSB objects.
+In fact, the vanilla scarlet model systematically under-estimates the size and the total flux of LSB objects.
 This is because the faint outskirts of LSBGs are typically not modeled well due to the non-parametric nature of vanilla scarlet.
@@
 
-When doing parametric modeling such as \sersic{} fitting, we effectively apply radial averaging within elliptical annulus and boost the SNR by binning pixels.
+When doing parametric modeling such as \sersic{} fitting, we effectively apply radial averaging within elliptical annuli and boost the signal-to-noise ratio by binning pixels.
 In other words, pixels within the same isophotal annulus are assumed to have the same intensity thus are strongly correlated.
 However, the non-parametric nature of vanilla \code{scarlet} only assumes monotonicity, which imposes quite weak correlations among pixels.
-Consequently, it is very hard for the non-parametric modeling to probe down to very low surface brightness features.
+Consequently, it is very hard for the non-parametric modeling to probe very low surface brightness features.
 Furthermore, the monotonicity constraint stops the model from growing in certain directions if there is another source along this direction, otherwise monotonicity is broken.
@@
 To be specific, we follow the spirit of deblending as described in Section \ref{sec:deblending}, but replace the non-parametric model for the target with a parametric model.
-In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized because they are modeled simultaneously.
+In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized because they are modeled simultaneously in all bands with non-parametric models.
 The parametric model for the target object does not suffer from the ``cookie-cutter'' issue any more.
@@
 We use the Spergel surface brightness profile \citep{Spergel2010} to model the LSBGs.
-The Spergel profile is motivated by having a simple analytical expression in the Fourier space, making it easy to be convolved with a PSF\footnote{On the opposite, the \sersic{} profile does not have a simple analytic form in the Fourier space.}.
-The surface brightness of a Spergel profile has a form of
+The Spergel profile is motivated by having a simple analytical expression in Fourier space, making it easy to convolve with a PSF.
+The surface brightness of a Spergel profile has the form:
 \begin{equation}
@@
 The half-light radius is $r_0$, the total luminosity is $L_0$, and $c_\nu$ satisfies the equation $(1 + \nu)f_{\nu + 1}(c_\nu) = 1/4$.
-Similar to the \sersic{} index, the parameter $\nu$ (dubbed as ``Spergel index'') controls the concentration of the light profile.
+Similar to the \sersic{} index, the parameter $\nu$ (dubbed as the ``Spergel index'') controls the concentration of the light profile.
 As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is relevant to the study of LSBGs.
@@
 Peaks within this bounding box (other than the target) are modeled using vanilla scarlet.
-For the target, we still require positivity constraint, and the monotonicity is automatically satisfied by the Spergel profile.
+For the target, we still require a positivity constraint, and the monotonicity is automatically satisfied by the Spergel profile.
 
@@
 
-\textbf{
-Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives. }
-\jiaxuan{Check if this is considered in the completeness.}
+% \textbf{
+% Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives.
+}
+% \jiaxuan{Check if this is considered in the completeness.}
 
 \subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}
-The completeness of the LSBG search is important not only for understanding our searching efficiency and improving the method in the future but also for deriving the completeness-corrected results for LSBG sciences.
-Similar to many other works \citep[e.g.,][]{Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and try to recover them from the image.
+The completeness of the LSBG search is important not only for understanding our search efficiency and improving the method in the future, but also for deriving the completeness-corrected results for LSBG sciences.
+Similar to many other works \citep[e.g.,][]{vdBurg2017,Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and recovering them from the image.
 Using these mock galaxies, we also characterize the measurement bias and uncertainty by comparing the measured properties with the truth.
 
-\subsubsection{Completeness}\label{sec:completeness}
 \begin{figure*}
@@
 We characterize the completeness by injecting mock \sersic{} galaxies into coadd images.
-The overall completeness (right panel) comprises the detection completeness (left panel, see Sec.
-\ref{sec:detection}) and deblending completeness (middle panel, see Sec.
-\ref{sec:deblending}) where false positives are removed.
+The overall completeness (right panel) comprises the detection completeness (left panel, see \S \ref{sec:detection}) and deblending completeness (middle panel, see \S \ref{sec:deblending}) where false positives are removed.
 The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours.
@@
 \end{figure*}
-
-A real LSBG can be missed in the detection step (Sec.
-\ref{sec:detection}) or be excluded in the deblending step (Sec.
-\ref{sec:deblending}).
+\subsubsection{Completeness}\label{sec:completeness}
+A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}).
 Thus, the overall completeness is a combination of detection completeness and deblending completeness.
-We performed a large suite of image simulation to derive the completeness.
+We performed a large suite of image simulations to derive the completeness.
 The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.
@@
 However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}.
-The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$) by resembling the LSBG distribution in \citetalias{Greco2018}.
+To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
 They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
-Then we run the detection step as described in Sec.
-\ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
+Then we run the detection step as described in \S \ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
 We split the size and surface brightness range into 15 bins with $\Delta r_e = 0.86\arcsec$, $\Delta \sbeff = 0.33\ \sbunit$, and interpolate over bins using an isotropic Gaussian kernel with $\sigma = 0.5$.
@@
 We compare our completeness with that of other LSBG searches.
-Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more as increasing size.
-\citet{CarlstenELVES2022} use a similar searching algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$.
+Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more quickly with increasing size.
+\citet{CarlstenELVES2022} use a similar search algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$ assuming a Sersic index $n \approx 1$.
 \citet{vdBurg2017} searched LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
-\citet{Zaritsky2021} focus on searching LSBGs in SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) survey and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$.
-Their low completeness might be explained by the fact that they remove a large fraction of the sky covered by the Galactic dust.
-\citet{Tanoglidis2021} conducted LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
+\citet{Zaritsky2021} focus on searching for LSBGs in the SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) images and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$ for $n=1$.
+Their low completeness might be explained by the fact that they remove a large fraction of the sky contaminated by Galactic dust.
+\citet{Tanoglidis2021} conducted an LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
 \citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but much smaller completeness above $\sbeff > 26.5\ \sbunit$.
-In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies.
-\jiaxuan{also cite dragonfly}
+The Dragonfly Wide Field Survey \citep{Danieli2020} reaches $\sim 29\ \sbunit$ for $>3\sigma$ detection on scales $\sim 1\arcmin$, which is deeper than all other surveys by sacrificing spatial resolution.
+In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies \citep[e.g.,][]{Huang2018,Kado-Fong2018}.
 
 \subsubsection{Measurement bias and uncertainty}\label{sec:meas_unc}
-
-% \begin{figure*}
-% 	\vbox{ 
-% 		\centering
-% 		\includegraphics[width=1\linewidth]{meas_bias.pdf}
-% 	}
-%     \caption{Caption}
-%     \label{fig:meas_bias}
-% \end{figure*}
 
@@
 The colors show the bias term while the dashed contours show the constant uncertainty lines.
-We derive the bias of total magnitudes from the biases of $r_e$, $\sbeff$, and colors consistently.
-We find that the bias and uncertainty of our measurement increase toward the fainter end.
+We derive the bias in the total magnitudes from the combined bias in $r_e$, $\sbeff$, and color.
+We find that the bias and uncertainty in our measurement increase toward the fainter end.
 We apply the bias correction to the real LSBGs before studying their physical properties.}
@@
 We compare the fitting results with the ground truth, and we find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
-For surface brightness fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
-As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than the truths.
-
-Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shapes.
+For surface brightnesses fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
+As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than reality.
+
+Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shape.
 However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index.
@@
 
-Given the size and surface brightness of our simulated galaxies, we set the ranges of the observed size and surface brightness to be $r_e\in[1\arcsec, 15\arcsec],\ \sbeff\in[23, 29]$.
+Given the size and surface brightness of our simulated galaxies, we set the range of the observed size and surface brightness to be $r_e\in[1\arcsec, 15\arcsec],\ \sbeff\in[23, 29]\,\sbunit$.
 We then split the observed $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias $\Delta X = X_{\rm truth} - X_{\rm meas}$ within each bin, where $X=\{\sbeff,\ g-i,\ g-r\}$.
@@
 Then we interpolate over the grid using a multi-quadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
-Unlike \citet{Zaritsky2021} where they fit models in 4-D space, we find interpolation working well enough in the 2-D space and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
+Unlike \citet{Zaritsky2021} where they fit models in 4-D space, we find interpolation works well enough in 2D and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
 We emphasize that the bias and uncertainty are modeled to be functions of the measured properties, not intrinsic ones, such that we can correct for bias based on our measurements.
@@
 It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
-We also find the bias in $g-i$ color quite small.
+We also find the bias in $g-i$ color to be quite small.
 
@@
 
-\jiaxuan{say somewhere in the results section that only SMUDGES measured and corrected measurement bias. vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$}
-
-\section{UDGs and UPGs in Milky-Way analogs}\label{sec:sample_construction}
-The goal of this paper is to study the diffuse galaxies hosted by MW-like galaxies.
-However, one of the major obstacles for studying LSBGs is that it is hard to get distance information.
-Beside direct distance measurements (e.g., SAGA, ELVES, \citealt{Kadowaki2021}), it is common to assume a distance to a dwarf candidate by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
+\section{Mass-size outliers in Milky-Way analogs}\label{sec:sample_construction}
+The goal of this paper is to study the mass-size outliers in the satellite systems around MW-like galaxies.
+However, distance information is needed to convert the observed size and magnitude to the physical size and stellar mass.
+One of the major obstacles for studying LSBGs is that it is hard to get their distance.
+Beside direct distance measurements (e.g., SAGA, ELVES, \citealt{Kadowaki2021}), it is common to assume a distance to a LSBG by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
 A statistical background subtraction is then needed to account for the contribution from background and foreground galaxies.
 Cross-correlation between the LSBG sample and a host galaxy sample can also reveal the distance distribution of LSBGs \citep{Greene2022}.
-These methods are also complemented by machine learning techniques \citep{Baxter2021,xSAGA-I}.
+These methods are also complemented by recent machine learning techniques \citep{Baxter2021,xSAGA-I}.
 In this Section, we cross-match our LSBG catalog with MW-like galaxies in the NSA catalog and construct the UDG and UPG sample.
@@
 The properties of the Milky Way itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016} and the definitions of MW analogs are different among different studies.
-In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig.
+In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$~mag, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig.
 2 in \citealt{SAGA-I}).
 This luminosity range approximately corresponds to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$.
-They also require the MW analogs to be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20--40 Mpc).
+SAGA also requires that the MW analogs be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20--40 Mpc).
 In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$~mag ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA.
@@
 
-Since UDGs are relatively scarce in MW analogs \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics.
+Since mass-size outliers including UDGs are relatively scarce in MW analogs \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics.
 We choose our redshift range to be $0.01 < z < 0.04$, which makes sure that we can detect a significant number of faint dwarf galaxies around MW-like hosts.
-The depth of HSC limits our detection below $z \approx 0.04$ since dwarf galaxies will be too small and too faint to be detected beyond that distance.
-We also exclude galaxies $z<0.01$ because 1) the number of UDGs will be very small due to the small volume; 2) their large angular size makes them more vulnerable to be shredded in the detection, so including them will introduce a number of spurious LSB objects.
+The depth of HSC limits our detection below $z \approx 0.04$ since dwarf galaxies will be too small and too faint to be detected beyond that distance\footnote{Our search only includes objects larger than $r_e\approx 2\arcsec$, which corresponds to $M_\star \sim 10^{8.5}\ M_\odot$ at $z=0.04$ assuming the \textit{average} mass-size relation from \citet{ELVES-I}.
+Going to higher redshift will make it more difficult to detect low-mass dwarfs.}.
+We also exclude galaxies $z<0.01$ because (1) the number of UDGs will be very small due to the small volume; (2) their large angular size makes them more vulnerable to be shredded in the detection, so including them will introduce a number of spurious LSB objects.
 We do not discriminate our hosts to be isolated or paired.
@@
 
-After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 MW-mass galaxies left.
-Then we match them to the initial LSBG sample (described in Section \ref{sec:detection}, before the deblending step) as follows.
-For a given MW analog, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar-halo mass relation in \citet{Behroozi2010}.
-It turns out that 40\% of our hosts have virial radii larger than 300 kpc, which is commonly used as the virial radius of MW.
+After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 MW-mass galaxies.
+We match them to the initial LSBG sample (described in \S \ref{sec:detection}, before the deblending step) as follows.
+For a given MW-like galaxy, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar-to-halo mass relation in \citet{Behroozi2010}.
+It turns out that 40\% of our hosts have virial radii larger than 300 kpc, which is commonly used for the virial radius of our Milky Way.
 Then we identify any LSBG that falls into the projected virial radius of the host on the sky.
@@
 
-However, there are still a significant fraction of spurious objects in this cross-matched LSBG sample, including galactic cirri, tidal streams, shredded large galaxies, compact sources blended with galaxy outskirts, etc.
+However, there are still a significant fraction of spurious objects in this cross-matched LSBG sample, including galactic cirrus, tidal streams, shredded large galaxies, and compact sources blended with galaxy outskirts.
 As described in Section \ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects.
@@
 These LSBGs are matched to MW hosts but do not have direct distance measurements.
-We apply the measurement bias correction (\S \ref{sec:meas_unc}) and assign completeness and important weights after bias correction.
+
+We apply the measurement bias correction (\S \ref{sec:meas_unc}) and assign completeness and importance weights after bias correction.
 In the end, we correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
-In the next subsection, we construct the UDG and UPG samples from the final LSBG sample.
-
-\subsection{UDG and UPG sample}\label{sec:sample}
-\jiaxuan{TODO: make data products (catalogs fake UDGs, website for their images, etc.)}
-The UDG sample is usually defined based on the surface brightness and the physical size of the galaxy.
-However, there are many different criteria in literature: \citep{vanDokkum2015} define UDGs to have effective radius $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}.
-The size criterion also varies from $r_e > 1$ kpc to $r_e > 1.5$ kpc.
-\citet{vanNest2022} explore these definitions and find that different choice of UDG can drastically change the selected subset of dwarfs, therefore affect our understanding of the UDG population.
-
-In practice, the measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020,ELVES-II,Somalwar2020} or other contaminants.
-Therefore in this work, we use the average surface brightness within effective radius $\sbeff$ to define UDGs.
-The difference between the average surface brightness and the central surface brightness can be analytically calculated for a \sersic{} profile: $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
-Since dwarf galaxies and UDGs typically have \sersic{} index of $0.8 < n < 1.2$ \citep[e.g.,][]{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value to convert $\mu_0$ to $\mu_{\mathrm{eff}}$.
-In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, where we also take the $1\sigma$ measurement errors into account.
-This definition maximizes the consistency with the definition in \citet{vanDokkum2015} while not losing UDGs harboring nuclear star clusters.
-
-Among the 2,510 LSBG candidates, there are 432 objects satisfying the UDG definition.
-We did a final visual inspection for these objects and excluded 16 objects that are false positives including blends and Galactic cirri.
-We also removed another 4 objects having completeness less than 0.1.
-In the end, we obtain our UDG sample with 412 objects associated with 258 hosts.
-The total sky area occupied by UDG hosts (out to 1 $R_{\rm{vir}}$) is 32.71 deg$^{2}$.
-
-\vspace{1em}
-
-The concept of UDG was proposed for those dwarf galaxies with unusually large size and diffuse light distribution.
-However, the size of a galaxy is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
-The slope of the mass-size relation in nearby Universe has been shown to be color- and morphology-dependent for galaxies above $M_\star > 10^{9}\ M_\odot$: blue star-forming galaxies have a shallower slope than the red quenched galaxies.
-However, in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$), \citet{ELVES-I} show that the average mass-size relation is quite universal: the slope and intercept are not sensitive to the color or morphology of dwarf galaxies.
+We derive the stellar masses of cross-matched LSBG from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
+\begin{align*}
+&\log \left(M_{\star} / L_{g}\right)=1.774\,(g-r)-0.783, \\
+&\log \left(M_{\star} / L_{g}\right)=1.297\,(g-i)-0.855.
+\end{align*}
+Because we have both $g-r$ and $g-i$ color available from the model fitting, we use the average of the $M_{\star}/L$ derived from the two colors for calculating stellar mass.
+We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}.
+
+\subsection{Mass-size outlier sample}\label{sec:sample}
+The concept of UDG was proposed to describe dwarf galaxies with unusually large size ($r_e>1.5$ kpc) and diffuse light distribution ($\sbcen > 24.0\ \sbunit$).
+Although UDGs are mass-size outliers in some sense, a constant size cut cannot describe the extendedness of every galaxy since the size of a galaxy is strongly correlated with its mass,
+% a defect in the UDG definition is that it ignores the fact that the size of a galaxy is strongly correlated with its mass, 
+known as the mass-size relation \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
+Therefore, a better definition for mass-size outliers should be based on a mass-size relation and its scatter.
+Ideally, galaxies that are $1.5\sigma$ or $2\sigma$ above the average mass-size relation represent the large-size tail of the population in a homogeneous manner.
+Following this thread, we propose such a new definition for mass-size outliers dubbed as \textit{ultra-puffy galaxies} (UPGs).
+In this section, we describe the definitions of UDG and UPG, then we select UDGs and UPGs from our LSBGs matched with MW hosts.
+
+\subsubsection{UPGs}
+To select mass-size outliers, a mass-size relation and its scatter are needed.
+However in general, the slope of the mass-size relation in the nearby Universe has been shown to be color- and morphology-dependent for galaxies above $M_\star > 10^{9}\ M_\odot$: blue star-forming galaxies have a shallower slope than the red quenched galaxies \citep{Lange2015}.
+Fortunately, in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$), \citet{ELVES-I} derive the mass-size relation from the satellites of MW analogs in the Local Volume and show that the average mass-size relation is quite universal: the slope and intercept are not sensitive to the color or morphology of dwarf galaxies.
+The residual from the mass-size relation follows a Gaussian distribution reasonably well.
 This gives us a chance to define a subset of dwarf galaxies that are size-outliers in terms of the average mass-size relation.
-Taking the measured average mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the average mass-size relation.
-We note that the mass-size relation in \citet{ELVES-I} is derived for a mass range of $10^{5.5} < M_\star < 10^{8.5}$.
-We have to extrapolate the mass-size relation to $M_\star \sim 10^9\ M_\odot$ to define our UPG sample.
-
-The UPGs are not absolutely large in physical size or absolutely faint in surface brightness, but they are outliers in size for their stellar masses.
-The definition of UPG based on the observed mass-size relation is more physically-motivated, and UPGs better represent a homogeneous subset of large-size dwarf galaxies.
 It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.
-We discuss the advantages and disadvantages of UDG and UPG in Section \ref{sec:artifact}.
+
+Taking the measured average mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.25\, \log\, (M_\star/M_\odot) + 1.07$ and a scatter of $\sigma=0.18$ dex, we define a population of UPGs to be galaxies that are $>1.5\sigma$ above the average mass-size relation.
+The UPGs are not absolutely large in size or absolutely faint in surface brightness, but they are outliers in size for their stellar masses.
+The definition of UPG based on the observed mass-size relation is more physically-motivated, and better allows us to study size outliers at a given stellar mass.
+We further discuss the advantages and disadvantages of UDG and UPG in Section \ref{sec:artifact}.
 
@@
 We demonstrate the catalog format in Table \ref{tab:catalog}.
-
-The distribution of UDGs and UPGs on the size-surface brightness plane are shown in Figure \ref{fig:udg_upg_re_mu}.
-The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively.
-The two marginal plots show the unnormalized histograms of galaxies in the two color bins.
-The numbers of red and blue galaxies are similar in the UDG sample, but there are more blue galaxies than red ones in the UPG sample.
-Since there is no hard surface brightness cut, the UPG sample includes many blue galaxies with higher surface brightness ($\sbeff > 25$).
-The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26$ because their stellar masses are too high for their sizes to make them being size outliers.
-% they are not LSB (hence low-mass) enough to be higher than $1.5\sigma$ from the mass-size relation.
-
+We note that the mass-size relation in \citet{ELVES-I} is derived for a mass range of $10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$.
+We extrapolate the mass-size relation to $M_\star \sim 10^9\ M_\odot$ to define our UPG sample.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{UDGs}
+Albeit the advantage of UPGs, there are very little literature on UPGs for us to compare.
+Thus, we also select a UDG sample from our LSBGs in order to compare with existing observations and simulations.
+The UDG sample is usually defined based on the surface brightness and the physical size of the galaxy.
+However, there are many different criteria in literature: \citep{vanDokkum2015} define UDGs to have effective radii $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}.
+The size criterion also varies from $r_e > 1$ kpc to $r_e > 1.5$ kpc.
+\citet{vanNest2022} explore these definitions and find that different choice of UDG can drastically change the selected subset of dwarfs, therefore affect our understanding of the UDG population.
+
+In practice, the measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020,ELVES-II,Somalwar2020} or other contaminants.
+Therefore in this work, we use the average surface brightness within an effective radius $\sbeff$ to define UDGs.
+The difference between the average surface brightness and the central surface brightness can be analytically calculated for a \sersic{} profile: $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
+Since dwarf galaxies and UDGs typically have \sersic{} index of $0.8 < n < 1.2$ \citep[e.g.,][]{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value to convert $\mu_0$ to $\mu_{\mathrm{eff}}$.
+In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, where we also take the $1\sigma$ measurement errors into account.
+This definition maximizes the consistency with the definition in \citet{vanDokkum2015} while not losing UDGs harboring nuclear star clusters.
+
+Among the 2,510 LSBG candidates, there are 432 objects satisfying the UDG definition.
+We did a final visual inspection for these objects and excluded 16 objects that are false positives including blends and Galactic cirrus.
+We also removed another 4 objects having completeness less than 0.1.
+In the end, we obtain our UDG sample with 412 objects associated with 258 hosts.
+The total sky area occupied by UDG hosts (out to 1 $R_{\rm{vir}}$) is 32.71 deg$^{2}$.
+We describe the properties of UPGs and UDGs in Section \ref{sec:mass-size}.
+
+\subsection{Background contamination}\label{sec:bkg}
+The major weakness of LSBG searches in imaging data is that distance information is typically unknown.
+Although we have matched LSBGs to MW analogs by proximity, the physical affiliation of LSBGs to the host is not guaranteed.
+As a result, a certain fraction of galaxies in our mass-size outlier sample might just be foreground or background galaxies that fall within the virial radius of the host in projection.
+Given the volume probed by our search, contamination is most likely to be dominated by background galaxies.
+We estimate the contamination fraction as follows.
+The methodology is to study the number of those LSBGs that mimic UPGs and UDGs by randomly matching LSBGs to our MW hosts.
+
+We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2.
+Then we perform the same deblending and modeling steps for the 2,707 LSBGs detected in this region.
+We also removed objects that are already in our mass-size outlier samples, and we did visual inspection to further remove false positives.
+In the end, there are 480 ``real'' LSBGs representing a population of possible contaminants.
+Next, because both UDG and UPG are defined based on physical size, we randomly associate the 480 LSBGs to the hosts of our UDGs and UPGs, respectively.
+Then we calculate a physical size for each LSBG and classify an LSBG as a ``fake`` UDG or UPG if it satisfies the corresponding definition.
+We repeat such random matching 200 times.
+In the end, we obtain 11,458 fake UDGs and 11,867 fake UPGs.
+These UDGs and UPGs are ``fake'' only in the sense of being associated with random MW hosts.
+
+In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.94\pm0.03\ \mathrm{deg}^{-2}$, and the number density of fake UPGs is $S_{\rm UPG} = 2.12\pm0.03\ \mathrm{deg}^{-2}$.
+The catalogs of fake UDG and UPGs are also available online\footnote{\url{https://github.com/AstroJacobLi/kuaizi/tree/master/data}}.
+Using the number densities and the probed area of our survey, we calculate the contamination fraction for both the UDG and UPG samples.
+For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 16\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 20\%$.
+We take the contamination fraction into account when calculating the abundances, size distributions, and radial distributions of the UDGs and UPGs respectively (Section \ref{sec:results}).
+We note that we do not apply any background correction in Figure \ref{fig:mass_size} and Figure \ref{fig:size_distribution} because such correction is in statistical sense.
+
+One of the main goals of this paper is to study the star-forming properties of mass-size outliers in satellites of MW analogs.
+The star formation rate of galaxies can be indicated by their broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs (see \S \ref{sec:quench} for more details).
+However, background contaminants affect the color distribution of the UDG (UPG) sample, and thus affect the calculated quenched fraction.
+If the fake UDGs (UPGs) have different properties from the real ones, we can use this information to derive a probability that an object is a real UDG (UPG) at the proposed distance.
+% If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG.
+Indeed, we find that the $g-i$ color distribution of the fake UDG (UPG) sample is bluer than that of the true UDG (UPG) sample, which motivates us to assign importance weights based on the $g-i$ color.
+Taking UDGs as an example, we first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at the $(g-i)_{k}$ bin) for both true UDG and fake UDG samples.
+Then we multiply $f_{\rm contam}^{\rm UDG}$ with the histogram of fake UDG sample ($\lambda_k^{\rm fake}$) such that the histogram sums up to the average contamination fraction.
+The weight assigned to UDGs in color bin $(g-i)_k$ is estimated to be $w_k = \max\,(1 - f_{\rm contam} \lambda_k^{\rm fake} / \lambda_k^{\rm true}, 0)$.
+This weight stands for a possibility of not being a contaminant.
+The weights of UPGs are assigned following the same procedure.
+We find this color-based contamination subtraction scheme is sufficient for this work since the contamination fraction is small.
+%Our main results shown in Section \ref{sec:quench} are robust against contamination subtraction.
+
+\section{Results}\label{sec:results}
+In this section, we present the statistical analysis of mass-size outliers including UDGs and UPGs associated with MW analogs at $0.01 < z < 0.04$.
+We first compare the distributions of UDGs and UPGs on the size-surface brightness plane and mass-size plane to gain intuition on the differences between UDG and UPG definitions.
+Then we present detailed analysis on the abundance, size distribution, spatial distribution, and quenching for UDGs and UPGs.
+
+\subsection{Properties of mass-size outliers}\label{sec:mass-size}
 \begin{figure*}
@@
 	}
-    \caption{The distribution of galaxies in the ultra-diffuse galaxy (UDG) sample (\textit{left}) and the ultra-puffy galaxy (UPG) sample (\textit{right}).
+    \caption{The distribution of galaxies in the UDG sample (\textit{left}) and the UPG sample (\textit{right}).
 The UDGs are galaxies with $r_e>1.5$ kpc and $\sbeff > 25.0\ \sbunit$.
-The UPGs is defined to be $1.5\sigma$ above the mass-size relation in \citet{ELVES-I}.
+The UPGs is defined to be $1.5\sigma$ above the average mass-size relation in \citet{ELVES-I}.
 We split the samples into two color bins and show them in red ($g-i>0.8$) and blue ($g-i<0.8$).
@@
 
-We derive the stellar masses of UDGs and UPGs from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
-\begin{align*}
-&\log \left(M_{\star} / L_{g}\right)=1.774\,(g-r)-0.783, \\
-&\log \left(M_{\star} / L_{g}\right)=1.297\,(g-i)-0.855.
-\end{align*}
-Because we have both $g-r$ and $g-i$ color available from the model fitting, we use the average of the $M_{\star}/L$ derived from the two colors for calculating stellar mass.
-We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}.
-
-\subsection{Background contamination}\label{sec:bkg}
-The major weakness of LSBG searches in imaging data is that distance information is typically unknown.
-Although we have matched LSBGs to MW analogs by proximity, the physical affiliation of LSBGs to the host is not guaranteed.
-As a result, a certain fraction of galaxies in our UDG and UPG sample might just be foreground or background galaxies that fall within the virial radius of the host in projection.
-Given the volume probed by our search, contamination is most likely to be dominated by background galaxies.
-We estimate the contamination fraction as follows.
-The methodology is to study the number of those LSBGs that mimic UDGs and UPGs by randomly matching LSBGs to our MW hosts.
-
-We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2.
-Then we perform the same deblending and modeling steps for the 2,707 LSBGs detected in this region.
-We also removed objects that are already in our UDG sample, and we did visual inspection to further remove spurious objects.
-In the end, there are 480 LSBGs representing a population of possible contaminants.
-Next, because both UDG and UPG are defined based on physical size, we randomly associate the 480 LSBGs to the hosts of our UDGs (UPGs).
-Then we calculate a physical size for each LSBG and classify an LSBG as a ``fake`` UDG (or UPG) if it satisfies the definition.
-We repeat such random matching for 200 times.
-In the end, we obtain 11,458 fake UDGs and 11,867 fake UPGs.
-These UDGs and UPGs are ``fake'' only in the sense of being associated with random MW hosts.
-
-In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.94\pm0.03\ \mathrm{deg}^{-2}$, and the number density of fake UPGs is $S_{\rm UPG} = 2.12\pm0.03\ \mathrm{deg}^{-2}$.
-The catalogs of fake UDG and UPGs are also available online\footnote{\url{https://github.com/AstroJacobLi/kuaizi/tree/master/data}}.
-Using the number densities and the probed area of our survey, we calculate the contamination fraction for both the UDG and UPG samples.
-For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 16\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 20\%$.
-We take the contamination fraction into account when calculating the abundance, size distribution, radial distribution of UDGs and UPGs in Section \ref{sec:results}.
-We note that we do not apply any background correction in Figure \ref{fig:mass_size} and Figure \ref{fig:size_distribution}.
-
-One of the main goals of this paper is to study the star-forming properties of UDGs and UPGs in MW analogs.
-The star formation rate of galaxies can be indicated by their broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs (see \S \ref{sec:quench} for more discussion).
-However, background contaminants affect the color distribution of the UDG (UPG) sample, thus affect the calculated quenched fraction.
-If the fake UDGs (UPGs) have different properties from the real ones, we can use these information to derive a possibility for an object of being a real UDG (UPG).
-% If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG.
-Indeed, we find that the $g-i$ color distribution of the fake UDG (UPG) sample is bluer than that of the true UDG (UPG) sample, which motivates us to assign importance weights based on the $g-i$ color.
-We first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at the $(g-i)_{k}$ bin) for both true UDG and fake UDG samples.
-Then we multiply $f_{\rm contam}^{\rm UDG}$ with the histogram of fake UDG sample ($\lambda_k^{\rm fake}$) such that the histogram sums up to the average contamination fraction.
-The weights of UDGs in color bin $(g-i)_k$ is estimated to be $w_k = \max\,(1 - f_{\rm contam} \lambda_k^{\rm fake} / \lambda_k^{\rm true}, 0)$.
-This weight stands for a possibility of not being a contaminant.
-The weights of UPGs are assigned following the same procedure.
-We find this color-based contamination subtraction scheme is sufficient for this work since the contamination fraction is small.
-Our main results shown in Section \ref{sec:quench} are robust against contamination subtraction.
-
-\section{Results}\label{sec:results}
-In this section, we present statistical analysis of UDGs and UPGs associated with MW analogs at $0.01 < z < 0.04$.
-
-\subsection{UDG and UPG on the mass-size plane}\label{sec:mass-size}
 \begin{figure*}
@@
 	}
-    \caption{The distributions of the UDG and UPG sample on the mass-size plane.
+    \caption{The distributions of the UDG and UPG samples on the mass-size plane.
 The data points are color-coded by the distance to the quenching color cut.
-Squares are those galaxies satisfying both UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
+Squares are those galaxies satisfying both the UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
     We plot the average mass-size relation (light green) and $1.5\sigma$ above the average relation (dark green) as dashed lines for reference.
 In the left panel, we show the constant surface brightness line as solid lines by assuming two different $g-i$ colors.
-Galaxies falling between these two lines are mostly red and quenched because blue UDGs have too be very large in size to satisfy the surface brightness criterion.
+Galaxies falling between these two lines are mostly red and quenched because blue UDGs have to be very large in size to satisfy the surface brightness criterion.
 This hard surface brightness cut makes the UDG quenched fraction high.
@@
 \end{figure*}
-Since we propose a new subset of LSBGs as UPG, some intuitions on the UPG population and the difference between UDG and UPG are needed.
-In order to build a more comprehensive understanding on our UDG and UPG sample, we show their distributions on the mass-size plane in Figure \ref{fig:mass_size}.
-In the left panel, UDGs that are also classified as UPGs are shown in squares, while UDGs that do not satisfy UPG definition are marked as stars.
+
+In order to build a more comprehensive understanding on our UDG and UPG sample, we show their distributions on the size-surface brightness plane in Figure \ref{fig:udg_upg_re_mu}.
+The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively.
+The two marginal plots show the unnormalized histograms of galaxies in the two color bins.
+The numbers of red and blue galaxies are similar in the UDG sample, but there are more blue galaxies than red ones in the UPG sample.
+Since there is no hard surface brightness cut, the UPG sample includes many blue galaxies with brighter surface brightness ($\sbeff < 25\ \sbunit$).
+The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26$ because their stellar masses are too high for their sizes to make them being size outliers.
+
+In Figure \ref{fig:mass_size}, we show UDGs and UPGs on the mass-size plane.
+In the left panel, UDGs that are also classified as UPGs are shown in squares, while UDGs that do not satisfy the UPG definition are marked as stars.
 In the right panel, triangles correspond to UPGs that are not classified as UDGs.
-To orient the readers on the mass-size plane, we also display the average mass-size relation derived from the satellites of MW analogs in the Local Volume \citep{ELVES-I} as the light green dashed line.
-The darker green line shows $1.5\sigma$ above the average mass-size relation assuming the scatter of the mass-size relation to be $\sigma=0.181$ dex \citep{ELVES-I}.
+To orient the reader to the mass-size plane, we also display the average mass-size relation from \citep{ELVES-I} as the light green dashed line.
+The darker green line shows $1.5\sigma$ above the average mass-size relation assuming the scatter of the mass-size relation to be $\sigma=0.18$ dex \citep{ELVES-I}.
 Because UDGs are defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$, we see a hard cut on size and surface brightness in the left panel.
 We also see that UPGs are all above the $1.5\sigma$ line by construction.
-Comparing the two panels, we find that the UDG sample includes a number of galaxies below $1.5\sigma$ line (highlighted as stars), but also lose a few low-mass galaxies with sizes smaller than 1.5 kpc.
-UDGs below $1.5\sigma$ line have sizes larger than 1.5 kpc, but they are not large enough for their stellar masses.
-It is also noticeable that the UPG sample has a few galaxies with $M_\star > 10^{8.5}\ M_\odot$ which have surface brightness brighter than $25.0\ \sbunit$.
-% As a consequence, the size distribution of UPGs at the smaller end is suppressed as shown in Fig. \ref{fig:size_distribution}.
+Limited by our detection limit and also the fact that our hosts are more distant than LV, our samples only reach to $M_\star \approx 10^{6.8}\ M_\odot$ which is $\sim 1$ dex higher than ELVES.
+
+Comparing the two panels, we find that the UDG sample includes a number of galaxies below the $1.5\sigma$ line (highlighted as stars), but also loses a few low-mass galaxies that are mass-size outliers but have sizes smaller than 1.5 kpc.
+UDGs below the $1.5\sigma$ line have sizes larger than 1.5 kpc, but they are not size outliers for their stellar masses.
+For the UDG sample, the stellar mass range only reaches $M_\star\approx 10^{8.3}\ M_\odot$ because galaxies with higher stellar mass no longer satisfy the surface brightness criterion for UDG.
+On the contrary, the UPG definition does not have a hard surface brightness cut.
+Thus a $M_\star > 10^{8.5}\ M_\odot$ galaxy can get into the UPG sample as long as it has an extraordinarily large size.
+As a consequence, background spiral galaxies could dominate the UPG sample at the high-mass end.
 
@@
 
-\jiaxuan{@Jenny: any other things to mention in this section?}
-
 \subsection{Abundance of UDGs and UPGs}\label{sec:n_udg}
@@
     \caption{The abundance of UDGs as a function of host halo mass.
-\textit{Left}: We compile the UDG abundance measurements from literature covering a wide range of host mass.
+\textit{Left}: We compile the UDG abundance measurements from the literature covering a wide range of host mass.
 The UDG abundance of our work $N_{\rm UDG} = 0.76\pm 0.04$ is shown as red square, the power-law relation from \citet{vdBurg2017} is shown in gray, and our fitting result is shown in pink.
@@
 Therefore the UDG abundance in \citet{SAGA-II} is about $N_{\rm UDG,\, SAGA} \approx 0.17\pm0.07$.
-In the ELVES survey \citep{CarlstenELVES2022}, there are 15 satellites (out of 404 satellites associated with 30 MW analogs) satisfying the UDG definition, leading to a UDG abundance of $N_{\rm UDG,\, ELVES} \approx 0.50\pm0.13$.
+In the ELVES survey \citep{CarlstenELVES2022}, there are 13 UDGs out of 358 satellites with secure distances ($P_{\rm sat} > 0.8$) in 30 MW analogs, leading to a UDG abundance of $N_{\rm UDG,\, ELVES} \approx 0.43\pm0.12$.
 \citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}.
@@
 This might be explained by the different photometric depth of data used.
-As pointed out by \citet{CarlstenELVES2022,Font2022}, SAGA survey reaches a surface brightness depth of $\sbeffr\approx 25\ \sbunit$, which is $\sim 2.5\ \sbunit$ shallower than the ELVES survey and this work.
+As pointed out by \citet{CarlstenELVES2022,Font2022}, the SAGA survey reaches a surface brightness depth of $\sbeffr\approx 25\ \sbunit$, which is $\sim 2.5\ \sbunit$ shallower than the ELVES survey and this work.
 It is probable that SAGA missed a significant fraction of red and lower surface brightness galaxies.
@@
 
-Another interesting quantity is the fraction of UDGs (UPGs) out of all satellites in a group or cluster.
+Another interesting quantity is the fraction of satellites that are mass-size outliers in a group or cluster.
 This fraction represent how efficient an environment is at producing diffuse galaxies.
-We denote this quantity as UDG (UPG) fraction hereafter, which characterizes the tail of the size distribution of satellites.
-In order to calculate this fraction, we assume that MW analogs have $\sim 5$ satellites with $M_\star > 10^{6.5}\ M_\odot$ \citep{CarlstenELVES2022}.
+We denote this quantity as the UDG (UPG) fraction hereafter, which characterizes the tail of the size distribution of satellites.
+In order to calculate this fraction, we assume that MW analogs have $\sim 6$ satellites with $M_\star > 10^{6.5}\ M_\odot$ \citep{CarlstenELVES2022}.
 This lower limit of stellar mass is roughly our detection limit (see Fig.
 \ref{fig:mass_size}).
-Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.15$ and $f_{\rm UPG} \approx 0.12$.
-\jiaxuan{In ELVES, there are 25 UDGs and 27 UPGs out of xxx satellites, so $f_{\rm UDG} \approx xxx$ and $f_{\rm UPG} \approx xxx$.
-The ELVES results are consistent with ours.} We also compare our results with the Virgo cluster.
-Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}), there are 15 UDGs and 24 UPGs out of 404 identified satellites without completeness correction.
-Thus their UDG (UPG) fraction is $f_{\rm UDG,\  Virgo}=0.04$ and $f_{\rm UPG,\ Virgo} = 0.06$.
+Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.15$ and $f_{\rm UPG} \approx 0.10$.
+In ELVES, we take the 351 satellites with secure distances in 30 MW-like hosts and identify 13 UDGs in 10 hosts, and 36 UPGs in 20 hosts.
+Thus the UDG fraction in ELVES is $f_{\rm UDG, ELVES} \approx 0.04$, the UPG fraction in ELVES is $f_{\rm UPG, ELVES} \approx 0.10$.
+We also compare our results with results in the Virgo cluster.
+Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}), there are 15 UDGs and 24 UPGs out of 404 identified satellites with no completeness correction.
+Thus their UDG (UPG) fraction is $f_{\rm UDG,Virgo} \approx 0.04$ and $f_{\rm UPG,Virgo} \approx 0.06$.
 However, we note that \citet{Ferrarese2020} only survey the central 4 deg$^2$ of the Virgo cluster, which probably biases the UDG (UPG) fraction.
+It seems our UDG fraction is higher than both ELVES and NGVS.
+Our UPG fraction is consistent with ELVES but higher than NVGS.
 A more systematic comparison on UDG (UPG) fraction in different environments is needed in the future.
@@
 We find that the power law slope increases as the average halo mass increases.
-It is possible that denser environments provide stronger tidal forces thus produce more smaller UDGs.
+It is possible that denser environments provide stronger tidal forces and thus produce smaller UDGs.
 The UPG size distribution is suppressed at the smaller size end because small galaxies are not $1.5\sigma$ above the mass-size relation.
@@
 The size distribution of UDGs is an important topic since it has been used to test UDG formation scenarios \citep[e.g.,][]{Amorisco2016,vdBurg2017}.
-In this section, we calculate the size distribution of our UDG and UPG sample.
+In this section, we calculate the size distribution of our UDG and UPG samples.
 First of all, we take the fake UDGs in random fields (\S \ref{sec:bkg}) and calculate their size distribution as a proxy for background contamination, shown as the gray dots in the left panel of Figure \ref{fig:size_distribution}.
@@
 Among others, \citet{vdBurg2016} focus on large galaxy clusters and find a very steep slope, \citet{vdBurg2017} includes less-massive groups and the slope is less steep.
-Combined with our findings, it might be possible that dense environment produces more smaller UDGs.
-As we will discuss in Section \ref{sec:discussion}, cluster environments provide stronger tidal fields and thus are more efficient on producing smaller UDGs due to tidal stripping.
+Combined with our findings, it might be possible that dense environment produces relatively more small UDGs, probably due to stronger tidal interactions.
+% As we will discuss in Section \ref{sec:discussion}, cluster environments provide stronger tidal fields and thus are more efficient on producing smaller UDGs due to tidal stripping.
 
 We also show the size distribution of UPGs in the right panel of Figure \ref{fig:size_distribution}.
-As we shown in Figure \ref{fig:mass_size}, the UPG sample does not have those galaxies below the $1.5\sigma$ line but larger than 1.5 kpc.
+As we show in Figure \ref{fig:mass_size}, the UPG sample does not have those galaxies below the $1.5\sigma$ line but larger than 1.5 kpc.
 Therefore, for a given mass, many small UDGs are not in the UPG sample since their sizes are not extreme on the mass-size plane.
@@
     \caption{The radial distributions of UDGs (\textit{left}) and UPGs (\textit{right}).
-We subtract the background contamination (shown in teal) and correct for completeness in each radial distance bin (shown in red).
-We fit the projected NFW and Einasto profiles to the radial distributions and find good fits for both profiles.
+We show the radial distributions after subtracting the background contamination (shown in teal) and correcting for completeness in each radial distance bin (shown in red).
+We fit projected NFW and Einasto profiles to the radial distributions and find good fits for both profiles.
 The radial distributions of UDGs and UPGs are similar in shape.
-The best-fit NFW concentrations is consistent with a MW-mass halo, whereas the best-fit Einasto profiles have smaller concentration than MW-mass halos.}
+The best-fit NFW concentration is consistent with a MW-mass halo, whereas the best-fit Einasto profiles has a smaller concentration than MW-mass halos.}
     \label{fig:radial_distribution}
@@
 Then we average over all hosts and correct for the completeness, as shown in Figure \ref{fig:radial_distribution}.
-Red squares are the number of UDGs (UPGs) per radial bin, and the error includes Poisson error, background subtraction error, and completeness error.
+Red squares are the number of UDGs (UPGs) per radial bin, and the error includes the Poisson, background subtraction, and completeness errors.
 The radial distributions of both UDGs and UPGs turn over around $R=0.2\,R_{\rm vir}$.
 It is known that the detection can be more incomplete as it gets closer to the host due to the blending between UDG and the host galaxy or due to sky subtraction issues.
-Although we have corrected the completeness for each object based on their size and surface brightness, it is still possible that our completeness does not fully characterize the radial dependence of completeness.
+Although we have corrected the completeness for each object based on their size and surface brightness, it is still possible that we have not fully corrected for radial incompleteness within a halo.
 As we mentioned above, it is also possible that UDGs and UPGs are depleted because of tidal disruption.
@@
 The errors in this plot correspond to $1\sigma$ Bernoulli standard error.
-We find that UDGs have high quenched fraction and remains a constant across a decade in stellar mass.
-The quenched fraction of UPGs drops as increasing stellar mass, remarkably similar to that of normal satellites of MW analogs.
+We find that UDGs have a high quenched fraction that remains a constant across a decade in stellar mass.
+The quenched fraction of UPGs drops with increasing satellite stellar mass, remarkably similar to that of normal satellites of MW analogs.
 The quenched fraction is larger for those associated to redder hosts and those that are closer to the host.
@@
     \includegraphics[width=1\linewidth]{quenched_frac_elves.pdf}
-    \caption{A comparison on UPG quenched fractions with ELVES (Greene et al., in prep).}
+    \caption{Quenched fractions of UPGs in this work and in ELVES (Greene et al., in prep).
+Using the same color cut to define quenched galaxies, we calculate the quenched fraction for UPGs in ELVES, shown as the brown line.
+The quenched fraction of UPGs in this work is highlighted in green, while the quenched fraction of the bulk of ELVES satellites is shown in orange \citep{CarlstenELVES2022}.
+We find that ELVES UPG quenched fraction agrees with our results quite well, and we do not find any significant dependence of quenched fraction on the size of satellites by comparing UPGs with the bulk of satellites.
+    }
     \label{fig:qfrac_upg_elves}
 \end{figure}
-The star-forming properties of UDGs and UPGs is an interesting subject given their diffuse stellar component and possible non-trivial formation history.
+
+The star-forming properties of UDGs and UPGs is an interesting subject given their diffuse stellar components and non-trivial formation history.
 In this section, we study the fraction of quenched UDGs and UPGs as a function of both stellar mass and their host properties.
@@
 We refer to quenching as the cessation of star formation in galaxies.
-In principle, direct estimates for the instantaneous star formation rate (SFR) from UV or H$\alpha$ or estimations for the \ion{H}{1} gas are needed to define a quenched galaxy  population.
+In principle, direct estimates of the instantaneous star formation rate (SFR) from UV or H$\alpha$ or estimates for the \ion{H}{1} gas are needed to define a quenched galaxy population.
 As an example, the SAGA survey measures the H$\alpha$ equivalent width (EW) from spectra to define quenched satellites.
 There are also many studies probing \ion{H}{1} masses for MW and M31 satellites \citep[e.g.,][]{Grcevich2009,Spekkens2014,Putman2021}.
-However, these specific data sets are either not deep enough to probe our UDGs and UPGs, or they are very expensive to obtain and cover all the footprint of our sample.
-Therefore, we seek other indicators including integrated color and morphology to approximate star-forming properties.
-\citet{CarlstenELVES2022} visually inspected all satellites and classified them into early-type (red and smooth) and late-type (blue, asymmetric, clumpy).
-Using this sample, they find that a mass-dependent color cut $(g-i)_{Q} = -0.067\, M_V - 0.23$ could also divide the sample into early- and late-type that are nearly identical to the ones based on morphology.
-The derived quenched fractions based on morphology and color are very similar.
+However, these specific data sets are either not deep enough to probe our UDGs and UPGs, or they are very expensive to obtain over the full footprint of our sample.
+Therefore, we seek other indicators for SFR including the integrated color and morphology.
+\citet{CarlstenELVES2022} visually inspected all satellites in the ELVES sample and classified them into early-type (red and smooth) and late-type (blue, asymmetric, clumpy).
+Using this sample, they find that a mass-dependent color cut $(g-i)_{Q} = -0.067\, M_V - 0.23$ could also divide the sample into early-type and late-type that are nearly identical to the ones based on morphology.
+The derived quenched fractions based on morphology and the color cut are very similar.
 Furthermore, \citet{Font2022} showed in simulations that this color cut effectively separates star forming galaxies from quenched ones.
-This makes the color cut more promising since their simulations are not fine tuned to match the observed properties of dwarfs.
-Since we do not visually inspect all UDGs and UPGs in our sample, we take the color cut from \citet{CarlstenELVES2022} to define our quenched galaxies: galaxies that are redder than $g-i > -0.067 M_V - 0.23$ are defined as quenched, whereas those bluer galaxies are thought to be star-forming.
-However, one caveat is that this criterion was derived from LV satellites in \citet{CarlstenELVES2022} and the bulk of them have higher surface brightness and less extended than our UDGs and UPGs.
+This makes the mass-dependent color cut more promising as a proxy for quenching since the simulations in \citet{Font2022} are not fine tuned to match the observed properties of ELVES satellites.
+Because we do not visually inspect all UDGs and UPGs in our sample, we just take the color cut from \citet{CarlstenELVES2022} to define quenched galaxies: UDGs and UPGs that are redder than $(g-i)_Q$ are defined as quenched, whereas those bluer galaxies are thought to be star-forming.
+However, one caveat is that this criterion was derived from LV satellites and the bulk of them have higher surface brightness and smaller size than our UDGs and UPGs.
 It is not guaranteed that the same color cut would work in our regime.
-\footnote{\jiaxuan{Add some robustness tests, such as ``Changing the intercept of the color cut to -0.28 makes the overall quenched fraction higher, but does not change the trend of quenched fraction as a function of stellar mass.''}}
-
-We derive $V$-band apparent magnitude following $V = g - 0.5784\, (g - r) - 0.0038$\footnote{This relation was derived for SDSS filters.
+For comparisons with ELVES and SAGA (Fig.
+\ref{fig:qfrac} and Fig.
+\ref{fig:qfrac_upg_elves}), we use the same color cut to keep the consistency.
+%\footnote{\jiaxuan{Add some robustness tests, such as ``Changing the intercept of the color cut to -0.28 makes the overall quenched fraction higher, but does not change the trend of quenched fraction as a function of stellar mass.''}}
+
+To apply the color cut, we derive the $V$-band apparent magnitude following $V = g - 0.5784\, (g - r) - 0.0038$\footnote{This relation was derived for SDSS filters.
 We neglect the small difference between SDSS and HSC filter systems.
 \url{http://classic.sdss.org/dr4/algorithms/sdssUBVRITransform.html\#Lupton2005}} and convert it to absolute magnitude $M_V$.
-For UDGs (UPGs) in each stellar mass bin, we calculate the fraction of quenched galaxies, but both denominator and numerator are weighted by the weights $w_k$ assigned in Section \ref{sec:bkg} to mitigate the impact of background contamination on quenched fractions.
-We also applied completeness correction.
+Then we divide the stellar mass range $6.4 < \log\,M_\star/M_\odot < 9.0$ into 8 bins and calculate the fraction of quenched galaxies for each bin.
+Both the denominator and numerator are weighted by the importance weights $w_k$ (see \S \ref{sec:bkg}) and corrected for completeness.
+Not applying the importance weights will make the quenched fraction lower since the background contaminants are bluer on average than UDGs and UPGs.
 % We notice that such statistical background subtraction actually raise the quenched fraction since it reduces the impact of contaminants that are bluer in color.
 
-\jiaxuan{Also describe that we don't see a redshift trend. Null trend in redshfit also attest that our sample is not subjecct to background contamination.}
-describe the quenched fraction in percentage, e.g., half of them are quenched at 1e8.
-
 In Figure \ref{fig:qfrac}, the green lines show the quenched fractions $f_q$ as a function of stellar mass for the whole UDG (\textit{left}) and UPG (\textit{right}) samples, and the error bars correspond to the $1\sigma$ Bernoulli standard error.
-The quenched fraction of UDGs is high ($\sim 0.7$) over $6.8 < \log\ M_\star/M_\odot < 8.5$ and weakly depends on the stellar mass.
-On the contrary, as increasing stellar mass, the quenched fraction of UPGs drastically decreases from $f_q \approx 0.8$ at $M_\star = 10^{6.8}\ M_\odot$ to $f_q \approx 0.1$ at $M_\star = 10^{8.5}\ M_\odot$.
+The quenched fraction of UDGs is high ($\sim 0.7$) over the full range of stellar mass ($6.5 < \log\,M_\star/M_\odot < 8$) and only weakly depends on the stellar mass.
+On the contrary, for UPGs, the quenched fraction strongly depends on the stellar mass.
+About 70\% of UPGs are quenched at $M_\star = 10^{6.8}\ M_\odot$, whereas only $\sim20\%$ of them are quenched at $M_\star = 10^{8.5}\ M_\odot$.
+At $M_\star \approx 10^{8}\ M_\odot$, about half of UPGs are quenched.
+This highlights the difference between the UDG and UPG populations.
+However, we argue that the high quenched fraction of UDGs is merely an artifact of the UDG definition, as discussed in Section \ref{sec:artifact}.
+
 We further divide the sample based on the projected radial distance to the host $R/R_{\rm vir}$ (top panels) and the host $g-i$ color (bottom panels).
 As shown in the top panels in Figure \ref{fig:qfrac}, we find that UDGs (UPGs) that are closer to the host have a higher quenched fraction.
-The average difference on quenched fractions between the two radial bins is $\sim 0.1$ for UDG and $\sim 0.2$ for UPG.
-This trend is expected because the density of CGM is higher when it is closer to the host and thus quenches the UDGs (UPGs) via ram pressure stripping more efficiently.
+The average difference in quenched fractions between the two radial bins is $\sim 0.1$ for UDGs and $\sim 0.2$ for UPGs.
+% This trend is expected because the density of CGM is higher when it is closer to the host and thus quenches the UDGs (UPGs) via ram pressure stripping more efficiently.
 The tidal stripping is also stronger as satellites get closer to the host.
@@
 But for UPGs, it seems that the host color impacts less than the distance to the host on the quenched fraction.
-This result might hint at ``galaxy conformity'', which refers to the fact that late-type hosts tend to have more late-type satellites \citep{Weinmann2006}.
-We also split the samples based on host stellar mass, but do not find a significant difference in quenched fractions.
-(echo Jenny's paper)
-
-We compare the quenched fractions of UDGs and UPGs with satellites of MW-mass hosts in the Local Volume (ELVES), in nearby Universe (SAGA), and in numerical simulations.
+% This result might hint at ``galaxy conformity'', which refers to the fact that late-type hosts tend to have more late-type satellites \citep{Weinmann2006}. 
+We also split the samples based on host stellar mass and host redshift, but do not find a significant difference in quenched fractions.
+The null trend with host redshift confirms that our background subtraction is valid.
+
+We compare the quenched fractions of UDGs and UPGs with satellites of MW-mass hosts in the Local Volume (ELVES), nearby Universe (SAGA), and numerical simulations.
+The ELVES sample already incorporates MW and M31 satellites.
 The quenched fractions from ELVES is shown in orange dashed lines, while SAGA results are shown as gray squares.
-The quenched fraction from ELVES and SAGA used the same color cut to define quenched galaxies as we do (see \citealt{CarlstenELVES2022}).
-SAGA quenched fractions are lower than ELVES arguably because SAGA survey is not sensitive to galaxies below $\sbeffr = 25\sbunit$ \citep{Font2022}.
-We also overlie the quenched fraction from ARTEMIS \citep[purple lines,][]{Font2022} and FIRE-2 \citep[pink dotted lines][]{Samuel2022} simulations, where the quenched galaxies are defined as those with no instantaneous (for ARTEMIS) or recent ($<200$ Myr for FIRE-2) star formation.\footnote{\citet{Font2022} find a similar quenched fraction when using the same color cut as we do.} We select ARTEMIS and FIRE-2 because they roughly cover the highest and lowest quenched fraction produced in simulations (see Fig.
-13 in \citealt{Samuel2022}).
-Compared with these results, we see that UDGs have a higher quenched fraction which does not drop as increasing stellar mass.
-Surprisingly, we find that the quenched fraction of UPGs agrees with both local volume observations and simulations quite well, although these results are dominated by the bulk of MW satellites that are not as large as our UPGs.
-
-Compare to ELVES and simulations, our sample spans a narrower range in stellar mass.
-The detection limit in surface brightness and size set the lower bound in stellar mass around $10^{6.8}\ M_\odot$.
-However for UDG sample, it only reaches to $M_\star\approx 10^{8.3}\ M_\odot$ because galaxies with higher stellar mass no longer satisfy the surface brightness cut for UDG.
-On the contrary, the UPG definition does not have a hard surface brightness cut such that $M_\star > 10^{8.5}\ M_\odot$ galaxy can get into the UPG sample as long as having an extraordinarily large size.
-As a consequence, background spiral galaxies could dominate the UPG sample at the high-mass end.
+The quenched fraction from ELVES and SAGA are calculated using the same color cut to define quenched galaxies as we do (see \citealt{CarlstenELVES2022}).
+SAGA quenched fractions are lower than ELVES arguably because SAGA survey is not sensitive to faint red galaxies below $\sbeffr = 25\sbunit$ \citep{CarlstenELVES2022,Font2022}. 
+We also overlie the quenched fractions from the ARTEMIS \citep[purple lines,][]{Font2022} and FIRE-2 \citep[pink dotted lines,][]{Samuel2022} simulations, where the quenched galaxies are defined as those with no instantaneous (for ARTEMIS) or recent ($<200$ Myr for FIRE-2) star formation.\footnote{\citet{Font2022} find a similar quenched fraction when using the color cut as we do.} We select ARTEMIS and FIRE-2 because they roughly cover the highest and lowest quenched fraction for MW satellites produced in simulations (see Fig.
+13 in \citealt{Samuel2022} for a compilation).
+Compared with these results, we see that UDGs have a higher quenched fraction than MW satellites especially at the high stellar mass end.
+Surprisingly, we find that the quenched fraction of UPGs agrees with both
+ELVES and simulations quite well, although these results are dominated by the bulk of MW satellites that are not as large as UPGs.
+
+Furthermore, we calculate the UPG quenched fraction in ELVES using the same color cut and highlight the results in Figure \ref{fig:qfrac_upg_elves}.
+We select 27 UPGs from 313 ELVES satellites with secure distances and their hosts all have coverage to 200 kpc.
+We find that the ELVES UPG quenched fraction agrees with our UPG quenched fraction very well albeit with large scatter.
+By comparing the quenched fraction of the whole ELVES sample with that of UPGs, we do not find any significant trend of quenched fraction on the size of the satellite.
 
@@
 
-\subsection{High and constant quenched fraction of UDGs is an artifact}\label{sec:artifact}
-In Section \ref{sec:quench}, we calculate the quenched fraction as a function of stellar mass for UDGs (left panels in Figure \ref{fig:qfrac}).
-We find that the quenched fraction of UDGs is higher than the quenched fractions of UPGs and the satellite population of MW analogs.
-Furthermore, it remains a constant over $>1$ dex in stellar mass.
-In this subsection, we argue that UDG's high and constant quenched fraction is merely an artifact due to its contrived definition.
-We also discuss the advantages and disadvantages of different definitions of low surface brightness galaxies.
-
-In Figure \ref{fig:mass_size}, we show our UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench})$ indicating how much a galaxy has been quenched.
-As we described in Section \ref{sec:mass-size}, the UDG sample includes a number of galaxies below the $1.5\sigma$ mass-size line.
-Additionally, these galaxies are mostly quenched (having zero or negative $\Delta(\mathrm{Quench})$).
-In order to help understand this phenomenon, we plot constant surface brightness lines of $\sbeff=25.0\ \sbunit$ for two different colors $g-i=0.4$ (blue solid line) and $g-i=0.8$ (red solid line).
+\subsection{A better definition of mass-size outliers}\label{sec:artifact}
+% High and constant quenched fraction of UDGs is an artifact
+In Section \ref{sec:sample_construction}, we have already argued that the hard size cut in UDG definition does not consider the mass-size relation, and we propose UPG which better represent the large-size tail of dwarf galaxy population.
+Here we discuss other defect in UDG definition which is the hard cut in surface brightness regardless of the galaxy color.
+We also discuss the advantages and disadvantages of different definitions of low surface brightness galaxies including UDG and UPG.
+
+In Section \ref{sec:quench}, we find that the quenched fraction of UDGs is higher than the quenched fractions of UPGs and the satellite population of MW analogs.
+Furthermore, it almost remains a constant over $>1.5$ dex in stellar mass.
+We argue that UDG's high and constant quenched fraction is merely an artifact due to its contrived definition.
+We start from Figure \ref{fig:mass_size} where we show UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ indicating how much a galaxy has been quenched (\S \ref{sec:quench}).
+The UDG sample includes a number of galaxies below the $1.5\sigma$ mass-size line, and these galaxies are mostly quenched (having zero or negative $\Delta(\mathrm{Quench})$).
+In order to help understand this phenomenon, we plot constant surface brightness lines of $\sbeff=25.0\ \sbunit$ for two different colors $g-i=0.4$ (blue solid line) and $g-i=0.8$ (red solid line) on the mass-size plane.
 For our redshift range, the cosmological dimming effect is negligible and the surface brightness is a constant with distance.
-For a given size, surface brightness (e.g., $\sbeff=25.0\ \sbunit$), redder galaxies have the same absolute magnitude as blue galaxies, but have larger stellar mass because they have larger mass-to-light ratio than blue galaxies.
-The mass-to-light ratio effect manifests itself on Figure \ref{fig:mass_size} by separating the two constant surface brightness lines apart.
-We recall that the UDG is defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$.
-As a result of the color-M/L relation, the UDG sample includes more red galaxies than blue ones by having a surface brightness cut at $\sbeff=25.0\ \sbunit$, and thus give rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}.
-It is the pathological definition of UDG that makes the quenched fraction high.
-We note that the color-$M_\star/L$ relation are only invoked when converting the absolute magnitude to stellar mass.
-Thus when studying the quenched fraction as a function of absolute magnitudes, the artifact on mass-size plane would disappears on the size-luminosity plane \citep[e.g., see][]{Danieli2019}.
-
-In this paper, we propose an alternative definition for large diffuse galaxies: ultra-puffy galaxies (UPGs).
-They are defined to be $1.5\sigma$ above the average mass-size relation.
-The specific value above the average mass-size relation can be changed to probe different parts of the size distribution.
-As we discussed in Section \ref{sec:sample}, a mass-dependent size cut for diffuse galaxies is more objective than a hard size cut because the average size gets larger as increasing stellar mass.
+For a given size and surface brightness (e.g., $\sbeff=25.0\ \sbunit$), redder galaxies have the same absolute magnitude as blue galaxies, but have higher stellar mass because they have higher mass-to-light ratio than blue galaxies.
+The color-$M_\star/L$ effect manifests itself on Figure \ref{fig:mass_size} by separating the two constant surface brightness lines.
+As a result, the UDG sample includes more red galaxies than blue ones due to the color-independent surface brightness cut at $\sbeff=25.0\ \sbunit$, and thus give rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}.
+It is the definition of UDG that makes the quenched fraction high.
+
+It worth emphasizing that the concept of UDG was originally proposed in a cluster context where the UDGs are mostly red and quenched \citep[e.g.,][]{vanDokkum2015} and the color-$M_\star/L$ effect does not matter that much.
+However, bluer UDGs are found in less dense environments.
+For a given stellar mass, the hard surface brightness cut in UDG definition removes blue galaxies because their surface brightnesses are higher but their $M_\star/L$ are lower than red ones.
+Therefore, the concept of UDG might not be optimal to study the mass-size outliers with different colors in different environments.
+% We note that the color-$M_\star/L$ relation are only invoked when converting the absolute magnitude to stellar mass.
+Thus when studying the quenched fraction on size-luminosity plane (e.g., g-band absolute magnitude), the artifact would disappear \citep[e.g., see][]{Danieli2019}.
+
+In this paper, we advocate an better definition for mass-size outliers: ultra-puffy galaxies (UPGs).
+They are defined to be $1.5\sigma$ above the average mass-size relation in the dwarf galaxy regime.
+The specific value above the average mass-size relation can vary to probe different parts of the size distribution.
+As we discussed in Section \ref{sec:sample}, a mass-dependent size cut for diffuse galaxies is more objective than a hard size cut because the average size gets larger with increasing stellar mass.
 However, the mass-size relation generally depends on the color, morphology, environment, and also redshift of the galaxies \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
@@
 This finding encourages definitions based on the mass-size relation for diffuse galaxies.
-For the UPG population, we show that it has similar quenched fraction as the bulk satellite population of MW analogs (Fig.
-\ref{fig:qfrac}).
-From Fig.
-\ref{fig:mass_size}, it is clear that the UPG definition naturally represents the large-size tail of the mass-size relation without introducing the color-$M_\star/L$ artifacts on stellar mass.
-We thus advocate studying the UPG population and how the properties vary as a function of the puffiness (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).
-
-However, everything comes with a price.
-In order to construct a UPG sample, one need to know the distance information as well as the color to convert observed magnitudes to stellar mass.
-The color-$M_\star/L$ relation also introduces additional uncertainties.
+From Figure \ref{fig:mass_size}, it is clear that the UPG definition naturally represents the large-size tail of the mass-size relation without introducing the artifacts due to the color-$M_\star/L$ relation.
+We further advocate studying the UPG population in both observation and simulation and explore different ``puffiness'' of UPGs (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).
+
+However, in order to construct a UPG sample, one need to know the distance, color, a color-$M_\star/L$ relation to convert observed magnitudes to stellar mass, and a mass-size relation and its scatter.
+None of these are easy to obtain and free from systematic errors.
+On one hand, reliable mass-size relation and its scatter are not available for all mass ranges.
 \citet{ELVES-I} derive the mass-size relation below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$.
-As a result, it is not clear about the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ and how it depends on color and morphology.
+It is not clear about the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ and how it depends on color and morphology.
 In this work, we simply extrapolate \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$.
-But the caveat on mass-size relation could make the UPG definition subject to systematical uncertainties.
-In this work we use the effective radius $r_e$, but other definitions of sizes might reduce the scatter of mass-size relation \citep[e.g.,][]{Miller2019,Trujillo2020} and further benefit the definition of UPGs.
-
-also, it is not clear that mass-size is well-described by a normal distribution in the tails.
-
-Both UDG and UPG represent subsets of dwarf galaxies that are larger and more diffuse than average.
-However, the hard cut on size (1.5 kpc) means that the UDG definition excludes ``large'' galaxies at the lower masses because as stellar mass goes smaller, the average size also gets smaller.
-There is also no color preference in the UPG definition for a given stellar mass.
-The surface brightness cut also biases the UDG sample because of the relation between galaxy color and mass-to-light ratio.
+On the other hand, it is not clear whether the size distribution for a given mass can be well-described by a Gaussian distribution.
+Fig.
+9 in \citet{ELVES-I} shows the residual in $\log(r_e)$ after fitting the mass-size relation, where the distribution of residual is roughly Gaussian but skewed toward the large-size end.
+With enough statistics in the future, one might be able to characterize the shape of large-size tail batter and define UPGs based on the percentiles of the size distribution.
+However, there are also other size definitions which help reduce the scatter of mass-size relation \citep[e.g.,][]{Miller2019,Trujillo2020} and can further benefit construct UPG samples.
+
+In the right panel of Figure \ref{fig:mass_size}, we also plot the constant average surface mass density lines, which is steeper than the mass-size relation but have the same slope as constant surface brightness lines.
+Hence another way to define diffuse galaxies is to select galaxies with low surface mass density.
+This method also alleviates the artifact introduced by color-$M_\star/L$ relation on the mass-size plane.
+We defer such studies to future works.
 
 % Find literature for quenched fraction as a function of distance to host (Einasto 1974, Spekkens2014, Karunakaran2022 for MW and M31).
-
-% SAGA misses a fraction of red faint galaxies in their initial detection catalogs. This also explains the low quenched fraction of SAGA \citep{CarlstenELVES2022}.
-% SAGA SB limit is 25. ARTEMIS is able to reproduce SAGA quenched fraction.
-
-% \jiaxuan{UPG help us define mass-size lognormal, more diverse environment. distances.}
 
@@
 In this paper, one surprising finding is that although UPGs have extremely large size for their stellar mass, they have similar quiescent fraction as normal satellites in MW analogs.
-In ELVES, Greene et al.
-(in prep) also find no trend of quenched fraction on size.
-\citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology (equivalently color) of satellites, suggesting that the quenching and morphological transformation involves very mild size evolution.
-Perhaps quenching and size growth happen separately.
+This is also confirmed by comparing ELVES UPGs with the bulk of ELVES (Fig.
+\ref{fig:qfrac_upg_elves}).
+\citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology or color of satellites, suggesting that the quenching and morphological transformation involves very mild size evolution.
+Together with our results, it is possible that quenching and size growth happen separately.
 Then the question is what physics is responsible for the two processes respectively.
-In this section, we first review the quenching of MW satellites and the mechanisms for puffing up normal dwarfs to produce UDGs (UPGs).
+In this section, we first review the quenching of MW satellites and the mechanisms to puff up normal dwarfs to make outliers with respect to the average mass-size relation.
 Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs.
-\jiaxuan{Cite the \citet{Pan2022} paper}
 
@@
 Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are more quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,Baxter2021,CarlstenELVES2022,Karunakaran2022}.
-This difference hints that the MW environments play an important role in regulating the star formation activities in dwarf galaxies.
-There have been extensive works using simulations to study the quenching of satellites in MW analogs \citep[e.g.,][]{Simpson2018,Buck2019,Garrison-Kimmel2019,Simons2020,Joshi2021,Akins2021,Karunakaran2021,Font2022,Samuel2022}, and many of them are able to reproduce the observed quenched fraction in the Local Group and in the Local Volume.
+This difference hints that environment plays an important role in regulating the star formation activities in satellite galaxies \citep{Peng2010}.
+There have been extensive works using simulations to study the quenching of satellites in MW analogs \citep[e.g.,][]{Simpson2018,Buck2019,Garrison-Kimmel2019,Simons2020,Joshi2021,Akins2021,Karunakaran2021,Font2022,Samuel2022,Pan2022}, and many of them are able to reproduce the observed quenched fraction in the Local Group and in the Local Volume.
 
 In theory, satellite galaxies in MW analogs are accreted from the field, therefore quenching can happen either before or after the infall to MW host.
-In the former case, isolated dwarf galaxies can be quenched by bursty stellar feedback \citep[e.g.,][]{Bahe2015,Kazantzidis2017,ElBadry2018}, reionization \citep[e.g.,][]{Bullock2000,Benson2002,Somerville2002,Tollerud2018,Applebaum2021}, or being backsplash satellites \citep{Simpson2018,Benavides2021}.
-If a satellite is star-forming before infall, the ram pressure \citep[e.g.,][]{GunnGott1972,McCarthy2008,Simpson2018,Tremmel2020,Samuel2022} experienced by the satellite as it moves through the hot circumgalactic medium (CGM) of the host could remove the gas and cause the cessation of star formation.
+In the former case, isolated dwarf galaxies can be quenched by bursty stellar feedback \citep[e.g.,][]{Bahe2015,Kazantzidis2017,ElBadry2018}, reionization for ultra-faint dwarfs \citep[e.g.,][]{Bullock2000,Benson2002,Somerville2002,Tollerud2018,Applebaum2021}, or spending time within a more massive halo, as in the case of so-called backsplash galaxies \citep{Simpson2018,Benavides2021}.
+If a satellite is star-forming before infall, the ram pressure \citep[e.g.,][]{GunnGott1972,McCarthy2008,Emerick2016,Simpson2018,Tremmel2020,Samuel2022} experienced by the satellite as it moves through the hot circumgalactic medium (CGM) of the host could remove the gas and cause the cessation of star formation.
 It has been shown that ram pressure stripping can
@@
 Another quenching mechanism is the so-called preprocessing in a lower-mass group prior to the infall into a MW analog \citep{Wetzel2015b,Jahn2022,Samuel2022}.
-Satellites might be quenched in the previous group via ram pressure striping or tidal interactions, and gas distribution can also be altered in preprocessing even without being quenched.
+Satellites might be quenched in the previous group via ram pressure stripping or tidal interactions, and the gas distribution can also be altered in preprocessing without being quenched.
 \citet{Samuel2022} show that 40\% of satellites were preprocessed before the infall to MW.
@@
 Analytical models also support a scenario where UDGs originate from a population of dwarf galaxies residing in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Rong2017,Liao2019}.
-\citet{Wright2021} show that field UDGs can also be formed from major mergers that cause star formation to
-migrate outward.
+\citet{Wright2021} show that field UDGs can also be formed from major mergers that cause star formation to migrate outward.
 For UDGs in groups and clusters, environmental effects are more pronounced and tidal interactions are believed to puff up normal dwarfs.
@@
 \citet{Tremmel2020} study UDG formation in the cluster environment and find UDGs with higher mass ($M_\star > 10^{8}\ M_\odot$) are puffed up suddenly due to tidal heating at pericenter, but UDGs with lower mass ($M_\star \sim 10^{7.5}\ M_\odot$) are gradually puffed up due to adiabatic expansion as a response to the mass loss from tidal stripping and ram pressures stripping.
-\citet{Kado-Fong2021} study the intrinsic shape of UDGs in observations and find the inferred shapes agree with merger scenario for field UDGs \citep{Wright2021} and tidal heating/adiabatic expansion for group/cluster UDGs \citep{Jiang2019,Tremmel2020}.
+\citet{Kado-Fong2021} study the intrinsic shapes of UDGs in observations and find the inferred shapes agree with merger scenario for field UDGs \citep{Wright2021} and tidal heating/adiabatic expansion for group/cluster UDGs \citep{Jiang2019,Tremmel2020}, but the intrinsic shapes of field UDGs are similar to those of cluster UDGs.
 
@@
 \citet{Jiang2019} argue that if tidal stripping dominates the quenching, the satellite closer to the host will have smaller stellar mass and effective radius since stars are also stripped.
-They find no such trend in simulation, but find that the average color is redder when the UDGs closer to the host, supporting that ram pressure stripping is more dominant.
+They find no such trend in simulation for group environments, but find that the average color is redder when the UDGs are closer to the host, supporting that ram pressure stripping is more dominant.
 In Section \ref{sec:size_distr}, we split the sample into two radial distance bins, and we do not find significant change in size or stellar mass distribution as UDGs get closer to the host.
@@
 In Figure \ref{fig:qfrac}, by comparing UDGs and UPGs at two radial bins, we find a very similar trend that UDGs (UPGs) closer to the host are more quiescent.
-In the ram pressure stripping picture, this is because the density of CGM increases when being closer to the host and the ram pressure is stronger.
+% In the ram pressure stripping picture, this is because the density of CGM increases when being closer to the host and the ram pressure is stronger. 
 Together with the null trend on size and stellar mass distribution as UDGs (UPGs) get closer to their hosts, our findings support that ram pressure stripping is the major quenching channel for UDGs (UPGs) in MW analogs.
 
-%Combining all these factors together, returning backsplash galaxies can also exhibit as other satellites.
-
-If UDGs and UPGs are quenched by ram pressure stripping, how are they puffed up?
+If UPGs are quenched by ram pressure stripping, how are they puffed up such that the quenching and size growth happen separately?
 UPGs can be puffed during the infall or prior to the infall.
-If UPGs are accreted into MW hosts from the field as normal dwarfs and puffed up due to tidal heating, we might expect a higher quenched fraction since they must undergo more violent tidal interactions, and the ram pressure is also stronger at distances closer to the host.
-If they are puffed up through longer-term adiabatic expansion from mass loss, the expansion should also be proportional to the amount of gas loss, which translates to quenched fraction.
-Therefore, tidal puffing during infall seems to contradict with the normal quenched fraction as seen in Figure \ref{fig:qfrac}.
-
-It is more feasible that UPGs are already puffed up before accretion and remain being star-forming.
-They are quenched by ram pressure stripping in the MW host with other normal satellites.
-In order to achieve similar quenched fraction as normal satellites, field UPGs prior to infall have to be star forming.
-Bursty star formation, early merger, higher halo spin, and preprocessing can all puff up the field dwarfs to become UPGs, and some of them seem not to quench the UPGs.
+If UPGs are accreted into MW hosts from the field as normal dwarfs and puffed up due to tidal heating near pericenter passages, we might expect a higher quenched fraction since they also undergo violent ram pressure stripping.
+If they are puffed up through a longer-term adiabatic expansion from the mass loss due to tidal stripping, the expansion should also be proportional to the amount of gas loss, which translates to quenched fraction.
+Therefore, tidal puffing during infall seems to contradict with the quenched fraction as seen in Figure \ref{fig:qfrac_upg_elves}.
+
+It is more feasible that UPGs are already puffed up and remain star-forming before accretion.
+They are quenched by ram pressure stripping in the MW host together with other normal satellites.
+In order to achieve similar quenched fraction as normal satellites, field UPGs prior to infall have to be star-forming.
+Stellar feedback, early merger, higher halo spin, and preprocessing can all puff up the field dwarfs to become UPGs, and some of them seem not to quench the UPGs.
 \citet{Wright2021} show that early merger does not significantly change the total SFR.
@@
 Although it is not clear whether the high halo spin is the cause or the consequence of UPG formation, it is probable that higher halo spin does not quench a UPG.
-If any of these mechanisms can only increase the size to make UPGs but not quench them, it provides a plausible way to produce the observed trend in Fig.
-\ref{fig:qfrac} where quenching and size growth are decoupled.
-However, the efficiency of ram pressure stripping also depends on the stellar mass density which provides the restoring force.
+If any of these mechanisms can only increase the size to make UPGs but not quench them, it provides a plausible way to produce the observed trend in Figure \ref{fig:qfrac} and Figure \ref{fig:qfrac_upg_elves}.
+
+However, the efficiency of ram pressure stripping also depends on the stellar mass density which provides the restoring force and the gas mass density.
 The diffuse stellar component might make UPGs more vulnerable to ram pressure stripping and tidal stripping.
-It is also possible that UPGs in MW analogs are a mixture of field UPGs and normal dwarfs puffed up during infall.
+Kado-Fong et al.
+(submitted) find that although UDGs have a diffuse stellar component, they harbor the same amount of \ion{H}{1} for their size as normal dwarfs.
+Therefore, for a given stellar mass, UDGs (UPGs) have higher \ion{H}{1} mass than normal dwarfs, thus even if UDGs and UPGs are more vulnerable to ram pressure stripping, there is more gas to be stripped.
+It is probable that the net effect of low stellar mass density and high \ion{H}{1} mass is that UPGs have similar quenched fraction as normal satellites.
+
+UPGs in MW analogs can also be a mixture of field UPGs and normal dwarfs puffed up during infall.
 Using our observations, it is hard to sort out detailed mechanisms for quenching and size growth of UPGs.
@@
 
-\jiaxuan{Discuss the UDG fraction v.s. group mass game. How environment shapes the size distribution.}
+% \jiaxuan{Discuss the UDG fraction v.s. group mass game. How environment shapes the size distribution.}
 
 % \citet{Wright2021} observed a temporary boost in spin after the early merger. 
-\citet{Liao2019} find that blue field UDGs indeed have higher halo spins.
-If field UDGs (UPGs) are born in high spin halos, they might have similar SFR as normal field dwarfs.
-
 % \citet{Samuel2022} show that 40\% of satellites were in another group prior to the infall to MW, and preprocessed satellites have higher quenched fraction, and 10\% were quenched during preprocessing.
-\jiaxuan{Do we need to discuss splashback anywhere?}
 
@@
 
-% Galaxy conformity: mass-size independent of color, jenny's quenched fraction independent of morph.
-
-% Scenarios:
-% 1. violent environmental effects: radial orbits, back-splash both explain large size and quenching. But according to Bernavidis et al, the quenched fraction drops with increasing mass.
-
-% 2. accreting field UDGs, and quench them due to ram pressure stripping. But how long do accreted UDGs last before being destroyed? Need to look at ram pressure stripping literature.
-
-% Homework:
-% 1. Move the stellar mass bin definition, try to match with red/blue, spiral/elliptical plot. If cannot match, does this hint the formation scenarios?
-% 2. How significant do we detect blue UDGs? 
-% 3. Split into redshift bins
-
-% UDG rejuvenate after ram pressure stripping?
-
 % calculate probability of being a backsplash satellite (e.g., splashed to 1.5 Mpc)
 % Compare spatial distribution with normal dwarf? iF they are indeed high-spin tail of normal dwarfs.
-% Host-to-host variation
 
 \section{Summary}\label{sec:summary}
+In this work, we present a comprehensive study for mass-size outliers including ultra-diffuse galaxies and ultra-puffy galaxies around Milky Way analogs at $0.01 < z < 0.04$.
+
+We summarize our main findings and prospects below.
+
 \begin{itemize}
-    \item we advocate studies for the quenched fraction as a function of size in simulations
-
-    \item Future works: nucleation, intrinsic shape, LSBG cross-correlation, unsupervised machine learning, color gradient, non-par shapes. 
+    \item Using the HSC PDR2 data ($\sim 300\ \mathrm{deg}^{2}$), we conduct a systematic search for LSBGs using the method in \citet{Greco2018} complemented by our new deblending and modeling methods.
+Utilizing the non-parametric models generated by \code{scarlet}, we design a metric based on morphological parameters to effectively rule out false positives in the LSBG detection.
+We measure the structural properties of LSBGs using Spergel profiles and carefully characterize the measurement biases and uncertainties.
+The completeness of the search is also derived by injecting mock galaxies.
+Our LSBG search achieves high completeness among other searches and demonstrate the power of HSC data on LSB sciences.
+
+    \item By matching LSBGs with MW analogs in NSA catalog, we construct samples of mass-size outliers
+
+    \item their abundance
+
+    \item their size and radial distribution
+
+    \item their quenched fraction
+
 \end{itemize}
 
+we advocate studies for the quenched fraction as a function of size in simulations
+
+Future works: nucleation, intrinsic shape, also the full LSBG sample of Johnny, LSBG cross-correlation, unsupervised machine learning, color gradient, non-par shapes.
+
 \section*{Acknowledgment}
-JL is grateful for discussions with Meng Gu, XXX, XXXX. The authors thank Yao-Yuan Mao for his tool for visualizing image cutouts.
+JL is grateful for discussions with Meng Gu, ChangHoon Hahn. The authors thank Yao-Yuan Mao for his tool for visualizing the image cutouts.
 

### 2022-09-08 main.tex
very ugly summary

@@
 \section{Summary}\label{sec:summary}
-In this work, we present a comprehensive study for mass-size outliers including ultra-diffuse galaxies and ultra-puffy galaxies around Milky Way analogs at $0.01 < z < 0.04$.
-
+In this work, we present a comprehensive study for mass-size outliers around Milky Way analogs at $0.01 < z < 0.04$.
+Beside the ultra-diffuse galaxies, we propose studying ``ultra-puffy galaxies'' which is defined to be $1.5\sigma$ above the average mass-size relation.
+We conduct statistical analysis for mass-size outliers and argue that UPGs better represent the large-size tail of the dwarf galaxy population.
+Surprisingly, we find that UPGs have similar quenched fraction as the bulk of MW satellites.
 We summarize our main findings and prospects below.
 
-\begin{itemize}
+\begin{enumerate}
+
+% \begin{itemize}
     \item Using the HSC PDR2 data ($\sim 300\ \mathrm{deg}^{2}$), we conduct a systematic search for LSBGs using the method in \citet{Greco2018} complemented by our new deblending and modeling methods.
@@
 
-    \item By matching LSBGs with MW analogs in NSA catalog, we construct samples of mass-size outliers
-
-    \item their abundance
-
-    \item their size and radial distribution
-
-    \item their quenched fraction
-
-\end{itemize}
-
-we advocate studies for the quenched fraction as a function of size in simulations
-
-Future works: nucleation, intrinsic shape, also the full LSBG sample of Johnny, LSBG cross-correlation, unsupervised machine learning, color gradient, non-par shapes.
+    \item By matching LSBGs with MW analogs in NSA catalog, we construct samples of mass-size outliers including UDGs and UPGs.
+We display their distributions on the size-surface brightness plane (Figure \ref{fig:udg_upg_re_mu}) and the mass-size plane (Figure \ref{fig:mass_size}).
+The UPG sample contains more bluer and higher surface brightness galaxies than the UDG sample.
+Instead, the UDG sample includes many red galaxies below $1.5\sigma$ from the average mass-size relation.
+
+    \item After correcting for background contamination, the UDG abundance in MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host and the UPG abundance is $N_{\rm UPG} = 0.61 \pm 0.04$ per host.
+Our UDG abundance is slightly higher than that in ELVES, but much higher than that in SAGA.
+Combining data from studies in denser environments, we find that the UDG abundance follows a sublinear power law with the host halo mass.
+    \item We find the size distribution of UDGs follows a power law $n\propto r_e^{-1.60\pm0.21}$ which is shallower than the UDG size distribution in larger groups and clusters \citep{vdBurg2016,vdBurg2017}.
+We do not find significant dependence of size distribution on host stellar mass or the distance to host.
+The UPG size follows a unimodal distribution peaks at $\sim 2.5$ kpc.
+
+    \item The radial distributions of UDGs and UPGs from their hosts can be described by projected NFW and Einasto profiles.
+We find that the best-fit NFW profiles are consistent with the NFW profile of a MW-mass halo, whereas the best-fit Einasto profiles have smaller concentrations than MW halos.
+The UDG and UPG follow similar radial distributions.
+
+    \item We find that UDGs have high quenched fractions ($\sim 70\%$) and remain constant over 1.5 dex in satellite stellar mass (Figure \ref{fig:qfrac}).
+For UPGs, the quenched fraction is high at the lower-mass end $M_\star = 10^{6.8}\ M_\odot$, but the quenched fraction drops to $\sim 20\%$ at $M_\star = 10^{8.5}\ M_\odot$.
+Almost half of UPGs are quenched at $M_\star \approx 10^{8}\ M_\odot$.
+The quenched fractions of both UDGs and UPGs increase as satellites get closer to the hosts.
+Redder hosts also harbor more quenched UDGs and UPGs.
+
+    \item Surprisingly, the quenched fraction of UPGs is very similar to the quenched fraction of the ``normal'' satellites in ELVES, although UPGs are mass-size outliers (Figure \ref{fig:qfrac_upg_elves}).
+We select ELVES UPGs and find they also have similar quenched fractions.
+The UPG quenched fraction also agrees with simulations (e.g., ARTEMIS \citealt{Font2022}, FIRE-2 \citealt{Samuel2022}) focusing on the bulk of MW satellites.
+The null trend of quenched fraction on the size of satellites indicates that quenching and size evolution of mass-size outliers happen separately in MW-like environments.
+It is plausible that these mass-size outliers are puffed up in the field before accretion, and quenched together with other MW satellites.
+
+    \item We argue that the high and constant quenched fraction for UDGs is merely an artifact of the UDG definition which does not consider the color-$M_\star/L$ relation.
+We advocate studying UPG which is more physically motivated, does not introduce artifacts in the mass-size distribution, and better represents the large-size tail of dwarf galaxy population.
+% \end{itemize}
+\end{enumerate}
+
+This study on mass-size outliers only explores a small subset of LSBG candidates detected in HSC PDR2.
+In future works, we would like to exploit the full sample to study interesting topics including redshift distributions, nucleation fractions, intrinsic shapes of LSBGs.
+We will also explore machine learning techniques to help us classify LSBGs and estimate structural parameters.
+With the upcoming Vera Rubin Observatory Legacy Survey of Space and Time \citep[LSST, ][]{lsst2009,LSST2019}, we will be able to study the LSBG population with much greater statistics and gain new insights on the formation and evolution of mass-size outliers.
 

### 2022-09-13 main.tex
before co-author's comments

@@
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-\author[0000-0002-2704-5028]{Remy Joseph}
-\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+
 \author[0000-0002-1841-2252]{Rachael Beaton}
@@
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+\author[0000-0002-2704-5028]{Remy Joseph}
+\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
 \author[0000-0002-1841-2252]{Erin Kado-Fong}
@@
 \begin{abstract}
-\jiaxuan{Need to rewrite abstract}
-Ultra-diffuse galaxies (UDGs) are dwarf galaxies with extreme sizes and low surface brightness.
-The formation and quenching mechanisms of these intriguing objects are still under debate.
-In this work, we present systematic search for ultra-diffuse galaxies associated with Milky Way (MW) analogs in the nearby Universe ($0.01 < z < 0.04$) using the Hyper Suprime-Cam Strategic Survey Program data.
-We also define a new subset of low surface brightness galaxies dubbed as ``ultra-puffy galaxies'' (UPGs) which better characterize the size outliers on the mass-size plane.
-We perform statistical studies for UDGs and UPGs and compare the results with previous studies for UDGs in clusters and groups.
-We further contrast UDGs and UPGs with the bulk of MW satellites in nearby Universe and simulations.
-We find that UDGs have a higher quenched fraction than MW satellites and the quenched fraction remains constant over 1 dex in stellar mass.
-We argue that this high quiescent fraction is an artifact of the UDG definition.
-Despite their large sizes, UPGs in MW analogs have similar quenched fractions as the bulk satellites.
-These results hint that the size growth and quenching of UPGs must happen separately.
+Large diffuse galaxies are hard to find, but understanding their environments and abundance, and ultimately their origins, is of intense interest.
+Using the Hyper Suprime-Cam Strategic Survey, we search for low surface-brightness galaxies and match them to Milky-Way like hosts in projection.
+We build a statistical sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way-mass galaxies in the nearby Universe ($0.01 < z < 0.04$).
+The number of these ``ultra-puffy'' galaxies per host is comparable to the observed abundance  at this halo mass in the Local Volume, and the galaxies follow an NFW profile around their halos.
+We argue that our definition, based on the mass-size relation, is more robust than the literature ultra-diffuse galaxy definition, which depends on surface brightness and thus yields different surface mass density cuts for quenched and star-forming galaxies.
+With our mass-size--based definition, we show that despite their extended size, the quenched fraction is comparable at a given satellite stellar mass between the ultra-puffy and normal dwarfs in MW-mass halo.
+These results hint that the size growth and quenching of mass-size outliers must happen separately.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-In a variety of galaxy populations, an interesting subset of galaxies with low surface brightness and large physical size have been identified in the past \citep[dubbed as LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
-Recently, new excitement was generated by the discovery by \citet{vanDokkum2015} of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and fields \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
-There have been a variety of studies of these extremely-diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022}, and stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
-The UDGs are dwarf galaxies with larger size ($r_e > 1.5$ kpc) and lower surface brightness ($\sbcen > 24.0\ \sbunit$) than normal dwarfs, thus are outliers from the average mass-size relation.
-Therefore, a central question about mass-size outliers including UDGs is what physical mechanisms are responsible for the formation and quenching of these large diffuse galaxies.
-
-% In \citet{vanDokkum2015}, the ultra-diffuse galaxies (UDGs) are defined as dwarf galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$).
+In a variety of galaxy populations, an interesting subset of galaxies with low surface brightness and large physical size have been identified \citep[dubbed as low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
+Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015} , accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
+There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
+The UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus are very large in size for their stellar mass.
+Therefore, a central questions about LSBGs, including UDGs, is what causes them to be outliers from the mass-size relation.
+% Therefore, a central question about mass-size outliers including UDGs is what physical mechanisms are responsible for the formation and quenching of these large diffuse galaxies.
 
 Different mechanisms are proposed to explain the presence of large diffuse galaxies in different environments.
-Field UDGs might form after star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or they were born in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019}.
-UDGs in groups and clusters are believed to be puffed up by tidal heating near pericenter \citep{Jiang2019} or to undergo adiabatic expansion due to mass loss \citep{Tremmel2020}.
+In the field, large size might be caused by star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or the galaxies inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019}.
+In groups and clusters, the large size may ensue from tidal heating near pericenter \citep{Jiang2019} or via adiabatic expansion due to mass loss \citep{Tremmel2020}.
 Despite theoretical advances, it is still an open question how mass-size outliers like UDGs in certain environments are formed and quenched.
 It is also unclear whether mass-size outliers belong to a special class of galaxy or are just a natural extension of dwarf systems to lower surface brightness.
-To answer these questions, we can compare mass-size outliers with the ``normal'' satellites which we have a better understanding.
-
-Our best knowledge in the dwarf galaxy regime is about the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}.
+To answer these questions, we can compare mass-size outliers with the ``normal'' satellites for which we have a better understanding.
+
+Our best knowledge in the dwarf satellite regime is about the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}.
 With the advent of deep sky surveys and dedicated spectroscopy programs, we are now mapping the satellite systems of MW analogs in the Local Volume and nearby Universe.
@@
 The goal of this paper is to study large diffuse galaxies in the reference frame of the satellite systems of MW analogs and try to elucidate their formation and quenching.
-Albeit large size and low surface brightness, UDGs are not necessarily mass-size outliers in terms of their offsets to the average mass-size relation (see \S \ref{sec:sample_construction}).
-Motivated by this fact, we propose studying ``ultra-puffy galaxies'' (UPGs) which are $1.5\sigma$ above the average mass-size relation, representing the large-size tail of the dwarf galaxy population.
-Using the Hyper-Suprime Camera imaging data, we construct a sample of low surface brightness galaxies (LSBGs) and match them with MW analogs at $0.01 < z < 0.04$.
-Assuming the host distance, we calculate the physical size and stellar mass for LSBGs and further construct the UDG and UPG samples.
-We compare the statistical properties of mass-size outliers (UDGs and UPGs) with LV satellites and simulations to shed light on questions about their formation and evolution.
+For this purpose, we propose a new definition for mass-size outliers, dubbed as ``ultra-puffy galaxies'' (UPGs), based on the observed mass-size relation and its scatter.
+This definition is more robust to mass-to-light differences between red and blue galaxies compared with the UDG definition.
+Leveraging the depth and wide sky coverage of Hyper-Suprime Camera (HSC) imaging data, we are able to build a large statistical sample of mass-size outliers that are likely satellites of MW-mass hosts in the nearby Universe.
+The good statistics of our samples enable us to examine the abundance, size distribution, spatial distribution, and quenching of mass-size outliers.
+By comparing mass-size outliers with normal satellites and simulations, our results might shed light on the formation and evolution of the large diffuse galaxies.
 
@@
 
-% UDGs found in groups and clusters are mostly red and quenched, whereas their blue counterparts are found in field environments (although several quenched UDGs are found in the field, \citealt{Roman2019,Prole2019}).
-This suggests that environmental effects play a critical role in the formation and quenching of UDGs.
-
 The layout of this paper is as follows.
 Section \ref{sec:data} describes the data used in this work.
-In Section \ref{sec:lsbg_search}, we describe how we search the LSBG candidates in HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), and modeling (\S \ref{sec:modeling}).
-In Section \ref{sec:sample_construction}, we propose the UPG definition and present our UDG and UPG samples.
+In Section \ref{sec:lsbg_search}, we describe the LSBG search in the HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), and modeling (\S \ref{sec:modeling}).
+In Section \ref{sec:sample_construction}, we propose a new definition for large and diffuse galaxies (the UPGs) and present our UDG and UPG samples.
 In Section \ref{sec:results}, we show statistical analysis for UDGs and UPGs including their abundances (\S \ref{sec:n_udg}), size distributions (\S \ref{sec:size_distr}), spatial distributions (\S \ref{sec:radial_distr}), and quenched fractions (\S \ref{sec:quench}).
@@
 The stellar mass used in this work is based on a \citet{Chabrier2003} initial mass function.
-
-% Continuing the work by \citep{Greco2018}, we conducted a systematic search for low surface brightness galaxies (LSBGs) in Hyper Suprime-Cam survey (HSC) imaging data (Li et al., in prep).
-In order to study the formation and evolution of UDGs in low-density environments, we first select host galaxies at $0.01 < z < 0.04$ with Milky-Way masses ($10.2 < \log M_*/M_\odot < 11.2$) in the NASA-Sloan Atlas.
-We matched our HSC LSBGs catalog with the MW-like hosts catalog.
-We assign an LSBG to a host if their angular separation is smaller than the projected virial radius of the host.
-Then we select a UDG sample by requiring the $g$-band average surface brightness within the effective radius\footnote{This surface brightness threshold is equivalent to $\mu_0(g) > 24.0\ \mathrm{mag\ arcsec^{-2}}$ (van Dokkum et al.
-2015) for S\'{e}rsic model with $n=1$.} $\overline{\mu_e} > 24.4\ \mathrm{mag\ arcsec^{-2}}$ and effective radius $R_e > 1.5$ kpc, under the assumption that all matched LSBGs are physically associated with the hosts.
-Following these steps, we have identified $\sim$ 250 UDG candidates to be associated with Milky Way-like hosts in projection.
-They span a wide range of surface brightness, size, color, nucleation, and host properties, making this sample ideal for studying UDG spatial distributions, quenched fractions, mass-size relations, nucleation fractions, and their dependence on host properties.
 
@@
 In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, where we also take the $1\sigma$ measurement errors into account.
+As a result, there are a few objects with smaller size but large uncertainty scattered in our UDG sample.
 This definition maximizes the consistency with the definition in \citet{vanDokkum2015} while not losing UDGs harboring nuclear star clusters.
@@
 The UDG abundance of this work is highlighted as the red square.
-As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo mass end.
+As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo mass end, but this might be due to the small statistics in prior studies and the difference in completeness.
 Our UDG abundance is similar to the value in ELVES survey, but much higher than the value from SAGA.
@@
 
-\subsection{A better definition of mass-size outliers}\label{sec:artifact}
-% High and constant quenched fraction of UDGs is an artifact
-In Section \ref{sec:sample_construction}, we have already argued that the hard size cut in UDG definition does not consider the mass-size relation, and we propose UPG which better represent the large-size tail of dwarf galaxy population.
-Here we discuss other defect in UDG definition which is the hard cut in surface brightness regardless of the galaxy color.
-We also discuss the advantages and disadvantages of different definitions of low surface brightness galaxies including UDG and UPG.
-
-In Section \ref{sec:quench}, we find that the quenched fraction of UDGs is higher than the quenched fractions of UPGs and the satellite population of MW analogs.
-Furthermore, it almost remains a constant over $>1.5$ dex in stellar mass.
-We argue that UDG's high and constant quenched fraction is merely an artifact due to its contrived definition.
-We start from Figure \ref{fig:mass_size} where we show UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ indicating how much a galaxy has been quenched (\S \ref{sec:quench}).
-The UDG sample includes a number of galaxies below the $1.5\sigma$ mass-size line, and these galaxies are mostly quenched (having zero or negative $\Delta(\mathrm{Quench})$).
+\subsection{Robust identification of mass-size outliers}\label{sec:artifact}
+% In this paper, we propose a robust definition of mass-size outliers (the UPGs). Here we contrast UPGs with UDGs to elaborate the fact that UPGs better represent mass-size outliers.
+
+% We also discuss the advantages and disadvantages of different definitions of low surface brightness galaxies including UDG and UPG.
+
+In the left panel of Figure \ref{fig:mass_size}, we find that combining a hard physical size cut with a surface brightness cut carves out an interesting region of the mass-size plane that is complicated in two ways.
+On the one hand, there are many galaxies classified as UDGs that are not size outliers at $M_\star \sim 10^{7.5}\ M_\odot$.
+On the other hand, the hard surface brightness cut corresponds to very different surface mass density between red and blue galaxies, making it hard to directly compare red and blue diffuse populations.
+These issues manifest themselves in the high quenched fractions of UDGs.
+As seen in Figure \ref{fig:mass_size}, the UDG sample includes a number of galaxies below the $1.5\sigma$ mass-size line, and these galaxies are mostly quenched (having zero or negative $\Delta(\mathrm{Quench})$).
 In order to help understand this phenomenon, we plot constant surface brightness lines of $\sbeff=25.0\ \sbunit$ for two different colors $g-i=0.4$ (blue solid line) and $g-i=0.8$ (red solid line) on the mass-size plane.
@@
 For a given size and surface brightness (e.g., $\sbeff=25.0\ \sbunit$), redder galaxies have the same absolute magnitude as blue galaxies, but have higher stellar mass because they have higher mass-to-light ratio than blue galaxies.
-The color-$M_\star/L$ effect manifests itself on Figure \ref{fig:mass_size} by separating the two constant surface brightness lines.
 As a result, the UDG sample includes more red galaxies than blue ones due to the color-independent surface brightness cut at $\sbeff=25.0\ \sbunit$, and thus give rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}.
@@
 
-It worth emphasizing that the concept of UDG was originally proposed in a cluster context where the UDGs are mostly red and quenched \citep[e.g.,][]{vanDokkum2015} and the color-$M_\star/L$ effect does not matter that much.
+% In Section \ref{sec:sample_construction}, we have already argued that the hard size cut in UDG definition does not map clearly onto the mass-size relation, and we propose identifying UPGs as outliers in the mass-size plane.
+Here we discuss another limitations in the UDG definition, namely the hard cut in surface brightness regardless of the galaxy color.
+We also discuss the advantages and disadvantages of different definitions of low surface brightness galaxies including UDG and UPG.
+% The above issues manifest themselves in the derived quenched fractions of UDGs.
+In Section \ref{sec:quench}, we find that the quenched fraction of UDGs is higher than the quenched fractions of UPGs and the satellite population of MW analogs.
+Furthermore, it almost remains a constant over $>1.5$ dex in stellar mass.
+% We argue that UDG's high and constant quenched fraction is merely an artifact of the definition.
+We start from Figure \ref{fig:mass_size}, where we show UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ indicating how much a galaxy has been quenched (\S \ref{sec:quench}).
+
+It is worth emphasizing that the concept of UDG was originally proposed in a cluster context where UDGs are mostly red and quenched \citep[e.g.,][]{vanDokkum2015} and the color-$M_\star/L$ effect does not matter that much.
 However, bluer UDGs are found in less dense environments.
@@
 
-In this paper, we advocate an better definition for mass-size outliers: ultra-puffy galaxies (UPGs).
+Our selection of UPGs is done directly based on the mass-size relation and thus alleviates the issues of UDG.
 They are defined to be $1.5\sigma$ above the average mass-size relation in the dwarf galaxy regime.
 The specific value above the average mass-size relation can vary to probe different parts of the size distribution.
-As we discussed in Section \ref{sec:sample}, a mass-dependent size cut for diffuse galaxies is more objective than a hard size cut because the average size gets larger with increasing stellar mass.
-However, the mass-size relation generally depends on the color, morphology, environment, and also redshift of the galaxies \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
-Fortunately, for dwarf galaxies ($10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$) in the nearby Universe, \citet{ELVES-I} find that the mass-size relation is not sensitive to the color and morphology.
-This finding encourages definitions based on the mass-size relation for diffuse galaxies.
-From Figure \ref{fig:mass_size}, it is clear that the UPG definition naturally represents the large-size tail of the mass-size relation without introducing the artifacts due to the color-$M_\star/L$ relation.
-We further advocate studying the UPG population in both observation and simulation and explore different ``puffiness'' of UPGs (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).
-
-However, in order to construct a UPG sample, one need to know the distance, color, a color-$M_\star/L$ relation to convert observed magnitudes to stellar mass, and a mass-size relation and its scatter.
+We further advocate studying the UPG population in both observations and simulations to explore different ``puffiness'' of UPGs (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).
+
+However, in order to construct a UPG sample, one needs to know the distance, color, a color-$M_\star/L$ relation to convert observed magnitudes to stellar mass, and a mass-size relation and its scatter.
 None of these are easy to obtain and free from systematic errors.
-On one hand, reliable mass-size relation and its scatter are not available for all mass ranges.
+On the one hand, reliable mass-size relation and its scatter are not available for all mass ranges.
 \citet{ELVES-I} derive the mass-size relation below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$.
-It is not clear about the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ and how it depends on color and morphology.
-In this work, we simply extrapolate \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$.
-On the other hand, it is not clear whether the size distribution for a given mass can be well-described by a Gaussian distribution.
+The mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is not well measured, nor is any dependence on color and morphology.
+In this work, we simply extrapolate the \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$.
+At the same time, it is not clear whether the size distribution for a given mass can be well-described by a Gaussian distribution.
 Fig.
-9 in \citet{ELVES-I} shows the residual in $\log(r_e)$ after fitting the mass-size relation, where the distribution of residual is roughly Gaussian but skewed toward the large-size end.
-With enough statistics in the future, one might be able to characterize the shape of large-size tail batter and define UPGs based on the percentiles of the size distribution.
-However, there are also other size definitions which help reduce the scatter of mass-size relation \citep[e.g.,][]{Miller2019,Trujillo2020} and can further benefit construct UPG samples.
-
-In the right panel of Figure \ref{fig:mass_size}, we also plot the constant average surface mass density lines, which is steeper than the mass-size relation but have the same slope as constant surface brightness lines.
+9 in \citet{ELVES-I} shows the residual in $\log(r_e)$ after fitting the mass-size relation, where the distribution of residuals is roughly Gaussian but skewed toward the large-size end.
+With enough statistics in the future, one might be able to characterize the shape of the large-size tail and define UPGs based on the percentiles of the size distribution.
+However, there are also other size definitions which help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Trujillo2020} and can further benefit construct UPG samples.
+
+In the right panel of Figure \ref{fig:mass_size}, we also plot constant average surface mass density lines, which are steeper than the mass-size relation but have the same slope as constant surface brightness lines.
 Hence another way to define diffuse galaxies is to select galaxies with low surface mass density.
@@
 We defer such studies to future works.
-
-% Find literature for quenched fraction as a function of distance to host (Einasto 1974, Spekkens2014, Karunakaran2022 for MW and M31).
 

### 2022-09-28 main.tex
before splitting it into two papers

@@
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+\affiliation{Center for Statistics \& Machine Learning, Princeton University, Princeton, NJ 08544, USA}
 
@@
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+\affiliation{Oskar Klein Centre for Cosmoparticle Physics, Department of Physics, Stockholm University, Stockholm SE-106 91, Sweden}
 \author[0000-0002-1841-2252]{Erin Kado-Fong}
+\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
+
+\author[0000-0002-1418-3309]{Ji Hoon Kim}
+\affiliation{Astronomy Program, Department of Physics and Astronomy, Seoul National University, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Republic of Korea}
+\affiliation{SNU Astronomy Research Center, Seoul National University, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Republic of Korea}
+
+\author{Lauren MacArthur}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
@@
 The number of these ``ultra-puffy'' galaxies per host is comparable to the observed abundance  at this halo mass in the Local Volume, and the galaxies follow an NFW profile around their halos.
-We argue that our definition, based on the mass-size relation, is more robust than the literature ultra-diffuse galaxy definition, which depends on surface brightness and thus yields different surface mass density cuts for quenched and star-forming galaxies.
+We argue that our definition, based on the mass-size relation, is more robust than the common definition of ultra-diffuse galaxies, which depends on surface brightness and thus yields different surface mass density cuts for quenched and star-forming galaxies.
 With our mass-size--based definition, we show that despite their extended size, the quenched fraction is comparable at a given satellite stellar mass between the ultra-puffy and normal dwarfs in MW-mass halo.
@@
 \section{Introduction} \label{sec:intro}
-In a variety of galaxy populations, an interesting subset of galaxies with low surface brightness and large physical size have been identified \citep[dubbed as low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
-Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015} , accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
+In a variety of galaxy populations, an interesting subset of galaxies with low surface brightness and large physical size have been identified \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
+Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
 There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
-The UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus are very large in size for their stellar mass.
-Therefore, a central questions about LSBGs, including UDGs, is what causes them to be outliers from the mass-size relation.
+UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus have very large sizes for their stellar mass.
+Therefore, a central question about LSBGs, including UDGs, is what causes them to be outliers from the mass-size relation.
 % Therefore, a central question about mass-size outliers including UDGs is what physical mechanisms are responsible for the formation and quenching of these large diffuse galaxies.
@@
 Different mechanisms are proposed to explain the presence of large diffuse galaxies in different environments.
-In the field, large size might be caused by star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or the galaxies inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019}.
-In groups and clusters, the large size may ensue from tidal heating near pericenter \citep{Jiang2019} or via adiabatic expansion due to mass loss \citep{Tremmel2020}.
-Despite theoretical advances, it is still an open question how mass-size outliers like UDGs in certain environments are formed and quenched.
-It is also unclear whether mass-size outliers belong to a special class of galaxy or are just a natural extension of dwarf systems to lower surface brightness.
-To answer these questions, we can compare mass-size outliers with the ``normal'' satellites for which we have a better understanding.
-
-Our best knowledge in the dwarf satellite regime is about the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}.
-With the advent of deep sky surveys and dedicated spectroscopy programs, we are now mapping the satellite systems of MW analogs in the Local Volume and nearby Universe.
+In the field (i.e, in isolation), their large sizes might be caused by star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}.
+In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019} or via adiabatic expansion due to mass loss \citep{Tremmel2020}.
+Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed and quenched.
+It is also unclear whether mass-size outliers belong to a special class of galaxies or are just a natural extension of dwarf systems to lower surface brightness.
+To answer these questions, we can compare mass-size outliers with ``normal'' low mass galaxies for which we have a better understanding.
+
+Our best understanding of the low mass regime comes from the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}.
+With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs in the Local Volume and nearby Universe.
 The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at $z\sim0.01$ \citep{SAGA-I,SAGA-II}.
-The Exploration of Local VolumE Satellites (ELVES) survey uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm satellites \citep{ELVES-I,ELVES-II,CarlstenELVES2022}.
+The Exploration of Local VolumE Satellites (ELVES) survey uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts \citep{ELVES-I,ELVES-II,CarlstenELVES2022}.
 Having the MW satellites as a reference frame, we can study the formation and quenching of large diffuse galaxies by comparing them with the bulk of observed and simulated MW satellites.
 However, there are only $\sim 30$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022}.
-A larger sample of mass-size outliers (including UDGs) associated with MW hosts is needed to conduct such studies.
+A larger sample of mass-size outliers (including UDGs) associated with MW hosts is needed to conduct such a comparison.
 
 The goal of this paper is to study large diffuse galaxies in the reference frame of the satellite systems of MW analogs and try to elucidate their formation and quenching.
-For this purpose, we propose a new definition for mass-size outliers, dubbed as ``ultra-puffy galaxies'' (UPGs), based on the observed mass-size relation and its scatter.
-This definition is more robust to mass-to-light differences between red and blue galaxies compared with the UDG definition.
+For this purpose, we propose a new definition for mass-size outliers, dubbed ``ultra-puffy galaxies'' (UPGs), based on the observed mass-size relation and its scatter.
+This definition is more robust to mass-to-light differences between red and blue galaxies compared to the UDG definition.
 Leveraging the depth and wide sky coverage of Hyper-Suprime Camera (HSC) imaging data, we are able to build a large statistical sample of mass-size outliers that are likely satellites of MW-mass hosts in the nearby Universe.
 The good statistics of our samples enable us to examine the abundance, size distribution, spatial distribution, and quenching of mass-size outliers.
-By comparing mass-size outliers with normal satellites and simulations, our results might shed light on the formation and evolution of the large diffuse galaxies.
+By comparing mass-size outliers with normal satellites and simulations, our results seek to shed light on the formation and evolution of the large diffuse galaxies.
 
@@
 The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section.
-For those who do not want to be bothered by technical details, we outline the major steps below and refer the reader to Section \ref{sec:sample_construction} for UDG and UPG sample construction.
+We outline the major steps below and refer the reader to Section \ref{sec:sample_construction} for UDG and UPG sample construction.
 \begin{enumerate}
-    \item Source Detection (\S \ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources.
+    \item Source Detection (\S \ref{sec:detection}): we run \code{SourceExtractor} on the coadd images after removing bright extended sources.
 Then we apply an initial size and color cut based on the output catalog.
@@
 
+{\bf Here you put one PP summarizing the main changes, and then put the rest of the details in 3.1 into Appendix 1.
+End this section with the numbers of targets at the end of this step, and I agree with Erin that having a flow-table with the numbers per step would be nice.}
+
 \subsubsection{Bright source removal}
@@
 \subsubsection{Source Extraction}
-We use \href{https://www.astromatic.net/software/sextractor/}{\code{Source Extractor}} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
+We use \href{https://www.astromatic.net/software/sextractor/}{\code{SourceExtractor}} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
 This step remains largely the same as in \citetalias{Greco2018}.
@@
 \subsubsection{Initial Sample Selection} 
-In this step, we take the output catalog from \code{Source Extractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors.
-To be specific, we require objects to have $g$-band half-light radii (measured by \code{Source Extractor}) greater than $r_{\rm min} = 2.0\arcsec$.
+In this step, we take the output catalog from \code{SourceExtractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors.
+To be specific, we require objects to have $g$-band half-light radii (measured by \code{SourceExtractor}) greater than $r_{\rm min} = 2.0\arcsec$.
 We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$.
@@
 It utilizes the color and morphology information to separate blended objects.
-In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation for more details.
-
-In \code{scarlet}, each source $k$ in the cutout is described by a morphology matrix $S^k_i$ and a Spectral Energy Distribution (SED) vector $A^k_i$, and the multi-band images is $Y_i$, where $i$ denotes different bands.
-The goal of the modeling is to minimize the objective function $f \propto \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF and $*$ is convolution.
-The morphology matrix of each source is limited by a bounding box.
-We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirts (monotonoicity constraint).
-The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample, this assumption still holds for most cases and provides an easy, sparse, and robust way to deblend overlapping sources.
+In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation\footnote{\url{https://pmelchior.github.io/scarlet/}} for more details.
+
+In \code{scarlet}, each source $k$ in the cutout is described by a morphology image $S^k_i$ and a Spectral Energy Distribution (SED) vector $A^k_i$, and the multi-band images is $Y_i$, where $i$ denotes different bands.
+The goal of the modeling is to minimize the objective function $f \propto \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i\times S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF and $*$ is convolution.
+The morphology image of each source is limited by a bounding box.
+We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirts.
+The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample this assumption still holds for most cases and provides an easy and robust way to deblend overlapping sources.
 We refer to this modeling method as \textit{vanilla scarlet}.
 
+{\bf Here I think belongs a paragraph with a high level summary of the steps and how they work, as above.
+So a few sentences on peak detection, model initialization, measurement and false positive removal.
+Then I'd think most of 3.2.1, 3.2.2 could go Appendix, but keeping most of the measurement stuff and visual inspection in the main text.}
+
 In vanilla scarlet, objects can be modeled with different types of models as follows.
-The point source has a morphology matrix simply be the normalized PSF.
-The single-extended source has a morphology matrix that follows positivity and monotonicity constraints.
+The point source has a morphology image simply be the normalized PSF.
+The single-extended source has a morphology image that follows positivity and monotonicity constraints.
 The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient.
-The compact source is a single-extended source initialized using the morphology matrix of a point-source, which encourages the model to be compact, but still allows the morphology matrix to be extended.
+The compact source is a single-extended source initialized using the morphology image of a point-source, which encourages the model to be compact, but still allows the morphology image to be extended.
 The flat-sky source has uniform color and morphology within the bounding box.
@@
 
-After peak detection, we need to decide which peaks to modeled, and we would like to initialize the model as best as we can.
+After peak detection, we need to decide which peaks to model, and we would like to initialize the model as best as we can.
 We note that \code{scarlet} optimizes the model instead of deriving the full posteriors, thus good initialization becomes really important.
-We tackle these problem as follows.
+We tackle these problems as follows.
 
@@
 
-We use a multi-extended source with two components to model the target object, such that the model is able to capture the galaxy structure and color gradient.
+We use an extended source model with two components to describe the target object, such that the model is able to capture the galaxy structure and color gradient.
 The source is initialized as follows.
 We convolve the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise.
-After smoothing, the LSB outskirts of the target galaxy become more prominent, which helps in determining the bounding box and initializing the morphology matrix.
+After smoothing, the LSB outskirts of the target galaxy become more prominent, which helps in determining the bounding box and initializing the morphology image.
 We take the smoothed image and threshold it with $0.1\sigma$ to remove the sky noise.
-The initial morphology matrix $S_i$ is determined by constructing a symmetric and monotonic approximation to the smoothed image around the target object.
+The initial morphology image $S_i$ is determined by constructing a symmetric and monotonic approximation to the smoothed image around the target object.
 The initial SED vector $A_i$ is set to be the sum of the morphology matrices $S_i$ in each band.
@@
 For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact.
-The reason why it passes our initial selection is that the galaxy outskirts are shredded by Source Extractor and happen to have a large size and the right color.
+The reason why it passes our initial selection is that the galaxy outskirts are shredded by SourceExtractor and happen to have a large size and the right color.
 But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.
@@
 
-After running the vanilla scarlet for LSGB candidates, we successfully deblend the target object from nearby sources.
-Unlike other modeling codes, the non-parametric \code{scarlet} model is very flexible on modeling galaxies with complex structures.
+After running the vanilla scarlet for LSBG candidates, we successfully deblend the target object from nearby sources.
+Unlike other modeling codes, the non-parametric \code{scarlet} model is very flexibly modeling galaxies with complex structures.
 But the non-parametric nature of the code means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model.
@@
 Many other works have been using machine learning (ML) algorithms to classify LSBG candidates and exclude spurious detection.
-Among others, \citet{Tanoglidis2021} take the output catalog from \code{Source Extractor} and use the Support Vector Machine algorithm to classify objects in their initial sample and reduce the number of objects that are visually inspected.
+Among others, \citet{Tanoglidis2021} take the output catalog from \code{SourceExtractor} and use the Support Vector Machine algorithm to classify objects in their initial sample and reduce the number of objects that are visually inspected.
 \citet{Zaritsky2019,Zaritsky2021,Zaritsky2022} use convolutional neural networks to classify LSBGs into binary classes based on their images.
 These endeavors certainly help reduce the human labor on visually inspecting tens of thousands of objects.
-However, training such a supervised ML algorithm relies on the labeled data which should also sample the parameter space evenly.
+However, training such a supervised ML algorithm relies on the labeled data which should also sample the parameter space fairly evenly.
 Once labels are assigned (e.g., LSBG v.s.
@@
 \subsection{Modeling}\label{sec:modeling}
+
+{\bf My proposal is to keep this entire discussion in main paper, not appendix, but I think it can be shortened a bit}
+
 Although the vanilla scarlet modeling provides useful information to help us remove false positives, it does not necessarily give us unbiased estimations on size, color, total magnitude, etc.
@@
 This issue, dubbed the ``cookie-cutter effect'', can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model of the target object never exceeds the other objects next to it.
-As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biasing the measurements.
+As a result, the non-parametric model often does not capture well the LSB outskirts of LSBG, thus biasing the measurements.
 In the following, we explore a novel method to perform parametric fitting while exploiting the advantages of \code{scarlet}.
@@
 
-For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
+For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
 This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
 However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}.
-To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
+To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
 They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
@@
 It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$.
-We find negligible dependence of completeness on \sersic{} index, color, and ellipticity.
+We find negligible dependence of completeness on \sersic index, color, and ellipticity.
 Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
@@
 We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness.
+Although \sersic galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic model still sets a baseline or upper limit on the real completeness.
 In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).
@@
 This gives us a chance to define a subset of dwarf galaxies that are size-outliers in terms of the average mass-size relation.
-It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.
+It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021,Benavides2022}.
 
@@
 With enough statistics in the future, one might be able to characterize the shape of the large-size tail and define UPGs based on the percentiles of the size distribution.
-However, there are also other size definitions which help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Trujillo2020} and can further benefit construct UPG samples.
+However, there are also other size definitions which help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Mowla2019,Trujillo2020} and can further benefit construct UPG samples.
 
@@
 
+J.H.K acknowledges the support from the National Research Foundation of Korea (NRF) grant, No. 2021M3F7A1084525, funded by the Korea government (MSIT).
+
 The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan and Taiwan, and Princeton University.
@@
 Funding was contributed by the FIRST program from Japanese Cabinet Office, Ministry of Education, Culture, Sports, Science and Technology (MEXT), Japan Society for the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA and Princeton University.
+Remy Joseph's work has been enabled by support from the research project grant ‘Understanding the Dynamic Universe’ funded by the Knut and Alice Wallenberg Foundation under Dnr KAW 2018.0067.
 

### 2022-10-06 paper1.tex
working on moving deblending to the appendix

--- 2022-09-28 main.tex
@@
 % \title{Ultra Diffuse Galaxies associated with Milky-Way Analogs}
-\title{Beyond Ultra-Diffuse Galaxy: Mass-Size Outliers in the Satellites of Milky Way Analogs}
+\title{Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers in the Satellites of Milky Way Analogs}
 
@@
 \affiliation{SNU Astronomy Research Center, Seoul National University, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Republic of Korea}
-
 \author{Lauren MacArthur}
@@
 \begin{abstract}
-Large diffuse galaxies are hard to find, but understanding their environments and abundance, and ultimately their origins, is of intense interest.
+[\textbf{Need to rewrite}] Large diffuse galaxies are hard to find, but understanding their environments and abundance, and ultimately their origins, is of intense interest.
 Using the Hyper Suprime-Cam Strategic Survey, we search for low surface-brightness galaxies and match them to Milky-Way like hosts in projection.
@@
 With our mass-size--based definition, we show that despite their extended size, the quenched fraction is comparable at a given satellite stellar mass between the ultra-puffy and normal dwarfs in MW-mass halo.
-These results hint that the size growth and quenching of mass-size outliers must happen separately.
+These results hint that the size growth and quenching of mass-size outliers happen separately.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-In a variety of galaxy populations, an interesting subset of galaxies with low surface brightness and large physical size have been identified \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
+[\textbf{Need to rewrite}] In a variety of galaxy populations, an interesting subset of galaxies with low surface brightness and large physical size have been identified \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
 Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
@@
 \subsection{NASA-Sloan Atlas}
-We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way, then we match the LSBGs to these MW analogs.
+We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way, then we match the LSBGs to these MW analogs (see \S \ref{sec:sample_construction}).
 The NSA catalog provides various physical properties of galaxies in the nearby universe as derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}.
@@
 The new version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions.
-In this paper, we use the stellar mass derived from elliptical Petrosian photometry using \code{kcorrect v4\_2}.
-The redshifts of galaxies in NSA come from several spectroscopic surveys, gas surveys, or direct distance measurements.
+In this paper, we use the stellar mass derived from elliptical Petrosian photometry using \code{kcorrect v4\_2} \citep{Blanton2007}.
+The redshifts of galaxies in NSA come from several spectroscopic surveys, \ion{H}{1} gas surveys, or direct distance measurements.
 
 \section{LSBG search in HSC PDR2}\label{sec:lsbg_search}
+
 Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies (LSBGs) in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}.
@@
 \begin{enumerate}
-    \item Source Detection (\S \ref{sec:detection}): we run \code{SourceExtractor} on the coadd images after removing bright extended sources.
+    \item Source Detection (\S \ref{sec:detection}): we run \href{https://www.astromatic.net/software/sextractor/}{\code{SourceExtractor}} \citep{Bertin1996} on the coadd images after removing bright extended sources.
 Then we apply an initial size and color cut based on the output catalog.
-    \item Deblending (\S \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \code{scarlet}.
+    \item Deblending (\S \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}.
 We use the \code{scarlet} models to define color-size-morphology-surface brightness cuts.
@@
 \end{enumerate}
+The number of objects remained after each step is shown in Table \ref{tab:steps_flow}.
 Our source detection pipeline \href{https://github.com/johnnygreco/hugs}{\code{hugs}} and deblending and modeling code \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} are open-sourced and available online.
+
+\begin{deluxetable*}{lcc}
+\tablecaption{LSBG search steps and the number of remaining objects after each step}
+\tablewidth{20cm}
+\label{tab:steps_flow}
+\tablehead{
+\colhead{Process} & \colhead{Description} &
+\colhead{Remaining objects}
+}
+\startdata
+Initial detection & \S\ref{sec:detection} & 86,002 \\
+Matching with MW analogs at $0.01 < z < 0.04$ & \S\ref{sec:match} & 10,579 \\
+Deblending &\S\ref{sec:deblending} & 2,673\\
+Spergel profile modeling & \S\ref{sec:modeling}, \S\ref{sec:match} & 2,510\\
+Completeness & \S\ref{sec:completeness} & 2,510 \\
+Measurement error and uncertainty & \S\ref{sec:meas_unc} & 2,510\\
+Mass-size outlier selection & \S\ref{sec:sample} & 362 (UPG), 432 (UDG)
+\enddata
+\end{deluxetable*}
 
@@
 These updates are guided by both our understanding of PDR2 data and the completeness tests using mock galaxies.
-In the following, we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity.
+We summarize the main steps of LSBG search method here, and refer the interested readers to \citetalias{Greco2018} and Appendix \ref{ap:detection} for more details.
+% In the following, we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity.
 We refer the interested readers to \citetalias{Greco2018} for more details.
 
-{\bf Here you put one PP summarizing the main changes, and then put the rest of the details in 3.1 into Appendix 1.
-End this section with the numbers of targets at the end of this step, and I agree with Erin that having a flow-table with the numbers per step would be nice.}
-
-\subsubsection{Bright source removal}
-Bright sources and their associated LSB outskirts can mimic objects of interest and obstruct the detection of LSBGs.
-In this step, we replace pixels related to bright sources and small compact sources with sky noise.
-The bright sources and their diffuse outskirts are detected in the $i$-band by applying a high thresholding and a low thresholding to the image, respectively.
-We associate a diffuse light component with a bright source if more than 15\% of its pixels are above the high threshold.
-In this way, we generate a footprint of bright sources and their associated LSB components.
-Then for the $gri$-bands, we replace every pixel within this footprint with Gaussian noise, where the noise level is determined by masking out all detected sources in the image.
-
-    In \citetalias{Greco2018}, the thresholds are set based on the noise level of the local sky.
-Thanks to the global sky subtraction in PDR2, LSB features are well conserved after subtracting the sky and the sky noise level varies less.
-Therefore, it makes more sense to set the thresholds based on the characteristic surface brightness instead of a certain sigma value above the sky background.
-In this work, we set the high threshold to $\mu_{\rm high} = 22\ \sbunit$ to capture all bright sources above this surface brightness, and the low threshold to $\mu_{\rm low} = 24.5\ \sbunit$ to capture the associated diffuse lights.
-Unlike in \citetalias{Greco2018}, we find it not necessary to smooth the image prior to the thresholding.
-
-    After this step, there are still a number of small and compact LSB objects, which are typically marginally resolved galaxies, blended sources, or just pixels standing out because of noise fluctuation.
-We add an extra step to detect and remove them since our main goal is to detect extended LSBGs.
-We run \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} on the ``cleaned'' images as described above.
-Based on the segmentation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$, and pixels within this mask are also replaced by sky noise.
-This step significantly improves the purity of LSBG search.
-The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by the completeness tests (\S \ref{sec:completeness}).
-    % This step effectively cleans out objects and features that hinder the detection of LSBGs.
-
-\subsubsection{Source Extraction}
-We use \href{https://www.astromatic.net/software/sextractor/}{\code{SourceExtractor}} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
-This step remains largely the same as in \citetalias{Greco2018}.
-The images are convolved with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast between LSBGs and sky background \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}.
-We take a mesh size of $43\arcsec$ (double the mesh size used in \citetalias{Greco2018} to allow bigger galaxies in our sample) to measure the local background and detect objects that are 0.7$\sigma$ per pixel above the local sky background.
-We also require the object to contain at least 100 contiguous pixels (equivalent to a square box with $1.7\arcsec$ on each side) to further remove small compact objects.
-We perform the detection in the $g$-band, but require that all sources are also detected in the $r$-band to exclude spurious detection and artifacts.
-
-\subsubsection{Initial Sample Selection} 
-In this step, we take the output catalog from \code{SourceExtractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors.
-To be specific, we require objects to have $g$-band half-light radii (measured by \code{SourceExtractor}) greater than $r_{\rm min} = 2.0\arcsec$.
-We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$.
-This color box is relatively conservative with respect to the color distribution of the discovered LSBGs \citep[e.g.,][]{SAGA-I,Greco2018,Zaritsky2019,Tanoglidis2021}.
-
-Compared with \citetalias{Greco2018}, we add a new metric based on the morphology of sources to further remove false positives.
-For each source, we compute the ratio of the 2-D autocorrelation function (ACT) within an aperture of 5 pixels and the ACT within an annulus between 5 pixels and 9 pixels from the center.
-The ACT ratio essentially characterizes the peakiness of the source.
-Peaky sources have higher ACT ratios, thus we remove point-like sources by applying a cut on ACT ratios $a_{\rm corr} < 2.5$.
-This step helps to improve the purity of our sample.
-%\textbf{Morphology? Auto-correlation? See `build_catalog.py` in `/tigress/jgreco/project-code/hugs-s18a-ana/scripts`}
-
-\vspace{2em}
+We start by replacing the bright sources and their associated LSB outskirts with the sky noise.
+Bright objects and their diffuse light are identified using surface brightness thresholding.
+Then we run a detection using \code{sep} \citep{Barbary2016} to remove small compact sources and noisy peaks and replace their footprints with sky noise.
+We use \code{SourceExtractor} to detect sources on the ``cleaned'' images with a low detection threshold.
+Taking the output catalog from \code{SourceExtractor}, we apply an initial selection based on the size, color, and peakiness of objects.
+
 After these steps, we have an initial sample that contains 86,002 LSBG candidates.
-We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because PDR2 has better sky subtraction, our detection here is more inclusive of larger objects, and our size cut is less restrictive for small objects.
+We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because HSC PDR2 has better sky subtraction, our detection here is more inclusive of larger objects, and our size cut is less restrictive for small objects.
 Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirrus, and blended compact sources.
 Therefore, we perform an extra ``deblending'' step to further remove false positives.
+
+% {\bf Here you put one PP summarizing the main changes, and then put the rest of the details in 3.1 into Appendix 1.
+End this section with the numbers of targets at the end of this step, and I agree with Erin that having a flow-table with the numbers per step would be nice.}
 
@@
 In order to identify and remove these objects from our sample, we perform non-parametric modeling for each object using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}.
-\code{Scarlet} is a deblending and modeling tool designed for multi-band imaging data.
+\code{Scarlet} is a deblending and modeling tool designed for multi-band and multi-resolution imaging data.
 It utilizes the color and morphology information to separate blended objects.
@@
 In \code{scarlet}, each source $k$ in the cutout is described by a morphology image $S^k_i$ and a Spectral Energy Distribution (SED) vector $A^k_i$, and the multi-band images is $Y_i$, where $i$ denotes different bands.
-The goal of the modeling is to minimize the objective function $f \propto \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i\times S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF and $*$ is convolution.
+The goal of the modeling is to minimize the objective function $f = \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i\times S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF and $*$ is convolution.
 The morphology image of each source is limited by a bounding box.
-We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirts.
-The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample this assumption still holds for most cases and provides an easy and robust way to deblend overlapping sources.
+We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirts (monotonoicity constraint).
+The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample this assumption still holds for most cases and provides an effective and robust way to deblend overlapping sources.
 We refer to this modeling method as \textit{vanilla scarlet}.
+
+% Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with the positions of detected peaks in the prior steps.
+The models are then optimized subject to the constraints.
+Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude false positives from our LSBG sample.
+In the following subsections, we describe our peak detection, model initialization, and measurement procedures.
+
+We use vanilla scarlet to model the LSBG candidate and extract structural and morphological parameters from the \code{scarlet} model, which are further used to exclude false positives from our LSBG sample.
+In the following subsections, we briefly describe our peak detection, model initialization, and measurement procedures.
+We refer the readers to Appendix \ref{ap:deblending} for more detailed descriptions.
+
+The deblending step is designed to model the sources in the vicinity of the LSBG candidate.
+Therefore, we run \code{sep} on the $griz$-combined image to detect objects (i.e., peaks) around the LSBG candidate.
+Objects that are close to the LSBG candidate are modeled using \code{scarlet} models.
+The models are initialized based on the smoothed image to capture the LSB outskirts of the target galaxy.
+Then the models are optimized using the adaptive proximal gradient method \citep{Melchior2019}.
+Typically, convergence is achieved after $\sim 50$ steps of optimization and the whole modeling takes about 40s for a typical LSBG.
+
+The deblending procedures are demonstrated in Figure \ref{fig:vanilla_scarlet_demo} with two distinct examples.
+The one shown in the top panels is a blue LSBG, whereas the one shown on the bottom is a high-$z$ galaxy blended with the outskirts of a nearby galaxy which falls in our initial sample as a false positive.
+The first column shows the $griz$ color-composite image \citep{Lupton2004}, where the white boxes mark the bounding box of each source in the scene.
+The gray shades over objects outside of the target bounding box indicate they are masked out during fitting.
+The second column shows the initial \code{scarlet} models.
+They look fuzzy because they are constructed from the smoothed image, but they capture the color and the faint outskirts of the LSBG quite well.
+The optimized model is shown in the middle column of Figure \ref{fig:vanilla_scarlet_demo} after convolving with the PSF, and the fourth column shows the residual image.
+The fifth column shows the optimized model only for the target object.
+
+We notice that the optimized model of the blue LSBG captures its color and morphology quite well.
+For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact.
+The reason why it passes our initial selection is that the galaxy outskirts are shredded by \code{SourceExtractor} and happen to have a large size and the right color.
+But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.
+
+% Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with the positions of detected peaks.
+
+% The models are then optimized subject to the constraints.
+Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude false positives from our LSBG sample.
+In the following subsections, we describe our peak detection, model initialization, and measurement procedures.
 
@@
 Then I'd think most of 3.2.1, 3.2.2 could go Appendix, but keeping most of the measurement stuff and visual inspection in the main text.}
-
-In vanilla scarlet, objects can be modeled with different types of models as follows.
-The point source has a morphology image simply be the normalized PSF.
-The single-extended source has a morphology image that follows positivity and monotonicity constraints.
-The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient.
-The compact source is a single-extended source initialized using the morphology image of a point-source, which encourages the model to be compact, but still allows the morphology image to be extended.
-The flat-sky source has uniform color and morphology within the bounding box.
-
-Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with the positions of detected peaks in the prior steps.
-The models are then optimized subject to the constraints.
-Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude blended objects from our sample.
-In the following subsections, we describe our peak detection, model initialization, and measurement procedures.
 
@@
 Next, we run \code{sep} on the detection image using a threshold of 4$\sigma$ above the sky, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels.
-This step identifies relatively extended sources in the detection image.
+This step identifies extended sources in the detection image.
 However, there are still faint and compact peaks not detected.
-We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep the high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering).
+We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep the high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering in the context of LSBGs).
 Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels.
@@
 We tackle these problems as follows.
+
+In vanilla scarlet, objects can be modeled with different types of models as follows.
+The point source has a morphology image simply be the normalized PSF.
+The single-extended source has a morphology image that follows positivity and monotonicity constraints.
+The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient.
+The compact source is a single-extended source initialized using the morphology image of a point-source, which encourages the model to be compact, but still allows the morphology image to be extended.
+The flat-sky source has uniform color and morphology within the bounding box.
 
@@
 However, scattered light from nearby bright stars and galaxies could bias the modeling of sources within the bounding box (e.g., the yellow star in the top left panel of Figure \ref{fig:vanilla_scarlet_demo}).
-We match our field with the Gaia catalog and mask out stars outside of the bounding box.
+We match our field with the Gaia catalog \citep{GAIA2016,GAIA2018} and mask out stars outside of the bounding box.
 Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.
@@
 
+{\bf I think you can combine 3.4.1 and 3.4.2, and put most of this into the Appendix, just introduce the idea of the simulations and show the figure.
+I'd keep the comparison with other works in the main body of the paper.}
+
 \begin{figure*}
@@
 
-For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
+For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
 This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
 However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}.
-To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
+To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
 They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
@@
 It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$.
-We find negligible dependence of completeness on \sersic index, color, and ellipticity.
+We find negligible dependence of completeness on \sersic{} index, color, and ellipticity.
 Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
@@
 		\centering
-		\includegraphics[width=1\linewidth]{mass_size_plane.pdf}
-	}
-    \caption{The distributions of the UDG and UPG samples on the mass-size plane.
+		\includegraphics[width=1\linewidth]{mass_size_plane_new.pdf}
+	}
+    \caption{[\textbf{Explain this figure better}] The distributions of the UDG and UPG samples on the mass-size plane.
 The data points are color-coded by the distance to the quenching color cut.
@@
 \appendix
+
+\section{LSBG detection}\label{ap:detection}
+\subsection{Bright source removal}
+Bright sources and their associated LSB outskirts can mimic objects of interest and obstruct the detection of LSBGs.
+In this step, we replace pixels related to bright sources and small compact sources with sky noise.
+The bright sources and their diffuse outskirts are detected in the $i$-band by applying a high thresholding and a low thresholding to the image, respectively.
+We associate a diffuse light component with a bright source if more than 15\% of its pixels are above the high threshold.
+In this way, we generate a footprint of bright sources and their associated LSB components.
+Then for the $gri$-bands, we replace every pixel within this footprint with Gaussian noise, where the noise level is determined by masking out all detected sources in the image.
+
+In \citetalias{Greco2018}, the thresholds are set based on the noise level of the local sky.
+Thanks to the global sky subtraction in PDR2, LSB features are well conserved after subtracting the sky and the sky noise level varies less.
+Therefore, it makes more sense to set the thresholds based on the characteristic surface brightness instead of a certain sigma value above the sky background.
+In this work, we set the high threshold to $\mu_{\rm high} = 22\ \sbunit$ to capture all bright sources above this surface brightness, and the low threshold to $\mu_{\rm low} = 24.5\ \sbunit$ to capture the associated diffuse lights.
+Unlike in \citetalias{Greco2018}, we find it not necessary to smooth the image prior to the thresholding.
+
+After this step, there are still a number of small and compact LSB objects, which are typically marginally resolved galaxies, blended sources, or just pixels standing out because of noise fluctuation.
+We add an extra step to detect and remove them since our main goal is to detect extended LSBGs.
+We run \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} on the ``cleaned'' images as described above.
+Based on the segmentation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$, and pixels within this mask are also replaced by sky noise.
+This step significantly improves the purity of LSBG search.
+The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by the completeness tests (\S \ref{sec:completeness}).
+% This step effectively cleans out objects and features that hinder the detection of LSBGs.
+
+\subsection{Source Extraction}
+We use \href{https://www.astromatic.net/software/sextractor/}{\code{SourceExtractor}} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
+This step remains largely the same as in \citetalias{Greco2018}.
+The images are convolved with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast between LSBGs and sky background \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}.
+We take a mesh size of $43\arcsec$ (double the mesh size used in \citetalias{Greco2018} to allow bigger galaxies in our sample) to measure the local background and detect objects that are 0.7$\sigma$ per pixel above the local sky background.
+We also require the object to contain at least 100 contiguous pixels (equivalent to a square box with $1.7\arcsec$ on each side) to further remove small compact objects.
+We perform the detection in the $g$-band, but require that all sources are also detected in the $r$-band to exclude spurious detection and artifacts.
+
+\subsection{Initial Sample Selection} 
+In this step, we take the output catalog from \code{SourceExtractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors.
+To be specific, we require objects to have $g$-band half-light radii (measured by \code{SourceExtractor}) greater than $r_{\rm min} = 2.0\arcsec$.
+We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$.
+This color box is relatively conservative with respect to the color distribution of the discovered LSBGs \citep[e.g.,][]{SAGA-I,Greco2018,Zaritsky2019,Tanoglidis2021}.
+
+Compared with \citetalias{Greco2018}, we add a new metric based on the morphology of sources to further remove false positives.
+For each source, we compute the ratio of the 2-D autocorrelation function (ACT) within an aperture of 5 pixels and the ACT within an annulus between 5 pixels and 9 pixels from the center.
+The ACT ratio essentially characterizes the peakiness of the source.
+Peaky sources have higher ACT ratios, thus we remove point-like sources by applying a cut on ACT ratios $a_{\rm corr} < 2.5$.
+This step helps to improve the purity of our sample.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Deblending details}\label{ap:deblending}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-10-07 paper1.tex
before moving completeness+measurement error to appendix

@@
 \subsection{Deblending}\label{sec:deblending}
+
+\begin{figure*}
+	\vbox{ 
+		%\vskip -10mm
+		\centering
+		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
+		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
+	}
+	\caption{A demonstration of the deblending step as described in \S\ref{sec:deblending}.
+Here we show two objects from our initial sample (\S\ref{sec:detection}): the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts.
+The data shown in the first column is $griz$ color-composite image with the bounding boxes overlay.
+The objects covered by the gray shades are masked during fitting.
+The bounding boxes and the initial models (second column) are determined from the smoothed image.
+The remaining columns show the optimized models (PSF convolved), residual image, and the only target galaxy itself.
+	}
+	\label{fig:vanilla_scarlet_demo}
+\end{figure*}
+
 Removing false positives from the initial sample while retaining high completeness is one of the major challenges in LSBG search \citep[e.g.,][]{vanDokkum2015,Koda2015,Yagi2016,Greco2018,SAGA-I,Zaritsky2019,Zaritsky2021,Tanoglidis2021,Zaritsky2022}.
@@
 Our initial detection cannot distinguish them from the real LSBGs.
-In order to identify and remove these objects from our sample, we perform non-parametric modeling for each object using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}.
+In order to identify and remove these objects from our sample, we perform non-parametric modeling using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018} and design an efficient metric to remove false positives.
+
+\subsubsection{\code{Scarlet} fitting}
 \code{Scarlet} is a deblending and modeling tool designed for multi-band and multi-resolution imaging data.
@@
 We use vanilla scarlet to model the LSBG candidate and extract structural and morphological parameters from the \code{scarlet} model, which are further used to exclude false positives from our LSBG sample.
-In the following subsections, we briefly describe our peak detection, model initialization, and measurement procedures.
+In the following subsections, we briefly describe how we detect peaks on the image, initialize and optimize \code{scarlet} models.
 We refer the readers to Appendix \ref{ap:deblending} for more detailed descriptions.
@@
 But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.
-
-% Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with the positions of detected peaks.
-
-% The models are then optimized subject to the constraints.
-Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude false positives from our LSBG sample.
-In the following subsections, we describe our peak detection, model initialization, and measurement procedures.
-
-{\bf Here I think belongs a paragraph with a high level summary of the steps and how they work, as above.
+A rubric based on the \code{scarlet} model is therefore needed to help us exclude the false positives.
+
+% {\bf Here I think belongs a paragraph with a high level summary of the steps and how they work, as above.
 So a few sentences on peak detection, model initialization, measurement and false positive removal.
@@
 
-\subsubsection{Peak detection}\label{sec:peak}
-We generate cutout images with a size of $1\arcmin$ in the $griz$-bands for each LSBG candidate in our initial sample.
-We then construct a detection image by taking an average of the four bands weighted by the inverse variance of each band.
-This detection image is considered to be deeper than the single-band images.
-Next, we run \code{sep} on the detection image using a threshold of 4$\sigma$ above the sky, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels.
-This step identifies extended sources in the detection image.
-However, there are still faint and compact peaks not detected.
-We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep the high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering in the context of LSBGs).
-Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels.
-This step detects many compact sources that were not included in the previous step.
-In the end, we combine the two detection catalogs.
-
-\subsubsection{Model initialization and optimization}
-
-\begin{figure*}
-	\vbox{ 
-		%\vskip -10mm
-		\centering
-		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
-		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
-	}
-	\caption{A demonstration of the deblending step as described in Section \ref{sec:deblending}.
-Here we show two objects from our initial sample (Sec \ref{sec:detection}): the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts.
-The data shown in the first column is $griz$ color-composite image with the bounding boxes overlay.
-The objects covered by the gray shades are masked.
-The bounding boxes and the initial models (second column) are determined from the smoothed image.
-The optimized models (PSF convolved) are shown in the third column, the fourth column shows the residual image, and the last column isolates the model of the target object and labels the measured color, size, and surface brightness.
-After such a deblending step, false positives such as the one in bottom panels can be easily removed based on their measured properties.
-	}
-	\label{fig:vanilla_scarlet_demo}
-\end{figure*}
-
-After peak detection, we need to decide which peaks to model, and we would like to initialize the model as best as we can.
-We note that \code{scarlet} optimizes the model instead of deriving the full posteriors, thus good initialization becomes really important.
-We tackle these problems as follows.
-
-In vanilla scarlet, objects can be modeled with different types of models as follows.
-The point source has a morphology image simply be the normalized PSF.
-The single-extended source has a morphology image that follows positivity and monotonicity constraints.
-The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient.
-The compact source is a single-extended source initialized using the morphology image of a point-source, which encourages the model to be compact, but still allows the morphology image to be extended.
-The flat-sky source has uniform color and morphology within the bounding box.
-
-The deblending step is designed to model the sources in the vicinity of the target object.
-Therefore, the size of the target object determines which peaks are relevant.
-We draw a square bounding box around the target object and model all the peaks inside this box.
-The size of the bounding box is determined as we initialize the model for the target object, described as follows.
-
-We use an extended source model with two components to describe the target object, such that the model is able to capture the galaxy structure and color gradient.
-The source is initialized as follows.
-We convolve the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise.
-After smoothing, the LSB outskirts of the target galaxy become more prominent, which helps in determining the bounding box and initializing the morphology image.
-We take the smoothed image and threshold it with $0.1\sigma$ to remove the sky noise.
-The initial morphology image $S_i$ is determined by constructing a symmetric and monotonic approximation to the smoothed image around the target object.
-The initial SED vector $A_i$ is set to be the sum of the morphology matrices $S_i$ in each band.
-As a byproduct of initialization, we get a bounding box from $S_i$ which indicates the extent of the target object.
-Consequently, the size of the bounding box depends on the smoothing kernel and the threshold.
-We choose the above values by trial and error such that the box is not so large as to include many irrelevant peaks, but not so small as to lose the flux from the target galaxy.
-
-Then we take all peaks within the bounding box of the target galaxy and initialize them in the same way.
-Recall that we have two rounds of peak detection (Sec \ref{sec:peak}), focusing on extended and compact sources respectively.
-The extended objects detected in the first peak detection step are modeled as single-extended sources.
-For compact objects that are only detected in the second peak detection, we model them as point sources if their FWHM $<$ 5 pixels, otherwise as compact-extended sources.
-We also add a flat-sky source to model the local sky around the target.
-This is helpful for situations where an object overlaps with the LSB outskirts of a bright galaxy (e.g., the bottom panel in Figure \ref{fig:vanilla_scarlet_demo}).
-
-As mentioned above, we only model peaks within the bounding box of the target.
-However, scattered light from nearby bright stars and galaxies could bias the modeling of sources within the bounding box (e.g., the yellow star in the top left panel of Figure \ref{fig:vanilla_scarlet_demo}).
-We match our field with the Gaia catalog \citep{GAIA2016,GAIA2018} and mask out stars outside of the bounding box.
-Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.
-
-We demonstrate the above procedures in Figure \ref{fig:vanilla_scarlet_demo} with two examples.
-The one shown in the top panels is a blue LSBG, whereas the one shown on the bottom is a high-$z$ galaxy blended with the outskirts of a nearby galaxy which falls in our initial sample as a false positive.
-The first column shows the $griz$ color-composite image \citep{Lupton2004}, where the white boxes mark the bounding box of each source in the scene.
-The gray shades over objects outside of the target bounding box indicate they are masked out.
-The second column shows the initial \code{scarlet} models.
-They look fuzzy because they are constructed from the smoothed image, but they capture the color and the faint outskirts of the LSBG quite well.
-
-The optimization process uses the adaptive proximal gradient method \citep{Melchior2019}, which is a robust method for optimization with constraints.
-The model is considered to be converged when the relative changes of parameters are smaller than \code{e\_rel\,=\,2e-4}.
-Typically, convergence is achieved after $\sim 50$ steps of optimization and the whole modeling takes about 40s for a typical LSBG.
-It takes longer when the target galaxy has large angular size since more peaks are modeled.
-The optimized model is shown in the middle column of Figure \ref{fig:vanilla_scarlet_demo} after convolving with the PSF, and the fourth column shows the residual image.
-The fifth column shows the optimized model only for the target object.
-
-We notice that the optimized model of the blue LSBG captures its color and morphology quite well.
-For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact.
-The reason why it passes our initial selection is that the galaxy outskirts are shredded by SourceExtractor and happen to have a large size and the right color.
-But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.
-
-\subsubsection{Measurement and false positive removal}\label{sec:non-par-measurement}
+\subsubsection{False positive removal}\label{sec:non-par-measurement}
 
@@
 After running the vanilla scarlet for LSBG candidates, we successfully deblend the target object from nearby sources.
-Unlike other modeling codes, the non-parametric \code{scarlet} model is very flexibly modeling galaxies with complex structures.
+Unlike other parametric modeling methods, the non-parametric \code{scarlet} model is very flexible on modeling galaxies with complex structures.
 But the non-parametric nature of the code means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model.
@@
 We refer the reader to \citet{statmorph} for more details on their definitions and implementations.
-The morphological and structural parameters are the same in different bands by construction in the \code{scarlet} model.
+We measure the morphological and structural parameters in $g$-band.
+%The morphological and structural parameters are the same in different bands by construction in the \code{scarlet} model.
 
 To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the labels to construct the metrics.
-We randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see \S \ref{sec:match} for details).
+To be specific, we randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see \S\ref{sec:match} for details).
 We run vanilla scarlet for all of them and measure morphological parameters as described above.
 Then we do visual inspection by looking at the $griz$ color-composite images with 0.5 arcmin on a side.
-Objects are classified into three types: \code{candy} (LSB galaxies with typically dwarf galaxy features), \code{galaxy} (high surface brightness galaxies, or galaxies with spiral galaxy features), and \code{junk} (false positives, including tidal streams, galaxy outskirts blends, and other artifacts).
+Objects are classified into three types: LSB galaxies with typically dwarf galaxy features (dubbed \code{candy}), high surface brightness galaxies, or galaxies with spiral galaxy features (\code{galaxy}), and false positives including tidal streams, galaxy outskirts blends, and other artifacts (\code{junk}).
 The difference between \code{candy} and \code{galaxy} can be quite ambiguous.
@@
 non-LSBG), there will be little way to change later.
-On the contrary, our cuts based on the measured properties can be tweaked to be more complete (including more junk) or be more pure (aggressive cuts) depending on the specific science goal.
+On the contrary, our cuts based on the measured properties can be tweaked to have higher completeness  (including more junk) or have higher purity (aggressive cuts) depending on the specific science goal.
 The visual inspection labels only guide us to design those metrics.
 This measurement-based method is more intuitive, reproducible, and transferable.
-We will also explore machine learning methods and compare with our deblending cuts in future work.
-We would also like to utilize information about Milky Way dust to exclude spurious detection on Galactic cirrus \citep{Zaritsky2021,Zaritsky2022}.
+We will also explore machine learning methods and compare with our deblending cuts in future works.
+We would also like to utilize information about Milky Way dust to exclude spurious detection on Galactic cirrus \citep[e.g.,][]{Zaritsky2021,Zaritsky2022}.
 
@@
 {\bf My proposal is to keep this entire discussion in main paper, not appendix, but I think it can be shortened a bit}
+
+% Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with the positions of detected peaks.
 
@@
 \subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}
-The completeness of the LSBG search is important not only for understanding our search efficiency and improving the method in the future, but also for deriving the completeness-corrected results for LSBG sciences.
-Similar to many other works \citep[e.g.,][]{vdBurg2017,Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and recovering them from the image.
-Using these mock galaxies, we also characterize the measurement bias and uncertainty by comparing the measured properties with the truth.
-
-{\bf I think you can combine 3.4.1 and 3.4.2, and put most of this into the Appendix, just introduce the idea of the simulations and show the figure.
-I'd keep the comparison with other works in the main body of the paper.}
-
 \begin{figure*}
@@
 \end{figure*}
-\subsubsection{Completeness}\label{sec:completeness}
+
+The completeness of the LSBG search is important not only for understanding our search efficiency and improving the method in the future, but also for deriving the completeness-corrected results for LSBG sciences.
+Similar to many other works \citep[e.g.,][]{vdBurg2017,Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and recovering them from the image.
+Using these mock galaxies, we also characterize the measurement bias and uncertainty by comparing the measured properties with the truth.
+We present the main steps below and describe details in Appendix \ref{ap:comp_meas_unc}.
+
 A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}).
@@
 We performed a large suite of image simulations to derive the completeness.
+We inject single \sersic{} light profile \citep{Sersic1963} to the coadd images and try do recover them using the detection method (\S\ref{sec:detection}), model them using vanilla \code{scarlet} (\S\ref{sec:deblending}), and apply the deblending cuts.
+The mock \sersic{} galaxies span a wide range in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$) and surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$).
 The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.
 
-For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
-This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
-However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}.
-To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
-They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
-Then we run the detection step as described in \S \ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
-We split the size and surface brightness range into 15 bins with $\Delta r_e = 0.86\arcsec$, $\Delta \sbeff = 0.33\ \sbunit$, and interpolate over bins using an isotropic Gaussian kernel with $\sigma = 0.5$.
-We notice that the size and surface brightness shown in Figure \ref{fig:completeness} are all the intrinsic values for the mock galaxies, which are different from the measured ones.
-We discuss measurement biases in Section \ref{sec:meas_unc}.
-
-We find that the detection completeness mainly depends on the size and surface brightness.
-As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
+We find that the completeness mainly depends on the size and surface brightness.
+As shown in Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
 It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$.
-We find negligible dependence of completeness on \sersic{} index, color, and ellipticity.
-Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
-We find the completeness declines for $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
-Please see \citet{Greene2022} for more details.}
-
-For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
-The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
-We measure the size and surface brightness on the scarlet models of the mock galaxies, then we apply the deblending cuts.
-The deblending completeness as a function of size and surface brightness is shown in the middle panel of Figure \ref{fig:completeness}.
-The deblending completeness is very high at the bright end, but starts to decline with increasing size and surface brightness.
+The deblending completeness is very high at the bright end, but starts to decline with increasing size and decreasing surface brightness.
 Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
@@
 We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-Although \sersic galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic model still sets a baseline or upper limit on the real completeness.
+Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness.
 In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).
@@
 
-\subsubsection{Measurement bias and uncertainty}\label{sec:meas_unc}
-
 \begin{figure*}
@@
 
-Due to the low surface brightness nature of LSBGs, their size, magnitude, surface brightness and shape are hard to characterize and are typically associated with large uncertainties.
+The size, magnitude, surface brightness, and shape of LSBGs are hard to characterize because of the low surface brightness nature. 
+\citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects.
+In the low surface brightness regime, the measured size and total magnitude can be quite biased and have large uncertainties.
+Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs.
+\citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth.
+\citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network.
+In this paper, we simply take the former method because of its simplicity.
+
+We perform the Spergel profile modeling (as described in \S\ref{sec:modeling}) for the mock \sersic{} galaxies and compare the modeling results with the ground truth.
+We find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
+For surface brightnesses fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
+As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than reality.
+Similar to \citet{Zaritsky2021}, we derive the measurement biases and uncertainties in size, surface brightness, total magnitude, and color as a function of size and surface brightness.
+We refer interested readers to Appendix \ref{ap:comp_meas_unc} for details.
+The main results are shown in Figure \ref{fig:meas_err}, where the colors show the bias terms as a function of the measured size and surface brightness.
+The size and surface brightness bias grows with increasing surface brightness.
+The bias term is not a monotonic function of size because the size here is not intrinsic size.
+It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
+We also find the bias in $g-i$ color to be quite small.
+The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the biases.
+We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
+
+In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on bias-corrected properties.
+We also incorporate the measurement errors into the science figures.
+The values presented in our catalogs are already bias-corrected, but we do provide the bias values for reference.
+
+% {\bf I think you can combine 3.4.1 and 3.4.2, and put most of this into the Appendix, just introduce the idea of the simulations and show the figure.
+I'd keep the comparison with other works in the main body of the paper.}
+
+\subsubsection{Completeness}\label{sec:completeness}
+A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}).
+Thus, the overall completeness is a combination of detection completeness and deblending completeness.
+We performed a large suite of image simulations to derive the completeness.
+The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.
+
+For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
+This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
+However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}.
+To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
+They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
+Then we run the detection step as described in \S \ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
+We split the size and surface brightness range into 15 bins with $\Delta r_e = 0.86\arcsec$, $\Delta \sbeff = 0.33\ \sbunit$, and interpolate over bins using an isotropic Gaussian kernel with $\sigma = 0.5$.
+We notice that the size and surface brightness shown in Figure \ref{fig:completeness} are all the intrinsic values for the mock galaxies, which are different from the measured ones.
+We discuss measurement biases in Section \ref{sec:meas_unc}.
+
+We find that the detection completeness mainly depends on the size and surface brightness.
+As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
+It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$.
+We find negligible dependence of completeness on \sersic{} index, color, and ellipticity.
+Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
+We find the completeness declines for $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
+Please see \citet{Greene2022} for more details.}
+
+For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
+The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
+We measure the size and surface brightness on the scarlet models of the mock galaxies, then we apply the deblending cuts.
+The deblending completeness as a function of size and surface brightness is shown in the middle panel of Figure \ref{fig:completeness}.
+The deblending completeness is very high at the bright end, but starts to decline with increasing size and surface brightness.
+Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
+Interestingly, the detection completeness and deblending completeness all drop below 40\% around $\sbeff=27.5\ \sbunit$.
+In this sense, the detection and deblending cooperate well in terms of completeness.
+
+The combined completeness is shown in the right panel of Figure \ref{fig:completeness}.
+The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours.
+The completeness drops as we go to fainter surface brightness and smaller size.
+We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
+Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness.
+In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).
+
+We compare our completeness with that of other LSBG searches.
+Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more quickly with increasing size.
+\citet{CarlstenELVES2022} use a similar search algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$ assuming a Sersic index $n \approx 1$.
+\citet{vdBurg2017} searched LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
+\citet{Zaritsky2021} focus on searching for LSBGs in the SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) images and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$ for $n=1$.
+Their low completeness might be explained by the fact that they remove a large fraction of the sky contaminated by Galactic dust.
+\citet{Tanoglidis2021} conducted an LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
+\citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but much smaller completeness above $\sbeff > 26.5\ \sbunit$.
+The Dragonfly Wide Field Survey \citep{Danieli2020} reaches $\sim 29\ \sbunit$ for $>3\sigma$ detection on scales $\sim 1\arcmin$, which is deeper than all other surveys by sacrificing spatial resolution.
+In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies \citep[e.g.,][]{Huang2018,Kado-Fong2018}.
+
+\subsubsection{Measurement bias and uncertainty}\label{sec:meas_unc}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
+	}
+    \caption{The measurement bias and uncertainty as a function of measured angular size $r_e$ and surface brightness $\sbeff$.
+The colors show the bias term while the dashed contours show the constant uncertainty lines.
+We derive the bias in the total magnitudes from the combined bias in $r_e$, $\sbeff$, and color.
+We find that the bias and uncertainty in our measurement increase toward the fainter end.
+We apply the bias correction to the real LSBGs before studying their physical properties.}
+    \label{fig:meas_err}
+\end{figure*}
+
+Due to the low surface brightness nature of LSBGs, their size, magnitude, surface brightness, and shape are hard to characterize and are typically associated with large uncertainties.
 \citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects.
@@
 With enough statistics in the future, one might be able to characterize the shape of the large-size tail and define UPGs based on the percentiles of the size distribution.
-However, there are also other size definitions which help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Mowla2019,Trujillo2020} and can further benefit construct UPG samples.
+However, there are also other size definitions which help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Mowla2019,Trujillo2020,Chamba2022} and can further benefit construct UPG samples.
 
@@
 \section{Deblending details}\label{ap:deblending}
+
+\subsection{Peak detection}\label{sec:peak}
+We generate cutout images with a size of $1\arcmin$ in the $griz$-bands for each LSBG candidate in our initial sample.
+We then construct a detection image by taking an average of the four bands weighted by the inverse variance of each band.
+This detection image is considered to be deeper than the single-band images.
+Next, we run \code{sep} on the detection image using a threshold of 4$\sigma$ above the sky, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels.
+This step identifies extended sources in the detection image.
+However, there are still faint and compact peaks not detected.
+We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep the high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering in the context of LSBGs).
+Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels.
+This step detects many compact sources that were not included in the previous step.
+In the end, we combine the two detection catalogs and remove duplicates.
+
+\subsection{Model initialization and optimization}
+
+After peak detection, we need to decide which peaks to model, and we would like to initialize the model as best as we can.
+We note that \code{scarlet} optimizes the model instead of deriving the full posteriors, thus good initialization becomes really important.
+We tackle these problems as follows.
+
+In vanilla scarlet, objects can be modeled with different types of models as follows.
+The point source has a morphology image simply be the normalized PSF.
+The single-extended source has a morphology image that follows positivity and monotonicity constraints.
+The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient.
+The compact source is a single-extended source initialized using the morphology image of a point-source, which encourages the model to be compact, but still allows the morphology image to be extended.
+The flat-sky source has uniform color and morphology within the bounding box.
+
+The deblending step is designed to model the sources in the vicinity of the target object.
+Therefore, the size of the target object determines which peaks are relevant.
+We draw a square bounding box around the target object and model all the peaks inside this box.
+The size of the bounding box is determined as we initialize the model for the target object, described as follows.
+
+We use an extended source model with two components to describe the target object, such that the model is able to capture the galaxy structure and color gradient.
+The source is initialized as follows.
+We convolve the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise.
+After smoothing, the LSB outskirts of the target galaxy become more prominent, which helps in determining the bounding box and initializing the morphology image.
+We take the smoothed image and threshold it with $0.1\sigma$ to remove the sky noise.
+The initial morphology image $S_i$ is determined by constructing a symmetric and monotonic approximation to the smoothed image around the target object.
+The initial SED vector $A_i$ is set to be the sum of the morphology matrices $S_i$ in each band.
+As a byproduct of initialization, we get a bounding box from $S_i$ which indicates the extent of the target object.
+Consequently, the size of the bounding box depends on the smoothing kernel and the threshold.
+We choose the above values by trial and error such that the box is not so large as to include many irrelevant peaks, but not so small as to lose the flux from the target galaxy.
+
+Then we take all peaks within the bounding box of the target galaxy and initialize them in the same way.
+Recall that we have two rounds of peak detection (Sec \ref{sec:peak}), focusing on extended and compact sources respectively.
+The extended objects detected in the first peak detection step are modeled as single-extended sources.
+For compact objects that are only detected in the second peak detection, we model them as point sources if their FWHM $<$ 5 pixels, otherwise as compact-extended sources.
+We also add a flat-sky source to model the local sky around the target.
+This is helpful for situations where an object overlaps with the LSB outskirts of a bright galaxy (e.g., the bottom panel in Figure \ref{fig:vanilla_scarlet_demo}).
+
+As mentioned above, we only model peaks within the bounding box of the target.
+However, scattered light from nearby bright stars and galaxies could bias the modeling of sources within the bounding box (e.g., the yellow star in the top left panel of Figure \ref{fig:vanilla_scarlet_demo}).
+We match our field with the Gaia catalog \citep{GAIA2016,GAIA2018} and mask out stars outside of the bounding box.
+Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.
+
+We demonstrate the above procedures in Figure \ref{fig:vanilla_scarlet_demo} with two examples.
+The one shown in the top panels is a blue LSBG, whereas the one shown on the bottom is a high-$z$ galaxy blended with the outskirts of a nearby galaxy which falls in our initial sample as a false positive.
+The first column shows the $griz$ color-composite image \citep{Lupton2004}, where the white boxes mark the bounding box of each source in the scene.
+The gray shades over objects outside of the target bounding box indicate they are masked out.
+The second column shows the initial \code{scarlet} models.
+They look fuzzy because they are constructed from the smoothed image, but they capture the color and the faint outskirts of the LSBG quite well.
+
+The optimization process uses the adaptive proximal gradient method \citep{Melchior2019}, which is a robust method for optimization with constraints.
+The model is considered to be converged when the relative changes of parameters are smaller than \code{e\_rel\,=\,2e-4}.
+Typically, convergence is achieved after $\sim 50$ steps of optimization and the whole modeling takes about 40s for a typical LSBG.
+It takes longer when the target galaxy has large angular size since more peaks are modeled.
+The optimized model is shown in the middle column of Figure \ref{fig:vanilla_scarlet_demo} after convolving with the PSF, and the fourth column shows the residual image.
+The fifth column shows the optimized model only for the target object.
+
+We notice that the optimized model of the blue LSBG captures its color and morphology quite well.
+For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact.
+The reason why it passes our initial selection is that the galaxy outskirts are shredded by SourceExtractor and happen to have a large size and the right color.
+But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.
 
@@
 It is thus reasonalbe to use Spergel profiles to model the LSBGs (Sec \ref{sec:modeling}) and enjoy its convenience in the Fourier space.
+
+\section{Completeness and Measurement Uncertainty}\label{ap:comp_meas_unc}
+A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}).
+Thus, the overall completeness is a combination of detection completeness and deblending completeness.
+We performed a large suite of image simulations to derive the completeness.
+The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.
+
+For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
+This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
+However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}.
+To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
+They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
+Then we run the detection step as described in \S \ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
+We split the size and surface brightness range into 15 bins with $\Delta r_e = 0.86\arcsec$, $\Delta \sbeff = 0.33\ \sbunit$, and interpolate over bins using an isotropic Gaussian kernel with $\sigma = 0.5$.
+We notice that the size and surface brightness shown in Figure \ref{fig:completeness} are all the intrinsic values for the mock galaxies, which are different from the measured ones.
+We discuss measurement biases in Section \ref{sec:meas_unc}.
+
+We find that the detection completeness mainly depends on the size and surface brightness.
+As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
+It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$.
+We find negligible dependence of completeness on \sersic{} index, color, and ellipticity.
+Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
+We find the completeness declines for $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
+Please see \citet{Greene2022} for more details.}
+
+For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
+The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
+We measure the size and surface brightness on the scarlet models of the mock galaxies, then we apply the deblending cuts.
+The deblending completeness as a function of size and surface brightness is shown in the middle panel of Figure \ref{fig:completeness}.
+The deblending completeness is very high at the bright end, but starts to decline with increasing size and surface brightness.
+Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
+Interestingly, the detection completeness and deblending completeness all drop below 40\% around $\sbeff=27.5\ \sbunit$.
+In this sense, the detection and deblending cooperate well in terms of completeness.
+
+The combined completeness is shown in the right panel of Figure \ref{fig:completeness}.
+The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours.
+The completeness drops as we go to fainter surface brightness and smaller size.
+We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
+Although \sersic galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic model still sets a baseline or upper limit on the real completeness.
+In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).
+
+We compare our completeness with that of other LSBG searches.
+Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more quickly with increasing size.
+\citet{CarlstenELVES2022} use a similar search algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$ assuming a Sersic index $n \approx 1$.
+\citet{vdBurg2017} searched LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
+\citet{Zaritsky2021} focus on searching for LSBGs in the SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) images and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$ for $n=1$.
+Their low completeness might be explained by the fact that they remove a large fraction of the sky contaminated by Galactic dust.
+\citet{Tanoglidis2021} conducted an LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
+\citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but much smaller completeness above $\sbeff > 26.5\ \sbunit$.
+The Dragonfly Wide Field Survey \citep{Danieli2020} reaches $\sim 29\ \sbunit$ for $>3\sigma$ detection on scales $\sim 1\arcmin$, which is deeper than all other surveys by sacrificing spatial resolution.
+In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies \citep[e.g.,][]{Huang2018,Kado-Fong2018}.
+
+\subsubsection{Measurement bias and uncertainty}\label{sec:meas_unc}
+
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
+	}
+    \caption{The measurement bias and uncertainty as a function of measured angular size $r_e$ and surface brightness $\sbeff$.
+The colors show the bias term while the dashed contours show the constant uncertainty lines.
+We derive the bias in the total magnitudes from the combined bias in $r_e$, $\sbeff$, and color.
+We find that the bias and uncertainty in our measurement increase toward the fainter end.
+We apply the bias correction to the real LSBGs before studying their physical properties.}
+    \label{fig:meas_err}
+\end{figure*}
+
+Due to the low surface brightness nature of LSBGs, their size, magnitude, surface brightness and shape are hard to characterize and are typically associated with large uncertainties.
+\citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects.
+In the low surface brightness regime, the measured size and total magnitude can be quite biased and have large uncertainties.
+Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs.
+\citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth.
+\citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network.
+In this paper, we simply take the former method because of its simplicity.
+
+In order to test how well we recover the photometric and structural parameters in the our measurement (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
+We compare the fitting results with the ground truth, and we find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
+For surface brightnesses fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
+As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than reality.
+
+Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shape.
+However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index.
+Thus we just model the bias and uncertainty as a function of the \textit{measured} angular size $r_e$ and surface brightness $\sbeff$.
+
+Given the size and surface brightness of our simulated galaxies, we set the range of the observed size and surface brightness to be $r_e\in[1\arcsec, 15\arcsec],\ \sbeff\in[23, 29]\,\sbunit$.
+We then split the observed $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias $\Delta X = X_{\rm truth} - X_{\rm meas}$ within each bin, where $X=\{\sbeff,\ g-i,\ g-r\}$.
+For $r_e$, we calculate the relative bias $\Delta r_e / r_e$ instead because it is less dependent on the angular size.
+Then we interpolate over the grid using a multi-quadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
+Unlike \citet{Zaritsky2021} where they fit models in 4-D space, we find interpolation works well enough in 2D and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
+We emphasize that the bias and uncertainty are modeled to be functions of the measured properties, not intrinsic ones, such that we can correct for bias based on our measurements.
+
+In Figure \ref{fig:meas_err}, the colors show the interpolated bias terms as a function of the measured size and surface brightness.
+The size and surface brightness bias grows with increasing surface brightness.
+The bias term is not a monotonic function of size because the size here is not intrinsic size.
+It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
+We also find the bias in $g-i$ color to be quite small.
+
+For LSBGs in our sample, we apply corrections for the bias using the interpolated bias terms.
+We first correct for the bias in size, $g$-band average surface brightness, $g-r$ and $g-i$ colors.
+Then we calculate the $g$-band total magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$.
+The magnitudes and surface brightnesses in other bands are derived using $g$-band magnitude, surface brightness, and colors.
+In this way, we apply a self-consistent correction for the measurement biases to the data.
+
+The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, neighboring contamination, etc.
+Unlike other parametric modeling codes, \code{scarlet} does not explore the full posterior space but rather finds one optimal solution.
+Thus we have no access to the statistical error on the measured properties from \code{scarlet}.
+Fortunately, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor.
+Following the same method as that of calculating the bias, in each bin we compute the $1\sigma$ standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid.
+The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the biases.
+We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
+
+In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on bias-corrected properties.
+We also incorporate the measurement errors into the science figures.
+The values presented in our catalogs are already bias-corrected, but we do provide the bias values for reference.
 

### 2022-10-09 paper1.tex
finished moving some of Sec 3 to Appendix

@@
 Spergel profile modeling & \S\ref{sec:modeling}, \S\ref{sec:match} & 2,510\\
-Completeness & \S\ref{sec:completeness} & 2,510 \\
-Measurement error and uncertainty & \S\ref{sec:meas_unc} & 2,510\\
+Completeness & \S\ref{sec:comp_meas},\S\ref{ap:comp_meas_unc} & 2,510 \\
+Measurement error and uncertainty & \S\ref{sec:comp_meas},\S\ref{ap:comp_meas_unc} & 2,510\\
 Mass-size outlier selection & \S\ref{sec:sample} & 362 (UPG), 432 (UDG)
@@
 Bright objects and their diffuse light are identified using surface brightness thresholding.
-Then we run a detection using \code{sep} \citep{Barbary2016} to remove small compact sources and noisy peaks and replace their footprints with sky noise.
+Then we run a detection using \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} to remove small compact sources and noisy peaks and also replace their footprints with sky noise.
 We use \code{SourceExtractor} to detect sources on the ``cleaned'' images with a low detection threshold.
@@
 	}
-	\caption{A demonstration of the deblending step as described in \S\ref{sec:deblending}.
-Here we show two objects from our initial sample (\S\ref{sec:detection}): the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts.
+	\caption{A demonstration of the deblending step as described in \S\ref{sec:deblending} and \S\ref{ap:deblending}.
+Here we show two objects from our initial sample: the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts.
 The data shown in the first column is $griz$ color-composite image with the bounding boxes overlay.
 The objects covered by the gray shades are masked during fitting.
-The bounding boxes and the initial models (second column) are determined from the smoothed image.
-The remaining columns show the optimized models (PSF convolved), residual image, and the only target galaxy itself.
+The remaining columns show the initial model, optimized models (PSF convolved), residual image, and the optimized model of the target galaxy only.
 	}
@@
 The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample this assumption still holds for most cases and provides an effective and robust way to deblend overlapping sources.
-We refer to this modeling method as \textit{vanilla scarlet}.
+We refer to this modeling method as \textit{vanilla \code{scarlet}}.
 
@@
 
-We use vanilla scarlet to model the LSBG candidate and extract structural and morphological parameters from the \code{scarlet} model, which are further used to exclude false positives from our LSBG sample.
+We use vanilla \code{scarlet} to model the LSBG candidate and extract structural and morphological parameters from the \code{scarlet} model, which are further used to exclude false positives from our LSBG sample.
 In the following subsections, we briefly describe how we detect peaks on the image, initialize and optimize \code{scarlet} models.
@@
 
-After running the vanilla scarlet for LSBG candidates, we successfully deblend the target object from nearby sources.
+After running the vanilla \code{scarlet} for LSBG candidates, we successfully deblend the target object from nearby sources.
 Unlike other parametric modeling methods, the non-parametric \code{scarlet} model is very flexible on modeling galaxies with complex structures.
@@
 The variance map and PSF are taken from HSC cutouts.
-We also force the sky level to be zero because sky has already been fit when running vanilla scarlet.
+We also force the sky level to be zero because sky has already been fit when running vanilla \code{scarlet}.
 
@@
 The total magnitudes are simply calculated by summing up the model in each band, and colors are defined using total magnitudes.\footnote{A Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
-We define the average surface brightness within the effective radius as $\mu_{\rm eff} = m - 2.5 \log_{10}(2 \pi r_e^2)$, where $m$ is the total magnitude.
+We define the average surface brightness within the effective radius as
+\begin{equation}\label{eq:mu_eff}
+    \mu_{\rm eff} = m - 2.5 \log_{10}(2 \pi r_e^2),
+\end{equation}
+where $m$ is the total magnitude.
 
@@
 To be specific, we randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see \S\ref{sec:match} for details).
-We run vanilla scarlet for all of them and measure morphological parameters as described above.
+We run vanilla \code{scarlet} for all of them and measure morphological parameters as described above.
 Then we do visual inspection by looking at the $griz$ color-composite images with 0.5 arcmin on a side.
@@
 Furthermore, the completeness of real LSBG detection remains high.
-In Section \ref{sec:completeness}, we characterize the completeness of this ``deblending'' step by injecting mock \sersic{} galaxies, and we achieve $\sim80\%$ completeness at $\sbeff = 27.0\ \sbunit$ and $>50\%$ completeness at $\sbeff = 27.5\ \sbunit$ (Fig.
+In Section \ref{sec:comp_meas}, we characterize the completeness of this ``deblending'' step by injecting mock \sersic{} galaxies, and we achieve $\sim80\%$ completeness at $\sbeff = 27.0\ \sbunit$ and $>50\%$ completeness at $\sbeff = 27.5\ \sbunit$ (Fig.
 \ref{fig:completeness}).
-We emphasize that the vanilla scarlet modeling and non-parametric measurements are not designed to recover the intrinsic properties of the galaxies.
+We emphasize that the vanilla \code{scarlet} modeling and non-parametric measurements are not designed to recover the intrinsic properties of the galaxies.
 They are used only as a diagnostic tool to remove false positives.
@@
 
-{\bf My proposal is to keep this entire discussion in main paper, not appendix, but I think it can be shortened a bit}
-
 % Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with the positions of detected peaks.
 
-Although the vanilla scarlet modeling provides useful information to help us remove false positives, it does not necessarily give us unbiased estimations on size, color, total magnitude, etc.
-In fact, the vanilla scarlet model systematically under-estimates the size and the total flux of LSB objects.
-This is because the faint outskirts of LSBGs are typically not modeled well due to the non-parametric nature of vanilla scarlet.
-We elaborate this point as follows.
-
+Although the vanilla \code{scarlet} modeling provides useful information to help us remove false positives, it does not necessarily give us reliable estimations on size, color, total magnitude, etc.
+In fact, the vanilla \code{scarlet} model systematically under-estimates the size and the total flux of LSB objects.
+This is because the faint outskirts of LSBGs are typically not modeled well due to the non-parametric nature of vanilla \code{scarlet}.
 When doing parametric modeling such as \sersic{} fitting, we effectively apply radial averaging within elliptical annuli and boost the signal-to-noise ratio by binning pixels.
@@
 However, the non-parametric nature of vanilla \code{scarlet} only assumes monotonicity, which imposes quite weak correlations among pixels.
-Consequently, it is very hard for the non-parametric modeling to probe very low surface brightness features.
-Furthermore, the monotonicity constraint stops the model from growing in certain directions if there is another source along this direction, otherwise monotonicity is broken.
-This issue, dubbed the ``cookie-cutter effect'', can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model of the target object never exceeds the other objects next to it.
-As a result, the non-parametric model often does not capture well the LSB outskirts of LSBG, thus biasing the measurements.
-In the following, we explore a novel method to perform parametric fitting while exploiting the advantages of \code{scarlet}.
-
-A traditional way of doing parametric modeling is to first mask out contaminants based on the detection segmentation map, then fit a model to the masked image.
-However, the fitting results are very sensitive to the masking scheme \citep[e.g.,][]{Greco2018} and sky background.
-A possible solution to this problem is to simultaneously model all the objects in the cutout and the sky using parametric models (e.g., in DECaLS, \citealt{Dey2019}).
+Consequently, it is hard for the non-parametric modeling to probe very low surface brightness features.
+Furthermore, the monotonicity constraint stops the model from growing in certain directions if there is another source along this direction, otherwise monotonicity is broken.\footnote{This issue can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model of the target object never exceeds the other objects next to it.} As a result, the non-parametric model often does not capture well the LSB outskirts of LSBG, thus biasing the measurements.
+In the following, we explore a novel method to perform robust parametric modeling and measurement while exploiting the deblending power of \code{scarlet}.
+
+A traditional way of doing parametric modeling is to mask out contaminants based on the detection segmentation map and fit a model to the masked image.
+However, such fitting results are very sensitive to the masking scheme \citep[e.g.,][]{Greco2018} and sky background.
+A possible solution to this problem is to simultaneously model all the objects in the cutout and the sky using parametric models (e.g., in DECaLS, \citealt{Lang2016,Dey2019}).
 In this work, we combine the advantage of parametric modeling with the power of deblending in \code{scarlet}.
-To be specific, we follow the spirit of deblending as described in Section \ref{sec:deblending}, but replace the non-parametric model for the target with a parametric model.
+To be specific, we follow the spirit of deblending as described in \S\ref{sec:deblending}, but replace the non-parametric model for the target galaxy with a parametric model.
 In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized because they are modeled simultaneously in all bands with non-parametric models.
-The parametric model for the target object does not suffer from the ``cookie-cutter'' issue any more.
-
-We use the Spergel surface brightness profile \citep{Spergel2010} to model the LSBGs.
+The parametric model for the target object can also extend to the whole scene and not stopped by neighboring objects.
+
+In this work, we use the Spergel surface brightness profile \citep{Spergel2010} to model the LSBGs (see Appendix \ref{ap:spergel} for details).
 The Spergel profile is motivated by having a simple analytical expression in Fourier space, making it easy to convolve with a PSF.
-The surface brightness of a Spergel profile has the form:
-\begin{equation}
-    \label{eq:spergel}
-    I_\nu(r) = \frac{c_{\nu}^{2} L_{0}}{2\pi r_{0}^{2}} f_{\nu}\left(\frac{c_{\nu} r}{r_{0}}\right),
-\end{equation}
-where 
-\begin{equation}
-    f_{\nu}(u)=\left(\frac{u}{2}\right)^{\nu} \frac{K_{\nu}(u)}{\Gamma(\nu+1)},
-\end{equation}
-and $K_\nu(u)$ is the Modified Bessel function of the second kind.
-The half-light radius is $r_0$, the total luminosity is $L_0$, and $c_\nu$ satisfies the equation $(1 + \nu)f_{\nu + 1}(c_\nu) = 1/4$.
-Similar to the \sersic{} index, the parameter $\nu$ (dubbed as the ``Spergel index'') controls the concentration of the light profile.
+Similar to the \sersic{} index, the parameter $\nu$ in \eqref{eq:spergel} (dubbed as the ``Spergel index'') controls the concentration of the light profile.
 As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is relevant to the study of LSBGs.
@@
 We initialize the Spergel model for the target object differently, while other objects are still initialized in the same way as in the deblending step (Section \ref{sec:deblending}).
-First, we initialize a vanilla scarlet model for the target object, and we measure the effective radius $r_e$, total flux, and the shape of the scarlet model.
+First, we initialize a vanilla \code{scarlet} model for the target object, and we measure the effective radius $r_e$, total flux, and the shape of the scarlet model.
 We use these numbers to initialize the Spergel profile.
 The size of the bounding box is also updated to be the maximum between 250 pixels and $10\, r_e$.
-Peaks within this bounding box (other than the target) are modeled using vanilla scarlet.
+Peaks within this bounding box (other than the target) are modeled using vanilla \code{scarlet}.
 For the target, we still require a positivity constraint, and the monotonicity is automatically satisfied by the Spergel profile.
-
 After optimization, we take the $r_0$ in Equation \eqref{eq:spergel} as the circularized half-light radius $r_e$, and take $L_0$ as the total flux.
-The average surface brightness $\overline{\mu}_{\rm eff}$ is calculated in the same way as in Section \ref{sec:non-par-measurement}.
+The average surface brightness $\overline{\mu}_{\rm eff}$ is calculated in the same way as in \eqref{eq:mu_eff}.
+The Spergel modeling results are used for studying the properties of LSBGs.
 In the following section, we assess the quality of the Spergel modeling by injecting mock \sersic{} galaxies and comparing the recovered properties with truth.
@@
 	\caption{The completeness of our LSBG search as a function of effective radius $r_e$ and the average surface brightness $\sbeff$.
-We characterize the completeness by injecting mock \sersic{} galaxies into coadd images.
-The overall completeness (right panel) comprises the detection completeness (left panel, see \S \ref{sec:detection}) and deblending completeness (middle panel, see \S \ref{sec:deblending}) where false positives are removed.
+The overall completeness (right panel) comprises the detection completeness (left panel, see \S \ref{sec:detection}) and deblending completeness (middle panel, see \S \ref{sec:deblending}) where the false positives are removed.
 The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours.
-The completeness drops for smaller sizes and faint surface brightness.
+The completeness drops as we go to fainter surface brightness and smaller size.
 We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-The completeness drops as we go to fainter surface brightness and smaller size.
-	%The mock galaxies span a large range in size, surface brightness, \sersic{} index, color, and ellipticity. 
 	}
@@
 
+\vspace{1em}
+
 The size, magnitude, surface brightness, and shape of LSBGs are hard to characterize because of the low surface brightness nature.
-\citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects.
-In the low surface brightness regime, the measured size and total magnitude can be quite biased and have large uncertainties.
-Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs.
-\citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth.
-\citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network.
-In this paper, we simply take the former method because of its simplicity.
-
-We perform the Spergel profile modeling (as described in \S\ref{sec:modeling}) for the mock \sersic{} galaxies and compare the modeling results with the ground truth.
+We characterize the measurement quality by comparing the Spergel modeling results with the ground truth for mock \sersic{} galaxies.
 We find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
@@
 I'd keep the comparison with other works in the main body of the paper.}
-
-\subsubsection{Completeness}\label{sec:completeness}
-A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}).
-Thus, the overall completeness is a combination of detection completeness and deblending completeness.
-We performed a large suite of image simulations to derive the completeness.
-The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.
-
-For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
-This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
-However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}.
-To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
-They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
-Then we run the detection step as described in \S \ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
-We split the size and surface brightness range into 15 bins with $\Delta r_e = 0.86\arcsec$, $\Delta \sbeff = 0.33\ \sbunit$, and interpolate over bins using an isotropic Gaussian kernel with $\sigma = 0.5$.
-We notice that the size and surface brightness shown in Figure \ref{fig:completeness} are all the intrinsic values for the mock galaxies, which are different from the measured ones.
-We discuss measurement biases in Section \ref{sec:meas_unc}.
-
-We find that the detection completeness mainly depends on the size and surface brightness.
-As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
-It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$.
-We find negligible dependence of completeness on \sersic{} index, color, and ellipticity.
-Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
-We find the completeness declines for $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
-Please see \citet{Greene2022} for more details.}
-
-For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
-The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
-We measure the size and surface brightness on the scarlet models of the mock galaxies, then we apply the deblending cuts.
-The deblending completeness as a function of size and surface brightness is shown in the middle panel of Figure \ref{fig:completeness}.
-The deblending completeness is very high at the bright end, but starts to decline with increasing size and surface brightness.
-Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
-Interestingly, the detection completeness and deblending completeness all drop below 40\% around $\sbeff=27.5\ \sbunit$.
-In this sense, the detection and deblending cooperate well in terms of completeness.
-
-The combined completeness is shown in the right panel of Figure \ref{fig:completeness}.
-The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours.
-The completeness drops as we go to fainter surface brightness and smaller size.
-We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness.
-In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).
-
-We compare our completeness with that of other LSBG searches.
-Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more quickly with increasing size.
-\citet{CarlstenELVES2022} use a similar search algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$ assuming a Sersic index $n \approx 1$.
-\citet{vdBurg2017} searched LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
-\citet{Zaritsky2021} focus on searching for LSBGs in the SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) images and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$ for $n=1$.
-Their low completeness might be explained by the fact that they remove a large fraction of the sky contaminated by Galactic dust.
-\citet{Tanoglidis2021} conducted an LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
-\citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but much smaller completeness above $\sbeff > 26.5\ \sbunit$.
-The Dragonfly Wide Field Survey \citep{Danieli2020} reaches $\sim 29\ \sbunit$ for $>3\sigma$ detection on scales $\sim 1\arcmin$, which is deeper than all other surveys by sacrificing spatial resolution.
-In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies \citep[e.g.,][]{Huang2018,Kado-Fong2018}.
-
-\subsubsection{Measurement bias and uncertainty}\label{sec:meas_unc}
-
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
-	}
-    \caption{The measurement bias and uncertainty as a function of measured angular size $r_e$ and surface brightness $\sbeff$.
-The colors show the bias term while the dashed contours show the constant uncertainty lines.
-We derive the bias in the total magnitudes from the combined bias in $r_e$, $\sbeff$, and color.
-We find that the bias and uncertainty in our measurement increase toward the fainter end.
-We apply the bias correction to the real LSBGs before studying their physical properties.}
-    \label{fig:meas_err}
-\end{figure*}
-
-Due to the low surface brightness nature of LSBGs, their size, magnitude, surface brightness, and shape are hard to characterize and are typically associated with large uncertainties.
-\citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects.
-In the low surface brightness regime, the measured size and total magnitude can be quite biased and have large uncertainties.
-Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs.
-\citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth.
-\citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network.
-In this paper, we simply take the former method because of its simplicity.
-
-In order to test how well we recover the photometric and structural parameters in the our measurement (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
-We compare the fitting results with the ground truth, and we find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
-For surface brightnesses fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
-As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than reality.
-
-Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shape.
-However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index.
-Thus we just model the bias and uncertainty as a function of the \textit{measured} angular size $r_e$ and surface brightness $\sbeff$.
-
-Given the size and surface brightness of our simulated galaxies, we set the range of the observed size and surface brightness to be $r_e\in[1\arcsec, 15\arcsec],\ \sbeff\in[23, 29]\,\sbunit$.
-We then split the observed $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias $\Delta X = X_{\rm truth} - X_{\rm meas}$ within each bin, where $X=\{\sbeff,\ g-i,\ g-r\}$.
-For $r_e$, we calculate the relative bias $\Delta r_e / r_e$ instead because it is less dependent on the angular size.
-Then we interpolate over the grid using a multi-quadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
-Unlike \citet{Zaritsky2021} where they fit models in 4-D space, we find interpolation works well enough in 2D and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
-We emphasize that the bias and uncertainty are modeled to be functions of the measured properties, not intrinsic ones, such that we can correct for bias based on our measurements.
-
-In Figure \ref{fig:meas_err}, the colors show the interpolated bias terms as a function of the measured size and surface brightness.
-The size and surface brightness bias grows with increasing surface brightness.
-The bias term is not a monotonic function of size because the size here is not intrinsic size.
-It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
-We also find the bias in $g-i$ color to be quite small.
-
-For LSBGs in our sample, we apply corrections for the bias using the interpolated bias terms.
-We first correct for the bias in size, $g$-band average surface brightness, $g-r$ and $g-i$ colors.
-Then we calculate the $g$-band total magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$.
-The magnitudes and surface brightnesses in other bands are derived using $g$-band magnitude, surface brightness, and colors.
-In this way, we apply a self-consistent correction for the measurement biases to the data.
-
-The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, neighboring contamination, etc.
-Unlike other parametric modeling codes, \code{scarlet} does not explore the full posterior space but rather finds one optimal solution.
-Thus we have no access to the statistical error on the measured properties from \code{scarlet}.
-Fortunately, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor.
-Following the same method as that of calculating the bias, in each bin we compute the $1\sigma$ standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid.
-The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the biases.
-We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
-
-In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on bias-corrected properties.
-We also incorporate the measurement errors into the science figures.
-The values presented in our catalogs are already bias-corrected, but we do provide the bias values for reference.
 
@@
 In our UDG sample, there are 412 UDGs associated with 258 hosts.
-After correcting for background contamination (see \S \ref{sec:bkg}) and completeness (see \S \ref{sec:completeness}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host.
+After correcting for background contamination (see \S \ref{sec:bkg}) and completeness (see \S \ref{sec:comp_meas}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host.
 The UPG abundance in our sample is $N_{\rm UPG} = 0.61\pm 0.04$ per host.
@@
 \section{LSBG detection}\label{ap:detection}
+In this appendix, we provide a more detailed description on our LSBG search method and how it is different from \citetalias{Greco2018}.
+
 \subsection{Bright source removal}
@@
 In \citetalias{Greco2018}, the thresholds are set based on the noise level of the local sky.
-Thanks to the global sky subtraction in PDR2, LSB features are well conserved after subtracting the sky and the sky noise level varies less.
+Thanks to the global sky subtraction in HSC PDR2, LSB features are well conserved after subtracting the sky and the sky noise level varies less.
 Therefore, it makes more sense to set the thresholds based on the characteristic surface brightness instead of a certain sigma value above the sky background.
@@
 We add an extra step to detect and remove them since our main goal is to detect extended LSBGs.
-We run \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} on the ``cleaned'' images as described above.
+We run \code{sep} on the ``cleaned'' images as described above.
 Based on the segmentation map, we generate a mask for sources smaller than $r_{\rm min} = 2\arcsec$, and pixels within this mask are also replaced by sky noise.
 This step significantly improves the purity of LSBG search.
-The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by the completeness tests (\S \ref{sec:completeness}).
+The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by the completeness tests (see \S \ref{sec:comp_meas},\S\ref{ap:comp_meas_unc}).
 % This step effectively cleans out objects and features that hinder the detection of LSBGs.
@@
 \subsection{Source Extraction}
-We use \href{https://www.astromatic.net/software/sextractor/}{\code{SourceExtractor}} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
+We use \code{SourceExtractor} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise.
 This step remains largely the same as in \citetalias{Greco2018}.
-The images are convolved with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast between LSBGs and sky background \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}.
+The images are convolved with a Gaussian kernel of FWHM=$1\arcsec$ to enhance the contrast between LSBGs and sky background \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}.
 We take a mesh size of $43\arcsec$ (double the mesh size used in \citetalias{Greco2018} to allow bigger galaxies in our sample) to measure the local background and detect objects that are 0.7$\sigma$ per pixel above the local sky background.
-We also require the object to contain at least 100 contiguous pixels (equivalent to a square box with $1.7\arcsec$ on each side) to further remove small compact objects.
+We also require the object to contain at least 100 contiguous pixels (equivalent to a square box with $1.7\arcsec$ on a side) to further remove small compact objects.
 We perform the detection in the $g$-band, but require that all sources are also detected in the $r$-band to exclude spurious detection and artifacts.
@@
 \subsection{Initial Sample Selection} 
-In this step, we take the output catalog from \code{SourceExtractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors.
+We take the output catalog from \code{SourceExtractor} and remove those objects that are not likely to be LSBGs based on their sizes and colors.
 To be specific, we require objects to have $g$-band half-light radii (measured by \code{SourceExtractor}) greater than $r_{\rm min} = 2.0\arcsec$.
@@
 
-Compared with \citetalias{Greco2018}, we add a new metric based on the morphology of sources to further remove false positives.
-For each source, we compute the ratio of the 2-D autocorrelation function (ACT) within an aperture of 5 pixels and the ACT within an annulus between 5 pixels and 9 pixels from the center.
+Compared with \citetalias{Greco2018}, we add a new metric based on the morphology of sources to further remove compact point-like sources.
+For each source, we compute the ratio between the 2-D autocorrelation function (ACT) within an aperture of 5 pixels and the ACT within an annulus between 5 pixels and 9 pixels from the center.
 The ACT ratio essentially characterizes the peakiness of the source.
-Peaky sources have higher ACT ratios, thus we remove point-like sources by applying a cut on ACT ratios $a_{\rm corr} < 2.5$.
+Peaky sources have higher ACT ratios, thus we remove point-like sources by applying a cut on the ACT ratio $a_{\rm corr} < 2.5$.
 This step helps to improve the purity of our sample.
@@
 \section{Deblending details}\label{ap:deblending}
+In \S\ref{sec:deblending}, we briefly introduce how we use \code{scarlet} to model the LSBG candidates in a non-parametric fashion and filter out false positives based on the structural and morphological parameters.
+In this appendix, we describe details of the implementation of vanilla \code{scarlet} which could help interested readers better understand the technique.
 
@@
 \subsection{Model initialization and optimization}
-
-After peak detection, we need to decide which peaks to model, and we would like to initialize the model as best as we can.
-We note that \code{scarlet} optimizes the model instead of deriving the full posteriors, thus good initialization becomes really important.
-We tackle these problems as follows.
-
-In vanilla scarlet, objects can be modeled with different types of models as follows.
+After the peak detection step, we need to decide which peaks to model.
+It is not necessary to model all detected peaks because the deblending step is designed to model the sources only in the vicinity of the target LSBG candidate.
+Therefore, the size of the target object determines which peaks are relevant.
+Nevertheless, it is also important to choose the appropriate model for each source and initialize them as best as possible.
+In practice, we draw a square bounding box around the target object and model all the peaks inside this box.
+The bounding box is in turn determined as we initialize the model for the target object.
+We describe the procedures as follows.
+
+First, in vanilla \code{scarlet}, objects can be modeled with different types of models\footnote{\url{https://pmelchior.github.io/scarlet/1-concepts.html\#Source}} including point source, single-extended source, multi-extended source, compact source, and flat-sky source.
 The point source has a morphology image simply be the normalized PSF.
@@
 
-The deblending step is designed to model the sources in the vicinity of the target object.
-Therefore, the size of the target object determines which peaks are relevant.
-We draw a square bounding box around the target object and model all the peaks inside this box.
-The size of the bounding box is determined as we initialize the model for the target object, described as follows.
-
-We use an extended source model with two components to describe the target object, such that the model is able to capture the galaxy structure and color gradient.
-The source is initialized as follows.
+For modeling the LSBG candidates, we use an extended source model with two components such that the model is able to capture the galaxy structure and color gradient.
+The target source is initialized as follows.
 We convolve the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise.
@@
 Consequently, the size of the bounding box depends on the smoothing kernel and the threshold.
-We choose the above values by trial and error such that the box is not so large as to include many irrelevant peaks, but not so small as to lose the flux from the target galaxy.
-
-Then we take all peaks within the bounding box of the target galaxy and initialize them in the same way.
+We choose the above values by trial and error such that the box is not so large as to include many irrelevant peaks, but not so small as to lose the LSB outskirts of the target galaxy.
+
+Then we take all peaks within the bounding box of the target galaxy and initialize them in the same way as described above.
 Recall that we have two rounds of peak detection (Sec \ref{sec:peak}), focusing on extended and compact sources respectively.
@@
 This is helpful for situations where an object overlaps with the LSB outskirts of a bright galaxy (e.g., the bottom panel in Figure \ref{fig:vanilla_scarlet_demo}).
-
-As mentioned above, we only model peaks within the bounding box of the target.
-However, scattered light from nearby bright stars and galaxies could bias the modeling of sources within the bounding box (e.g., the yellow star in the top left panel of Figure \ref{fig:vanilla_scarlet_demo}).
+We note that whether adding a flat-sky source could significantly change the size and total magnitude of the \code{scarlet} model.
+
+Although we only model peaks within the bounding box of the target, the scattered light from nearby bright stars and galaxies could bias the modeling of the sources within the bounding box (e.g., the yellow star in the top left panel of Figure \ref{fig:vanilla_scarlet_demo}).
 We match our field with the Gaia catalog \citep{GAIA2016,GAIA2018} and mask out stars outside of the bounding box.
-Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies.
-
-We demonstrate the above procedures in Figure \ref{fig:vanilla_scarlet_demo} with two examples.
-The one shown in the top panels is a blue LSBG, whereas the one shown on the bottom is a high-$z$ galaxy blended with the outskirts of a nearby galaxy which falls in our initial sample as a false positive.
-The first column shows the $griz$ color-composite image \citep{Lupton2004}, where the white boxes mark the bounding box of each source in the scene.
-The gray shades over objects outside of the target bounding box indicate they are masked out.
-The second column shows the initial \code{scarlet} models.
-They look fuzzy because they are constructed from the smoothed image, but they capture the color and the faint outskirts of the LSBG quite well.
+Since we have already detected peaks throughout the whole cutout image, we also generate a mask for objects outside the bounding box to reduce the impact of scattered light from bright galaxies on the modeling of the flat-sky source.
 
@@
 It takes longer when the target galaxy has large angular size since more peaks are modeled.
-The optimized model is shown in the middle column of Figure \ref{fig:vanilla_scarlet_demo} after convolving with the PSF, and the fourth column shows the residual image.
-The fifth column shows the optimized model only for the target object.
-
-We notice that the optimized model of the blue LSBG captures its color and morphology quite well.
-For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact.
-The reason why it passes our initial selection is that the galaxy outskirts are shredded by SourceExtractor and happen to have a large size and the right color.
-But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.
+We note that \code{scarlet} optimizes the model instead of deriving the full posteriors, thus a good initialization becomes especially important for fast convergence.
 
@@
 In this appendix, we demonstrate that the Spergel profile can approximate \sersic{} profile and profile a lookup table for the correspondence between \sersic{} index $n$ and Spergel index $\nu$.
+
+The surface brightness of a Spergel profile has the form \citep{Spergel2010}:
+\begin{equation}
+    \label{eq:spergel}
+    I_\nu(r) = \frac{c_{\nu}^{2} L_{0}}{2\pi r_{0}^{2}} f_{\nu}\left(\frac{c_{\nu} r}{r_{0}}\right),
+\end{equation}
+where 
+\begin{equation}
+    f_{\nu}(u)=\left(\frac{u}{2}\right)^{\nu} \frac{K_{\nu}(u)}{\Gamma(\nu+1)},
+\end{equation}
+and $K_\nu(u)$ is the Modified Bessel function of the second kind.
+The half-light radius is $r_0$, the total luminosity is $L_0$, and $c_\nu$ satisfies the equation $(1 + \nu)f_{\nu + 1}(c_\nu) = 1/4$.
+The Spergel profile has a simple analytical expression in Fourier space, making it easy to convolve with a PSF.
 
@@
 \end{equation}
-The Spergel profile is described in Section \ref{sec:modeling}.
 
@@
 It is well-known that the light profiles of low-mass galaxies are quite flat and can be described using \sersic{} profiles with $0.5 < n < 1.5$ \citep[e.g.,][]{vanDokkum2015,Lange2015,Greco2018,Zaritsky2021,ELVES-I}.
-It is thus reasonalbe to use Spergel profiles to model the LSBGs (Sec \ref{sec:modeling}) and enjoy its convenience in the Fourier space.
+It is thus reasonalbe to use Spergel profiles to model the LSBGs (\S\ref{sec:modeling}) and enjoy its convenience in Fourier space.
 
 \section{Completeness and Measurement Uncertainty}\label{ap:comp_meas_unc}
-A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}).
-Thus, the overall completeness is a combination of detection completeness and deblending completeness.
-We performed a large suite of image simulations to derive the completeness.
-The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.
-
-For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
+\subsection{Completeness}
+The total completeness is a multiplication between the detection completeness and deblending completeness. Below we describe how we generate mock galaxies and derive the recovered fraction.
+
+For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
 This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
@@
 We notice that the size and surface brightness shown in Figure \ref{fig:completeness} are all the intrinsic values for the mock galaxies, which are different from the measured ones.
-We discuss measurement biases in Section \ref{sec:meas_unc}.
-
-We find that the detection completeness mainly depends on the size and surface brightness.
-As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes.
-It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$.
-We find negligible dependence of completeness on \sersic{} index, color, and ellipticity.
+We find negligible dependence of detection completeness on \sersic{} index, color, and ellipticity.
 Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
@@
 
-For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them.
-The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$.
+For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla \code{scarlet} on them.
+The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 \cdot (g-i) + \mathcal{N}(0, 0.03^2)$.
 We measure the size and surface brightness on the scarlet models of the mock galaxies, then we apply the deblending cuts.
-The deblending completeness as a function of size and surface brightness is shown in the middle panel of Figure \ref{fig:completeness}.
-The deblending completeness is very high at the bright end, but starts to decline with increasing size and surface brightness.
-Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
-Interestingly, the detection completeness and deblending completeness all drop below 40\% around $\sbeff=27.5\ \sbunit$.
-In this sense, the detection and deblending cooperate well in terms of completeness.
-
-The combined completeness is shown in the right panel of Figure \ref{fig:completeness}.
-The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours.
-The completeness drops as we go to fainter surface brightness and smaller size.
-We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-Although \sersic galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic model still sets a baseline or upper limit on the real completeness.
-In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).
-
-We compare our completeness with that of other LSBG searches.
-Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more quickly with increasing size.
-\citet{CarlstenELVES2022} use a similar search algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$ assuming a Sersic index $n \approx 1$.
-\citet{vdBurg2017} searched LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
-\citet{Zaritsky2021} focus on searching for LSBGs in the SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) images and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$ for $n=1$.
-Their low completeness might be explained by the fact that they remove a large fraction of the sky contaminated by Galactic dust.
-\citet{Tanoglidis2021} conducted an LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
-\citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but much smaller completeness above $\sbeff > 26.5\ \sbunit$.
-The Dragonfly Wide Field Survey \citep{Danieli2020} reaches $\sim 29\ \sbunit$ for $>3\sigma$ detection on scales $\sim 1\arcmin$, which is deeper than all other surveys by sacrificing spatial resolution.
-In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies \citep[e.g.,][]{Huang2018,Kado-Fong2018}.
-
-\subsubsection{Measurement bias and uncertainty}\label{sec:meas_unc}
-
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
-	}
-    \caption{The measurement bias and uncertainty as a function of measured angular size $r_e$ and surface brightness $\sbeff$.
-The colors show the bias term while the dashed contours show the constant uncertainty lines.
-We derive the bias in the total magnitudes from the combined bias in $r_e$, $\sbeff$, and color.
-We find that the bias and uncertainty in our measurement increase toward the fainter end.
-We apply the bias correction to the real LSBGs before studying their physical properties.}
-    \label{fig:meas_err}
-\end{figure*}
+We also find that the deblending cut mainly depends on the size and surface brightness.
+
+\subsection{Measurement bias and uncertainty}\label{sec:meas_unc}
 
@@
 In order to test how well we recover the photometric and structural parameters in the our measurement (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
-We compare the fitting results with the ground truth, and we find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
-For surface brightnesses fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
-As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than reality.
-
-Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shape.
+We model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shape.
 However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index.
@@
 
-In Figure \ref{fig:meas_err}, the colors show the interpolated bias terms as a function of the measured size and surface brightness.
-The size and surface brightness bias grows with increasing surface brightness.
-The bias term is not a monotonic function of size because the size here is not intrinsic size.
-It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
-We also find the bias in $g-i$ color to be quite small.
-
 For LSBGs in our sample, we apply corrections for the bias using the interpolated bias terms.
@@
 In this way, we apply a self-consistent correction for the measurement biases to the data.
-
 The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, neighboring contamination, etc.
-Unlike other parametric modeling codes, \code{scarlet} does not explore the full posterior space but rather finds one optimal solution.
+Unlike other parametric modeling codes such as \code{imfit} \citep{imfit} and \code{the Tractor} \citep{Lang2016}, \code{scarlet} does not explore the full posterior space but rather finds one optimal solution.
 Thus we have no access to the statistical error on the measured properties from \code{scarlet}.
@@
 We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
-
-In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on bias-corrected properties.
-We also incorporate the measurement errors into the science figures.
-The values presented in our catalogs are already bias-corrected, but we do provide the bias values for reference.
 
@@
 
-Also add external link for fake UDG catalog, etc.
-
 \end{CJK*}

### 2022-10-11 paper1.tex
done except for discussion section

@@
 \begin{abstract}
-[\textbf{Need to rewrite}] Large diffuse galaxies are hard to find, but understanding their environments and abundance, and ultimately their origins, is of intense interest.
-Using the Hyper Suprime-Cam Strategic Survey, we search for low surface-brightness galaxies and match them to Milky-Way like hosts in projection.
-We build a statistical sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way-mass galaxies in the nearby Universe ($0.01 < z < 0.04$).
-The number of these ``ultra-puffy'' galaxies per host is comparable to the observed abundance  at this halo mass in the Local Volume, and the galaxies follow an NFW profile around their halos.
-We argue that our definition, based on the mass-size relation, is more robust than the common definition of ultra-diffuse galaxies, which depends on surface brightness and thus yields different surface mass density cuts for quenched and star-forming galaxies.
-With our mass-size--based definition, we show that despite their extended size, the quenched fraction is comparable at a given satellite stellar mass between the ultra-puffy and normal dwarfs in MW-mass halo.
-These results hint that the size growth and quenching of mass-size outliers happen separately.
+Large diffuse galaxies are hard to find, but understanding their environments and abundance, and ultimately their origins, is of intense interest.
+Using the Hyper Suprime-Cam data, we perform a systematic search for low surface-brightness galaxies and present novel and effective methods for detecting and modeling them.
+As a case study, we build a statistical sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$).
+These ``ultra-puffy'' galaxies, defined to be $1.5\sigma$ above the average mass-size relation, better represents the tail of satellite size distribution.
+We find that the number of ultra-puffy galaxies per host is comparable to the observed abundance at this halo mass in the Local Volume.
+We also construct a sample of ultra-diffuse galaxies and compare their abundance with literature.
+We argue that our definition, based on the mass-size relation, is more robust than the common definition of ultra-diffuse galaxies, which depends on a surface brightness cut and thus yields different surface mass density cuts for quenched and star-forming galaxies.
 \end{abstract}
@@
 By comparing mass-size outliers with normal satellites and simulations, our results seek to shed light on the formation and evolution of the large diffuse galaxies.
+
+\jiaxuan{Bring up something like: we develop the machinery, and only applied it to MW analogs as a touchstone.}
 
@@
 \subsection{Hyper Suprime-Camera data}
-The Hyper Suprime-Camera Subaru Strategic Program Survey (\citealt{Aihara2018}; hereafter the HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}.
+The Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP, \citealt{Aihara2018}; hereafter the HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}.
 The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection).
-HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Large Synoptic Survey Telescope (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.
+HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Legacy Survey of Space and Time (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.
 
@@
 We also incorporate the measurement errors into the science figures.
-The values presented in our catalogs are already bias-corrected, but we do provide the bias values for reference.
+The values presented in our catalogs (Table \ref{tab:catalog}) are already bias-corrected, but we do provide the bias values for reference.
 
@@
 However, distance information is needed to convert the observed size and magnitude to the physical size and stellar mass.
-One of the major obstacles for studying LSBGs is that it is hard to get their distance.
+It is well-known that getting the distances to LSBGs is one of the major obstacles for studying their properties.
 Beside direct distance measurements (e.g., SAGA, ELVES, \citealt{Kadowaki2021}), it is common to assume a distance to a LSBG by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
 A statistical background subtraction is then needed to account for the contribution from background and foreground galaxies.
-Cross-correlation between the LSBG sample and a host galaxy sample can also reveal the distance distribution of LSBGs \citep{Greene2022}.
+Furthermore, cross-correlation between an LSBG sample and a host galaxy sample can also reveal the distance distribution of LSBGs \citep{Greene2022}.
 These methods are also complemented by recent machine learning techniques \citep{Baxter2021,xSAGA-I}.
-In this Section, we cross-match our LSBG catalog with MW-like galaxies in the NSA catalog and construct the UDG and UPG sample.
+In this Section, we cross-match our LSBG catalog with MW-like galaxies in the NSA catalog.
+For the LSBGs matched with MW analogs, we run the deblending step to exclude false positives (\S\ref{sec:deblending}) and then run Spergel modeling to measure the properties of LSBGs (\S\ref{sec:modeling}).
+In the end, we construct the samples of mass-size outliers in the satellites of MW analogs.
 
@@
 The properties of the Milky Way itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016} and the definitions of MW analogs are different among different studies.
-In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$~mag, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig.
+In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$~mag, which is derived using abundance matching by assuming a simple galaxy-halo connection model (see Fig.
 2 in \citealt{SAGA-I}).
@@
 
-Since mass-size outliers including UDGs are relatively scarce in MW analogs \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics.
+Mass-size outliers, by definition, are relatively scarce compared with normal-sized satellites in MW analogs \citep{SAGA-II,CarlstenELVES2022}.
+It is therefore helpful to probe a larger volume to obtain good statistics.
 We choose our redshift range to be $0.01 < z < 0.04$, which makes sure that we can detect a significant number of faint dwarf galaxies around MW-like hosts.
@@
 
-After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 MW-mass galaxies.
+After applying the stellar mass and redshift cuts to the NSA catalog (\S\ref{sec:data}), there are 23,218 MW-like galaxies.
 We match them to the initial LSBG sample (described in \S \ref{sec:detection}, before the deblending step) as follows.
@@
 However, there are still a significant fraction of spurious objects in this cross-matched LSBG sample, including galactic cirrus, tidal streams, shredded large galaxies, and compact sources blended with galaxy outskirts.
-As described in Section \ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects.
+As described in \S\ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects.
 There are 2,673 objects left after the deblending cuts.
-Next, we model them using the Spergel profile as described in Section \ref{sec:modeling} and obtain their photometry and structural parameters from the best-fit models.
-Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives.
+Next, we model them using the Spergel profile as described in \S\ref{sec:modeling} and obtain their photometry and structural parameters from the best-fit models.
+% Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives.
 We also remove duplicated objects.
 In the end, we have 2,510 LSBG candidates as our final LSBG sample.
-These LSBGs are matched to MW hosts but do not have direct distance measurements.
-
-We apply the measurement bias correction (\S \ref{sec:meas_unc}) and assign completeness and importance weights after bias correction.
+We note that these LSBGs are matched to MW hosts in projection but do not have direct distance measurements.
+
+We apply the measurement bias correction (\S \ref{sec:comp_meas}) and assign completeness after bias correction.
 In the end, we correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
@@
 The concept of UDG was proposed to describe dwarf galaxies with unusually large size ($r_e>1.5$ kpc) and diffuse light distribution ($\sbcen > 24.0\ \sbunit$).
-Although UDGs are mass-size outliers in some sense, a constant size cut cannot describe the extendedness of every galaxy since the size of a galaxy is strongly correlated with its mass,
-% a defect in the UDG definition is that it ignores the fact that the size of a galaxy is strongly correlated with its mass, 
-known as the mass-size relation \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
-Therefore, a better definition for mass-size outliers should be based on a mass-size relation and its scatter.
-Ideally, galaxies that are $1.5\sigma$ or $2\sigma$ above the average mass-size relation represent the large-size tail of the population in a homogeneous manner.
-Following this thread, we propose such a new definition for mass-size outliers dubbed as \textit{ultra-puffy galaxies} (UPGs).
-In this section, we describe the definitions of UDG and UPG, then we select UDGs and UPGs from our LSBGs matched with MW hosts.
+Although UDGs are large in size, the constant size cut does not account for the fact that the galaxy size is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
+Therefore, an more intuitive definition for diffuse and puffy dwarf galaxies (i.e., mass-size outliers) should be based on a mass-size relation and its scatter.
+Following this thread, we propose a new definition for mass-size outliers dubbed as \textit{ultra-puffy galaxies} (UPGs).
+In this section, we describe the definitions of UPG and contrast it with UDG, then we select UDGs and UPGs from our LSBGs matched with MW hosts.
+% Ideally, galaxies that are $1.5\sigma$ or $2\sigma$ above the average mass-size relation represent the large-size tail of the population in a homogeneous manner.
 
@@
 To select mass-size outliers, a mass-size relation and its scatter are needed.
-However in general, the slope of the mass-size relation in the nearby Universe has been shown to be color- and morphology-dependent for galaxies above $M_\star > 10^{9}\ M_\odot$: blue star-forming galaxies have a shallower slope than the red quenched galaxies \citep{Lange2015}.
+However in general, the slope of the mass-size relation in the nearby Universe has been shown to be color- and morphology-dependent for galaxies above $M_\star > 10^{9}\ M_\odot$: blue star-forming galaxies have a shallower slope than the red quenched galaxies \citep[e.g.,][]{Lange2015}.
 Fortunately, in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$), \citet{ELVES-I} derive the mass-size relation from the satellites of MW analogs in the Local Volume and show that the average mass-size relation is quite universal: the slope and intercept are not sensitive to the color or morphology of dwarf galaxies.
-The residual from the mass-size relation follows a Gaussian distribution reasonably well.
-This gives us a chance to define a subset of dwarf galaxies that are size-outliers in terms of the average mass-size relation.
+The residual from the mass-size relation follows a log-normal distribution reasonably well.
+This gives us a chance to define a subset of dwarf galaxies that are size-outliers with respect to the average mass-size relation.
 It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021,Benavides2022}.
 
-Taking the measured average mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.25\, \log\, (M_\star/M_\odot) + 1.07$ and a scatter of $\sigma=0.18$ dex, we define a population of UPGs to be galaxies that are $>1.5\sigma$ above the average mass-size relation.
+Taking the measured average mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.25\, \log\, (M_\star/M_\odot) + 1.07$ and a scatter of $\sigma=0.18$ dex, we define a population of ultra-puffy galaxies to be galaxies that are $>1.5\sigma$ above the average mass-size relation.
+We choose $1.5\sigma$ just because it gives us a statistically significant sample.
+One can certainly select $>2\sigma$ or $>3\sigma$ UPGs if a larger LSBG sample is available.
 The UPGs are not absolutely large in size or absolutely faint in surface brightness, but they are outliers in size for their stellar masses.
 The definition of UPG based on the observed mass-size relation is more physically-motivated, and better allows us to study size outliers at a given stellar mass.
-We further discuss the advantages and disadvantages of UDG and UPG in Section \ref{sec:artifact}.
-
-There are 362 objects in our LSBG candidates that fall $1.5\sigma$ above the ridge line of the mass-size relation.
-After visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
+We further discuss the advantages and disadvantages of UDG and UPG in \S\ref{sec:mass-size} and \S\ref{sec:discussion}.
+
+There are 362 objects in our LSBG candidates that fall $1.5\sigma$ above the ridge line of the mass-size relation.\footnote{We note that the mass-size relation in \citet{ELVES-I} is derived for a mass range of $10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$.
+We extrapolate the mass-size relation to $M_\star \sim 10^9\ M_\odot$ to define our UPG sample.} After removing spurious objects after visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
 These UPGs are associated with 239 hosts.
 The total sky area occupied by UPG hosts (out to 1 $R_{\rm{vir}}$) is 32.37 deg$^{2}$.
-The UDG and UPG catalogs are available in machine-readable format online\footnote{\url{https://github.com/AstroJacobLi/kuaizi/blob/master/data/}}.
+The catalogs are available in machine-readable format online\footnote{\url{https://github.com/AstroJacobLi/kuaizi/blob/master/data/}}.
 We demonstrate the catalog format in Table \ref{tab:catalog}.
-We note that the mass-size relation in \citet{ELVES-I} is derived for a mass range of $10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$.
-We extrapolate the mass-size relation to $M_\star \sim 10^9\ M_\odot$ to define our UPG sample.
 
@@
 \subsubsection{UDGs}
-Albeit the advantage of UPGs, there are very little literature on UPGs for us to compare.
-Thus, we also select a UDG sample from our LSBGs in order to compare with existing observations and simulations.
+Albeit the advantage of UPGs, there are very little literature on UPGs for us to compare with.
+Thus, we also select a UDG sample from our LSBGs in order to compare with existing observations and simulations in different environments.
 The UDG sample is usually defined based on the surface brightness and the physical size of the galaxy.
-However, there are many different criteria in literature: \citep{vanDokkum2015} define UDGs to have effective radii $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}.
+However, there are many different criteria in literature: \citet{vanDokkum2015} define UDGs to have effective radii $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}.
 The size criterion also varies from $r_e > 1$ kpc to $r_e > 1.5$ kpc.
-\citet{vanNest2022} explore these definitions and find that different choice of UDG can drastically change the selected subset of dwarfs, therefore affect our understanding of the UDG population.
+\citet{vanNest2022} explore these definitions in simulation and find that different choice of UDG can drastically change the selected subset of dwarfs, therefore affect our understanding of the UDG population.
 
 In practice, the measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020,ELVES-II,Somalwar2020} or other contaminants.
-Therefore in this work, we use the average surface brightness within an effective radius $\sbeff$ to define UDGs.
+Therefore in this work, we use the average surface brightness within the effective radius $\sbeff$ to define UDGs.
 The difference between the average surface brightness and the central surface brightness can be analytically calculated for a \sersic{} profile: $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
-Since dwarf galaxies and UDGs typically have \sersic{} index of $0.8 < n < 1.2$ \citep[e.g.,][]{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value to convert $\mu_0$ to $\mu_{\mathrm{eff}}$.
+Since dwarf galaxies and UDGs typically have \sersic{} index of $0.8 < n < 1.2$ \citep[e.g.,][]{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.0$ as an average value to convert $\mu_0$ to $\mu_{\mathrm{eff}}$.
 In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, where we also take the $1\sigma$ measurement errors into account.
@@
 The total sky area occupied by UDG hosts (out to 1 $R_{\rm{vir}}$) is 32.71 deg$^{2}$.
-We describe the properties of UPGs and UDGs in Section \ref{sec:mass-size}.
-
-\subsection{Background contamination}\label{sec:bkg}
-The major weakness of LSBG searches in imaging data is that distance information is typically unknown.
+We describe the properties of the mass-size outliers (including UPGs and UDGs) in \S\ref{sec:mass-size}.
+
+\subsection{Background contamination fraction}\label{sec:bkg}
+% The major weakness of LSBG searches in imaging data is that distance information is typically unknown. 
 Although we have matched LSBGs to MW analogs by proximity, the physical affiliation of LSBGs to the host is not guaranteed.
-As a result, a certain fraction of galaxies in our mass-size outlier sample might just be foreground or background galaxies that fall within the virial radius of the host in projection.
+As a result, a certain fraction of galaxies in our mass-size outlier samples might just be foreground or background galaxies that fall within the virial radius of the host in projection.
 Given the volume probed by our search, contamination is most likely to be dominated by background galaxies.
-We estimate the contamination fraction as follows.
-The methodology is to study the number of those LSBGs that mimic UPGs and UDGs by randomly matching LSBGs to our MW hosts.
-
-We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2.
+In the section, we try estimate the contamination fraction empirically by studying the number of those LSBGs that mimic UPGs and UDGs by randomly matching LSBGs to our MW hosts.
+
+We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2 regardless of whether containing MW analogs.
 Then we perform the same deblending and modeling steps for the 2,707 LSBGs detected in this region.
-We also removed objects that are already in our mass-size outlier samples, and we did visual inspection to further remove false positives.
-In the end, there are 480 ``real'' LSBGs representing a population of possible contaminants.
-Next, because both UDG and UPG are defined based on physical size, we randomly associate the 480 LSBGs to the hosts of our UDGs and UPGs, respectively.
+We also removed objects that are already in our mass-size outlier samples and objects with completeness less than 0.1.
+Furthermore, we also did the same visual inspection as for UDGs and UPGs to remove false positives.
+In the end, there are 480 LSBGs (not false positives) representing a population of possible contaminants for the UDG and UPG samples.
+Next, because both UDG and UPG are defined based on a physical size, we randomly associate the 480 LSBGs to the hosts of our UDGs and UPGs, respectively.
 Then we calculate a physical size for each LSBG and classify an LSBG as a ``fake`` UDG or UPG if it satisfies the corresponding definition.
@@
 For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 16\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 20\%$.
-We take the contamination fraction into account when calculating the abundances, size distributions, and radial distributions of the UDGs and UPGs respectively (Section \ref{sec:results}).
-We note that we do not apply any background correction in Figure \ref{fig:mass_size} and Figure \ref{fig:size_distribution} because such correction is in statistical sense.
-
-One of the main goals of this paper is to study the star-forming properties of mass-size outliers in satellites of MW analogs.
+We take the contamination fraction into account when calculating the abundances (\S\ref{sec:results}).
+
+% One of the main goals of this paper is to study the star-forming properties of mass-size outliers in satellites of MW analogs.
 The star formation rate of galaxies can be indicated by their broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs (see \S \ref{sec:quench} for more details).
@@
 % If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG.
-Indeed, we find that the $g-i$ color distribution of the fake UDG (UPG) sample is bluer than that of the true UDG (UPG) sample, which motivates us to assign importance weights based on the $g-i$ color.
+% Indeed, we find that the $g-i$ color distribution of the fake UDG (UPG) sample is bluer than that of the true UDG (UPG) sample, which motivates us to assign importance weights based on the $g-i$ color.
 Taking UDGs as an example, we first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at the $(g-i)_{k}$ bin) for both true UDG and fake UDG samples.
@@
 \section{Results}\label{sec:results}
-In this section, we present the statistical analysis of mass-size outliers including UDGs and UPGs associated with MW analogs at $0.01 < z < 0.04$.
+In this section, we present a statistical analysis for mass-size outliers in the satellites of MW analogs at $0.01 < z < 0.04$.
 We first compare the distributions of UDGs and UPGs on the size-surface brightness plane and mass-size plane to gain intuition on the differences between UDG and UPG definitions.
-Then we present detailed analysis on the abundance, size distribution, spatial distribution, and quenching for UDGs and UPGs.
+Then we present the abundances of UDGs and UPGs and compare with literature.
 
@@
 	}
-    \caption{The distribution of galaxies in the UDG sample (\textit{left}) and the UPG sample (\textit{right}).
-The UDGs are galaxies with $r_e>1.5$ kpc and $\sbeff > 25.0\ \sbunit$.
-The UPGs is defined to be $1.5\sigma$ above the average mass-size relation in \citet{ELVES-I}.
-We split the samples into two color bins and show them in red ($g-i>0.8$) and blue ($g-i<0.8$).
+    \caption{The distribution ultra-diffuse galaxies (UDGs, \textit{left}) and ultra-puffy galaxies (UPGs, \textit{right}) on the size-surface brightness plane.
+The UPGs is defined to be galaxies that are $1.5\sigma$ above the average mass-size relation in \citet{ELVES-I}.
+The samples are split into two color bins and shown in red ($g-i>0.8$) and blue ($g-i<0.8$).
 The marginal histograms are not normalized to highlight the relative number of red and blue galaxies.
-Compared with the UDG sample, the UPG sample includes blue galaxies with surface brightness higher than the UDG cut ($\sbeff < 25\ \sbunit$) and excludes red galaxies at $25 < \sbeff < 26\ \sbunit$.
-We note that this plot is not corrected for background contamination.
+Compared with the UDG sample, the UPG sample includes blue galaxies with surface brightness higher than the UDG cut ($\sbeff < 25\ \sbunit$) and excludes red galaxies at $25 < \sbeff < 26\ \sbunit$, due to the color-$M_*/L$ dependence.
     }
@@
 	}
-    \caption{[\textbf{Explain this figure better}] The distributions of the UDG and UPG samples on the mass-size plane.
-The data points are color-coded by the distance to the quenching color cut.
-Squares are those galaxies satisfying both the UDG and UPG definition, stars (triangles) are those only satisfying UDG (UPG) definition.
-    We plot the average mass-size relation (light green) and $1.5\sigma$ above the average relation (dark green) as dashed lines for reference.
-In the left panel, we show the constant surface brightness line as solid lines by assuming two different $g-i$ colors.
-Galaxies falling between these two lines are mostly red and quenched because blue UDGs have to be very large in size to satisfy the surface brightness criterion.
-This hard surface brightness cut makes the UDG quenched fraction high.
-The constant surface mass density lines in the right panel might provide us new ways to define diffuse dwarf galaxies.
+    \caption{\textit{Left panel}: a schematic diagram showing the UDG size cut (gray band), survey limit (blue shade), the average mass-size relation (dark green dashed line) and $1.5\sigma$ above it (light green line).
+The solid lines are constant surface brightness cuts at $\sbeff=25\ \sbunit$ for two different colors $g-i=0.4,\ 0.8$.
+The constant surface stellar mass density line is in purple.
+\textit{Right panel}: The distributions of UDGs and UPGs on the mass-size plane.
+UDGs that are also classified as UPGs are shown as orange squares, while UDGs that do not satisfy the UPG definition are marked as red stars.
+Blue triangles are UPGs that are not classified as UDGs.
+UDG sample includes a significant amount of galaxies that are not mass-size outliers (below the $1.5\sigma$ line) which are red in color because the surface brightness cuts are different on mass-size plane for blue and red galaxies.
     }
@@
 The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively.
+We note that we do not apply any background contamination correction in Figure \ref{fig:udg_upg_re_mu} because such correction can only be done in a statistical sense.
+The error bars correspond to $1\sigma$ measurement uncertainties (\S\ref{sec:comp_meas}).
+Some galaxies with size smaller than 1.5 kpc are still scattered in the UDG sample because their sizes have large uncertainty.
 The two marginal plots show the unnormalized histograms of galaxies in the two color bins.
 The numbers of red and blue galaxies are similar in the UDG sample, but there are more blue galaxies than red ones in the UPG sample.
-Since there is no hard surface brightness cut, the UPG sample includes many blue galaxies with brighter surface brightness ($\sbeff < 25\ \sbunit$).
-The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26$ because their stellar masses are too high for their sizes to make them being size outliers.
-
-In Figure \ref{fig:mass_size}, we show UDGs and UPGs on the mass-size plane.
-In the left panel, UDGs that are also classified as UPGs are shown in squares, while UDGs that do not satisfy the UPG definition are marked as stars.
-In the right panel, triangles correspond to UPGs that are not classified as UDGs.
-To orient the reader to the mass-size plane, we also display the average mass-size relation from \citep{ELVES-I} as the light green dashed line.
-The darker green line shows $1.5\sigma$ above the average mass-size relation assuming the scatter of the mass-size relation to be $\sigma=0.18$ dex \citep{ELVES-I}.
-Because UDGs are defined to have $r_e > 1.5$ kpc and $\sbeff > 25.0\ \sbunit$, we see a hard cut on size and surface brightness in the left panel.
-We also see that UPGs are all above the $1.5\sigma$ line by construction.
-Limited by our detection limit and also the fact that our hosts are more distant than LV, our samples only reach to $M_\star \approx 10^{6.8}\ M_\odot$ which is $\sim 1$ dex higher than ELVES.
-
-Comparing the two panels, we find that the UDG sample includes a number of galaxies below the $1.5\sigma$ line (highlighted as stars), but also loses a few low-mass galaxies that are mass-size outliers but have sizes smaller than 1.5 kpc.
-UDGs below the $1.5\sigma$ line have sizes larger than 1.5 kpc, but they are not size outliers for their stellar masses.
-For the UDG sample, the stellar mass range only reaches $M_\star\approx 10^{8.3}\ M_\odot$ because galaxies with higher stellar mass no longer satisfy the surface brightness criterion for UDG.
-On the contrary, the UPG definition does not have a hard surface brightness cut.
-Thus a $M_\star > 10^{8.5}\ M_\odot$ galaxy can get into the UPG sample as long as it has an extraordinarily large size.
+Since there is no hard surface brightness cut for UPGs, the UPG sample includes many blue galaxies with brighter surface brightness ($23 \lesssim \sbeff < 25\ \sbunit$).
+Due to the surface brightness cut ($\sbeff > 23\ \sbunit$) in the deblending step, there is little chance for a LSB disk galaxy with bright bulge to scatter in the UPG sample.
+The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26\ \sbunit$ because their stellar masses are too high for their sizes to make them being size-outliers.
+
+We show UDGs and UPGs on the mass-size plane in Figure \ref{fig:mass_size}.
+To orient the reader to the mass-size plane, we first show a schematic diagram in the left panel where the lines and regions relevant to the definition of UDG and UPG are highlighted.
+The light blue shade shows the survey limit where we cannot effectively probe LSBGs fainter than $\sbeff \gtrsim 27.5\ \sbunit$ (see \S\ref{sec:comp_meas}).
+For defining UDGs, a size cut and a surface brightness cut are needed.
+We show the $r_e = 1.5$ kpc cut as a gray band to acknowledge the fact that smaller galaxies with large size uncertainty can also get into the UDG sample.
+The slant solid lines show the constant surface brightness lines with $\sbeff = 25.0\ \sbunit$ for two different colors ($g-i=0.4$ and $g-i=0.8$).
+The constant surface brightness lines depends on color because of the color-$M_\star/L$ relation.
+We also show the constant surface stellar mass density ($\mu_\star$) line, which is parallel to the constant surface brightness lines.
+Therefore, at a given size, blue UDGs are less massive than red UDGs; at a given stellar mass, blue UDGs are larger than red UDGs in size.
+Such a constant surface brightness cut leads to a UDG population that is inhomogeneous in surface mass density.
+
+In the left panel of Figure \ref{fig:mass_size}, the dark green dashed line shows the average mass-size relation from \citep{ELVES-I}, and the lighter green line shows $1.5\sigma$ above the average mass-size relation assuming the scatter of the mass-size relation to be $\sigma=0.18$ dex \citep{ELVES-I}.
+UPGs would lie above the $1.5\sigma$ line by construction, and there will be overlap between UDGs and UPGs.
+The mass-size relation is shallower than the constant surface brightness and surface mass density lines.
+
+We highlight the similarity and difference between UDG and UPG in the right panel.
+UDGs that are also classified as UPGs are shown as orange squares, while UDGs that do not satisfy the UPG definition are marked as red stars.
+Blue triangles correspond to UPGs that are not classified as UDGs.
+Limited by the detection limit and also the fact that our hosts are more distant than the Local Volume, our samples only reach to $M_\star \approx 10^{6.8}\ M_\odot$ which is $\sim 1$ dex higher than ELVES.
+Compared with the UPG sample, we find that the UDG sample (orange squares + red stars) comprises a number of galaxies below the $1.5\sigma$ line, but also loses several low-mass galaxies that are above $1.5\sigma$ line but have sizes smaller than 1.5 kpc.
+For the UDG sample, the stellar mass range only reaches $M_\star\approx 10^{8.3}\ M_\odot$ because galaxies with higher stellar mass are too bright to satisfy the surface brightness criterion for UDG.
+On the contrary, since the UPG definition does not have a hard surface brightness cut, it includes many galaxies that are more massive than UDGs as long as it has an extraordinarily large size.
 As a consequence, background spiral galaxies could dominate the UPG sample at the high-mass end.
 
-As we will introduce in Section \ref{sec:quench}, we use a color cut $(g-i)_{Q}$ to separate galaxies with active star formation from quiescent ones.
+\jiaxuan{Discuss whether UPGs are LSB disks?}
+
+% discriminative for blue and red galaxies.
+
+% As we will introduce in Section \ref{sec:quench}, we use a color cut $(g-i)_{Q}$ to separate galaxies with active star formation from quiescent ones.
 Here we define $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ as an indicator for the star formation rate of the galaxy.
@@
 
-\subsection{Abundance of UDGs and UPGs}\label{sec:n_udg}
+\subsection{Abundance of mass-size outliers}\label{sec:n_udg}
 
@@
 
-As demonstrated by many previous studies \citep[e.g.,][]{vdBurg2016,vdBurg2017,Roman2017a}, the average number of UDGs per host scales with host halo mass.
+As demonstrated by many previous studies \citep[e.g.,][]{vdBurg2016,vdBurg2017,Roman2017a,Karunakaran2022b}, the average number of UDGs per host scales with host halo mass.
 While much literature focuses on finding UDGs in clusters and large groups, there are fewer constraints on the UDG abundance at the lower halo mass end.
@@
 In the SAGA survey \citep{SAGA-II}, 6 satellite galaxies (out of 127 spectroscopy-confirmed satellites around 36 MW analogs) satisfy the definition of UDG.
-Therefore the UDG abundance in \citet{SAGA-II} is about $N_{\rm UDG,\, SAGA} \approx 0.17\pm0.07$.
-In the ELVES survey \citep{CarlstenELVES2022}, there are 13 UDGs out of 358 satellites with secure distances ($P_{\rm sat} > 0.8$) in 30 MW analogs, leading to a UDG abundance of $N_{\rm UDG,\, ELVES} \approx 0.43\pm0.12$.
+Therefore the UDG abundance in \citet{SAGA-II} is about $N_{\rm UDG}^{\rm SAGA}\approx 0.17\pm0.07$.
+In the ELVES survey \citep{CarlstenELVES2022}, there are 13 UDGs out of 358 satellites with secure distances ($P_{\rm sat} > 0.8$) in 30 MW analogs, leading to a UDG abundance of $N_{\rm UDG}^{\rm ELVES} \approx 0.43\pm0.12$.
 \citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}.
@@
 Among these studies, only \citet{vdBurg2017} applies a background subtraction and completeness correction to the raw counts.
+
 % In the Auriga simulations, \citet{Liao2019} find $N_{\rm UDG,\,Auriga}=1.27\pm 1.06$ for UDGs in MW-mass hosts.
+
 The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray.
@@
 Taking all data points from literature (as shown in Figure \ref{fig:n_udg}), we use the orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the red dashed line in Figure \ref{fig:n_udg}.
-The slope of the power law is shallower than \citet{vdBurg2017} ($\beta=1.11\pm0.07$) but still steeper than \citet{Roman2017b} ($\beta=0.85\pm0.05$).
+The slope of the power law is shallower than \citet{vdBurg2017} ($\beta=1.11\pm0.07$) but steeper than \citet{Roman2017b} ($\beta=0.85\pm0.05$).
 \citet{ManceraPina2018} survey eight clusters and find sublinear power laws.
+Recently \citet{Karunakaran2022b} perform a similar analysis including SAGA and ELVES and find slightly shallower power law of $\beta=0.87\pm0.07$.
 Since most individual studies do not have a statistical estimation for background contamination and completeness, the UDG abundances for large groups should be interpreted as lower limits.
-If completeness is applied, it is possible that the slope $\beta$ will be steeper than what we are showing in Figure \ref{fig:n_udg}.
-We also note that many studies do no consider measurement bias and uncertainty, which makes the comparisons more difficult.
+One major caveat in such studies is that most literature results are not completeness corrected and background subtracted, and these effects could significantly bias the results when combing them together.
+Therefore we caution that the power law index here should not be over-interpreted.
+% If completeness is applied, it is possible that the slope $\beta$ will be steeper than what we are showing in Figure \ref{fig:n_udg}. 
+% We also note that many studies do no consider measurement bias and uncertainty, which makes the comparisons more difficult.
 
@@
 
+Because there is little literature on UPGs, we only compare our UPG abundance with ELVES.
+In ELVES, we take the 351 satellites with secure distances in 30 MW analogs and identify 36 UPGs associated with 20 hosts.
+Thus the UPG abundance fraction in ELVES is $N_{\rm UPG}^{\rm ELVES} = 1.20 \pm 0.20$, which is higher than our UPG abundance.
+
 Another interesting quantity is the fraction of satellites that are mass-size outliers in a group or cluster.
-This fraction represent how efficient an environment is at producing diffuse galaxies.
+This fraction represent how efficient an environment is at producing puffy satellites.
 We denote this quantity as the UDG (UPG) fraction hereafter, which characterizes the tail of the size distribution of satellites.
@@
 Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.15$ and $f_{\rm UPG} \approx 0.10$.
-In ELVES, we take the 351 satellites with secure distances in 30 MW-like hosts and identify 13 UDGs in 10 hosts, and 36 UPGs in 20 hosts.
-Thus the UDG fraction in ELVES is $f_{\rm UDG, ELVES} \approx 0.04$, the UPG fraction in ELVES is $f_{\rm UPG, ELVES} \approx 0.10$.
+In ELVES, among 351 satellites with secure distances in 30 MW analogs, we identify 13 UDGs associated with 10 hosts, and 36 UPGs associated with 20 hosts.
+Thus the UDG fraction in ELVES is $f_{\rm UDG}^{\rm ELVES} \approx 0.04$, the UPG fraction in ELVES is $f_{\rm UPG}^{\rm ELVES} \approx 0.10$.
 We also compare our results with results in the Virgo cluster.
@@
 Our UPG fraction is consistent with ELVES but higher than NVGS.
-A more systematic comparison on UDG (UPG) fraction in different environments is needed in the future.
-
-\subsection{Size distribution}\label{sec:size_distr}
-
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{size_distribution.pdf}
-	}
-    \caption{The size distribution of UDGs (\textit{left}) and UPGs (\textit{right}).
-The contribution from the background contaminants (gray dots) are subtracted and the completeness has been corrected.
-We fit a power law to the size distribution of UDGs and get a power law shallower than that from \citet{vdBurg2016,vdBurg2017}.
-We find that the power law slope increases as the average halo mass increases.
-It is possible that denser environments provide stronger tidal forces and thus produce smaller UDGs.
-The UPG size distribution is suppressed at the smaller size end because small galaxies are not $1.5\sigma$ above the mass-size relation.
-    }
-    \label{fig:size_distribution}
-\end{figure*}
-
-The size distribution of UDGs is an important topic since it has been used to test UDG formation scenarios \citep[e.g.,][]{Amorisco2016,vdBurg2017}.
-In this section, we calculate the size distribution of our UDG and UPG samples.
-First of all, we take the fake UDGs in random fields (\S \ref{sec:bkg}) and calculate their size distribution as a proxy for background contamination, shown as the gray dots in the left panel of Figure \ref{fig:size_distribution}.
-For each host, we calculate the raw size distribution of the associated UDGs (black dots), and we multiply the background size distribution by the virial area of the host and subtract it from the raw size distribution.
-Then we combine the UDG size distributions for all hosts together, and correct for completeness (red squares).
-Since the stellar masses of the hosts in our sample are quite similar, we do not weight each host according to their masses.
-The error shown in Figure \ref{fig:size_distribution} takes both Poisson error and the measurement error in size into account.
-
-We find that the UDG size distribution roughly follows a power law.
-We fit a power law relation to our UDG size distribution and get $n\propto r_e^{-1.60\pm0.21}$.
-This is shallower than the power law presented in \citet{vdBurg2016} ($n\propto r_e^{-3.40\pm0.19}$) and \citet{vdBurg2017} ($n\propto r_e^{-2.71\pm0.33}$, shown as gray dash-dotted lines in Figure \ref{fig:size_distribution}).
-We also split the UDG sample based on their host stellar masses and distance to hosts, but consistently find shallow power-laws with index $\sim -1.6$.
-In particular, we do not find significant change in the size distribution as UDGs (UPGs) get closer to their hosts.
-Among others, \citet{vdBurg2016} focus on large galaxy clusters and find a very steep slope, \citet{vdBurg2017} includes less-massive groups and the slope is less steep.
-Combined with our findings, it might be possible that dense environment produces relatively more small UDGs, probably due to stronger tidal interactions.
-% As we will discuss in Section \ref{sec:discussion}, cluster environments provide stronger tidal fields and thus are more efficient on producing smaller UDGs due to tidal stripping.
-
-We also show the size distribution of UPGs in the right panel of Figure \ref{fig:size_distribution}.
-As we show in Figure \ref{fig:mass_size}, the UPG sample does not have those galaxies below the $1.5\sigma$ line but larger than 1.5 kpc.
-Therefore, for a given mass, many small UDGs are not in the UPG sample since their sizes are not extreme on the mass-size plane.
-As a consequence, the size distribution of UPG sample is suppressed at the smaller size end.
-
-\subsection{Radial distribution}\label{sec:radial_distr}
-
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{radial_distribution.pdf}
-	}
-    \caption{The radial distributions of UDGs (\textit{left}) and UPGs (\textit{right}).
-We show the radial distributions after subtracting the background contamination (shown in teal) and correcting for completeness in each radial distance bin (shown in red).
-We fit projected NFW and Einasto profiles to the radial distributions and find good fits for both profiles.
-The radial distributions of UDGs and UPGs are similar in shape.
-The best-fit NFW concentration is consistent with a MW-mass halo, whereas the best-fit Einasto profiles has a smaller concentration than MW-mass halos.}
-    \label{fig:radial_distribution}
-\end{figure*}
-
-The radial distribution of UDGs around the hosts has been used to test various UDG formation theories \citep[e.g.,][]{Tremmel2020}.
-In \citet{vanDokkum2015}, UDGs are not found within 300 kpc from the cluster center, hinting that UDGs might not survive in such a dense environment.
-\citet{vdBurg2016,ManceraPina2018} also found that the number of UDGs is depleted near the center of clusters.
-In \citet{vdBurg2016}, the radial distribution of UDGs in cluster environments roughly follows a projected Einasto profile \citep{Einasto1965}.
-In this subsection, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.
-
-We calculate the radial distribution as follows.
-For each host, we count the number of UDGs (UPGs) in each radial bin scaled by $R_{\rm vir}$ and calculate the number density of UDGs (UPGs) within each radial annulus.
-We subtract the contribution of background contaminants based on the background contamination density (\S \ref{sec:bkg}) and the angular area occupied by the host.
-Then we average over all hosts and correct for the completeness, as shown in Figure \ref{fig:radial_distribution}.
-Red squares are the number of UDGs (UPGs) per radial bin, and the error includes the Poisson, background subtraction, and completeness errors.
-The radial distributions of both UDGs and UPGs turn over around $R=0.2\,R_{\rm vir}$.
-It is known that the detection can be more incomplete as it gets closer to the host due to the blending between UDG and the host galaxy or due to sky subtraction issues.
-Although we have corrected the completeness for each object based on their size and surface brightness, it is still possible that we have not fully corrected for radial incompleteness within a halo.
-As we mentioned above, it is also possible that UDGs and UPGs are depleted because of tidal disruption.
-
-We fit the radial distributions of UDGs (UPGs) with the projected NFW and Einasto profiles for $R > 0.2 R_{\rm vir}$.
-The Einasto profile introduces an extra ``shape'' parameter $\alpha$ and has been argued to be a better description to the dark matter halo profiles \citep[e.g.,][]{Navarro2004,Gao2008,Navarro2010,Dutton2014}.
-The Einasto profile also makes concentration estimates less sensitive to the radial range fitted.
-The best-fit NFW (blue) and Einasto (red) profiles are shown in Figure \ref{fig:radial_distribution} as solid lines.
-The best-fit Einasto profile from \citet{vdBurg2016} is shown as the dashed gray line.
-
-Compared with \citet{vdBurg2016}, there are more UDGs at smaller radial distances in our sample, thus the UDG radial distribution is more concentrated although we exclude $R < 0.2\ R_{\rm vir}$.
-Unlike \citet{vdBurg2016}, we find that both NFW and Einasto could describe the radial distribution of UDGs (UPGs) quite well.
-The concentration of the best-fit NFW profile is $c_{\rm NFW, UDG} = 10.1^{+6.5}_{-3.9}$ for UDGs and $c_{\rm NFW, UPG} = 10.9^{+8.9}_{-4.9}$ for UPGs.
-The best-fit Einasto profile has $\alpha_{\rm Ein, UDG} = 0.44^{+0.42}_{-0.22},\ c_{\rm Ein, UDG} = 3.30^{+2.07}_{-1.27}$ for UDGs and $\alpha_{\rm Ein, UPG} = 0.40^{+0.56}_{-0.23},\ c_{\rm Ein, UPG} = 3.55^{+3.63}_{-1.80}$ for UPGs.
-The radial distribution profiles of UDGs and UPGs are found to be very similar in shape.
-Our best-fit Einasto profiles have lower $\alpha$ and higher concentration compared with \citet{vdBurg2016} where they have $\alpha_{\rm Ein, UDG} = 0.92^{+0.08}_{-0.18},\ c_{\rm Ein, UDG} = 1.83^{+0.13}_{-0.12}$.
-
-According to the concentration-mass relation of dark matter halos, the concentration of MW-like halo is $c_{\rm NFW} \sim 10$ \citep[e.g.,][]{Bullock2001,Duffy2008,Dutton2014,Diemer2019}.
-Therefore, if assuming an NFW profile, the UDGs and UPGs follow the underlying dark matter distribution of the host.
-However, the Einasto shape parameter for a MW-like halo is $\alpha\sim 0.15$ at $z=0$ and its concentration is $c\sim 8-10$.
-\citep{Gao2008,Dutton2014}.
-Comparing with this, the best-fit Einasto profiles for UDGs and UPGs are in tension with MW dark matter profile.
-We notice that the errors of the best-fit parameters are large due to the sample size and also the fact that concentration is most sensitive to data at smaller radial distances which are excluded in the analysis.
-Therefore, we consider the UDG (UPG) radial distribution to be consistent with the dark matter distribution of the host at a $2\sigma$ level.
-Nevertheless, a larger, cleaner, and more complete sample is needed to better constrain the radial distributions.
-
-\subsection{Quenched fraction}\label{sec:quench}
-
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{quenched_frac_dist2host.pdf}
-		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
-	}
-    \caption{The quenched fractions of UDGs (left panels) and UPGs (right) as a function of their stellar masses.
-The results for the whole sample are shown in green dots.
-The samples are further divided into bins based on the radial distance to the host (top panels) and host color (bottom panels), and are displayed in blue and red lines.
-We also overlie the results from Local Volume \citep[ELVES,][]{CarlstenELVES2022}, nearby Universe \citep[SAGA,][]{SAGA-II}, and simulations including ARTEMIS \citep{Font2022} and FIRE-2 \citep{Samuel2022}.
-The errors in this plot correspond to $1\sigma$ Bernoulli standard error.
-We find that UDGs have a high quenched fraction that remains a constant across a decade in stellar mass.
-The quenched fraction of UPGs drops with increasing satellite stellar mass, remarkably similar to that of normal satellites of MW analogs.
-The quenched fraction is larger for those associated to redder hosts and those that are closer to the host.
-}
-    \label{fig:qfrac}
-\end{figure*}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=1\linewidth]{quenched_frac_elves.pdf}
-    \caption{Quenched fractions of UPGs in this work and in ELVES (Greene et al., in prep).
-Using the same color cut to define quenched galaxies, we calculate the quenched fraction for UPGs in ELVES, shown as the brown line.
-The quenched fraction of UPGs in this work is highlighted in green, while the quenched fraction of the bulk of ELVES satellites is shown in orange \citep{CarlstenELVES2022}.
-We find that ELVES UPG quenched fraction agrees with our results quite well, and we do not find any significant dependence of quenched fraction on the size of satellites by comparing UPGs with the bulk of satellites.
-    }
-    \label{fig:qfrac_upg_elves}
-\end{figure}
-
-The star-forming properties of UDGs and UPGs is an interesting subject given their diffuse stellar components and non-trivial formation history.
-In this section, we study the fraction of quenched UDGs and UPGs as a function of both stellar mass and their host properties.
-We defer the discussion on the implications of these results to Section \ref{sec:discussion}.
-
-We refer to quenching as the cessation of star formation in galaxies.
-In principle, direct estimates of the instantaneous star formation rate (SFR) from UV or H$\alpha$ or estimates for the \ion{H}{1} gas are needed to define a quenched galaxy population.
-As an example, the SAGA survey measures the H$\alpha$ equivalent width (EW) from spectra to define quenched satellites.
-There are also many studies probing \ion{H}{1} masses for MW and M31 satellites \citep[e.g.,][]{Grcevich2009,Spekkens2014,Putman2021}.
-However, these specific data sets are either not deep enough to probe our UDGs and UPGs, or they are very expensive to obtain over the full footprint of our sample.
-Therefore, we seek other indicators for SFR including the integrated color and morphology.
-\citet{CarlstenELVES2022} visually inspected all satellites in the ELVES sample and classified them into early-type (red and smooth) and late-type (blue, asymmetric, clumpy).
-Using this sample, they find that a mass-dependent color cut $(g-i)_{Q} = -0.067\, M_V - 0.23$ could also divide the sample into early-type and late-type that are nearly identical to the ones based on morphology.
-The derived quenched fractions based on morphology and the color cut are very similar.
-Furthermore, \citet{Font2022} showed in simulations that this color cut effectively separates star forming galaxies from quenched ones.
-This makes the mass-dependent color cut more promising as a proxy for quenching since the simulations in \citet{Font2022} are not fine tuned to match the observed properties of ELVES satellites.
-Because we do not visually inspect all UDGs and UPGs in our sample, we just take the color cut from \citet{CarlstenELVES2022} to define quenched galaxies: UDGs and UPGs that are redder than $(g-i)_Q$ are defined as quenched, whereas those bluer galaxies are thought to be star-forming.
-However, one caveat is that this criterion was derived from LV satellites and the bulk of them have higher surface brightness and smaller size than our UDGs and UPGs.
-It is not guaranteed that the same color cut would work in our regime.
-For comparisons with ELVES and SAGA (Fig.
-\ref{fig:qfrac} and Fig.
-\ref{fig:qfrac_upg_elves}), we use the same color cut to keep the consistency.
-%\footnote{\jiaxuan{Add some robustness tests, such as ``Changing the intercept of the color cut to -0.28 makes the overall quenched fraction higher, but does not change the trend of quenched fraction as a function of stellar mass.''}}
-
-To apply the color cut, we derive the $V$-band apparent magnitude following $V = g - 0.5784\, (g - r) - 0.0038$\footnote{This relation was derived for SDSS filters.
-We neglect the small difference between SDSS and HSC filter systems.
-\url{http://classic.sdss.org/dr4/algorithms/sdssUBVRITransform.html\#Lupton2005}} and convert it to absolute magnitude $M_V$.
-Then we divide the stellar mass range $6.4 < \log\,M_\star/M_\odot < 9.0$ into 8 bins and calculate the fraction of quenched galaxies for each bin.
-Both the denominator and numerator are weighted by the importance weights $w_k$ (see \S \ref{sec:bkg}) and corrected for completeness.
-Not applying the importance weights will make the quenched fraction lower since the background contaminants are bluer on average than UDGs and UPGs.
-% We notice that such statistical background subtraction actually raise the quenched fraction since it reduces the impact of contaminants that are bluer in color.
-
-In Figure \ref{fig:qfrac}, the green lines show the quenched fractions $f_q$ as a function of stellar mass for the whole UDG (\textit{left}) and UPG (\textit{right}) samples, and the error bars correspond to the $1\sigma$ Bernoulli standard error.
-The quenched fraction of UDGs is high ($\sim 0.7$) over the full range of stellar mass ($6.5 < \log\,M_\star/M_\odot < 8$) and only weakly depends on the stellar mass.
-On the contrary, for UPGs, the quenched fraction strongly depends on the stellar mass.
-About 70\% of UPGs are quenched at $M_\star = 10^{6.8}\ M_\odot$, whereas only $\sim20\%$ of them are quenched at $M_\star = 10^{8.5}\ M_\odot$.
-At $M_\star \approx 10^{8}\ M_\odot$, about half of UPGs are quenched.
-This highlights the difference between the UDG and UPG populations.
-However, we argue that the high quenched fraction of UDGs is merely an artifact of the UDG definition, as discussed in Section \ref{sec:artifact}.
-
-We further divide the sample based on the projected radial distance to the host $R/R_{\rm vir}$ (top panels) and the host $g-i$ color (bottom panels).
-As shown in the top panels in Figure \ref{fig:qfrac}, we find that UDGs (UPGs) that are closer to the host have a higher quenched fraction.
-The average difference in quenched fractions between the two radial bins is $\sim 0.1$ for UDGs and $\sim 0.2$ for UPGs.
-% This trend is expected because the density of CGM is higher when it is closer to the host and thus quenches the UDGs (UPGs) via ram pressure stripping more efficiently.
-The tidal stripping is also stronger as satellites get closer to the host.
-From the bottom panels in Figure \ref{fig:qfrac}, we find that UDGs (UPGs) hosted by redder hosts also have a higher quenched fraction.
-The difference on quenched fraction between the two host color bins is $\sim 0.2$ for UDGs.
-But for UPGs, it seems that the host color impacts less than the distance to the host on the quenched fraction.
-% This result might hint at ``galaxy conformity'', which refers to the fact that late-type hosts tend to have more late-type satellites \citep{Weinmann2006}. 
-We also split the samples based on host stellar mass and host redshift, but do not find a significant difference in quenched fractions.
-The null trend with host redshift confirms that our background subtraction is valid.
-
-We compare the quenched fractions of UDGs and UPGs with satellites of MW-mass hosts in the Local Volume (ELVES), nearby Universe (SAGA), and numerical simulations.
-The ELVES sample already incorporates MW and M31 satellites.
-The quenched fractions from ELVES is shown in orange dashed lines, while SAGA results are shown as gray squares.
-The quenched fraction from ELVES and SAGA are calculated using the same color cut to define quenched galaxies as we do (see \citealt{CarlstenELVES2022}).
-SAGA quenched fractions are lower than ELVES arguably because SAGA survey is not sensitive to faint red galaxies below $\sbeffr = 25\sbunit$ \citep{CarlstenELVES2022,Font2022}. 
-We also overlie the quenched fractions from the ARTEMIS \citep[purple lines,][]{Font2022} and FIRE-2 \citep[pink dotted lines,][]{Samuel2022} simulations, where the quenched galaxies are defined as those with no instantaneous (for ARTEMIS) or recent ($<200$ Myr for FIRE-2) star formation.\footnote{\citet{Font2022} find a similar quenched fraction when using the color cut as we do.} We select ARTEMIS and FIRE-2 because they roughly cover the highest and lowest quenched fraction for MW satellites produced in simulations (see Fig.
-13 in \citealt{Samuel2022} for a compilation).
-Compared with these results, we see that UDGs have a higher quenched fraction than MW satellites especially at the high stellar mass end.
-Surprisingly, we find that the quenched fraction of UPGs agrees with both
-ELVES and simulations quite well, although these results are dominated by the bulk of MW satellites that are not as large as UPGs.
-
-Furthermore, we calculate the UPG quenched fraction in ELVES using the same color cut and highlight the results in Figure \ref{fig:qfrac_upg_elves}.
-We select 27 UPGs from 313 ELVES satellites with secure distances and their hosts all have coverage to 200 kpc.
-We find that the ELVES UPG quenched fraction agrees with our UPG quenched fraction very well albeit with large scatter.
-By comparing the quenched fraction of the whole ELVES sample with that of UPGs, we do not find any significant trend of quenched fraction on the size of the satellite.
-
-% lower-mass satellites are mostly quiescent, roughly half of intermediate-mass satellites are quiescent, and higher-mass satellites are mostly star-forming
-% the satellites in MW analogs are mostly quiescent below $M_\star\approx 10^7\ M_\odot$, and the quenched fraction drops as increasing stellar mass.
-
-\section{Discussion}\label{sec:discussion}
-
-\subsection{Robust identification of mass-size outliers}\label{sec:artifact}
+A systematic and careful comparison on UDG (UPG) fraction in different environments is needed in the future.
+
+\section{Discussion: robust identification of mass-size outliers}\label{sec:discussion}
+
+% \subsection{}\label{sec:artifact}
 % In this paper, we propose a robust definition of mass-size outliers (the UPGs). Here we contrast UPGs with UDGs to elaborate the fact that UPGs better represent mass-size outliers.
@@
 
-\subsection{UDG and UPG formation}
-In this paper, one surprising finding is that although UPGs have extremely large size for their stellar mass, they have similar quiescent fraction as normal satellites in MW analogs.
-This is also confirmed by comparing ELVES UPGs with the bulk of ELVES (Fig.
-\ref{fig:qfrac_upg_elves}).
-\citet{ELVES-I} find that the mass-size relation of satellites in MW analogs does not depend on the morphology or color of satellites, suggesting that the quenching and morphological transformation involves very mild size evolution.
-Together with our results, it is possible that quenching and size growth happen separately.
-Then the question is what physics is responsible for the two processes respectively.
-In this section, we first review the quenching of MW satellites and the mechanisms to puff up normal dwarfs to make outliers with respect to the average mass-size relation.
-Then we combine the results presented in Section \ref{sec:results} and discuss possible implications on the formation and quenching of UDGs and UPGs.
-
-%%%%%%%%%%%%%%%%%%%
-Isolated dwarf galaxies in the field are known to be star-forming \citep{Geha2012}, but satellites in the Local Group and Local Volume are more quiescent \citep{Grcevich2009,Spekkens2014,Wetzel2015,Putman2021,Baxter2021,CarlstenELVES2022,Karunakaran2022}.
-This difference hints that environment plays an important role in regulating the star formation activities in satellite galaxies \citep{Peng2010}.
-There have been extensive works using simulations to study the quenching of satellites in MW analogs \citep[e.g.,][]{Simpson2018,Buck2019,Garrison-Kimmel2019,Simons2020,Joshi2021,Akins2021,Karunakaran2021,Font2022,Samuel2022,Pan2022}, and many of them are able to reproduce the observed quenched fraction in the Local Group and in the Local Volume.
-
-In theory, satellite galaxies in MW analogs are accreted from the field, therefore quenching can happen either before or after the infall to MW host.
-In the former case, isolated dwarf galaxies can be quenched by bursty stellar feedback \citep[e.g.,][]{Bahe2015,Kazantzidis2017,ElBadry2018}, reionization for ultra-faint dwarfs \citep[e.g.,][]{Bullock2000,Benson2002,Somerville2002,Tollerud2018,Applebaum2021}, or spending time within a more massive halo, as in the case of so-called backsplash galaxies \citep{Simpson2018,Benavides2021}.
-If a satellite is star-forming before infall, the ram pressure \citep[e.g.,][]{GunnGott1972,McCarthy2008,Emerick2016,Simpson2018,Tremmel2020,Samuel2022} experienced by the satellite as it moves through the hot circumgalactic medium (CGM) of the host could remove the gas and cause the cessation of star formation.
-It has been shown that ram pressure stripping can
-efficiently quench galaxies at $M_\star < 10^{8}\ M_\odot$ \citep{Fillingham2016,Simpson2018,Buck2019}.
-Tidal stripping can also remove the gas from the satellite or stop the gas accretion and starve the galaxy \citep{Simpson2018}, but strong tidal interactions are needed because dark matter needs to be stripped before significant gas loss happens.
-Another quenching mechanism is the so-called preprocessing in a lower-mass group prior to the infall into a MW analog \citep{Wetzel2015b,Jahn2022,Samuel2022}.
-Satellites might be quenched in the previous group via ram pressure stripping or tidal interactions, and the gas distribution can also be altered in preprocessing without being quenched.
-\citet{Samuel2022} show that 40\% of satellites were preprocessed before the infall to MW.
-Some studies also show that the paired host environments might enhance the quenching of satellites (\citealt{Garrison-Kimmel2019,Putman2021}, but also see \citealt{Samuel2022}).
-
-For UDGs and UPGs in MW analogs, we are still left with the question of how they became so physically large for their mass.
-Many mechanisms are proposed to explain the large size of UDGs (UPGs) in simulations.
-For isolated UDGs, bursty stellar feedback can cause the stellar component of the dwarf galaxy to expand \citep[e.g.,][]{DiCintio2017,Chan2018,Martin2019,Jiang2019,Carleton2019}.
-Analytical models also support a scenario where UDGs originate from a population of dwarf galaxies residing in halos with higher spin \citep{Dalcanton1997,Amorisco2016,Rong2017,Liao2019}.
-\citet{Wright2021} show that field UDGs can also be formed from major mergers that cause star formation to migrate outward.
-For UDGs in groups and clusters, environmental effects are more pronounced and tidal interactions are believed to puff up normal dwarfs.
-\citet{Jiang2019} find that the UDGs in groups are either accreted as UDGs from the field or accreted as normal dwarfs but tidally heated near the orbital pericenter.
-\citet{Tremmel2020} study UDG formation in the cluster environment and find UDGs with higher mass ($M_\star > 10^{8}\ M_\odot$) are puffed up suddenly due to tidal heating at pericenter, but UDGs with lower mass ($M_\star \sim 10^{7.5}\ M_\odot$) are gradually puffed up due to adiabatic expansion as a response to the mass loss from tidal stripping and ram pressures stripping.
-\citet{Kado-Fong2021} study the intrinsic shapes of UDGs in observations and find the inferred shapes agree with merger scenario for field UDGs \citep{Wright2021} and tidal heating/adiabatic expansion for group/cluster UDGs \citep{Jiang2019,Tremmel2020}, but the intrinsic shapes of field UDGs are similar to those of cluster UDGs.
-
-For UDGs in groups, since they probably experienced strong tidal interactions, it is not obviously clear whether they are quenched mainly by tidal stripping or ram pressure stripping. 
-% In the tidal stripping scenario, dark matter needs to be removed before a significant fraction of gas are deprived by tidal force, indicating a longer quenching timescale. 
-\citet{Jiang2019} argue that if tidal stripping dominates the quenching, the satellite closer to the host will have smaller stellar mass and effective radius since stars are also stripped.
-They find no such trend in simulation for group environments, but find that the average color is redder when the UDGs are closer to the host, supporting that ram pressure stripping is more dominant.
-In Section \ref{sec:size_distr}, we split the sample into two radial distance bins, and we do not find significant change in size or stellar mass distribution as UDGs get closer to the host.
-
-In the Auriga simulations, \citet{Simpson2018} show that the quenched fraction of satellites $M_\star < 10^8\ M_\odot$ have a strong dependence on the distance to the hosts.
-Using the FIRE-2 simulation, \citet{Samuel2022} also show that the quenched fraction increase as the distance to the host decreases, and hosts with higher CGM mass have more quenched satellites.
-In Figure \ref{fig:qfrac}, by comparing UDGs and UPGs at two radial bins, we find a very similar trend that UDGs (UPGs) closer to the host are more quiescent.
-% In the ram pressure stripping picture, this is because the density of CGM increases when being closer to the host and the ram pressure is stronger. 
-Together with the null trend on size and stellar mass distribution as UDGs (UPGs) get closer to their hosts, our findings support that ram pressure stripping is the major quenching channel for UDGs (UPGs) in MW analogs.
-
-If UPGs are quenched by ram pressure stripping, how are they puffed up such that the quenching and size growth happen separately?
-UPGs can be puffed during the infall or prior to the infall.
-If UPGs are accreted into MW hosts from the field as normal dwarfs and puffed up due to tidal heating near pericenter passages, we might expect a higher quenched fraction since they also undergo violent ram pressure stripping.
-If they are puffed up through a longer-term adiabatic expansion from the mass loss due to tidal stripping, the expansion should also be proportional to the amount of gas loss, which translates to quenched fraction.
-Therefore, tidal puffing during infall seems to contradict with the quenched fraction as seen in Figure \ref{fig:qfrac_upg_elves}.
-
-It is more feasible that UPGs are already puffed up and remain star-forming before accretion.
-They are quenched by ram pressure stripping in the MW host together with other normal satellites.
-In order to achieve similar quenched fraction as normal satellites, field UPGs prior to infall have to be star-forming.
-Stellar feedback, early merger, higher halo spin, and preprocessing can all puff up the field dwarfs to become UPGs, and some of them seem not to quench the UPGs.
-\citet{Wright2021} show that early merger does not significantly change the total SFR.
-\citet{Samuel2022} show that preprocessing can marginally boost the quenched fraction by 20\% at $M_\star \approx 10^8\ M_\odot$ and merely change the quenched fraction for lower mass satellites.
-Although it is not clear whether the high halo spin is the cause or the consequence of UPG formation, it is probable that higher halo spin does not quench a UPG.
-If any of these mechanisms can only increase the size to make UPGs but not quench them, it provides a plausible way to produce the observed trend in Figure \ref{fig:qfrac} and Figure \ref{fig:qfrac_upg_elves}.
-
-However, the efficiency of ram pressure stripping also depends on the stellar mass density which provides the restoring force and the gas mass density.
-The diffuse stellar component might make UPGs more vulnerable to ram pressure stripping and tidal stripping.
-Kado-Fong et al.
-(submitted) find that although UDGs have a diffuse stellar component, they harbor the same amount of \ion{H}{1} for their size as normal dwarfs.
-Therefore, for a given stellar mass, UDGs (UPGs) have higher \ion{H}{1} mass than normal dwarfs, thus even if UDGs and UPGs are more vulnerable to ram pressure stripping, there is more gas to be stripped.
-It is probable that the net effect of low stellar mass density and high \ion{H}{1} mass is that UPGs have similar quenched fraction as normal satellites.
-
-UPGs in MW analogs can also be a mixture of field UPGs and normal dwarfs puffed up during infall.
-Using our observations, it is hard to sort out detailed mechanisms for quenching and size growth of UPGs.
-More detailed studies in observation and simulation are needed to solve this puzzle.
-
-% \jiaxuan{Discuss the UDG fraction v.s. group mass game. How environment shapes the size distribution.}
-
-% \citet{Wright2021} observed a temporary boost in spin after the early merger. 
-% \citet{Samuel2022} show that 40\% of satellites were in another group prior to the infall to MW, and preprocessed satellites have higher quenched fraction, and 10\% were quenched during preprocessing.
-
-% \jiaxuan{But UDGs have higher HI surface density?} 
-% splashback: they must be quenched in their prior infall.
-
-% \citet{Samuel2022} find that HI gas can form a concentrated core after ram-pressure stripping and be there for quite long.
-\citet{Font2022} find LSB galaxies in FIRE-2 have concentrated stellar core.
-Oh, but the core might not be dense enough to form stars.
-
-% calculate probability of being a backsplash satellite (e.g., splashed to 1.5 Mpc)
-% Compare spatial distribution with normal dwarf? iF they are indeed high-spin tail of normal dwarfs.
-
 \section{Summary}\label{sec:summary}
-In this work, we present a comprehensive study for mass-size outliers around Milky Way analogs at $0.01 < z < 0.04$.
+In this work, we present a comprehensive study for mass-size outliers around MW analogs at $0.01 < z < 0.04$.
 Beside the ultra-diffuse galaxies, we propose studying ``ultra-puffy galaxies'' which is defined to be $1.5\sigma$ above the average mass-size relation.
@@
 
-    \item The radial distributions of UDGs and UPGs from their hosts can be described by projected NFW and Einasto profiles.
-We find that the best-fit NFW profiles are consistent with the NFW profile of a MW-mass halo, whereas the best-fit Einasto profiles have smaller concentrations than MW halos.
-The UDG and UPG follow similar radial distributions.
-
-    \item We find that UDGs have high quenched fractions ($\sim 70\%$) and remain constant over 1.5 dex in satellite stellar mass (Figure \ref{fig:qfrac}).
-For UPGs, the quenched fraction is high at the lower-mass end $M_\star = 10^{6.8}\ M_\odot$, but the quenched fraction drops to $\sim 20\%$ at $M_\star = 10^{8.5}\ M_\odot$.
-Almost half of UPGs are quenched at $M_\star \approx 10^{8}\ M_\odot$.
-The quenched fractions of both UDGs and UPGs increase as satellites get closer to the hosts.
-Redder hosts also harbor more quenched UDGs and UPGs.
-
-    \item Surprisingly, the quenched fraction of UPGs is very similar to the quenched fraction of the ``normal'' satellites in ELVES, although UPGs are mass-size outliers (Figure \ref{fig:qfrac_upg_elves}).
-We select ELVES UPGs and find they also have similar quenched fractions.
-The UPG quenched fraction also agrees with simulations (e.g., ARTEMIS \citealt{Font2022}, FIRE-2 \citealt{Samuel2022}) focusing on the bulk of MW satellites.
-The null trend of quenched fraction on the size of satellites indicates that quenching and size evolution of mass-size outliers happen separately in MW-like environments.
-It is plausible that these mass-size outliers are puffed up in the field before accretion, and quenched together with other MW satellites.
-
-    \item We argue that the high and constant quenched fraction for UDGs is merely an artifact of the UDG definition which does not consider the color-$M_\star/L$ relation.
-We advocate studying UPG which is more physically motivated, does not introduce artifacts in the mass-size distribution, and better represents the large-size tail of dwarf galaxy population.
+    \item We advocate studying UPG which is more physically motivated, does not introduce artifacts in the mass-size distribution, and better represents the large-size tail of dwarf galaxy population.
 % \end{itemize}
@@
 With the upcoming Vera Rubin Observatory Legacy Survey of Space and Time \citep[LSST, ][]{lsst2009,LSST2019}, we will be able to study the LSBG population with much greater statistics and gain new insights on the formation and evolution of mass-size outliers.
+
+\jiaxuan{Mention our paper II (to be submitted)}
 

### 2022-10-12 paper0.tex
done except for discussion section
before sending to coauthors

--- 2022-10-09 paper1.tex
@@
 % \title{Ultra Diffuse Galaxies associated with Milky-Way Analogs}
-\title{Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers in the Satellites of Milky Way Analogs}
+\title{Original Beyond Ultra-Diffuse Galaxies: Mass-Size Outliers in the Satellites of Milky Way Analogs}
 
@@
 Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed and quenched.
-It is also unclear whether mass-size outliers belong to a special class of galaxies or are just a natural extension of dwarf systems to lower surface brightness.
+It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness.
 To answer these questions, we can compare mass-size outliers with ``normal'' low mass galaxies for which we have a better understanding.

### 2022-10-12 paper1.tex
before sending to coauthors

@@
 
-% \title{Ultra Diffuse Galaxies associated with Milky-Way Analogs}
 \title{Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers in the Satellites of Milky Way Analogs}
@@
 \begin{abstract}
-Large diffuse galaxies are hard to find, but understanding their environments and abundance, and ultimately their origins, is of intense interest.
+Large diffuse galaxies are hard to find, but understanding the environments where they live and their numbers, and ultimately their origins, is of intense interest and important for galaxy formation and evolution.
 Using the Hyper Suprime-Cam data, we perform a systematic search for low surface-brightness galaxies and present novel and effective methods for detecting and modeling them.
 As a case study, we build a statistical sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$).
-These ``ultra-puffy'' galaxies, defined to be $1.5\sigma$ above the average mass-size relation, better represents the tail of satellite size distribution.
-We find that the number of ultra-puffy galaxies per host is comparable to the observed abundance at this halo mass in the Local Volume.
-We also construct a sample of ultra-diffuse galaxies and compare their abundance with literature.
-We argue that our definition, based on the mass-size relation, is more robust than the common definition of ultra-diffuse galaxies, which depends on a surface brightness cut and thus yields different surface mass density cuts for quenched and star-forming galaxies.
+These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, better represents the tail of satellite size distribution.
+We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is comparable to the observed abundance at this halo mass in the Local Volume.
+We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.76\pm0.04$ per host.
+We compare with literature results including UDG searches in clusters and massive groups.
+The UDG abundance scales with the host halo mass following a sublinear power law.
+We argue that our definition for ultra-puffy galaxies, which is based on the mass-size relation, is more physically-motivated and objective than the common definition of ultra-diffuse galaxies, which depends on a surface brightness cut and thus yields different surface mass density cuts for quenched and star-forming galaxies.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-[\textbf{Need to rewrite}] In a variety of galaxy populations, an interesting subset of galaxies with low surface brightness and large physical size have been identified \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
+In a variety of galaxies in the Universe, an interesting subset of galaxies with low surface brightness and large physical size have been identified \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
 Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
-There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
-UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus have very large sizes for their stellar mass.
-Therefore, a central question about LSBGs, including UDGs, is what causes them to be outliers from the mass-size relation.
+There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
+UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus have very large sizes for their stellar mass compared to normal dwarf galaxies.
+Therefore, a central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation?
 % Therefore, a central question about mass-size outliers including UDGs is what physical mechanisms are responsible for the formation and quenching of these large diffuse galaxies.
 
-Different mechanisms are proposed to explain the presence of large diffuse galaxies in different environments.
-In the field (i.e, in isolation), their large sizes might be caused by star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}.
-In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019} or via adiabatic expansion due to mass loss \citep{Tremmel2020}.
+Various mechanisms have been proposed to explain the presence of large, diffuse galaxies (as mass-size outliers) across different environments.
+In the field (i.e, in isolation), their large sizes might be caused by stellar feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}.
+In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019}, via adiabatic expansion due to mass loss \citep{Tremmel2020}, or even via a bullet-dwarf collision \citep{vandokkum2022Nat,vanDokkum2022GC}.
 Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed and quenched.
-It is also unclear whether mass-size outliers belong to a special class of galaxies or are just a natural extension of dwarf systems to lower surface brightness.
-To answer these questions, we can compare mass-size outliers with ``normal'' low mass galaxies for which we have a better understanding.
-
-Our best understanding of the low mass regime comes from the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}.
+It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness or larger size.
+A nice way to to answer these questions is to compare these mass-size outliers with ``normal'' low mass galaxies for which we have a better understanding.
+
+Our best understanding of the low mass galaxy regime comes from the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}.
 With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs in the Local Volume and nearby Universe.
-The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at $z\sim0.01$ \citep{SAGA-I,SAGA-II}.
-The Exploration of Local VolumE Satellites (ELVES) survey uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts \citep{ELVES-I,ELVES-II,CarlstenELVES2022}.
-Having the MW satellites as a reference frame, we can study the formation and quenching of large diffuse galaxies by comparing them with the bulk of observed and simulated MW satellites.
-However, there are only $\sim 30$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022}.
-A larger sample of mass-size outliers (including UDGs) associated with MW hosts is needed to conduct such a comparison.
-
-The goal of this paper is to study large diffuse galaxies in the reference frame of the satellite systems of MW analogs and try to elucidate their formation and quenching.
-For this purpose, we propose a new definition for mass-size outliers, dubbed ``ultra-puffy galaxies'' (UPGs), based on the observed mass-size relation and its scatter.
-This definition is more robust to mass-to-light differences between red and blue galaxies compared to the UDG definition.
-Leveraging the depth and wide sky coverage of Hyper-Suprime Camera (HSC) imaging data, we are able to build a large statistical sample of mass-size outliers that are likely satellites of MW-mass hosts in the nearby Universe.
-The good statistics of our samples enable us to examine the abundance, size distribution, spatial distribution, and quenching of mass-size outliers.
-By comparing mass-size outliers with normal satellites and simulations, our results seek to shed light on the formation and evolution of the large diffuse galaxies.
-
-\jiaxuan{Bring up something like: we develop the machinery, and only applied it to MW analogs as a touchstone.}
+The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at 20-40 Mpc \citep{SAGA-I,SAGA-II}.
+The Exploration of Local VolumE Satellites (ELVES,  \citealt{ELVES-I,ELVES-II,CarlstenELVES2022}) survey uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts.
+Having these MW satellites as a reference frame, we can contrast them with the large diffuse galaxies in the same environment to understand the formation of diffuse galaxies.
+However, there are only $\sim 40$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022,Karunakaran2022b}.
+A larger sample of mass-size outliers (including UDGs) associated with MW-like hosts is needed to conduct such a comparison between the mass-size outliers and the normal satellites.
+
+The goal of this paper is to find and study large diffuse galaxies in the context of the satellite systems of MW analogs.
+Leveraging the depth and wide sky coverage of Hyper-Suprime Cam (HSC) Subaru Strategic Program imaging data, we perform a search for LSBGs using novel methods in detection, false positive identification, and modeling.
+We further build a large sample of mass-size outliers that are likely satellites of MW-mass hosts in the nearby Universe.
+We propose a new definition for mass-size outliers, dubbed ``ultra-puffy galaxies'' (UPGs), based on the observed mass-size relation in the Local Volume using ELVES sample.
+This concept is less affected by the galaxy color and provides a robust avenue to study the mass-size outlier population.
+We examine the abundance of mass-size outliers in MW analogs and compare with their abundances in other environments.
+Our results seek to shed light on the role of environment on the formation of large diffuse galaxies.
+%By comparing mass-size outliers with normal satellites and simulations, our results seek to shed light on the formation and evolution of the large diffuse galaxies.
 
@@
 Section \ref{sec:data} describes the data used in this work.
-In Section \ref{sec:lsbg_search}, we describe the LSBG search in the HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), and modeling (\S \ref{sec:modeling}).
+In Section \ref{sec:lsbg_search}, we describe the LSBG search in the HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), modeling (\S \ref{sec:modeling}), and completeness and uncertainty (\S\ref{sec:comp_meas}).
 In Section \ref{sec:sample_construction}, we propose a new definition for large and diffuse galaxies (the UPGs) and present our UDG and UPG samples.
-In Section \ref{sec:results}, we show statistical analysis for UDGs and UPGs including their abundances (\S \ref{sec:n_udg}), size distributions (\S \ref{sec:size_distr}), spatial distributions (\S \ref{sec:radial_distr}), and quenched fractions (\S \ref{sec:quench}).
-We argue why we need to move beyond UDG and discuss possible implications of our results on the formation and quenching of mass-size outliers in Section \ref{sec:discussion}.
+In Section \ref{sec:results}, we show statistical analysis for UDGs and UPGs including their distribution on the mass-size plane and their abundances (\S \ref{sec:n_udg}).
+We further argue why we need to move beyond UDG and adopt UPG definition in Section \ref{sec:discussion}.
 Section \ref{sec:summary} presents a summary of this work and prospects for the future.
-In this work, we refer to LSBGs as objects selected purely by surface brightness, whereas UDGs and UPGs are selected by both physical size and surface brightness.
+In a companion paper (Li et al., to be submitted), we discuss the size distributions, spatial distributions, and star formation quenching of UDGs and UPGs.
+
+In this work, we refer to LSBGs as objects selected purely by surface brightness, whereas mass-size outliers (including UDGs and UPGs) are selected based on physical size, surface brightness, or stellar mass.
 We adopt a flat $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$.
@@
 \section{Data} \label{sec:data}
-\subsection{Hyper Suprime-Camera data}
+\subsection{Hyper Suprime-Cam Subaru Strategic Program}
 The Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP, \citealt{Aihara2018}; hereafter the HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}.
@@
 In this work, we use the \code{Wide} layer coadd data from the Public Data Release 2 (PDR2, also known as \code{S18A}, \citealt{Aihara2018}) of the HSC survey.
-It covers $\sim 300\ \rm{deg}^2$ in all five bands, being 1.5 times larger than the data set (\code{S16A}) analyzed in \citet{Greco2018}.
+It covers $\sim 300\ \rm{deg}^2$ in all five bands, which is 1.5 times larger than the dataset (\code{S16A}) analyzed in \citet{Greco2018}.
 One of the key improvements made in PDR2 is the sky background subtraction.
 Compared with previous data releases, PDR2 adopted a full focal plane sky subtraction algorithm to overcome the over-subtraction of the local sky background around bright objects \citep{Aihara2018,Li2021}.
-The unprecedented depth and careful sky subtraction make PDR2 an ideal data set to study low surface brightness galaxies.
+The unprecedented depth and careful sky subtraction make PDR2 an ideal dataset to study low surface brightness galaxies.
 In this work we use the PSF models generated by \code{hscPipe}.
 
-%HSC \code{S18A} also provides bitmasks indicating bad pixels, cosmic rays, edges of CCDs and pixels with source detection, helping us generate image masks when extracting surface brightness profiles (Section \ref{sec:hsc_methods}).
-In this paper, we use the \code{WIDE} layer data from \code{S18A} (\code{PDR2}).
-It covers $\sim 300$ deg$^2$ in all five bands.
-
 \subsection{NASA-Sloan Atlas}
-We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way, then we match the LSBGs to these MW analogs (see \S \ref{sec:sample_construction}).
-The NSA catalog provides various physical properties of galaxies in the nearby universe as derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}.
-We use the newer version of the NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$.
-The new version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions.
+We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way based on their stellar mass (see \S\ref{sec:match}), then we match the LSBGs to these MW analogs.
+The NSA catalog provides various physical properties of galaxies in the nearby Universe as derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}.
+We use the most recent version of the NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$.
+This version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions.
 In this paper, we use the stellar mass derived from elliptical Petrosian photometry using \code{kcorrect v4\_2} \citep{Blanton2007}.
@@
 The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section.
-We outline the major steps below and refer the reader to Section \ref{sec:sample_construction} for UDG and UPG sample construction.
+We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for UDG and UPG sample construction.
+
 \begin{enumerate}
@@
 The number of objects remained after each step is shown in Table \ref{tab:steps_flow}.
-Our source detection pipeline \href{https://github.com/johnnygreco/hugs}{\code{hugs}} and deblending and modeling code \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} are open-sourced and available online.
+Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} and deblending and modeling code \code{kuaizi}\footnote{\url{https://github.com/AstroJacobLi/kuaizi}} are open-sourced and available online.
 
@@
 \citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs.
-We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction compared to previous data releases.
+We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction for LSB studies compared to previous data releases.
 We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate PDR2 data.
-These updates are guided by both our understanding of PDR2 data and the completeness tests using mock galaxies.
+These updates are guided by both our understanding of PDR2 data and completeness tests using mock galaxies.
 We summarize the main steps of LSBG search method here, and refer the interested readers to \citetalias{Greco2018} and Appendix \ref{ap:detection} for more details.
@@
 After these steps, we have an initial sample that contains 86,002 LSBG candidates.
-We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because HSC PDR2 has better sky subtraction, our detection here is more inclusive of larger objects, and our size cut is less restrictive for small objects.
+We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because HSC PDR2 has a sky subtraction suited for finding LSB features, our detection here is more inclusive of larger objects, and our size cut is less restrictive for small objects.
 Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirrus, and blended compact sources.
@@
 Here we show two objects from our initial sample: the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts.
-The data shown in the first column is $griz$ color-composite image with the bounding boxes overlay.
+The first columns show the $griz$ color-composite images with the bounding boxes overlaid.
 The objects covered by the gray shades are masked during fitting.
@@
 
-Removing false positives from the initial sample while retaining high completeness is one of the major challenges in LSBG search \citep[e.g.,][]{vanDokkum2015,Koda2015,Yagi2016,Greco2018,SAGA-I,Zaritsky2019,Zaritsky2021,Tanoglidis2021,Zaritsky2022}.
+Removing false positives from the initial sample while retaining high completeness is one of the major challenges in LSBG searches \citep[e.g.,][]{vanDokkum2015,Koda2015,Yagi2016,Greco2018,SAGA-I,Zaritsky2019,Zaritsky2021,Tanoglidis2021,Zaritsky2022}.
 A common type of false positive occurs when point-like sources are blended with diffuse light from background galaxies or the LSB outskirts of stars and galaxies.
-Our initial detection cannot distinguish them from the real LSBGs.
+Our initial detection cannot distinguish them from real LSBGs.
 In order to identify and remove these objects from our sample, we perform non-parametric modeling using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018} and design an efficient metric to remove false positives.
@@
 \code{Scarlet} is a deblending and modeling tool designed for multi-band and multi-resolution imaging data.
-It utilizes the color and morphology information to separate blended objects.
+It utilizes color and morphology information to separate blended objects.
 In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation\footnote{\url{https://pmelchior.github.io/scarlet/}} for more details.
 
-In \code{scarlet}, each source $k$ in the cutout is described by a morphology image $S^k_i$ and a Spectral Energy Distribution (SED) vector $A^k_i$, and the multi-band images is $Y_i$, where $i$ denotes different bands.
-The goal of the modeling is to minimize the objective function $f = \frac{1}{2}\sum_i ||Y_i - P \ast (\sum_k A^k_i\times S^k_i)||^{2}$ under certain constraints, where $P$ is the PSF and $*$ is convolution.
+In \code{scarlet}, each source $k$ in the cutout is described by a morphology image $S_k$ and a Spectral Energy Distribution (SED) vector $A_k$, and the multi-band images is $Y$.
+The goal of the modeling is to minimize the objective function $f = \frac{1}{2} ||Y - P \ast (\sum_k A_k^\top \times S_k)||^{2}$ under certain constraints, where $P$ is the PSF and $*$ is convolution.
 The morphology image of each source is limited by a bounding box.
@@
 
-After running the vanilla \code{scarlet} for LSBG candidates, we successfully deblend the target object from nearby sources.
-Unlike other parametric modeling methods, the non-parametric \code{scarlet} model is very flexible on modeling galaxies with complex structures.
+After running vanilla \code{scarlet} for LSBG candidates, the target object has been successfully deblended from nearby sources.
+Unlike other parametric modeling methods, the non-parametric \code{scarlet} model is flexible enough to adequately represent galaxies with complex structures.
 But the non-parametric nature of the code means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model.
@@
 The variance map and PSF are taken from HSC cutouts.
-We also force the sky level to be zero because sky has already been fit when running vanilla \code{scarlet}.
+We also force the sky level in \code{Statmorph} to be zero because sky has already been fit when running vanilla \code{scarlet}.
 
@@
 In \code{statmorph}, the effective radius is calculated using elliptical apertures, where the ellipticity $\varepsilon$ is determined by calculating the second moment of the image.
-The total magnitudes are simply calculated by summing up the model in each band, and colors are defined using total magnitudes.\footnote{A Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
+The total magnitudes are simply calculated by summing up the model flux in each band, and colors are defined using total magnitudes.\footnote{A Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
 We define the average surface brightness within the effective radius as
@@
 
-To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the labels to construct the metrics.
-To be specific, we randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see \S\ref{sec:match} for details).
+To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the classification results to help construct the metrics.
+To be specific, we randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ from the NSA catalog (see \S\ref{sec:match} for details).
 We run vanilla \code{scarlet} for all of them and measure morphological parameters as described above.
-Then we do visual inspection by looking at the $griz$ color-composite images with 0.5 arcmin on a side.
-Objects are classified into three types: LSB galaxies with typically dwarf galaxy features (dubbed \code{candy}), high surface brightness galaxies, or galaxies with spiral galaxy features (\code{galaxy}), and false positives including tidal streams, galaxy outskirts blends, and other artifacts (\code{junk}).
+Then we do visual inspection of the $griz$ color-composite images with 0.5 arcmin on a side.
+Objects are classified into three types: LSB galaxies with typical dwarf galaxy features (dubbed \code{candy}), high surface brightness galaxies, or galaxies with spiral galaxy features (\code{galaxy}), and false positives including tidal streams, galaxy outskirts blends, and other artifacts (\code{junk}).
 The difference between \code{candy} and \code{galaxy} can be quite ambiguous.
@@
 
-We use these visual inspection results to teach us how to use the morphological and structural diagnostics.
+We use these visual inspection results to inform how to use the morphological and structural diagnostics.
 The distributions of \code{candy} (blue), \code{galaxy} (green), and \code{junk} (red) in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}.
@@
 These criteria (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove objects that are not likely to be LSBGs of interest.
-The color cuts here are restrictive than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and background high redshift galaxies.
+The color cuts here are more restrictive than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and background high redshift galaxies.
 We not only remove objects with small sizes, but also exclude objects with large size, very low surface brightness, and high concentration.
 This is because the scarlet models of some junk can be very concentrated in the center but also very extended.
-The slant demarcation line on the Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to separate merging galaxies from normal galaxies.
+The slanted demarcation line on the Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to separate merging galaxies from normal galaxies.
 
@@
 With these cuts, 97\% of the false positives are removed, but the majority (70\%) of \code{candy} still remains.
-The number of \code{galaxy} also drops by 76\%.
+The \code{galaxy} subset also drops by 76\%.
 This empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample.
@@
 We will also explore machine learning methods and compare with our deblending cuts in future works.
-We would also like to utilize information about Milky Way dust to exclude spurious detection on Galactic cirrus \citep[e.g.,][]{Zaritsky2021,Zaritsky2022}.
+Future work will also utilize information about Milky Way dust to exclude spurious detection on Galactic cirrus \citep[e.g.,][]{Zaritsky2021,Zaritsky2022}.
 
@@
 Although UDGs are large in size, the constant size cut does not account for the fact that the galaxy size is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
-Therefore, an more intuitive definition for diffuse and puffy dwarf galaxies (i.e., mass-size outliers) should be based on a mass-size relation and its scatter.
+
+A more intuitive definition for diffuse and puffy dwarf galaxies (i.e., mass-size outliers) should be based on a mass-size relation and its scatter.
 Following this thread, we propose a new definition for mass-size outliers dubbed as \textit{ultra-puffy galaxies} (UPGs).
@@
 The size criterion also varies from $r_e > 1$ kpc to $r_e > 1.5$ kpc.
-\citet{vanNest2022} explore these definitions in simulation and find that different choice of UDG can drastically change the selected subset of dwarfs, therefore affect our understanding of the UDG population.
+\citet{vanNest2022} explore these definitions in simulations and find that different definitions of ``UDG'' can drastically change the selected subset of dwarfs, therefore affecting our understanding of the UDG population.
 
@@
 
-We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2 regardless of whether containing MW analogs.
+We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2 regardless of whether containing MW analogs\footnote{$345\ \deg < \rm{R.A.} < 351\ \deg$, $-1.5\ \deg < \rm{Dec} < 2.5\ \deg$, which is not dominated by Galactic cirrus and stars.}.
 Then we perform the same deblending and modeling steps for the 2,707 LSBGs detected in this region.
@@
 Furthermore, we also did the same visual inspection as for UDGs and UPGs to remove false positives.
-In the end, there are 480 LSBGs (not false positives) representing a population of possible contaminants for the UDG and UPG samples.
+In the end, there are 480 LSBGs (excluding false positives) representing a population of possible contaminants for the UDG and UPG samples.
 Next, because both UDG and UPG are defined based on a physical size, we randomly associate the 480 LSBGs to the hosts of our UDGs and UPGs, respectively.
@@
     \caption{\textit{Left panel}: a schematic diagram showing the UDG size cut (gray band), survey limit (blue shade), the average mass-size relation (dark green dashed line) and $1.5\sigma$ above it (light green line).
-The solid lines are constant surface brightness cuts at $\sbeff=25\ \sbunit$ for two different colors $g-i=0.4,\ 0.8$.
-The constant surface stellar mass density line is in purple.
+The solid lines are constant surface brightness cuts at $\sbeff=25\ \sbunit$ for two different colors $g-i=0.4$ (blue) and $g-i=0.8$ (red).
+The constant surface stellar mass density line is in purple, which is parallel to the solid lines.
 \textit{Right panel}: The distributions of UDGs and UPGs on the mass-size plane.
@@
 We show the $r_e = 1.5$ kpc cut as a gray band to acknowledge the fact that smaller galaxies with large size uncertainty can also get into the UDG sample.
-The slant solid lines show the constant surface brightness lines with $\sbeff = 25.0\ \sbunit$ for two different colors ($g-i=0.4$ and $g-i=0.8$).
+The slanted solid lines show the constant surface brightness lines with $\sbeff = 25.0\ \sbunit$ for two different colors ($g-i=0.4$ and $g-i=0.8$).
+For our redshift range, the cosmological dimming effect is negligible and the surface brightness is a constant with distance.
 The constant surface brightness lines depends on color because of the color-$M_\star/L$ relation.
-We also show the constant surface stellar mass density ($\mu_\star$) line, which is parallel to the constant surface brightness lines.
+We also show the constant surface stellar mass density ($\mu_\star$) line, which is parallel to the constant surface brightness lines because the surface mass density is proportional to surface brightness multiplied by mass-to-light ratio.
 Therefore, at a given size, blue UDGs are less massive than red UDGs; at a given stellar mass, blue UDGs are larger than red UDGs in size.
@@
 We note that \citet{Roman2017b} do not estimate the background contamination fraction and correct for completeness.
+Because there is little literature on UPGs, we only compare our UPG abundance with ELVES.
+In ELVES, we take the 351 satellites with secure distances in 30 MW analogs and identify 36 UPGs associated with 20 hosts.
+Thus the UPG abundance fraction in ELVES is $N_{\rm UPG}^{\rm ELVES} = 1.20 \pm 0.20$, which is higher than our UPG abundance.
+
 We plot the UDG abundances of these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017}.
-Among these studies, only \citet{vdBurg2017} applies a background subtraction and completeness correction to the raw counts.
-
-% In the Auriga simulations, \citet{Liao2019} find $N_{\rm UDG,\,Auriga}=1.27\pm 1.06$ for UDGs in MW-mass hosts.
-
 The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray.
@@
 Therefore we caution that the power law index here should not be over-interpreted.
+% Among these studies, only \citet{vdBurg2017} applies a background subtraction and completeness correction to the raw counts.
 % If completeness is applied, it is possible that the slope $\beta$ will be steeper than what we are showing in Figure \ref{fig:n_udg}.
-% We also note that many studies do no consider measurement bias and uncertainty, which makes the comparisons more difficult.
 
@@
 We find that the UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger with host color.
-% Since there are not many data sets available for us to derive UPG abundances, we only take the ELVES results \citep{CarlstenELVES2022} and obtain $N_{\rm UPG} = $
-
-Because there is little literature on UPGs, we only compare our UPG abundance with ELVES.
-In ELVES, we take the 351 satellites with secure distances in 30 MW analogs and identify 36 UPGs associated with 20 hosts.
-Thus the UPG abundance fraction in ELVES is $N_{\rm UPG}^{\rm ELVES} = 1.20 \pm 0.20$, which is higher than our UPG abundance.
+\vspace{1em}
 
@@
 Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}), there are 15 UDGs and 24 UPGs out of 404 identified satellites with no completeness correction.
-Thus their UDG (UPG) fraction is $f_{\rm UDG,Virgo} \approx 0.04$ and $f_{\rm UPG,Virgo} \approx 0.06$.
+Thus their UDG (UPG) fraction is $f_{\rm UDG}^{\rm Virgo} \approx 0.04$ and $f_{\rm UPG}^{\rm Virgo} \approx 0.06$.
 However, we note that \citet{Ferrarese2020} only survey the central 4 deg$^2$ of the Virgo cluster, which probably biases the UDG (UPG) fraction.
@@
 
-In the left panel of Figure \ref{fig:mass_size}, we find that combining a hard physical size cut with a surface brightness cut carves out an interesting region of the mass-size plane that is complicated in two ways.
-On the one hand, there are many galaxies classified as UDGs that are not size outliers at $M_\star \sim 10^{7.5}\ M_\odot$.
-On the other hand, the hard surface brightness cut corresponds to very different surface mass density between red and blue galaxies, making it hard to directly compare red and blue diffuse populations.
-These issues manifest themselves in the high quenched fractions of UDGs.
-As seen in Figure \ref{fig:mass_size}, the UDG sample includes a number of galaxies below the $1.5\sigma$ mass-size line, and these galaxies are mostly quenched (having zero or negative $\Delta(\mathrm{Quench})$).
-In order to help understand this phenomenon, we plot constant surface brightness lines of $\sbeff=25.0\ \sbunit$ for two different colors $g-i=0.4$ (blue solid line) and $g-i=0.8$ (red solid line) on the mass-size plane.
-For our redshift range, the cosmological dimming effect is negligible and the surface brightness is a constant with distance.
-For a given size and surface brightness (e.g., $\sbeff=25.0\ \sbunit$), redder galaxies have the same absolute magnitude as blue galaxies, but have higher stellar mass because they have higher mass-to-light ratio than blue galaxies.
-As a result, the UDG sample includes more red galaxies than blue ones due to the color-independent surface brightness cut at $\sbeff=25.0\ \sbunit$, and thus give rise to a high quenched fraction as we see in Figure \ref{fig:qfrac}.
-It is the definition of UDG that makes the quenched fraction high.
-
+In Figure \ref{fig:mass_size}, we find that combining a hard physical size cut with a surface brightness cut carves out an interesting region of the mass-size plane that is complicated in two ways.
+On the one hand, there are many galaxies classified as UDGs that are not size outliers at $M_\star \sim 10^{7.5}\ M_\odot$ (highlighted as red stars in Fig.
+\ref{fig:mass_size}).
+On the other hand, the hard surface brightness cut corresponds to very different surface mass density between red and blue galaxies, making it hard to directly compare red and blue UDGs since they occupy different regions on the mass-size plane.
+For a given stellar mass and size (e.g., at $M_\star \sim 10^{7.5}\ M_\odot$), the hard surface brightness cut in the UDG definition preferentially removes blue galaxies because their surface brightnesses are higher and their $M_\star/L$ are lower.
+Thus, red UDGs are over-represented.
+If one calculates the quenched fraction of UDGs as a function of stellar mass, it will be biased high because of the constant surface brightness cut.
+
+It is worth emphasizing that the concept of UDG was originally proposed in a cluster context where UDGs are mostly red and quenched \citep[e.g.,][]{vanDokkum2015} and the color-$M_\star/L$ effect does not matter much.
+However, UDGs are not all red and blue UDGs are also found in less dense environments.
+Therefore, the concept of UDG might not be optimal for systematic studies of diffuse dwarf galaxies with a range of colors in different environments.
+A more physically-motivated definition for mass-size outliers is needed.
+
+% These issues manifest themselves in the high quenched fractions of UDGs. 
 % In Section \ref{sec:sample_construction}, we have already argued that the hard size cut in UDG definition does not map clearly onto the mass-size relation, and we propose identifying UPGs as outliers in the mass-size plane.
@@
 We start from Figure \ref{fig:mass_size}, where we show UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ indicating how much a galaxy has been quenched (\S \ref{sec:quench}).
-
-It is worth emphasizing that the concept of UDG was originally proposed in a cluster context where UDGs are mostly red and quenched \citep[e.g.,][]{vanDokkum2015} and the color-$M_\star/L$ effect does not matter that much.
-However, bluer UDGs are found in less dense environments.
-For a given stellar mass, the hard surface brightness cut in UDG definition removes blue galaxies because their surface brightnesses are higher but their $M_\star/L$ are lower than red ones.
-Therefore, the concept of UDG might not be optimal to study the mass-size outliers with different colors in different environments.
 % We note that the color-$M_\star/L$ relation are only invoked when converting the absolute magnitude to stellar mass.
@@
 
-Our selection of UPGs is done directly based on the mass-size relation and thus alleviates the issues of UDG.
+The concept of ultra-puffy galaxy is defined based on the average mass-size relation and thus alleviates some of the issues in the UDG definition.
 They are defined to be $1.5\sigma$ above the average mass-size relation in the dwarf galaxy regime.
 The specific value above the average mass-size relation can vary to probe different parts of the size distribution.
-We further advocate studying the UPG population in both observations and simulations to explore different ``puffiness'' of UPGs (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).
-
-However, in order to construct a UPG sample, one needs to know the distance, color, a color-$M_\star/L$ relation to convert observed magnitudes to stellar mass, and a mass-size relation and its scatter.
+We advocate studying the UPG population in both observations and simulations to explore samples with different ``puffiness'' (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).
+
+However, in order to construct a UPG sample, one needs to know the distance, the color, a color-$M_\star/L$ relation to convert observed magnitudes to stellar mass, and a mass-size relation and its scatter.
 None of these are easy to obtain and free from systematic errors.
+Both size and stellar mass could have large uncertainties in the LSB regime.
+One also needs to apply a surface brightness cut (such as $\sbeff > 23.0\ \sbunit$ in this work) to make sure the UPG sample is not contaminated by disk galaxies with high surface brightness due to the bulges.
 On the one hand, reliable mass-size relation and its scatter are not available for all mass ranges.
@@
 9 in \citet{ELVES-I} shows the residual in $\log(r_e)$ after fitting the mass-size relation, where the distribution of residuals is roughly Gaussian but skewed toward the large-size end.
-With enough statistics in the future, one might be able to characterize the shape of the large-size tail and define UPGs based on the percentiles of the size distribution.
+With enough statistics in the future, one might be able to characterize the shape of the large-size tail and define UPGs based on the percentiles of the size distribution \citep{Greene2022}.
 However, there are also other size definitions which help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Mowla2019,Trujillo2020,Chamba2022} and can further benefit construct UPG samples.
@@
 This method also alleviates the artifact introduced by color-$M_\star/L$ relation on the mass-size plane.
-We defer such studies to future works.
+We defer exploration of this definition to future works.
 
 \section{Summary}\label{sec:summary}
-In this work, we present a comprehensive study for mass-size outliers around MW analogs at $0.01 < z < 0.04$.
+In this work, we perform a search for low surface brightness galaxies in HSC PDR2 data and construct samples for mass-size outliers around MW analogs at $0.01 < z < 0.04$.
 Beside the ultra-diffuse galaxies, we propose studying ``ultra-puffy galaxies'' which is defined to be $1.5\sigma$ above the average mass-size relation.
 We conduct statistical analysis for mass-size outliers and argue that UPGs better represent the large-size tail of the dwarf galaxy population.
-Surprisingly, we find that UPGs have similar quenched fraction as the bulk of MW satellites.
 We summarize our main findings and prospects below.
@@
 \begin{enumerate}
-
-% \begin{itemize}
     \item Using the HSC PDR2 data ($\sim 300\ \mathrm{deg}^{2}$), we conduct a systematic search for LSBGs using the method in \citet{Greco2018} complemented by our new deblending and modeling methods.
@@
 The completeness of the search is also derived by injecting mock galaxies.
-Our LSBG search achieves high completeness among other searches and demonstrate the power of HSC data on LSB sciences.
-
-    \item By matching LSBGs with MW analogs in NSA catalog, we construct samples of mass-size outliers including UDGs and UPGs.
+Our LSBG search achieves high completeness compared with other searches and demonstrates the power of HSC data for LSB sciences.
+
+    \item By matching LSBGs with MW analogs in the NSA catalog, we construct samples of mass-size outliers including UDGs and UPGs.
 We display their distributions on the size-surface brightness plane (Figure \ref{fig:udg_upg_re_mu}) and the mass-size plane (Figure \ref{fig:mass_size}).
-The UPG sample contains more bluer and higher surface brightness galaxies than the UDG sample.
-Instead, the UDG sample includes many red galaxies below $1.5\sigma$ from the average mass-size relation.
+The UPG sample contains more blue and higher surface brightness galaxies than the UDG sample.
+In contrast, the UDG sample includes many red galaxies below $1.5\sigma$ from the average mass-size relation.
 
@@
 Combining data from studies in denser environments, we find that the UDG abundance follows a sublinear power law with the host halo mass.
-    \item We find the size distribution of UDGs follows a power law $n\propto r_e^{-1.60\pm0.21}$ which is shallower than the UDG size distribution in larger groups and clusters \citep{vdBurg2016,vdBurg2017}.
-We do not find significant dependence of size distribution on host stellar mass or the distance to host.
-The UPG size follows a unimodal distribution peaks at $\sim 2.5$ kpc.
+The power law slope agrees with other studies.
+We caution that many other studies do not correct for completeness which could bias the results.
+
+    \item For a MW analog, on average, about 15\% of its satellites are UDGs and about 10\% of its satellites are UPGs.
+The UDG and UPG fractions are slightly higher than those in ELVES and NGVS, which suffer from small number statistics due to their sample sizes.
 
@@
 
-This study on mass-size outliers only explores a small subset of LSBG candidates detected in HSC PDR2.
+This paper presents the UDG and UPG sample and explores their abundances.
+In our Paper II (to be submitted), we study their size and spatial distribution and their star formation status.
+This study is focused on a small subset of LSBG candidates matched with MW analogs.
 In future works, we would like to exploit the full sample to study interesting topics including redshift distributions, nucleation fractions, intrinsic shapes of LSBGs.
 We will also explore machine learning techniques to help us classify LSBGs and estimate structural parameters.
-With the upcoming Vera Rubin Observatory Legacy Survey of Space and Time \citep[LSST, ][]{lsst2009,LSST2019}, we will be able to study the LSBG population with much greater statistics and gain new insights on the formation and evolution of mass-size outliers.
-
-\jiaxuan{Mention our paper II (to be submitted)}
+With the upcoming LSST \citep{lsst2009,LSST2019}, we will be able to study the LSBG population with much greater statistics and gain new insights into the formation and evolution of mass-size outliers.
 
@@
 Thanks to the global sky subtraction in HSC PDR2, LSB features are well conserved after subtracting the sky and the sky noise level varies less.
-Therefore, it makes more sense to set the thresholds based on the characteristic surface brightness instead of a certain sigma value above the sky background.
-In this work, we set the high threshold to $\mu_{\rm high} = 22\ \sbunit$ to capture all bright sources above this surface brightness, and the low threshold to $\mu_{\rm low} = 24.5\ \sbunit$ to capture the associated diffuse lights.
-Unlike in \citetalias{Greco2018}, we find it not necessary to smooth the image prior to the thresholding.
+We therefore set the thresholds based on the characteristic surface brightness instead of a certain sigma value above the sky background.
+In this work, we set the high threshold to $\mu_{\rm high} = 22\ \sbunit$ to capture all bright sources above this surface brightness, and the low threshold to $\mu_{\rm low} = 24.5\ \sbunit$ to capture the associated diffuse light.
+Unlike in \citetalias{Greco2018}, we find it unnecessary to smooth the image prior to the thresholding based on our completeness tests (see \S \ref{sec:comp_meas},\S\ref{ap:comp_meas_unc}).
 
@@
 This step significantly improves the purity of LSBG search.
-The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by the completeness tests (see \S \ref{sec:comp_meas},\S\ref{ap:comp_meas_unc}).
+The values of ($\mu_{\rm high},\ \mu_{\rm low},\ r_{\rm min})$ are chosen by trial and error, but guided by the completeness tests.
 % This step effectively cleans out objects and features that hinder the detection of LSBGs.
@@
 First, in vanilla \code{scarlet}, objects can be modeled with different types of models\footnote{\url{https://pmelchior.github.io/scarlet/1-concepts.html\#Source}} including point source, single-extended source, multi-extended source, compact source, and flat-sky source.
-The point source has a morphology image simply be the normalized PSF.
+The morphology image of a point source is simply the normalized PSF model.
 The single-extended source has a morphology image that follows positivity and monotonicity constraints.
-The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture color gradient.
+The multi-extended source is a combination of two or more co-centered single-extended sources, making it possible to model galaxies with more complex structures and capture any color gradients.
 The compact source is a single-extended source initialized using the morphology image of a point-source, which encourages the model to be compact, but still allows the morphology image to be extended.
@@
 For modeling the LSBG candidates, we use an extended source model with two components such that the model is able to capture the galaxy structure and color gradient.
-The target source is initialized as follows.
+The target source is initialized in the following way.
 We convolve the detection image with a circular Gaussian kernel with $\sigma=1.5$ pixels to boost the contrast between the signal and the sky noise.
@@
 Consequently, the size of the bounding box depends on the smoothing kernel and the threshold.
-We choose the above values by trial and error such that the box is not so large as to include many irrelevant peaks, but not so small as to lose the LSB outskirts of the target galaxy.
+We choose the above values by trial and error such that the box is not so large as to include many irrelevant peaks, but not so small as to lose a significant fraction of LSB outskirts of the target galaxy.
 
@@
 It takes longer when the target galaxy has large angular size since more peaks are modeled.
-We note that \code{scarlet} optimizes the model instead of deriving the full posteriors, thus a good initialization becomes especially important for fast convergence.
+We note that \code{scarlet} only find the maximum likelihood estimation of the model instead of deriving the full posteriors, thus a good initialization becomes especially important for fast convergence.
 

### 2022-10-14 paper1.tex
Updates from Overleaf

@@
 
-\title{Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers in the Satellites of Milky Way Analogs}
+\title{Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers Among the Satellites of Milky Way Analogs}
 
@@
 \section{Introduction} \label{sec:intro}
-In a variety of galaxies in the Universe, an interesting subset of galaxies with low surface brightness and large physical size have been identified \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
+In a variety of galaxies in the Universe, there is an interesting subset of galaxies with low surface brightness and large physical size \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
 Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
 There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
-UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus have very large sizes for their stellar mass compared to normal dwarf galaxies.
-Therefore, a central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation?
+UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus UDGs are outliers in size and surface brightness for their stellar mass compared to normal dwarf galaxies.
+A central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation of dwarf galaxies?
 % Therefore, a central question about mass-size outliers including UDGs is what physical mechanisms are responsible for the formation and quenching of these large diffuse galaxies.
@@
 With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs in the Local Volume and nearby Universe.
-The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at 20-40 Mpc \citep{SAGA-I,SAGA-II}.
+The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at 20--40 Mpc \citep{SAGA-I,SAGA-II}.
 The Exploration of Local VolumE Satellites (ELVES,  \citealt{ELVES-I,ELVES-II,CarlstenELVES2022}) survey uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts.
-Having these MW satellites as a reference frame, we can contrast them with the large diffuse galaxies in the same environment to understand the formation of diffuse galaxies.
+Having these MW satellites as a reference frame, we can contrast them with the mass-size outliers in the same environment to understand the formation of large diffuse galaxies.
 However, there are only $\sim 40$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022,Karunakaran2022b}.
-A larger sample of mass-size outliers (including UDGs) associated with MW-like hosts is needed to conduct such a comparison between the mass-size outliers and the normal satellites.
-
-The goal of this paper is to find and study large diffuse galaxies in the context of the satellite systems of MW analogs.
+Therefore, a larger sample of mass-size outliers associated with MW-like hosts is needed to conduct such a comparison between the mass-size outliers and the normal satellites.
+
+The goal of this paper is to find and study large diffuse satellite galaxies in the context of MW analogs.
 Leveraging the depth and wide sky coverage of Hyper-Suprime Cam (HSC) Subaru Strategic Program imaging data, we perform a search for LSBGs using novel methods in detection, false positive identification, and modeling.
 We further build a large sample of mass-size outliers that are likely satellites of MW-mass hosts in the nearby Universe.
-We propose a new definition for mass-size outliers, dubbed ``ultra-puffy galaxies'' (UPGs), based on the observed mass-size relation in the Local Volume using ELVES sample.
+We propose a new definition for mass-size outliers, dubbed ``\textit{ultra-puffy galaxies}'' (UPGs), based on the observed mass-size relation in the Local Volume using ELVES sample.
 This concept is less affected by the galaxy color and provides a robust avenue to study the mass-size outlier population.
-We examine the abundance of mass-size outliers in MW analogs and compare with their abundances in other environments.
-Our results seek to shed light on the role of environment on the formation of large diffuse galaxies.
+We calculate the abundance of mass-size outliers in MW analogs and compare with their abundances in other environments.
+Our results seek to shed light on the role of environment on the formation of large diffuse dwarf galaxies.
 %By comparing mass-size outliers with normal satellites and simulations, our results seek to shed light on the formation and evolution of the large diffuse galaxies.
@@
 Section \ref{sec:data} describes the data used in this work.
-In Section \ref{sec:lsbg_search}, we describe the LSBG search in the HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), modeling (\S \ref{sec:modeling}), and completeness and uncertainty (\S\ref{sec:comp_meas}).
+In Section \ref{sec:lsbg_search}, we describe the LSBG search in HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), modeling (\S \ref{sec:modeling}), and completeness and uncertainty (\S\ref{sec:comp_meas}).
 In Section \ref{sec:sample_construction}, we propose a new definition for large and diffuse galaxies (the UPGs) and present our UDG and UPG samples.
-In Section \ref{sec:results}, we show statistical analysis for UDGs and UPGs including their distribution on the mass-size plane and their abundances (\S \ref{sec:n_udg}).
-We further argue why we need to move beyond UDG and adopt UPG definition in Section \ref{sec:discussion}.
+In Section \ref{sec:results}, we compare the UDGs and UPGs on the mass-size plane.
+We calculate their abundances and compare with literature (\S \ref{sec:n_udg}).
+Based on these results, we further argue why we need to move beyond UDG and adopt the UPG definition in Section \ref{sec:discussion}.
 Section \ref{sec:summary} presents a summary of this work and prospects for the future.
-In a companion paper (Li et al., to be submitted), we discuss the size distributions, spatial distributions, and star formation quenching of UDGs and UPGs.
-
-In this work, we refer to LSBGs as objects selected purely by surface brightness, whereas mass-size outliers (including UDGs and UPGs) are selected based on physical size, surface brightness, or stellar mass.
+In a companion paper (Li et al., to be submitted), we discuss the size distributions, spatial distributions, and quenching of UDGs and UPGs.
+
+In this work, we refer to LSBGs as objects selected purely by surface brightness without knowing distance information.
+We refer to mass-size outliers (including UDGs and UPGs) as galaxies with large physical sizes compared to normal dwarf galaxies.
 We adopt a flat $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$.

### 2022-10-15 paper1.tex
cannot compile

@@
 
-\author[0000-0003-4970-2874]{Johnny Greco}
+\author[0000-0003-4970-2874]{Johnny P. Greco}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
@@
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-\author[0000-0002-2991-9251]{Kirsten Casey}
+\author[0000-0002-2991-9]{Kirsten Casey}
 \affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
@@
 For the LSBGs matched with MW analogs, we run the deblending step to exclude false positives (\S\ref{sec:deblending}) and then run Spergel modeling to measure the properties of LSBGs (\S\ref{sec:modeling}).
-In the end, we construct the samples of mass-size outliers in the satellites of MW analogs.
+In the end, we construct the samples of mass-size outliers among the satellites of MW analogs.
 
@@
 The properties of the Milky Way itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016} and the definitions of MW analogs are different among different studies.
-In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$~mag, which is derived using abundance matching by assuming a simple galaxy-halo connection model (see Fig.
-2 in \citealt{SAGA-I}).
-This luminosity range approximately corresponds to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$.
-SAGA also requires that the MW analogs be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20--40 Mpc).
+In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$~mag (corresponding to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$) and redshift $0.005 < z < 0.01$ (20--40 Mpc).
+SAGA also requires that the MW analogs be in isolation (without nearby bright galaxies).
 In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$~mag ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA.
@@
 We also remove duplicated objects.
-In the end, we have 2,510 LSBG candidates as our final LSBG sample.
+In the end, we have 2,510 LSBG candidates associated with 689 MW analogs as our final LSBG sample.
 We note that these LSBGs are matched to MW hosts in projection but do not have direct distance measurements.
@@
 Although UDGs are large in size, the constant size cut does not account for the fact that the galaxy size is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
-
-A more intuitive definition for diffuse and puffy dwarf galaxies (i.e., mass-size outliers) should be based on a mass-size relation and its scatter.
+For example, a galaxy with $r_e = 1.5$ kpc is very extended if its stellar mass is $10^7\ M_\odot$, but is normal-sized if its stellar mass is $10^{8.5}\ M_\odot$.
+Thus, a more intuitive definition for diffuse and puffy dwarf galaxies (i.e., mass-size outliers) should be based on a mass-size relation and its scatter.
 Following this thread, we propose a new definition for mass-size outliers dubbed as \textit{ultra-puffy galaxies} (UPGs).
@@
 This gives us a chance to define a subset of dwarf galaxies that are size-outliers with respect to the average mass-size relation.
-It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021,Benavides2022}.
+It is worth noting that a definition based on the mass-size relation was already used in simulation studies where the absolute sizes were uniformly too large such that size outliers can only be selected relative to the simulated mass-size relation \citep[e.g.,][]{Benavides2021,Benavides2022}.
 
@@
 One can certainly select $>2\sigma$ or $>3\sigma$ UPGs if a larger LSBG sample is available.
-The UPGs are not absolutely large in size or absolutely faint in surface brightness, but they are outliers in size for their stellar masses.
+The UPGs are not absolutely large in size or absolutely faint in surface brightness, but they are outliers in size for their stellar masses\footnote{A UPG with $M_\star = 10^7\ M_\odot$ has a size larger than 1.2 kpc and surface brightness fainter than $\sbeff > 25.5\ \sbunit$ for $g-i=0.4$ and $\sbeff > 26.8\ \sbunit$ for $g-i=0.8$.
+A UPG with $M_\star = 10^{8.5}\ M_\odot$ has a size larger than 2.7 kpc and surface brightness fainter than $\sbeff > 23.7\ \sbunit$ for $g-i=0.4$ and $\sbeff > 25.0\ \sbunit$ for $g-i=0.8$.}.
 The definition of UPG based on the observed mass-size relation is more physically-motivated, and better allows us to study size outliers at a given stellar mass.
@@
 
-We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2 regardless of whether containing MW analogs\footnote{$345\ \deg < \rm{R.A.} < 351\ \deg$, $-1.5\ \deg < \rm{Dec} < 2.5\ \deg$, which is not dominated by Galactic cirrus and stars.}.
+We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2 regardless of whether containing MW analogs\footnote{$345\ \deg < \rm{R.A.} < 351\ \deg$, $-1.5\ \deg < \rm{Dec} < 2.5\ \deg$, which is not dominated by Galactic cirrus and stars.
+Such a patch of sky with 24 deg$^2$ is already enough for us to derive a background contamination fraction with small Poisson error.}.
 Then we perform the same deblending and modeling steps for the 2,707 LSBGs detected in this region.
@@
 \section{Results}\label{sec:results}
-In this section, we present a statistical analysis for mass-size outliers in the satellites of MW analogs at $0.01 < z < 0.04$.
+In this section, we present a statistical analysis for mass-size outliers among the satellites of MW analogs at $0.01 < z < 0.04$.
 We first compare the distributions of UDGs and UPGs on the size-surface brightness plane and mass-size plane to gain intuition on the differences between UDG and UPG definitions.
@@
 Since there is no hard surface brightness cut for UPGs, the UPG sample includes many blue galaxies with brighter surface brightness ($23 \lesssim \sbeff < 25\ \sbunit$).
-Due to the surface brightness cut ($\sbeff > 23\ \sbunit$) in the deblending step, there is little chance for a LSB disk galaxy with bright bulge to scatter in the UPG sample.
-The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26\ \sbunit$ because their stellar masses are too high for their sizes to make them being size-outliers.
+For blue UPGs (shown as blue dots), the correlation between $\sbeff$ and $r_e$ is merely the fact that blue UPGs pile up around the $1.5\sigma$ line above the mass-size relation.
+
+Due to the surface brightness cut ($\sbeff > 23.0\ \sbunit$) in the deblending step, there is little chance for a LSB disk galaxy with bright bulge to scatter in the UPG sample.
+The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26\ \sbunit$ because their stellar masses are high but their sizes are too small to be mass-size outliers.
 
@@
 
-\jiaxuan{Discuss whether UPGs are LSB disks?}
-
-% discriminative for blue and red galaxies.
-
 % As we will introduce in Section \ref{sec:quench}, we use a color cut $(g-i)_{Q}$ to separate galaxies with active star formation from quiescent ones.
@@
 We define the UDG (UPG) abundance as the average number of UDGs (UPGs) per host galaxy.
+We searched 901 MW analogs.
 In our UDG sample, there are 412 UDGs associated with 258 hosts.
@@
 A systematic and careful comparison on UDG (UPG) fraction in different environments is needed in the future.
+
+We note that ELVES probes less massive dwarfs than our search.
 

### 2022-10-22 paper1.tex
fixed bug
Updates from Overleaf
a new deblending figure and new text

@@
 
-%% The default is a single spaced, 10 point font, single spaced article.
-%% There are 5 other style options available via an optional argument. They
-%% can be invoked like this:
-%%
-%% \documentclass[arguments]{aastex631}
-%% 
-%% where the layout options are:
-%%
-%%  twocolumn   : two text columns, 10 point font, single spaced article.
-%%                This is the most compact and represent the final published
-%%                derived PDF copy of the accepted manuscript from the publisher
-%%  manuscript  : one text column, 12 point font, double spaced article.
-%%  preprint    : one text column, 12 point font, single spaced article.  
-%%  preprint2   : two text columns, 12 point font, single spaced article.
-%%  modern      : a stylish, single text column, 12 point font, article with
-%% 		  wider left and right margins. This uses the Daniel
-%% 		  Foreman-Mackey and David Hogg design.
-%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
-%%                but now that abstracts are required this is obsolete for
-%%                AAS Journals. Authors might need it for other reasons. DO NOT
-%%                use \begin{abstract} and \end{abstract} with this style.
-%%
-%% Note that you can submit to the AAS Journals in any of these 6 styles.
-%%
-%% There are other optional arguments one can invoke to allow other stylistic
-%% actions. The available options are:
-%%
-%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
-%%   tighten      : Makes baselineskip slightly smaller, only works with 
-%%                  the twocolumn substyle.
-%%   times        : uses times font instead of the default
-%%   linenumbers  : turn on lineno package.
-%%   trackchanges : required to see the revision mark up and print its output
-%%   longauthor   : Do not use the more compressed footnote style (default) for 
-%%                  the author/collaboration/affiliations. Instead print all
-%%                  affiliation information after each name. Creates a much 
-%%                  longer author list but may be desirable for short 
-%%                  author papers.
-%% twocolappendix : make 2 column appendix.
-%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
-%%                  for dual anonymous review.
-%%
-%% these can be used in any combination, e.g.
-%%
-%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
-%%
-%% AASTeX v6.* now includes \hyperref support. While we have built in specific
-%% defaults into the classfile you can manually override them with the
-%% \hypersetup command. For example,
-%%
-%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
-%%
-%% will change the color of the internal links to red, the links to the
-%% bibliography to green, the file links to cyan, and the external links to
-%% magenta. Additional information on \hyperref options can be found here:
-%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
-%%
-%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
-%% to improve the accessibility of the compiled pdf file.
-%%
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
 %%
@@
 
-\shorttitle{Mass-size outliers in MW satellites}
+\shorttitle{Mass-size outliers among MW satellites}
 \shortauthors{Li et al.}
-%%
-%% You can add a light gray and diagonal water-mark to the first page 
-%% with this command:
-%% \watermark{text}
-%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
-%% long you can control the water-mark size with:
-%% \setwatermarkfontsize{dimension}
-%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
 %%
@@
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-\author[0000-0002-2991-9]{Kirsten Casey}
+\author[0000-0002-2991-9251]{Kirsten Casey}
 \affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
@@
 \affiliation{SNU Astronomy Research Center, Seoul National University, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Republic of Korea}
-\author{Lauren MacArthur}
+
+\author{Lauren A. MacArthur}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-
-%% Note that the \and command from previous versions of AASTeX is now
-%% depreciated in this version as it is no longer necessary. AASTeX 
-%% automatically takes care of all commas and "and"s between authors names.
-
-%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
-%% provide the collaboration status of a group of authors. These commands 
-%% can be used either before or after the list of corresponding authors. The
-%% argument for \collaboration is the collaboration identifier. Authors are
-%% encouraged to surround collaboration identifiers with ()s. The 
-%% \nocollaboration command takes no argument and exists to indicate that
-%% the nearby authors are not part of surrounding collaborations.
 
@@
 Large diffuse galaxies are hard to find, but understanding the environments where they live and their numbers, and ultimately their origins, is of intense interest and important for galaxy formation and evolution.
-Using the Hyper Suprime-Cam data, we perform a systematic search for low surface-brightness galaxies and present novel and effective methods for detecting and modeling them.
+Using Subaru's Hyper Suprime-Cam Strategic Survey Program data, we perform a systematic search for low surface-brightness galaxies and present novel and effective methods for detecting and modeling them.
 As a case study, we build a statistical sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$).
-These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, better represents the tail of satellite size distribution.
+These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represents the tail of the satellite size distribution.
 We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is comparable to the observed abundance at this halo mass in the Local Volume.
 We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.76\pm0.04$ per host.
-We compare with literature results including UDG searches in clusters and massive groups.
-The UDG abundance scales with the host halo mass following a sublinear power law.
-We argue that our definition for ultra-puffy galaxies, which is based on the mass-size relation, is more physically-motivated and objective than the common definition of ultra-diffuse galaxies, which depends on a surface brightness cut and thus yields different surface mass density cuts for quenched and star-forming galaxies.
+With literature results, we confirm that the UDG abundance scales with the host halo mass following a sublinear power law.
+We argue that our definition for ultra-puffy galaxies, which is based on the mass-size relation, is more physically-motivated than the common definition of ultra-diffuse galaxies, which depends on an arbitrary surface brightness cut and thus yields different surface mass density cuts for quenched and star-forming galaxies.
 \end{abstract}
@@
 A central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation of dwarf galaxies?
-% Therefore, a central question about mass-size outliers including UDGs is what physical mechanisms are responsible for the formation and quenching of these large diffuse galaxies.
 
@@
 It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness or larger size.
-A nice way to to answer these questions is to compare these mass-size outliers with ``normal'' low mass galaxies for which we have a better understanding.
+A nice way to to answer these questions is to compare these mass-size outliers with ``normal'' low mass galaxies which have been studied extensively.
 
 Our best understanding of the low mass galaxy regime comes from the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}.
-With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs in the Local Volume and nearby Universe.
+With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs (typically defined as galaxies having similar stellar mass or halo mass to MW) in the Local Volume and nearby Universe.
 The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at 20--40 Mpc \citep{SAGA-I,SAGA-II}.
@@
 The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection).
-HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Legacy Survey of Space and Time (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.
+HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Vera Rubin Observatory Legacy Survey of Space and Time (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.
 
@@
 This version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions.
-In this paper, we use the stellar mass derived from elliptical Petrosian photometry using \code{kcorrect v4\_2} \citep{Blanton2007}.
-The redshifts of galaxies in NSA come from several spectroscopic surveys, \ion{H}{1} gas surveys, or direct distance measurements.
+In this paper, we use the stellar masses derived from the elliptical Petrosian photometry using \code{kcorrect v4\_2} \citep{Blanton2007}.
+The redshifts of the galaxies in NSA come from several spectroscopic surveys, \ion{H}{1} gas surveys, or direct distance measurements.
 
@@
 
-Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies (LSBGs) in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}.
-The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section.
-We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for UDG and UPG sample construction.
+Continuing the work of \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies (LSBGs) in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}.
+The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the search completeness and purity by adding several new steps, which are highlighted in this section.
+We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for the UDG and UPG sample construction.
 
@@
 \end{enumerate}
-The number of objects remained after each step is shown in Table \ref{tab:steps_flow}.
-Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} and deblending and modeling code \code{kuaizi}\footnote{\url{https://github.com/AstroJacobLi/kuaizi}} are open-sourced and available online.
+The number of objects remaining after each step is shown in Table \ref{tab:steps_flow}.
+Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} and the deblending and modeling code \code{kuaizi}\footnote{\url{https://github.com/AstroJacobLi/kuaizi}} are open-sourced and available online.
 
@@
 \citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs.
-We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction for LSB studies compared to previous data releases.
-We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate PDR2 data.
+We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has a sky subtraction better suited for LSB studies compared to previous data releases.
+We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate the PDR2 data.
 These updates are guided by both our understanding of PDR2 data and completeness tests using mock galaxies.
-We summarize the main steps of LSBG search method here, and refer the interested readers to \citetalias{Greco2018} and Appendix \ref{ap:detection} for more details.
+We summarize the main steps of the LSBG search method here, and refer the interested reader to \citetalias{Greco2018} and Appendix \ref{ap:detection} for more details.
 % In the following, we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity.
@@
 Bright objects and their diffuse light are identified using surface brightness thresholding.
-Then we run a detection using \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} to remove small compact sources and noisy peaks and also replace their footprints with sky noise.
+Then we run a detection using \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} to remove small compact sources and noisy peaks and replace their footprints with sky noise.
 We use \code{SourceExtractor} to detect sources on the ``cleaned'' images with a low detection threshold.
@@
 The objects covered by the gray shades are masked during fitting.
-The remaining columns show the initial model, optimized models (PSF convolved), residual image, and the optimized model of the target galaxy only.
+The remaining columns show the initial model, the optimized model (PSF convolved), the residual image, and the optimized model of the target galaxy only.
 	}
@@
 
-We use vanilla \code{scarlet} to model the LSBG candidate and extract structural and morphological parameters from the \code{scarlet} model, which are further used to exclude false positives from our LSBG sample.
-In the following subsections, we briefly describe how we detect peaks on the image, initialize and optimize \code{scarlet} models.
-We refer the readers to Appendix \ref{ap:deblending} for more detailed descriptions.
+We use vanilla \code{scarlet} to model the LSBG candidate and the structural and morphological parameters are then used to exclude false positives from our LSBG sample.
+In the following subsections, we briefly describe how we detect peaks on the image to initialize and optimize \code{scarlet} models.
+We refer the readers to Appendix \ref{ap:deblending} for a more detailed description.
 
@@
 For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact.
-The reason why it passes our initial selection is that the galaxy outskirts are shredded by \code{SourceExtractor} and happen to have a large size and the right color.
+It passes our initial selection because the galaxy outskirts are shredded by \code{SourceExtractor} and happen to have a large size and similar color to our LSB galaxies.
 But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.
-A rubric based on the \code{scarlet} model is therefore needed to help us exclude the false positives.
+A rubric based on the \code{scarlet} model is therefore needed to help us identify and exclude the false positives.
 
@@
 
-\begin{figure*}
-	\vbox{
-		\centering
-		\includegraphics[width=1.0\linewidth]{deblending_cuts.pdf}
-	}
-	\caption{The distribution of LSBG candidates from our initial sample in the parameter space as measured from the \code{scarlet} models.
-We visually inspected 5,000 LSBG candidates and labeled them as \code{candy} (LSBGs with typically dwarf galaxy features), \code{galaxy} (higher surface brightness galaxies or galaxies with spiral galaxy features), and \code{junk} (false positives).
-We propose a selection based on size, color, surface brightness and morphology (dashed boxes) to effectively remove false positives but still achieves a high completeness.
+% \begin{figure*}
+% 	\vbox{
+% 		\centering
+% 		\includegraphics[width=1.0\linewidth]{deblending_cuts.pdf}
+% 	}
+% 	\caption{The distribution of \code{scarlet} measurements for the LSBG candidates from our initial sample.
+We visually inspected 5,000 LSBG candidates and labeled them as \code{candy} (LSBGs with dwarf galaxy features), \code{galaxy} (higher surface brightness galaxies or galaxies with spiral galaxy features), and \code{junk} (false positives).
+We propose a selection based on size, color, surface brightness and morphology (dashed boxes) to effectively remove false positives but still achieve a high completeness.
 After such cuts (bottom panels), 97\% of false positives and 76\% of non-LSB galaxies are removed according to our visual inspection results.
-	}
-	\label{fig:deblending_cuts}
-\end{figure*}
-
-After running vanilla \code{scarlet} for LSBG candidates, the target object has been successfully deblended from nearby sources.
+% 	}
+% 	\label{fig:deblending_cuts}
+% \end{figure*}
+
+After running vanilla \code{scarlet} for LSBG candidates, the target object is successfully deblended from nearby sources.
 Unlike other parametric modeling methods, the non-parametric \code{scarlet} model is flexible enough to adequately represent galaxies with complex structures.
@@
 We measure the morphological and structural parameters in $g$-band.
-%The morphological and structural parameters are the same in different bands by construction in the \code{scarlet} model.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{deblending_cuts_morph.pdf}
+    \caption{The distribution of \code{scarlet} morphological measurements for the LSBG candidates from our initial sample.
+The sample after the color-size-surface brightness cuts is shown in the top panels.
+We further remove false positives (\code{junk}, highlighted in red) by selecting their morphological parameters (dashed boxes).
+Morphology cuts (bottom panels) removes another 82\% of \code{junk}.
+In total, 98\% of false positives are removed in the deblending step.
+	}
+	\label{fig:deblending_cuts}
+\end{figure}
 
 To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the classification results to help construct the metrics.
-To be specific, we randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ from the NSA catalog (see \S\ref{sec:match} for details).
+To be specific, we randomly select 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ from the NSA catalog (see \S\ref{sec:match} for details).
 We run vanilla \code{scarlet} for all of them and measure morphological parameters as described above.
 Then we do visual inspection of the $griz$ color-composite images with 0.5 arcmin on a side.
-Objects are classified into three types: LSB galaxies with typical dwarf galaxy features (dubbed \code{candy}), high surface brightness galaxies, or galaxies with spiral galaxy features (\code{galaxy}), and false positives including tidal streams, galaxy outskirts blends, and other artifacts (\code{junk}).
-The difference between \code{candy} and \code{galaxy} can be quite ambiguous.
-
-The visual inspection was done by coauthors JEG, JG, SH, RB, KC, AG, and EKF.
+False positives, including tidal streams, galaxy outskirts blends, and other artifacts (dubbed \code{junk}), are identified during the visual inspection by coauthors JEG, JG, SH, RB, KC, AG, and EKF.
 Each object has been inspected by at least one person.
 In the end, we combine the votes from different people.
-An object is classified as \code{junk} if the number of votes as \code{junk} is larger than the number of votes as \code{candy} and \code{galaxy}.
-For objects that are not \code{junk}, if the number of votes as \code{candy} is greater than the votes as \code{galaxy}, we classify this object as \code{candy}.
-Everything else is classified as \code{galaxy}.
-In total, there are 1153 \code{candies}, 2150 \code{galaxies}, and 1697 \code{junk}.
-
-We use these visual inspection results to inform how to use the morphological and structural diagnostics.
-The distributions of \code{candy} (blue), \code{galaxy} (green), and \code{junk} (red) in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}.
-Although \code{junk} is scattered throughout the parameter space, a large fraction of the junk comprises small things with very red colors, very low surface brightness, large concentration and large asymmetry.
-Therefore, we come up with the following selection cuts to remove the false positives:
+An object is classified as \code{junk} if the number of votes as \code{junk} is larger than the number of votes as \code{non-junk}.
+In total, there are 1661 objects classified as \code{junk}.
+The visual inspection is summarized in Table \ref{tab:deblending_vis}.
+
+We first apply the following selection cuts to remove false positive and background galaxies.
+They are motivated based on the knowledge of the color distribution of LSBGs \citep[e.g.,][]{SAGA-I,Greco2018,Zaritsky2019,Tanoglidis2021} and survey completeness in size and surface brightness (\S\ref{sec:comp_meas}).
 \begin{itemize}
@@
     \item Size: \[1.8 \arcsec < r_e < 12 \arcsec\]
-    \item Surface brightness: \[\mu_0(g) > 22.5,\quad 23.0 < \mu_{\rm eff}(g) < 27.5,\]
+    \item Surface brightness: \[\mu_0(g) > 22.5,\quad 23.0 < \mu_{\rm eff}(g) < 27.5.\]
+\end{itemize}
+The color cuts here are more restrictive than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and high redshift galaxies.
+We not only remove objects with small sizes, but also exclude objects with large size and very low surface brightness because they are mostly \code{junk}.
+After such cuts, there are 200 \code{junk} and 1407 \code{non-junk} remaining.
+The color-size-surface brightness cuts removes 88\% of \code{junk} and 58\% of \code{non-junk}.
+We note that although we lose a lot of \code{non-junk} objects, most of them are small, red  objects which are not likely to be LSBGs of our interest.
+
+We further use these visual inspection results to inform how to use the morphological diagnostics.
+In the top panels of Figure \ref{fig:deblending_cuts}, we show the distributions of \code{junk} (red) and \code{non-junk} (green) in the parameter space spanned by four morphological parameters.
+There are still a significant amount of \code{junk} with high $M_{20}$, Gini coefficient, and asymmetry.
+Therefore, we add another set of selection cuts to further remove \code{junk}:
+\begin{itemize}
     \item Morphology: 
@@
 \end{itemize}
-These criteria (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove objects that are not likely to be LSBGs of interest.
-The color cuts here are more restrictive than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and background high redshift galaxies.
-We not only remove objects with small sizes, but also exclude objects with large size, very low surface brightness, and high concentration.
-This is because the scarlet models of some junk can be very concentrated in the center but also very extended.
 The slanted demarcation line on the Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to separate merging galaxies from normal galaxies.
-
-The bottom panels in Figure \ref{fig:deblending_cuts} show the objects after applying the above selections.
-With these cuts, 97\% of the false positives are removed, but the majority (70\%) of \code{candy} still remains.
-The \code{galaxy} subset also drops by 76\%.
-This empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample.
+The bottom panels in Figure \ref{fig:deblending_cuts} show the objects after applying the morphology selections, which remove another 82\% of \code{junk} while only remove 9\% of \code{non-junk}.
+Such morphology cuts (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove false positives that are not likely to be LSBGs of interest.
+
+In this way, we obtain an LSBG sample with high purity, where 98\% of the false positives are removed.
+Therefore, our empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample.
 Furthermore, the completeness of real LSBG detection remains high.
@@
 \ref{fig:completeness}).
-We emphasize that the vanilla \code{scarlet} modeling and non-parametric measurements are not designed to recover the intrinsic properties of the galaxies.
+We emphasize that the vanilla \code{scarlet} modeling and non-parametric measurements are not designed to measure the structural properties of the galaxies.
 They are used only as a diagnostic tool to remove false positives.
@@
 
-Many other works have been using machine learning (ML) algorithms to classify LSBG candidates and exclude spurious detection.
+\begin{deluxetable}{lccc}
+\tablecaption{The number of objects remained after each deblending cut}
+\tablewidth{6cm}
+\label{tab:deblending_vis}
+\tablehead{
+\colhead{Process} & \colhead{\# \code{junk}} &
+\colhead{\# \code{non-junk}} & \colhead{\# Total}
+}
+\startdata
+Visual inspection & 1661 & 3339 & 5000 \\
+Color-size-SB cuts & 200 & 1407 & 1607 \\
+Morphology cuts & 37 & 1278 & 1305\\
+% \hline
+% Removed fraction & 98\% & 62\% & 74\%
+\enddata
+\end{deluxetable}
+
+Many other works have used machine learning (ML) algorithms to classify LSBG candidates and exclude spurious detection.
 Among others, \citet{Tanoglidis2021} take the output catalog from \code{SourceExtractor} and use the Support Vector Machine algorithm to classify objects in their initial sample and reduce the number of objects that are visually inspected.
-\citet{Zaritsky2019,Zaritsky2021,Zaritsky2022} use convolutional neural networks to classify LSBGs into binary classes based on their images.
-These endeavors certainly help reduce the human labor on visually inspecting tens of thousands of objects.
-However, training such a supervised ML algorithm relies on the labeled data which should also sample the parameter space fairly evenly.
-Once labels are assigned (e.g., LSBG v.s.
-non-LSBG), there will be little way to change later.
-On the contrary, our cuts based on the measured properties can be tweaked to have higher completeness  (including more junk) or have higher purity (aggressive cuts) depending on the specific science goal.
-The visual inspection labels only guide us to design those metrics.
-This measurement-based method is more intuitive, reproducible, and transferable.
-We will also explore machine learning methods and compare with our deblending cuts in future works.
+\citet{Zaritsky2019,Zaritsky2021,Zaritsky2022} use convolutional neural networks to classify LSBGs into binary classes based on candidate images.
+These endeavors certainly help reduce the human labor of visually inspecting tens of thousands of objects.
+However, our measurement-based method is more intuitive, reproducible, and transferable compared with many ML methods.
+We will explore machine learning methods and compare with our deblending cuts in future work.
 Future work will also utilize information about Milky Way dust to exclude spurious detection on Galactic cirrus \citep[e.g.,][]{Zaritsky2021,Zaritsky2022}.
@@
 Although the vanilla \code{scarlet} modeling provides useful information to help us remove false positives, it does not necessarily give us reliable estimations on size, color, total magnitude, etc.
-In fact, the vanilla \code{scarlet} model systematically under-estimates the size and the total flux of LSB objects.
+In fact, the vanilla \code{scarlet} model systematically under-estimates the size and total flux of LSB objects.
 This is because the faint outskirts of LSBGs are typically not modeled well due to the non-parametric nature of vanilla \code{scarlet}.
 When doing parametric modeling such as \sersic{} fitting, we effectively apply radial averaging within elliptical annuli and boost the signal-to-noise ratio by binning pixels.
-In other words, pixels within the same isophotal annulus are assumed to have the same intensity thus are strongly correlated.
+In other words, pixels within the same isophotal annulus are assumed to have the same intensity and thus are strongly correlated.
 However, the non-parametric nature of vanilla \code{scarlet} only assumes monotonicity, which imposes quite weak correlations among pixels.
 Consequently, it is hard for the non-parametric modeling to probe very low surface brightness features.
-Furthermore, the monotonicity constraint stops the model from growing in certain directions if there is another source along this direction, otherwise monotonicity is broken.\footnote{This issue can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model of the target object never exceeds the other objects next to it.} As a result, the non-parametric model often does not capture well the LSB outskirts of LSBG, thus biasing the measurements.
+Furthermore, the monotonicity constraint stops the model from growing in certain directions if there is another source along this direction.\footnote{This issue can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model of the target object never exceeds the other objects next to it.} As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biasing the measurements.
 In the following, we explore a novel method to perform robust parametric modeling and measurement while exploiting the deblending power of \code{scarlet}.
@@
 In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized because they are modeled simultaneously in all bands with non-parametric models.
-The parametric model for the target object can also extend to the whole scene and not stopped by neighboring objects.
+The parametric model for the target object can also extend to the whole scene without artificially truncating if it encounters a neighboring object.
 
@@
 The Spergel profile is motivated by having a simple analytical expression in Fourier space, making it easy to convolve with a PSF.
-Similar to the \sersic{} index, the parameter $\nu$ in \eqref{eq:spergel} (dubbed as the ``Spergel index'') controls the concentration of the light profile.
+Similar to the \sersic{} index, the parameter $\nu$ in \eqref{eq:spergel} (the ``Spergel index'') controls the concentration of the light profile.
 As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is relevant to the study of LSBGs.
@@
 The completeness drops as we go to fainter surface brightness and smaller size.
-We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
+In a size range of $3\arcsec < r_e < 14\arcsec$, we are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
 	}
@@
 
-The completeness of the LSBG search is important not only for understanding our search efficiency and improving the method in the future, but also for deriving the completeness-corrected results for LSBG sciences.
+The completeness of the LSBG search is important not only for understanding our search efficiency and improving the method in the future, but also for deriving the completeness-corrected results for LSBG science.
 Similar to many other works \citep[e.g.,][]{vdBurg2017,Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and recovering them from the image.
@@
 A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}).
-Thus, the overall completeness is a combination of detection completeness and deblending completeness.
-We performed a large suite of image simulations to derive the completeness.
-We inject single \sersic{} light profile \citep{Sersic1963} to the coadd images and try do recover them using the detection method (\S\ref{sec:detection}), model them using vanilla \code{scarlet} (\S\ref{sec:deblending}), and apply the deblending cuts.
+Thus, the overall completeness combines the detection deblending steps.
+We perform a large suite of image simulations to derive the completeness.
+We inject single \sersic{} light profile \citep{Sersic1963} into the coadd images and try do recover them using the detection method (\S\ref{sec:detection}), model them using vanilla \code{scarlet} (\S\ref{sec:deblending}), and apply the deblending cuts.
 The mock \sersic{} galaxies span a wide range in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$) and surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$).
@@
 The deblending completeness is very high at the bright end, but starts to decline with increasing size and decreasing surface brightness.
-Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy.
-Interestingly, the detection completeness and deblending completeness all drop below 40\% around $\sbeff=27.5\ \sbunit$.
+Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending with other compact sources with the mock galaxy.
+Interestingly, the detection completeness and deblending completeness both drop below 40\% around $\sbeff=27.5\ \sbunit$.
 In this sense, the detection and deblending cooperate well in terms of completeness.
@@
 Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness.
-In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).
+In the future, we might be more capable of generating realistic LSBGs using deep learning techniques.
 
 We compare our completeness with that of other LSBG searches.
-Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more quickly with increasing size.
+Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more quickly with increasing size than ours does.
 \citet{CarlstenELVES2022} use a similar search algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$ assuming a Sersic index $n \approx 1$.
-\citet{vdBurg2017} searched LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
+\citet{vdBurg2017} searched for LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
 \citet{Zaritsky2021} focus on searching for LSBGs in the SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) images and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$ for $n=1$.
@@
 The Dragonfly Wide Field Survey \citep{Danieli2020} reaches $\sim 29\ \sbunit$ for $>3\sigma$ detection on scales $\sim 1\arcmin$, which is deeper than all other surveys by sacrificing spatial resolution.
-In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies \citep[e.g.,][]{Huang2018,Kado-Fong2018}.
+In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great power of HSC data on LSBG studies \citep[e.g.,][]{Huang2018,Kado-Fong2018}.
 
@@
 
-The size, magnitude, surface brightness, and shape of LSBGs are hard to characterize because of the low surface brightness nature.
-We characterize the measurement quality by comparing the Spergel modeling results with the ground truth for mock \sersic{} galaxies.
-We find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
-For surface brightnesses fainter than $27\ \sbunit$, the measured size can be much smaller than the truth.
-As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than reality.
-Similar to \citet{Zaritsky2021}, we derive the measurement biases and uncertainties in size, surface brightness, total magnitude, and color as a function of size and surface brightness.
+The size, magnitude, surface brightness, and shape of LSBGs are hard to characterize because of their low surface brightness nature.
+We characterize the quality of the structural measurements by comparing the Spergel modeling results with the ground truth for mock \sersic{} galaxies.
+We find that the measured effective radius $r_e$ tends to be smaller than the truth, and the bias depends on the surface brightness and the angular size.
+For surface brightness fainter than $>27\ \sbunit$, the measured size can be much smaller than the truth.
+As a result, the measured total magnitude $m$ and average surface brightness $\overline{\mu}_{\rm eff}$ are also too low.
+Similar to \citet{Zaritsky2021}, we derive the measurement bias and uncertainties in size, surface brightness, total magnitude, and color as a function of size and surface brightness.
 We refer interested readers to Appendix \ref{ap:comp_meas_unc} for details.
@@
 It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
-We also find the bias in $g-i$ color to be quite small.
-The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the biases.
-We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
+We find the bias in $g-i$ color to be quite small.
+The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the bias.
+We set the minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
 
@@
 
-% {\bf I think you can combine 3.4.1 and 3.4.2, and put most of this into the Appendix, just introduce the idea of the simulations and show the figure.
-I'd keep the comparison with other works in the main body of the paper.}
-
-\section{Mass-size outliers in Milky-Way analogs}\label{sec:sample_construction}
+\section{Mass-size outliers in the Milky-Way analogs}\label{sec:sample_construction}
 The goal of this paper is to study the mass-size outliers in the satellite systems around MW-like galaxies.
@@
 It is well-known that getting the distances to LSBGs is one of the major obstacles for studying their properties.
-Beside direct distance measurements (e.g., SAGA, ELVES, \citealt{Kadowaki2021}), it is common to assume a distance to a LSBG by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
+Beside direct distance measurements (e.g., SAGA, ELVES, \citealt{Kadowaki2021}), it is common to assume a distance to an LSBG by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
 A statistical background subtraction is then needed to account for the contribution from background and foreground galaxies.
@@
 In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$~mag ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA.
-In this work, we choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($M_{\star, \mathrm{MW}}\approx 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
+In this work, we choose the stellar mass range of our MW analog sample to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($M_{\star, \mathrm{MW}}\approx 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
 MW analogs selected using this definition are very close to those in SAGA but are slightly less massive than the ELVES hosts since ELVES has several groups more massive than SAGA hosts.
 
-Mass-size outliers, by definition, are relatively scarce compared with normal-sized satellites in MW analogs \citep{SAGA-II,CarlstenELVES2022}.
+Mass-size outliers, by definition, are relatively scarce compared with ``normal'' satellites around MW analogs \citep{SAGA-II,CarlstenELVES2022}.
 It is therefore helpful to probe a larger volume to obtain good statistics.
-We choose our redshift range to be $0.01 < z < 0.04$, which makes sure that we can detect a significant number of faint dwarf galaxies around MW-like hosts.
-The depth of HSC limits our detection below $z \approx 0.04$ since dwarf galaxies will be too small and too faint to be detected beyond that distance\footnote{Our search only includes objects larger than $r_e\approx 2\arcsec$, which corresponds to $M_\star \sim 10^{8.5}\ M_\odot$ at $z=0.04$ assuming the \textit{average} mass-size relation from \citet{ELVES-I}.
+We choose our redshift range to be $0.01 < z < 0.04$, which ensures that we can detect a significant number of faint dwarf galaxies around MW-like hosts.
+The depth of HSC limits our detection to below $z \approx 0.04$, since dwarf galaxies will be too small and too faint to be detected beyond that distance\footnote{Our search only includes objects larger than $r_e\approx 2\arcsec$, which corresponds to $M_\star \sim 10^{8.5}\ M_\odot$ at $z=0.04$ assuming the \textit{average} mass-size relation from \citet{ELVES-I}.
 Going to higher redshift will make it more difficult to detect low-mass dwarfs.}.
-We also exclude galaxies $z<0.01$ because (1) the number of UDGs will be very small due to the small volume; (2) their large angular size makes them more vulnerable to be shredded in the detection, so including them will introduce a number of spurious LSB objects.
-We do not discriminate our hosts to be isolated or paired.
+We also exclude galaxies $z<0.01$ because (1) the number of UDGs will be very small due to the small volume; (2) their large angular size makes them more vulnerable to being shredded during detection, so including them will introduce a number of spurious LSB objects.
+We do not discriminate between isolated or paired hosts.
 %Our LSBG sample complements the ELVES sample and SAGA sample in our redshift range.
@@
 We match them to the initial LSBG sample (described in \S \ref{sec:detection}, before the deblending step) as follows.
-For a given MW-like galaxy, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar-to-halo mass relation in \citet{Behroozi2010}.
-It turns out that 40\% of our hosts have virial radii larger than 300 kpc, which is commonly used for the virial radius of our Milky Way.
+For a given MW-like galaxy, we first calculate a virial radius $R_{\rm vir}$ assuming the stellar-to-halo mass relation in \citet{Behroozi2010}.
+It turns out that 40\% of our hosts have virial radii larger than 300 kpc, which is commonly used for the virial radius of the Milky Way.
 Then we identify any LSBG that falls into the projected virial radius of the host on the sky.
@@
 
-However, there are still a significant fraction of spurious objects in this cross-matched LSBG sample, including galactic cirrus, tidal streams, shredded large galaxies, and compact sources blended with galaxy outskirts.
-As described in \S\ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects.
+However, a significant fraction of spurious objects remain in this cross-matched LSBG sample, including galactic cirrus, tidal streams, shredded large galaxies, and compact sources blended with galaxy outskirts.
+As described in \S\ref{sec:deblending}, we then perform a deblending step to effectively remove spurious objects.
 There are 2,673 objects left after the deblending cuts.
-Next, we model them using the Spergel profile as described in \S\ref{sec:modeling} and obtain their photometry and structural parameters from the best-fit models.
+Next, we model these remaining objects using the Spergel profile as described in \S\ref{sec:modeling} and obtain their photometry and structural parameters from the best-fit models.
 % Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives.
-We also remove duplicated objects.
-In the end, we have 2,510 LSBG candidates associated with 689 MW analogs as our final LSBG sample.
+We also remove duplicate objects.
+We are left with 2,510 LSBG candidates associated with 689 MW analogs as our final LSBG sample.
 We note that these LSBGs are matched to MW hosts in projection but do not have direct distance measurements.
@@
 We apply the measurement bias correction (\S \ref{sec:comp_meas}) and assign completeness after bias correction.
-In the end, we correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
+Lastly, we correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
 We derive the stellar masses of cross-matched LSBG from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
@@
 \end{align*}
-Because we have both $g-r$ and $g-i$ color available from the model fitting, we use the average of the $M_{\star}/L$ derived from the two colors for calculating stellar mass.
+Because we have both $g-r$ and $g-i$ color available from the model fitting, we use the average $M_{\star}/L$ derived from the two colors to calculate stellar mass.
 We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}.
@@
 \subsection{Mass-size outlier sample}\label{sec:sample}
-The concept of UDG was proposed to describe dwarf galaxies with unusually large size ($r_e>1.5$ kpc) and diffuse light distribution ($\sbcen > 24.0\ \sbunit$).
+The concept of UDG was proposed to describe dwarf galaxies with unusually large size ($r_e>1.5$ kpc) and a diffuse light distribution ($\sbcen > 24.0\ \sbunit$).
 Although UDGs are large in size, the constant size cut does not account for the fact that the galaxy size is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
 For example, a galaxy with $r_e = 1.5$ kpc is very extended if its stellar mass is $10^7\ M_\odot$, but is normal-sized if its stellar mass is $10^{8.5}\ M_\odot$.
-Thus, a more intuitive definition for diffuse and puffy dwarf galaxies (i.e., mass-size outliers) should be based on a mass-size relation and its scatter.
+Thus, a more intuitive definition for diffuse and puffy dwarf galaxies (i.e., mass-size outliers) would be based on a mass-size relation and its scatter.
 Following this thread, we propose a new definition for mass-size outliers dubbed as \textit{ultra-puffy galaxies} (UPGs).
@@
 To select mass-size outliers, a mass-size relation and its scatter are needed.
-However in general, the slope of the mass-size relation in the nearby Universe has been shown to be color- and morphology-dependent for galaxies above $M_\star > 10^{9}\ M_\odot$: blue star-forming galaxies have a shallower slope than the red quenched galaxies \citep[e.g.,][]{Lange2015}.
+In general, the slope of the mass-size relation in the nearby Universe has been shown to be color- and morphology-dependent for galaxies above $M_\star > 10^{9}\ M_\odot$: blue star-forming galaxies have a shallower mass-size relation than do red quenched galaxies \citep[e.g.,][]{Lange2015}.
 Fortunately, in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$), \citet{ELVES-I} derive the mass-size relation from the satellites of MW analogs in the Local Volume and show that the average mass-size relation is quite universal: the slope and intercept are not sensitive to the color or morphology of dwarf galaxies.
-The residual from the mass-size relation follows a log-normal distribution reasonably well.
-This gives us a chance to define a subset of dwarf galaxies that are size-outliers with respect to the average mass-size relation.
+Residuals from the mass-size relation follow a log-normal distribution reasonably well.
+This fact allows us to define a subset of dwarf galaxies that are outliers with respect to the average mass-size relation.
 It is worth noting that a definition based on the mass-size relation was already used in simulation studies where the absolute sizes were uniformly too large such that size outliers can only be selected relative to the simulated mass-size relation \citep[e.g.,][]{Benavides2021,Benavides2022}.
@@
 Taking the measured average mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.25\, \log\, (M_\star/M_\odot) + 1.07$ and a scatter of $\sigma=0.18$ dex, we define a population of ultra-puffy galaxies to be galaxies that are $>1.5\sigma$ above the average mass-size relation.
-We choose $1.5\sigma$ just because it gives us a statistically significant sample.
+We choose $1.5\sigma$ because it gives us a statistically significant sample.
 One can certainly select $>2\sigma$ or $>3\sigma$ UPGs if a larger LSBG sample is available.
@@
 A UPG with $M_\star = 10^{8.5}\ M_\odot$ has a size larger than 2.7 kpc and surface brightness fainter than $\sbeff > 23.7\ \sbunit$ for $g-i=0.4$ and $\sbeff > 25.0\ \sbunit$ for $g-i=0.8$.}.
-The definition of UPG based on the observed mass-size relation is more physically-motivated, and better allows us to study size outliers at a given stellar mass.
+The definition of UPG based on the observed mass-size relation is physically-motivated, and better allows us to study size outliers at a given stellar mass.
 We further discuss the advantages and disadvantages of UDG and UPG in \S\ref{sec:mass-size} and \S\ref{sec:discussion}.
 
-There are 362 objects in our LSBG candidates that fall $1.5\sigma$ above the ridge line of the mass-size relation.\footnote{We note that the mass-size relation in \citet{ELVES-I} is derived for a mass range of $10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$.
-We extrapolate the mass-size relation to $M_\star \sim 10^9\ M_\odot$ to define our UPG sample.} After removing spurious objects after visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
+There are 362 LSBG candidates that fall $1.5\sigma$ above the ridge line of the mass-size relation.\footnote{We note that the mass-size relation in \citet{ELVES-I} is derived for a mass range of $10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$.
+We extrapolate the mass-size relation to $M_\star \sim 10^9\ M_\odot$ to define our UPG sample.} After removing spurious objects by visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
 These UPGs are associated with 239 hosts.
@@
 Thus, we also select a UDG sample from our LSBGs in order to compare with existing observations and simulations in different environments.
-The UDG sample is usually defined based on the surface brightness and the physical size of the galaxy.
-However, there are many different criteria in literature: \citet{vanDokkum2015} define UDGs to have effective radii $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}.
+The UDG sample is usually defined based on surface brightness and physical size of the galaxy.
+However, there are many different criteria in the literature: \citet{vanDokkum2015} define UDGs to have effective radii $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}.
 The size criterion also varies from $r_e > 1$ kpc to $r_e > 1.5$ kpc.
@@
 The difference between the average surface brightness and the central surface brightness can be analytically calculated for a \sersic{} profile: $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}.
-Since dwarf galaxies and UDGs typically have \sersic{} index of $0.8 < n < 1.2$ \citep[e.g.,][]{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.0$ as an average value to convert $\mu_0$ to $\mu_{\mathrm{eff}}$.
-In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, where we also take the $1\sigma$ measurement errors into account.
-As a result, there are a few objects with smaller size but large uncertainty scattered in our UDG sample.
+Since dwarf galaxies and UDGs typically have \sersic{} indices of $0.8 < n < 1.2$ \citep[e.g.,][]{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.0$ as an average value to convert $\mu_0$ to $\mu_{\mathrm{eff}}$.
+In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$ to take the $1\sigma$ measurement errors into account.
+As a result, there are a few objects with nominally smaller size but large uncertainty that scatter into our UDG sample.
 This definition maximizes the consistency with the definition in \citet{vanDokkum2015} while not losing UDGs harboring nuclear star clusters.
@@
 Although we have matched LSBGs to MW analogs by proximity, the physical affiliation of LSBGs to the host is not guaranteed.
-As a result, a certain fraction of galaxies in our mass-size outlier samples might just be foreground or background galaxies that fall within the virial radius of the host in projection.
+As a result, a certain fraction of galaxies in our mass-size outlier samples are foreground or background galaxies that fall within the virial radius of the host in projection.
 Given the volume probed by our search, contamination is most likely to be dominated by background galaxies.
-In the section, we try estimate the contamination fraction empirically by studying the number of those LSBGs that mimic UPGs and UDGs by randomly matching LSBGs to our MW hosts.
-
-We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2 regardless of whether containing MW analogs\footnote{$345\ \deg < \rm{R.A.} < 351\ \deg$, $-1.5\ \deg < \rm{Dec} < 2.5\ \deg$, which is not dominated by Galactic cirrus and stars.
+In thie section, we try estimate the contamination fraction empirically by randomly matching LSBGs to our MW hosts and measuring the number density of apparent UPG and UDG.
+
+We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2 regardless of whether it contains MW analogs\footnote{$345\ \deg < \rm{R.A.} < 351\ \deg$, $-1.5\ \deg < \rm{Dec} < 2.5\ \deg$, which is not dominated by Galactic cirrus and stars.
 Such a patch of sky with 24 deg$^2$ is already enough for us to derive a background contamination fraction with small Poisson error.}.
@@
 In the end, there are 480 LSBGs (excluding false positives) representing a population of possible contaminants for the UDG and UPG samples.
-Next, because both UDG and UPG are defined based on a physical size, we randomly associate the 480 LSBGs to the hosts of our UDGs and UPGs, respectively.
+Next, because both UDG and UPG are defined based on a physical size, we randomly associate the 480 LSBGs with the hosts of our UDGs and UPGs, respectively.
 Then we calculate a physical size for each LSBG and classify an LSBG as a ``fake`` UDG or UPG if it satisfies the corresponding definition.
@@
 \section{Results}\label{sec:results}
-In this section, we present a statistical analysis for mass-size outliers among the satellites of MW analogs at $0.01 < z < 0.04$.
-We first compare the distributions of UDGs and UPGs on the size-surface brightness plane and mass-size plane to gain intuition on the differences between UDG and UPG definitions.
-Then we present the abundances of UDGs and UPGs and compare with literature.
+In this section, we compare the distributions of UDGs and UPGs on the size-surface brightness and mass-size planes to gain intuition on the differences between UDG and UPG definitions.
+Then we present the abundances of UDGs and UPGs and compare with the literature.
 
@@
     \caption{The distribution ultra-diffuse galaxies (UDGs, \textit{left}) and ultra-puffy galaxies (UPGs, \textit{right}) on the size-surface brightness plane.
-The UPGs is defined to be galaxies that are $1.5\sigma$ above the average mass-size relation in \citet{ELVES-I}.
+The UPGs are defined to be galaxies that are $1.5\sigma$ above the average mass-size relation in \citet{ELVES-I}.
 The samples are split into two color bins and shown in red ($g-i>0.8$) and blue ($g-i<0.8$).
@@
 UDGs that are also classified as UPGs are shown as orange squares, while UDGs that do not satisfy the UPG definition are marked as red stars.
-Blue triangles are UPGs that are not classified as UDGs.
-UDG sample includes a significant amount of galaxies that are not mass-size outliers (below the $1.5\sigma$ line) which are red in color because the surface brightness cuts are different on mass-size plane for blue and red galaxies.
+Conversely, blue triangles are UPGs that are not classified as UDGs.
+The UDG sample includes a significant number of galaxies that are not mass-size outliers (falling below the $1.5\sigma$ line) which are red in color because the surface brightness cuts are different on the mass-size plane for blue and red galaxies.
     }
@@
 
-In order to build a more comprehensive understanding on our UDG and UPG sample, we show their distributions on the size-surface brightness plane in Figure \ref{fig:udg_upg_re_mu}.
+In order to build a more comprehensive understanding of our UDG and UPG sample, we show their distributions on the size-surface brightness plane in Figure \ref{fig:udg_upg_re_mu}.
 The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively.
-We note that we do not apply any background contamination correction in Figure \ref{fig:udg_upg_re_mu} because such correction can only be done in a statistical sense.
+We note that we do not apply any background contamination correction in Figure \ref{fig:udg_upg_re_mu} because such corrections can only be done in a statistical sense.
 The error bars correspond to $1\sigma$ measurement uncertainties (\S\ref{sec:comp_meas}).
-Some galaxies with size smaller than 1.5 kpc are still scattered in the UDG sample because their sizes have large uncertainty.
+Some galaxies with sizes smaller than 1.5 kpc are still scattered into the UDG sample because their sizes have large uncertainty.
 The two marginal plots show the unnormalized histograms of galaxies in the two color bins.
@@
 Since there is no hard surface brightness cut for UPGs, the UPG sample includes many blue galaxies with brighter surface brightness ($23 \lesssim \sbeff < 25\ \sbunit$).
-For blue UPGs (shown as blue dots), the correlation between $\sbeff$ and $r_e$ is merely the fact that blue UPGs pile up around the $1.5\sigma$ line above the mass-size relation.
-
-Due to the surface brightness cut ($\sbeff > 23.0\ \sbunit$) in the deblending step, there is little chance for a LSB disk galaxy with bright bulge to scatter in the UPG sample.
+For blue UPGs (shown as blue dots), the apparent correlation between $\sbeff$ and $r_e$ is merely due to the fact that blue UPGs pile up around the $1.5\sigma$ line above the mass-size relation.
+
+Due to the surface brightness cut ($\sbeff > 23.0\ \sbunit$) in the deblending step, there is little chance for an LSB disk galaxy with a bright bulge to scatter into the UPG sample.
 The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26\ \sbunit$ because their stellar masses are high but their sizes are too small to be mass-size outliers.
@@
 We show UDGs and UPGs on the mass-size plane in Figure \ref{fig:mass_size}.
-To orient the reader to the mass-size plane, we first show a schematic diagram in the left panel where the lines and regions relevant to the definition of UDG and UPG are highlighted.
-The light blue shade shows the survey limit where we cannot effectively probe LSBGs fainter than $\sbeff \gtrsim 27.5\ \sbunit$ (see \S\ref{sec:comp_meas}).
+To orient the readers to the mass-size plane, we first show a schematic diagram in the left panel where regions relevant to the definitions of UDG and UPG are highlighted.
+The light blue shade shows the survey limit; we cannot effectively probe LSBGs fainter than $\sbeff \gtrsim 27.5\ \sbunit$ (see \S\ref{sec:comp_meas}).
 For defining UDGs, a size cut and a surface brightness cut are needed.
-We show the $r_e = 1.5$ kpc cut as a gray band to acknowledge the fact that smaller galaxies with large size uncertainty can also get into the UDG sample.
+We show the $r_e = 1.5$ kpc cut as a horizontal gray band to acknowledge the fact that smaller galaxies with large size uncertainties are included in the UDG sample.
 The slanted solid lines show the constant surface brightness lines with $\sbeff = 25.0\ \sbunit$ for two different colors ($g-i=0.4$ and $g-i=0.8$).
-For our redshift range, the cosmological dimming effect is negligible and the surface brightness is a constant with distance.
-The constant surface brightness lines depends on color because of the color-$M_\star/L$ relation.
+For our redshift range, the cosmological dimming effect is negligible and the surface brightness is constant with distance.
+The constant surface brightness lines depend on color because of the color-$M_\star/L$ relation.
 We also show the constant surface stellar mass density ($\mu_\star$) line, which is parallel to the constant surface brightness lines because the surface mass density is proportional to surface brightness multiplied by mass-to-light ratio.
@@
 
-We highlight the similarity and difference between UDG and UPG in the right panel.
+We highlight the similarities and differences between the UDGs and UPGs in the right panel.
 UDGs that are also classified as UPGs are shown as orange squares, while UDGs that do not satisfy the UPG definition are marked as red stars.
 Blue triangles correspond to UPGs that are not classified as UDGs.
-Limited by the detection limit and also the fact that our hosts are more distant than the Local Volume, our samples only reach to $M_\star \approx 10^{6.8}\ M_\odot$ which is $\sim 1$ dex higher than ELVES.
+Limited by the detection limit and the fact that our hosts lie beyong the Local Volume, our mass limit is $M_\star \approx 10^{6.8}\ M_\odot$, which is $\sim 1$ dex higher than ELVES.
 Compared with the UPG sample, we find that the UDG sample (orange squares + red stars) comprises a number of galaxies below the $1.5\sigma$ line, but also loses several low-mass galaxies that are above $1.5\sigma$ line but have sizes smaller than 1.5 kpc.
-For the UDG sample, the stellar mass range only reaches $M_\star\approx 10^{8.3}\ M_\odot$ because galaxies with higher stellar mass are too bright to satisfy the surface brightness criterion for UDG.
-On the contrary, since the UPG definition does not have a hard surface brightness cut, it includes many galaxies that are more massive than UDGs as long as it has an extraordinarily large size.
+For the UDG sample, the stellar mass range only reaches $M_\star\approx 10^{8.3}\ M_\odot$ because galaxies with higher stellar mass are too bright to satisfy the UDG surface brightness criterion.
+On the contrary, since the UPG definition does not have a hard surface brightness cut, it includes many galaxies that are more massive than UDGs provided they have an extraordinarily large size.
 As a consequence, background spiral galaxies could dominate the UPG sample at the high-mass end.
-
-% As we will introduce in Section \ref{sec:quench}, we use a color cut $(g-i)_{Q}$ to separate galaxies with active star formation from quiescent ones.
-Here we define $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ as an indicator for the star formation rate of the galaxy.
-Higher $\Delta(\mathrm{Quench})$ indicates that the galaxy is actively star-forming, whereas lower $\Delta(\rm Quench)$ means the galaxy has lower star formation rate.
-We color-code the galaxies in Figure \ref{fig:mass_size} with $\Delta(\mathrm{Quench})$.
-UDGs below the $1.5\sigma$ line have near zero or negative $\Delta(\mathrm{Quench})$, indicating that the UDG sample includes plenty of quenched galaxies compared with the UPG sample.
-Instead, the UPG sample is comprised of many star-forming galaxies at the high-mass end.
-
-% In Figure \ref{fig:mass_size}, we also show constant surface brightness lines in the left panel and constant mass surface density in the right panel.
-We will discuss how the definition of UDG could bias the quenched fraction later in Sec.
-\ref{sec:discussion}.
 
@@
 \textit{Left}: We compile the UDG abundance measurements from the literature covering a wide range of host mass.
-The UDG abundance of our work $N_{\rm UDG} = 0.76\pm 0.04$ is shown as red square, the power-law relation from \citet{vdBurg2017} is shown in gray, and our fitting result is shown in pink.
+The UDG abundance from our work $N_{\rm UDG} = 0.76\pm 0.04$ is shown as a red square, the power-law relation from \citet{vdBurg2017} is shown in gray, and our fitting result is shown in pink.
 Our UDG abundance is consistent with ELVES but significantly higher than that in SAGA.
@@
 As demonstrated by many previous studies \citep[e.g.,][]{vdBurg2016,vdBurg2017,Roman2017a,Karunakaran2022b}, the average number of UDGs per host scales with host halo mass.
-While much literature focuses on finding UDGs in clusters and large groups, there are fewer constraints on the UDG abundance at the lower halo mass end.
+While much literature focuses on finding UDGs in clusters and large groups, there are fewer constraints on the UDG abundance at the lower halo-mass end.
 In this section, we calculate the UDG and UPG abundances of MW analogs, and compare with other surveys.
@@
 We define the UDG (UPG) abundance as the average number of UDGs (UPGs) per host galaxy.
-We searched 901 MW analogs.
+We searched 689 MW analogs.
 In our UDG sample, there are 412 UDGs associated with 258 hosts.
@@
 Because both SAGA and ELVES select satellites based on distance measurements and do not correct for completeness, we interpret their UDG abundances as lower limits.
-We note that \citet{Roman2017b} do not estimate the background contamination fraction and correct for completeness.
+We note that \citet{Roman2017b} do not estimate the background contamination fraction and do correct for completeness.
 Because there is little literature on UPGs, we only compare our UPG abundance with ELVES.
@@
 The UDG abundance of this work is highlighted as the red square.
-As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo mass end, but this might be due to the small statistics in prior studies and the difference in completeness.
+As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo-mass end, but this might be due to the small statistics in prior studies and the differences in completeness.
 Our UDG abundance is similar to the value in ELVES survey, but much higher than the value from SAGA.
-This might be explained by the different photometric depth of data used.
+This might be explained by the different photometric depths of data used.
 As pointed out by \citet{CarlstenELVES2022,Font2022}, the SAGA survey reaches a surface brightness depth of $\sbeffr\approx 25\ \sbunit$, which is $\sim 2.5\ \sbunit$ shallower than the ELVES survey and this work.
@@
 \citet{ManceraPina2018} survey eight clusters and find sublinear power laws.
-Recently \citet{Karunakaran2022b} perform a similar analysis including SAGA and ELVES and find slightly shallower power law of $\beta=0.87\pm0.07$.
+Recently \citet{Karunakaran2022b} perform a similar analysis including SAGA and ELVES and find a slightly shallower power law of $\beta=0.87\pm0.07$.
 Since most individual studies do not have a statistical estimation for background contamination and completeness, the UDG abundances for large groups should be interpreted as lower limits.
@@
 Another interesting quantity is the fraction of satellites that are mass-size outliers in a group or cluster.
-This fraction represent how efficient an environment is at producing puffy satellites.
+This fraction represents how efficient an environment is at producing puffy satellites.
 We denote this quantity as the UDG (UPG) fraction hereafter, which characterizes the tail of the size distribution of satellites.
 In order to calculate this fraction, we assume that MW analogs have $\sim 6$ satellites with $M_\star > 10^{6.5}\ M_\odot$ \citep{CarlstenELVES2022}.
-This lower limit of stellar mass is roughly our detection limit (see Fig.
+This lower limit in stellar mass is roughly our detection limit (see Fig.
 \ref{fig:mass_size}).
@@
 We also compare our results with results in the Virgo cluster.
-Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}), there are 15 UDGs and 24 UPGs out of 404 identified satellites with no completeness correction.
+Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}), there are 15 UDGs and 24 UPGs out of 404 identified satellites (with no completeness correction).
 Thus their UDG (UPG) fraction is $f_{\rm UDG}^{\rm Virgo} \approx 0.04$ and $f_{\rm UPG}^{\rm Virgo} \approx 0.06$.
 However, we note that \citet{Ferrarese2020} only survey the central 4 deg$^2$ of the Virgo cluster, which probably biases the UDG (UPG) fraction.
-It seems our UDG fraction is higher than both ELVES and NGVS.
+It seems that our UDG fraction is higher than both ELVES and NGVS.
 Our UPG fraction is consistent with ELVES but higher than NVGS.
@@
 
-We note that ELVES probes less massive dwarfs than our search.
+\jiaxuan{We note that ELVES probes less massive dwarfs than our search. }
 
@@
 \ref{fig:mass_size}).
-On the other hand, the hard surface brightness cut corresponds to very different surface mass density between red and blue galaxies, making it hard to directly compare red and blue UDGs since they occupy different regions on the mass-size plane.
-For a given stellar mass and size (e.g., at $M_\star \sim 10^{7.5}\ M_\odot$), the hard surface brightness cut in the UDG definition preferentially removes blue galaxies because their surface brightnesses are higher and their $M_\star/L$ are lower.
+On the other hand, the hard surface brightness cut corresponds to very different surface mass densities between red and blue galaxies, making it hard to directly compare red and blue UDGs, since they occupy different regions on the mass-size plane.
+For a given stellar mass and size (e.g., at $M_\star \sim 10^{7.5}\ M_\odot$ and $r_e = 1.5$ kpc), the hard surface brightness cut in the UDG definition preferentially removes blue galaxies because their surface brightnesses are higher and their $M_\star/L$ are lower.
 Thus, red UDGs are over-represented.
-If one calculates the quenched fraction of UDGs as a function of stellar mass, it will be biased high because of the constant surface brightness cut.
+If one calculates the quenched fraction of UDGs as a function of stellar mass, it will be biased high because of this constant surface brightness cut in the UDG definition.
 
@@
 A more physically-motivated definition for mass-size outliers is needed.
-
-% These issues manifest themselves in the high quenched fractions of UDGs. 
-% In Section \ref{sec:sample_construction}, we have already argued that the hard size cut in UDG definition does not map clearly onto the mass-size relation, and we propose identifying UPGs as outliers in the mass-size plane.
-Here we discuss another limitations in the UDG definition, namely the hard cut in surface brightness regardless of the galaxy color.
-We also discuss the advantages and disadvantages of different definitions of low surface brightness galaxies including UDG and UPG.
-% The above issues manifest themselves in the derived quenched fractions of UDGs.
-In Section \ref{sec:quench}, we find that the quenched fraction of UDGs is higher than the quenched fractions of UPGs and the satellite population of MW analogs.
-Furthermore, it almost remains a constant over $>1.5$ dex in stellar mass.
-% We argue that UDG's high and constant quenched fraction is merely an artifact of the definition.
-We start from Figure \ref{fig:mass_size}, where we show UDGs and UPGs on the mass-size plane color-coded by $\Delta(\mathrm{Quench}) = (g-i) - (g-i)_{Q}$ indicating how much a galaxy has been quenched (\S \ref{sec:quench}).
-% We note that the color-$M_\star/L$ relation are only invoked when converting the absolute magnitude to stellar mass.
-Thus when studying the quenched fraction on size-luminosity plane (e.g., g-band absolute magnitude), the artifact would disappear \citep[e.g., see][]{Danieli2019}.
-
-The concept of ultra-puffy galaxy is defined based on the average mass-size relation and thus alleviates some of the issues in the UDG definition.
-They are defined to be $1.5\sigma$ above the average mass-size relation in the dwarf galaxy regime.
+The ultra-puffy galaxy is defined based on the average mass-size relation and thus alleviates some of the issues in the UDG definition.
+UPGs are defined to lie $1.5\sigma$ above the average mass-size relation of the satellites in MW analogs in the Local Volume.
 The specific value above the average mass-size relation can vary to probe different parts of the size distribution.
@@
 Both size and stellar mass could have large uncertainties in the LSB regime.
-One also needs to apply a surface brightness cut (such as $\sbeff > 23.0\ \sbunit$ in this work) to make sure the UPG sample is not contaminated by disk galaxies with high surface brightness due to the bulges.
-On the one hand, reliable mass-size relation and its scatter are not available for all mass ranges.
-\citet{ELVES-I} derive the mass-size relation below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$.
-The mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is not well measured, nor is any dependence on color and morphology.
+One also needs to apply a surface brightness cut (such as $\sbeff > 23.0\ \sbunit$ in this work) to make sure that the UPG sample is not contaminated by disk galaxies with high surface brightness due to the bulges.
+Reliable mass-size relations with scatter are not available for all galaxy mass ranges.
+\citet{ELVES-I} derive the mass-size relation of satellite galaxies below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$.
+The mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is not well measured, nor is any dependence on color or morphology.
 In this work, we simply extrapolate the \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$.
@@
 Hence another way to define diffuse galaxies is to select galaxies with low surface mass density.
-This method also alleviates the artifact introduced by color-$M_\star/L$ relation on the mass-size plane.
-We defer exploration of this definition to future works.
+This method also alleviates the artifacts introduced by the color-$M_\star/L$ relation on the mass-size plane.
+We defer exploration of this definition to future work.
 
@@
 In this work, we perform a search for low surface brightness galaxies in HSC PDR2 data and construct samples for mass-size outliers around MW analogs at $0.01 < z < 0.04$.
-Beside the ultra-diffuse galaxies, we propose studying ``ultra-puffy galaxies'' which is defined to be $1.5\sigma$ above the average mass-size relation.
-We conduct statistical analysis for mass-size outliers and argue that UPGs better represent the large-size tail of the dwarf galaxy population.
-We summarize our main findings and prospects below.
+Besides the ultra-diffuse galaxies, we propose studying ``ultra-puffy galaxies'' which is defined to be $1.5\sigma$ above the average mass-size relation.
+We calculate the abundances of mass-size outliers and compare with literature.
+We also argue that UPGs better represent the large-size tail of the dwarf galaxy population.
+Our main findings and prospects are summarized below.
 
@@
 Utilizing the non-parametric models generated by \code{scarlet}, we design a metric based on morphological parameters to effectively rule out false positives in the LSBG detection.
-We measure the structural properties of LSBGs using Spergel profiles and carefully characterize the measurement biases and uncertainties.
+We measure the structural properties of LSBGs using the Spergel profile and carefully characterize the measurement biases and uncertainties.
 The completeness of the search is also derived by injecting mock galaxies.
-Our LSBG search achieves high completeness compared with other searches and demonstrates the power of HSC data for LSB sciences.
+Our LSBG search achieves high completeness compared with other searches and demonstrates the power of HSC (and future LSST) data for LSB science.
 
@@
 
-    \item After correcting for background contamination, the UDG abundance in MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host and the UPG abundance is $N_{\rm UPG} = 0.61 \pm 0.04$ per host.
+    \item After correcting for background contamination and completeness, the UDG abundance in MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host and the UPG abundance is $N_{\rm UPG} = 0.61 \pm 0.04$ per host.
 Our UDG abundance is slightly higher than that in ELVES, but much higher than that in SAGA.
 Combining data from studies in denser environments, we find that the UDG abundance follows a sublinear power law with the host halo mass.
-The power law slope agrees with other studies.
+The power law slope agrees with other studies considering the errors.
 We caution that many other studies do not correct for completeness which could bias the results.
@@
     \item For a MW analog, on average, about 15\% of its satellites are UDGs and about 10\% of its satellites are UPGs.
-The UDG and UPG fractions are slightly higher than those in ELVES and NGVS, which suffer from small number statistics due to their sample sizes.
-
-    \item We advocate studying UPG which is more physically motivated, does not introduce artifacts in the mass-size distribution, and better represents the large-size tail of dwarf galaxy population.
-% \end{itemize}
+The UDG and UPG fractions are slightly higher than those in ELVES and NGVS, which do not correct for completeness and suffer from small number statistics due to their sample sizes.
+
+    \item We advocate the concept of UPG which is more physically motivated, does not introduce artifacts in the mass-size distribution, and better represents the large-size tail of dwarf galaxy population.
 \end{enumerate}
@@
 This paper presents the UDG and UPG sample and explores their abundances.
-In our Paper II (to be submitted), we study their size and spatial distribution and their star formation status.
+In our Paper II (to be submitted), we study their size and spatial distributions and their star formation status.
 This study is focused on a small subset of LSBG candidates matched with MW analogs.
-In future works, we would like to exploit the full sample to study interesting topics including redshift distributions, nucleation fractions, intrinsic shapes of LSBGs.
+In future works, we would like to exploit the full sample to study interesting topics on LSBGs including their redshift distributions, nucleation fractions, and intrinsic shapes.
 We will also explore machine learning techniques to help us classify LSBGs and estimate structural parameters.
-With the upcoming LSST \citep{lsst2009,LSST2019}, we will be able to study the LSBG population with much greater statistics and gain new insights into the formation and evolution of mass-size outliers.
+With the upcoming LSST \citep{lsst2009,LSST2019}, we will be able to study the LSBG population with much greater statistical power and gain new insights into the formation and evolution of mass-size outliers.
 
 \section*{Acknowledgment}
-JL is grateful for discussions with Meng Gu, ChangHoon Hahn. The authors thank Yao-Yuan Mao for his tool for visualizing the image cutouts.
+JL is grateful for discussions with Meng Gu, ChangHoon Hahn, Sihao Cheng.
+The authors thank Yao-Yuan Mao for his \href{https://github.com/yymao/decals-image-list-tool}{tool} for visualizing the image cutouts.
+
+{\bf JEG needs to add her grant here}
 
@@
 We also require the measured colors to satisfy $-0.1 < g-i < 1.4$ and $|(g-r) - 0.7\cdot (g-i)| < 0.4$.
-This color box is relatively conservative with respect to the color distribution of the discovered LSBGs \citep[e.g.,][]{SAGA-I,Greco2018,Zaritsky2019,Tanoglidis2021}.
+This color box is relatively conservative with respect to the color distribution of discovered LSBGs \citep[e.g.,][]{SAGA-I,Greco2018,Zaritsky2019,Tanoglidis2021}.
 
@@
 In \S\ref{sec:deblending}, we briefly introduce how we use \code{scarlet} to model the LSBG candidates in a non-parametric fashion and filter out false positives based on the structural and morphological parameters.
-In this appendix, we describe details of the implementation of vanilla \code{scarlet} which could help interested readers better understand the technique.
+In this appendix, we describe details of the implementation of vanilla \code{scarlet} to help interested readers better understand the technique.
 
@@
 The model is considered to be converged when the relative changes of parameters are smaller than \code{e\_rel\,=\,2e-4}.
-Typically, convergence is achieved after $\sim 50$ steps of optimization and the whole modeling takes about 40s for a typical LSBG.
+Typically, convergence is achieved after $\sim 50$ steps of optimization and the whole modeling process takes about 40s for a typical LSBG.
 It takes longer when the target galaxy has large angular size since more peaks are modeled.
-We note that \code{scarlet} only find the maximum likelihood estimation of the model instead of deriving the full posteriors, thus a good initialization becomes especially important for fast convergence.
+We note that \code{scarlet} only finds the maximum likelihood estimation of the model instead of deriving the full posteriors, thus a good initialization becomes especially important for fast convergence.
 
@@
     \caption{The correspondence between the \sersic{} profile \eqref{eq:sersic} and the Spergel profile \eqref{eq:spergel}.
-We fit a Spergel profile to \sersic{} while fixing the total luminosity and half-light radius.
+We fit a Spergel profile to each \sersic{} while fixing the total luminosity and half-light radius.
 The left panel shows the best-fit Spergel index $\nu$ as a function of \sersic{} index $n$.
 In the right panel, two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) are shown.
-Spergel profile approximates \sersic{} well for small \sersic{} indices.
+The Spergel profile approximates the \sersic{} profile well at small \sersic{} index.
     }
@@
 
-In this appendix, we demonstrate that the Spergel profile can approximate \sersic{} profile and profile a lookup table for the correspondence between \sersic{} index $n$ and Spergel index $\nu$.
+In this appendix, we demonstrate that the Spergel profile can approximate the \sersic{} profile and providee a lookup table for the correspondence between \sersic{} index $n$ and Spergel index $\nu$.
 
@@
 
-To study the correspondence between \sersic{} and Spergel profiles, we generate \sersic{} profiles with different \sersic{} indices, and try to fit Spergel profiles to \sersic{} ones.
+To study the correspondence between \sersic{} and Spergel profiles, we generate \sersic{} profiles with different \sersic{} indices, and try to fit Spergel profiles to \sersic{} models.
 The \sersic{} index ranges from $n=0.5$ to $n=4.5$, and both profiles are normalized using $r_e$.
@@
 
-For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
+To estimate the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
 This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
@@
 We split the size and surface brightness range into 15 bins with $\Delta r_e = 0.86\arcsec$, $\Delta \sbeff = 0.33\ \sbunit$, and interpolate over bins using an isotropic Gaussian kernel with $\sigma = 0.5$.
-We notice that the size and surface brightness shown in Figure \ref{fig:completeness} are all the intrinsic values for the mock galaxies, which are different from the measured ones.
+We note that the size and surface brightness shown in Figure \ref{fig:completeness} are all the intrinsic values for the mock galaxies, which are different from the measured ones.
 We find negligible dependence of detection completeness on \sersic{} index, color, and ellipticity.
@@
 Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs.
-\citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth.
+\citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into coadded images and compare the recovered properties with the truth.
 \citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network.
@@
 
-In order to test how well we recover the photometric and structural parameters in the our measurement (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
+In order to test how well we recover the photometric and structural parameters in our measurements (Sec \ref{sec:modeling}), we take the 5,000 mock \sersic{} galaxies used for computing the deblending completeness and model them using the Spergel light profile.
 We model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shape.
@@
 In this way, we apply a self-consistent correction for the measurement biases to the data.
-The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, neighboring contamination, etc.
+The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, neighbor contamination, etc.
 Unlike other parametric modeling codes such as \code{imfit} \citep{imfit} and \code{the Tractor} \citep{Lang2016}, \code{scarlet} does not explore the full posterior space but rather finds one optimal solution.

### 2022-10-23 paper1.tex
before my final read

@@
 Large diffuse galaxies are hard to find, but understanding the environments where they live and their numbers, and ultimately their origins, is of intense interest and important for galaxy formation and evolution.
-Using Subaru's Hyper Suprime-Cam Strategic Survey Program data, we perform a systematic search for low surface-brightness galaxies and present novel and effective methods for detecting and modeling them.
-As a case study, we build a statistical sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$).
+Using Subaru's Hyper Suprime-Cam Strategic Survey Program, we perform a systematic search for low surface brightness galaxies and present novel and effective methods for detecting and modeling them.
+As a case study, we build a large sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$).
 These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represents the tail of the satellite size distribution.
-We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is comparable to the observed abundance at this halo mass in the Local Volume.
+We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is slightly smaller than the observed abundance at this halo mass in the Local Volume.
 We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.76\pm0.04$ per host.
@@
 \section{Introduction} \label{sec:intro}
-In a variety of galaxies in the Universe, there is an interesting subset of galaxies with low surface brightness and large physical size \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
+In a variety of galaxies in the Universe, there is an interesting subset of galaxies with low surface brightness \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
 Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
 There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
-UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus UDGs are outliers in size and surface brightness for their stellar mass compared to normal dwarf galaxies.
+UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus UDGs are outliers in size and surface brightness compared to normal dwarf galaxies.
 A central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation of dwarf galaxies?
@@
 In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019}, via adiabatic expansion due to mass loss \citep{Tremmel2020}, or even via a bullet-dwarf collision \citep{vandokkum2022Nat,vanDokkum2022GC}.
-Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed and quenched.
+Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed.
 It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness or larger size.
-A nice way to to answer these questions is to compare these mass-size outliers with ``normal'' low mass galaxies which have been studied extensively.
+A straightforward way to answer these questions is to compare mass-size outliers with ``normal'' low mass galaxies which have been studied extensively.
 
@@
 With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs (typically defined as galaxies having similar stellar mass or halo mass to MW) in the Local Volume and nearby Universe.
-The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at 20--40 Mpc \citep{SAGA-I,SAGA-II}.
-The Exploration of Local VolumE Satellites (ELVES,  \citealt{ELVES-I,ELVES-II,CarlstenELVES2022}) survey uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts.
+The Satellites Around Galactic Analogs survey (SAGA, \citealt{SAGA-I,SAGA-II}) is designed to spectroscopically confirm the satellites of 100 MW analogs at 20--40 Mpc.
+The Exploration of Local VolumE Satellites survey (ELVES,  \citealt{ELVES-I,ELVES-II,CarlstenELVES2022}) uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts.
 Having these MW satellites as a reference frame, we can contrast them with the mass-size outliers in the same environment to understand the formation of large diffuse galaxies.
-However, there are only $\sim 40$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022,Karunakaran2022b}.
+However, there are only $\sim 40$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022,Nashimoto2022,Karunakaran2022b}.
 Therefore, a larger sample of mass-size outliers associated with MW-like hosts is needed to conduct such a comparison between the mass-size outliers and the normal satellites.
@@
 Unlike other parametric modeling methods, the non-parametric \code{scarlet} model is flexible enough to adequately represent galaxies with complex structures.
-But the non-parametric nature of the code means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model.
+But the non-parametric nature of the code means that we have to make additional measurements to quantify the size and shape of the \code{scarlet} model.
 As shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}, we isolate the model of the target object and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}.
@@
 \begin{equation}\label{eq:mu_eff}
-    \mu_{\rm eff} = m - 2.5 \log_{10}(2 \pi r_e^2),
+    \overline{\mu}_{\rm eff} = m - 2.5 \log_{10}(2 \pi r_e^2),
 \end{equation}
@@
 We measure the morphological and structural parameters in $g$-band.
+
+To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the classification results to help construct the metrics.
+To be specific, we randomly select 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ from the NSA catalog (see \S\ref{sec:match} for details).
+We run vanilla \code{scarlet} for all of them and measure morphological parameters as described above.
+Then we do visual inspection of the $griz$ color-composite images with 0.5 arcmin on a side.
+False positives, including tidal streams, galaxy outskirts blends, and other artifacts (dubbed \code{junk}), are identified during the visual inspection by coauthors JEG, JG, SH, RB, KC, AG, and EKF.
+Each object has been inspected by at least two people.
+In the end, we combine the votes from different people.
+An object is classified as \code{junk} if the number of votes as \code{junk} is larger than the number of votes as \code{non-junk}.
+In total, there are 1661 objects classified as \code{junk}.
+The visual inspection is summarized in Table \ref{tab:deblending_vis}.
+
+We first apply the following selection cuts to remove false positive and background galaxies.
+They are motivated based on the knowledge of the color distribution of LSBGs \citep[e.g.,][]{SAGA-I,Greco2018,Zaritsky2019,Tanoglidis2021} and survey completeness in size and surface brightness (\S\ref{sec:comp_meas}).
+\begin{itemize}
+    \item Color:
+    \[0.0 < g-i < 1.2,\quad |(g-r) - 0.7\cdot (g-i)| < 0.25\]
+    \item Size: \[1.8 \arcsec < r_e < 12 \arcsec\]
+    \item Surface brightness: \[\mu_0(g) > 22.5,\quad 23.0 < \sbeff < 27.5\ \sbunit.\]
+\end{itemize}
+The color cuts here are more restrictive than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and high redshift galaxies.
+We not only remove objects with small sizes, but also exclude objects with large size and very low surface brightness because they are mostly \code{junk}.
+After such cuts, there are 200 \code{junk} and 1407 \code{non-junk} remaining.
+The color-size-surface brightness cuts removes 88\% of \code{junk} and 58\% of \code{non-junk}.
+We note that although we lose a lot of \code{non-junk} objects, most of them are small, red  objects which are not likely to be LSBGs of our interest.
 
@@
 \end{figure}
-
-To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the classification results to help construct the metrics.
-To be specific, we randomly select 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ from the NSA catalog (see \S\ref{sec:match} for details).
-We run vanilla \code{scarlet} for all of them and measure morphological parameters as described above.
-Then we do visual inspection of the $griz$ color-composite images with 0.5 arcmin on a side.
-False positives, including tidal streams, galaxy outskirts blends, and other artifacts (dubbed \code{junk}), are identified during the visual inspection by coauthors JEG, JG, SH, RB, KC, AG, and EKF.
-Each object has been inspected by at least one person.
-In the end, we combine the votes from different people.
-An object is classified as \code{junk} if the number of votes as \code{junk} is larger than the number of votes as \code{non-junk}.
-In total, there are 1661 objects classified as \code{junk}.
-The visual inspection is summarized in Table \ref{tab:deblending_vis}.
-
-We first apply the following selection cuts to remove false positive and background galaxies.
-They are motivated based on the knowledge of the color distribution of LSBGs \citep[e.g.,][]{SAGA-I,Greco2018,Zaritsky2019,Tanoglidis2021} and survey completeness in size and surface brightness (\S\ref{sec:comp_meas}).
-\begin{itemize}
-    \item Color:
-    \[0.0 < g-i < 1.2,\quad |(g-r) - 0.7\cdot (g-i)| < 0.25\]
-    \item Size: \[1.8 \arcsec < r_e < 12 \arcsec\]
-    \item Surface brightness: \[\mu_0(g) > 22.5,\quad 23.0 < \mu_{\rm eff}(g) < 27.5.\]
-\end{itemize}
-The color cuts here are more restrictive than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and high redshift galaxies.
-We not only remove objects with small sizes, but also exclude objects with large size and very low surface brightness because they are mostly \code{junk}.
-After such cuts, there are 200 \code{junk} and 1407 \code{non-junk} remaining.
-The color-size-surface brightness cuts removes 88\% of \code{junk} and 58\% of \code{non-junk}.
-We note that although we lose a lot of \code{non-junk} objects, most of them are small, red  objects which are not likely to be LSBGs of our interest.
 
@@
 \begin{deluxetable}{lccc}
-\tablecaption{The number of objects remained after each deblending cut}
+\tablecaption{The number of objects remaining after each deblending cut}
 \tablewidth{6cm}
@@
 
-% Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with the positions of detected peaks.
-
 Although the vanilla \code{scarlet} modeling provides useful information to help us remove false positives, it does not necessarily give us reliable estimations on size, color, total magnitude, etc.
 In fact, the vanilla \code{scarlet} model systematically under-estimates the size and total flux of LSB objects.
-This is because the faint outskirts of LSBGs are typically not modeled well due to the non-parametric nature of vanilla \code{scarlet}.
+This is because non-parametric modeling cannot capture the faint outskirts of LSBGs very well.
 When doing parametric modeling such as \sersic{} fitting, we effectively apply radial averaging within elliptical annuli and boost the signal-to-noise ratio by binning pixels.
-In other words, pixels within the same isophotal annulus are assumed to have the same intensity and thus are strongly correlated.
+In this case, pixels within the same isophotal annulus are assumed to have the same intensity and thus are strongly correlated.
 However, the non-parametric nature of vanilla \code{scarlet} only assumes monotonicity, which imposes quite weak correlations among pixels.
@@
 Furthermore, the monotonicity constraint stops the model from growing in certain directions if there is another source along this direction.\footnote{This issue can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model of the target object never exceeds the other objects next to it.} As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biasing the measurements.
-In the following, we explore a novel method to perform robust parametric modeling and measurement while exploiting the deblending power of \code{scarlet}.
+In the following, we explore a novel method to perform robust parametric modeling and measurement for LSBGs.
 
 A traditional way of doing parametric modeling is to mask out contaminants based on the detection segmentation map and fit a model to the masked image.
-However, such fitting results are very sensitive to the masking scheme \citep[e.g.,][]{Greco2018} and sky background.
-A possible solution to this problem is to simultaneously model all the objects in the cutout and the sky using parametric models (e.g., in DECaLS, \citealt{Lang2016,Dey2019}).
+However, such fitting results are very sensitive to the masking scheme and sky background \citep[e.g.,][]{Greco2018}.
+A possible solution to this problem is to simultaneously model all the objects in the cutout and the sky using parametric models \citep[e.g.,][]{Lang2016,Dey2019}.
 In this work, we combine the advantage of parametric modeling with the power of deblending in \code{scarlet}.
@@
 The Spergel profile is motivated by having a simple analytical expression in Fourier space, making it easy to convolve with a PSF.
-Similar to the \sersic{} index, the parameter $\nu$ in \eqref{eq:spergel} (the ``Spergel index'') controls the concentration of the light profile.
+Similar to the \sersic{} index, the parameter $\nu$ in Equation \eqref{eq:spergel} (the ``Spergel index'') controls the concentration of the light profile.
 As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is relevant to the study of LSBGs.
 
-We initialize the Spergel model for the target object differently, while other objects are still initialized in the same way as in the deblending step (Section \ref{sec:deblending}).
+While other objects are initialized in the same way as in the deblending step (Section \ref{sec:deblending}), we initialize the Spergel model for the target object differently.
 First, we initialize a vanilla \code{scarlet} model for the target object, and we measure the effective radius $r_e$, total flux, and the shape of the scarlet model.
-We use these numbers to initialize the Spergel profile.
-The size of the bounding box is also updated to be the maximum between 250 pixels and $10\, r_e$.
-Peaks within this bounding box (other than the target) are modeled using vanilla \code{scarlet}.
+The size of the bounding box of is also updated to be the maximum between 250 pixels and $10\, r_e$.
 For the target, we still require a positivity constraint, and the monotonicity is automatically satisfied by the Spergel profile.
@@
 The completeness drops as we go to fainter surface brightness and smaller size.
-In a size range of $3\arcsec < r_e < 14\arcsec$, we are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
+For a size range of $3\arcsec < r_e < 14\arcsec$, we are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
 	}
@@
 We perform a large suite of image simulations to derive the completeness.
-We inject single \sersic{} light profile \citep{Sersic1963} into the coadd images and try do recover them using the detection method (\S\ref{sec:detection}), model them using vanilla \code{scarlet} (\S\ref{sec:deblending}), and apply the deblending cuts.
+We inject single \sersic{} light profile \citep{Sersic1963} into the coadd images and try to recover them using the detection method (\S\ref{sec:detection}), model them using vanilla \code{scarlet} (\S\ref{sec:deblending}), and apply the deblending cuts.
 The mock \sersic{} galaxies span a wide range in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$) and surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$).
@@
 The completeness drops as we go to fainter surface brightness and smaller size.
-We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
+For the size range of $3\arcsec < r_e < 14\arcsec$, we are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
 Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness.
@@
 \citet{Tanoglidis2021} conducted an LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
-\citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but much smaller completeness above $\sbeff > 26.5\ \sbunit$.
+\citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but a much smaller completeness above $\sbeff > 26.5\ \sbunit$.
 The Dragonfly Wide Field Survey \citep{Danieli2020} reaches $\sim 29\ \sbunit$ for $>3\sigma$ detection on scales $\sim 1\arcmin$, which is deeper than all other surveys by sacrificing spatial resolution.
@@
 	}
-    \caption{The measurement bias and uncertainty as a function of measured angular size $r_e$ and surface brightness $\sbeff$.
+    \caption{The measurement bias (defined as truth $-$ measurement) and uncertainty as a function of measured angular size $r_e$ and surface brightness $\sbeff$.
 The colors show the bias term while the dashed contours show the constant uncertainty lines.
@@
 For surface brightness fainter than $>27\ \sbunit$, the measured size can be much smaller than the truth.
-As a result, the measured total magnitude $m$ and average surface brightness $\overline{\mu}_{\rm eff}$ are also too low.
+As a result, the measured total magnitude $m$ is also too low.
+For the measured average surface brightness $\overline{\mu}_{\rm eff}$, the trade-off between magnitude and size biases makes it less biased than the total magnitude.
 Similar to \citet{Zaritsky2021}, we derive the measurement bias and uncertainties in size, surface brightness, total magnitude, and color as a function of size and surface brightness.
 We refer interested readers to Appendix \ref{ap:comp_meas_unc} for details.
-The main results are shown in Figure \ref{fig:meas_err}, where the colors show the bias terms as a function of the measured size and surface brightness.
+The main results are summarized in Figure \ref{fig:meas_err}, where the colors show the bias terms as a function of the measured size and surface brightness.
 The size and surface brightness bias grows with increasing surface brightness.
@@
 We find the bias in $g-i$ color to be quite small.
-The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the bias.
-We set the minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
-
-In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on bias-corrected properties.
-We also incorporate the measurement errors into the science figures.
+The $1\sigma$ measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the bias.
+We set the minimum uncertainties to be $\sigma(r_e) \geqslant 0.3\arcsec,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05\ \sbunit,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
+
+In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on the bias-corrected properties. 
+% We also incorporate the measurement errors into the science figures. 
 The values presented in our catalogs (Table \ref{tab:catalog}) are already bias-corrected, but we do provide the bias values for reference.
@@
 These methods are also complemented by recent machine learning techniques \citep{Baxter2021,xSAGA-I}.
-In this Section, we cross-match our LSBG catalog with MW-like galaxies in the NSA catalog.
+
+In this section, we cross-match our LSBG catalog with MW-like galaxies in the NSA catalog.
 For the LSBGs matched with MW analogs, we run the deblending step to exclude false positives (\S\ref{sec:deblending}) and then run Spergel modeling to measure the properties of LSBGs (\S\ref{sec:modeling}).
 In the end, we construct the samples of mass-size outliers among the satellites of MW analogs.
+Table \ref{tab:steps_flow} summarizes the number of objects after each step.
 
@@
 Going to higher redshift will make it more difficult to detect low-mass dwarfs.}.
-We also exclude galaxies $z<0.01$ because (1) the number of UDGs will be very small due to the small volume; (2) their large angular size makes them more vulnerable to being shredded during detection, so including them will introduce a number of spurious LSB objects.
+We also exclude galaxies at $z<0.01$ because (1) the number of mass-size outliers will be very small due to the small volume; (2) their large angular size makes them more vulnerable to being shredded during detection, so including them will introduce a number of spurious LSB objects.
 We do not discriminate between isolated or paired hosts.
-%Our LSBG sample complements the ELVES sample and SAGA sample in our redshift range.
 
@@
 
-However, a significant fraction of spurious objects remain in this cross-matched LSBG sample, including galactic cirrus, tidal streams, shredded large galaxies, and compact sources blended with galaxy outskirts.
+% However, a significant fraction of spurious objects remain in this cross-matched LSBG sample, including galactic cirrus, tidal streams, shredded large galaxies, and compact sources blended with galaxy outskirts.
 As described in \S\ref{sec:deblending}, we then perform a deblending step to effectively remove spurious objects.
@@
 For example, a galaxy with $r_e = 1.5$ kpc is very extended if its stellar mass is $10^7\ M_\odot$, but is normal-sized if its stellar mass is $10^{8.5}\ M_\odot$.
-Thus, a more intuitive definition for diffuse and puffy dwarf galaxies (i.e., mass-size outliers) would be based on a mass-size relation and its scatter.
+Thus, a more intuitive definition for puffy dwarf galaxies (i.e., mass-size outliers) would be based on a mass-size relation and its scatter.
 Following this thread, we propose a new definition for mass-size outliers dubbed as \textit{ultra-puffy galaxies} (UPGs).
 In this section, we describe the definitions of UPG and contrast it with UDG, then we select UDGs and UPGs from our LSBGs matched with MW hosts.
-% Ideally, galaxies that are $1.5\sigma$ or $2\sigma$ above the average mass-size relation represent the large-size tail of the population in a homogeneous manner.
+The catalogs and mosaic images of UDGs and UPGs are available online\footnote{\url{https://astrojacobli.github.io/research/BeyondUDG/}}.
 
@@
 Taking the measured average mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.25\, \log\, (M_\star/M_\odot) + 1.07$ and a scatter of $\sigma=0.18$ dex, we define a population of ultra-puffy galaxies to be galaxies that are $>1.5\sigma$ above the average mass-size relation.
+We note that the mass-size relation in \citet{ELVES-I} is derived for a mass range of $10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$, so the mass-size relation is extrapolated to $M_\star \sim 10^9\ M_\odot$ to define our UPG sample.
 We choose $1.5\sigma$ because it gives us a statistically significant sample.
 One can certainly select $>2\sigma$ or $>3\sigma$ UPGs if a larger LSBG sample is available.
-The UPGs are not absolutely large in size or absolutely faint in surface brightness, but they are outliers in size for their stellar masses\footnote{A UPG with $M_\star = 10^7\ M_\odot$ has a size larger than 1.2 kpc and surface brightness fainter than $\sbeff > 25.5\ \sbunit$ for $g-i=0.4$ and $\sbeff > 26.8\ \sbunit$ for $g-i=0.8$.
-A UPG with $M_\star = 10^{8.5}\ M_\odot$ has a size larger than 2.7 kpc and surface brightness fainter than $\sbeff > 23.7\ \sbunit$ for $g-i=0.4$ and $\sbeff > 25.0\ \sbunit$ for $g-i=0.8$.}.
+The UPGs are not absolutely large in size or absolutely faint in surface brightness, but they are outliers in size for their stellar masses.
+For example, a UPG with $M_\star = 10^7\ M_\odot$ has a size larger than 1.2 kpc and surface brightness fainter than $\sbeff > 25.5\ \sbunit$ for $g-i=0.4$ and $\sbeff > 26.8\ \sbunit$ for $g-i=0.8$.
+A UPG with $M_\star = 10^{8.5}\ M_\odot$ has a size larger than 2.7 kpc and surface brightness fainter than $\sbeff > 23.7\ \sbunit$ for $g-i=0.4$ and $\sbeff > 25.0\ \sbunit$ for $g-i=0.8$.
 The definition of UPG based on the observed mass-size relation is physically-motivated, and better allows us to study size outliers at a given stellar mass.
@@
 
-There are 362 LSBG candidates that fall $1.5\sigma$ above the ridge line of the mass-size relation.\footnote{We note that the mass-size relation in \citet{ELVES-I} is derived for a mass range of $10^{5.5}\ M_\odot < M_\star < 10^{8.5}\ M_\odot$.
-We extrapolate the mass-size relation to $M_\star \sim 10^9\ M_\odot$ to define our UPG sample.} After removing spurious objects by visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
+There are 362 LSBG candidates that fall $1.5\sigma$ above the ridge line of the mass-size relation.
+After removing spurious objects by another round of visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
 These UPGs are associated with 239 hosts.
 The total sky area occupied by UPG hosts (out to 1 $R_{\rm{vir}}$) is 32.37 deg$^{2}$.
-The catalogs are available in machine-readable format online\footnote{\url{https://github.com/AstroJacobLi/kuaizi/blob/master/data/}}.
-We demonstrate the catalog format in Table \ref{tab:catalog}.
+The catalogs are available online, and we demonstrate the catalog format in Table \ref{tab:catalog}.
 
@@
 \subsubsection{UDGs}
-Albeit the advantage of UPGs, there are very little literature on UPGs for us to compare with.
-Thus, we also select a UDG sample from our LSBGs in order to compare with existing observations and simulations in different environments.
+We also select a UDG sample from our LSBGs in order to compare with existing observations and simulations in different environments.
 The UDG sample is usually defined based on surface brightness and physical size of the galaxy.
@@
 \subsection{Background contamination fraction}\label{sec:bkg}
-% The major weakness of LSBG searches in imaging data is that distance information is typically unknown. 
 Although we have matched LSBGs to MW analogs by proximity, the physical affiliation of LSBGs to the host is not guaranteed.
@@
 Given the volume probed by our search, contamination is most likely to be dominated by background galaxies.
-In thie section, we try estimate the contamination fraction empirically by randomly matching LSBGs to our MW hosts and measuring the number density of apparent UPG and UDG.
+In this section, we try to estimate the contamination fraction empirically by randomly matching LSBGs to our MW hosts and measuring the number density of apparent UPG and UDG.
 
 We randomly select a continuous patch of sky of 24 deg$^{2}$ in HSC PDR2 regardless of whether it contains MW analogs\footnote{$345\ \deg < \rm{R.A.} < 351\ \deg$, $-1.5\ \deg < \rm{Dec} < 2.5\ \deg$, which is not dominated by Galactic cirrus and stars.
-Such a patch of sky with 24 deg$^2$ is already enough for us to derive a background contamination fraction with small Poisson error.}.
-Then we perform the same deblending and modeling steps for the 2,707 LSBGs detected in this region.
+Such a patch of sky with 24 deg$^2$ is already enough for us to derive a background contamination fraction with small Poisson noise.}.
+Then we perform the same deblending and modeling steps for the 2,707 LSBG candidates detected in this region.
 We also removed objects that are already in our mass-size outlier samples and objects with completeness less than 0.1.
-Furthermore, we also did the same visual inspection as for UDGs and UPGs to remove false positives.
+We also did the same visual inspection as for UDGs and UPGs to remove false positives.
 In the end, there are 480 LSBGs (excluding false positives) representing a population of possible contaminants for the UDG and UPG samples.
@@
 For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 16\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 20\%$.
-We take the contamination fraction into account when calculating the abundances (\S\ref{sec:results}).
-
-% One of the main goals of this paper is to study the star-forming properties of mass-size outliers in satellites of MW analogs.
-The star formation rate of galaxies can be indicated by their broad-band colors, and we use color to calculate the quenched fraction of UDGs and UPGs (see \S \ref{sec:quench} for more details).
-However, background contaminants affect the color distribution of the UDG (UPG) sample, and thus affect the calculated quenched fraction.
-If the fake UDGs (UPGs) have different properties from the real ones, we can use this information to derive a probability that an object is a real UDG (UPG) at the proposed distance.
-% If the fake UDGs (UPGs) span a different region from the true UDGs in the observable space, we can use these observables to assign weights to each object in our UDG sample indicating the possibility of being a true UDG.
-% Indeed, we find that the $g-i$ color distribution of the fake UDG (UPG) sample is bluer than that of the true UDG (UPG) sample, which motivates us to assign importance weights based on the $g-i$ color.
-Taking UDGs as an example, we first compute the normalized histograms of $g-i$ colors (denoted as $\lambda_k$ at the $(g-i)_{k}$ bin) for both true UDG and fake UDG samples.
-Then we multiply $f_{\rm contam}^{\rm UDG}$ with the histogram of fake UDG sample ($\lambda_k^{\rm fake}$) such that the histogram sums up to the average contamination fraction.
-The weight assigned to UDGs in color bin $(g-i)_k$ is estimated to be $w_k = \max\,(1 - f_{\rm contam} \lambda_k^{\rm fake} / \lambda_k^{\rm true}, 0)$.
-This weight stands for a possibility of not being a contaminant.
-The weights of UPGs are assigned following the same procedure.
-We find this color-based contamination subtraction scheme is sufficient for this work since the contamination fraction is small.
-%Our main results shown in Section \ref{sec:quench} are robust against contamination subtraction.
+We take the contamination fraction into account when calculating the abundances in \S\ref{sec:results}.
 
@@
 \subsection{Properties of mass-size outliers}\label{sec:mass-size}
-\begin{figure*}
-	\vbox{ 
-		\centering
-		\includegraphics[width=1\linewidth]{udg_upg_sample.pdf}
-	}
-    \caption{The distribution ultra-diffuse galaxies (UDGs, \textit{left}) and ultra-puffy galaxies (UPGs, \textit{right}) on the size-surface brightness plane.
-The UPGs are defined to be galaxies that are $1.5\sigma$ above the average mass-size relation in \citet{ELVES-I}.
-The samples are split into two color bins and shown in red ($g-i>0.8$) and blue ($g-i<0.8$).
-The marginal histograms are not normalized to highlight the relative number of red and blue galaxies.
-Compared with the UDG sample, the UPG sample includes blue galaxies with surface brightness higher than the UDG cut ($\sbeff < 25\ \sbunit$) and excludes red galaxies at $25 < \sbeff < 26\ \sbunit$, due to the color-$M_*/L$ dependence.
-    }
-    \label{fig:udg_upg_re_mu}
-\end{figure*}
 
@@
 
-In order to build a more comprehensive understanding of our UDG and UPG sample, we show their distributions on the size-surface brightness plane in Figure \ref{fig:udg_upg_re_mu}.
-The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively.
-We note that we do not apply any background contamination correction in Figure \ref{fig:udg_upg_re_mu} because such corrections can only be done in a statistical sense.
-The error bars correspond to $1\sigma$ measurement uncertainties (\S\ref{sec:comp_meas}).
-Some galaxies with sizes smaller than 1.5 kpc are still scattered into the UDG sample because their sizes have large uncertainty.
-The two marginal plots show the unnormalized histograms of galaxies in the two color bins.
-The numbers of red and blue galaxies are similar in the UDG sample, but there are more blue galaxies than red ones in the UPG sample.
-Since there is no hard surface brightness cut for UPGs, the UPG sample includes many blue galaxies with brighter surface brightness ($23 \lesssim \sbeff < 25\ \sbunit$).
-For blue UPGs (shown as blue dots), the apparent correlation between $\sbeff$ and $r_e$ is merely due to the fact that blue UPGs pile up around the $1.5\sigma$ line above the mass-size relation.
-
-Due to the surface brightness cut ($\sbeff > 23.0\ \sbunit$) in the deblending step, there is little chance for an LSB disk galaxy with a bright bulge to scatter into the UPG sample.
-The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26\ \sbunit$ because their stellar masses are high but their sizes are too small to be mass-size outliers.
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=1\linewidth]{udg_upg_sample.pdf}
+	}
+    \caption{The distribution ultra-diffuse galaxies (UDGs, \textit{left}) and ultra-puffy galaxies (UPGs, \textit{right}) on the size-surface brightness plane.
+The UPGs are defined to be galaxies that are $1.5\sigma$ above the average mass-size relation in \citet{ELVES-I}.
+The samples are split into two color bins and shown in red ($g-i>0.8$) and blue ($g-i<0.8$).
+The marginal histograms are not normalized to highlight the relative number of red and blue galaxies.
+Compared with the UDG sample, the UPG sample includes blue galaxies with surface brightness higher than the UDG cut ($\sbeff < 25\ \sbunit$) and excludes red galaxies at $25 < \sbeff < 26\ \sbunit$, due to the color-$M_\star/L$ dependence.
+    }
+    \label{fig:udg_upg_re_mu}
+\end{figure*}
 
@@
 
-In the left panel of Figure \ref{fig:mass_size}, the dark green dashed line shows the average mass-size relation from \citep{ELVES-I}, and the lighter green line shows $1.5\sigma$ above the average mass-size relation assuming the scatter of the mass-size relation to be $\sigma=0.18$ dex \citep{ELVES-I}.
+In the left panel of Figure \ref{fig:mass_size}, the green dashed lines show the average mass-size relation and $1.5\sigma$ above it.
 UPGs would lie above the $1.5\sigma$ line by construction, and there will be overlap between UDGs and UPGs.
@@
 Blue triangles correspond to UPGs that are not classified as UDGs.
-Limited by the detection limit and the fact that our hosts lie beyong the Local Volume, our mass limit is $M_\star \approx 10^{6.8}\ M_\odot$, which is $\sim 1$ dex higher than ELVES.
+Limited by the detection limit and the fact that our hosts lie beyond the Local Volume, our mass limit is $M_\star \approx 10^{6.8}\ M_\odot$, which is $\sim 1$ dex higher than ELVES.
 Compared with the UPG sample, we find that the UDG sample (orange squares + red stars) comprises a number of galaxies below the $1.5\sigma$ line, but also loses several low-mass galaxies that are above $1.5\sigma$ line but have sizes smaller than 1.5 kpc.
@@
 On the contrary, since the UPG definition does not have a hard surface brightness cut, it includes many galaxies that are more massive than UDGs provided they have an extraordinarily large size.
-As a consequence, background spiral galaxies could dominate the UPG sample at the high-mass end.
+We also note that the mass-size relation from \citet{ELVES-I} is extrapolated to define UPGs in $10^{8.5}\ M_\odot < M_\star < 10^9\ M_\odot$, where about 10\% our UPGs are located in.
+However, the mass-size relation might show color and morphology dependence for $M_\odot > 10^{8.5}\ M_\odot$.
+As a consequence, disk galaxies might contribute to the UPG sample at the high-mass end.
+
+We also show the UDG and UPG samples on the size-surface brightness plane in Figure \ref{fig:udg_upg_re_mu}.
+The galaxies are split into two color bins and are shown in blue ($g-i < 0.8$) and red ($g-i > 0.8$), respectively.
+We do not apply any background contamination correction in Figure \ref{fig:udg_upg_re_mu} because such corrections can only be done in a statistical sense.
+The error bars correspond to $1\sigma$ measurement uncertainties (\S\ref{sec:comp_meas}).
+The two marginal plots show the unnormalized histograms of galaxies in the two color bins.
+The numbers of red and blue galaxies are similar in the UDG sample, but there are more blue galaxies than red ones in the UPG sample.
+Since there is no hard surface brightness cut for UPGs, the UPG sample includes many blue galaxies with brighter surface brightness ($23 \lesssim \sbeff < 25\ \sbunit$).
+For blue UPGs (shown as blue dots), the apparent correlation between $\sbeff$ and $r_e$ is merely due to the fact that blue UPGs pile up around the $1.5\sigma$ line above the mass-size relation.
+Due to the surface brightness cut ($\sbeff > 23.0\ \sbunit$) in the deblending step, there is little chance for an LSB disk galaxy with a bright bulge to scatter into the UPG sample.
+The UPG sample also loses a significant fraction of red galaxies at $25 < \sbeff < 26\ \sbunit$ because their stellar masses are high but their sizes are too small to be mass-size outliers (i.e., red stars in Figure \ref{fig:mass_size}).
 
@@
 After including more measurements at the lower halo mass end, the power-law is shallower than the relation reported in \citet{vdBurg2017}.
-\textit{Right}: We split the UDG sample into bins based on the host halo mass (triangles) and $g-i$ color (pentagons).
+\textit{Right}: We split the UDG sample into bins based on the host halo mass (circles) and $g-i$ color (diamonds).
 The UDG abundance is higher for more massive host and redder host.
@@
 
-Taking all data points from literature (as shown in Figure \ref{fig:n_udg}), we use the orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the red dashed line in Figure \ref{fig:n_udg}.
+Taking all data points from literature (as shown in Figure \ref{fig:n_udg}), we use the orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the red solid line in Figure \ref{fig:n_udg}.
 The slope of the power law is shallower than \citet{vdBurg2017} ($\beta=1.11\pm0.07$) but steeper than \citet{Roman2017b} ($\beta=0.85\pm0.05$).
-\citet{ManceraPina2018} survey eight clusters and find sublinear power laws.
-Recently \citet{Karunakaran2022b} perform a similar analysis including SAGA and ELVES and find a slightly shallower power law of $\beta=0.87\pm0.07$.
-Since most individual studies do not have a statistical estimation for background contamination and completeness, the UDG abundances for large groups should be interpreted as lower limits.
-One major caveat in such studies is that most literature results are not completeness corrected and background subtracted, and these effects could significantly bias the results when combing them together.
+\citet{ManceraPina2018} survey eight clusters and find sublinear power law.
+Recently \citet{Karunakaran2022b} perform a similar analysis including SAGA, ELVES, and \citet{Nashimoto2022} and find a slightly shallower power law of $\beta=0.87\pm0.07$.
+We note that their surface brightness cut for UDGs is brighter than ours and thus they include more ``UDGs'' for MW-like hosts and have a shallower power law.
+One should be aware of the fact that literature results are not completeness corrected and background subtracted, and UDG definition also varies in different studies.
+These effects could significantly bias the results when combing them together.
 Therefore we caution that the power law index here should not be over-interpreted.
-% Among these studies, only \citet{vdBurg2017} applies a background subtraction and completeness correction to the raw counts.
-% If completeness is applied, it is possible that the slope $\beta$ will be steeper than what we are showing in Figure \ref{fig:n_udg}.
-
-In the right panel of Figure \ref{fig:n_udg}, we split the UDG sample into different bins based on their host halo mass (shown as triangles) and host color (shown as pentagons).
+
+In the right panel of Figure \ref{fig:n_udg}, we split the UDG sample into different bins based on their host halo mass (shown as circles) and host color (shown as diamonds).
 We find that the UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger with host color.
@@
 We denote this quantity as the UDG (UPG) fraction hereafter, which characterizes the tail of the size distribution of satellites.
-In order to calculate this fraction, we assume that MW analogs have $\sim 6$ satellites with $M_\star > 10^{6.5}\ M_\odot$ \citep{CarlstenELVES2022}.
+In order to calculate this fraction, we assume that MW analogs have $\sim 6 \pm 1$ satellites with $M_\star > 10^{6.5}\ M_\odot$ \citep{CarlstenELVES2022}.
 This lower limit in stellar mass is roughly our detection limit (see Fig.
 \ref{fig:mass_size}).
-Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.15$ and $f_{\rm UPG} \approx 0.10$.
+Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.12 \pm 0.03$ and $f_{\rm UPG} \approx 0.10 \pm 0.03$.
 In ELVES, among 351 satellites with secure distances in 30 MW analogs, we identify 13 UDGs associated with 10 hosts, and 36 UPGs associated with 20 hosts.
-Thus the UDG fraction in ELVES is $f_{\rm UDG}^{\rm ELVES} \approx 0.04$, the UPG fraction in ELVES is $f_{\rm UPG}^{\rm ELVES} \approx 0.10$.
+Thus the UDG fraction in ELVES is $f_{\rm UDG}^{\rm ELVES} \approx 0.04 \pm 0.01$, the UPG fraction in ELVES is $f_{\rm UPG}^{\rm ELVES} \approx 0.10 \pm 0.02$.
+We further select ELVES galaxies with $M_\star > 10^{6.5}\ M_\odot$ and find the same UDG and UPG fractions.
 We also compare our results with results in the Virgo cluster.
-Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}), there are 15 UDGs and 24 UPGs out of 404 identified satellites (with no completeness correction).
-Thus their UDG (UPG) fraction is $f_{\rm UDG}^{\rm Virgo} \approx 0.04$ and $f_{\rm UPG}^{\rm Virgo} \approx 0.06$.
+Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}) and only consider satellites with $M_\star > 10^{6.5}\ M_\odot$, there are 14 UDGs and 17 UPGs out of 218 identified satellites (with no completeness correction).
+Thus their UDG (UPG) fraction is $f_{\rm UDG}^{\rm Virgo} \approx 0.06\pm 0.02$ and $f_{\rm UPG}^{\rm Virgo} \approx 0.08\pm 0.02$.
 However, we note that \citet{Ferrarese2020} only survey the central 4 deg$^2$ of the Virgo cluster, which probably biases the UDG (UPG) fraction.
 It seems that our UDG fraction is higher than both ELVES and NGVS.
-Our UPG fraction is consistent with ELVES but higher than NVGS.
+Our UPG fraction is consistent with ELVES and NVGS.
 A systematic and careful comparison on UDG (UPG) fraction in different environments is needed in the future.
 
-\jiaxuan{We note that ELVES probes less massive dwarfs than our search. }
-
-\section{Discussion: robust identification of mass-size outliers}\label{sec:discussion}
-
-% \subsection{}\label{sec:artifact}
-% In this paper, we propose a robust definition of mass-size outliers (the UPGs). Here we contrast UPGs with UDGs to elaborate the fact that UPGs better represent mass-size outliers.
-
-% We also discuss the advantages and disadvantages of different definitions of low surface brightness galaxies including UDG and UPG.
+\section{Robust identification of mass-size outliers}\label{sec:discussion}
 
@@
 In this work, we perform a search for low surface brightness galaxies in HSC PDR2 data and construct samples for mass-size outliers around MW analogs at $0.01 < z < 0.04$.
-Besides the ultra-diffuse galaxies, we propose studying ``ultra-puffy galaxies'' which is defined to be $1.5\sigma$ above the average mass-size relation.
+Besides the ultra-diffuse galaxies, we define ``ultra-puffy galaxies'' to be $1.5\sigma$ above the average mass-size relation.
 We calculate the abundances of mass-size outliers and compare with literature.
@@
     \item Using the HSC PDR2 data ($\sim 300\ \mathrm{deg}^{2}$), we conduct a systematic search for LSBGs using the method in \citet{Greco2018} complemented by our new deblending and modeling methods.
-Utilizing the non-parametric models generated by \code{scarlet}, we design a metric based on morphological parameters to effectively rule out false positives in the LSBG detection.
-We measure the structural properties of LSBGs using the Spergel profile and carefully characterize the measurement biases and uncertainties.
+Utilizing the non-parametric models generated by \code{scarlet}, we design a metric based on morphological parameters to effectively remove false positives in the initial LSBG sample.
+We measure the structural properties of LSBGs using parametric modeling and carefully characterize the measurement biases and uncertainties.
 The completeness of the search is also derived by injecting mock galaxies.
@@
 
-    \item For a MW analog, on average, about 15\% of its satellites are UDGs and about 10\% of its satellites are UPGs.
-The UDG and UPG fractions are slightly higher than those in ELVES and NGVS, which do not correct for completeness and suffer from small number statistics due to their sample sizes.
-
-    \item We advocate the concept of UPG which is more physically motivated, does not introduce artifacts in the mass-size distribution, and better represents the large-size tail of dwarf galaxy population.
+    \item For a MW analog, on average, about 12\% of its satellites are UDGs and about 10\% of its satellites are UPGs.
+Although the UPG fraction is consistent with ELVES and NGVS, the UDG fraction is found to be higher than those in ELVES and NGVS, which are not corrected for completeness and suffer from small number statistics.
+
+    \item We advocate the concept of UPG which is physically-motivated, does not introduce artifacts in the mass-size distribution, and better represents the large-size tail of dwarf galaxy population.
 \end{enumerate}
@@
 The authors thank Yao-Yuan Mao for his \href{https://github.com/yymao/decals-image-list-tool}{tool} for visualizing the image cutouts.
-
-{\bf JEG needs to add her grant here}
-
-J.H.K acknowledges the support from the National Research Foundation of Korea (NRF) grant, No. 2021M3F7A1084525, funded by the Korea government (MSIT).
+JEG gratefully acknowledges support from NSF grant AST-1007052.
+J.H.K acknowledges the support from the National Research Foundation of Korea (NRF) grant, No.
+2021M3F7A1084525, funded by the Korea government (MSIT).
 
@@
           \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph},
-        %   \href{https://halotools.readthedocs.io/en/latest}{\code{Halotools}} \citep{Hearin2017},
           \href{https://bdiemer.bitbucket.io/colossus/index.html}{\code{Colossus}} \citep{Colossus},
@@
 In \citetalias{Greco2018}, the thresholds are set based on the noise level of the local sky.
-Thanks to the global sky subtraction in HSC PDR2, LSB features are well conserved after subtracting the sky and the sky noise level varies less.
+Thanks to the global sky subtraction in HSC PDR2, LSB features are well conserved after subtracting the sky and the sky noise level varies less than in prior reductions.
 We therefore set the thresholds based on the characteristic surface brightness instead of a certain sigma value above the sky background.
@@
 The ACT ratio essentially characterizes the peakiness of the source.
-Peaky sources have higher ACT ratios, thus we remove point-like sources by applying a cut on the ACT ratio $a_{\rm corr} < 2.5$.
+We expect extended LSBG to have a strong correlation across a large number of pixels, making the ACT less peaky than point-like sources.
+Thus we apply a cut on the ACT ratio $a_{\rm corr} < 2.5$ to remove point sources.
 This step helps to improve the purity of our sample.
@@
 
-In this appendix, we demonstrate that the Spergel profile can approximate the \sersic{} profile and providee a lookup table for the correspondence between \sersic{} index $n$ and Spergel index $\nu$.
+In this appendix, we demonstrate that the Spergel profile can approximate the \sersic{} profile and provide a lookup table for the correspondence between \sersic{} index $n$ and Spergel index $\nu$.
 
@@
 We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
-
-% \section{Measurement Error}\label{ap:meas_error}
-
-% We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{ap:meas_error}.
-Overall speaking, the measurement agrees with the truth quite well.
-However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$ is under-estiamted.
-We also characterize the bias and the scatter in measurement as a function of size and surface brightness.
-We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.
-
-% vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$, when deriving the completeness (recovered fraction)
-
-% Remember to ref SMUDGES papers here.
 
@@
 $\sigma(\overline{\mu}_{\mathrm{eff}}(g))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(g)$           \\
-% $\overline{\mu}_{\mathrm{eff}}(r)$               & $\sbunit$ & $r$-band average surface brightness within $r_e$ \\
-% $\sigma(\overline{\mu}_{\mathrm{eff}}(r))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(r)$           \\
-% $\overline{\mu}_{\mathrm{eff}}(i)$               & $\sbunit$ & $i$-band average surface brightness within $r_e$ \\
-% $\sigma(\overline{\mu}_{\mathrm{eff}}(i))$       & $\sbunit$ & Uncertainty of $\overline{\mu}_{\mathrm{eff}}(i)$           \\
 $m_g$                    & mag     & $g$-band apparent magnitude     \\
 $\sigma(m_g)$            & mag     & Uncertainty of $m_g$            \\
-% $m_r$                    & mag     & $r$-band apparent magnitude     \\
-% $\sigma(m_r)$            & mag     & Uncertainty of $m_r$            \\
-% $m_i$                    & mag     & $i$-band apparent magnitude     \\
-% $\sigma(m_i)$            & mag     & Uncertainty of $m_i$            \\
 $g-r$                    & mag     & $g-r$ color                     \\

### 2022-10-25 paper1.tex
just did a final read. But have to think more about the sky area used for background subtraction. Is it the area of 250 hosts, or 689 hosts?

@@
 \author[0000-0002-1841-2252]{Shany Danieli}
+\altaffiliation{NASA Hubble Fellow}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
@@
 \begin{abstract}
-Large diffuse galaxies are hard to find, but understanding the environments where they live and their numbers, and ultimately their origins, is of intense interest and important for galaxy formation and evolution.
+Large diffuse galaxies are hard to find, but understanding the environments where they live, their numbers, and ultimately their origins, is of intense interest and importance for galaxy formation and evolution.
 Using Subaru's Hyper Suprime-Cam Strategic Survey Program, we perform a systematic search for low surface brightness galaxies and present novel and effective methods for detecting and modeling them.
 As a case study, we build a large sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$).
-These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represents the tail of the satellite size distribution.
-We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is slightly smaller than the observed abundance at this halo mass in the Local Volume.
+These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represent the tail of the satellite size distribution.
+We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is consistent with the observed abundance at this halo mass in the Local Volume.
 We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.76\pm0.04$ per host.
 With literature results, we confirm that the UDG abundance scales with the host halo mass following a sublinear power law.
-We argue that our definition for ultra-puffy galaxies, which is based on the mass-size relation, is more physically-motivated than the common definition of ultra-diffuse galaxies, which depends on an arbitrary surface brightness cut and thus yields different surface mass density cuts for quenched and star-forming galaxies.
+We argue that our definition for ultra-puffy galaxies, which is based on the mass-size relation, is more physically-motivated than the common definition of ultra-diffuse galaxies, which depends on surface brightness and size cuts and thus yields different surface mass density cuts for quenched and star-forming galaxies.
 \end{abstract}
@@
 In a variety of galaxies in the Universe, there is an interesting subset of galaxies with low surface brightness \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
-Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
-There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}.
-UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus UDGs are outliers in size and surface brightness compared to normal dwarf galaxies.
-A central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation of dwarf galaxies?
+Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019,Danieli2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
+There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Danieli2019DF2,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Pandya2018,Villaume2022}.
+We refer to LSBGs as objects selected purely by surface brightness without distance information.
+When knowing distances, people define UDGs to be galaxies with large sizes ($r_e > 1.5$ kpc) and low surface brightnesses ($\sbcen > 24.0\ \sbunit$), and thus UDGs are outliers in size and surface brightness compared to normal dwarf galaxies.
+A central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation of dwarf galaxies.
 
 Various mechanisms have been proposed to explain the presence of large, diffuse galaxies (as mass-size outliers) across different environments.
-In the field (i.e, in isolation), their large sizes might be caused by stellar feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}.
+In the field (i.e, in isolation), their large sizes might be a result of stellar feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites; \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}.
 In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019}, via adiabatic expansion due to mass loss \citep{Tremmel2020}, or even via a bullet-dwarf collision \citep{vandokkum2022Nat,vanDokkum2022GC}.
@@
 The Exploration of Local VolumE Satellites survey (ELVES,  \citealt{ELVES-I,ELVES-II,CarlstenELVES2022}) uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts.
-Having these MW satellites as a reference frame, we can contrast them with the mass-size outliers in the same environment to understand the formation of large diffuse galaxies.
+Having these satellites of MW analogs as a reference frame, we can contrast them with the mass-size outliers in the same environment to understand the formation of large diffuse galaxies.
 However, there are only $\sim 40$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022,Nashimoto2022,Karunakaran2022b}.
@@
 We further build a large sample of mass-size outliers that are likely satellites of MW-mass hosts in the nearby Universe.
-We propose a new definition for mass-size outliers, dubbed ``\textit{ultra-puffy galaxies}'' (UPGs), based on the observed mass-size relation in the Local Volume using ELVES sample.
+We propose a new definition for mass-size outliers, dubbed ``\textit{ultra-puffy galaxies}'' (UPGs), based on the observed mass-size relation in the Local Volume using the ELVES sample.
 This concept is less affected by the galaxy color and provides a robust avenue to study the mass-size outlier population.
@@
 Section \ref{sec:data} describes the data used in this work.
-In Section \ref{sec:lsbg_search}, we describe the LSBG search in HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), modeling (\S \ref{sec:modeling}), and completeness and uncertainty (\S\ref{sec:comp_meas}).
+In Section \ref{sec:lsbg_search}, we describe the LSBG search in HSC data, including source detection (\S \ref{sec:detection}), deblending (\S \ref{sec:deblending}), modeling (\S \ref{sec:modeling}), completeness, and uncertainty (\S\ref{sec:comp_meas}).
 In Section \ref{sec:sample_construction}, we propose a new definition for large and diffuse galaxies (the UPGs) and present our UDG and UPG samples.
 In Section \ref{sec:results}, we compare the UDGs and UPGs on the mass-size plane.
-We calculate their abundances and compare with literature (\S \ref{sec:n_udg}).
-Based on these results, we further argue why we need to move beyond UDG and adopt the UPG definition in Section \ref{sec:discussion}.
+We calculate their abundances and compare with the literature (\S \ref{sec:n_udg}).
+Based on these results, we further argue that we should move beyond UDGs and adopt the UPG definition in Section \ref{sec:discussion}.
 Section \ref{sec:summary} presents a summary of this work and prospects for the future.
@@
 
-In this work, we refer to LSBGs as objects selected purely by surface brightness without knowing distance information.
-We refer to mass-size outliers (including UDGs and UPGs) as galaxies with large physical sizes compared to normal dwarf galaxies.
+In this work, we refer to mass-size outliers (including both UDGs and UPGs) as galaxies with large physical sizes compared to normal dwarf galaxies.
 We adopt a flat $\Lambda$CDM cosmology from \citet{Planck15} with $\Omega_{\rm m}= 0.307$ and $H_0 = 67.7\ $km s$^{-1}$ Mpc$^{-1}$.
@@
 \section{Data} \label{sec:data}
-\subsection{Hyper Suprime-Cam Subaru Strategic Program}
+\subsection{The Hyper Suprime-Cam Subaru Strategic Program}
 The Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP, \citealt{Aihara2018}; hereafter the HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}.
 The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection).
-HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Vera Rubin Observatory Legacy Survey of Space and Time (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.
+HSC data are processed using  \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Vera Rubin Observatory Legacy Survey of Space and Time (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.
 
@@
 We use the most recent version of the NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$.
-This version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions.
+This version also updates the aperture photometry to elliptical Petrosian photometry which is considered to be more reliable than the photometry used in the older versions.
 In this paper, we use the stellar masses derived from the elliptical Petrosian photometry using \code{kcorrect v4\_2} \citep{Blanton2007}.
-The redshifts of the galaxies in NSA come from several spectroscopic surveys, \ion{H}{1} gas surveys, or direct distance measurements.
+The redshifts of the galaxies in the NSA come from several spectroscopic surveys, \ion{H}{1} gas surveys, or direct distance measurements.
 
@@
 
-Continuing the work of \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies (LSBGs) in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}.
+Continuing the work of \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}.
 The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the search completeness and purity by adding several new steps, which are highlighted in this section.
-We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for the UDG and UPG sample construction.
+We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for the mass-size outlier sample construction.
 
@@
 We use the \code{scarlet} models to define color-size-morphology-surface brightness cuts.
-This step removes roughly 97\% of false positives.
-    \item Modeling (\S \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
-    \item Completeness and measurement uncertainties (\S \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
+This step removes roughly 98\% of false positives.
+    \item Modeling (\S \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their properties including size, total magnitude, and average surface brightness. 
+    \item Completeness and measurement bias and uncertainties (\S \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images and recovering them following the procedures as described above.
 \end{enumerate}
@@
 \citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs.
-We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has a sky subtraction better suited for LSB studies compared to previous data releases.
+We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has a sky subtraction better suited for LSB studies compared to prior data releases.
 We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate the PDR2 data.
@@
 Bright objects and their diffuse light are identified using surface brightness thresholding.
-Then we run a detection using \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} to remove small compact sources and noisy peaks and replace their footprints with sky noise.
-We use \code{SourceExtractor} to detect sources on the ``cleaned'' images with a low detection threshold.
+We run an additional detection using \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} to remove small compact sources and noisy peaks and replace their footprints with sky noise.
+Then we use \code{SourceExtractor} to detect sources on the ``cleaned'' images with a low detection threshold.
 Taking the output catalog from \code{SourceExtractor}, we apply an initial selection based on the size, color, and peakiness of objects.
@@
 We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because HSC PDR2 has a sky subtraction suited for finding LSB features, our detection here is more inclusive of larger objects, and our size cut is less restrictive for small objects.
-Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirrus, and blended compact sources.
+Among these objects, there are still many false positives, including shredded galaxy outskirts, tidal features, Galactic cirrus, and blended compact sources.
 Therefore, we perform an extra ``deblending'' step to further remove false positives.
-
-% {\bf Here you put one PP summarizing the main changes, and then put the rest of the details in 3.1 into Appendix 1.
-End this section with the numbers of targets at the end of this step, and I agree with Erin that having a flow-table with the numbers per step would be nice.}
 
@@
 	\caption{A demonstration of the deblending step as described in \S\ref{sec:deblending} and \S\ref{ap:deblending}.
-Here we show two objects from our initial sample: the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts.
+Here we show two objects from our initial sample: the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection, which is a blend between high-$z$ galaxy and galaxy outskirts.
 The first columns show the $griz$ color-composite images with the bounding boxes overlaid.
@@
 The remaining columns show the initial model, the optimized model (PSF convolved), the residual image, and the optimized model of the target galaxy only.
+The red dashed circle in the rightmost column denotes the measured half-light radius.
 	}
@@
 Our initial detection cannot distinguish them from real LSBGs.
-In order to identify and remove these objects from our sample, we perform non-parametric modeling using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018} and design an efficient metric to remove false positives.
+In order to identify and remove these objects from our sample, we perform non-parametric modeling of all LSBG candidates using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018} and design an effective metric to remove false positives.
 
@@
 \code{Scarlet} is a deblending and modeling tool designed for multi-band and multi-resolution imaging data.
-It utilizes color and morphology information to separate blended objects.
+It utilizes color and morphology information to separate blended objects and model objects in a non-parametric fashion.
 In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation\footnote{\url{https://pmelchior.github.io/scarlet/}} for more details.
 
-In \code{scarlet}, each source $k$ in the cutout is described by a morphology image $S_k$ and a Spectral Energy Distribution (SED) vector $A_k$, and the multi-band images is $Y$.
+In \code{scarlet}, each source $k$ in the cutout is described by a morphology image $S_k$ and a Spectral Energy Distribution (SED) vector $A_k$.
+The multi-band images are represented as $Y$.
 The goal of the modeling is to minimize the objective function $f = \frac{1}{2} ||Y - P \ast (\sum_k A_k^\top \times S_k)||^{2}$ under certain constraints, where $P$ is the PSF and $*$ is convolution.
 The morphology image of each source is limited by a bounding box.
-We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirts (monotonoicity constraint).
+We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirts (monotonicity constraint).
 The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample this assumption still holds for most cases and provides an effective and robust way to deblend overlapping sources.
@@
 
-We use vanilla \code{scarlet} to model the LSBG candidate and the structural and morphological parameters are then used to exclude false positives from our LSBG sample.
-In the following subsections, we briefly describe how we detect peaks on the image to initialize and optimize \code{scarlet} models.
+We use vanilla \code{scarlet} to model the LSBG candidate, and the structural and morphological parameters are then used to exclude false positives from our LSBG sample.
+In the following, we briefly describe how we detect peaks on the image to initialize and optimize \code{scarlet} models.
 We refer the readers to Appendix \ref{ap:deblending} for a more detailed description.
@@
 Then the models are optimized using the adaptive proximal gradient method \citep{Melchior2019}.
-Typically, convergence is achieved after $\sim 50$ steps of optimization and the whole modeling takes about 40s for a typical LSBG.
+Typically, convergence is achieved after $\sim 50$ steps of optimization and the whole modeling process takes about 40s for a typical LSBG.
 
@@
 The one shown in the top panels is a blue LSBG, whereas the one shown on the bottom is a high-$z$ galaxy blended with the outskirts of a nearby galaxy which falls in our initial sample as a false positive.
-The first column shows the $griz$ color-composite image \citep{Lupton2004}, where the white boxes mark the bounding box of each source in the scene.
+%The first column shows the $griz$ color-composite image \citep{Lupton2004}, where the white boxes mark the bounding box of each source in the scene.
 The gray shades over objects outside of the target bounding box indicate they are masked out during fitting.
@@
 
-We notice that the optimized model of the blue LSBG captures its color and morphology quite well.
-For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact.
+We note that the optimized model of the blue LSBG captures its color and morphology quite well.
+For the false-positive case, the optimized model has a notable bright background because we model the sky together with all other sources.
+The model for the target itself is actually very red and compact.
 It passes our initial selection because the galaxy outskirts are shredded by \code{SourceExtractor} and happen to have a large size and similar color to our LSB galaxies.
@@
 
-% {\bf Here I think belongs a paragraph with a high level summary of the steps and how they work, as above.
-So a few sentences on peak detection, model initialization, measurement and false positive removal.
-Then I'd think most of 3.2.1, 3.2.2 could go Appendix, but keeping most of the measurement stuff and visual inspection in the main text.}
-
 \subsubsection{False positive removal}\label{sec:non-par-measurement}
-
 % \begin{figure*}
@@
 But the non-parametric nature of the code means that we have to make additional measurements to quantify the size and shape of the \code{scarlet} model.
-As shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}, we isolate the model of the target object and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}.
+As shown in the rightmost column of Figure \ref{fig:vanilla_scarlet_demo}, we isolate the model of the target object and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}.
 The purpose of this analysis is to extract the structural and morphological parameters of the target object.
@@
 The variance map and PSF are taken from HSC cutouts.
-We also force the sky level in \code{Statmorph} to be zero because sky has already been fit when running vanilla \code{scarlet}.
+We also force the sky level in \code{Statmorph} to be zero because the sky has already been fit when running vanilla \code{scarlet}.
 
@@
 We refer the reader to \citet{statmorph} for more details on their definitions and implementations.
-We measure the morphological and structural parameters in $g$-band.
+All the morphological and structural parameters are measured in the $g$ band.
 
 To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the classification results to help construct the metrics.
-To be specific, we randomly select 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ from the NSA catalog (see \S\ref{sec:match} for details).
-We run vanilla \code{scarlet} for all of them and measure morphological parameters as described above.
+More specifically, we randomly select 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ from the NSA catalog (see \S\ref{sec:match} for details).
+We run vanilla \code{scarlet} for all of them and measure the structural and morphological parameters as described above.
 Then we do visual inspection of the $griz$ color-composite images with 0.5 arcmin on a side.
-False positives, including tidal streams, galaxy outskirts blends, and other artifacts (dubbed \code{junk}), are identified during the visual inspection by coauthors JEG, JG, SH, RB, KC, AG, and EKF.
+False positives, including tidal streams, galaxy outskirts, blends, and other artifacts (dubbed \code{junk}), are identified during the visual inspection by coauthors JEG, JG, SH, RB, KC, AG, and EKF.
 Each object has been inspected by at least two people.
-In the end, we combine the votes from different people.
-An object is classified as \code{junk} if the number of votes as \code{junk} is larger than the number of votes as \code{non-junk}.
+In the end, an object is classified as \code{junk} if the number of votes as \code{junk} is larger than the number of votes as \code{non-junk}.
 In total, there are 1661 objects classified as \code{junk}.
@@
 The color cuts here are more restrictive than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and high redshift galaxies.
-We not only remove objects with small sizes, but also exclude objects with large size and very low surface brightness because they are mostly \code{junk}.
+We not only remove objects with small sizes, but also exclude objects with large size and very low surface brightness because they are mostly spurious objects.
 After such cuts, there are 200 \code{junk} and 1407 \code{non-junk} remaining.
@@
 In the top panels of Figure \ref{fig:deblending_cuts}, we show the distributions of \code{junk} (red) and \code{non-junk} (green) in the parameter space spanned by four morphological parameters.
-There are still a significant amount of \code{junk} with high $M_{20}$, Gini coefficient, and asymmetry.
+There is still a significant amount of \code{junk} with high $M_{20}$, Gini coefficient, and asymmetry.
 Therefore, we add another set of selection cuts to further remove \code{junk}:
@@
 The slanted demarcation line on the Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to separate merging galaxies from normal galaxies.
-The bottom panels in Figure \ref{fig:deblending_cuts} show the objects after applying the morphology selections, which remove another 82\% of \code{junk} while only remove 9\% of \code{non-junk}.
+The bottom panels in Figure \ref{fig:deblending_cuts} show the objects after applying the morphology selections, which remove another 82\% of \code{junk} while only removing 9\% of \code{non-junk}.
 Such morphology cuts (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove false positives that are not likely to be LSBGs of interest.
 
-In this way, we obtain an LSBG sample with high purity, where 98\% of the false positives are removed.
-Therefore, our empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample.
+In this way, we obtain an LSBG sample with high purity, where 98\% of the false positives are removed (see Table \ref{tab:deblending_vis}).
+Therefore, our empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of small red galaxies (most likely background galaxies) in our initial sample.
 Furthermore, the completeness of real LSBG detection remains high.
-In Section \ref{sec:comp_meas}, we characterize the completeness of this ``deblending'' step by injecting mock \sersic{} galaxies, and we achieve $\sim80\%$ completeness at $\sbeff = 27.0\ \sbunit$ and $>50\%$ completeness at $\sbeff = 27.5\ \sbunit$ (Fig.
+In \S\ref{sec:comp_meas}, we characterize the completeness of this ``deblending'' step by injecting mock \sersic{} galaxies, and we achieve $\sim80\%$ completeness at $\sbeff = 27.0\ \sbunit$ and $>50\%$ completeness at $\sbeff = 27.5\ \sbunit$ (Fig.
 \ref{fig:completeness}).
@@
 They are used only as a diagnostic tool to remove false positives.
-We perform more detailed modeling in Section \ref{sec:modeling} to measure galaxy properties for science.
+We perform more detailed modeling in \S\ref{sec:modeling} to measure galaxy properties for science.
 
@@
 
-Although the vanilla \code{scarlet} modeling provides useful information to help us remove false positives, it does not necessarily give us reliable estimations on size, color, total magnitude, etc.
+Although the vanilla \code{scarlet} modeling provides useful information to help us remove false positives, it does not necessarily give us reliable estimations of galaxy size, color, total magnitude, etc.
 In fact, the vanilla \code{scarlet} model systematically under-estimates the size and total flux of LSB objects.
@@
 Consequently, it is hard for the non-parametric modeling to probe very low surface brightness features.
-Furthermore, the monotonicity constraint stops the model from growing in certain directions if there is another source along this direction.\footnote{This issue can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model of the target object never exceeds the other objects next to it.} As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biasing the measurements.
+Furthermore, the monotonicity constraint stops the model from growing in certain directions if there is another source along this direction.\footnote{This issue can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model of the target object never exceeds the other objects next to it.} As a result, the non-parametric model often does not capture the very LSB outskirts of LSBG, thus biasing the measurements.
 In the following, we explore a novel method to perform robust parametric modeling and measurement for LSBGs.
@@
 However, such fitting results are very sensitive to the masking scheme and sky background \citep[e.g.,][]{Greco2018}.
-A possible solution to this problem is to simultaneously model all the objects in the cutout and the sky using parametric models \citep[e.g.,][]{Lang2016,Dey2019}.
+A possible solution to this problem is to simultaneously model all the objects in the cutout and the sky using parametric models \citep[e.g.,][]{Lang2016,Dey2019,Liu2022}.
 In this work, we combine the advantage of parametric modeling with the power of deblending in \code{scarlet}.
@@
 First, we initialize a vanilla \code{scarlet} model for the target object, and we measure the effective radius $r_e$, total flux, and the shape of the scarlet model.
-The size of the bounding box of is also updated to be the maximum between 250 pixels and $10\, r_e$.
+The size of the bounding box is also updated to be the maximum between 250 pixels and $10\, r_e$.
 For the target, we still require a positivity constraint, and the monotonicity is automatically satisfied by the Spergel profile.
@@
 The Spergel modeling results are used for studying the properties of LSBGs.
-In the following section, we assess the quality of the Spergel modeling by injecting mock \sersic{} galaxies and comparing the recovered properties with truth.
+In the following section, we assess the quality of the Spergel modeling by injecting mock \sersic{} galaxies and comparing the recovered properties with the truth.
 
@@
 	\caption{The completeness of our LSBG search as a function of effective radius $r_e$ and the average surface brightness $\sbeff$.
-The overall completeness (right panel) comprises the detection completeness (left panel, see \S \ref{sec:detection}) and deblending completeness (middle panel, see \S \ref{sec:deblending}) where the false positives are removed.
+The overall completeness (right panel) comprises the detection completeness (left panel) and deblending completeness (middle panel).
 The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours.
 The completeness drops as we go to fainter surface brightness and smaller size.
-For a size range of $3\arcsec < r_e < 14\arcsec$, we are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
+For the size range of $3\arcsec < r_e < 14\arcsec$, we are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
 	}
@@
 
-The completeness of the LSBG search is important not only for understanding our search efficiency and improving the method in the future, but also for deriving the completeness-corrected results for LSBG science.
+The completeness of the LSBG search is important not only for understanding our search efficiency and improving the method in the future, but also for deriving the completeness-corrected results for science purposes.
 Similar to many other works \citep[e.g.,][]{vdBurg2017,Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and recovering them from the image.
@@
 A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}).
-Thus, the overall completeness combines the detection deblending steps.
+Thus, the overall completeness combines the detection and deblending steps.
 We perform a large suite of image simulations to derive the completeness.
-We inject single \sersic{} light profile \citep{Sersic1963} into the coadd images and try to recover them using the detection method (\S\ref{sec:detection}), model them using vanilla \code{scarlet} (\S\ref{sec:deblending}), and apply the deblending cuts.
+We inject single \sersic{} light profiles \citep{Sersic1963} into the coadd images and try to recover them using the detection method (\S\ref{sec:detection}), model them using vanilla \code{scarlet} (\S\ref{sec:deblending}), and apply the deblending cuts.
 The mock \sersic{} galaxies span a wide range in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$) and surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$).
@@
 The deblending completeness is very high at the bright end, but starts to decline with increasing size and decreasing surface brightness.
-Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending with other compact sources with the mock galaxy.
+Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending between compact sources and the mock galaxy.
 Interestingly, the detection completeness and deblending completeness both drop below 40\% around $\sbeff=27.5\ \sbunit$.
@@
 For the size range of $3\arcsec < r_e < 14\arcsec$, we are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness.
+Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on the \sersic{} model tests still sets a baseline on the real completeness.
 In the future, we might be more capable of generating realistic LSBGs using deep learning techniques.
@@
 Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more quickly with increasing size than ours does.
-\citet{CarlstenELVES2022} use a similar search algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$ assuming a Sersic index $n \approx 1$.
+This is because HSC PDR2 has a better sky subtraction for LSB studies than S16A in \citetalias{Greco2018}, and our initial selection is more inclusive for large objects.
+\citet{CarlstenELVES2022} search LSBGs in the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) and Canada–France–Hawaii Telescope (CFHT) data using a similar search algorithm to \citetalias{Greco2018} and ours.
+They reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$ assuming a Sersic index $n \approx 1$.
 \citet{vdBurg2017} searched for LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
 \citet{Zaritsky2021} focus on searching for LSBGs in the SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) images and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$ for $n=1$.
-Their low completeness might be explained by the fact that they remove a large fraction of the sky contaminated by Galactic dust.
+Their lower completeness might be explained by the fact that they remove a large fraction of the sky contaminated by Galactic dust.
 \citet{Tanoglidis2021} conducted an LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
-\citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but a much smaller completeness above $\sbeff > 26.5\ \sbunit$.
+\citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but a much lower completeness for $\sbeff > 26.5\ \sbunit$.
 The Dragonfly Wide Field Survey \citep{Danieli2020} reaches $\sim 29\ \sbunit$ for $>3\sigma$ detection on scales $\sim 1\arcmin$, which is deeper than all other surveys by sacrificing spatial resolution.
@@
 For surface brightness fainter than $>27\ \sbunit$, the measured size can be much smaller than the truth.
-As a result, the measured total magnitude $m$ is also too low.
-For the measured average surface brightness $\overline{\mu}_{\rm eff}$, the trade-off between magnitude and size biases makes it less biased than the total magnitude.
+As a result, the measured total magnitude $m$ is also too faint.
+For the measured average surface brightness $\overline{\mu}_{\rm eff}$, the trade-off between the total magnitude and size makes it less biased than the total magnitude.
 Similar to \citet{Zaritsky2021}, we derive the measurement bias and uncertainties in size, surface brightness, total magnitude, and color as a function of size and surface brightness.
@@
 The size and surface brightness bias grows with increasing surface brightness.
-The bias term is not a monotonic function of size because the size here is not intrinsic size.
-It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$.
+The bias term is not a monotonic function of size because the size here in Figure \ref{fig:meas_err} is not intrinsic size.
+It is the bias in size measurement that makes galaxies with large intrinsic size pile up around $r_e\sim 6\arcsec$.
 We find the bias in $g-i$ color to be quite small.
 The $1\sigma$ measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the bias.
-We set the minimum uncertainties to be $\sigma(r_e) \geqslant 0.3\arcsec,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05\ \sbunit,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.
-
-In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on the bias-corrected properties. 
+We set the minimum uncertainties to be $\sigma(r_e) \geqslant 0.3\arcsec,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05\ \sbunit,\ \sigma(g-i) \geqslant 0.05$ to avoid meaninglessly small uncertainties.
+
+We apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on the bias-corrected properties. 
 % We also incorporate the measurement errors into the science figures. 
@@
 
-\section{Mass-size outliers in the Milky-Way analogs}\label{sec:sample_construction}
-The goal of this paper is to study the mass-size outliers in the satellite systems around MW-like galaxies.
+\section{Mass-size outliers Around Milky-Way analogs}\label{sec:sample_construction}
+The goal of this paper is to study the mass-size outliers in the satellite systems of MW-like galaxies.
 However, distance information is needed to convert the observed size and magnitude to the physical size and stellar mass.
@@
 Beside direct distance measurements (e.g., SAGA, ELVES, \citealt{Kadowaki2021}), it is common to assume a distance to an LSBG by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
-A statistical background subtraction is then needed to account for the contribution from background and foreground galaxies.
+A statistical background subtraction is then needed to account for the contribution from background and foreground sources.
 Furthermore, cross-correlation between an LSBG sample and a host galaxy sample can also reveal the distance distribution of LSBGs \citep{Greene2022}.
@@
 \subsection{Matching with Milky-Way analogs}\label{sec:match}
-The properties of the Milky Way itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016} and the definitions of MW analogs are different among different studies.
-In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$~mag (corresponding to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$) and redshift $0.005 < z < 0.01$ (20--40 Mpc).
-SAGA also requires that the MW analogs be in isolation (without nearby bright galaxies).
+The properties of the Milky Way itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016} and the definitions of MW analogs vary between studies.
+In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on the absolute $K$-band magnitude $-23 > M_K > -24.6$~mag (corresponding to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$) and redshift $0.005 < z < 0.01$ (20--40 Mpc).
+SAGA generally requires that the MW analogs be in isolation (without nearby bright galaxies).
 In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$~mag ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA.
-In this work, we choose the stellar mass range of our MW analog sample to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($M_{\star, \mathrm{MW}}\approx 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
+In this work, we choose the stellar mass range of our MW analog sample to be $10.2 < \log\, M_\star/M_\odot < 11.2$ based on NSA stellar mass, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($M_{\star, \mathrm{MW}}\approx 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
 MW analogs selected using this definition are very close to those in SAGA but are slightly less massive than the ELVES hosts since ELVES has several groups more massive than SAGA hosts.
+We do not discriminate between isolated or paired hosts.
 
 Mass-size outliers, by definition, are relatively scarce compared with ``normal'' satellites around MW analogs \citep{SAGA-II,CarlstenELVES2022}.
-It is therefore helpful to probe a larger volume to obtain good statistics.
-We choose our redshift range to be $0.01 < z < 0.04$, which ensures that we can detect a significant number of faint dwarf galaxies around MW-like hosts.
-The depth of HSC limits our detection to below $z \approx 0.04$, since dwarf galaxies will be too small and too faint to be detected beyond that distance\footnote{Our search only includes objects larger than $r_e\approx 2\arcsec$, which corresponds to $M_\star \sim 10^{8.5}\ M_\odot$ at $z=0.04$ assuming the \textit{average} mass-size relation from \citet{ELVES-I}.
+It is therefore helpful to probe a larger volume to obtain better statistics.
+We choose our redshift range to be $0.01 < z < 0.04$, which ensures that we can detect a significant number of LSB satellite candidates around MW-like hosts.
+The depth of HSC limits our detection to below $z \approx 0.04$ because dwarf galaxies will be too small and too faint to be detected beyond that distance\footnote{Our search only includes objects larger than $r_e\approx 2\arcsec$, which corresponds to $M_\star \sim 10^{8.5}\ M_\odot$ at $z=0.04$ assuming the \textit{average} mass-size relation from \citet{ELVES-I}.
 Going to higher redshift will make it more difficult to detect low-mass dwarfs.}.
 We also exclude galaxies at $z<0.01$ because (1) the number of mass-size outliers will be very small due to the small volume; (2) their large angular size makes them more vulnerable to being shredded during detection, so including them will introduce a number of spurious LSB objects.
-We do not discriminate between isolated or paired hosts.
 
@@
 We match them to the initial LSBG sample (described in \S \ref{sec:detection}, before the deblending step) as follows.
-For a given MW-like galaxy, we first calculate a virial radius $R_{\rm vir}$ assuming the stellar-to-halo mass relation in \citet{Behroozi2010}.
+For a given MW-like galaxy, we first calculate a virial mass assuming the stellar-to-halo mass relation in \citet{Behroozi2010} then calculate the corresponding virial radius $R_{\rm vir}$.
 It turns out that 40\% of our hosts have virial radii larger than 300 kpc, which is commonly used for the virial radius of the Milky Way.
-Then we identify any LSBG that falls into the projected virial radius of the host on the sky.
+Then we identify any LSBG that falls inside the projected virial radius of a host.
 If one LSBG is matched to multiple hosts, we assign it to the nearest host based on the separation normalized by host virial radius.
-Finally, we have 901 MW-like hosts and 10,579 LSBG candidates associated with them.
+There are 901 MW-like hosts and 10,579 LSBG candidates associated with them.
 
@@
 Next, we model these remaining objects using the Spergel profile as described in \S\ref{sec:modeling} and obtain their photometry and structural parameters from the best-fit models.
-% Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives.
 We also remove duplicate objects.
-We are left with 2,510 LSBG candidates associated with 689 MW analogs as our final LSBG sample.
-We note that these LSBGs are matched to MW hosts in projection but do not have direct distance measurements.
+In the final catalog, we are left with 2,510 LSBG candidates associated with 689 MW analogs as our final LSBG sample.
+The host number drops to 689 because many hosts in the prior sample has no true positives as their satellites.
+We note that these LSBGs are matched to MW hosts in projection but do not have direct distance measurements, and we have not applied any statistical background correction at this stage.
 
@@
 Lastly, we correct for the effect of Galactic extinction on colors based on \citet{SFD1998,Schlafly2011}.
-We derive the stellar masses of cross-matched LSBG from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
+The stellar masses of cross-matched LSBG are derived from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
 \begin{align*}
@@
 \subsection{Mass-size outlier sample}\label{sec:sample}
-The concept of UDG was proposed to describe dwarf galaxies with unusually large size ($r_e>1.5$ kpc) and a diffuse light distribution ($\sbcen > 24.0\ \sbunit$).
+The concept of UDG was proposed to describe galaxies with unusually large size ($r_e>1.5$ kpc) and low central surface brightness ($\sbcen > 24.0\ \sbunit$, \citealt{vanDokkum2015}).
 Although UDGs are large in size, the constant size cut does not account for the fact that the galaxy size is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Graham2003,Trujillo2007,vanDokkum2013,Cappellari2013,Lange2015}.
@@
 Thus, a more intuitive definition for puffy dwarf galaxies (i.e., mass-size outliers) would be based on a mass-size relation and its scatter.
-Following this thread, we propose a new definition for mass-size outliers dubbed as \textit{ultra-puffy galaxies} (UPGs).
-In this section, we describe the definitions of UPG and contrast it with UDG, then we select UDGs and UPGs from our LSBGs matched with MW hosts.
+Following this thread, we propose a new definition for mass-size outliers, dubbed \textit{ultra-puffy galaxies} (UPGs).
+In this section, we describe the definition of UPG and contrast it with UDG.
+Then we select UDGs and UPGs from our LSBGs matched with MW hosts.
 The catalogs and mosaic images of UDGs and UPGs are available online\footnote{\url{https://astrojacobli.github.io/research/BeyondUDG/}}.
@@
 In general, the slope of the mass-size relation in the nearby Universe has been shown to be color- and morphology-dependent for galaxies above $M_\star > 10^{9}\ M_\odot$: blue star-forming galaxies have a shallower mass-size relation than do red quenched galaxies \citep[e.g.,][]{Lange2015}.
-Fortunately, in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$), \citet{ELVES-I} derive the mass-size relation from the satellites of MW analogs in the Local Volume and show that the average mass-size relation is quite universal: the slope and intercept are not sensitive to the color or morphology of dwarf galaxies.
+In the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$), \citet{ELVES-I} derive the mass-size relation from the satellites of MW analogs in the Local Volume and show that the average mass-size relation is quite universal: the slope and intercept are not sensitive to the color or morphology of dwarf galaxies.
 Residuals from the mass-size relation follow a log-normal distribution reasonably well.
 This fact allows us to define a subset of dwarf galaxies that are outliers with respect to the average mass-size relation.
-It is worth noting that a definition based on the mass-size relation was already used in simulation studies where the absolute sizes were uniformly too large such that size outliers can only be selected relative to the simulated mass-size relation \citep[e.g.,][]{Benavides2021,Benavides2022}.
+It is worth noting that a definition based on the mass-size relation was already used in simulation studies where the absolute sizes were uniformly too large such that size outliers could only be selected relative to the simulated mass-size relation \citep[e.g.,][]{Benavides2021,Benavides2022}.
 
@@
 The total sky area occupied by UPG hosts (out to 1 $R_{\rm{vir}}$) is 32.37 deg$^{2}$.
-The catalogs are available online, and we demonstrate the catalog format in Table \ref{tab:catalog}.
+The catalogs are available online\footnote{\url{https://astrojacobli.github.io/research/BeyondUDG/}}, and we demonstrate the catalog format in Table \ref{tab:catalog}.
 
@@
 The UDG sample is usually defined based on surface brightness and physical size of the galaxy.
-However, there are many different criteria in the literature: \citet{vanDokkum2015} define UDGs to have effective radii $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019}.
+However, there are many different criteria in the literature: \citet{vanDokkum2015} define UDGs to have effective radii $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019,Karunakaran2022b}.
 The size criterion also varies from $r_e > 1$ kpc to $r_e > 1.5$ kpc.
@@
 We also removed another 4 objects having completeness less than 0.1.
-In the end, we obtain our UDG sample with 412 objects associated with 258 hosts.
+In the end, we obtain our UDG sample with 412 objects (associated with 258 hosts) after searching around 689 MW analogs.
 The total sky area occupied by UDG hosts (out to 1 $R_{\rm{vir}}$) is 32.71 deg$^{2}$.
@@
 \subsection{Background contamination fraction}\label{sec:bkg}
-Although we have matched LSBGs to MW analogs by proximity, the physical affiliation of LSBGs to the host is not guaranteed.
-As a result, a certain fraction of galaxies in our mass-size outlier samples are foreground or background galaxies that fall within the virial radius of the host in projection.
-Given the volume probed by our search, contamination is most likely to be dominated by background galaxies.
+Although we have matched LSBGs to MW analogs by proximity in projection, the physical affiliation of LSBGs to the host is not guaranteed.
+As a result, a certain fraction of galaxies in our mass-size outlier samples are foreground or background galaxies that fall within the virial radius of the host by chance.
+Given the volume and the surface brightness range of our search, contamination is most likely to be dominated by background galaxies.
 In this section, we try to estimate the contamination fraction empirically by randomly matching LSBGs to our MW hosts and measuring the number density of apparent UPG and UDG.
@@
 Then we perform the same deblending and modeling steps for the 2,707 LSBG candidates detected in this region.
-We also removed objects that are already in our mass-size outlier samples and objects with completeness less than 0.1.
+We also remove objects that are already in our mass-size outlier samples and objects with completeness less than 0.1.
 We also did the same visual inspection as for UDGs and UPGs to remove false positives.
@@
 In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.94\pm0.03\ \mathrm{deg}^{-2}$, and the number density of fake UPGs is $S_{\rm UPG} = 2.12\pm0.03\ \mathrm{deg}^{-2}$.
-The catalogs of fake UDG and UPGs are also available online\footnote{\url{https://github.com/AstroJacobLi/kuaizi/tree/master/data}}.
+The catalogs of fake UDG and UPGs are also available online\footnote{\url{https://astrojacobli.github.io/research/BeyondUDG/}}.
 Using the number densities and the probed area of our survey, we calculate the contamination fraction for both the UDG and UPG samples.
@@
 	}
-    \caption{The distribution ultra-diffuse galaxies (UDGs, \textit{left}) and ultra-puffy galaxies (UPGs, \textit{right}) on the size-surface brightness plane.
+    \caption{The distribution of ultra-diffuse galaxies (UDGs, \textit{left}) and ultra-puffy galaxies (UPGs, \textit{right}) on the size-surface brightness plane.
 The UPGs are defined to be galaxies that are $1.5\sigma$ above the average mass-size relation in \citet{ELVES-I}.
@@
 We show UDGs and UPGs on the mass-size plane in Figure \ref{fig:mass_size}.
-To orient the readers to the mass-size plane, we first show a schematic diagram in the left panel where regions relevant to the definitions of UDG and UPG are highlighted.
+To orient the reader to the mass-size plane, we first show a schematic diagram in the left panel where regions relevant to the definitions of UDG and UPG are highlighted.
 The light blue shade shows the survey limit; we cannot effectively probe LSBGs fainter than $\sbeff \gtrsim 27.5\ \sbunit$ (see \S\ref{sec:comp_meas}).
-For defining UDGs, a size cut and a surface brightness cut are needed.
+For defining UDGs, a physical size cut and a surface brightness cut are needed.
 We show the $r_e = 1.5$ kpc cut as a horizontal gray band to acknowledge the fact that smaller galaxies with large size uncertainties are included in the UDG sample.
@@
 We also show the constant surface stellar mass density ($\mu_\star$) line, which is parallel to the constant surface brightness lines because the surface mass density is proportional to surface brightness multiplied by mass-to-light ratio.
-Therefore, at a given size, blue UDGs are less massive than red UDGs; at a given stellar mass, blue UDGs are larger than red UDGs in size.
+Therefore, at a given size and surface brightness, blue UDGs are less massive than red UDGs; at a given stellar mass and  surface brightness, blue UDGs are larger than red UDGs in size.
 Such a constant surface brightness cut leads to a UDG population that is inhomogeneous in surface mass density.
 
-In the left panel of Figure \ref{fig:mass_size}, the green dashed lines show the average mass-size relation and $1.5\sigma$ above it.
+In the left panel of Figure \ref{fig:mass_size}, the green dashed lines show the average mass-size relation and the $1.5\sigma$ line above the average relation.
 UPGs would lie above the $1.5\sigma$ line by construction, and there will be overlap between UDGs and UPGs.
@@
 We highlight the similarities and differences between the UDGs and UPGs in the right panel.
-UDGs that are also classified as UPGs are shown as orange squares, while UDGs that do not satisfy the UPG definition are marked as red stars.
+UDGs that are also classified as UPGs are shown as orange squares, whereas UDGs that do not satisfy the UPG definition are marked as red stars.
 Blue triangles correspond to UPGs that are not classified as UDGs.
-Limited by the detection limit and the fact that our hosts lie beyond the Local Volume, our mass limit is $M_\star \approx 10^{6.8}\ M_\odot$, which is $\sim 1$ dex higher than ELVES.
-Compared with the UPG sample, we find that the UDG sample (orange squares + red stars) comprises a number of galaxies below the $1.5\sigma$ line, but also loses several low-mass galaxies that are above $1.5\sigma$ line but have sizes smaller than 1.5 kpc.
+Limited by the detection limit and the fact that our hosts lie beyond the Local Volume, our mass limit is $M_\star \approx 10^{6.5}\ M_\odot$, which is $\sim 1$ dex higher than ELVES.
+Compared with the UPG sample, we find that the UDG sample (orange squares + red stars) comprises a number of galaxies below the $1.5\sigma$ line, but also loses several low-mass galaxies that are above the $1.5\sigma$ line but have sizes smaller than 1.5 kpc.
 For the UDG sample, the stellar mass range only reaches $M_\star\approx 10^{8.3}\ M_\odot$ because galaxies with higher stellar mass are too bright to satisfy the UDG surface brightness criterion.
 On the contrary, since the UPG definition does not have a hard surface brightness cut, it includes many galaxies that are more massive than UDGs provided they have an extraordinarily large size.
-We also note that the mass-size relation from \citet{ELVES-I} is extrapolated to define UPGs in $10^{8.5}\ M_\odot < M_\star < 10^9\ M_\odot$, where about 10\% our UPGs are located in.
+We also note that the mass-size relation from \citet{ELVES-I} is extrapolated to define UPGs in $10^{8.5}\ M_\odot < M_\star < 10^9\ M_\odot$, where about 10\% our UPGs are located.
 However, the mass-size relation might show color and morphology dependence for $M_\odot > 10^{8.5}\ M_\odot$.
@@
 Therefore the UDG abundance in \citet{SAGA-II} is about $N_{\rm UDG}^{\rm SAGA}\approx 0.17\pm0.07$.
-In the ELVES survey \citep{CarlstenELVES2022}, there are 13 UDGs out of 358 satellites with secure distances ($P_{\rm sat} > 0.8$) in 30 MW analogs, leading to a UDG abundance of $N_{\rm UDG}^{\rm ELVES} \approx 0.43\pm0.12$.
+In the ELVES survey \citep{CarlstenELVES2022}, there are 13 UDGs out of 351 satellites with secure distances ($P_{\rm sat} > 0.8$) in 30 MW analogs, leading to a UDG abundance of $N_{\rm UDG}^{\rm ELVES} \approx 0.43\pm0.12$.
+If we only take UDGs more massive than our detection limit $M_\star > 10^{6.5}\ M_\odot$, we obtain slightly lower UDG abundances of $N_{\rm UDG, 6.5}^{\rm ELVES} \approx 0.36\pm0.11$.
 \citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}.
@@
 We note that \citet{Roman2017b} do not estimate the background contamination fraction and do correct for completeness.
+
 Because there is little literature on UPGs, we only compare our UPG abundance with ELVES.
 In ELVES, we take the 351 satellites with secure distances in 30 MW analogs and identify 36 UPGs associated with 20 hosts.
-Thus the UPG abundance fraction in ELVES is $N_{\rm UPG}^{\rm ELVES} = 1.20 \pm 0.20$, which is higher than our UPG abundance.
+Thus the UPG abundance fraction in ELVES is $N_{\rm UPG}^{\rm ELVES} = 1.20 \pm 0.20$.
+When only selecting UPGs with $M_\star > 10^{6.5}\ M_\odot$, we obtain 23 UPGs in 30 MW analogs, thus $N_{\rm UPG, 6.5}^{\rm ELVES} = 0.77 \pm 0.16$, which is slightly higher than our UPG abundance, but is consistent our result within $1\sigma$.
 
@@
 As pointed out by \citet{CarlstenELVES2022,Font2022}, the SAGA survey reaches a surface brightness depth of $\sbeffr\approx 25\ \sbunit$, which is $\sim 2.5\ \sbunit$ shallower than the ELVES survey and this work.
-It is probable that SAGA missed a significant fraction of red and lower surface brightness galaxies.
+It is probable that SAGA missed some fraction of red and lower surface brightness galaxies.
 Our UDG abundance is marginally higher than the prediction from \citet{vdBurg2017} but is still consistent considering the large scatter of the power law.
 
-Taking all data points from literature (as shown in Figure \ref{fig:n_udg}), we use the orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the red solid line in Figure \ref{fig:n_udg}.
+Taking all data points from the literature (as shown in Figure \ref{fig:n_udg}), we use the orthogonal distance regression (ODR) to fit a power-law between $N_{\rm UDG}$ and host halo mass $M_h$ and find $N_{\rm UDG} \propto M_h^{0.96\pm 0.04}$, shown as the red solid line in Figure \ref{fig:n_udg}.
 The slope of the power law is shallower than \citet{vdBurg2017} ($\beta=1.11\pm0.07$) but steeper than \citet{Roman2017b} ($\beta=0.85\pm0.05$).
-\citet{ManceraPina2018} survey eight clusters and find sublinear power law.
-Recently \citet{Karunakaran2022b} perform a similar analysis including SAGA, ELVES, and \citet{Nashimoto2022} and find a slightly shallower power law of $\beta=0.87\pm0.07$.
+\citet{ManceraPina2018} survey eight clusters and find a sublinear power law.
+Recently \citet{Karunakaran2022b} performed a similar analysis including SAGA, ELVES, and \citet{Nashimoto2022} and find a slightly shallower power law of $\beta=0.87\pm0.07$.
 We note that their surface brightness cut for UDGs is brighter than ours and thus they include more ``UDGs'' for MW-like hosts and have a shallower power law.
-One should be aware of the fact that literature results are not completeness corrected and background subtracted, and UDG definition also varies in different studies.
-These effects could significantly bias the results when combing them together.
+One should be aware of the fact that literature results are not completeness corrected and background subtracted, and UDG definitions also vary across different studies.
+These effects could significantly bias the results when combining them.
 Therefore we caution that the power law index here should not be over-interpreted.
@@
 We also compare our results with results in the Virgo cluster.
-Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}) and only consider satellites with $M_\star > 10^{6.5}\ M_\odot$, there are 14 UDGs and 17 UPGs out of 218 identified satellites (with no completeness correction).
+Taking the data from the Next Generation Virgo Cluster Survey (NGVS, \citealt{Ferrarese2020}) and only considering satellites with $M_\star > 10^{6.5}\ M_\odot$, there are 14 UDGs and 17 UPGs out of 218 identified satellites (with no completeness correction).
 Thus their UDG (UPG) fraction is $f_{\rm UDG}^{\rm Virgo} \approx 0.06\pm 0.02$ and $f_{\rm UPG}^{\rm Virgo} \approx 0.08\pm 0.02$.
 However, we note that \citet{Ferrarese2020} only survey the central 4 deg$^2$ of the Virgo cluster, which probably biases the UDG (UPG) fraction.
-It seems that our UDG fraction is higher than both ELVES and NGVS.
-Our UPG fraction is consistent with ELVES and NVGS.
-A systematic and careful comparison on UDG (UPG) fraction in different environments is needed in the future.
+It seems that our UDG abundance and fraction are higher than both ELVES and NGVS.
+Our UPG abundance and fraction are consistent with ELVES and NVGS.
+In the future, a systematic and careful comparison on UDG (UPG) fraction in different environments is needed.
 
@@
 \ref{fig:mass_size}).
-On the other hand, the hard surface brightness cut corresponds to very different surface mass densities between red and blue galaxies, making it hard to directly compare red and blue UDGs, since they occupy different regions on the mass-size plane.
+On the other hand, the hard surface brightness cut corresponds to very different surface mass densities between red and blue UDGs, making it hard to directly compare them, since they occupy different regions on the mass-size plane.
 For a given stellar mass and size (e.g., at $M_\star \sim 10^{7.5}\ M_\odot$ and $r_e = 1.5$ kpc), the hard surface brightness cut in the UDG definition preferentially removes blue galaxies because their surface brightnesses are higher and their $M_\star/L$ are lower.
@@
 UPGs are defined to lie $1.5\sigma$ above the average mass-size relation of the satellites in MW analogs in the Local Volume.
-The specific value above the average mass-size relation can vary to probe different parts of the size distribution.
+The specific value above the average mass-size relation can be varied to probe different parts of the size distribution.
 We advocate studying the UPG population in both observations and simulations to explore samples with different ``puffiness'' (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).
 
-However, in order to construct a UPG sample, one needs to know the distance, the color, a color-$M_\star/L$ relation to convert observed magnitudes to stellar mass, and a mass-size relation and its scatter.
-None of these are easy to obtain and free from systematic errors.
+However, in order to construct a UPG sample, one needs to know the distance, the color, a color-$M_\star/L$ relation to convert observed magnitudes to stellar mass, and a mass-size relation and the scatter therein.
+None of these are easy to obtain or free from systematic errors.
 Both size and stellar mass could have large uncertainties in the LSB regime.
 One also needs to apply a surface brightness cut (such as $\sbeff > 23.0\ \sbunit$ in this work) to make sure that the UPG sample is not contaminated by disk galaxies with high surface brightness due to the bulges.
-Reliable mass-size relations with scatter are not available for all galaxy mass ranges.
-\citet{ELVES-I} derive the mass-size relation of satellite galaxies below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$.
-The mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is not well measured, nor is any dependence on color or morphology.
+
+Our definition of UPG greatly benefits from the well-measured mass-size relation in \citet{ELVES-I} and the fact that this mass-size relation is independent of galaxy color and morphology.
+However, such mass-size relations are not available for all galaxy mass ranges and environments (in field or in group/cluster).
+\citet{ELVES-I} derive the mass-size relation of satellite galaxies of MW analogs below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$.
+The mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is not well measured, nor is any dependence on color, morphology, or environment.
 In this work, we simply extrapolate the \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$.
-At the same time, it is not clear whether the size distribution for a given mass can be well-described by a Gaussian distribution.
+However, it is not clear whether the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is sensitive to color or morphology.
+
+At the same time, whether the size distribution for a given mass can be well-described by a Gaussian distribution is still a question.
 Fig.
@@
     \item By matching LSBGs with MW analogs in the NSA catalog, we construct samples of mass-size outliers including UDGs and UPGs.
-We display their distributions on the size-surface brightness plane (Figure \ref{fig:udg_upg_re_mu}) and the mass-size plane (Figure \ref{fig:mass_size}).
+We display their distributions on the mass-size plane (Figure \ref{fig:mass_size}) and the size-surface brightness plane (Figure \ref{fig:udg_upg_re_mu}).
 The UPG sample contains more blue and higher surface brightness galaxies than the UDG sample.
@@
 Our UDG abundance is slightly higher than that in ELVES, but much higher than that in SAGA.
-Combining data from studies in denser environments, we find that the UDG abundance follows a sublinear power law with the host halo mass.
+When considering the detection depth, our UPG abundance agrees with ELVES result within $1\sigma$.
+
+    \item Combining data from studies in denser environments, we find that the UDG abundance follows a sublinear power law with the host halo mass.
 The power law slope agrees with other studies considering the errors.
-We caution that many other studies do not correct for completeness which could bias the results.
+We caution that each study adopts different UDG definitions and may or may not correct for completeness, which could bias the results.
 
     \item For a MW analog, on average, about 12\% of its satellites are UDGs and about 10\% of its satellites are UPGs.
-Although the UPG fraction is consistent with ELVES and NGVS, the UDG fraction is found to be higher than those in ELVES and NGVS, which are not corrected for completeness and suffer from small number statistics.
+Although the UPG fraction is consistent with ELVES and NGVS, the UDG fraction is found to be higher than those in ELVES and NGVS.
 
@@
 This study is focused on a small subset of LSBG candidates matched with MW analogs.
-In future works, we would like to exploit the full sample to study interesting topics on LSBGs including their redshift distributions, nucleation fractions, and intrinsic shapes.
+In future work, we would like to exploit the full sample to study interesting topics on LSBGs including their redshift distributions, nucleation fractions, and intrinsic shapes.
 We will also explore machine learning techniques to help us classify LSBGs and estimate structural parameters.

### 2022-10-25 paper1.tex
fixed numbers of contam

@@
 Measurement error and uncertainty & \S\ref{sec:comp_meas},\S\ref{ap:comp_meas_unc} & 2,510\\
-Mass-size outlier selection & \S\ref{sec:sample} & 362 (UPG), 432 (UDG)
+Mass-size outlier selection & \S\ref{sec:sample} & 337 (UPG), 412 (UDG)
 \enddata
@@
 In the final catalog, we are left with 2,510 LSBG candidates associated with 689 MW analogs as our final LSBG sample.
+These MW analogs occupy a sky area of 75.94 deg$^{2}$ (out to $1\ R_{\rm vir}$).
 The host number drops to 689 because many hosts in the prior sample has no true positives as their satellites.
@@
 In the end, there are 480 LSBGs (excluding false positives) representing a population of possible contaminants for the UDG and UPG samples.
-Next, because both UDG and UPG are defined based on a physical size, we randomly associate the 480 LSBGs with the hosts of our UDGs and UPGs, respectively.
+Next, because both UDG and UPG are defined based on a physical size, we randomly associate the 480 LSBGs with the 689 MW analogs that are surveyed in this paper.
 Then we calculate a physical size for each LSBG and classify an LSBG as a ``fake`` UDG or UPG if it satisfies the corresponding definition.
 We repeat such random matching 200 times.
-In the end, we obtain 11,458 fake UDGs and 11,867 fake UPGs.
+In the end, we obtain 8,392 fake UDGs and 8,485 fake UPGs.
 These UDGs and UPGs are ``fake'' only in the sense of being associated with random MW hosts.
 
-In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.94\pm0.03\ \mathrm{deg}^{-2}$, and the number density of fake UPGs is $S_{\rm UPG} = 2.12\pm0.03\ \mathrm{deg}^{-2}$.
+In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.75\pm0.03\ \mathrm{deg}^{-2}$, and the number density of fake UPGs is $S_{\rm UPG} = 1.70\pm0.03\ \mathrm{deg}^{-2}$.
 The catalogs of fake UDG and UPGs are also available online\footnote{\url{https://astrojacobli.github.io/research/BeyondUDG/}}.
 Using the number densities and the probed area of our survey, we calculate the contamination fraction for both the UDG and UPG samples.
-For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 16\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 20\%$.
+For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 32\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 38\%$.
+We take the contamination fraction into account when calculating the abundances in \S\ref{sec:results}.
+
+% For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 36\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 47\%$.
 We take the contamination fraction into account when calculating the abundances in \S\ref{sec:results}.
@@
 In our UDG sample, there are 412 UDGs associated with 258 hosts.
-After correcting for background contamination (see \S \ref{sec:bkg}) and completeness (see \S \ref{sec:comp_meas}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host.
-The UPG abundance in our sample is $N_{\rm UPG} = 0.61\pm 0.04$ per host.
+After correcting for background contamination (see \S \ref{sec:bkg}) and completeness (see \S \ref{sec:comp_meas}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.61\pm 0.04$ per host.
+The UPG abundance in our sample is $N_{\rm UPG} = 0.47\pm 0.04$ per host.
 Here we neglect the fact that the number of satellites contained within the virial sphere is different from the number of satellite within a projected cylinder with virial radius (the so-called deprojection factor, \citealt{vdBurg2017}).
@@
 \ref{fig:mass_size}).
-Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.12 \pm 0.03$ and $f_{\rm UPG} \approx 0.10 \pm 0.03$.
+Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.10 \pm 0.03$ and $f_{\rm UPG} \approx 0.08 \pm 0.03$.
 In ELVES, among 351 satellites with secure distances in 30 MW analogs, we identify 13 UDGs associated with 10 hosts, and 36 UPGs associated with 20 hosts.

### 2022-10-25 paper1.tex
Updates from Overleaf

@@
 These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represent the tail of the satellite size distribution.
-We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is consistent with the observed abundance at this halo mass in the Local Volume.
-We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.76\pm0.04$ per host.
+We find that each MW analog hosts $N_{\rm UPG} = 0.31\pm 0.05$ ultra-puffy galaxies on average, which is consistent but slightly lower than the observed abundance at this halo mass in the Local Volume.
+We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.44\pm0.05$ per host.
 With literature results, we confirm that the UDG abundance scales with the host halo mass following a sublinear power law.
@@
 In a variety of galaxies in the Universe, there is an interesting subset of galaxies with low surface brightness \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}.
-Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019,Danieli2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
+Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019,Danieli2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,Roman2021,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
 There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Danieli2019DF2,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Pandya2018,Villaume2022}.
@@
 After applying the stellar mass and redshift cuts to the NSA catalog (\S\ref{sec:data}), there are 23,218 MW-like galaxies.
-We match them to the initial LSBG sample (described in \S \ref{sec:detection}, before the deblending step) as follows.
+We then select those within HSC PDR2 footprint and match them to the initial LSBG sample (described in \S \ref{sec:detection}, before the deblending step) as follows.
 For a given MW-like galaxy, we first calculate a virial mass assuming the stellar-to-halo mass relation in \citet{Behroozi2010} then calculate the corresponding virial radius $R_{\rm vir}$.
@@
 If one LSBG is matched to multiple hosts, we assign it to the nearest host based on the separation normalized by host virial radius.
-There are 901 MW-like hosts and 10,579 LSBG candidates associated with them.
+There are 922 MW-like hosts and 10,579 LSBG candidates associated with them.
+These MW analogs occupy a sky area of 89.19 deg$^{2}$ (out to $1\ R_{\rm vir}$).
 
 % However, a significant fraction of spurious objects remain in this cross-matched LSBG sample, including galactic cirrus, tidal streams, shredded large galaxies, and compact sources blended with galaxy outskirts.
-As described in \S\ref{sec:deblending}, we then perform a deblending step to effectively remove spurious objects.
+As described in \S\ref{sec:deblending}, we perform a deblending step to effectively remove spurious objects.
 There are 2,673 objects left after the deblending cuts.
@@
 In the final catalog, we are left with 2,510 LSBG candidates associated with 689 MW analogs as our final LSBG sample.
-These MW analogs occupy a sky area of 75.94 deg$^{2}$ (out to $1\ R_{\rm vir}$).
-The host number drops to 689 because many hosts in the prior sample has no true positives as their satellites.
+The host number drops from 922 to 689 because many hosts in the prior sample has no true positives as their satellites.
 We note that these LSBGs are matched to MW hosts in projection but do not have direct distance measurements, and we have not applied any statistical background correction at this stage.
@@
 In the end, there are 480 LSBGs (excluding false positives) representing a population of possible contaminants for the UDG and UPG samples.
-Next, because both UDG and UPG are defined based on a physical size, we randomly associate the 480 LSBGs with the 689 MW analogs that are surveyed in this paper.
+Next, because both UDG and UPG are defined based on a physical size, we randomly associate the 480 LSBGs with the 922 MW analogs that are surveyed in this paper.
 Then we calculate a physical size for each LSBG and classify an LSBG as a ``fake`` UDG or UPG if it satisfies the corresponding definition.
 We repeat such random matching 200 times.
-In the end, we obtain 8,392 fake UDGs and 8,485 fake UPGs.
+In the end, we obtain 7,625 fake UDGs and 8,267 fake UPGs.
 These UDGs and UPGs are ``fake'' only in the sense of being associated with random MW hosts.
 
-In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.75\pm0.03\ \mathrm{deg}^{-2}$, and the number density of fake UPGs is $S_{\rm UPG} = 1.70\pm0.03\ \mathrm{deg}^{-2}$.
+In this way, the number density of fake UDGs is estimated to be $S_{\rm UDG} = 1.60\pm0.25\ \mathrm{deg}^{-2}$, and the number density of fake UPGs is $S_{\rm UPG} = 1.72\pm0.23\ \mathrm{deg}^{-2}$.
 The catalogs of fake UDG and UPGs are also available online\footnote{\url{https://astrojacobli.github.io/research/BeyondUDG/}}.
-Using the number densities and the probed area of our survey, we calculate the contamination fraction for both the UDG and UPG samples.
-For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 32\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 38\%$.
-We take the contamination fraction into account when calculating the abundances in \S\ref{sec:results}.
-
-% For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 36\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 47\%$.
+Using the number densities and the probed area of our survey (89.19 deg$^{2}$ occupied by 922 hosts), we calculate the contamination fraction for both the UDG and UPG samples.
+For the UDG sample, we find $f_{\rm contam}^{\rm UDG} \approx 35\%\pm5\%$; for the UPG sample, the contamination fraction is $f_{\rm contam}^{\rm UPG} \approx 45\%\pm6\%$.
 We take the contamination fraction into account when calculating the abundances in \S\ref{sec:results}.
@@
 \textit{Left}: We compile the UDG abundance measurements from the literature covering a wide range of host mass.
-The UDG abundance from our work $N_{\rm UDG} = 0.76\pm 0.04$ is shown as a red square, the power-law relation from \citet{vdBurg2017} is shown in gray, and our fitting result is shown in pink.
+The UDG abundance from our work $N_{\rm UDG} = 0.44\pm 0.05$ is shown as a red square, the power-law relation from \citet{vdBurg2017} is shown in gray, and our fitting result is shown in pink.
 Our UDG abundance is consistent with ELVES but significantly higher than that in SAGA.
@@
 We define the UDG (UPG) abundance as the average number of UDGs (UPGs) per host galaxy.
-We searched 689 MW analogs.
+We searched 922 MW analogs.
 In our UDG sample, there are 412 UDGs associated with 258 hosts.
-After correcting for background contamination (see \S \ref{sec:bkg}) and completeness (see \S \ref{sec:comp_meas}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.61\pm 0.04$ per host.
-The UPG abundance in our sample is $N_{\rm UPG} = 0.47\pm 0.04$ per host.
+After correcting for background contamination (see \S \ref{sec:bkg}) and completeness (see \S \ref{sec:comp_meas}), the UDG abundance of MW analogs is $N_{\rm UDG} = 0.44\pm 0.05$ per host.
+The UPG abundance in our sample is $N_{\rm UPG} = 0.31\pm 0.04$ per host.
 Here we neglect the fact that the number of satellites contained within the virial sphere is different from the number of satellite within a projected cylinder with virial radius (the so-called deprojection factor, \citealt{vdBurg2017}).
@@
 If we only take UDGs more massive than our detection limit $M_\star > 10^{6.5}\ M_\odot$, we obtain slightly lower UDG abundances of $N_{\rm UDG, 6.5}^{\rm ELVES} \approx 0.36\pm0.11$.
-\citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}.
 Because both SAGA and ELVES select satellites based on distance measurements and do not correct for completeness, we interpret their UDG abundances as lower limits.
-We note that \citet{Roman2017b} do not estimate the background contamination fraction and do correct for completeness.
-
-Because there is little literature on UPGs, we only compare our UPG abundance with ELVES.
-In ELVES, we take the 351 satellites with secure distances in 30 MW analogs and identify 36 UPGs associated with 20 hosts.
-Thus the UPG abundance fraction in ELVES is $N_{\rm UPG}^{\rm ELVES} = 1.20 \pm 0.20$.
-When only selecting UPGs with $M_\star > 10^{6.5}\ M_\odot$, we obtain 23 UPGs in 30 MW analogs, thus $N_{\rm UPG, 6.5}^{\rm ELVES} = 0.77 \pm 0.16$, which is slightly higher than our UPG abundance, but is consistent our result within $1\sigma$.
-
-We plot the UDG abundances of these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017}.
+\citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}, but it is hard to calculate a UDG abundance due to small number statistics.
+Our UDG abundance is consistent with the value in ELVES survey, but higher than the value from SAGA.
+This might be explained by the different photometric depths of data used.
+As pointed out by \citet{CarlstenELVES2022,Font2022}, the SAGA survey reaches a surface brightness depth of $\sbeffr\approx 25\ \sbunit$, which is $\sim 2.5\ \sbunit$ shallower than the ELVES survey and this work.
+It is probable that SAGA missed some fraction of red and lower surface brightness galaxies.
+%We note that \citet{Roman2017b} do not estimate the background contamination fraction and do correct for completeness.
+\jiaxuan{Due to different methods, completeness, depth, comparisons can be hard}
+
+We plot the UDG abundances from these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017}.
 The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray.
@@
 As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo-mass end, but this might be due to the small statistics in prior studies and the differences in completeness.
-Our UDG abundance is similar to the value in ELVES survey, but much higher than the value from SAGA.
-This might be explained by the different photometric depths of data used.
-As pointed out by \citet{CarlstenELVES2022,Font2022}, the SAGA survey reaches a surface brightness depth of $\sbeffr\approx 25\ \sbunit$, which is $\sim 2.5\ \sbunit$ shallower than the ELVES survey and this work.
-It is probable that SAGA missed some fraction of red and lower surface brightness galaxies.
 Our UDG abundance is marginally higher than the prediction from \citet{vdBurg2017} but is still consistent considering the large scatter of the power law.
@@
 We note that their surface brightness cut for UDGs is brighter than ours and thus they include more ``UDGs'' for MW-like hosts and have a shallower power law.
-One should be aware of the fact that literature results are not completeness corrected and background subtracted, and UDG definitions also vary across different studies.
+One should be aware of the fact that literature results are of different depths, often not completeness corrected and background subtracted, and UDG definitions also vary across different studies.
 These effects could significantly bias the results when combining them.
-Therefore we caution that the power law index here should not be over-interpreted.
+Therefore we caution that the UDG abundance and the power law index here should not be over-interpreted.
 
@@
 We find that the UDG abundance is slightly higher for hosts with higher halo mass and redder color, but the trend is stronger with host color.
+
+Because there is little literature on UPGs, we only compare our UPG abundance with ELVES.
+In ELVES, we take the 351 satellites with secure distances in 30 MW analogs and identify 36 UPGs associated with 20 hosts.
+Thus the UPG abundance fraction in ELVES is $N_{\rm UPG}^{\rm ELVES} = 1.20 \pm 0.20$.
+When only selecting UPGs with $M_\star > 10^{6.5}\ M_\odot$, we obtain 23 UPGs in 30 MW analogs, thus $N_{\rm UPG, 6.5}^{\rm ELVES} = 0.77 \pm 0.16$, which is slightly higher than our UPG abundance.
+
 \vspace{1em}
@@
 \ref{fig:mass_size}).
-Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.10 \pm 0.03$ and $f_{\rm UPG} \approx 0.08 \pm 0.03$.
+Then for our samples, the UDG (UPG) fraction is $f_{\rm UDG} \approx 0.07 \pm 0.02$ and $f_{\rm UPG} \approx 0.05 \pm 0.02$.
 In ELVES, among 351 satellites with secure distances in 30 MW analogs, we identify 13 UDGs associated with 10 hosts, and 36 UPGs associated with 20 hosts.
 Thus the UDG fraction in ELVES is $f_{\rm UDG}^{\rm ELVES} \approx 0.04 \pm 0.01$, the UPG fraction in ELVES is $f_{\rm UPG}^{\rm ELVES} \approx 0.10 \pm 0.02$.
-We further select ELVES galaxies with $M_\star > 10^{6.5}\ M_\odot$ and find the same UDG and UPG fractions.
+We further only select ELVES galaxies with $M_\star > 10^{6.5}\ M_\odot$ and find the same UDG and UPG fractions.
 We also compare our results with results in the Virgo cluster.
@@
 However, we note that \citet{Ferrarese2020} only survey the central 4 deg$^2$ of the Virgo cluster, which probably biases the UDG (UPG) fraction.
-It seems that our UDG abundance and fraction are higher than both ELVES and NGVS.
-Our UPG abundance and fraction are consistent with ELVES and NVGS.
-In the future, a systematic and careful comparison on UDG (UPG) fraction in different environments is needed.
+We interpret our UDG and UPG fractions to be consistent with ELVES and NGVS.
+However, we emphasize that it is challenging to compare across various searches due to the differences in the host sample selection, depth, completeness, and contamination estimation.
+In the future, a more systematic and careful comparison on UDG (UPG) fraction in different environments is needed.
 
@@
 Both size and stellar mass could have large uncertainties in the LSB regime.
-One also needs to apply a surface brightness cut (such as $\sbeff > 23.0\ \sbunit$ in this work) to make sure that the UPG sample is not contaminated by disk galaxies with high surface brightness due to the bulges.
+One also needs to apply a surface brightness cut (such as $\sbeff > 23.0\ \sbunit$ in this work) to make sure that the UPG sample is not dominated by disk galaxies with high surface brightness due to the bulges.
+In \S\ref{sec:bkg}, we find that the UPG sample has a higher contamination fraction than the UDG sample.
+Since the UPG definition does not preferentially exclude blue LSBGs, background disk galaxies are more easily to be identified as UPGs.
+Based on our test, a UPG sample with more aggressive cut (e.g., $>2\sigma$ above the average mass-size relation) would have a higher purity, but only possible when one have a much larger LSBG sample.
 
@@
 
-    \item After correcting for background contamination and completeness, the UDG abundance in MW analogs is $N_{\rm UDG} = 0.76\pm 0.04$ per host and the UPG abundance is $N_{\rm UPG} = 0.61 \pm 0.04$ per host.
-Our UDG abundance is slightly higher than that in ELVES, but much higher than that in SAGA.
-When considering the detection depth, our UPG abundance agrees with ELVES result within $1\sigma$.
+    \item After correcting for background contamination and completeness, the UDG abundance in MW analogs is $N_{\rm UDG} = 0.44\pm 0.05$ per host and the UPG abundance is $N_{\rm UPG} = 0.31 \pm 0.04$ per host.
+Our UDG abundance agrees with ELVES quite well, but is much higher than that in SAGA.
+We obtain a UPG abundance lower than that in ELVES.
 
@@
 
-    \item For a MW analog, on average, about 12\% of its satellites are UDGs and about 10\% of its satellites are UPGs.
-Although the UPG fraction is consistent with ELVES and NGVS, the UDG fraction is found to be higher than those in ELVES and NGVS.
+    \item For a MW analog, on average, about $7\%\pm2\%$ of its satellites are UDGs and about $5\%\pm2\%$ of its satellites are UPGs. Our UDG and UPG fraction are consistent with ELVES and NGVS.
 
@@
 2021M3F7A1084525, funded by the Korea government (MSIT).
+S.D.
+is supported by NASA through Hubble Fellowship grant HST-HF2-51454.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Incorporated, under NASA contract NAS5-26555.
 

### 2022-10-26 paper1.tex
Updates from Overleaf

@@
 
-%%
 \newcommand{\vdag}{(v)^\dagger}
@@
 \newcommand\latex{La\TeX}
-% \newcommand{\sbunit}{mag~arcsec$^{-2}$}
 \newcommand{\sbunit}{\mathrm{mag\ arcsec}^{-2}}
@@
 
-% \newcommand{\code}[1]{\textbf{\texttt{#1}}}
 \newcommand{\code}[1]{\texttt{#1}}
@@
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
-% \received{\today}
-% \revised{\today}
-% \accepted{\today}
-
-% \submitjournal{ApJ}
+\received{\today}
+\revised{\today}
+\accepted{\today}
+
+\submitjournal{ApJ}
 
@@
 Using Subaru's Hyper Suprime-Cam Strategic Survey Program, we perform a systematic search for low surface brightness galaxies and present novel and effective methods for detecting and modeling them.
-As a case study, we build a large sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$).
+As a case study, we surveyed 922 Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$) and build a large sample of satellites galaxies that are outliers in the mass-size relation.
 These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represent the tail of the satellite size distribution.
-We find that each MW analog hosts $N_{\rm UPG} = 0.31\pm 0.05$ ultra-puffy galaxies on average, which is consistent but slightly lower than the observed abundance at this halo mass in the Local Volume.
+We find that each MW analog hosts $N_{\rm UPG} = 0.31\pm 0.05$ ultra-puffy galaxies on average, which is consistent with but slightly lower than the observed abundance at this halo mass in the Local Volume.
 We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.44\pm0.05$ per host.
@@
 \subsubsection{False positive removal}\label{sec:non-par-measurement}
-% \begin{figure*}
-% 	\vbox{
-% 		\centering
-% 		\includegraphics[width=1.0\linewidth]{deblending_cuts.pdf}
-% 	}
-% 	\caption{The distribution of \code{scarlet} measurements for the LSBG candidates from our initial sample.
-We visually inspected 5,000 LSBG candidates and labeled them as \code{candy} (LSBGs with dwarf galaxy features), \code{galaxy} (higher surface brightness galaxies or galaxies with spiral galaxy features), and \code{junk} (false positives).
-We propose a selection based on size, color, surface brightness and morphology (dashed boxes) to effectively remove false positives but still achieve a high completeness.
-After such cuts (bottom panels), 97\% of false positives and 76\% of non-LSB galaxies are removed according to our visual inspection results.
-% 	}
-% 	\label{fig:deblending_cuts}
-% \end{figure*}
 
@@
 
-% \textbf{
-% Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives.
-}
-% \jiaxuan{Check if this is considered in the completeness.}
-
 \subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}
@@
 We also remove duplicate objects.
-In the final catalog, we are left with 2,510 LSBG candidates associated with 689 MW analogs as our final LSBG sample.
+In the final catalog, we are left with 2,510 LSBG candidates associated with 689 MW analogs (out of 922) as our final LSBG sample.
 The host number drops from 922 to 689 because many hosts in the prior sample has no true positives as their satellites.
@@
 It is probable that SAGA missed some fraction of red and lower surface brightness galaxies.
-%We note that \citet{Roman2017b} do not estimate the background contamination fraction and do correct for completeness.
-\jiaxuan{Due to different methods, completeness, depth, comparisons can be hard}
+On the other hand, ELVES includes several more massive hosts than our search and SAGA do, and consequently bias the UDG abundance.
 
@@
 The specific value above the average mass-size relation can be varied to probe different parts of the size distribution.
-We advocate studying the UPG population in both observations and simulations to explore samples with different ``puffiness'' (e.g., comparing UPG with $1.5\sigma$ with UPG with $2\sigma$).
+We advocate studying the UPG population in both observations and simulations to explore samples with different ``puffiness'' (e.g., comparing UPG at $1.5\sigma$ and $2\sigma$ from the mass-size relation).
 
@@
 In \S\ref{sec:bkg}, we find that the UPG sample has a higher contamination fraction than the UDG sample.
-Since the UPG definition does not preferentially exclude blue LSBGs, background disk galaxies are more easily to be identified as UPGs.
-Based on our test, a UPG sample with more aggressive cut (e.g., $>2\sigma$ above the average mass-size relation) would have a higher purity, but only possible when one have a much larger LSBG sample.
+Since the UPG definition does not preferentially exclude blue LSBGs, many background disk galaxies can be misidentified as UPGs.
+Based on our tests, a UPG sample with a more aggressive cut (e.g., $>2\sigma$ above the average mass-size relation) would have a higher purity, but building a significant sample of these is only possible when one has a much larger LSBG sample.
 
 Our definition of UPG greatly benefits from the well-measured mass-size relation in \citet{ELVES-I} and the fact that this mass-size relation is independent of galaxy color and morphology.
-However, such mass-size relations are not available for all galaxy mass ranges and environments (in field or in group/cluster).
-\citet{ELVES-I} derive the mass-size relation of satellite galaxies of MW analogs below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$.
-The mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is not well measured, nor is any dependence on color, morphology, or environment.
+However, such mass-size relations are not always available for all galaxy mass ranges and environments (in the field or in groups and clusters).
+\citet{ELVES-I} derive the mass-size relation of satellite galaxies of MW analogs below $M_\star \sim 10^{8.5}\ M_\odot$, and find it similar to the mass-size relation of field late-type dwarfs in \citet{Karachentsev2013}.
+\citet{Lange2015} have relatively good constraints on the mass-size relation above $M_\star \sim 10^{9}\ M_\odot$.
+However, the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9.5}\ M_\odot$ has been shown to be very shallow \citep{SmithCastelli2008,Misgeld2008,Misgeld2011,Eigenthaler2018}, and its dependence on color, morphology, or environment is still unclear.
 In this work, we simply extrapolate the \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$.
@@
 With enough statistics in the future, one might be able to characterize the shape of the large-size tail and define UPGs based on the percentiles of the size distribution \citep{Greene2022}.
-However, there are also other size definitions which help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Mowla2019,Trujillo2020,Chamba2022} and can further benefit construct UPG samples.
+However, there are also other size definitions which may help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Mowla2019,Trujillo2020,Chamba2022} and can further benefit construct UPG samples.
 

### 2022-10-26 paper1.tex
right before submitting to arxiv

@@
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{\today}
-\revised{\today}
-\accepted{\today}
+% \received{\today}
+% \revised{\today}
+% \accepted{\today}
 
@@
 \citet{Lange2015} have relatively good constraints on the mass-size relation above $M_\star \sim 10^{9}\ M_\odot$.
-However, the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9.5}\ M_\odot$ has been shown to be very shallow \citep{SmithCastelli2008,Misgeld2008,Misgeld2011,Eigenthaler2018}, and its dependence on color, morphology, or environment is still unclear.
+However, the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9.5}\ M_\odot$ has been shown to be very shallow for red galaxies \citep{SmithCastelli2008,Misgeld2008,Misgeld2011,Eigenthaler2018}, and its dependence on color, morphology, or environment is still unclear.
 In this work, we simply extrapolate the \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$.

### 2023-06-01 paper1.tex
finished my own edits to respond the referee report

@@
-\documentclass[twocolumn,astrosymb,twocolappendix]{aastex631}
+\documentclass[twocolumn,astrosymb,twocolappendix,linenumbers]{aastex631}
 
@@
 \newcommand{\jiaxuan}[1]{\textcolor{orange}{\textbf{Jiaxuan: #1}}}
+\newcommand{\emphasize}{\textcolor{orange}}
 
@@
 \usepackage{amsmath,amssymb}
-
+\usepackage{soul}
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
@@
 
-\author[0000-0002-1841-2252]{Rachael Beaton}
+\author[0000-0002-1691-8217]{Rachael Beaton}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
@@
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
-\author[0000-0002-1841-2252]{Andy Goulding}
+\author[0000-0003-4700-663X]{Andy Goulding}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
@@
 \affiliation{Oskar Klein Centre for Cosmoparticle Physics, Department of Physics, Stockholm University, Stockholm SE-106 91, Sweden}
-\author[0000-0002-1841-2252]{Erin Kado-Fong}
+\author[0000-0002-0332-177X]{Erin Kado-Fong}
 \affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
@@
 Using Subaru's Hyper Suprime-Cam Strategic Survey Program, we perform a systematic search for low surface brightness galaxies and present novel and effective methods for detecting and modeling them.
-As a case study, we surveyed 922 Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$) and build a large sample of satellites galaxies that are outliers in the mass-size relation.
+As a case study, we surveyed 922 Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$) and build a large sample of satellite galaxies that are outliers in the mass-size relation.
 These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represent the tail of the satellite size distribution.
@@
 Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019,Danieli2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,Roman2021,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}.
-There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Danieli2019DF2,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Pandya2018,Villaume2022}.
+There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Danieli2019DF2,Wasserman2019,ManceraPina2019b,Keim2022,ManceraPina2022,Kong2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC,Gannon2022}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Pandya2018,Villaume2022}.
 We refer to LSBGs as objects selected purely by surface brightness without distance information.
@@
 Various mechanisms have been proposed to explain the presence of large, diffuse galaxies (as mass-size outliers) across different environments.
-In the field (i.e, in isolation), their large sizes might be a result of stellar feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites; \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}.
+In the field (i.e, in isolation), their large sizes might be a result of stellar feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites; \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,ManceraPina2020,Benavides2022,Kong2022}.
 In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019}, via adiabatic expansion due to mass loss \citep{Tremmel2020}, or even via a bullet-dwarf collision \citep{vandokkum2022Nat,vanDokkum2022GC}.
@@
 It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness or larger size.
-A straightforward way to answer these questions is to compare mass-size outliers with ``normal'' low mass galaxies which have been studied extensively.
+A straightforward way to answer these questions is to compare mass-size outliers with ``normal'' low-mass galaxies which have been studied extensively.
 
@@
 We further build a large sample of mass-size outliers that are likely satellites of MW-mass hosts in the nearby Universe.
-We propose a new definition for mass-size outliers, dubbed ``\textit{ultra-puffy galaxies}'' (UPGs), based on the observed mass-size relation in the Local Volume using the ELVES sample.
+We propose a new definition for mass-size outliers, dubbed ``\textit{ultra-puffy galaxies}'' (UPGs), based on the observed mass-size relation of satellites of MW analogs in the Local Volume using the ELVES sample.
 This concept is less affected by the galaxy color and provides a robust avenue to study the mass-size outlier population.
@@
 Our results seek to shed light on the role of environment on the formation of large diffuse dwarf galaxies.
-%By comparing mass-size outliers with normal satellites and simulations, our results seek to shed light on the formation and evolution of the large diffuse galaxies.
-
-% The occurrence rate of UDGs in these low-density environments is unknown, and whether UDGs are quenched in such a regime has not been explored.
-With a sample of UDGs around MW-like hosts, we can compare the structural parameters, quenched fractions, nucleation fractions, and radial distributions with normal satellites in the nearby universe \citep[e.g.,][]{SAGA-II,CarlstenELVES2022}, to shed light on questions about the formation and evolution of the UDGs.
 
@@
 Section \ref{sec:summary} presents a summary of this work and prospects for the future.
-In a companion paper (Li et al., to be submitted), we discuss the size distributions, spatial distributions, and quenching of UDGs and UPGs.
+In a companion paper \citep{Li2023}, we discuss the size distributions, spatial distributions, and quenching of UDGs and UPGs.
 
@@
 
-In this work, we use the \code{Wide} layer coadd data from the Public Data Release 2 (PDR2, also known as \code{S18A}, \citealt{Aihara2018}) of the HSC survey.
+In this work, we use the \code{Wide} layer of the coadd data from the Public Data Release 2 (PDR2, also known as \code{S18A}, \citealt{Aihara2018}) of the HSC survey.
 It covers $\sim 300\ \rm{deg}^2$ in all five bands, which is 1.5 times larger than the dataset (\code{S16A}) analyzed in \citet{Greco2018}.
@@
 The unprecedented depth and careful sky subtraction make PDR2 an ideal dataset to study low surface brightness galaxies.
-In this work we use the PSF models generated by \code{hscPipe}.
+In this work we take the \emphasize{point-spread function (PSF)} models in \emphasize{\code{hscPipe} \citep{Bosch2018}, where the Point Spread Function Extractor \citep[\texttt{PSFEx},][]{Bertin2011} takes a star catalog and generates the PSF model.}
 
@@
 In \code{statmorph}, the effective radius is calculated using elliptical apertures, where the ellipticity $\varepsilon$ is determined by calculating the second moment of the image.
-The total magnitudes are simply calculated by summing up the model flux in each band, and colors are defined using total magnitudes.\footnote{A Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by extrapolating the surface brightness profile to $r\to 0$.
-We define the average surface brightness within the effective radius as
+The total magnitudes are simply calculated by summing up the model flux in each band, and colors are defined using total magnitudes.\footnote{A Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by \emphasize{linearly extrapolating the surface brightness profile to $r\to 0$ using \code{scipy} function \footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.interp1d.html}} \citep{scipy}.} We define the average surface brightness within the effective radius as
 \begin{equation}\label{eq:mu_eff}
@@
 We refer the reader to \citet{statmorph} for more details on their definitions and implementations.
-All the morphological and structural parameters are measured in the $g$ band.
+\emphasize{\st{All the morphological and structural parameters are measured in the $g$ band.}}
 
@@
 The color cuts here are more restrictive than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and high redshift galaxies.
-We not only remove objects with small sizes, but also exclude objects with large size and very low surface brightness because they are mostly spurious objects.
+We not only remove objects with small sizes, but also exclude objects with large sizes and very low surface brightness because they are mostly spurious objects.
 After such cuts, there are 200 \code{junk} and 1407 \code{non-junk} remaining.
@@
 However, our measurement-based method is more intuitive, reproducible, and transferable compared with many ML methods.
-We will explore machine learning methods and compare with our deblending cuts in future work.
+We will explore machine learning methods and compare them with our deblending cuts in future work.
 Future work will also utilize information about Milky Way dust to exclude spurious detection on Galactic cirrus \citep[e.g.,][]{Zaritsky2021,Zaritsky2022}.
@@
 For the size range of $3\arcsec < r_e < 14\arcsec$, we are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.
-Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on the \sersic{} model tests still sets a baseline on the real completeness.
+Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on the \sersic{} model tests still sets a baseline for the real completeness.
 In the future, we might be more capable of generating realistic LSBGs using deep learning techniques.
@@
 They reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$ assuming a Sersic index $n \approx 1$.
-\citet{vdBurg2017} searched for LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
-\citet{Zaritsky2021} focus on searching for LSBGs in the SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) images and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$ for $n=1$.
+\emphasize{\citet{vdBurg2016} survey eight galaxy clusters at $0.044 < z < 0.063$ using CFHT data and achieve $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$.
+\citet{vdBurg2017} search for LSBGs from the ESO Kilo-Degree Survey data and achieve similar completeness as in \citet{vdBurg2016}.
+\citet{ManceraPina2019a} also search UDGs in nearby clusters using the 2.5-m Issac Newton Telescope (INT) and achieve $\sim 50\%$ completeness at $\sbeffr\approx 26.5\ \sbunit$ or equivalently $\sbeff \approx 27.1\ \sbunit$.} \citet{Zaritsky2021} focus on searching for LSBGs in the SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) images and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$ for $n=1$.
 Their lower completeness might be explained by the fact that they remove a large fraction of the sky contaminated by Galactic dust.
-\citet{Tanoglidis2021} conducted an LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
+\citet{Tanoglidis2021} conduct an LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data and conclude an overall completeness of $\sim 40\%$ by comparing their catalog with the deeper observations in the Fornax cluster.
 \citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but a much lower completeness for $\sbeff > 26.5\ \sbunit$.
@@
 The main results are summarized in Figure \ref{fig:meas_err}, where the colors show the bias terms as a function of the measured size and surface brightness.
-The size and surface brightness bias grows with increasing surface brightness.
+The size and surface brightness bias grow with increasing surface brightness.
 The bias term is not a monotonic function of size because the size here in Figure \ref{fig:meas_err} is not intrinsic size.
@@
 \section{Mass-size outliers Around Milky-Way analogs}\label{sec:sample_construction}
+
+\jiaxuan{Need to clearly cite \citet{Lim2020}, also cite \citet{LaMarca2022,Venhola2022}. also \citep{Trujillo2017,ManceraPina2018} this issue wont manifest since every UDG is quenched in clusters.}
+
 The goal of this paper is to study the mass-size outliers in the satellite systems of MW-like galaxies.
 However, distance information is needed to convert the observed size and magnitude to the physical size and stellar mass.
-It is well-known that getting the distances to LSBGs is one of the major obstacles for studying their properties.
-Beside direct distance measurements (e.g., SAGA, ELVES, \citealt{Kadowaki2021}), it is common to assume a distance to an LSBG by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
-A statistical background subtraction is then needed to account for the contribution from background and foreground sources.
-Furthermore, cross-correlation between an LSBG sample and a host galaxy sample can also reveal the distance distribution of LSBGs \citep{Greene2022}.
+It is well-known that getting the distances to LSBGs is one of the major obstacles to studying their properties.
+Besides direct distance measurements (e.g., SAGA, ELVES, \citealt{Kadowaki2021}), it is common to assume a distance to an LSBG by associating it with a host galaxy based on the projected angular distance \citep[e.g.,][]{vanDokkum2015,vdBurg2016,Wang2021,Zaritsky2022,Nashimoto2022}.
+Statistical background subtraction is then needed to account for the contribution from background and foreground sources.
+Furthermore, the cross-correlation between an LSBG sample and a host galaxy sample can also reveal the distance distribution of LSBGs \citep{Greene2022}.
 These methods are also complemented by recent machine learning techniques \citep{Baxter2021,xSAGA-I}.
@@
 In this work, we choose the stellar mass range of our MW analog sample to be $10.2 < \log\, M_\star/M_\odot < 11.2$ based on NSA stellar mass, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($M_{\star, \mathrm{MW}}\approx 10^{10.7}\ M_\odot$, \citealt{Licquia2015}).
-MW analogs selected using this definition are very close to those in SAGA but are slightly less massive than the ELVES hosts since ELVES has several groups more massive than SAGA hosts.
+MW analogs selected using this definition are very close to those in SAGA but are slightly less massive than the ELVES hosts since ELVES has several groups more massive than SAGA hosts\footnote{\emphasize{We note that it is also possible to select MW analogs in linear stellar mass such as $1.5 \times 10^{10} < M_\star < 8.5\times 10^{10}\,M_\odot$.
+Compared to our logarithmic selection, a linear selection excludes 10\% of high-mass MW analogs at $10.9 < \log M_\star/M_\odot < 11.2$, and will result in lower abundances of UDGs and UPGs.}}.
 We do not discriminate between isolated or paired hosts.
@@
 The depth of HSC limits our detection to below $z \approx 0.04$ because dwarf galaxies will be too small and too faint to be detected beyond that distance\footnote{Our search only includes objects larger than $r_e\approx 2\arcsec$, which corresponds to $M_\star \sim 10^{8.5}\ M_\odot$ at $z=0.04$ assuming the \textit{average} mass-size relation from \citet{ELVES-I}.
-Going to higher redshift will make it more difficult to detect low-mass dwarfs.}.
+Going to a higher redshift will make it more difficult to detect low-mass dwarfs.}.
 We also exclude galaxies at $z<0.01$ because (1) the number of mass-size outliers will be very small due to the small volume; (2) their large angular size makes them more vulnerable to being shredded during detection, so including them will introduce a number of spurious LSB objects.
@@
 We then select those within HSC PDR2 footprint and match them to the initial LSBG sample (described in \S \ref{sec:detection}, before the deblending step) as follows.
-For a given MW-like galaxy, we first calculate a virial mass assuming the stellar-to-halo mass relation in \citet{Behroozi2010} then calculate the corresponding virial radius $R_{\rm vir}$.
-It turns out that 40\% of our hosts have virial radii larger than 300 kpc, which is commonly used for the virial radius of the Milky Way.
+
+For a given MW-like galaxy, \emphasize{we calculate its virial mass based on the stellar-to-halo mass relation (SHMR) in \citet{Behroozi2010} using \href{https://halotools.readthedocs.io/en/latest/index.html}{\code{halotools}} \citep{Hearin2017}.
+The viral mass is defined to be the enclosed mass with $\rho > \Delta_{\rm vir}(z) \rho_c(z)$, where the virial overdensity only depends on cosmological parameters and redshift \citep{Bryan1998}.
+Then we convert virial mass to virial radius $R_{\rm vir}$ using the virial overdensity}.
+It turns out that 40\% of our hosts have virial radii larger than 300 kpc, which is commonly used for the virial radius of the Milky Way.\footnote{\emphasize{We note that the SHMR from abundance matching might overestimate the halo mass for massive spirals \citep[e.g.,][]{Posti2019,Mancera2022b}, implying that our sample might include LSBGs beyond the virial radius.
+We also compare different SHMRs \citep[e.g.,][]{Moster2013} and do not find significant differences in the distribution of $R_{\rm vir}$.}}
+
 Then we identify any LSBG that falls inside the projected virial radius of a host.
-If one LSBG is matched to multiple hosts, we assign it to the nearest host based on the separation normalized by host virial radius.
+\emphasize{About 40\% of LSBGs are matched with 2 hosts and about 15\% of them are matched with 3 or more hosts.} If an LSBG is matched to multiple hosts, we assign it to the nearest host based on the separation normalized by the host virial radius.
 There are 922 MW-like hosts and 10,579 LSBG candidates associated with them.
@@
 In the final catalog, we are left with 2,510 LSBG candidates associated with 689 MW analogs (out of 922) as our final LSBG sample.
-The host number drops from 922 to 689 because many hosts in the prior sample has no true positives as their satellites.
+The host number drops from 922 to 689 because many hosts in the prior sample have no true positives as their satellites.
 We note that these LSBGs are matched to MW hosts in projection but do not have direct distance measurements, and we have not applied any statistical background correction at this stage.
@@
 The stellar masses of cross-matched LSBG are derived from the Spergel model fitting and a relation between color and mass-to-light ratio $M_{\star}/L$ from \citet{Into2013}:
+
 \begin{align*}
@@
 \end{align*}
-Because we have both $g-r$ and $g-i$ color available from the model fitting, we use the average $M_{\star}/L$ derived from the two colors to calculate stellar mass.
+
+Because we have both $g-r$ and $g-i$ colors available from the model fitting, we use the average $M_{\star}/L$ derived from the two colors to calculate stellar mass.
 We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}.
+\emphasize{We note that the stellar mass derived using the color-$M_\star/L$ relation from \citet{Herrmann2016,Du2020} is $\sim 0.2$ dex lower than the one derived using \citet{Into2013} relation.}
 
@@
 In general, the slope of the mass-size relation in the nearby Universe has been shown to be color- and morphology-dependent for galaxies above $M_\star > 10^{9}\ M_\odot$: blue star-forming galaxies have a shallower mass-size relation than do red quenched galaxies \citep[e.g.,][]{Lange2015}.
-In the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$), \citet{ELVES-I} derive the mass-size relation from the satellites of MW analogs in the Local Volume and show that the average mass-size relation is quite universal: the slope and intercept are not sensitive to the color or morphology of dwarf galaxies.
+In the dwarf galaxy regime ($10^{5.5} < M_\star/M_\odot < 10^{8.5}$), \citet{ELVES-I} derive the mass-size relation from the satellites of MW analogs in the Local Volume and show that the average mass-size relation is quite universal: the slope and intercept are not sensitive to the color or morphology of dwarf galaxies.
 Residuals from the mass-size relation follow a log-normal distribution reasonably well.
 This fact allows us to define a subset of dwarf galaxies that are outliers with respect to the average mass-size relation.
-It is worth noting that a definition based on the mass-size relation was already used in simulation studies where the absolute sizes were uniformly too large such that size outliers could only be selected relative to the simulated mass-size relation \citep[e.g.,][]{Benavides2021,Benavides2022}.
+\emphasize{It is worth noting that in several works \citep[e.g.,][]{Lim2020,Venhola2022}, UDGs in galaxy clusters are defined as the outliers of the scaling relations among size, surface brightness, and total luminosity.} A UDG definition based on the mass-size relation is also used in simulation studies where the absolute sizes were uniformly too large such that size outliers could only be selected relative to the simulated mass-size relation \citep[e.g.,][]{Benavides2021,Benavides2022}.
 
@@
 There are 362 LSBG candidates that fall $1.5\sigma$ above the ridge line of the mass-size relation.
-After removing spurious objects by another round of visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
-These UPGs are associated with 239 hosts.
+After removing spurious objects \emphasize{(e.g., shredded galaxy outskirts, cirrus, tidal feature, blends)} by another round of visual inspection and removing objects with completeness less than 0.1, we have 337 galaxies in our UPG sample.
+\footnote{\emphasize{For context, there are 155 (39) galaxies being $2\sigma$ ($3\sigma$) above the average mass-size relation.}} These UPGs are associated with 239 hosts.
 The total sky area occupied by UPG hosts (out to 1 $R_{\rm{vir}}$) is 32.37 deg$^{2}$.
@@
 The UDG sample is usually defined based on surface brightness and physical size of the galaxy.
-However, there are many different criteria in the literature: \citet{vanDokkum2015} define UDGs to have effective radii $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,Martin2019,Karunakaran2022b}.
+However, there are many different criteria in the literature: \citet{vanDokkum2015} define UDGs to have effective radii $r_e$ larger than 1.5 kpc and central surface brightness $\mu_0(g)$ fainter than $24.0\ \sbunit$; other groups also use the surface brightness at $r_e$ \citep[e.g.,][]{DiCintio2017,Cardona-Barrero2020} or \emphasize{the average surface brightness within $r_e$ to define UDGs \citep[e.g.,][]{Koda2015,Yagi2016,vdBurg2016,Leisman2017,ManceraPina2018,ManceraPina2019a,Martin2019,Karunakaran2022b}}.
 The size criterion also varies from $r_e > 1$ kpc to $r_e > 1.5$ kpc.
@@
 In this section, we compare the distributions of UDGs and UPGs on the size-surface brightness and mass-size planes to gain intuition on the differences between UDG and UPG definitions.
-Then we present the abundances of UDGs and UPGs and compare with the literature.
+Then we present the abundances of UDGs and UPGs and compare them with the literature.
 
@@
 The constant surface stellar mass density line is in purple, which is parallel to the solid lines.
+The dotted part of the green lines indicates where we linearly extrapolate the mass-size relation to define UPGs.
 \textit{Right panel}: The distributions of UDGs and UPGs on the mass-size plane.
@@
 For defining UDGs, a physical size cut and a surface brightness cut are needed.
-We show the $r_e = 1.5$ kpc cut as a horizontal gray band to acknowledge the fact that smaller galaxies with large size uncertainties are included in the UDG sample.
+We show the $r_e = 1.5$ kpc cut as a horizontal gray band \emphasize{(spanning from 1.1 kpc to 1.5 kpc)} to acknowledge the fact that smaller galaxies with large size uncertainties are included in the UDG sample.
 The slanted solid lines show the constant surface brightness lines with $\sbeff = 25.0\ \sbunit$ for two different colors ($g-i=0.4$ and $g-i=0.8$).
@@
 On the contrary, since the UPG definition does not have a hard surface brightness cut, it includes many galaxies that are more massive than UDGs provided they have an extraordinarily large size.
-We also note that the mass-size relation from \citet{ELVES-I} is extrapolated to define UPGs in $10^{8.5}\ M_\odot < M_\star < 10^9\ M_\odot$, where about 10\% our UPGs are located.
+We also note that the mass-size relation from \citet{ELVES-I} is extrapolated to define UPGs in $10^{8.5}\ M_\odot < M_\star < 10^9\ M_\odot$, where about 10\% our UPGs are located (dotted green lines in Figure \ref{fig:mass_size}).
 However, the mass-size relation might show color and morphology dependence for $M_\odot > 10^{8.5}\ M_\odot$.
-As a consequence, disk galaxies might contribute to the UPG sample at the high-mass end.
+\emphasize{As a consequence, disk galaxies might contribute to the UPG sample at the high-mass end.
+We visually checked the UPG sample and do find some blue UPGs resembling disk galaxies at the high-mass end.
+Spectroscopic follow-ups are needed to confirm whether they are just blue background galaxies.}
 
@@
 \citet{Roman2017b} identified 11 UDGs around three galaxy groups in the IAC Stripe 82 Legacy Survey \citep{Fliri2016}, but it is hard to calculate a UDG abundance due to small number statistics.
-Our UDG abundance is consistent with the value in ELVES survey, but higher than the value from SAGA.
+Our UDG abundance is consistent with the value in the ELVES survey, but higher than the value from SAGA.
 This might be explained by the different photometric depths of data used.
@@
 
-We plot the UDG abundances from these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017}.
+We plot the UDG abundances from these surveys in the left panel of Figure \ref{fig:n_udg}, together with the results for larger galaxy groups and clusters \citep{Koda2015,Munoz2015,Roman2017a,Roman2017b,Janssens2017,vdBurg2017,LaMarca2022}.
 The power-law regression result from \citet{vdBurg2017} $N_{\rm UDG} \propto M_h^{1.11\pm 0.07}$ is shown in gray.
-The UDG abundance of this work is highlighted as the red square.
+\emphasize{We also show the result from \citet{ManceraPina2018} $N_{\rm UDG} \propto M_h^{0.84\pm 0.07}$ as a blue-dashed line where they homogeneously combined the samples in \citet{vdBurg2016} and \citet{Roman2017b}.} The UDG abundance of this work is highlighted as the red square.
 As shown in Figure \ref{fig:n_udg}, the scatter in the $N_{\rm UDG}-M_h$ relation gets larger at the lower halo-mass end, but this might be due to the small statistics in prior studies and the differences in completeness.
@@
 
+% We note that \citet{Lim2020} define UDGs in the Virgo cluster as the outliers of the scaling relations of Virgo satellites.
+
 In Figure \ref{fig:mass_size}, we find that combining a hard physical size cut with a surface brightness cut carves out an interesting region of the mass-size plane that is complicated in two ways.
@@
 If one calculates the quenched fraction of UDGs as a function of stellar mass, it will be biased high because of this constant surface brightness cut in the UDG definition.
+\emphasize{These limitations of the original UDG definition are also discussed in \citet{Trujillo2017,ManceraPina2018}.}
 
@@
 
-    \item For a MW analog, on average, about $7\%\pm2\%$ of its satellites are UDGs and about $5\%\pm2\%$ of its satellites are UPGs. Our UDG and UPG fraction are consistent with ELVES and NGVS.
+    \item For a MW analog, on average, about $7\%\pm2\%$ of its satellites are UDGs and about $5\%\pm2\%$ of its satellites are UPGs. Our UDG and UPG fractions are consistent with ELVES and NGVS.
 
@@
 This paper presents the UDG and UPG sample and explores their abundances.
-In our Paper II (to be submitted), we study their size and spatial distributions and their star formation status.
+In our Paper II \citep{Li2023}, we study their size and spatial distributions and their star formation status.
 This study is focused on a small subset of LSBG candidates matched with MW analogs.
@@
 \section*{Acknowledgment}
-JL is grateful for discussions with Meng Gu, ChangHoon Hahn, Sihao Cheng.
+We thank the anonymous reviewer for useful comments which make the manuscript clearer.
+JL is grateful for the discussions with Meng Gu, ChangHoon Hahn, Sihao Cheng.
 The authors thank Yao-Yuan Mao for his \href{https://github.com/yymao/decals-image-list-tool}{tool} for visualizing the image cutouts.
@@
 Typically, convergence is achieved after $\sim 50$ steps of optimization and the whole modeling process takes about 40s for a typical LSBG.
-It takes longer when the target galaxy has large angular size since more peaks are modeled.
+It takes longer when the target galaxy has a large angular size since more peaks are modeled.
 We note that \code{scarlet} only finds the maximum likelihood estimation of the model instead of deriving the full posteriors, thus a good initialization becomes especially important for fast convergence.
@@
 		\centering
-		\includegraphics[width=0.75\linewidth]{spergel_sersic_calib.pdf}
+		\includegraphics[width=0.85\linewidth]{spergel_sersic_calib.pdf}
 	}
@@
 We fit a Spergel profile to each \sersic{} while fixing the total luminosity and half-light radius.
-The left panel shows the best-fit Spergel index $\nu$ as a function of \sersic{} index $n$.
+The black line in the left panel shows the best-fit Spergel index $\nu$ as a function of \sersic{} index $n$.
+We also provide a symbolic approximation to this relation in \eqref{eq:symbolic}, shown as the gray dash-dotted line.
 In the right panel, two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) are shown.
@@
 
-To study the correspondence between \sersic{} and Spergel profiles, we generate \sersic{} profiles with different \sersic{} indices, and try to fit Spergel profiles to \sersic{} models.
-The \sersic{} index ranges from $n=0.5$ to $n=4.5$, and both profiles are normalized using $r_e$.
+To study the correspondence between \sersic{} and Spergel profiles, \emphasize{we generate \sersic{} 1-D profiles with different \sersic{} indices using \code{astropy}\footnote{\url{https://docs.astropy.org/en/stable/api/astropy.modeling.functional_models.Sersic1D.html}}, and try to fit the \sersic{} profiles using the Spergel model}.
+The \sersic{} index ranges from $n=0.5$ to $n=4.5$, and both profiles are normalized \emphasize{at the half-light radius} (see the right panel in Figure \ref{fig:spgl_calib}).
 For each \sersic{} profile, we calculate the total luminosity $L_0$ according to \eqref{eq:sersic_lum} and plug it into the Spergel profile \eqref{eq:spergel} as a fixed value.
 Therefore, only the Spergel index $\nu$ is allowed to vary during the fitting.
-The best-fit Spergel index $\nu$ as a function of \sersic{} index $n$ is shown in the left panel of Figure \ref{fig:spgl_calib}.
-As two examples, we show two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) in the right panel.
+\emphasize{The fitting uses the least-square fitting with Levenberg-Marquardt algorithm implemented in \code{astropy.modeling.fitting}\footnote{\url{https://docs.astropy.org/en/stable/api/astropy.modeling.fitting.LevMarLSQFitter.html\#astropy.modeling.fitting.LevMarLSQFitter}}, which is a commonly-used robust algorithm to solve non-linear least square fitting problems.} The best-fit Spergel index $\nu$ as a function of \sersic{} index $n$ is shown in the left panel of Figure \ref{fig:spgl_calib}.
 A Spergel profile with $\nu=0.5$ is exactly an exponential profile with $n=1$.
 The de Vaucouleurs profile \citep{deVaucouleurs1948} with $n=4$ can be approximated by a Spergel profile with $\nu=-0.74$.
-
-As shown in Figure \ref{fig:spgl_calib}, a \sersic{} profile with small \sersic{} index ($0.5 < n < 1.5$) can be well-approximated by a Spergel profile, although the Spergel profile seems to be more extended than \sersic{} in the outskirts.
-For a \sersic{} profile with high \sersic{} index, the approximation gets worse at both small and large radii.
+As two examples, we show two \sersic{} profiles (solid) and their best-fit Spergel profiles (dash-dotted) in the right panel.
+\emphasize{Overall, the Spergel profile provides a good approximation for the \sersic{} profile.
+}
+
+As shown in Figure \ref{fig:spgl_calib}, a \sersic{} profile with a small \sersic{} index ($0.5 < n < 1.5$) can be well-approximated by a Spergel profile, although the Spergel profile seems to be more extended than \sersic{} in the outskirts.
+For a \sersic{} profile with a high \sersic{} index, the approximation gets worse at both small and large radii.
 Overall, the Spergel profile is a good approximation to \sersic{} from $n\approx 0.5$ to $n\approx 4.5$.
+\emphasize{Using the symbolic regression package \code{PySR} \citep{Cranmer2023}, the best-fit relation between $n$ and $\nu$ for $0.5<n<4.5$ is given as follows:}
+\begin{equation}\label{eq:symbolic}
+    \nu = 1.06\,n^{-2.5} \cos(\sin(3.74/n))^{1/2} - 0.365\,n^{1/2}
+\end{equation}
+
 It is well-known that the light profiles of low-mass galaxies are quite flat and can be described using \sersic{} profiles with $0.5 < n < 1.5$ \citep[e.g.,][]{vanDokkum2015,Lange2015,Greco2018,Zaritsky2021,ELVES-I}.
-It is thus reasonalbe to use Spergel profiles to model the LSBGs (\S\ref{sec:modeling}) and enjoy its convenience in Fourier space.
+It is thus reasonable to use Spergel profiles to model the LSBGs (\S\ref{sec:modeling}) and enjoy its convenience in Fourier space.
 
@@
 
-To estimate the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies into the raw images and going through the entire data reduction pipeline.
-This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}.
-However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}.
+To estimate the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles into the coadd images.
+\emphasize{The mock galaxies are generated using \texttt{GalSim} \citep{Rowe2015} and are injected after being convolved with HSC PSF generated by \code{hscPipe}.
+We directly inject the mock galaxies into the coadd images without adding extra noise.
+The galaxies are placed randomly on the image but we require all mock galaxies to be separated by at least 80\arcsec{} from each other to minimize the impact of mock galaxies on the image noise properties.
+We have also done extensive tests on injecting mock galaxies into the raw images, adding Poisson noise, and going through the entire data reduction pipeline using \code{SynPipe} \citep{Huang2018synpipe}.
+This is very expensive in terms of both CPU time and disk space since we must run the full \code{hscPipe}.
+However, we find no noticeable difference in the completeness between this method and the direct injection to coadd images.}
+
 To resemble the real LSBG population in \citetalias{Greco2018}, we generate mock galaxies following uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$).
 They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.
-Then we run the detection step as described in \S \ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
+\emphasize{The ranges spanned by these colors and \sersic{} indices cover most of the observed LSBGs in \citetalias{Greco2018}.} Then we run the detection step described in \S \ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.
 We split the size and surface brightness range into 15 bins with $\Delta r_e = 0.86\arcsec$, $\Delta \sbeff = 0.33\ \sbunit$, and interpolate over bins using an isotropic Gaussian kernel with $\sigma = 0.5$.
@@
 We find negligible dependence of detection completeness on \sersic{} index, color, and ellipticity.
-Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
+Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulations where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps).
 We find the completeness declines for $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample.
@@
 The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 \cdot (g-i) + \mathcal{N}(0, 0.03^2)$.
+\emphasize{This mock galaxy population represents the real UDG/UPG population well.
+To be specific, the Gaussian color prior covers 86\% of the UPGs within $1.5\sigma$, the ellipticity prior covers 98\% of them, and the \sersic{} index prior covers 60\% of them.}
 We measure the size and surface brightness on the scarlet models of the mock galaxies, then we apply the deblending cuts.
@@
 For $r_e$, we calculate the relative bias $\Delta r_e / r_e$ instead because it is less dependent on the angular size.
-Then we interpolate over the grid using a multi-quadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}.
+Then we interpolate over the grid using a multi-quadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}} with \code{epsilon=0.5, smooth=1}.
 Unlike \citet{Zaritsky2021} where they fit models in 4-D space, we find interpolation works well enough in 2D and do not use polynomial fitting to avoid meaningless results outside of the fitting range.
@@
 $\log\ M_\star$ & $M_\odot$ & Stellar mass of UDG (UPG) \\
+\emphasize{$\sigma(\log\ M_\star)$} & $M_\odot$ & Uncertainty of stellar mass\\
 comp & & Completeness \\

### 2023-06-02 paper1.tex
shared with coauthors

@@
 In Section \ref{sec:results}, we compare the UDGs and UPGs on the mass-size plane.
-We calculate their abundances and compare with the literature (\S \ref{sec:n_udg}).
+We calculate their abundances and compare them with the literature (\S \ref{sec:n_udg}).
 Based on these results, we further argue that we should move beyond UDGs and adopt the UPG definition in Section \ref{sec:discussion}.
@@
 The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the search completeness and purity by adding several new steps, which are highlighted in this section.
-We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for the mass-size outlier sample construction.
+We outline the major steps below and refer the readers who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for the mass-size outlier sample construction.
 
@@
 The morphology image of each source is limited by a bounding box.
-We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from center to outskirts (monotonicity constraint).
+We assume two constraints when running \code{scarlet}: all sources have positive fluxes (positivity constraint) and the light profiles of all sources monotonically decrease from the center to the outskirts (monotonicity constraint).
 The monotonicity constraint is over-simplified for well-resolved galaxies with complicated structures, but for objects in our sample this assumption still holds for most cases and provides an effective and robust way to deblend overlapping sources.
@@
 One of the most important diagnostics is the effective radius of the object.
-In this paper, we refer to effective radius as the circularized effective radius $r_{e}$, defined as the $r_{e} = r_{\rm eff, sma} \sqrt{b/a}$ where $r_{\rm eff, sma}$ is the effective radius measured along the semi-major axis of the aligned elliptical isophotes, and $b/a$ is the axis ratio of the isophotes.
-In \code{statmorph}, the effective radius is calculated using elliptical apertures, where the ellipticity $\varepsilon$ is determined by calculating the second moment of the image.
-The total magnitudes are simply calculated by summing up the model flux in each band, and colors are defined using total magnitudes.\footnote{A Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by \emphasize{linearly extrapolating the surface brightness profile to $r\to 0$ using \code{scipy} function \footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.interp1d.html}} \citep{scipy}.} We define the average surface brightness within the effective radius as
+In this paper, we refer to the effective radius as the circularized effective radius $r_{e}$, defined as the $r_{e} = r_{\rm eff, sma} \sqrt{b/a}$ where $r_{\rm eff, sma}$ is the effective radius measured along the semi-major axis of the aligned elliptical isophotes, and $b/a$ is the axis ratio of the isophotes.
+\footnote{\emphasize{We note that some authors use $r_{\rm eff, sma}$ as effective radius.
+There is no consensus on which choice is better in the literature.}} In \code{statmorph}, the effective radius is calculated using elliptical apertures, where the ellipticity $\varepsilon$ is determined by calculating the second moment of the image.
+The total magnitudes are simply calculated by summing up the model flux in each band, and colors are defined using total magnitudes.\footnote{A Galactic extinction correction is not applied at this point.} The central surface brightness $\mu_0$ is measured by \emphasize{linearly extrapolating the surface brightness profile to $r\to 0$ using \code{scipy} function\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.interp1d.html}} \citep{scipy}.} We define the average surface brightness within the effective radius as
 \begin{equation}\label{eq:mu_eff}
@@
 
-\jiaxuan{Need to clearly cite \citet{Lim2020}, also cite \citet{LaMarca2022,Venhola2022}. also \citep{Trujillo2017,ManceraPina2018} this issue wont manifest since every UDG is quenched in clusters.}
-
 The goal of this paper is to study the mass-size outliers in the satellite systems of MW-like galaxies.
@@
 \end{align*}
-
-Because we have both $g-r$ and $g-i$ colors available from the model fitting, we use the average $M_{\star}/L$ derived from the two colors to calculate stellar mass.
-We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}.
-\emphasize{We note that the stellar mass derived using the color-$M_\star/L$ relation from \citet{Herrmann2016,Du2020} is $\sim 0.2$ dex lower than the one derived using \citet{Into2013} relation.}
+\emphasize{\citet{Kado-Fong2022} show that the UDG population can be described by the color-$M_\star/L$ relation from \citet{Into2013}.
+The stellar mass of dwarf in the ELVES survey is also derived using this relation \citep{CarlstenELVES2022}.} In our case, because we have both $g-r$ and $g-i$ colors available from the model fitting, we use the average $M_{\star}/L$ derived from the two colors to calculate stellar mass.
+We assume the solar absolute magnitude in $g$-band to be 5.03 \citep{Willmer2018}.\footnote{\emphasize{We note that the stellar mass derived using the color-$M_\star/L$ relation from \citet{Herrmann2016} and \citet{Du2020} is $\sim 0.2$ dex lower than the one derived using \citet{Into2013} relation.
+We use \citet{Into2013} prescription in this work encouraged by the finding in \citet{Kado-Fong2022} and for being consistent with ELVES.}}
 
@@
 We visually checked the UPG sample and do find some blue UPGs resembling disk galaxies at the high-mass end.
-Spectroscopic follow-ups are needed to confirm whether they are just blue background galaxies.}
+Spectroscopic follow-ups are needed to confirm whether they are just blue background galaxies.} \emphasize{We also note that 7\% of UDGs and 3\% of UPGs have \sersic{} indices $n>1.5$.
+We believe these galaxies with large \sersic{} indices are mostly interlopers given the fact that $\sim$40\% of UDGs and UPGs are interlopers (see \S\ref{sec:bkg}).
+We do not consider this as an issue given their small contribution to the whole sample.}
 
@@
 
+\begin{figure*}
+	\vbox{ 
+		\centering
+		\includegraphics[width=0.9\linewidth]{figures/mock_sample_upg.pdf}
+	}
+    \caption{The distribution of UPGs (blue) and mock galaxies (red) in $g-i$ color, ellipticity, and \sersic{} index $n$.
+We translate the Spergel index to the \sersic{} index using the relation \eqref{eq:symbolic}.
+The mock galaxy population represents the real UDG/UPG population well.
+    }
+    \label{fig:mock_params}
+\end{figure*}
+
 In this appendix, we demonstrate that the Spergel profile can approximate the \sersic{} profile and provide a lookup table for the correspondence between \sersic{} index $n$ and Spergel index $\nu$.
@@
 The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 \cdot (g-i) + \mathcal{N}(0, 0.03^2)$.
-\emphasize{This mock galaxy population represents the real UDG/UPG population well.
+\emphasize{We show the distribution of mock galaxies and UPGs in Figure \ref{fig:mock_params}.
+This mock galaxy population represents the real UDG/UPG population well.
 To be specific, the Gaussian color prior covers 86\% of the UPGs within $1.5\sigma$, the ellipticity prior covers 98\% of them, and the \sersic{} index prior covers 60\% of them.}
